### 2018-10-04 Fsing/TestIdealsPaper/TestIdeals.tex
Update TestIdeals.tex
Added information about my grant at the time of the workshop in 2015

\documentclass{amsart}
\usepackage{calc,amssymb,amsthm,amsmath}
%\usepackage{mathtools}
\RequirePackage[dvipsnames,usenames]{xcolor}

\usepackage{fancyvrb}
\usepackage{hyperref}
\hypersetup{
bookmarks,
bookmarksdepth=3,
bookmarksopen,
bookmarksnumbered,
pdfstartview=FitH,
colorlinks,backref,hyperindex,
linkcolor=Sepia,
anchorcolor=BurntOrange,
citecolor=MidnightBlue,
citecolor=OliveGreen,
filecolor=BlueViolet,
menucolor=Yellow,
urlcolor=OliveGreen
}
\usepackage{xspace}
%\usepackage{rotating}
\interfootnotelinepenalty=100000

\usepackage{mabliautoref}
\usepackage{colonequals}
\frenchspacing
\input{kmacros3.sty}
\usepackage{stmaryrd}

\usepackage{verbatim}
\usepackage{enumerate}

\usepackage[normalem]{ulem}
%\usepackage{marginnote}

% TODO NOTES
\usepackage[textwidth=3.5 cm,textsize=small,shadow,
%disable
%%option disable removes the notes
]{todonotes}

\newcommand{\warning}[2][]
{\todo[color=red,caption={},#1]{#2}}
\newcommand{\details}[2][]
{\todo[linecolor=cyan,backgroundcolor=cyan!40, caption={},#1]{#2}}
\newcommand{\postit}[2][]
{\todo[linecolor=orange,backgroundcolor=yellow!40, caption={},#1]{#2}}
\newcommand{\myexample}[2][]
{\todo[linecolor=green,backgroundcolor=green!50,caption={}, #1]{#2}}
\newcommand{\flag}[2][]
{\todo[linecolor=orange,backgroundcolor=yellow, caption={},#1]{#2}}
\newcommand{\oldargument}[2][]
{\todo[linecolor=darkgray,backgroundcolor=gray!40, caption={},#1]{#2}}
\newcommand{\myquestion}[2][]
{\todo[linecolor=purple,backgroundcolor=purple!80,caption={}, #1]{#2}}
\newcommand{\answer}[2][]
{\todo[noline, backgroundcolor=white, bordercolor=purple, caption={},#1]{#2}}
\newcommand{\pedro}[2][]
{\todo[linecolor=blue,backgroundcolor=blue!10,caption={}, #1]{#2}}
\newcommand{\billy}[2][]
{\todo[linecolor=green,backgroundcolor=green!10,caption={}, #1]{#2}}
\newcommand{\bob}[2][]
{\todo[linecolor=purple,backgroundcolor=purple!20,caption={}, #1]{#2}}
\newcommand{\jimmy}[2][]
{\todo[linecolor=orange,backgroundcolor=orange!10,caption={}, #1]{#2}}

\DeclareMathOperator{\HH}{H}
\newcommand{\fram}{\mathfrak{m}}
%\DeclareMathOperator{\Image}{image}

\DefineVerbatimEnvironment%
  {MyVerbatim}{Verbatim}
  {formatcom=\color{Violet}}

\renewcommand{\geq}{\geqslant}
\renewcommand{\leq}{\leqslant}
\renewcommand{\ge}{\geqslant}
\renewcommand{\le}{\leqslant}

\newtheorem*{caveat}{Caveat}

\begin{document}
\title{The  {TestIdeals} package for \emph{Macaulay2}}
\author[Alberto F.\ Boix et at.]{Alberto F.\ Boix}
\address{Department of Mathematics, Ben-Gurion University of the Negev, Beer-Sheva 8410501, Israel}
\email{fernanal@post.bgu.ac.il}
\thanks{A.F.~Boix was supported by Israel Science Foundation (grant No. 844/14) and Spanish Ministerio de Econom\'ia y Competitividad MTM2016-7881-P}

\author[]{Daniel J.\ Hern\'andez}
\address{Department of Mathematics, University of Kansas, Lawrence, KS~66045, USA}
\email{hernandez@ku.edu}
\thanks{D.~J.~Hern\'andez was partially supported by NSF DMS \#1600702.}

\author[]{Zhibek Kadyrsizova}
\address{School of Science and Technology, Nazarbayev University, Astana, 010000, Republic of Kazakhstan}
\email{zhibek.kadyrsizova@nu.edu.kz}
\thanks{Z. Kadyrsizova was partially supported by NSF DMS \#1401384 and the Barbour Scholarship at the University of Michigan.}

\author[]{Mordechai Katzman}
\address{Department of Pure Mathematics, University of Sheffield, Sheffield S37RH, United Kingdom}
\email{M.Katzman@sheffield.ac.uk}

\author[]{Sara Malec}
\address{Department of Mathematics, Hood College, Frederick, MD 21701}
\email{malec@hood.edu}

\author[]{Marcus Robinson}
\address{Department of Mathematics, University of Utah, Salt Lake City, UT~84112, USA}
\email{robinson@math.utah.edu}

\author[]{Karl Schwede}
\address{Department of Mathematics, University of Utah, Salt Lake City, UT~84112, USA}
\thanks{K.~Schwede was supported by NSF CAREER Grant DMS \#1252860/1501102, NSF FRG Grant DMS \#1265261/1501115, NSF grant \#1801849 and a Sloan Fellowship.}
\email{schwede@math.utah.edu}

\author[]{Daniel Smolkin}
\address{Department of Mathematics, University of Utah, Salt Lake City, UT~84112, USA}
\email{smolkin@math.utah.edu}
\thanks{D.~Smolkin was supported by NSF RTG Grant DMS \#1246989, NSF CAREER Grant DMS \#1252860/1501102, and NSF FRG Grant DMS \#1265261/1501115.}

\author[]{Pedro Teixeira}
\address{Department of Mathematics, Knox College, Galesburg, IL~61401, USA}
\email{pteixeir@knox.edu}

\author[]{Emily E.\ Witt}
\address{Department of Mathematics, University of Kansas, Lawrence, KS~66045, USA}
\email{witt@ku.edu}
\thanks{E.E.~Witt was partially supported by NSF DMS \#1623035.}
\date{\today}

\begin{abstract}
	This note describes a \emph{Macaulay2} package for computations in prime characteristic commutative algebra.  This includes Frobenius powers and roots, $p^{-e}$-linear and $p^{e}$-linear  maps,
  singularities defined in terms of these maps, different types of test ideals and modules, and ideals compatible with a given $p^{-e}$-linear map.
\end{abstract}

\subjclass[2010]{13A35}%=

\keywords{Macaulay2}

\maketitle

\section{Introduction}

This paper describes methods for computing objects and numerical invariants in prime characteristic commutative algebra, implemented in the \texttt{TestIdeals.m2} package for the computer algebra system \emph{Macaulay2}.
A ring $R$ of prime characteristic $p$ comes equipped with the Frobenius endomorphism
\[ F: R \to R \ \text{ given by } F(x) =  x^p,\]
which is the basis for many constructions and methods.
Notably, the Frobenius endomorphism can be used to detect whether a ring is regular \cite{KunzCharacterizationsOfRegularLocalRings}, and further, to quantify how far a ring is from being regular, measuring the severity of a singularity.

In this direction, two notable applications of the Frobenius endomorphism are the theory of tight closure
(see \cite{HochsterHunekeTC1,HochsterFoundations} for an introduction)
and the resulting theory of test ideals
(see the survey \cite{SchwedeTuckerTestIdealSurvey}).  These methods are used by a wide group of commutative algebraists and algebraic geometers.
%That said, it remains a fundamental tool in the expanding area of prime characteristic commutative algebra.

The \texttt{TestIdeals.m2} package was started during a \emph{Macaulay2} development workshop in 2012, hosted by Wake Forest University.
The package, at that time called \texttt{PosChar.m2}, aimed at providing a unified and efficient set of tools to study singularities in characteristic $p > 0$, and in particular, collecting and implementing several algorithms that had been described in research papers.
Since then, \texttt{PosChar.m2} was split into two packages, \texttt{TestIdeals.m2} and \texttt{FThresholds.m2}, and
much more functionality has been added by many contributors, during several more \emph{Macaulay2} development workshops.\footnote{Development workshops hosted by the University of California, Berkeley (2014, 2017), Boise State University (2015), and the University of Utah (2016).}

%{\color{blue} [Maybe we don't need to list all examples?  Several other algorithms were implemented independently and incorporated into the package.]}
Starting at least with Kunz \cite{KunzCharacterizationsOfRegularLocalRings} and Fedder \cite{FedderFPureRat}, it has been known that the Frobenius endormorphism offers \emph{effective} methods for measuring singularities in positive characteristic.
However, the algorithms that form the basis of this package are the methods for computing Frobenius roots, $\star$-closures, and parameter test ideals.
These first appeared in \cite{KatzmanParameterTestIdealOfCMRings,BlickleMustataSmithDiscretenessAndRationalityOfFThresholds,BlickleMustataSmithFThresholdsOfHypersurfaces,KatzmanFrobeniusMapsOnInjectiveHulls}.
Another algorithm in \cite{KatzmanSchwedeAlgorithm} for computing prime ideals compatible with a given $p^{-e}$-linear map was implemented and used to produce the examples in that paper.  The methods for computing test ideals and test modules that were used implicitly in papers such as \cite{BlickleSchwedeTakagiZhang,KatzmanLyubeznikZhangOnDiscretenessAndRationality,SchwedeTuckerTestIdealFiniteMaps} became implementable via the Frobenius roots functionality.
Algorithms for computing $F$-pure thresholds from \cite{HernandezFInvariantsOfDiagonalHyp}, \cite{HernandezFPureThresholdOfBinomial}, and \cite{HernandezTeixeiraFThresholdFunctions} form some of the key methods in the forthcoming \texttt{FThresholds.m2} package.
%{\hfill\large\color{red} [Expand: how were the test module methods conceived?]}\\

\subsection*{Acknowledgements}
The authors thank other contributors of the \texttt{TestIdeals.m2} package, namely
Erin Bela, Juliette Bruce, Drew Ellingson, Matthew Mastroeni, and Maral Mostafazadehfard.
This paper, and the finishing touches to the \texttt{TestIdeals.m2} package, were made at the University of Utah in 2018, and the visiting authors thank the Department of Mathematics for its hospitality.

\section{Frobenius powers and Frobenius roots}\label{Section: Frobenius powers and Frobenius roots}

Let $R$ denote a commutative ring of prime characteristic $p$.

\begin{definition}
Given an ideal $I\subseteq R$ and an integer $e\geq 0$, we define the \emph{$p^e$-th Frobenius power of $I$}, denoted $I^{[p^e]}$, to be the ideal
generated by the $p^e$-th powers of all elements of $I$.
\end{definition}

It is easy to see that if $I$ is generated by $g_1, \dots, g_\ell$, then $I^{[p^e]}$ is generated by $g_1^{p^e}, \dots, g_\ell^{p^e}$.

\begin{definition}
Given an ideal $I\subseteq R$ and an integer $e\geq 0$, we define the \emph{$p^e$-th Frobenius root of $I$}, denoted $I^{[1/p^{e}]}$, to be the smallest ideal $J$ such that $I\subseteq J^{[p^e]}$, if such an ideal exists.
\end{definition}

Frobenius roots always exist in polynomial and power series rings, and in $F$-finite regular rings
(cf.~\cite[\S 2]{BlickleMustataSmithDiscretenessAndRationalityOfFThresholds} and \cite[\S 5]{KatzmanParameterTestIdealOfCMRings}).
Below is an example of a computation of a Frobenius root in a polynomial ring.
In Section~\ref{ss: math behind} we describe the main ideas behind such computations.

\medskip
{\small
\begin{MyVerbatim}
i1 : R = ZZ/5[x,y,z];
i2 : I = ideal( x^6*y*z + x^2*y^12*z^3 + x*y*z^18 );
o2 : Ideal of R
i3 : frobeniusPower( 1/5, I )
                2   3
o3 = ideal (x, y , z )
o3 : Ideal of R
\end{MyVerbatim}
}
\medskip

\subsection{The mathematics behind the computation of Frobenius roots}
\label{ss: math behind}

We can also describe Frobenius roots as follows:  In a (sufficiently local) regular ring, we have an identification of $R$ with its canonical module $\omega_R$.
On the other hand, the Grothendieck dual to the $e$-iterated Frobenius map\footnote{In a reduced ring $R$, it is often convenient to express the Frobenius endomorphism $R \to R$ as the inclusion $R \hookrightarrow R^{1/p}$, so that the source and target  are distinguished.} $R \to R^{1/p^e}$ provides a map
\begin{equation}
\label{eq.DualToFrobenius}
T : \omega_{R^{1/p^e}} \to \omega_R,
\end{equation}
which using the identification $R \cong \omega_R$ gives us a map
\[
T : R^{1/p^e} \to R.
\]
It is not difficult to prove that
$T(I^{1/p^e})=I^{[1/p^e]}$,
where $I^{1/p^e} \subseteq R^{1/p^e}$ is simply the ideal of $p^e$-th roots of the elements of $I$.
In the case that
\[
R = \bF_{p^e}[x_1, \ldots, x_d],
\]
$R^{1/p^e}$ is a free $R$-module with basis consisting of the monomials
\[
\mathbf{x}^{\boldsymbol{\lambda}/p^e}= x_1^{\lambda_1/p^e} \cdots x_d^{\lambda_d/p^e},
\]
where $0 \leq \lambda_i \leq p^e-1$.
Furthermore, the map $T : R^{1/p^e} \to R$ is simply the projection defined as follows:
\[
T(x_1^{\lambda_1/p^e} \cdots x_d^{\lambda_d/p^e}) = \left\{ \begin{array}{rl} 1 &\text{if } \lambda_i = p^{e}-1 \text{ for all }i \\ 0 & \text{otherwise}  \end{array} \right.
\]
Using this, it is not difficult to see that if
\begin{equation}
\label{eqn1}
f^{1/p^e} = \sum_{\boldsymbol{\lambda}} f_{\boldsymbol{\lambda}} \mathbf{x}^{\boldsymbol{\lambda} / p^e},
\end{equation}
where $\boldsymbol{\lambda}$ runs over the tuples $(\lambda_1, \dots, \lambda_d)$ with $0 \leq \lambda_j \leq p^e-1$, and $f_{\boldsymbol{\lambda}} \in R$, then
$(f)^{[1/p^e]} = T( (f)^{1/p^e})$ is the ideal generated by the $f_{\boldsymbol{\lambda}}$.
We can then compute $I^{[1/p^e]}$ for more general $I$ by linearity: if $I=(f_1,\ldots,f_m)$, then $I^{[1/p^e]}= \sum(f_i)^{[1/p^e]}$.

\subsubsection{Complexity}
The computation of Frobenius roots is the workhorse behind many of the methods in \texttt{TestIdeals.m2}.
Hence it is important to understand how this is implemented, and its computational complexity.

The computation of Frobenius roots of ideals reduces to the case of principal ideals, and its complexity grows linearly with the number of generators of the ideal.
Furthermore the calculation of  $(f)^{[1/p^e]}$ reduces to finding the summands in (\ref{eqn1}), which essentially amounts to
taking each term in $f$, computing the $p^e$-th root of the coefficient in $\mathbb{K}$, and dividing the monomial exponent vector by $p^e$ with remainder.
Hence the complexity of computing $(f)^{[1/p^e]}$ is proportional to the number of terms in $f$, and is independent of its degree.
We emphasize that the calculation of Frobenius roots \emph{does not involve the calculation of Gr\"obner bases.}

\subsection{Dual to Frobenius on quotient rings and Frobenius on top local cohomology}
\label{subsec.DualToFrobeniusOnQuotientRings}
For \emph{any} reduced ring $R$ with finite $e$-iterated Frobenius map identified with $R \hookrightarrow R^{1/p^e}$, we always have a map
\[
T_R : \omega_{R^{1/p^e}} \to \omega_R.
\]
At a maximal ideal $\fram$ of height $d$, this map is Matlis dual to the Frobenius map on $H^d_{\fram}(R)$.
Hence we can study local cohomology by studying this map.
If $R = S/I$, where $S$ is a polynomial ring over a finite field, we can implement this map \cite{FedderFPureRat, KatzmanParameterTestIdealOfCMRings}.  We briefly explain the case of a hypersurface here.

If $I = (f)$, then again $\omega_R \cong R = S/I$, and the action of $T_R$ can be computed on $S$.  In fact, if $\overline{J} \subseteq R \cong \omega_R$ has preimage  $J \subseteq S$,
then setting $u = f^{p^e-1}$, we have that $T_R({\overline J}^{1/p^e})$ is the image of $(u J)^{[1/p^e]}$ in $R$.
More generally, for non-hypersurfaces, the analog to $u$ is chosen to be an element that maps onto the generator of the cyclic $R$-module
\[
\frac{(I^{[p^e]} : I) \cap (\Omega^{[p^e]} : \Omega)}{ I^{[p^e]}},
\]
where $\Omega$ is an ideal of $S$ with $I\subseteq \Omega$ and whose image in $R$ is isomorphic to the canonical module of $R$; see \cite{KatzmanParameterTestIdealOfCMRings} for details.
Here we compute two examples.

\medskip
{\small
\begin{MyVerbatim}
i1 : S = ZZ/5[x,y,z];
i2 : f = x^3 + y^3 + z^3;
i3 : u = f^(5-1);
i4 : frobeniusRoot( 1, ideal u )
o4 = ideal (z, y, x)
o4 : Ideal of R

i5 : S = ZZ/7[x,y,z];
i6 : f = x^3 + y^3 + z^3;
i7 : u = f^(7-1)
i8 : frobeniusRoot( 1, ideal u )
o8 = ideal 1
o8 : Ideal of R
\end{MyVerbatim}
}\medskip

The above example has shown that the Frobenius map on top local cohomology of the cone over the Fermat elliptic curve is injective in characteristic $7$ (the dual map $\omega_{R^{1/p}} \to \omega_R$ is surjective) and not injective in characteristic $5$ (the dual map $\omega_{R^{1/p}} \to \omega_R$ is not surjective).

\subsection{A generalization of Frobenius powers and roots}

Let $R$ be an $F$-finite regular ring.
We can extend the definition of Frobenius powers as follows.

\begin{definition}[\cite{HernandezTeixeiraWittFrobeniusPowers}]
Let  $I\subseteq R$ be an ideal.
\begin{enumerate}
 \item[(a)] If $n$ is a positive integer with base $p$ expansion  $n=d_0 + d_1 p +  \dots + d_r p^r$, we define
\[ I^{[n]}=I^{d_0} (I^{d_1})^{[p]} \dots  (I^{d_r})^{[p^r]}.\]
 \item[(b)] If $t$ is a nonnegative rational number of the form $t = a/p^e$, we define  $I^{[t]} = {\big(I^{[a]}\big)}^{[1/p^e]}.$
 \item[(c)] If $t$ is any nonnegative rational number, and $\{a_n/p^{e_n}\}_{n\geq 1}$ is a sequence of rational numbers converging to $t$ from above, we define $I^{[t]}$
 to be the stable value of the non-decreasing chain of ideals $\{I^{[a_n/p^{e_n}]}\}_{n\geq 1}$.
\end{enumerate}
\end{definition}

\medskip
{\small
\begin{MyVerbatim}
i1 : p = 3;
i2 : R = ZZ/p[x,y];
i3 : m = monomialIdeal( x, y );
o3 : MonomialIdeal of R
i4 : I = m^5;
o4 : MonomialIdeal of R
i5 : t = 3/5 - 1/(5*p^3);
i6 : frobeniusPower( t, I )
             2        2
o6 = ideal (y , x*y, x )
o6 : Ideal of R
i7 : frobeniusPower( t - 1/p^5, I )
o7 = ideal (y, x)
o7 : Ideal of R
\end{MyVerbatim}
}
\medskip

The generalized Frobenius powers of an ideal are test ideals (see Section~\ref{Section: Test Ideals}) of sufficiently general linear combinations of generators of that ideal.
Thus, the ideals computed above are test ideals of generic quintics in two variables in characteristic $p=3$, and these computations suggest that $\frac35-\frac1{5p^3}$ is a higher $F$-jumping exponent of such quintics, which is indeed the case for any $p\equiv 3 \bmod 5$ (see \cite{hernandez+etal.frobenius_examples}).
To illustrate, compare the computations above with the following.

\medskip
{\small
\begin{MyVerbatim}
i8 : S = ZZ/3[a..f,x,y];
i9 : G = a*x^5 + b*x^4*y + c*x^3*y^2 + d*x^2*y^3 + e*x*y^4 + f*y^5;
i10 : testIdeal( t, G )
              2        2
o10 = ideal (y , x*y, x )
o10 : Ideal of S
i11 : testIdeal( t - 1/p^5, G )
o11 = ideal (y, x)
o11 : Ideal of S
\end{MyVerbatim}
}
\medskip

\begin{caveat}
   The computations of Frobenius powers with exponents whose denominators are not powers of the characteristic $p$ are often very slow, and in several instances it is more efficient to introduce more variables and compute the test ideal of a ``very general'' linear combination of the generators of the ideal, as above.
   The code used for computations of Frobenius powers needs to undergo significant optimization.
\end{caveat}

\subsection{Frobenius  roots of submodules of free modules}

Let $S$ be a polynomial ring or power series ring.
Given a submodule $M$ of the free module $S^k$,
%
%\pedro{What are the assumptions on $S$ here?}
%
there is a smallest submodule $N$ of $S^k$ that contains $M$, for which $M\subseteq N^{[p^e]}$.
Here,  $N^{[p^e]}$ is the submodule  of $S^k$ generated by the vectors of $N$ with all coordinates raised to the $p^e$-th power. (Cf.~\cite{KatzmanZhangAlgorithm}).
Extending the previous definitions,
we call this $N$ the $p^e$-th Frobenius root of $M$, and denote it by $M^{[1/p^e]}$.

\begin{example}
Let $R=\ZZ/p\ZZ[a,b,c,d]$, and consider the ideals $\mathfrak{m}=(a,b,c,d)$ and
$$I= (a,b) \cap (a,c) \cap (c,d) \cap (c+d, a^3+b d^2).$$
Then $R/I$ is a $3$-dimensional non-Cohen-Macaulay ring.
Matlis Duality applied to $H^2_{\mathfrak{m}} (R/I)$ with its natural Frobenius map
yields a $p^{-1}$-linear map $U$ on $\Ext^2_R(R/ I, R)$.
%$\Ext^2(R/ I, R) \xrightarrow{U} \Ext^2(R/I, R)$.

\medskip
{\small
\begin{MyVerbatim}
i1 : p = 2;
i2 : R = ZZ/p[a,b,c,d];
i3 : I = intersect(ideal(a,b),ideal(a,c),ideal(c,d),ideal(c+d,a^3+b*d^2));
o3 : Ideal of R
i4 : f = inducedMap( R^1/I, R^1/frobenius(I) );
o4 : Matrix
i5 : E2 = Ext^2( f, R^1 )
o5 = {-8}  | a4+abc2+abcd a2b            |
     {-10} | a2cd3        a3cd+a3d2+bcd3 |
o5 : Matrix
i6 : target E2
o6 = cokernel {-8}  | 0     a2 b2c2 |
              {-10} | c2+d2 d4 a4d2 |
                            2
o6 : R-module, quotient of R
i7 : source E2
o7 = cokernel {-4} | 0   a  bc  |
              {-5} | c+d d2 a2d |
                            2
o7 : R-module, quotient of R
\end{MyVerbatim}
}
\medskip

The Frobenius map on $H^2_{\mathfrak{m}} (R/I)$
is injective if and only the image of
$(\Image U)^{[1/p]}$ in $\Ext^2_R(R/ I, R)$
as computed above is the whole of $R^2$.

\medskip
{\small
\begin{MyVerbatim}
i8 : U = matrix entries E2;
             2       2
o8 : Matrix R  <--- R
i9 : A = matrix entries relations source E2;
             2       3
o9 : Matrix R  <--- R
i10 : frobeniusRoot( 1, U )
o10 = {-2} | 1 0 0 |
      {0}  | 0 d a |
              2       3
o10 : Matrix R  <--- R
\end{MyVerbatim}
}\medskip

The calculation above shows that $R/I$ is not $F$-injective (cf. Section \ref{Section: F-singularities}).
Moreover, it shows that $H^2_{\mathfrak{m}} (R/I)\cong \Ann_{E^2} A^t$,
where $E$ is the injective hull of $R_{\mathfrak{m}}/ {\mathfrak{m}} R_{\mathfrak{m}}$,
and the Frobenius map on  $H^2_{\mathfrak{m}} (R/I)$ induced from Frobenius on $R$
is given by $U^t \Theta$, where $\Theta$ is the induced Frobenius on $E$.
The submodule of nilpotent elements in  $H^2_{\mathfrak{m}} (R/I)$ is
given by $\Ann_{E^2} B^t$, where $B$ is the smallest submodule of $R^2$ containing $\Image A + \Image U$ such that $U  B \subseteq B^{[p]}$.
The method \texttt{ascendModule} can be used to calculate  $B$ (see a detailed description of the similar method \texttt{ascendIdeal} in Section \ref{Section: Test Ideals}).

\medskip
{\small
\begin{MyVerbatim}
i11 : V = ascendModule( 1, A, U )
o11 = | 0   a  bc  |
      | c+d d2 a2d |
              2       3
o11 : Matrix R  <--- R
\end{MyVerbatim}
}\medskip

\end{example}

%\section{$p^{-e}$- and $p^{e}$-linear maps}\label{Section: p-linear maps}

%\begin{definition}%{\hfill\large\color{red} [Add references]}\\
%Let $M$ be an $S$-module and $e$ a nonnegative integer.
%\begin{enumerate}
% \item[(a)] A $p^{-e}$-linear map $\phi:M \rightarrow M$ is an additive map such that
% $\phi(s^{p^e} m)= s\phi(m)$ for all $s\in S$ and $m\in M$.
% \item[(b)] A $p^{e}$-linear map $\psi:M \rightarrow M$ is an additive map such that
% $\phi(s m)= s^{p^e}\phi(m)$ for all $s\in S$ and $m\in M$.
%\end{enumerate}
%\end{definition}

%The following two examples describe  prototypical
%$p^{-e}$- and $p^{e}$-linear maps.
%\begin{example}
%For any $S$-module $M$, we can construct a new $S$-module $M^{1/p^e}$ with elements $\{  m^{1/p^e} \,|\,m\in M\}$ by defining
%$m_1^{1/p^e} +  m_2^{1/p^e} =  (m_1 +  m_2)^{1/p^e}$ for all $m_1, m_2 \in M$ and
%$s  m^{1/p^e}=  (s^{p^e} m)^{1/p^e}$ for all $m\in M$ and $s\in S$.

%Consider any $\phi\in \Hom_S(M^{1/p^e}, M)$: if we identify $M^{1/p^e}$ with $M$ we can interpret $\phi$ as a $p^{-e}$-linear map.
%\end{example}

%\begin{example}
%The $e$-th Frobenius map $f:S \rightarrow S$  raising elements to their $p^e$-th power is clearly $p^{e}$-linear.
%Furthermore, for any ideal $I\subseteq S$ and $k\geq 0$, $f$ induces a $p^{e}$-linear map $H_I^k (S) \rightarrow H_I^k (S)$.
%\end{example}

%Let $R$ be a polynomial ring with irrelevant ideal $\mathfrak{m}$ and let $g$ be a nonzero element of $R$.
%Let $E=E_{R_{\mathfrak{m}}}(R_{\mathfrak{m}}/\mathfrak{m})$ denote the injective hull of $R_{\mathfrak{m}}/\mathfrak{m}$.

%The Frobenius map on $R$ induces a Frobenius map $S$ and on
%$H^{\dim R-1}_{\mathfrak{m}} (S)=E_S(S/\mathfrak{m}S)=\Ann_E g$ and the kernel of this map is given by
%$\Ann_E (g^{p-1}R)^{[1/p]}$ (cf.~\cite[\S 5]{KatzmanParameterTestIdealOfCMRings}).

%Thus we see that the induced $p^{e}$-linear map on $H_{(x,y,z)}^{2} \left( \mathbb{K}[x,y,z]/(x^3+y^3+z^3) \right)$ is injective
%when the characteristic of $\mathbb{K}$ is $7$ and non-injective when the characteristic is $5$.

%\subsection{Implementation and complexity}

%Let $R=\mathbb{K}[x_1, \dots, x_n]$ and fix $B$ to be $\mathbb{K}$-basis for $\mathbb{K}^{1/p^e}$.
%It is not hard to see that $R^{1/p^e}$ is a free $R$-module with free basis
%$$\left\{ b x_1^{\alpha_1/p^e} \dots x_n^{\alpha_n/p^e} \,|\, b \in B, 0\leq \alpha_1, \dots, \alpha_n < p^e \right\}.$$

%\begin{proposition}(cf. \cite[\S 5]{KatzmanParameterTestIdealOfCMRings})
%\begin{enumerate}
%\item[(a)] If the ideal $I\subseteq R$ is generated by $g_1, \dots, g_k\in R$, then $I^{[1/p^e]}=\sum_{i=1}^k (g_i R)^{[1/p^e]}$.
%\item[(b)] If
%\begin{equation}\label{eqn1}
%g=\sum_{b\in B, \atop{0\leq \alpha_1, \dots, \alpha_n < p^e}} r_{b, \alpha_1, \dots, \alpha_n} \left(b x_1^{\alpha_1/p^e} \dots x_n^{\alpha_n/p^e}\right),
%\end{equation}
%then $(gR)^{[1/p^e]}$ is generated by $\{ r_{b, \alpha_1, \dots, \alpha_n} \,|\, b\in B, 0\leq \alpha_1, \dots, \alpha_n < p^e \}$.
%\end{enumerate}
%\end{proposition}

\section{$F$-singularities}\label{Section: F-singularities}

The \texttt{TestIdeals.m2} package includes methods for determining if a ring is $F$-injective, $F$-pure, $F$-rational, or $F$-regular.

\subsection{$F$-injectivity}

\begin{definition}
A local ring $(R, \mathfrak{m})$ is called \emph{F-injective} if the map
$H^{i}_{\mathfrak{m}}(R) \rightarrow H^{i}_{\mathfrak{m}}(R^{1/p})$ is
injective for all $i >0$. An arbitrary ring is called \emph{$F$-injective} if its
localization at each prime ideal of $R$ is $F$-injective.
\end{definition}

The function \texttt{isFInjective} determines whether the ring $R = S/I$ is
$F$-injective, where $S$ is a polynomial ring.

\medskip
{\small
\begin{MyVerbatim}
i1 : R = ZZ/7[x,y,z]/ideal( x^3 + y^3 + z^3 );
i2 : isFInjective R
o2 = true
i3 : R = ZZ/5[x,y,z]/ideal( x^3 + y^3 + z^3 );
i4 : isFInjective R
o4 = false
\end{MyVerbatim}
}\medskip

Equivalently, a ring is $F$-injective if the maps on the cohomology of the dualizing complex
\[
h^{-i} \omega_{R^{1/p}}^{\mydot} \to h^{-i} \omega_R^{\mydot}
\]
surject for all $i$.
Note that $h^{-i} \omega_R^{\mydot} \cong \Ext^{\dim S - i}(R, S)$, the latter of which \emph{Macaulay2} readily computes.
The algorithm used by \texttt{isFInjective} works by checking the surjectivity of the dual Frobenius map
\[
\Ext^{\dim S - i}(R^{1/p}, S) \to \Ext^{\dim S - i}(R, S).
\]
%using the fact that the Matlist dual of \Ext^{i}(\blank, S)$ \cong H^{\dim S -
%i}_{\mathfrak{m}}(\blank) $.
We begin by computing the map $R
\rightarrow R^{1/p}$ using the \texttt{PushForward.m2} package \cite{PushForward}.
Next the algorithm computes
$\Ext^{i}( \blank, S)$ applied to the map from the previous step.  Then $R$ is $F$-injective precisely when the
cokernel of $\Ext^{i}( \blank, S)$ is trivial for $i$.

The Frobenius action on top local cohomology (dual to $\omega_R$) is usually computed in a different (faster) way than the other cohomologies, and this is modified by the \texttt{CanonicalStrategy} option.
The default value for this option is \texttt{Katzman}, which instead of using the \texttt{PushForward.m2} package, relies on the fact that we already know how to compute the Frobenius action on the canonical module, as described in \autoref{subsec.DualToFrobeniusOnQuotientRings}.

%The \texttt{CanonicalStrategy} tag can be used to modify the strategy the
%algorithm uses to check the Frobenius action on the top local cohomology.
%By default the algorithm is set to \texttt{CanonicalStrategy => Katzman} which
%then uses the strategy of Katzman {\hfill\large\color{red} [Add
%references]}. If the tag is set to anything else \texttt{CanonicalStrategy =>
%null} the algorithm checks the top local cohomology using the same brute
%force strategy used to check the injectivity at lower degrees. The Katzman
%strategy is typically much faster.

The performance of the algorithm can be improved if the ring of interest is
nice enough. If the ring is Cohen-Macaulay, then setting \texttt{AssumeCM =>
true} (the default value is \texttt{false}) lets the algorithm check the Frobenius action only on top cohomology
(which is typically much faster, as explained above).
%The default value for the option \texttt{AssumeCM} is \texttt{false}.
%Of
%course, telling the algorithm to assume the ring is Cohen-Macaulay when it
%is not can lead to an incorrect answer if the non-injective Frobenius
%occurs in a lower degree. For an example of this see the documentation.
When studying a reduced ring,  setting \texttt{AssumeReduced => true} (the default value) avoids
computing the bottom local cohomology, and when studying a normal ring, setting
\texttt{AssumeNormal => true} (the default is \texttt{false}) avoids computing the bottom two local
cohomologies.

By default the algorithm checks for $F$-injectivity at all points of $\Spec R$.  However, one
can choose to check $F$-injectivity only at the origin by setting the
option \texttt{IsLocal} to  \texttt{true}.

\medskip
{\small
\begin{MyVerbatim}
i1 : R = ZZ/7[x,y,z]/ideal( (x-1)^5 + (y+1)^5 + z^5 );
i2 : isFInjective R -- R is not globally F-injective...
o2 = false
i3 : isFInjective( R, IsLocal => true ) -- but is F-injective at the origin
o3 = true
\end{MyVerbatim}
}\medskip

\subsection{$F$-regularity}

\begin{definition}[\cite{HochsterHunekeTC1,HaraWatanabeFRegFPure}]
A ring $R$ is called \emph{strongly $F$-regular} if the (big) test ideal $\tau(R)$ is equal to $R$.  Likewise a pair $(R, f^t)$ is called \emph{strongly $F$-regular} if $\tau(R, f^t) = R$.
\end{definition}

The command \texttt{isFRegular} checks whether a ring or pair is strongly
$F$-regular. Below are two examples, one of which is $F$-regular and the other one is not.

\medskip
{\small
\begin{MyVerbatim}
i1 : R = ZZ/5[x,y,z]/ideal( x^2 + y*z );
i2 : isFRegular R
o2 = true
i3 : R = ZZ/7[x,y,z]/ideal( x^3 + y^3 + z^3 );
i4 : isFRegular R
o4 = false
\end{MyVerbatim}
}\medskip

We can also check whether a pair $(R, f^t)$ is $F$-regular.

\medskip
{\small
\begin{MyVerbatim}
i1 : R = ZZ/5[x,y];
i2 : f = y^2 - x^3;
i3 : isFRegular( 1/2, f )
o3 = true
i4 : isFRegular( 5/6, f )
o4 = false
i5 : isFRegular( 4/5, f )
o5 = false
i6 : isFRegular( 4/5 - 1/100000, f )
o6 = true
\end{MyVerbatim}
}\medskip

All of these checks are done by actually computing the test ideal, as described in \autoref{Section: Test Ideals}.

If the input ring is $\mathbb{Q}$-Gorenstein, then in each of the cases above, the output is a boolean indicating if the
ring is strongly $F$-regular. If the input ring is not
$\mathbb{Q}$-Gorenstein, then the algorithm can be used to determine if a
ring is strongly $F$-regular, but cannot prove that a ring is not strongly
$F$-regular (this latter functionality can, however, be enabled by setting \texttt{QGorensteinIndex => infinity}).

In the case that $R$ is $\mathbb{Q}$-Gorenstein, the algorithm works by
computing the test ideal $\tau$ of the ring  (or the pair) using \texttt{testIdeal}
and checking whether $\tau=R$.
In the non-$\mathbb{Q}$-Gorenstein case, the algorithm checks for
strong $F$-regularity by computing better and
better approximations of the test ideal, and checking whether any of these is the unit ideal.
To compute approximations of the
test ideal, the algorithm computes a test element $c$ with \texttt{testElement}
and then uses \texttt{frobeniusRoot} to compute the $e$-th root of
$c(I^{[p^{e}]} : I)$; appropriate modifications are made for pairs. If at
any step the approximation is the unit ideal, then then the algorithm
returns \texttt{true}. Otherwise the algorithm continues checking for each $e$
until a specified limit is reached. The default limit is 2, and can be
changed using the option \texttt{DepthOfSearch}.

A number of options can be used to speed up the performance of some of the
internal functions. The option \texttt{AssumeDomain} can be used if $R$ is an
integral domain, \texttt{FrobeniusRootStrategy} chooses a strategy for
internal \texttt{frobeniusRoot} calls, \texttt{MaxCartierIndex} sets the
maximum Gorenstein index to search for when working with a
$\mathbb{Q}$-Gorenstein ambient ring, and \texttt{QGorensteinIndex}
allows the user to specify the $\mathbb{Q}$-Gorenstein index of the ring.

The default behavior of \texttt{isFRegular} is that it checks for strong $F$-regularity
globally. If the option \texttt{IsLocal} is set to \texttt{true}, the algorithm will only
check $F$-regularity at the origin, by checking whether the computed test ideal is in the irrelevant ideal.
Below are examples for both a ring and a pair.

\medskip
{\small
\begin{MyVerbatim}
i1 : R = ZZ/7[x,y,z]/ideal( (x-1)^3 + (y+1)^3 + z^3 );
i2 : isFRegular R -- R is not globally F-regular...
o2 = false
i3 : isFRegular( R, IsLocal => true ) -- but is F-regular at the origin
o3 = true
i4 : R = ZZ/13[x,y];
i5 : f = (y-2)^2 - (x-3)^3;
i6 : isFRegular( 5/6, f ) -- (R,f^(5/6)) is not F-regular...
o6 = false
i7 : isFRegular( 5/6, f, IsLocal => true ) -- but is F-regular at the origin
o7 = true
\end{MyVerbatim}
}\medskip

\subsection{$F$-purity}
\begin{definition}
A ring $R$ is called \emph{$F$-pure} if
the inclusion $R \hookrightarrow R^{1/p^{e}}$ is a pure map, i.e.,
the tensor of this map with any $R$-module remains injective.  If $R^{1/p}$ is a finite $R$-module, this is equivalent to requiring that the inclusion $R \hookrightarrow R^{1/p}$ split as a map of $R$-modules.
\end{definition}

The function \texttt{isFPure} checks whether a ring is $F$-pure.
Either a ring or a defining ideal can be input, as seen in the following example.

\medskip
{\small
\begin{MyVerbatim}
i1 : R = ZZ/5[x,y,z]/ideal( x^2 + y*z );
i2 : isFPure R
o2 = true
i3 : R = ZZ/7[x,y,z]/ideal( x^3 + y^3 + z^3 );
i4 : isFPure R
o4 = true
i5 : S = ZZ/2[x,y,z];
i5 : isFPure ideal( y^2 - x^3 )
o5 = false
i6 : isFPure ideal( z^2 - x*y*z + x*y^2 + x^2*y )
o6 = true
\end{MyVerbatim}
}\medskip

The algorithm works by applying Fedder's Criterion {\cite{FedderFPureRat}}, which states that a
local ring $(R, \mathfrak{m})$ is $F$-pure if and only if $(I^{[p]} : I)
\not\subseteq \mathfrak{m}^{[p]}$.
When \texttt{IsLocal} is set to \texttt{true}, the algorithm checks $F$-purity only at the origin, by explicitly checking the above
containment. When \texttt{IsLocal} is set to \texttt{false}, which is its default value, the
algorithm computes the non $F$-pure locus, by applying \texttt{frobeniusRoot}
to $I^{[p]} :I$. If the non $F$-pure locus is the whole ring, the algorithm
returns \texttt{true}.

\subsection{$F$-rationality}

\begin{definition}
Suppose that $R$ is a Cohen-Macaulay ring and that $T_{R} :
\omega_{R^{1/p}} \rightarrow \omega_{R}$ is the canonical dual to the
Frobenius. We say that $R$ has \emph{$F$-rational singularities}, of simply that \emph{$R$ is $F$-rational}, if there
are no non-zero proper submodules $M$ of $\omega_{R}$ such that
$T_{R}(M^{1/p}) \subseteq M$.
\end{definition}

The command \texttt{isFRational} checks if a ring is $F$-rational.

\medskip
{\small
\begin{MyVerbatim}
i1 : S = ZZ/3[a,b,c,d,t];
i2 : m = 4;
i3 : n = 3;
i4 : M = matrix{ { a^2 + t^m, b, d }, { c, a^2, b^n-d } };
i5 : I = minors( 2, M );
i6 : R = S/I;
i7 : isFRational R
o7 = true
\end{MyVerbatim}
}\medskip

The algorithm used by \texttt{isFRational} first checks if the ring is Cohen-Macaulay, unless the option \texttt{isCohenMacaulay} is set to \texttt{true}. If the ring
is not Cohen-Macaulay then \texttt{false} is returned. Next, the algorithm
computes the test module $M \subseteq \omega_{R}$ and checks to see if
$\omega_{R} \subseteq M$;  see the next section for the description of a test module.

The options \texttt{AssumeDomain} and \texttt{FrobeniusRootStrategy} can be
used to improve the speed of the \texttt{testModule} computation. By default,
these options are set to \texttt{false} and \texttt{Substitution}, respectively.
Finally, if \texttt{IsLocal} is set to \texttt{true}, then $F$-rationality is checked only at the origin.

\section{Test ideals}\label{Section: Test Ideals}

In this section, we explain how to compute parameter test modules, parameter test ideals, test ideals, and HSLG-modules\footnote{HSLG-modules can be used to give a scheme structure to the $F$-injective or $F$-pure locus.}.

\subsection{Parameter test modules}
%
\pedro{Are we assuming here that $R$ is a quotient of a polynomial ring?}
%
Given an $F$-finite reduced ring $R$, the Frobenius map $R \hookrightarrow R^{1/p^e}$ is dual to $T : \omega_{R^{1/p^e}} \to \omega_R$.  As in \autoref{subsec.DualToFrobeniusOnQuotientRings}, we can represent the canonical module $\omega_R \subseteq R$ as an ideal, we can write $R = S/I$, and so we can find an element $u \in S^{1/p^e}$ representing the map $T:\omega_{R^{1/p^e}} \to \omega_R$; see \autoref{subsec.DualToFrobeniusOnQuotientRings} or \cite{KatzmanParameterTestIdealOfCMRings}.

\begin{definition}
   The \emph{parameter test submodule} is the smallest submodule $M \subseteq \omega_R$ (and hence ideal of $R$, since $M \subseteq \omega_R \subseteq R$) that agrees generically with $\omega_R$ and that satisfies
   %
   \pedro{What is the quantifier for $e$ here?}
   %
\[
T (M^{1/p^e}) \subseteq M.
\]
\end{definition}

Using \emph{Macaulay2}, we can compute this using the \texttt{testModule} command as follows.

\medskip
{\small
\begin{MyVerbatim}
i1 : R = ZZ/5[x,y,z]/ideal( x^4 + y^4 + z^4 );
i2 : N = testModule R;
i3 : N#0
             2             2        2
o3 = ideal (z , y*z, x*z, y , x*y, x )
o3 : Ideal of R
i4 : N#1
o4 = ideal 1
o4 : Ideal of R
\end{MyVerbatim}
}\medskip

The output of \texttt{testModule} is a list, consisting of three items:
\begin{enumerate}[(1)]
\item The test module itself, given as an ideal of $R$.
\item The canonical module that contains the test module, given as an ideal of $R$.
\item The element $u$ described above (not displayed above, since it takes a lot of space).
\end{enumerate}

Note since this ring is Gorenstein, the canonical module is simply represented as the unit ideal. Here is another example, where the ring is not Gorenstein.

\medskip
{\small
\begin{MyVerbatim}
i1 : R = ZZ/5[x,y,z]/ideal( y*z, x*z, x*y );
i2 : N = testModule R;
i3 : N#0
             2   2   2
o3 = ideal (z , y , x )
o3 : Ideal of R
i4 : N#1
o4 = ideal (y - z, x + z)
o4 : Ideal of R
\end{MyVerbatim}
}\medskip

We briefly explain how this is computed:  First, we find a \emph{test element}.
\begin{remark}[Computation of test elements]
\label{rem.ComputationOfTestElements}
We recall that, roughly, an element of the Jacobian ideal that is not contained in any minimal prime is a test element \cite{HochsterFoundations}.  We compute test elements by computing random partial derivatives (and linear combinations thereof) until we find an element that does not vanish at all the minimal primes.  This method is much faster than computing the entire Jacobian ideal.  If it is known that the ring is a domain, setting \texttt{AssumeDomain => true} can speed this up further.
\end{remark}

After the test element $c$ has been identified, we pull back the ideal $\omega_R$ to an ideal $J \subseteq S$.  Next, we compute the following ascending sequence of ideals:
\begin{equation}
\label{eq.AscendIdealExplanation}
\begin{array}{lll}
J_1 &\colonequals   J + (c J)^{[1/p]} & \\
J_2 &\colonequals   J_1 + (c J_1)^{[1/p]} & = J + (c J)^{[1/p]} + (c^{1+p} J)^{[1/p^2]} \\
J_3 &\colonequals    J_2 + (cJ_2)^{[1/p]} & = J + (c J)^{[1/p]} + (c^{1+p} J)^{[1/p^2]} + (c^{1+p+p^2} J)^{[1/p^3]} \\
\vdots
\end{array}
\end{equation}
As soon as this ascending sequence of ideals stabilizes, we are done.
In fact, because this strategy is used in several contexts, the user can call it directly for a chosen ideal $J$ and $u$ with the function \texttt{ascendIdeal} (this is done for test ideals below).

We can also compute parameter test modules of pairs $(\omega_R, f^{t})$ with $t \in \mathbb{Q}_{\geq 0}$.
This is done by modifying the element $u$ when the denominator of $t$ is not divisible by $p$.
When $t$ has $p$ in its denominator, we rely on the fact (see \cite{BlickleMustataSmithDiscretenessAndRationalityOfFThresholds,SchwedeTuckerTestIdealFiniteMaps}) that
\[
\begin{array}{rcl}
T(\tau(\omega_R, f^a)) & = & \tau(\omega_R, f^{a/p})\\
{\tt frobeniusRoot(1, u*I_1)} & {\tt =} & {\tt I_2}
\end{array}
\]
where the second line roughly explains how this is accomplished internally.
Here ${\tt I_1}$ is $\tau(\omega_R, f^a)$ pulled back to $S$ and, likewise, $I_2$ defines $\tau(\omega_R, f^{a/p})$ modulo the defining ideal of $R$.

\begin{remark}[Optimizations in \texttt{ascendIdeal} and other \texttt{testModule} computations]
Throughout the computations described above, we very frequently use the following fact:
\[
(f^p \cdot J)^{[1/p]} = f \cdot (J^{[1/p]}).
\]
To access this enhancement, one should try to pass functions like \texttt{ascendIdeal} and \texttt{frobeniusRoot} the elements and their exponents (see the documentation).
In particular, when computing the $p^e$-th Frobenius root of an ideal of the form $f^n \cdot J$, one should not multiply out $f^n$ and $J$, nor even raise $f$ to the $n^\mathrm{th}$ power, but rather call \texttt{frobeniusRoot(e,n,f,J)}.
\end{remark}

\subsection{Parameter test ideals}

The parameter test ideal is simply the annihilator of $\omega_R/\tau(\omega_R)$.  In other words, it is
\[
( \tau(\omega_R) : \omega_R ).
\]
This can also be described as
\[
\bigcap_{I} (I^* : I),
\]
where $I$ varies over ideals defined by a partial system of parameters, and $I^*$ denotes its tight closure.  This latter description is not computable, however.

\begin{example}\label{Example: parameter test ideal}
In this example we repeat the calculation in \cite[\S 9]{KatzmanParameterTestIdealOfCMRings}.

\medskip
{\small
\begin{MyVerbatim}
i1 : R = ZZ/2[a..e];
i2 : E = matrix { {a,b,b,e}, {d,d,c,a} };
             2       4
o2 : Matrix R  <--- R
i3 : I = minors( 2, E );
o3 : Ideal of R
i4 : S = R/I;
i5 : J = parameterTestIdeal S
o5 = ideal (c + d, b, a)
o5 : Ideal of S
i6 : J = substitute( J, R );
o6 : Ideal of R
i7 : mingens( J+I )
o7 = | c+d b a de |
             1       4
o7 : Matrix R  <--- R
\end{MyVerbatim}
}\medskip

\end{example}

\subsection{Test ideals}

For an $F$-finite reduced ring $R = S/I$, where $S$ is a regular ring, the (big) test ideal\footnote{The notion of test ideals was originally introduced in \cite{HochsterHunekeTC1} in the context of tight closure in finitely generated modules, whereas our notion of test ideals arises from
tight closure in possibly non finitely generated (``big'') modules. Confusingly, big test ideals are included in (small) test ideals.}
of $R$ is the smallest ideal $J$ in $R$, not contained in any minimal prime, such that for all $e > 0$ and all $\phi \in \Hom_R(R^{1/p^e}, R)$ we have
\[ \phi(J^{1/p^e}) \subseteq J.\]
In the case that $R$ is Gorenstein,
$\Hom_R(R^{1/p^e}, R)$ is a cyclic $R^{1/p^e}$-module generated by
$\Phi_e$, which corresponds with the map $T$ above based on the identification
$\omega_R \cong R$ \cite{BlickleSchwedeSurveyPMinusE}.  More generally, if $R$ is $\bQ$-Gorenstein with index not divisible by $p$, then for at least sufficiently divisible $e > 0$, such a generating $\Phi_e$ still exists.

If such a $\Phi_e$ exists, it can be identified to a generator of the module $(I^{[p^e]} : I) / I^{[p^e]}$ by Fedder's Lemma \cite{FedderFPureRat}.  Hence we can find a corresponding\footnote{This is done via the function \texttt{QGorensteinGenerator}. } $u \in I^{[p^e]} : I$.  In this case, if $c \in S$ is the pre-image of a test element of $R$, then setting $I_0 = cR$, it follows that
\[
\tau(R) = {\tt ascendIdeal(e, u, I_0)},
\]
where \texttt{ascendIdeal} is the method explained above, in \autoref{eq.AscendIdealExplanation}.
The $e$ here means all Frobenius roots are taken as multiples of $e$.
%
\pedro{I am not sure what this last sentence is saying}
%

Here is an example (a $\bZ/3\bZ$-quotient, where $3 | (7-1)$), where exactly this logic occurs.

\medskip
{\small
\begin{MyVerbatim}
i1 : T = ZZ/7[x,y];
i2 : S = ZZ/7[a,b,c,d];
i3 : f = map( T, S, { x^3, x^2*y, x*y^2, y^3 } );
i4 : I = ker f;
i5 : R = S/I;
i6 : testIdeal R
o6 = ideal 1
o6 : Ideal of R
\end{MyVerbatim}
}\medskip

However, the term $u$ constructed above can be quite complicated if $e > 1$ (which happens exactly when $(p -1)K_R$ is not Cartier).  For instance, even in the above example we have an extremely complex $u$:

\medskip
{\small
\begin{MyVerbatim}
i7 : toString QGorensteinGenerator( 1, R )
o7 = a^2*b^6*c^12+a^3*b^4*c^13+a^3*b^5*c^11*d+a^4*b^3*c^12*d+a^5*b*c^13*d+b^
     12*c^6*d^2+a^3*b^6*c^9*d^2+a^4*b^4*c^10*d^2+a^5*b^2*c^11*d^2+a^6*c^12*d
     ^2+b^13*c^4*d^3+a*b^11*c^5*d^3+a^2*b^9*c^6*d^3+a^4*b^5*c^8*d^3+a^5*b^3*
     c^9*d^3+a^6*b*c^10*d^3+a*b^12*c^3*d^4+a^2*b^10*c^4*d^4+a^3*b^8*c^5*d^4+
     a^4*b^6*c^6*d^4+a^5*b^4*c^7*d^4+a^6*b^2*c^8*d^4+a^7*c^9*d^4+a*b^13*c*d^
     5+a^2*b^11*c^2*d^5+a^3*b^9*c^3*d^5+a^4*b^7*c^4*d^5+a^5*b^5*c^5*d^5+a^6*
     b^3*c^6*d^5+a^7*b*c^7*d^5+a^2*b^12*d^6+a^3*b^10*c*d^6+a^4*b^8*c^2*d^6+a
     ^5*b^6*c^3*d^6+a^6*b^4*c^4*d^6+a^7*b^2*c^5*d^6+a^8*c^6*d^6+a^4*b^9*d^7+
     a^5*b^7*c*d^7+a^6*b^5*c^2*d^7+a^7*b^3*c^3*d^7+a^8*b*c^4*d^7+a^6*b^6*d^8
     +a^7*b^4*c*d^8+a^8*b^2*c^2*d^8+a^9*c^3*d^8+a^8*b^3*d^9+a^9*b*c*d^9+a^10
     *d^10
\end{MyVerbatim}
}\medskip

Therefore, we use a different strategy if either $(p-1)K_R$ is not Cartier or, more generally, if $R$ is $\bQ$-Gorenstein of index divisible by $p$.
In these situations, this alternate strategy typically appears to be faster.  We rely on the observation (see \cite{BlickleSchwedeTuckerTestAlterations}) that
\[
\tau(\omega_R, K_R) \cong \tau(R).
\]
In fact, by embedding $\omega_R \subseteq R$, we can compute $g$ so that $\tau(\omega_R, K_R) = g\cdot \tau(R)$.  We can therefore find $\tau(R)$ if we can find $\tau(\omega_R, K_R)$.
Next, if $K_R$ is $\bQ$-Cartier with $nK_R = \Div_R(f)$ for some $f \in R$ and $n > 0$, then
\[
\tau(\omega_R, K_R) =\tau(\omega_R, f^{1/n}).
\]
Thus we directly compute $\tau(\omega_R, f^{1/n})$ via the command \texttt{testModule(1/n, f)}.  Consider the following example, a $\mu_3$-quotient, which uses the logic described above.

\medskip
{\small
\begin{MyVerbatim}
i1 : T = ZZ/3[x,y];
i2 : S = ZZ/3[a,b,c,d];
i3 : f = map( T, S, { x^3, x^2*y, x*y^2, y^3 } );
i4 : I = ker f;
i5 : R = S/I;
i6 : testIdeal R
o6 = ideal 1
o6 : Ideal of R
\end{MyVerbatim}
}\medskip

\begin{remark}[Non-graded caveats]
   It frequently happens that $(I^{[p^e]} : I)/I^{[p^e]}$ is principal but \emph{Macaulay2} cannot identify the principal generator (since \emph{Macaulay2} cannot always find minimal generators of non-graded ideals or modules).
   The same thing can happen when computing the element $u$ corresponding to the map $T : \omega_{R^{1/p}} \to \omega_R$, as described in \autoref{subsec.DualToFrobeniusOnQuotientRings}.
   In such situations, instead of a single $u$, \emph{Macaulay2} will produce $u_1, \dots, u_n$ (all multiples of $u$, and $u$ is a linear combination of the $u_i$).  Instead of computing the ideal
\[
(u \cdot J)^{[1/p]},
\]
we compute
\[
(u_1 \cdot J)^{[1/p]} + \dots + (u_n \cdot J)^{[1/p]},
\]
which will produce the same answer.
\end{remark}

We can similarly use the \texttt{testIdeal} command to compute test ideals of pairs, $\tau(R, f^t)$, and even mixed test ideals, $\tau(R, f_1^{t_1} \cdots f_n^{t_n})$.

\subsection{HSLG module; computing $F$-pure submodules of rank-1 Cartier modules}

Again, consider the maps $T^e : \omega_{R^{1/p^e}} \to \omega_R$ we have considered throughout this section.  It is a theorem of Hartshorne-Speiser, Lyubeznik, and Gabber \cite{HartshorneSpeiserLocalCohomologyInCharacteristicP,LyubeznikFModulesApplicationsToLocalCohomology,Gabber.tStruc} that the descending images
\begin{equation}\label{eq: descending images}
\omega_R \supseteq T(\omega_{R^{1/p}}) \supseteq \dots \supseteq T^e(\omega_{R^{1/p^e}}) \supseteq T^{e+1}(\omega_{R^{1/p^{e+1}}}) \supseteq \cdots
\end{equation}
stabilize for $e \gg 0$.
The function \texttt{HSLGModule} computes the stable submodule in this chain, called the \emph{HSLG module}, and returns a list containing the following items:
\begin{enumerate}[(1)]
   \item The HSLG module;
   \item The canonical module;
   \item The element $u$ representing the map on the canonical module (see
   \autoref{subsec.DualToFrobeniusOnQuotientRings});
   \item The value of $e > 0$ at which the descending images in \eqref{eq: descending images} stabilize.
\end{enumerate}

\medskip
{\small
\begin{MyVerbatim}
i1 : R = ZZ/3[x,y,z]/ideal( x^3 + y^4 + z^5 );
i2 : L = HSLGModule R;
i3 : L#0
                          2        2   3
o3 = ideal (0, y*z, x*z, y , x*y, x , z )
o3 : Ideal of R
i4 : L#1
o4 = ideal 1
o4 : Ideal of R
i5 : L#3
o5 = 1
\end{MyVerbatim}
}\medskip

%\bigskip\sout{In a Gorenstein ring, this submodule coincides philosophically with the maximal non-LC ideal of Fujino-Schwede-Takagi.}
%\marginnote{Can someone explain this without recourse to philosophy or morality?}

More generally, for any ideal $J$ with a map $\phi : J^{1/p^e} \to J$, we have that the images
\[
J \supseteq \phi(J^{1/p^e}) \supseteq \phi^2(J^{1/p^{2e}}) \supseteq \cdots
\]
stabilize as well (in fact, the analogous result even holds for modules).

\section{Ideals compatible with given $p^{-e}$-linear map}\label{Section: compatible ideals}

Throughout this section let $R$ denote a polynomial $\mathbb{K}[x_1, \dots, x_n]$. In this section we address the following question:
given a $R$-linear map $\phi: R^{1/p^e} \rightarrow R$, what are all ideals $I\subseteq R$ such that $\phi(I^{1/p^e})=I$?
We call these ideals $\phi$-compatible.

Recall that  $\Hom_R( R^{1/p^e}, R)$  is a principal $R^{1/p^e}$-module generated
the \emph{trace map} $T\in \Hom_R(R^{1/p^e}, R)$, constructed as follows (cf. \cite[Lemma 1.6]{FedderFPureRat} and \cite[Example 1.3.1]{BrionKumarFrobeniusSplitting}).
Recall that, if $B$ is a $\mathbb{K}$-basis for $\mathbb{K}^{1/p^e}$ (with $1\in B$),
$R^{1/p^e}$ is a free $R$-module with basis
$$\left\{ b x_1^{\alpha_1/p^e} \dots x_n^{\alpha_n/p^e} \,|\, 0\leq \alpha_1, \dots, \alpha_n < p^e \right\} ;$$
the trace map $T$ is the projection onto the free summand
$R x_1^{(p^e-1)/p^e} \cdots x_n^{(p^e-1)/p^e}\cong R$.

We can now write our given $\phi$ as multiplication by some $u^{1/p^e}$ followed by $T$ and it is not hard to see that
an ideal $I\subseteq R$ is $\phi$-compatible if and only if $u I \subseteq I^{[p^e]}$.

\begin{theorem}\label{Theorem: finitely many compatible primes}
If $\phi$ is surjective, there are finitely many $\phi$-compatible ideals, consisting of all possible intersections
of $\phi$-compatible prime ideals \textup(cf.\ \cite{KumarMehtaFiniteness}, \cite{SchwedeFAdjunction},
\cite{SharpGradedAnnihilatorsOfModulesOverTheFrobeniusSkewPolynomialRing}, \cite{EnescuHochsterTheFrobeniusStructureOfLocalCohomology}\textup).
In general, there are finitely many $\phi$-compatible prime ideals not containing $\sqrt{\Image \phi}$ \textup(cf.\ \cite{KatzmanSchwedeAlgorithm}\textup).

\end{theorem}

The method \emph{compatibleIdeals} produces the finite set of $\phi$-compatible prime ideals in the second statement of Theorem \ref{Theorem: finitely many compatible primes}.

\medskip
{\small
\begin{MyVerbatim}
i1 : R = ZZ/3[u,v];
i2 : u = u^2*v^2;
i3 : compatibleIdeals u
o3 = {ideal v, ideal (v, u), ideal u}
o3 : List
\end{MyVerbatim}
}\medskip

The defining condition $u I = I^{[p]}$ for $\phi$-compatible ideals allows us to
think of these in a dual form: write $\mathfrak{m}=(x_1, \dots, x_n)R$,
$E=E_{R_\mathfrak{m}}(R_{\mathfrak{m}}/\mathfrak{m})=H^n_{\mathfrak{m}} (R)$, and let
$\Theta: E \rightarrow E$ be the $p^e$-linear map\footnote{I.e., $\Theta$ is additivive and $\Theta (r a)= r^{p^e} \Theta (a)$ for all $a\in E$ and $r\in R$.}
induced from the Frobenius map on $R$.
If $\psi=u \Theta$, then $\psi \Ann_E I \subseteq \Ann_E I$ if and only if $u I = I^{[p]}$!
Thus finding all $R$-submodules of $E$ compatible with $\psi=u \Theta$ also amounts to finding all
$\phi=T \circ u^{1/p^e}$-compatible ideals.

\begin{example}

We return to Example \ref{Example: parameter test ideal}.
In (cf.~\cite[\S 9]{KatzmanParameterTestIdealOfCMRings}) it is shown that
there is a surjection $\Ann_E I \rightarrow H^2_{\mathfrak{m}} (R/I)$
which is compatible with with the induced $p^1$-linear map on $H^2_{\mathfrak{m}} (R/I)$
and the $p^1$-linear map $u \Theta$ on $\Ann_E I$ where $u$ is computed as follows.

\medskip
{\small
\begin{MyVerbatim}
i1 : R = ZZ/2[a..f];
i2 : E = matrix { {a,b,b,e}, {d,d,c,a} };
             2       4
o2 : Matrix R  <--- R
i3 : I = minors( 2, E );
o3 : Ideal of R
i4 : S = R/I;
i5 : isCohenMacaulay S
o5 = true
\end{MyVerbatim}
}\medskip

In \cite{KatzmanParameterTestIdealOfCMRings} it is shown that as that $R/I$ is Cohen-Macaulay $u$
can be taken as the generator of the cyclic module $(I^{[p]}:I) \cap (\Omega^{[p]}:\Omega)/I^{[p]}$
where $\Omega \subseteq R$ is an ideal whose image in $I$ is a canonical module of $R/I$.

\medskip
{\small
\begin{MyVerbatim}
i6 : omega = canonicalIdeal S
o6 = ideal (e, d, a)
o6 : Ideal of S
i7 : omega = substitute( omega, R ) + I;
o7 : Ideal of R
i8 : u = intersect( (frobenius I ):I, ( frobenius omega ):omega );
o8 : Ideal of R
i9 : u = compress( (gens u) % gens( frobenius I) )
o9 = | a3bc+a3bd+a2cde+abcde+abd2e+b2d2e+cd2e2+d3e2 |
             1       1
o9 : Matrix R  <--- R
i10 : u = first first entries u
       3       3       2                         2     2 2       2 2    3 2
o10 = a b*c + a b*d + a c*d*e + a*b*c*d*e + a*b*d e + b d e + c*d e  + d e
o10 : R
\end{MyVerbatim}
}
\medskip

Now we can compute all annihilators of $R$-submodules of $E$ stable under the $p^1$-linear map $uT$

\medskip
{\small
\begin{MyVerbatim}
i11 : L = compatibleIdeals u;
i12 : print \ L;
       3       3       2                         2     2 2       2 2    3 2
ideal(a b*c + a b*d + a c*d*e + a*b*c*d*e + a*b*d e + b d e + c*d e  + d e )
               2
ideal (a + b, a  + d*e)
ideal (d, a)
ideal (d, a, e)
ideal (e, d, a, c)
ideal (e, d, c, b, a)
ideal (e, d, b, a)
ideal (d, a, c)
ideal (d, c, b, a)
ideal (d, b, a)
                      2
ideal (c + d, a + b, b  + d*e)
ideal (c + d, b, a, e)
ideal (b, a, e)
\end{MyVerbatim}
}
\medskip

and all annihilators of $R$-submodules of $H^2_{\mathfrak{m}} (R/I)$ stable under the $p^1$-linear map induced from the Frobenius map on $R/I$.

\medskip
{\small
\begin{MyVerbatim}
i13 : print \ unique apply( L, J -> J : omega );
       3       3       2                         2     2 2       2 2    3 2
ideal(a b*c + a b*d + a c*d*e + a*b*c*d*e + a*b*d e + b d e + c*d e  + d e )
               2
ideal (a + b, b  + d*e)
ideal (d, a)
ideal (e, d, a)
ideal 1
ideal (d, c, a)
ideal (d, c, b, a)
ideal (d, b, a)
                      2
ideal (c + d, a + b, b  + d*e)
ideal (e, c + d, b, a)
ideal (e, b, a)
\end{MyVerbatim}
}
\medskip

\end{example}

\section{Future plans}

In \cite{KatzmanZhangAlgorithm} the algorithms behind the method in Section \ref{Section: compatible ideals} were extended
to compute prime annihilators of submodules of Artinian modules compatible with a given $p^{e}$-linear map.
This would require, among other things, a faster implementation of our method for finding Frobenius roots of submodules of free modules.

On the other hand, it should be possible to compute test ideals of pairs $(R, \fra^t)$ even when $\fra$ is not principal.  One strategy to do this is outlined in \cite{SchwedeTuckerTestIdealsOfNonPrincipal} although certain improvement can be made.

We hope to achieve all these things during a future \emph{Macaulay2} workshop.  We also want to bring to the reader's attention the package \texttt{FThresholds.m2} which computes $F$-pure thresholds, $F$-thresholds, $F$-jumping numbers and more!

\bibliographystyle{skalpha}
\bibliography{MainBib}

\end{document}

### 2018-10-04 Fsing/TestIdealsPaper/TestIdeals.tex
Small changes to paper

@@
 
-\section{Ideals compatible with given $p^{-e}$-linear map}\label{Section: compatible ideals}
-
-Throughout this section let $R$ denote a polynomial $\mathbb{K}[x_1, \dots, x_n]$. In this section we address the following question:
-given a $R$-linear map $\phi: R^{1/p^e} \rightarrow R$, what are all ideals $I\subseteq R$ such that $\phi(I^{1/p^e})=I$?
+\section{Ideals compatible with a given $p^{-e}$-linear map}\label{Section: compatible ideals}
+
+Throughout this section, let $R$ denote a polynomial $\mathbb{K}[x_1, \dots, x_n]$.
+In this section we address the following question:
+given a $R$-linear map $\phi: R^{1/p^e} \rightarrow R$, what are the ideals $I\subseteq R$ such that $\phi(I^{1/p^e})\subseteq I$?
 We call these ideals $\phi$-compatible.
@@
 the \emph{trace map} $T\in \Hom_R(R^{1/p^e}, R)$, constructed as follows (cf. \cite[Lemma 1.6]{FedderFPureRat} and \cite[Example 1.3.1]{BrionKumarFrobeniusSplitting}).
-Recall that, if $B$ is a $\mathbb{K}$-basis for $\mathbb{K}^{1/p^e}$ (with $1\in B$),
+If $B$ is a $\mathbb{K}$-basis for $\mathbb{K}^{1/p^e}$, with $1\in B$, then 
 $R^{1/p^e}$ is a free $R$-module with basis
-$$\left\{ b x_1^{\alpha_1/p^e} \dots x_n^{\alpha_n/p^e} \,|\, 0\leq \alpha_1, \dots, \alpha_n < p^e \right\} ;$$
+$$\left\{ b\,  x_1^{\alpha_1/p^e} \cdots x_n^{\alpha_n/p^e} \,|\, 0\leq \alpha_1, \dots, \alpha_n < p^e, b\in B \right\} ;$$
 the trace map $T$ is the projection onto the free summand
 $R x_1^{(p^e-1)/p^e} \cdots x_n^{(p^e-1)/p^e}\cong R$.
+%
+\pedro{This paragraph is a bit redundant; we could just refer to Section~\ref{ss: math behind}}
+%
 
@@
 
-The method \emph{compatibleIdeals} produces the finite set of $\phi$-compatible prime ideals in the second statement of Theorem \ref{Theorem: finitely many compatible primes}.
+The method \texttt{compatibleIdeals} produces the finite set of $\phi$-compatible prime ideals in the second claim of Theorem \ref{Theorem: finitely many compatible primes}.
 
@@
 
-The defining condition $u I = I^{[p]}$ for $\phi$-compatible ideals allows us to
-think of these in a dual form: write $\mathfrak{m}=(x_1, \dots, x_n)R$,
+The defining condition $u I \subseteq I^{[p^e]}$ for $\phi$-compatible ideals allows us to
+think of these in a dual form: write $\mathfrak{m}=(x_1, \dots, x_n)$,
 $E=E_{R_\mathfrak{m}}(R_{\mathfrak{m}}/\mathfrak{m})=H^n_{\mathfrak{m}} (R)$, and let
-$\Theta: E \rightarrow E$ be the $p^e$-linear map\footnote{I.e., $\Theta$ is additivive and $\Theta (r a)= r^{p^e} \Theta (a)$ for all $a\in E$ and $r\in R$.}
+$\Theta: E \rightarrow E$ be the $p^e$-linear map\footnote{That is, $\Theta$ is additivive and $\Theta (r a)= r^{p^e} \Theta (a)$ for all $a\in E$ and $r\in R$.}
 induced from the Frobenius map on $R$.
-If $\psi=u \Theta$, then $\psi \Ann_E I \subseteq \Ann_E I$ if and only if $u I = I^{[p]}$!
+If $\psi=u \Theta$, then $\psi \Ann_E I \subseteq \Ann_E I$ if and only if $u I \subseteq  I^{[p^e]}$.
 Thus finding all $R$-submodules of $E$ compatible with $\psi=u \Theta$ also amounts to finding all
-$\phi=T \circ u^{1/p^e}$-compatible ideals.
+$\phi$-compatible ideals, where $\phi=T \circ u^{1/p^e}$.
 
 \begin{example}
-
 We return to Example \ref{Example: parameter test ideal}.
@@
 there is a surjection $\Ann_E I \rightarrow H^2_{\mathfrak{m}} (R/I)$
-which is compatible with with the induced $p^1$-linear map on $H^2_{\mathfrak{m}} (R/I)$
-and the $p^1$-linear map $u \Theta$ on $\Ann_E I$ where $u$ is computed as follows.
+which is compatible  with the induced $p^1$-linear map on $H^2_{\mathfrak{m}} (R/I)$
+and the $p^1$-linear map $u \Theta$ on $\Ann_E I$, where $u$ is computed as follows.
 
@@
 
-In \cite{KatzmanParameterTestIdealOfCMRings} it is shown that as that $R/I$ is Cohen-Macaulay $u$
+In \cite{KatzmanParameterTestIdealOfCMRings} it is shown that as $R/I$ is Cohen-Macaulay, $u$
 can be taken as the generator of the cyclic module $(I^{[p]}:I) \cap (\Omega^{[p]}:\Omega)/I^{[p]}$
-where $\Omega \subseteq R$ is an ideal whose image in $I$ is a canonical module of $R/I$.
+where $\Omega \subseteq R$ is an ideal whose image in $R/I$ is a canonical module of that ring.
 
@@
 
-Now we can compute all annihilators of $R$-submodules of $E$ stable under the $p^1$-linear map $uT$
+Now we can compute all annihilators of $R$-submodules of $E$ stable under the $p^1$-linear map $uT$.
 
@@
 
-and all annihilators of $R$-submodules of $H^2_{\mathfrak{m}} (R/I)$ stable under the $p^1$-linear map induced from the Frobenius map on $R/I$.
+We can also compute  all annihilators of $R$-submodules of $H^2_{\mathfrak{m}} (R/I)$ stable under the $p^1$-linear map induced from the Frobenius map on $R/I$.
 
@@
 
-In \cite{KatzmanZhangAlgorithm} the algorithms behind the method in Section \ref{Section: compatible ideals} were extended
+In \cite{KatzmanZhangAlgorithm}, the algorithms behind the methods in Section \ref{Section: compatible ideals} were extended
 to compute prime annihilators of submodules of Artinian modules compatible with a given $p^{e}$-linear map.

### 2018-10-05 Fsing/TestIdealsPaper/TestIdeals.tex
Addressed Pedro's comments.

@@
 %
-\pedro{Are we assuming here that $R$ is a quotient of a polynomial ring?}
+%\pedro{Are we assuming here that $R$ is a quotient of a polynomial ring?}
 %
-Given an $F$-finite reduced ring $R$, the Frobenius map $R \hookrightarrow R^{1/p^e}$ is dual to $T : \omega_{R^{1/p^e}} \to \omega_R$.
+Given an reduced ring $R$ of finite type over a perfect field $k$, the Frobenius map $R \hookrightarrow R^{1/p^e}$ is dual to $T : \omega_{R^{1/p^e}} \to \omega_R$.
 As in \autoref{subsec.DualToFrobeniusOnQuotientRings}, we can represent the canonical module $\omega_R \subseteq R$ as an ideal, we can write $R = S/I$, and so we can find an element $u \in S^{1/p^e}$ representing the map $T:\omega_{R^{1/p^e}} \to \omega_R$; see \autoref{subsec.DualToFrobeniusOnQuotientRings} or \cite{KatzmanParameterTestIdealOfCMRings}.
@@
    %
-   \pedro{What is the quantifier for $e$ here?}
+   %\pedro{What is the quantifier for $e$ here?}
    %
 \[
-T (M^{1/p^e}) \subseteq M.
-\]
+T (M^{1/p^e}) \subseteq M
+\]
+for some $e > 0$ (or equivalently for all $e > 0$).
 \end{definition}
@@
 where \texttt{ascendIdeal} is the method explained above, in \autoref{eq.AscendIdealExplanation}.
-The $e$ here means all Frobenius roots are taken as multiples of $e$.
+The $e$ here means all Frobenius roots are taken as multiples of $e$.  In other words, we first compute ${\tt I_0 +  (u \cdot I_0)^{1/p^{[e]}}}$.  Then we compute 
+\[
+{\tt I_0 +  (u\cdot I_0)^{1/p^{[e]}} + (u^{p^e + 1} \cdot I_0)^{1/p^{[2e]}} }
+\]
+etc.
 %
-\pedro{I am not sure what this last sentence is saying}
+%\pedro{I am not sure what this last sentence is saying}
 %
@@
 Recall that  $\Hom_R( R^{1/p^e}, R)$  is a principal $R^{1/p^e}$-module generated
-the \emph{trace map} $T\in \Hom_R(R^{1/p^e}, R)$, constructed as follows (cf. \cite[Lemma 1.6]{FedderFPureRat} and \cite[Example 1.3.1]{BrionKumarFrobeniusSplitting}).
-If $B$ is a $\mathbb{K}$-basis for $\mathbb{K}^{1/p^e}$, with $1\in B$, then 
-$R^{1/p^e}$ is a free $R$-module with basis
-$$\left\{ b\,  x_1^{\alpha_1/p^e} \cdots x_n^{\alpha_n/p^e} \,|\, 0\leq \alpha_1, \dots, \alpha_n < p^e, b\in B \right\} ;$$
-the trace map $T$ is the projection onto the free summand
-$R x_1^{(p^e-1)/p^e} \cdots x_n^{(p^e-1)/p^e}\cong R$.
+the \emph{trace map} $T\in \Hom_R(R^{1/p^e}, R)$, constructed as in \autoref{ss: math behind}, (cf. \cite[Lemma 1.6]{FedderFPureRat} and \cite[Example 1.3.1]{BrionKumarFrobeniusSplitting}).
+%If $B$ is a $\mathbb{K}$-basis for $\mathbb{K}^{1/p^e}$, with $1\in B$, then
+%$R^{1/p^e}$ is a free $R$-module with basis
+%$$\left\{ b\,  x_1^{\alpha_1/p^e} \cdots x_n^{\alpha_n/p^e} \,|\, 0\leq \alpha_1, \dots, \alpha_n < p^e, b\in B \right\} ;$$
+%the trace map $T$ is the projection onto the free summand
+%$R x_1^{(p^e-1)/p^e} \cdots x_n^{(p^e-1)/p^e}\cong R$.
 %
-\pedro{This paragraph is a bit redundant; we could just refer to Section~\ref{ss: math behind}}
+%\pedro{This paragraph is a bit redundant; we could just refer to Section~\ref{ss: math behind}}
 %

### 2018-10-05 Fsing/TestIdealsPaper/TestIdeals.tex
Formatting consistency changes.

@@
 Below is an example of a computation of a Frobenius root in a polynomial ring.
-In Section~\ref{ss: math behind} we describe the main ideas behind such computations.
+In \autoref{ss: math behind} we describe the main ideas behind such computations.
 
@@
 
-The generalized Frobenius powers of an ideal are test ideals (see Section~\ref{Section: Test Ideals}) of sufficiently general linear combinations of generators of that ideal.
+The generalized Frobenius powers of an ideal are test ideals (see \autoref{Section: Test Ideals}) of sufficiently general linear combinations of generators of that ideal.
 Thus, the ideals computed above are test ideals of generic quintics in two variables in characteristic $p=3$, and these computations suggest that $\frac35-\frac1{5p^3}$ is a higher $F$-jumping exponent of such quintics, which is indeed the case for any $p\equiv 3 \bmod 5$ (see \cite{hernandez+etal.frobenius_examples}).
@@
 
-The calculation above shows that $R/I$ is not $F$-injective (cf. Section \ref{Section: F-singularities}).
+The calculation above shows that $R/I$ is not $F$-injective (cf. \autoref{Section: F-singularities}).
 Moreover, it shows that $H^2_{\mathfrak{m}} (R/I)\cong \Ann_{E^2} A^t$,
@@
 given by $\Ann_{E^2} B^t$, where $B$ is the smallest submodule of $R^2$ containing $\Image A + \Image U$ such that $U  B \subseteq B^{[p]}$.
-The method \texttt{ascendModule} can be used to calculate  $B$ (see a detailed description of the similar method \texttt{ascendIdeal} in Section \ref{Section: Test Ideals}).
+The method \texttt{ascendModule} can be used to calculate  $B$ (see a detailed description of the similar method \texttt{ascendIdeal} in \autoref{Section: Test Ideals}).
 
@@
 
-The method \texttt{compatibleIdeals} produces the finite set of $\phi$-compatible prime ideals in the second claim of Theorem \ref{Theorem: finitely many compatible primes}.
+The method \texttt{compatibleIdeals} produces the finite set of $\phi$-compatible prime ideals in the second claim of \autoref{Theorem: finitely many compatible primes}.
 
@@
 \begin{example}
-We return to Example \ref{Example: parameter test ideal}.
+We return to \autoref{Example: parameter test ideal}.
 In (cf.~\cite[\S 9]{KatzmanParameterTestIdealOfCMRings}) it is shown that
@@
 
-In \cite{KatzmanZhangAlgorithm}, the algorithms behind the methods in Section \ref{Section: compatible ideals} were extended
+In \cite{KatzmanZhangAlgorithm}, the algorithms behind the methods in \autoref{Section: compatible ideals} were extended
 to compute prime annihilators of submodules of Artinian modules compatible with a given $p^{e}$-linear map.

### 2018-10-05 Fsing/TestIdealsPaper/TestIdeals.tex
Tiny change to paper.

@@
 %
-Given an reduced ring $R$ of finite type over a perfect field $k$, the Frobenius map $R \hookrightarrow R^{1/p^e}$ is dual to $T : \omega_{R^{1/p^e}} \to \omega_R$.
+Given a reduced ring $R$ of finite type over a perfect field $k$, the Frobenius map $R \hookrightarrow R^{1/p^e}$ is dual to $T : \omega_{R^{1/p^e}} \to \omega_R$.
 As in \autoref{subsec.DualToFrobeniusOnQuotientRings}, we can represent the canonical module $\omega_R \subseteq R$ as an ideal, we can write $R = S/I$, and so we can find an element $u \in S^{1/p^e}$ representing the map $T:\omega_{R^{1/p^e}} \to \omega_R$; see \autoref{subsec.DualToFrobeniusOnQuotientRings} or \cite{KatzmanParameterTestIdealOfCMRings}.

### 2018-10-05 Fsing/TestIdealsPaper/TestIdeals.tex
Fixed some bad breaks.

@@
 Erin Bela, Juliette Bruce, Drew Ellingson, Matthew Mastroeni, and Maral Mostafazadehfard.
-This paper, and the finishing touches to the \texttt{TestIdeals.m2} package, were made at the University of Utah in 2018, and the visiting authors thank the Department of Mathematics for its hospitality.
+This paper, and the finishing touches to the package \texttt{TestIdeals.m2}, were made at the University of Utah in 2018, and the visiting authors thank the Department of Mathematics for its hospitality.
 

### 2018-10-12 Fsing/TestIdealsPaper/TestIdeals.tex
Added subsection about the level of a polynomial

@@
 
+\subsection{Computing the level of a polynomial}
+Another interesting invariant that can be calculated using this package
+is the so--called \emph{level} of a polynomial; more precisely:
+
+\begin{definition}
+Let $K$ be an $F$--finite field of prime characteristic $p,$ and let
+$f\in R=K[x_1,\ldots, x_d].$ We define the \emph{level of} $f$ as the
+smallest possible integer $e$ where the descending chain
+\[
+R=(f^{p^0-1})^{[1/p^0]}\supseteq (f^{p-1})^{[1/p]}\supseteq
+(f^{p^2-1})^{[1/p^2]}\supseteq\ldots\supseteq (f^{p^{i-1}-1})^{[1/p^{i-1}]}
+\supseteq (f^{p^i-1})^{[1/p^i]}\supseteq\ldots
+\]
+stabilizes.
+\end{definition}
+This invariant was introduced in \cite{AlvarezBlickleLyubeznik2005}. One interesting particular
+case is when $K=\mathbb{F}_p$ and $f$ is the defining homogeneous polynomial of a hyperelliptic curve
+of genus $g;$ when $g=1,$ it was proved in
+\cite{BoixDeStefaniVanzo2015} that the corresponding elliptic curve defined by $f$
+is ordinary if and only if its level is $1,$ (equivalently, if and only if
+$(R/(f))_{(x,y,z)}$ is $F$--pure \cite{TakTak08}) and supersingular if and only if its level is $2.$ When
+the genus is at least $2,$ level $2$ is a necessary (but not sufficient) condition for the curve
+for being ordinary \cite{BlancoBoixFordhamYilmaz2018}; in this case, one also
+has that, if the curve is supersingular, then its level has to be at least $3,$ so the level can
+always distinguish these two properties in any genus. We illustrate these results by means
+of the following examples.
+
+\medskip
+{\small
+\begin{MyVerbatim}
+i1 : R = ZZ/2[x,y,z];
+i2 : f = x^3+y^2*z+y*z^2;
+i3 : frobeniusPower( 1/2, ideal f )
+o3 = ideal (x, y , z )
+o3 : Ideal of R
+i4 : u=f^3;
+i5 : frobeniusPower( 1/4, ideal u )
+o6 = ideal (x, y , z )
+o6 : Ideal of R
+\end{MyVerbatim}
+}\medskip
+
+This shows that this elliptic curve has level $2,$ hence it is supersingular. The next example
+shows a non--ordinary hyperelliptic curve of genus $2$ with level $2.$
+
+\medskip
+{\small
+\begin{MyVerbatim}
+i1 : R = ZZ/11[x,y,z];
+i2 : f = y^2*z^3-x^5-2*z^5;
+i3 : frobeniusPower( 1/11, ideal f )
+             2        3
+o3 = ideal (z , x*z, x )
+o3 : Ideal of R
+i4 : u=f^{121-1};
+i5 : frobeniusPower( 1/121, ideal u )
+             2        3
+o6 = ideal (z , x*z, x )
+o6 : Ideal of R
+\end{MyVerbatim}
+}\medskip
+
 \subsection{$F$-rationality}

### 2018-10-16 Fsing/TestIdealsPaper/TestIdeals.tex
Added explanation of HSLG module stuff.

--- 2018-10-05 Fsing/TestIdealsPaper/TestIdeals.tex
@@
    \autoref{subsec.DualToFrobeniusOnQuotientRings});
-   \item The value of $e > 0$ at which the descending images in \eqref{eq: descending images} stabilize.
+   \item The value of $e > 0$ at which the descending images in \eqref{eq: descending images} stabilize.  This is sometimes also called the HSLG-number of the canonical module as a Cartier module.
 \end{enumerate}
@@
 \]
-stabilize as well (in fact, the analogous result even holds for modules).
+stabilize as well (in fact, the analogous result even holds for modules \cite{Gabber.tStruc}).
+
+\subsection{Computing the level of a polynomial}
+Another interesting invariant that can be calculated using this package
+is the so--called \emph{level} of a polynomial; more precisely:
+
+\begin{definition}
+Let $K$ be an $F$--finite field of prime characteristic $p,$ and let
+$f\in R=K[x_1,\ldots, x_d].$ We define the \emph{level of} $f$ as the
+smallest possible integer $e$ where the descending chain
+\[
+R=(f^{p^0-1})^{[1/p^0]}\supseteq (f^{p-1})^{[1/p]}\supseteq
+(f^{p^2-1})^{[1/p^2]}\supseteq\ldots%\supseteq (f^{p^{i-1}-1})^{[1/p^{i-1}]}
+\supseteq (f^{p^i-1})^{[1/p^i]}\supseteq\ldots
+\]
+stabilizes.
+\end{definition}
+This invariant was introduced in \cite{AlvarezBlickleLyubeznik2005}.  It is also essentially the same data as the HSLG-number of the pair $(R, f^1)$ as computed in (4) above (it is that number $+1$).
+One interesting particular
+case is when $K=\mathbb{F}_p$ and $f$ is the defining homogeneous polynomial of a hyperelliptic curve
+of genus $g;$ when $g=1,$ it was proved in
+\cite{BoixDeStefaniVanzo2015} that the corresponding elliptic curve defined by $f$
+is ordinary if and only if its level is $1,$ (equivalently, if and only if
+$(R/(f))_{(x,y,z)}$ is $F$--pure% \cite{TakTak08}
+) and supersingular if and only if its level is $2.$ When
+the genus is at least $2,$ level $2$ is a necessary (but not sufficient) condition for the curve
+for being ordinary \cite{BlancoBoixFordhamYilmaz2018}; in this case, one also
+has that, if the curve is supersingular, then its level has to be at least $3,$ so the level can
+always distinguish these two properties in any genus. We illustrate these results by means
+of the following examples.
+
+\medskip
+{\small
+\begin{MyVerbatim}
+i1 : R = ZZ/2[x,y,z];
+i2 : f = x^3+y^2*z+y*z^2;
+i3 : frobeniusPower( 1/2, ideal f )
+o3 = ideal (x, y , z )
+o3 : Ideal of R
+i4 : u=f^3;
+i5 : frobeniusPower( 1/4, ideal u )
+o6 = ideal (x, y , z )
+o6 : Ideal of R
+i7 : ((HSLGModule(1, f))#3) + 1
+o7 : 2
+\end{MyVerbatim}
+}\medskip
+
+This shows that this elliptic curve has level $2,$ hence it is supersingular. The next example
+shows a non--ordinary hyperelliptic curve of genus $2$ with level $2.$
+
+\medskip
+{\small
+\begin{MyVerbatim}
+i1 : R = ZZ/11[x,y,z];
+i2 : f = y^2*z^3-x^5-2*z^5;
+i3 : frobeniusPower( 1/11, ideal f )
+             2        3
+o3 = ideal (z , x*z, x )
+o3 : Ideal of R
+i4 : u=f^{121-1};
+i5 : frobeniusPower( 1/121, ideal u )
+             2        3
+o6 = ideal (z , x*z, x )
+o6 : Ideal of R
+i7 : ((HSLGModule(1, f))#3) + 1
+o7 : 2
+\end{MyVerbatim}
+}\medskip
 

### 2018-10-17 Fsing/TestIdealsPaper/TestIdeals.tex
Modification in the level part, \cite{TakTak08}
I just point out that the equivalence for an elliptic curve between F-purity and being ordinary was already proved by Takagi and Takahashi.

@@
 is ordinary if and only if its level is $1,$ (equivalently, if and only if
-$(R/(f))_{(x,y,z)}$ is $F$--pure% \cite{TakTak08}
+$(R/(f))_{(x,y,z)}$ is $F$--pure, this was already proved by Takagi and Takahashi in \cite{TakTak08}
 ) and supersingular if and only if its level is $2.$ When

### 2018-10-19 Fsing/TestIdealsPaper/TestIdeals.tex
Removed TakTak08 reference as I believe equivalent statements were known decades earlier.

--- 2018-10-16 Fsing/TestIdealsPaper/TestIdeals.tex
@@
 is ordinary if and only if its level is $1,$ (equivalently, if and only if
-$(R/(f))_{(x,y,z)}$ is $F$--pure% \cite{TakTak08}
+$(R/(f))_{(x,y,z)}$ is $F$--pure, %this was already proved by Takagi and Takahashi in \cite{TakTak08}
 ) and supersingular if and only if its level is $2.$ When

### 2019-01-19 Fsing/TestIdealsPaper/TestIdeals.tex
Fixed couple of typos found by referee

@@
 \title{The  {TestIdeals} package for \emph{Macaulay2}}
-\author[Alberto F.\ Boix et at.]{Alberto F.\ Boix}
+\author[Alberto F.\ Boix et al.]{Alberto F.\ Boix}
 \address{Department of Mathematics, Ben-Gurion University of the Negev, Beer-Sheva 8410501, Israel}
@@
 i3 : frobeniusPower( 1/2, ideal f )
-o3 = ideal (x, y , z )
+o3 = ideal (x, y, z)
 o3 : Ideal of R
@@
 i5 : frobeniusPower( 1/4, ideal u )
-o6 = ideal (x, y , z )
+o6 = ideal (x, y, z)
 o6 : Ideal of R
@@
 This shows that this elliptic curve has level $2,$ hence it is supersingular. The next example
-shows a non--ordinary hyperelliptic curve of genus $2$ with level $2.$
+shows a non-ordinary hyperelliptic curve of genus $2$ with level $2$.
 
@@
 i3 : frobeniusPower( 1/11, ideal f )
-             2        3
-o3 = ideal (z , x*z, x )
+o3 = ideal 1
 o3 : Ideal of R
-i4 : u=f^{121-1};
+i4 : u = f^(121-1);
 i5 : frobeniusPower( 1/121, ideal u )

### 2019-01-29 Fsing/TestIdealsPaper/TestIdeals.tex
Updated paper as referee suggested.  Also made a change to how frobeniusPowerHelper works in the case of Strategy=>Safe.  It should be much faster that way.

@@
 o4 = ideal (z, y, x)
-o4 : Ideal of R
+o4 : Ideal of S
 
@@
 o8 = ideal 1
-o8 : Ideal of R
+o8 : Ideal of S
 \end{MyVerbatim}
@@
 \item The canonical module that contains the test module, given as an ideal of $R$.
+(Note the representation of the canonical module as an ideal is not unique, it is only unique up to isomorphism, hence it is important to return this module as well).
 \item The element $u$ described above (not displayed above, since it takes a lot of space).
@@
    \item The HSLG module;
-   \item The canonical module;
+   \item The canonical module, embedded (non-uniquely) as an ideal;
    \item The element $u$ representing the map on the canonical module (see
@@
 i2 : f = y^2*z^3-x^5-2*z^5;
-i3 : frobeniusPower( 1/11, ideal f )
+i3 : frobeniusPower( 10/11, ideal f )
 o3 = ideal 1
 o3 : Ideal of R
-i4 : u = f^(121-1);
-i5 : frobeniusPower( 1/121, ideal u )
+i5 : frobeniusPower( 120/121, ideal f )
              2        3

### 2019-01-29 Fsing/TestIdealsPaper/TestIdeals.tex
Fixed a typo in the paper.

@@
 i2 : f = y^2*z^3-x^5-2*z^5;
-i3 : frobeniusPower( 10/11, ideal f )
-o3 = ideal 1
+i3 : frobeniusPower( 1/11, ideal f^10 )
+             2        3
+o6 = ideal (z , x*z, x )
 o3 : Ideal of R
-i5 : frobeniusPower( 120/121, ideal f )
+i5 : frobeniusPower( 1/121, ideal f^120 )
              2        3

### 2019-04-14 Fsing/TestIdealsPaper/TestIdeals.tex
Changes in doc for testModule

@@
 
-The algorithm used by \texttt{isFRational} first checks if the ring is Cohen-Macaulay, unless the option \texttt{isCohenMacaulay} is set to \texttt{true}. If the ring
+The algorithm used by \texttt{isFRational} first checks if the ring is Cohen-Macaulay, unless the option \texttt{AssumeCM} is set to \texttt{true}. If the ring
 is not Cohen-Macaulay then \texttt{false} is returned. Next, the algorithm

### 2019-04-16 Fsing/TestIdealsPaper/TestIdeals.tex
Update TestIdeals.tex

@@
 The computation of Frobenius roots of ideals reduces to the case of principal ideals, and its complexity grows linearly with the number of generators of the ideal.
-Furthermore the calculation of  $(f)^{[1/p^e]}$ reduces to finding the summands in (\ref{eqn1}), which essentially amounts to
+Furthermore the calculation of  $(f)^{[1/p^e]}$ reduces to finding the terms in the right hand side of (\ref{eqn1}), which essentially amounts to
 taking each term in $f$, computing the $p^e$-th root of the coefficient in $\mathbb{K}$, and dividing the monomial exponent vector by $p^e$ with remainder.

### 2019-04-16 Fsing/TestIdealsPaper/TestIdeals.tex
Update TestIdeals.tex

@@
 
-This paper describes methods for computing objects and numerical invariants in prime characteristic commutative algebra, implemented in the \texttt{TestIdeals.m2} package for the computer algebra system \emph{Macaulay2}.
+This paper describes methods for computing objects and numerical invariants in prime characteristic commutative algebra, implemented in the \texttt{TestIdeals.m2} package for the computer algebra system \emph{Macaulay2} \cite{M2}.
 A ring $R$ of prime characteristic $p$ comes equipped with the Frobenius endomorphism

### 2019-04-18 Fsing/TestIdealsPaper/TestIdeals.tex
Changes 1 and 3 asked by referee:M2 and summands
Following referee's comments on the paper, I cited M2 in the bibliography and I modified the issue between terms and summands, writing it as referee suggests.
Changes to doc of testIdeal

@@
 \email{fernanal@post.bgu.ac.il}
-\thanks{A.F.~Boix was supported by Israel Science Foundation (grant No. 844/14) and Spanish Ministerio de Econom\'ia y Competitividad MTM2016-7881-P}
+\thanks{A.F.\,Boix was supported by Israel Science Foundation (grant No. 844/14) and Spanish Ministerio de Econom\'ia y Competitividad MTM2016-7881-P}
 
@@
  \item[(a)] If $n$ is a positive integer with base $p$ expansion  $n=d_0 + d_1 p +  \dots + d_r p^r$, we define
-\[ I^{[n]}=I^{d_0} (I^{d_1})^{[p]} \dots  (I^{d_r})^{[p^r]}.\]
+\[ I^{[n]}=I^{d_0} (I^{d_1})^{[p]} \cdots  (I^{d_r})^{[p^r]}.\]
  \item[(b)] If $t$ is a nonnegative rational number of the form $t = a/p^e$, we define  $I^{[t]} = {\big(I^{[a]}\big)}^{[1/p^e]}.$
@@
 $$I= (a,b) \cap (a,c) \cap (c,d) \cap (c+d, a^3+b d^2).$$
-Then $R/I$ is a $3$-dimensional non-Cohen-Macaulay ring.
+Then $R/I$ is a $3$-dimensional non-Cohen--Macaulay ring.
 Matlis Duality applied to $H^2_{\mathfrak{m}} (R/I)$ with its natural Frobenius map
@@
 The performance of the algorithm can be improved if the ring of interest is
-nice enough. If the ring is Cohen-Macaulay, then setting \texttt{AssumeCM =>
+nice enough. If the ring is Cohen--Macaulay, then setting \texttt{AssumeCM =>
 true} (the default value is \texttt{false}) lets the algorithm check the Frobenius action only on top cohomology
@@
 %Of
-%course, telling the algorithm to assume the ring is Cohen-Macaulay when it
+%course, telling the algorithm to assume the ring is Cohen--Macaulay when it
 %is not can lead to an incorrect answer if the non-injective Frobenius
@@
 \begin{definition}
-Suppose that $R$ is a Cohen-Macaulay ring and that $T_{R} :
+Suppose that $R$ is a Cohen--Macaulay ring and that $T_{R} :
 \omega_{R^{1/p}} \rightarrow \omega_{R}$ is the canonical dual to the
@@
 
-The algorithm used by \texttt{isFRational} first checks if the ring is Cohen-Macaulay, unless the option \texttt{AssumeCM} is set to \texttt{true}. If the ring
-is not Cohen-Macaulay then \texttt{false} is returned. Next, the algorithm
+The algorithm used by \texttt{isFRational} first checks if the ring is Cohen--Macaulay, unless the option \texttt{AssumeCM} is set to \texttt{true}. If the ring
+is not Cohen--Macaulay then \texttt{false} is returned. Next, the algorithm
 computes the test module $M \subseteq \omega_{R}$ and checks to see if
@@
 
-In \cite{KatzmanParameterTestIdealOfCMRings} it is shown that as $R/I$ is Cohen-Macaulay, $u$
+In \cite{KatzmanParameterTestIdealOfCMRings} it is shown that as $R/I$ is Cohen--Macaulay, $u$
 can be taken as the generator of the cyclic module $(I^{[p]}:I) \cap (\Omega^{[p]}:\Omega)/I^{[p]}$

### 2019-04-24 Fsing/TestIdealsPaper/TestIdeals.tex
Several small changes in formatting

@@
 i1 : R = ZZ/5[x,y,z];
-i2 : I = ideal( x^6*y*z + x^2*y^12*z^3 + x*y*z^18 );
+i2 : I = ideal(x^6*y*z + x^2*y^12*z^3 + x*y*z^18);
 o2 : Ideal of R
-i3 : frobeniusPower( 1/5, I )
+i3 : frobeniusPower(1/5, I)
                 2   3
@@
 i2 : f = x^3 + y^3 + z^3;
-i3 : u = f^(5-1);
-i4 : frobeniusRoot( 1, ideal u )
+i3 : u = f^(5 - 1);
+i4 : frobeniusRoot(1, ideal u)
 o4 = ideal (z, y, x)
@@
 i6 : f = x^3 + y^3 + z^3;
-i7 : u = f^(7-1)
-i8 : frobeniusRoot( 1, ideal u )
+i7 : u = f^(7 - 1)
+i8 : frobeniusRoot(1, ideal u)
 o8 = ideal 1
@@
 i2 : R = ZZ/p[x,y];
-i3 : m = monomialIdeal( x, y );
+i3 : m = monomialIdeal(x, y);
 o3 : MonomialIdeal of R
@@
 i5 : t = 3/5 - 1/(5*p^3);
-i6 : frobeniusPower( t, I )
+i6 : frobeniusPower(t, I)
              2        2
@@
 o6 : Ideal of R
-i7 : frobeniusPower( t - 1/p^5, I )
+i7 : frobeniusPower(t - 1/p^5, I)
 o7 = ideal (y, x)
@@
 i9 : G = a*x^5 + b*x^4*y + c*x^3*y^2 + d*x^2*y^3 + e*x*y^4 + f*y^5;
-i10 : testIdeal( t, G )
+i10 : testIdeal(t, G)
               2        2
@@
 o10 : Ideal of S
-i11 : testIdeal( t - 1/p^5, G )
+i11 : testIdeal(t - 1/p^5, G)
 o11 = ideal (y, x)
@@
 i2 : R = ZZ/p[a,b,c,d];
-i3 : I = intersect(ideal(a,b),ideal(a,c),ideal(c,d),ideal(c+d,a^3+b*d^2));
+i3 : I = intersect(ideal(a, b),ideal(a, c),ideal(c, d),ideal(c + d, a^3 + b*d^2));
 o3 : Ideal of R
-i4 : f = inducedMap( R^1/I, R^1/frobenius(I) );
+i4 : f = inducedMap(R^1/I, R^1/frobenius(I));
 o4 : Matrix
-i5 : E2 = Ext^2( f, R^1 )
+i5 : E2 = Ext^2(f, R^1)
 o5 = {-8}  | a4+abc2+abcd a2b            |
@@
 o9 : Matrix R  <--- R
-i10 : frobeniusRoot( 1, U )
+i10 : frobeniusRoot(1, U)
 o10 = {-2} | 1 0 0 |
@@
 \begin{MyVerbatim}
-i11 : V = ascendModule( 1, A, U )
+i11 : V = ascendModule(1, A, U)
 o11 = | 0   a  bc  |
@@
 \begin{MyVerbatim}
-i1 : R = ZZ/7[x,y,z]/ideal( x^3 + y^3 + z^3 );
+i1 : R = ZZ/7[x,y,z]/(x^3 + y^3 + z^3);
 i2 : isFInjective R
 o2 = true
-i3 : R = ZZ/5[x,y,z]/ideal( x^3 + y^3 + z^3 );
+i3 : R = ZZ/5[x,y,z]/(x^3 + y^3 + z^3);
 i4 : isFInjective R
@@
 \begin{MyVerbatim}
-i1 : R = ZZ/7[x,y,z]/ideal( (x-1)^5 + (y+1)^5 + z^5 );
+i1 : R = ZZ/7[x,y,z]/((x - 1)^5 + (y + 1)^5 + z^5);
 i2 : isFInjective R -- R is not globally F-injective...
 o2 = false
-i3 : isFInjective( R, IsLocal => true ) -- but is F-injective at the origin
+i3 : isFInjective(R, IsLocal => true) -- but is F-injective at the origin
 o3 = true
@@
 \begin{MyVerbatim}
-i1 : R = ZZ/5[x,y,z]/ideal( x^2 + y*z );
+i1 : R = ZZ/5[x,y,z]/(x^2 + y*z);
 i2 : isFRegular R
 o2 = true
-i3 : R = ZZ/7[x,y,z]/ideal( x^3 + y^3 + z^3 );
+i3 : R = ZZ/7[x,y,z]/(x^3 + y^3 + z^3);
 i4 : isFRegular R
@@
 i2 : f = y^2 - x^3;
-i3 : isFRegular( 1/2, f )
+i3 : isFRegular(1/2, f)
 o3 = true
-i4 : isFRegular( 5/6, f )
+i4 : isFRegular(5/6, f)
 o4 = false
-i5 : isFRegular( 4/5, f )
+i5 : isFRegular(4/5, f)
 o5 = false
-i6 : isFRegular( 4/5 - 1/100000, f )
+i6 : isFRegular(4/5 - 1/100000, f)
 o6 = true
@@
 \begin{MyVerbatim}
-i1 : R = ZZ/7[x,y,z]/ideal( (x-1)^3 + (y+1)^3 + z^3 );
+i1 : R = ZZ/7[x,y,z]/((x - 1)^3 + (y + 1)^3 + z^3);
 i2 : isFRegular R -- R is not globally F-regular...
 o2 = false
-i3 : isFRegular( R, IsLocal => true ) -- but is F-regular at the origin
+i3 : isFRegular(R, IsLocal => true) -- but is F-regular at the origin
 o3 = true
 i4 : R = ZZ/13[x,y];
-i5 : f = (y-2)^2 - (x-3)^3;
-i6 : isFRegular( 5/6, f ) -- (R,f^(5/6)) is not F-regular...
+i5 : f = (y - 2)^2 - (x - 3)^3;
+i6 : isFRegular(5/6, f) -- (R,f^(5/6)) is not F-regular...
 o6 = false
-i7 : isFRegular( 5/6, f, IsLocal => true ) -- but is F-regular at the origin
+i7 : isFRegular(5/6, f, IsLocal => true) -- but is F-regular at the origin
 o7 = true
@@
 \begin{MyVerbatim}
-i1 : R = ZZ/5[x,y,z]/ideal( x^2 + y*z );
+i1 : R = ZZ/5[x,y,z]/(x^2 + y*z);
 i2 : isFPure R
 o2 = true
-i3 : R = ZZ/7[x,y,z]/ideal( x^3 + y^3 + z^3 );
+i3 : R = ZZ/7[x,y,z]/(x^3 + y^3 + z^3);
 i4 : isFPure R
@@
 i5 : S = ZZ/2[x,y,z];
-i5 : isFPure ideal( y^2 - x^3 )
+i5 : isFPure ideal(y^2 - x^3)
 o5 = false
-i6 : isFPure ideal( z^2 - x*y*z + x*y^2 + x^2*y )
+i6 : isFPure ideal(z^2 - x*y*z + x*y^2 + x^2*y)
 o6 = true
@@
 i3 : n = 3;
-i4 : M = matrix{ { a^2 + t^m, b, d }, { c, a^2, b^n-d } };
-i5 : I = minors( 2, M );
+i4 : M = matrix{{ a^2 + t^m, b, d }, { c, a^2, b^n - d }};
+i5 : I = minors(2, M);
 i6 : R = S/I;
@@
 
-In this section, we explain how to compute parameter test modules, parameter test ideals, test ideals, and HSLG-modules\footnote{HSLG-modules can be used to give a scheme structure to the $F$-injective or $F$-pure locus.}.
+In this section, we explain how to compute parameter test modules, parameter test ideals, test ideals, and HSLG modules\footnote{HSLG modules can be used to give a scheme structure to the $F$-injective or $F$-pure locus.}.
 
@@
 \begin{MyVerbatim}
-i1 : R = ZZ/5[x,y,z]/ideal( x^4 + y^4 + z^4 );
+i1 : R = ZZ/5[x,y,z]/(x^4 + y^4 + z^4);
 i2 : N = testModule R;
@@
 \begin{MyVerbatim}
-i1 : R = ZZ/5[x,y,z]/ideal( y*z, x*z, x*y );
+i1 : R = ZZ/5[x,y,z]/(y*z, x*z, x*y);
 i2 : N = testModule R;
@@
 i1 : R = ZZ/2[a..e];
-i2 : E = matrix { {a,b,b,e}, {d,d,c,a} };
+i2 : E = matrix {{a, b, b, e}, {d, d, c, a}};
              2       4
 o2 : Matrix R  <--- R
-i3 : I = minors( 2, E );
+i3 : I = minors(2, E);
 o3 : Ideal of R
@@
 o5 : Ideal of S
-i6 : J = substitute( J, R );
+i6 : J = substitute(J, R);
 o6 : Ideal of R
-i7 : mingens( J+I )
+i7 : mingens(J + I)
 o7 = | c+d b a de |
@@
 i2 : S = ZZ/7[a,b,c,d];
-i3 : f = map( T, S, { x^3, x^2*y, x*y^2, y^3 } );
+i3 : f = map(T, S, {x^3, x^2*y, x*y^2, y^3});
 i4 : I = ker f;
@@
 \begin{MyVerbatim}
-i7 : toString QGorensteinGenerator( 1, R )
+i7 : toString QGorensteinGenerator(1, R)
 o7 = a^2*b^6*c^12+a^3*b^4*c^13+a^3*b^5*c^11*d+a^4*b^3*c^12*d+a^5*b*c^13*d+b^
@@
 i2 : S = ZZ/3[a,b,c,d];
-i3 : f = map( T, S, { x^3, x^2*y, x*y^2, y^3 } );
+i3 : f = map(T, S, {x^3, x^2*y, x*y^2, y^3});
 i4 : I = ker f;
@@
 \begin{enumerate}[(1)]
-   \item The HSLG module;
+   \item The HSLGmodule;
    \item The canonical module, embedded (non-uniquely) as an ideal;
@@
    \autoref{subsec.DualToFrobeniusOnQuotientRings});
-   \item The value of $e > 0$ at which the descending images in \eqref{eq: descending images} stabilize.  This is sometimes also called the HSLG-number of the canonical module as a Cartier module.
+   \item The value of $e > 0$ at which the descending images in \eqref{eq: descending images} stabilize.  This is sometimes also called the HSLG number of the canonical module as a Cartier module.
 \end{enumerate}
@@
 \begin{MyVerbatim}
-i1 : R = ZZ/3[x,y,z]/ideal( x^3 + y^4 + z^5 );
+i1 : R = ZZ/3[x,y,z]/(x^3 + y^4 + z^5);
 i2 : L = HSLGModule R;
@@
 \end{definition}
-This invariant was introduced in \cite{AlvarezBlickleLyubeznik2005}.  It is also essentially the same data as the HSLG-number of the pair $(R, f^1)$ as computed in (4) above (it is that number $+1$).
+This invariant was introduced in \cite{AlvarezBlickleLyubeznik2005}.  It is also essentially the same data as the HSLG number of the pair $(R, f^1)$ as computed in (4) above (it is that number $+1$).
 One interesting particular
@@
 i1 : R = ZZ/2[x,y,z];
-i2 : f = x^3+y^2*z+y*z^2;
-i3 : frobeniusPower( 1/2, ideal f )
+i2 : f = x^3 + y^2*z + y*z^2;
+i3 : frobeniusPower(1/2, ideal f)
 o3 = ideal (x, y, z)
@@
 i4 : u=f^3;
-i5 : frobeniusPower( 1/4, ideal u )
+i5 : frobeniusPower(1/4, ideal u)
 o6 = ideal (x, y, z)
@@
 i1 : R = ZZ/11[x,y,z];
-i2 : f = y^2*z^3-x^5-2*z^5;
-i3 : frobeniusPower( 1/11, ideal f^10 )
+i2 : f = y^2*z^3 - x^5 - 2*z^5;
+i3 : frobeniusPower(1/11, ideal f^10)
              2        3
@@
 o3 : Ideal of R
-i5 : frobeniusPower( 1/121, ideal f^120 )
+i5 : frobeniusPower(1/121, ideal f^120)
              2        3
@@
 i1 : R = ZZ/2[a..f];
-i2 : E = matrix { {a,b,b,e}, {d,d,c,a} };
+i2 : E = matrix {{a, b, b, e}, {d, d, c, a}};
              2       4
 o2 : Matrix R  <--- R
-i3 : I = minors( 2, E );
+i3 : I = minors(2, E);
 o3 : Ideal of R
@@
 o6 : Ideal of S
-i7 : omega = substitute( omega, R ) + I;
+i7 : omega = substitute(omega, R) + I;
 o7 : Ideal of R
-i8 : u = intersect( (frobenius I ):I, ( frobenius omega ):omega );
+i8 : u = intersect((frobenius I):I, (frobenius omega) : omega);
 o8 : Ideal of R
-i9 : u = compress( (gens u) % gens( frobenius I) )
+i9 : u = compress((gens u) % gens(frobenius I))
 o9 = | a3bc+a3bd+a2cde+abcde+abd2e+b2d2e+cd2e2+d3e2 |
@@
         3       3       2                         2     2 2       2 2    3 2
-ideal(a b*c + a b*d + a c*d*e + a*b*c*d*e + a*b*d e + b d e + c*d e  + d e )
+ideal (a b*c + a b*d + a c*d*e + a*b*c*d*e + a*b*d e + b d e + c*d e  + d e )
                2
@@
 \begin{MyVerbatim}
-i13 : print \ unique apply( L, J -> J : omega );
+i13 : print \ unique apply(L, J -> J : omega);
         3       3       2                         2     2 2       2 2    3 2
-ideal(a b*c + a b*d + a c*d*e + a*b*c*d*e + a*b*d e + b d e + c*d e  + d e )
+ideal (a b*c + a b*d + a c*d*e + a*b*c*d*e + a*b*d e + b d e + c*d e  + d e )
                2

### 2019-04-24 Fsing/TestIdealsPaper/TestIdeals.tex
Renamed HSLGModule to FPureSubmodule.

--- 2019-04-18 Fsing/TestIdealsPaper/TestIdeals.tex
@@
 stabilize for $e \gg 0$.
-The function \texttt{HSLGModule} computes the stable submodule in this chain, called the \emph{HSLG module}, and returns a list containing the following items:
+The function \texttt{FPureModule} computes the stable submodule in this chain, called the \emph{HSLG module}, and returns a list containing the following items:
 \begin{enumerate}[(1)]
@@
 i1 : R = ZZ/3[x,y,z]/ideal( x^3 + y^4 + z^5 );
-i2 : L = HSLGModule R;
+i2 : L = FPureModule R;
 i3 : L#0
@@
 o6 : Ideal of R
-i7 : ((HSLGModule(1, f))#3) + 1
+i7 : ((FPureModule(1, f))#3) + 1
 o7 : 2

### 2019-04-24 Fsing/TestIdealsPaper/TestIdeals_BACKUP_5127.tex
Renamed HSLGModule to FPureSubmodule.

\documentclass[11pt]{amsart}
\usepackage{calc,amssymb,amsthm,amsmath,fullpage    }
%\usepackage{mathtools}
\RequirePackage[dvipsnames,usenames]{xcolor}
\usepackage{hyperref}
\hypersetup{
bookmarks,
bookmarksdepth=3,
bookmarksopen,
bookmarksnumbered,
pdfstartview=FitH,
colorlinks,backref,hyperindex,
linkcolor=Sepia,
anchorcolor=BurntOrange,
citecolor=MidnightBlue,
citecolor=OliveGreen,
filecolor=BlueViolet,
menucolor=Yellow,
urlcolor=OliveGreen
}
\usepackage{alltt}
\usepackage{multicol}
%\usepackage{etex}
\usepackage{xspace}
\usepackage{rotating}
\interfootnotelinepenalty=100000

\usepackage{mabliautoref}
\usepackage{colonequals}
\frenchspacing
\input{kmacros3.sty}
\usepackage{stmaryrd}

\usepackage{verbatim}
\usepackage{enumerate}

\DeclareMathOperator{\HH}{H}
%\DeclareMathOperator{\Image}{image}

\begin{document}
\title{{TestIdeals} package for \emph{Macaulay2}}
\author{Daniel Hern\'andez}
\author{Mordechai Katzman}
\author{Marcus Robinson}
\author{Karl Schwede}
\author{Daniel Smolkin}
\author{Pedro Teixeira}
\author{Emily Witt}
\date{\today}
\address{Department of Mathematics, University of Utah, 155 S 1400 E Room 233, Salt Lake City, UT, 84112}
\email{schwede@math.utah.edu}

\begin{abstract}
  This note describes a \emph{Macaulay2} package for computations in commutative rings prime related to $p^{-e}$-linear and $p^{e}$-linear  maps,
  singularities defined in terms of these maps,  various test ideals and modules, and ideals compatible with a given $p^{-e}$-linear map.
\end{abstract}

\subjclass[2010]{13A35}

\keywords{Macaulay2}

%\thanks{The first named author was supported in part by the NSF FRG Grant DMS \#1265261, NSF CAREER Grant DMS \#1252860 and a Sloan Fellowship.}
%\thanks{The second named author was supported in part by the NSF CAREER Grant DMS \#1252860.}
\maketitle

\section{Introduction}

This paper constructive methods for computing various objects related to commutative rings of prime characteristic $p$.
Such a ring $R$ comes equipped with a built-in endomorphism, namely the Frobenius endomorphism $f:R \rightarrow R$ which is the basis for many constructions and definitions
which affords a handle on many problems which is not otherwise available. Two notable examples of the use of the Frobenius endomorphism are the theory of tight closure
(see \cite{HochsterHunekeTC1} for an introduction)
and the resulting theory of test ideals
(cf. the survey \cite{SchwedeTuckerTestIdealSurvey}).

Work on the \emph{TestIdeals} package started as a library of methods to compute the Frobenius roots, and $\star$-closures, and to implement the algorithm for computing parameter-test-ideals
developed in \cite{KatzmanParameterTestIdealOfCMRings} and \cite{KatzmanFrobeniusMapsOnInjectiveHulls} used to produce the examples in that paper.
Later, the algorithm in  \cite{KatzmanSchwedeAlgorithm} for computing prime ideals compatible with a given $p^{-e}$-linear map was implemented and
used to produce the examples in that paper. The work to turn these libraries into a comprehensive package for computations related to test-ideals
started in earnest on the Summer of 2012 in the Macaulay2 workshop held at Wake Forest. Further work on this package was undertaken in the Macaulay2 workshops in
Berkeley (2014 and 2017), and Salt Lake City (2016).
{\hfill\large\color{red} [Expand: how were the test module methods start life?]}\\

\subsection*{Acknowledgements}

We thank ??? for useful conversations and comments on the development of this package.

\section{Frobenius powers and Frobenius roots}\label{Section: Frobenius powers and Frobenius roots}

%%% Throughout  this paper $R$ will denote a polynomial ring over a field $\mathbb{K}$ of prime characteristic $p$.

Let $S$ denote any commutative ring of prime characteristic $p$.

\begin{definition}
For any ideal $I\subseteq S$ and any integer $e\geq I$, we define the \emph{$e$th Frobenius power of $I$} to be the ideal denoted $I^{[p^e]}$ which is
generated by all $p^e$th powers of elements in $I$.
\end{definition}

It is easy to see that, if $I$ is generated by $g_1, \dots, g_\ell$, $I^{[p^e]}$ is generated by $g_1^{p^e}, \dots, g_\ell^{p^e}$.

\begin{definition}
For any ideal $I\subseteq S$ and any integer $e\geq I$, we define the \emph{$e$th Frobenius root of $I$} to be the ideal denoted $I^{[1/p^{e}]}$ which is
the smallest ideal $J$ such that $I\subseteq J^{[p^e]}$, if such ideal exists.
\end{definition}

$e$th Frobenius roots exist in polynomial rings (cf.~\cite[\S 2]{BlickleMustataSmithDiscretenessAndRationalityOfFThresholds}) and in power series rings
(cf.~\cite[\S 5]{KatzmanParameterTestIdealOfCMRings}).

\begin{verbatim}
i2 :      R=ZZ/5[x,y,z]
i3 :      I=ideal(x^6*y*z+x^2*y^12*z^3+x*y*z^18)
                18    2 12 3    6
o3 = ideal(x*y*z   + x y  z  + x y*z)
o3 : Ideal of R
i4 :      frobeniusPower(1/5,I)
                2   3
o4 = ideal (x, y , z )
\end{verbatim}

We can extend the definition of Frobenius powers as follows
\begin{definition}[cf. \cite{HernandezTeixeiraWittFrobeniusPowers}]
Let  $I\subseteq S$ be an ideal.
\begin{enumerate}
 \item[(a)] If $a$ is a positive integer with base-$p$ expansion  $a=a_0 + a_1 p +  \dots + a_r p^r$, we define
 $I^{[n]}=I^{a_0} \left(I^{a_1}\right)^{[p]} \dots  (I^{a_r})^{[p^r]}$. %\left( I^{a_r}\right)^{[p^r]}$ .
 \item[(b)] If $t$ is a non-negative rational number of the form $t = a/p^e$, we define  $I^{[t]} = (I^{[a]})^{[1/p^e]}.$
 \item[(c)] If $t$ is any non-negative rational number, and $\{a_n/p^{e_n}\}_{n\geq 1}$ is a sequence of rational numbers converging to $t$ from above, we define $I^{[t]}$
 to be the stable value of the increasing chain of ideals $\{I^{[a_n/p^{e_n}]}\}_{n\geq 1}$.

\end{enumerate}
\end{definition}

\begin{verbatim}
i5 :      frobeniusPower(1/2, ideal(y^2-x^3))
o5 = ideal 1
o5 : Ideal of R
i6 :      frobeniusPower(5/6, ideal(y^2-x^3))
o6 = ideal (y, x)
o6 : Ideal of R
\end{verbatim}

\section{$p^{-e}$- and $p^{e}$-linear maps}\label{Section: p-linear maps}

\begin{definition}%{\hfill\large\color{red} [Add references]}\\
Let  $M$ be an $S$-module and $e$ a non-negative integer.
\begin{enumerate}
 \item[(a)] A $p^{-e}$-linear map $\phi:M \rightarrow M$ is an additive map such that
 $\phi(s^{p^e} m)= s\phi(m)$ for all $s\in S$ and $m\in M$.
 \item[(b)] A $p^{e}$-linear map $\psi:M \rightarrow M$ is an additive map such that
 $\phi(s m)= s^{p^e}\phi(m)$ for all $s\in S$ and $m\in M$.
\end{enumerate}
\end{definition}

The following two examples describe two prototypical
$p^{-e}$- and $p^{e}$-linear maps.
\begin{example}
For any $S$-module $M$, we can construct a new $S$-module $M^{1/p^e}$ with elements $\{  m^{1/p^e} \,|\,m\in M\}$ by defining
$m_1^{1/p^e} +  m_2^{1/p^e} =  (m_1 +  m_2)^{1/p^e}$ for all $m_1, m_2 \in M$ and
$s  m^{1/p^e}=  (s^{p^e} m)^{1/p^e}$ for all $m\in M$ and $s\in S$.

Consider any $\phi\in \Hom_S(M^{1/p^e}, M)$: if we identify $M^{1/p^e}$ with $M$ we can interpret $\phi$ as a $p^{-e}$-linear map.
\end{example}

\begin{example}
The $e$th Frobenius map $f:S \rightarrow S$  raising elements to their $p^e$th power is clearly $p^{e}$-linear.
Furthermore, for any ideal $I\subseteq S$ and $k\geq 0$, $f$ induces a $p^{e}$-linear map $\HH_I^k (S) \rightarrow \HH_I^k (S)$.
\end{example}

Let $R$ be a polynomial ring with irrelevant ideal $\mathfrak{m}$ and let $g\in R\setminus \{0\}$.
Let $E=E_{R_{\mathfrak{m}}}(R_{\mathfrak{m}}/\mathfrak{m})$ denote the injective hull of $R_{\mathfrak{m}}/\mathfrak{m}$.

The Frobenius map on $R$ induces a Frobenius map $S$ and on
$\HH^{\dim R-1}_{\mathfrak{m}} (S)=E_S(S/\mathfrak{m}S)=\Ann_E g$ and the kernel of this map is given by
$\Ann_E (g^{p-1}R)^{[1/p]}$ (cf.~\cite[\S 5]{KatzmanParameterTestIdealOfCMRings}).

\begin{verbatim}
i2 :      R=ZZ/5[x,y,z]
i3 :      g=x^3+y^3+z^3
i4 :      u=g^(5-1)
i5 :      frobeniusPower(1/5,ideal(u))
o5 = ideal (z, y, x)
o5 : Ideal of R

i6 :      R=ZZ/7[x,y,z]
i7 :      g=x^3+y^3+z^3
i8 :      u=g^(7-1)
i9 :      frobeniusPower(1/7,ideal(u))
o9 = ideal 1
\end{verbatim}

Thus we see that the induced $p^{e}$-linear map on $\HH_{(x,y,z)}^{2} \left( \mathbb{K}[x,y,z]/(x^3+y^3+z^3) \right)$ is injective
when the characteristic of $\mathbb{K}$ is $7$ and non-injective when the characteristic is $5$.

\subsection{Implementation and complexity}

The computation of Frobenius roots $(-)^{[1/p^e]}$ is the computational workhorse behind many of the methods in \emph{TestIdeals}
hence it is important to understand how it is computed and its computational complexity.

Let $R=\mathbb{K}[x_1, \dots, x_n]$ and fix $B$ to be $\mathbb{K}$-basis for $\mathbb{K}^{1/p^e}$;
it is not hard to see that $R^{1/p^e}$ is a free $R$-module with free basis
$$\left\{ b x_1^{\alpha_1/p^e} \dots x_n^{\alpha_n/p^e} \,|\, 0\leq \alpha_1, \dots, \alpha_n < p^e \right\}.$$

\begin{proposition}(cf. \cite[\S 5]{KatzmanParameterTestIdealOfCMRings})
\begin{enumerate}
\item[(a)] If the ideal $I\subseteq R$ is generated by $g_1, \dots, g_k\in R$, then $I^{[1/p^e]}=\sum_{i=1}^k (g_i R)^{[1/p^e]}$.
\item[(b)] If
\begin{equation}\label{eqn1}
g=\bigoplus_{b\in B, \atop{0\leq \alpha_1, \dots, \alpha_n < p^e}} r_{b, \alpha_1, \dots, \alpha_n} b x_1^{\alpha_1/p^e} \dots x_n^{\alpha_n/p^e},
\end{equation}
then $(gR)^{[1/p^e]}$ is generated by $\{ r_{b, \alpha_1, \dots, \alpha_n} \,|\, b\in B, 0\leq \alpha_1, \dots, \alpha_n < p^e \}$.
\end{enumerate}
\end{proposition}

Thus the computation of Frobenius roots of ideals reduces to the case of principal ideals, and the complexity grows linearly with the number of generators of the ideal.
Furthermore the calculation of  $(gR)^{[1/p^e]}$ reduces to finding the summands in (\ref{eqn1}), which essentially amounts
taking each term in $g$, computing the $p^e$th root of the coefficient in $\mathbb{K}$, and dividing the monomial exponent vector by $p^e$ with remainder.
Thus the complexity of  computing $(gR)^{[1/p^e]}$ is proportional to the number of terms in $g$ and is independent of its degree.
\emph{The calculation of Frobenius roots does not involve the calculation of Gr\"obner bases.}

\section{$F$-singularities}

This package includes a method for checking if a ring of finite type over a prime field is $F$-injective or not.
\begin{definition}
A local ring $(R, \mathfrak{m})$ is called \emph{F-injective} if the map $H^{i}_{\mathfrak{m}}(R) \rightarrow H^{i}_{\mathfrak{m}}(R^{1/p})$ is injective for all $i >0$. An arbitrary ring is called $F$-injective if each of the localizations at a prime ideal are $F$-injective.
\end{definition}

\begin{verbatim}
i2 : R = ZZ/7[x,y,z]/ideal(x^3 + y^3 + z^3);
i3 : isFinjective(R)
o3 = true
i4 : R = ZZ/5[x,y,z]/ideal(x^3 + y^3 + z^3);
i5 : isFinjective(R)
o5 = false
\end{verbatim}

The algorithm {\tt isFinjective} determines whether the ring  $R = S/I$ is F-injective or not. The algorithm works by checking the injectivity of the frobenius map using the functoriallity of $\Ext$.  The algorithm starts by computing  the map $R \rightarrow F_{*}R$ using {\tt frobPFMap}. This outputs a map represented as a matrix over $R$, using {\tt pushFwdToAmbient} to allows this map to instead be represented over the ambient ring $S$. The next step computes the module $\Ext^{i}( \blank, S)$ using the map from the previous step. Finally the algorithm checks the dimension of the cokernel of  $\Ext^{i}( \blank, S)$. If the dimension does not equal negative one then the Frobenius action is not injective and the algorithm terminates and returns false. Otherwise the algorithm continues on and checks the next degree in the same way.

The {\tt CanonicalStrategy} tag can be used to modify the strategy the algorithm uses to check the Frobenius action on the top local cohomology. By default the algorithm is set to {\tt CanonicalStrategy => Katzman} which then uses the strategy of Katzman  {\hfill\large\color{red} [Add references]}. If the tag is set to anything else {\tt CanonicalStrategy => null} the algorithm checks the top local cohomology using the same brute force strategy used to check the injectivity at lower degrees. The Katzman strategy is typically much faster.

There are a number of options to improve the performance of the algorithm if the ring of interest is nice enough. If the ring is Cohen-Macaulay then setting {\tt AssumeCM => true} lets the algorithm check the Frobenius action only on top cohomology (which is typically much faster).  The default value is {\tt false}. Of course, telling the algorithm to assume the ring is Cohen-Macaulay when it is not can lead to an incorrect answer if the non-injective Frobenius occurs in a lower degree. For an example of this see the documentation.  If the ring is reduced then setting {\tt AssumedReduced => true} avoids computing the bottom local cohomology, if the ring is normal then setting {\tt AssumeNormal => true} avoids computing the bottom two local cohomologies. The default setting for both of these tags is {\tt false}.

By default the algorithm checks for $F$-injectivity everywhere however one can choose to check $F$-injectivity only at the origin by setting the option {\tt IsLocal => true}.
\begin{verbatim}
i2 : R = ZZ/5[x,y,z]/ideal( (x-1)^4 + y^4 + z^4 );
i3 : isFinjective(R)
o3 = false
i4 : isFinjective(R, IsLocal=>true)
o4 = true
\end{verbatim}

\begin{definition}
A ring $R$ is called strongly $F$-regular if $\tau(R) = R$.
\end{definition}

The command {\tt isFregular} checks whether a ring or pair is strongly $F$-regular. Below are two examples one $F$-regulare and one not.

\begin{verbatim}
i2 : R = ZZ/5[x,y,z]/ideal(x^2 + y*z);
i3 : isFregular(R)
o3 = true
i4 : R = ZZ/7[x,y,z]/ideal(x^3 + y^3 + z^3);
i5 : isFregular(R)
o5 = false
\end{verbatim}

We can also perform these types computations for pairs.

\begin{verbatim}
i2 : R = ZZ/5[x,y];
i3 : f = y^2-x^3;
i4 : isFregular(1/2, f)
o4 = true
i5 : isFregular(5/6, f)
o5 = false
i6 : isFregular(4/5, f)
o6 = false
i7 : isFregular(4/5-1/100000, f)
o7 = true
\end{verbatim}

The inputs for {\tt isFregular} can be a ring, an integer and a ring element, a rational number and a ring element or a list of rational numbers and a list of ring elements.

If the input ring is $\mathbb{Q}$-Gorenstein then in each of the cases above the output is a boolean indicating if the ring is strongly $F$-regular. If the input ring is not $\mathbb{Q}$-Gorenstein then the algorithm can be used to determine if a ring is strongly $F$-regular but cannot prove a ring is not strongly $F$-regular

In the case that $R$ is $\mathbb{Q}$-Gorenstein, the algorithm works by computing the test ideal of the ring (or the pair) and then uses {\tt isSubset} to check if $(1)$  is contained in the test ideal. In the non-$\mathbb{Q}$-Gorenstein case the algorithm checks for strong $F$-regularity by checking if $(1)$ is contained in better and better approximations of the test ideal. To compute approximations of the test ideal the algorithm uses {\tt frobeniusRoot} to compute the $e$th root of $c(I^{[p^{e}]} : I)$ (in the case we are checking strong F-regularity for a ring, appropriate modifications are made for pairs). If at any step $(1)$ is contained in the approximation then then the algorithm returns {\tt true}. Otherwise the algorithm continues checking for each $e$ until a specified limit is reached. The default limit is 2 and can be changed using {\tt DepthOfSearch => ZZ}.

The default behavior of {\tt isFregular} checks for strong $F$-regularity everywhere. If the option {\tt IsLocal => true}, the algorithm will only check at the origin (this uses a similar computation but checks for the containment of $(1)$ instead of the test ideal plus the maximal ideal at the origin). Below is an example for both a ring and a pair.

\begin{verbatim}
i2 : R = ZZ/7[x,y,z]/ideal((x-1)^3+(y-2)^3+z^3);
i3 : isFregular(R)
o3 = false
i4 : isFregular(R, IsLocal=>true)
o4 = true
i5 : R = ZZ/13[x,y];
i6 : f = (y-2)^2 - (x-3)^3;
i7 : isFregular(5/6, f)
o7 = false
i8 : isFregular(5/6, f, IsLocal=>true)
o8 = true
\end{verbatim}

\section{Test ideals}

In this section, we explain how to compute parameter test modules, parameter test ideals, test ideals and $F$-Pure-modules\footnote{$F$-pure-modules (i.e. HSLG-modules) can be used to give a scheme structure to the $F$-injective or $F$-pure locus.}.

\subsection{Parameter test modules}

Given an $F$-finite reduced ring $R$, the Frobenius map $R \to R^{1/p^e}$ is dual to $T : \omega_{R^{1/p^e}} \to \omega_R$.  As before in \autoref{}, we can represent $\omega_R \subseteq R$ as an ideal, we can write $R = S/I$, and so we can find a $u \in S^{1/p^e}$ representing the map $\omega_{R^{1/p^e}} \to \omega_R$ \cite{}.  See also \autoref{} below.

The parameter test submodule is the smallest submodule $M \subseteq \omega_R$ (and hence ideal of $R$ since $M \subseteq R$) that agrees generically with $\omega_R$ and that satisfies
\[
T (M^{1/p^e}) \subseteq M.
\]
From within Macualay2, we can compute this using the {\tt testModule} command as follows.
\begin{verbatim}
i3 : R = ZZ/5[x,y,z]/ideal(x^4+y^4+z^4);
i4 : N = testModule(R);
i5 : N#0
             2             2        2
o5 = ideal (z , y*z, x*z, y , x*y, x )
o5 : Ideal of R
i6 : N#1
o6 = ideal 1
o6 : Ideal of R
\end{verbatim}
The output of {\tt testModule} is a list with three items.  The first entry is the test module, the second is the canonical module (as an ideal) that it lives inside, and the third is the element $u$ described above (not listed here, since it is rather complicated).  Note since this ring is Gorenstein, the canonical module is simply represented as the unit ideal.

Here is another example where the ring is not Gorenstein.
\begin{verbatim}
i2 : R = ZZ/5[x,y,z]/ideal(y*z, x*z, x*y);
i3 : N = testModule(R);
i4 : N#0
             2   2   2
o4 = ideal (z , y , x )
o4 : Ideal of R
i5 : N#1
o5 = ideal (y - z, x + z)
o5 : Ideal of R
\end{verbatim}

We briefly explain how this is computed.  First we find a \emph{test element}.
\begin{remark}[Computation of test elements]
\label{rem.ComputationOfTestElements}
Roughly, we recall that an element of the Jacobian ideal that is not contained in any minimal prime is a test element \cite{}.  We compute test elements by computing random partial derivatives (and linear combinations thereof) until we find an element that doesn't vanish at all the minimal primes.  This method is much faster than computing the entire Jacobian ideal.  If you know your ring is a domain, you can use the {\tt AssumeDomain} flag to speed this up further.
\end{remark}

After the test element $c$ has been identified, we pullback the ideal $\omega_R$ to an ideal $J = S$.  Then we compute the following ascending sequence of ideals
\begin{equation}
\label{eq.AscendIdealExplanation}
\begin{array}{rll}
J_1 := & = J + (c J)^{[1/p]} & = {\tt J + frobeniusRoot(1, c*J)}\\
J_2 := & = J + (c J)^{[1/p]} + (c^{1+p} J)^{[1/p^2]} & = {\tt J + frobeniusRoot(1, c*J_1)}\\
J_3 := & = J + (c J)^{[1/p]} + (c^{1+p} J)^{[1/p^2]} + (c^{1+p+p^2} J)^{[1/p^3]} & = {\tt J + frobeniusRoot(1, c*J_2)}.\\
\dots
\end{array}
\end{equation}
As soon as this ascending sequence of ideals stabilizes, we are done.
In fact, because this strategy is used in several contexts, you can call it directly for a chosen ideal $J$ and $u$ with the function {\tt ascendIdeal} (this is done for test ideals below).

We can also compute parameter test modules of pairs $\tau(\omega_R, f^{t})$ with $t \in \mathbb{Q}_{\geq 0}$.  This is done by modifying the element $u$ when the denominator of $t$ is not divisible by $p$.  When $t$ has $p$ in the denominator, we rely on the fact (see \cite{}) that
\[
\begin{array}{rcl}
T(\tau(\omega_R, f^a)) & = & \tau(\omega_R, f^{a/p})\\
{\tt frobeniusRoot(1, u*I_1)} & {\tt =} & {\tt I_2}
\end{array}
\]
Where the second line roughly explains how this is accomplished internally, here ${\tt I_1}$ is $\tau(\omega_R, f^a)$ pulled back to $S$ and likewise $I_2$ defines $\tau(\omega_R, f^a)$ modulo the defining ideal of $R$.

\begin{remark}[Optimizations in {\tt ascendIdeal} and other {\tt testModule} computations]
Throughout the computations described above, we very frequently use the following fact:
\[
(f^p \cdot J)^{[1/p]} = f \cdot (J^{[1/p]}).
\]
To access this enhancement, one should try to pass functions like {\tt ascendIdeal} and {\tt frobeniusRoot} the elements and their exponents (see the documentation).  In particular, do not multiply out things like $f^n \cdot J$ if you will be applying {\tt frobeniusRoot}.
\end{remark}

\subsection{Parameter test ideals}

The parameter test ideal is simply the annihilator of $\omega_R/\tau(\omega_R)$.  Or in other words, it is
\[
\tau(\omega_R) : \omega_R.
\]
This can also be described as
\[
\bigcap_{I} (I^* : I)
\]
where $I$ varies over ideals defined by a partial system of parameters and $I^*$ denotes its tight closure.  This latter description is not computable however.

\begin{verbatim}
todo (Moty will insert a good example)
\end{verbatim}

\subsection{Test ideals}

For an $F$-finite reduced ring $R = S/I$ where $S$ is a regular ring, the test ideal of $R$ is the smallest ideal $J$ in $R$, not contained in any minimal prime, such that for all $e > 0$ and all
\[
\phi \in \Hom_R(R^{1/p^e}, R) \text{ we have } \phi(J^{1/p^e}) \subseteq J.
\]
In the case that $R$ is Gorenstein, there is a map $\Phi_e \in \Hom_R(R^{1/p^e}, R)$ which generates the $\Hom$-set as an $R^{1/p^e}$-module.  In fact this $\Phi_e$ is identified with the map $T$ above based on the identification $\omega_R \cong R$, \cite{}.  More generally, if $R$ is $\bQ$-Gorenstein with index not divisible by $p$, then for at least sufficiently divisible $e > 0$, such a generating $\Phi_e$ still exists \cite{}.

If such a $\Phi_e$ exists, it can be identified as the generator of the module $(I^{[p^e]} : I) / I^{[p^e]}$ by Fedder's Lemma, \cite{}.  Hence we can find a corresponding\footnote{This is done via the function {\tt QGorensteinGenerator}. } $u \in I^{[p^e]} : I$.  In this case, if $c \in S$ is the pre-image of a test element of $R$, then setting $I_0 = cR$, it follows that
\[
\tau(R) = {\tt ascendIdeal(e, u, I_0)}.
\]
Recall that {\tt ascendIdeal} is explained above in \autoref{eq.AscendIdealExplanation}.  The $e$ here means all $e$th roots are taken as multiples of $e$.  See \cite{}.

Here is an example (a $\bZ/3\bZ$-quotient where $3 | (7-1)$), where exactly this logic occurs.
\begin{verbatim}
i3 : T = ZZ/7[x,y];
i4 : S = ZZ/7[a,b,c,d];
i5 : f = map(T, S, {x^3, x^2*y, x*y^2, y^3});
i6 : I = ker f;
i7 : R= S/I;
i8 : testIdeal(R)
o8 = ideal 1
o8 : Ideal of R
\end{verbatim}
However, the term $u$ constructed above can be quite involved if $e > 1$ (which happens exactly when $(p -1)K_R$ is not Cartier).  For instance, even in the above example:
\begin{verbatim}
i9 : toString(QGorensteinGenerator(1, R))
o9 = a^2*b^6*c^12+a^3*b^4*c^13+a^3*b^5*c^11*d+a^4*b^3*c^12*d+a^5*b*c^13*d+b^12
      *c^6*d^2+a^3*b^6*c^9*d^2+a^4*b^4*c^10*d^2+a^5*b^2*c^11*d^2+a^6*c^12*d^2+b
      ^13*c^4*d^3+a*b^11*c^5*d^3+a^2*b^9*c^6*d^3+a^4*b^5*c^8*d^3+a^5*b^3*c^9*d^
      3+a^6*b*c^10*d^3+a*b^12*c^3*d^4+a^2*b^10*c^4*d^4+a^3*b^8*c^5*d^4+a^4*b^6*
      c^6*d^4+a^5*b^4*c^7*d^4+a^6*b^2*c^8*d^4+a^7*c^9*d^4+a*b^13*c*d^5+a^2*b^11
      *c^2*d^5+a^3*b^9*c^3*d^5+a^4*b^7*c^4*d^5+a^5*b^5*c^5*d^5+a^6*b^3*c^6*d^5+
      a^7*b*c^7*d^5+a^2*b^12*d^6+a^3*b^10*c*d^6+a^4*b^8*c^2*d^6+a^5*b^6*c^3*d^6
      +a^6*b^4*c^4*d^6+a^7*b^2*c^5*d^6+a^8*c^6*d^6+a^4*b^9*d^7+a^5*b^7*c*d^7+a^
      6*b^5*c^2*d^7+a^7*b^3*c^3*d^7+a^8*b*c^4*d^7+a^6*b^6*d^8+a^7*b^4*c*d^8+a^8
      *b^2*c^2*d^8+a^9*c^3*d^8+a^8*b^3*d^9+a^9*b*c*d^9+a^10*d^10
\end{verbatim}
Therefore, we use a different strategy if either $(p-1)K_R$ is not Cartier or more generally if $R$ is $\bQ$-Gorenstein of index divisible by $p$ which appears to typically be faster.  We rely on the following observation, see \cite{}.
\[
\tau(\omega_R, K_R) \cong \tau(R).
\]
In fact, by embedding $\omega_R \subseteq R$, we can compute $g$ so that $\tau(\omega_R, K_R) = g \tau(R)$.  We can therefore find $\tau(R)$ if we can find $\tau(\omega_R, K_R)$.
Next, if $K_R$ is $\bQ$-Cartier with $nK_R = \Div_R(f)$ for some $f \in R$ and $n > 0$, then
\[
\tau(\omega_R, K_R) =\tau(\omega_R, f^{1/n}).
\]
Thus we directly compute $\tau(\omega_R, f^{1/n})$ via the command {\tt testModule(1/n, f)}.  Consider the following example, a $\mu_3$-quotient.
\begin{verbatim}
i2 : T = ZZ/3[x,y];
i3 : S = ZZ/3[a,b,c,d];
i4 : f = map(T, S, {x^3, x^2*y, x*y^2, y^3});
i5 : I = ker f;
i6 : R = S/I;
i7 : testIdeal(R)
o7 = ideal 1
o7 : Ideal of R
\end{verbatim}
Which uses the logic described above.

\begin{remark}[Non graded caveats]
It frequently can happen that $(I^{[p^e]} : I)/I^{[p^e]}$ is principal but Macaulay2 cannot identify the principal generator (since Macaulay2 cannot always find minimal generators of non-graded ideals or modules).  The same thing can happen when computing the $u$ corresponding to the map $T : \omega_{R^{1/p}} \to \omega_R$, as described in \autoref{} above.  In such situations, instead of a single $u$, we Macaulay2 will produce $u_1, \dots, u_n$ (all multiples of $u$, and $u$ is a linear combination of the $u_i$).  Instead of computing things like
\[
(u \cdot J)^{[1/p]},
\]
we will instead compute
\[
(u_1 \cdot J)^{[1/p]} + \dots + (u_n \cdot J)^{[1/p]}
\]
which will produce the same answer.
\end{remark}

We can similarly use the {\tt testIdeal} command to compute test ideals of pairs $\tau(R, f^t)$, and even more general mixed test ideals $\tau(R, f_1^{t_1} \cdots f_n^{t_n})$.

\subsection{FPureSubmodule, computing $F$-pure submodules of rank-1 Cartier modules}

Again consider the maps $T^e : \omega_{R^{1/p^e}} \to \omega_R$ we have considered throughout this section.  It is a theorem of Hartshorne-Speiser, Lyubeznik, and Gabber \cite{} that the descending images
\[
\omega_R \supseteq T(\omega_{R^{1/p}}) \supseteq \dots \supseteq T^e(\omega_{R^{1/p^e}}) \supseteq T_{e+1}(\omega_{R^{1/p^{e+1}}}) \supseteq \dots
\]
stabilize for $e \gg 0$.  The function {\tt FPureModule} computes this.
\begin{verbatim}
i4 : R = ZZ/3[x,y,z]/ideal(x^3+y^4+z^5);
i5 : L = FPureModule(R);
i6 : L#0
                          2        2   3
o6 = ideal (0, y*z, x*z, y , x*y, x , z )
o6 : Ideal of R
i7 : L#1
o7 = ideal 1
o7 : Ideal of R
i8 : L#3
o8 = 1
\end{verbatim}
The function returns a list.  The first entry is the submodule.  The second is the canonical module.  The third entry is the $u$ representing the map on the canonical module (as in \autoref{} above) and the final entry is at what value of $e > 0$ the image stabilizes.

In a Gorenstein ring, this submodule coincides philosophically with the maximal non-LC ideal of Fujino-Schwede-Takagi.

More generally for any ideal $J$ with a map $\phi : J^{1/p^e} \to J$, we have that the images
\[
J \supseteq \phi(J^{1/p^e}) \supseteq \phi^2(J^{1/p^{2e}}) \supseteq \dots
\]
stabilize as well (in fact, the analogous result even holds for modules).

\section{Ideals compatible with given $p^{-e}$-linear map}

Throughout this section let $R$ denote a polynomial $\mathbb{K}[x_1, \dots, x_n]$. In this section we address the following question:
given a $p^{-e}$ linear map $\phi: R \rightarrow R$, what are all ideals $I\subseteq R$ such that $\phi(I)=I$?
We call these ideals $\phi$-compatible.

Recall that in section \ref{Section: p-linear maps} we identified $p^{-e}$ linear maps
with elements of $\Hom_R( R^{1/p^e}, R)$ and it turns out that this is a principal $R^{1/p^e}$-module generated
the \emph{trace map} $\pi\in \Hom_R(^{1/p^e}, R)$, constructed as follows (cf. \cite[Lemma 1.6]{FedderFPureRat} and \cite[Example 1.3.1]{BrionKumarFrobeniusSplitting}).
Recall that if $B$ is a $\mathbb{K}$-basis for $\mathbb{K}^{1/p^e}$;
$R^{1/p^e}$ is a free $R$-module with basis
$$\left\{ b x_1^{\alpha_1/p^e} \dots x_n^{\alpha_n/p^e} \,|\, 0\leq \alpha_1, \dots, \alpha_n < p^e \right\} ;$$
the trace map $\pi$ is the projection onto the free summand
$R x_1^{(p^e-1)/p^e} \dots x_n^{(p^e-1)/p^e}\cong R$.

We can now write our given $\phi$ as multiplication by some $u^{1/p^e}$ followed by $\pi$ and it is not hard to see that
an ideal $I\subseteq R$ is $\phi$-compatible if and only if $u I \subseteq I^{[p^e]}$.

\begin{theorem}\label{Theorem: finitely many compatible primes}
If $\phi$ is surjective, there are finitely many $\phi$-compatible ideals, consisting of all possible intersections
of $\phi$-compatible prime ideals (cf. \cite{KumarMehtaFiniteness}, \cite{SchwedeFAdjunction},
\cite{SharpGradedAnnihilatorsOfModulesOverTheFrobeniusSkewPolynomialRing}, \cite{EnescuHochsterTheFrobeniusStructureOfLocalCohomology}).

In general, there are finitely many $\phi$-compatible prime ideals not containing $\sqrt{\Image \phi}$ (cf. \cite{KatzmanSchwedeAlgorithm}).

\end{theorem}

The method \emph{compatibleIdeals} produces the finite set of $\phi$-compatible prime ideals in the second statement of Theorem \ref{Theorem: finitely many compatible primes}.

\begin{verbatim}
i2 :      R = ZZ/3[u,v];
i3 :      u = u^2*v^2;
i4 :      compatibleIdeals(u)
o4 = {ideal v, ideal (v, u), ideal u}
o4 : List
\end{verbatim}

The defining condition $u I = I^{[p]}$ for $\phi$-compatible ideals allows us to
think of these in a dual form: write $\mathfrak{m}=(x_1, \dots, x_n)R$,
$E=E_{R\mathfrak{m}}(R_{\mathfrak{m}}/\mathfrak{m})=\HH^n_{\mathfrak{m}} (R)$, and let $T: E \rightarrow E$ be the $p^e$-linear map
induced from the Frobenius map on $R$.
If $\psi=u T$, then $\psi \Ann_E I \subseteq \Ann_E I$ if and only if $u I = I^{[p]}$!
Thus finding all $R$-submodules of $E$ compatible with $\psi=u T$ also amounts to finding all
$\phi=\pi \circ u^{1/p^e}$-compatible ideals.

Let $\mathbb{K}=\mathbb{Z}/2\mathbb{Z}$, $R=\mathbb{K}[x_1, x_2, x_3, x_4, x_5]$, $\mathfrak{m}=(x_1, \dots, x_5)R$, and let $I$ be the ideal of
$2\times 2$ minors of
$$
\left[
\begin{array}{c c c c}
 x_1 & x_2 & x_2 & x_5\\
 x_4 & x_4 & x_3 & x_1
\end{array}
\right]
$$
In (cf.~\cite[\S 9]{KatzmanParameterTestIdealOfCMRings}) it is shown that
there is a surjection $\Ann_E I \rightarrow \HH^2_{\mathfrak{m}} (R/I)$
which is compatible with with the induced $p^1$-linear map on $\HH^2_{\mathfrak{m}} (R/I)$
and the $p^1$-linear map $u T$ on $\Ann_E I$ with
$$u=x_1^3x_2x_3 + x_1^3x_2x_4+x_1^2x_3x_4x_5+ x_1x_2x_3x_4x_5+ x_1x_2x_4^2x_5+ x_2^2x_4^2x_5+x_3x_4^2x_5^2+ x_4^3x_5^2 .$$

\begin{verbatim}
i2 :      R=ZZ/2[x_1..x_5];
i3 :      I=minors(2, matrix {{x_1,x_2,x_2,x_5},{x_4,x_4,x_3,x_1}} )
                                                   2
o3 = ideal (x x  + x x , x x  + x x , x x  + x x , x  + x x , x x  + x x , x x
             1 4    2 4   1 3    2 4   2 3    2 4   1    4 5   1 2    4 5   1 2
     --------------------------------------------------------------------------
     + x x )
        3 5
o3 : Ideal of R
i4 :      u=x_1^3*x_2*x_3 + x_1^3*x_2*x_4+x_1^2*x_3*x_4*x_5+ x_1*x_2*x_3*x_4*x_5+
          x_1*x_2*x_4^2*x_5+ x_2^2*x_4^2*x_5+x_3*x_4^2*x_5^2+ x_4^3*x_5^2;
i5 :      compatibleIdeals(u)
             3        3        2                           2      2 2
o5 = {ideal(x x x  + x x x  + x x x x  + x x x x x  + x x x x  + x x x  +
             1 2 3    1 2 4    1 3 4 5    1 2 3 4 5    1 2 4 5    2 4 5
     --------------------------------------------------------------------------
        2 2    3 2                    2
     x x x  + x x ), ideal (x  + x , x  + x x ), ideal (x , x ), ideal (x , x ,
      3 4 5    4 5           1    2   1    4 5           4   1           4   1
     --------------------------------------------------------------------------

     x ), ideal (x , x , x , x ), ideal (x , x , x , x , x ), ideal (x , x ,
      5           5   4   1   3           5   4   3   2   1           5   4
     --------------------------------------------------------------------------

     x , x ), ideal (x , x , x ), ideal (x , x , x , x ), ideal (x , x , x ),
      2   1           4   1   3           4   3   2   1           4   2   1
     --------------------------------------------------------------------------
                               2
     ideal (x  + x , x  + x , x  + x x ), ideal (x  + x , x , x , x ), ideal
             3    4   1    2   2    4 5           3    4   2   1   5
     --------------------------------------------------------------------------
     (x , x , x )}
       2   1   5

o5 : List
\end{verbatim}

\section{Future plans}

\bibliographystyle{skalpha}
\bibliography{MainBib}

\end{document}

### 2019-04-24 Fsing/TestIdealsPaper/TestIdeals_REMOTE_5127.tex
Renamed HSLGModule to FPureSubmodule.

--- 2019-04-24 Fsing/TestIdealsPaper/TestIdeals_BACKUP_5127.tex
@@
  \item[(c)] If $t$ is any non-negative rational number, and $\{a_n/p^{e_n}\}_{n\geq 1}$ is a sequence of rational numbers converging to $t$ from above, we define $I^{[t]}$
- to be the stable value of the increasing chain of ideals $\{I^{[a_n/p^{e_n}]}\}_{n\geq 1}$.
+ to be the stable value of increasing chain of ideals $\{I^{[a_n/p^{e_n}]}\}_{n\geq 1}$.
 
@@
 \begin{example}
-For any $S$-module $M$, we can construct a new $S$-module $M^{1/p^e}$ with elements $\{  m^{1/p^e} \,|\,m\in M\}$ by defining
-$m_1^{1/p^e} +  m_2^{1/p^e} =  (m_1 +  m_2)^{1/p^e}$ for all $m_1, m_2 \in M$ and
-$s  m^{1/p^e}=  (s^{p^e} m)^{1/p^e}$ for all $m\in M$ and $s\in S$.
+For any $S$-module $M$, we can construct a new $S$-module $F_*^e M$ with elements $\{ F_*^e m \,|\,m\in M\}$ by defining
+$F_*^e m_1 + F_*^e m_2 = F_*^e (m_1 +  m_2)$ for all $m_1, m_2 \in M$ and
+$s F_*^e m= F_*^e s^{p^e}$ for all $m\in M$ and $s\in S$.
 
-Consider any $\phi\in \Hom_S(M^{1/p^e}, M)$: if we identify $M^{1/p^e}$ with $M$ we can interpret $\phi$ as a $p^{-e}$-linear map.
+Consider any $\phi\in \Hom_S(F_*^e M, M)$: if we identify $F_*^e M$ with $M$ we can interpret $\phi$ as a $p^{-e}$-linear map.
 \end{example}
@@
 when the characteristic of $\mathbb{K}$ is $7$ and non-injective when the characteristic is $5$.
-
-\subsection{Implementation and complexity}
-
-The computation of Frobenius roots $(-)^{[1/p^e]}$ is the computational workhorse behind many of the methods in \emph{TestIdeals}
-hence it is important to understand how it is computed and its computational complexity.
-
-Let $R=\mathbb{K}[x_1, \dots, x_n]$ and fix $B$ to be $\mathbb{K}$-basis for $\mathbb{K}^{1/p^e}$;
-it is not hard to see that $R^{1/p^e}$ is a free $R$-module with free basis
-$$\left\{ b x_1^{\alpha_1/p^e} \dots x_n^{\alpha_n/p^e} \,|\, 0\leq \alpha_1, \dots, \alpha_n < p^e \right\}.$$
-
-\begin{proposition}(cf. \cite[\S 5]{KatzmanParameterTestIdealOfCMRings})
-\begin{enumerate}
-\item[(a)] If the ideal $I\subseteq R$ is generated by $g_1, \dots, g_k\in R$, then $I^{[1/p^e]}=\sum_{i=1}^k (g_i R)^{[1/p^e]}$.
-\item[(b)] If
-\begin{equation}\label{eqn1}
-g=\bigoplus_{b\in B, \atop{0\leq \alpha_1, \dots, \alpha_n < p^e}} r_{b, \alpha_1, \dots, \alpha_n} b x_1^{\alpha_1/p^e} \dots x_n^{\alpha_n/p^e},
-\end{equation}
-then $(gR)^{[1/p^e]}$ is generated by $\{ r_{b, \alpha_1, \dots, \alpha_n} \,|\, b\in B, 0\leq \alpha_1, \dots, \alpha_n < p^e \}$.
-\end{enumerate}
-\end{proposition}
-
-Thus the computation of Frobenius roots of ideals reduces to the case of principal ideals, and the complexity grows linearly with the number of generators of the ideal.
-Furthermore the calculation of  $(gR)^{[1/p^e]}$ reduces to finding the summands in (\ref{eqn1}), which essentially amounts
-taking each term in $g$, computing the $p^e$th root of the coefficient in $\mathbb{K}$, and dividing the monomial exponent vector by $p^e$ with remainder.
-Thus the complexity of  computing $(gR)^{[1/p^e]}$ is proportional to the number of terms in $g$ and is independent of its degree.
-\emph{The calculation of Frobenius roots does not involve the calculation of Gr\"obner bases.}
 
@@
 
-In this section, we explain how to compute parameter test modules, parameter test ideals, test ideals and $F$-Pure-modules\footnote{$F$-pure-modules (i.e.
-HSLG-modules) can be used to give a scheme structure to the $F$-injective or $F$-pure locus.}.
+In this section, we explain how to compute parameter test modules, parameter test ideals, test ideals and HSLG-modules\footnote{HSLG-modules can be used to give a scheme structure to the $F$-injective or $F$-pure locus.}.
 
@@
 
-\subsection{FPureSubmodule, computing $F$-pure submodules of rank-1 Cartier modules}
+\subsection{HSLG module, computing $F$-pure submodules of rank-1 Cartier modules}
 
@@
 Recall that in section \ref{Section: p-linear maps} we identified $p^{-e}$ linear maps
-with elements of $\Hom_R( R^{1/p^e}, R)$ and it turns out that this is a principal $R^{1/p^e}$-module generated
-the \emph{trace map} $\pi\in \Hom_R(^{1/p^e}, R)$, constructed as follows (cf. \cite[Lemma 1.6]{FedderFPureRat} and \cite[Example 1.3.1]{BrionKumarFrobeniusSplitting}).
-Recall that if $B$ is a $\mathbb{K}$-basis for $\mathbb{K}^{1/p^e}$;
-$R^{1/p^e}$ is a free $R$-module with basis
-$$\left\{ b x_1^{\alpha_1/p^e} \dots x_n^{\alpha_n/p^e} \,|\, 0\leq \alpha_1, \dots, \alpha_n < p^e \right\} ;$$
-the trace map $\pi$ is the projection onto the free summand
-$R x_1^{(p^e-1)/p^e} \dots x_n^{(p^e-1)/p^e}\cong R$.
+with elements of $\Hom_R(F_*^e R, R)$ and it turns out that this is a principal $F_*^e R$-module generated
+the \emph{trace map} $\pi\in \Hom_R(F_*^e R, R)$, constructed as follows (cf. \cite[Lemma 1.6]{FedderFPureRat} and \cite[Example 1.3.1]{BrionKumarFrobeniusSplitting}).
+Let $B$ be a $\mathbb{K}^{p^e}$-basis for $\mathbb{K}$;
+$F_*^e R$ is a free $R$-module with basis
+$$\left\{ F_*^e b x_1^{\alpha_1} \dots x_n^{\alpha_n} \,|\, 0\leq \alpha_1, \dots, \alpha_n < p^e \right\}$$
+and the trace map $\pi$ is the projection onto the free summand
+$R F_*^e  x_1^{p^e-1} \dots x_n^{p^e-1}\cong R$.
 
-We can now write our given $\phi$ as multiplication by some $u^{1/p^e}$ followed by $\pi$ and it is not hard to see that
+We can now write our given $\phi$ as multiplication by some $F_*^e u$ followed by $\pi$ and it is not hard to see that
 an ideal $I\subseteq R$ is $\phi$-compatible if and only if $u I \subseteq I^{[p^e]}$.
@@
 Thus finding all $R$-submodules of $E$ compatible with $\psi=u T$ also amounts to finding all
-$\phi=\pi \circ u^{1/p^e}$-compatible ideals.
+$\phi=\pi \circ F_*^e u$ ideals.
 

### 2019-04-24 Fsing/TestIdealsPaper/TestIdeals.tex

--- 2019-04-24 Fsing/TestIdealsPaper/TestIdeals.tex
@@
 \begin{MyVerbatim}
-i1 : R = ZZ/3[x,y,z]/(x^3 + y^4 + z^5);
-i2 : L = HSLGModule R;
+i1 : R = ZZ/3[x,y,z]/ideal( x^3 + y^4 + z^5 );
+i2 : L = FPureModule R;
 i3 : L#0

### 2019-04-28 Fsing/TestIdealsPaper/TestIdeals.tex
Small changes
Changes in examples of paper

@@
 \documentclass{amsart}
-\usepackage{calc,amssymb,amsthm,amsmath}
+\usepackage{calc,amssymb,amsthm,amsmath,setspace}
 %\usepackage{mathtools}
@@
 
-% TODO NOTES
-\usepackage[textwidth=3.5 cm,textsize=small,shadow,
-%disable
-%%option disable removes the notes
-]{todonotes}
-
-\newcommand{\warning}[2][]
-{\todo[color=red,caption={},#1]{#2}}
-\newcommand{\details}[2][]
-{\todo[linecolor=cyan,backgroundcolor=cyan!40, caption={},#1]{#2}}
-\newcommand{\postit}[2][]
-{\todo[linecolor=orange,backgroundcolor=yellow!40, caption={},#1]{#2}}
-\newcommand{\myexample}[2][]
-{\todo[linecolor=green,backgroundcolor=green!50,caption={}, #1]{#2}}
-\newcommand{\flag}[2][]
-{\todo[linecolor=orange,backgroundcolor=yellow, caption={},#1]{#2}}
-\newcommand{\oldargument}[2][]
-{\todo[linecolor=darkgray,backgroundcolor=gray!40, caption={},#1]{#2}}
-\newcommand{\myquestion}[2][]
-{\todo[linecolor=purple,backgroundcolor=purple!80,caption={}, #1]{#2}}
-\newcommand{\answer}[2][]
-{\todo[noline, backgroundcolor=white, bordercolor=purple, caption={},#1]{#2}}
-\newcommand{\pedro}[2][]
-{\todo[linecolor=blue,backgroundcolor=blue!10,caption={}, #1]{#2}}
-\newcommand{\billy}[2][]
-{\todo[linecolor=green,backgroundcolor=green!10,caption={}, #1]{#2}}
-\newcommand{\bob}[2][]
-{\todo[linecolor=purple,backgroundcolor=purple!20,caption={}, #1]{#2}}
-\newcommand{\jimmy}[2][]
-{\todo[linecolor=orange,backgroundcolor=orange!10,caption={}, #1]{#2}}
-
 \DeclareMathOperator{\HH}{H}
@@
 {\small
+\setstretch{.7}
 \begin{MyVerbatim}
 i1 : R = ZZ/5[x,y,z];
+
 i2 : I = ideal(x^6*y*z + x^2*y^12*z^3 + x*y*z^18);
+
 o2 : Ideal of R
+
 i3 : frobeniusPower(1/5, I)
+
                 2   3
 o3 = ideal (x, y , z )
+
 o3 : Ideal of R
@@
 {\small
+   \setstretch{.7}
 \begin{MyVerbatim}
 i1 : S = ZZ/5[x,y,z];
+
 i2 : f = x^3 + y^3 + z^3;
-i3 : u = f^(5 - 1);
+
+i3 : u = f^(5-1);
+
 i4 : frobeniusRoot(1, ideal u)
+
 o4 = ideal (z, y, x)
+
 o4 : Ideal of S
@@
 i5 : S = ZZ/7[x,y,z];
+
 i6 : f = x^3 + y^3 + z^3;
-i7 : u = f^(7 - 1)
+
+i7 : u = f^(7-1);
+
 i8 : frobeniusRoot(1, ideal u)
+
 o8 = ideal 1
+
 o8 : Ideal of S
@@
 {\small
+   \setstretch{.7}
 \begin{MyVerbatim}
 i1 : p = 3;
+
 i2 : R = ZZ/p[x,y];
+
 i3 : m = monomialIdeal(x, y);
+
 o3 : MonomialIdeal of R
+
 i4 : I = m^5;
+
 o4 : MonomialIdeal of R
+
 i5 : t = 3/5 - 1/(5*p^3);
+
 i6 : frobeniusPower(t, I)
+
              2        2
 o6 = ideal (y , x*y, x )
+
 o6 : Ideal of R
+
 i7 : frobeniusPower(t - 1/p^5, I)
+
 o7 = ideal (y, x)
+
 o7 : Ideal of R
@@
 {\small
+   \setstretch{.7}
 \begin{MyVerbatim}
 i8 : S = ZZ/3[a..f,x,y];
+
 i9 : G = a*x^5 + b*x^4*y + c*x^3*y^2 + d*x^2*y^3 + e*x*y^4 + f*y^5;
+
 i10 : testIdeal(t, G)
+
               2        2
 o10 = ideal (y , x*y, x )
+
 o10 : Ideal of S
+
 i11 : testIdeal(t - 1/p^5, G)
+
 o11 = ideal (y, x)
+
 o11 : Ideal of S
@@
 {\small
-\begin{MyVerbatim}
-i1 : p = 2;
-i2 : R = ZZ/p[a,b,c,d];
-i3 : I = intersect(ideal(a, b),ideal(a, c),ideal(c, d),ideal(c + d, a^3 + b*d^2));
-o3 : Ideal of R
-i4 : f = inducedMap(R^1/I, R^1/frobenius(I));
+   \setstretch{.7}
+\begin{MyVerbatim}
+i1 : R = ZZ/2[a,b,c,d];
+
+i2 : I = intersect(ideal(a,b),ideal(a,c),ideal(c,d),ideal(c+d,a^3+b*d^2));
+
+o2 : Ideal of R
+
+i3 : f = inducedMap(R^1/I, R^1/frobenius(I));
+
+o3 : Matrix
+
+i4 : E2 = Ext^2(f, R^1)
+
+o4 = {-8}  | a4+abc2+abcd a2b            |
+     {-10} | a2cd3        a3cd+a3d2+bcd3 |
+
 o4 : Matrix
-i5 : E2 = Ext^2(f, R^1)
-o5 = {-8}  | a4+abc2+abcd a2b            |
-     {-10} | a2cd3        a3cd+a3d2+bcd3 |
-o5 : Matrix
-i6 : target E2
-o6 = cokernel {-8}  | 0     a2 b2c2 |
+
+i5 : target E2
+
+o5 = cokernel {-8}  | 0     a2 b2c2 |
               {-10} | c2+d2 d4 a4d2 |
+
+                            2
+o5 : R-module, quotient of R
+
+i6 : source E2
+
+o6 = cokernel {-4} | 0   a  bc  |
+              {-5} | c+d d2 a2d |
+
                             2
 o6 : R-module, quotient of R
-i7 : source E2
-o7 = cokernel {-4} | 0   a  bc  |
-              {-5} | c+d d2 a2d |
-                            2
-o7 : R-module, quotient of R
 \end{MyVerbatim}
@@
 \medskip
-{\small
-\begin{MyVerbatim}
-i8 : U = matrix entries E2;
+{\small\setstretch{.7}
+\begin{MyVerbatim}
+i7 : U = matrix entries E2;
+
              2       2
+o7 : Matrix R  <--- R
+
+i8 : A = matrix entries relations source E2;
+
+             2       3
 o8 : Matrix R  <--- R
-i9 : A = matrix entries relations source E2;
+
+i9 : frobeniusRoot(1, U)
+
+o9 = {-2} | 1 0 0 |
+     {0}  | 0 d a |
+
               2       3
 o9 : Matrix R  <--- R
-i10 : frobeniusRoot(1, U)
-o10 = {-2} | 1 0 0 |
-      {0}  | 0 d a |
-              2       3
-o10 : Matrix R  <--- R
 \end{MyVerbatim}
@@
 \medskip
-{\small
-\begin{MyVerbatim}
-i11 : V = ascendModule(1, A, U)
-o11 = | 0   a  bc  |
+{\small\setstretch{.7}
+\begin{MyVerbatim}
+i10 : V = ascendModule(1, A, U)
+
+o10 = | 0   a  bc  |
       | c+d d2 a2d |
+
               2       3
-o11 : Matrix R  <--- R
+o10 : Matrix R  <--- R
 \end{MyVerbatim}

### 2019-04-28 Fsing/TestIdealsPaper/TestIdeals.tex
More changes in examples of paper

@@
 
-i3 : u = f^(5-1);
+i3 : u = f^(5 - 1);
 
@@
 
-i7 : u = f^(7-1);
+i7 : u = f^(7 - 1);
 
@@
 \medskip
-{\small
+{\small\setstretch{.7}
 \begin{MyVerbatim}
 i1 : R = ZZ/7[x,y,z]/(x^3 + y^3 + z^3);
+
 i2 : isFInjective R
+
 o2 = true
+
 i3 : R = ZZ/5[x,y,z]/(x^3 + y^3 + z^3);
+
 i4 : isFInjective R
+
 o4 = false
@@
 \medskip
-{\small
+{\small\setstretch{.7}
 \begin{MyVerbatim}
 i1 : R = ZZ/7[x,y,z]/((x - 1)^5 + (y + 1)^5 + z^5);
+
 i2 : isFInjective R -- R is not globally F-injective...
+
 o2 = false
+
 i3 : isFInjective(R, IsLocal => true) -- but is F-injective at the origin
+
 o3 = true
@@
 \medskip
-{\small
+{\small\setstretch{.7}
 \begin{MyVerbatim}
 i1 : R = ZZ/5[x,y,z]/(x^2 + y*z);
+
 i2 : isFRegular R
+
 o2 = true
+
 i3 : R = ZZ/7[x,y,z]/(x^3 + y^3 + z^3);
+
 i4 : isFRegular R
+
 o4 = false
@@
 \medskip
-{\small
+{\small\setstretch{.7}
 \begin{MyVerbatim}
 i1 : R = ZZ/5[x,y];
+
 i2 : f = y^2 - x^3;
+
 i3 : isFRegular(1/2, f)
+
 o3 = true
+
 i4 : isFRegular(5/6, f)
+
 o4 = false
+
 i5 : isFRegular(4/5, f)
+
 o5 = false
+
 i6 : isFRegular(4/5 - 1/100000, f)
+
 o6 = true
@@
 \medskip
-{\small
+{\small\setstretch{.7}
 \begin{MyVerbatim}
 i1 : R = ZZ/7[x,y,z]/((x - 1)^3 + (y + 1)^3 + z^3);
+
 i2 : isFRegular R -- R is not globally F-regular...
+
 o2 = false
+
 i3 : isFRegular(R, IsLocal => true) -- but is F-regular at the origin
+
 o3 = true
+
 i4 : R = ZZ/13[x,y];
+
 i5 : f = (y - 2)^2 - (x - 3)^3;
+
 i6 : isFRegular(5/6, f) -- (R,f^(5/6)) is not F-regular...
+
 o6 = false
+
 i7 : isFRegular(5/6, f, IsLocal => true) -- but is F-regular at the origin
+
 o7 = true
@@
 \medskip
-{\small
+{\small\setstretch{.7}
 \begin{MyVerbatim}
 i1 : R = ZZ/5[x,y,z]/(x^2 + y*z);
+
 i2 : isFPure R
+
 o2 = true
+
 i3 : R = ZZ/7[x,y,z]/(x^3 + y^3 + z^3);
+
 i4 : isFPure R
+
 o4 = true
+
 i5 : S = ZZ/2[x,y,z];
+
 i5 : isFPure ideal(y^2 - x^3)
+
 o5 = false
+
 i6 : isFPure ideal(z^2 - x*y*z + x*y^2 + x^2*y)
+
 o6 = true
@@
 \medskip
-{\small
+{\small\setstretch{.7}
 \begin{MyVerbatim}
 i1 : S = ZZ/3[a,b,c,d,t];
-i2 : m = 4;
-i3 : n = 3;
-i4 : M = matrix{{ a^2 + t^m, b, d }, { c, a^2, b^n - d }};
-i5 : I = minors(2, M);
-i6 : R = S/I;
-i7 : isFRational R
-o7 = true
+
+i2 : M = matrix{{ a^2 + t^4, b, d }, { c, a^2, b^3 - d }};
+
+             2       3
+o2 : Matrix S  <--- S
+
+i3 : I = minors(2, M);
+
+o3 : Ideal of S
+
+i4 : R = S/I;
+
+i5 : isFRational R
+
+o5 = true
 \end{MyVerbatim}
@@
 \medskip
-{\small
+{\small\setstretch{.7}
 \begin{MyVerbatim}
 i1 : R = ZZ/5[x,y,z]/(x^4 + y^4 + z^4);
+
 i2 : N = testModule R;
+
 i3 : N#0
+
              2             2        2
 o3 = ideal (z , y*z, x*z, y , x*y, x )
+
 o3 : Ideal of R
+
 i4 : N#1
+
 o4 = ideal 1
+
 o4 : Ideal of R
@@
 
-The output of \texttt{testModule} is a list, consisting of three items:
+The output of \texttt{testModule} is a sequence, consisting of three items:
 \begin{enumerate}[(1)]
@@
 \medskip
-{\small
+{\small\setstretch{.7}
 \begin{MyVerbatim}
 i1 : R = ZZ/5[x,y,z]/(y*z, x*z, x*y);
+
 i2 : N = testModule R;
+
 i3 : N#0
+
              2   2   2
 o3 = ideal (z , y , x )
+
 o3 : Ideal of R
+
 i4 : N#1
-o4 = ideal (y - z, x + z)
+
+o4 = ideal (y + 2z, x - z)
+
 o4 : Ideal of R
@@
 \medskip
-{\small
+{\small\setstretch{.7}
 \begin{MyVerbatim}
 i1 : R = ZZ/2[a..e];
+
 i2 : E = matrix {{a, b, b, e}, {d, d, c, a}};
+
              2       4
 o2 : Matrix R  <--- R
+
 i3 : I = minors(2, E);
+
 o3 : Ideal of R
+
 i4 : S = R/I;
+
 i5 : J = parameterTestIdeal S
+
 o5 = ideal (c + d, b, a)
+
 o5 : Ideal of S
+
 i6 : J = substitute(J, R);
+
 o6 : Ideal of R
+
 i7 : mingens(J + I)
+
 o7 = | c+d b a de |
+
              1       4
@@
 \medskip
-{\small
+{\small\setstretch{.7}
 \begin{MyVerbatim}
 i1 : T = ZZ/7[x,y];
+
 i2 : S = ZZ/7[a,b,c,d];
+
 i3 : f = map(T, S, {x^3, x^2*y, x*y^2, y^3});
+
 i4 : I = ker f;
+
 i5 : R = S/I;
+
 i6 : testIdeal R
+
 o6 = ideal 1
+
 o6 : Ideal of R
@@
 \medskip
-{\small
+{\small\setstretch{.7}
 \begin{MyVerbatim}
 i7 : toString QGorensteinGenerator(1, R)
+
 o7 = a^2*b^6*c^12+a^3*b^4*c^13+a^3*b^5*c^11*d+a^4*b^3*c^12*d+a^5*b*c^13*d+b^

### 2019-04-29 Fsing/TestIdealsPaper/TestIdeals.tex
Finsehd recomputing examples.

@@
 {\small
-\setstretch{.7}
+\setstretch{.67}
 \begin{MyVerbatim}
@@
 {\small
-   \setstretch{.7}
+   \setstretch{.67}
 \begin{MyVerbatim}
@@
 \medskip
-{\small\setstretch{.7}
+{\small\setstretch{.67}
 \begin{MyVerbatim}
@@
 {\small
-\begin{MyVerbatim}
-i1 : T = ZZ/3[x,y];
-i2 : S = ZZ/3[a,b,c,d];
-i3 : f = map(T, S, {x^3, x^2*y, x*y^2, y^3});
-i4 : I = ker f;
-i5 : R = S/I;
-i6 : testIdeal R
-o6 = ideal 1
-o6 : Ideal of R
+\setstretch{.67}
+\begin{MyVerbatim}
+i2 : T = ZZ/3[x,y];
+
+i3 : S = ZZ/3[a,b,c,d];
+
+i4 : f = map(T, S, {x^3, x^2*y, x*y^2, y^3});
+
+o4 : RingMap T <--- S
+
+i5 : I = ker f;
+
+o5 : Ideal of S
+
+i6 : R = S/I;
+
+i7 : testIdeal R
+
+o7 = ideal 1
+
+o7 : Ideal of R
 \end{MyVerbatim}
@@
 {\small
-\begin{MyVerbatim}
-i1 : R = ZZ/3[x,y,z]/ideal( x^3 + y^4 + z^5 );
-i2 : L = FPureModule R;
-i3 : L#0
+\setstretch{.67}
+\begin{MyVerbatim}
+i2 : R = ZZ/3[x,y,z]/ideal( x^3 + y^4 + z^5 );
+
+i3 : L = FPureModule R;
+
+i4 : L#0
+
                        2        2   3
-o3 = ideal (0, y*z, x*z, y , x*y, x , z )
-o3 : Ideal of R
-i4 : L#1
-o4 = ideal 1
+o4 = ideal (y*z, x*z, y , x*y, x , z )
+
 o4 : Ideal of R
-i5 : L#3
-o5 = 1
+
+i5 : L#1
+
+o5 = ideal 1
+
+o5 : Ideal of R
+
+i6 : L#3
+
+o6 = 1i2 : R = ZZ/3[x,y,z]/ideal( x^3 + y^4 + z^5 );
+
+i3 : L = FPureModule R;
+
+i4 : L#0
+
+                       2        2   3
+o4 = ideal (y*z, x*z, y , x*y, x , z )
+
+o4 : Ideal of R
+
+i5 : L#1
+
+o5 = ideal 1
+
+o5 : Ideal of R
+
+i6 : L#3
+
+o6 = 1
 \end{MyVerbatim}
@@
 {\small
-\begin{MyVerbatim}
-i1 : R = ZZ/2[x,y,z];
-i2 : f = x^3 + y^2*z + y*z^2;
-i3 : frobeniusPower(1/2, ideal f)
-o3 = ideal (x, y, z)
-o3 : Ideal of R
-i4 : u=f^3;
-i5 : frobeniusPower(1/4, ideal u)
-o6 = ideal (x, y, z)
+\setstretch{.67}
+\begin{MyVerbatim}
+i2 : R = ZZ/2[x,y,z];
+
+i3 : f = x^3 + y^2*z + y*z^2;
+
+i4 : frobeniusPower(1/2, ideal f)
+
+o4 = ideal (z, y, x)
+
+o4 : Ideal of R
+
+i5 : u=f^3;
+
+i6 : frobeniusPower(1/4, ideal u)
+
+o6 = ideal (z, y, x)
+
 o6 : Ideal of R
+
 i7 : ((FPureModule(1, f))#3) + 1
-o7 : 2
+
+o7 = 2
 \end{MyVerbatim}
@@
 {\small
-\begin{MyVerbatim}
-i1 : R = ZZ/11[x,y,z];
-i2 : f = y^2*z^3 - x^5 - 2*z^5;
-i3 : frobeniusPower(1/11, ideal f^10)
+\setstretch{.67}
+\begin{MyVerbatim}
+i2 : R = ZZ/11[x,y,z];
+
+i3 : f = y^2*z^3 - x^5 - 2*z^5;
+
+i4 : frobeniusPower(1/11, ideal f^10)
+
              2        3
-o6 = ideal (z , x*z, x )
-o3 : Ideal of R
+o4 = ideal (z , x*z, x )
+
+o4 : Ideal of R
+
 i5 : frobeniusPower(1/121, ideal f^120)
+
              2        3
-o6 = ideal (z , x*z, x )
-o6 : Ideal of R
-i7 : ((FPureModule(1, f))#3) + 1
-o7 : 2
+o5 = ideal (z , x*z, x )
+
+o5 : Ideal of R
+
+i6 : ((FPureModule(1, f))#3) + 1
+
+o6 = 2
 \end{MyVerbatim}
@@
 {\small
-\begin{MyVerbatim}
-i1 : R = ZZ/3[u,v];
-i2 : u = u^2*v^2;
-i3 : compatibleIdeals u
-o3 = {ideal v, ideal (v, u), ideal u}
-o3 : List
+\setstretch{.67}
+\begin{MyVerbatim}
+i2 : R = ZZ/3[u,v];
+
+i3 : u = u^2*v^2;
+
+i4 : compatibleIdeals u
+
+o4 = {ideal v, ideal (v, u), ideal u}
+
+o4 : List
 \end{MyVerbatim}
@@
 {\small
-\begin{MyVerbatim}
-i1 : R = ZZ/2[a..f];
-i2 : E = matrix {{a, b, b, e}, {d, d, c, a}};
+\setstretch{.67}
+\begin{MyVerbatim}
+i2 : R = ZZ/2[a..f];
+
+i3 : E = matrix {{a, b, b, e}, {d, d, c, a}};
+
              2       4
-o2 : Matrix R  <--- R
-i3 : I = minors(2, E);
-o3 : Ideal of R
-i4 : S = R/I;
-i5 : isCohenMacaulay S
-o5 = true
+o3 : Matrix R  <--- R
+
+i4 : I = minors(2, E);
+
+o4 : Ideal of R
+
+i5 : S = R/I;
+
+i6 : isCohenMacaulay S
+
+o6 = true
 \end{MyVerbatim}
@@
 {\small
-\begin{MyVerbatim}
-i6 : omega = canonicalIdeal S
-o6 = ideal (e, d, a)
-o6 : Ideal of S
-i7 : omega = substitute(omega, R) + I;
-o7 : Ideal of R
-i8 : u = intersect((frobenius I):I, (frobenius omega) : omega);
+\setstretch{.67}
+\begin{MyVerbatim}
+i7 : omega = canonicalIdeal S
+
+o7 = ideal (e, d, a)
+
+o7 : Ideal of S
+
+i8 : omega = substitute(omega, R) + I;
+
 o8 : Ideal of R
-i9 : u = compress((gens u) % gens(frobenius I))
-o9 = | a3bc+a3bd+a2cde+abcde+abd2e+b2d2e+cd2e2+d3e2 |
+
+i9 : u = intersect((frobenius I):I, (frobenius omega) : omega);
+
+o9 : Ideal of R
+
+i10 : u = compress((gens u) % gens(frobenius I))
+
+o10 = | a3bc+a3bd+a2cde+abcde+abd2e+b2d2e+cd2e2+d3e2 |
+
               1       1
-o9 : Matrix R  <--- R
-i10 : u = first first entries u
+o10 : Matrix R  <--- R
+
+i11 :  u = first first entries u
+
        3       3       2                         2     2 2       2 2    3 2
-o10 = a b*c + a b*d + a c*d*e + a*b*c*d*e + a*b*d e + b d e + c*d e  + d e
-o10 : R
+o11 = a b*c + a b*d + a c*d*e + a*b*c*d*e + a*b*d e + b d e + c*d e  + d e
+
+o11 : R
 \end{MyVerbatim}
@@
 {\small
-\begin{MyVerbatim}
-i11 : L = compatibleIdeals u;
-i12 : print \ L;
+\setstretch{.67}
+\begin{MyVerbatim}
+L = compatibleIdeals u;
+
+i13 : print \ L;
        3       3       2                         2     2 2       2 2    3 2
-ideal (a b*c + a b*d + a c*d*e + a*b*c*d*e + a*b*d e + b d e + c*d e  + d e )
+ideal(a b*c + a b*d + a c*d*e + a*b*c*d*e + a*b*d e + b d e + c*d e  + d e )
                2
 ideal (a + b, a  + d*e)
-ideal (d, a)
-ideal (d, a, e)
+ideal (e, a, d)
 ideal (e, d, a, c)
@@
 ideal (e, d, b, a)
+ideal (e, b, a)
+ideal (e, b, a, c + d)
+                      2
+ideal (c + d, a + b, b  + d*e)
+ideal (d, a)
 ideal (d, a, c)
@@
 ideal (d, b, a)
+\end{MyVerbatim}
+}
+\medskip
+
+We can also compute  all annihilators of $R$-submodules of $H^2_{\mathfrak{m}} (R/I)$ stable under the $p^1$-linear map induced from the Frobenius map on $R/I$.
+
+\medskip
+{\small
+\setstretch{.67}
+\begin{MyVerbatim}
+ print \ unique apply(L, J -> J : omega);
+       3       3       2                         2     2 2       2 2    3 2
+ideal(a b*c + a b*d + a c*d*e + a*b*c*d*e + a*b*d e + b d e + c*d e  + d e )
+               2
+ideal (a + b, b  + d*e)
+ideal (e, d, a)
+ideal 1
+ideal (e, b, a)
+ideal (e, c + d, b, a)
                       2
 ideal (c + d, a + b, b  + d*e)
-ideal (c + d, b, a, e)
-ideal (b, a, e)
-\end{MyVerbatim}
-}
-\medskip
-
-We can also compute  all annihilators of $R$-submodules of $H^2_{\mathfrak{m}} (R/I)$ stable under the $p^1$-linear map induced from the Frobenius map on $R/I$.
-
-\medskip
-{\small
-\begin{MyVerbatim}
-i13 : print \ unique apply(L, J -> J : omega);
-        3       3       2                         2     2 2       2 2    3 2
-ideal (a b*c + a b*d + a c*d*e + a*b*c*d*e + a*b*d e + b d e + c*d e  + d e )
-               2
-ideal (a + b, b  + d*e)
 ideal (d, a)
-ideal (e, d, a)
-ideal 1
 ideal (d, c, a)
@@
 ideal (d, b, a)
-                      2
-ideal (c + d, a + b, b  + d*e)
-ideal (e, c + d, b, a)
-ideal (e, b, a)
 \end{MyVerbatim}

### 2019-04-29 Fsing/TestIdealsPaper/TestIdeals.tex
More work on examples in paper

@@
 \medskip
-{\small
-\setstretch{.67}
+{\small\setstretch{.7}
 \begin{MyVerbatim}
@@
 \[
-R = \bF_{p^e}[x_1, \ldots, x_d],
-\]
+R = \mathbb{K}[x_1, \ldots, x_d],
+\]
+where $\mathbb{K}$ is a perfect field,
 $R^{1/p^e}$ is a free $R$-module with basis consisting of the monomials
@@
 Furthermore the calculation of  $(f)^{[1/p^e]}$ reduces to finding the terms in the right hand side of (\ref{eqn1}), which essentially amounts to
-taking each term in $f$, computing the $p^e$-th root of the coefficient in $\mathbb{K}$, and dividing the monomial exponent vector by $p^e$ with remainder.
+taking each term in $f$, computing the $p^e$-th root of its coefficient, and dividing the monomial exponent vector by $p^e$ with remainder.
 Hence the complexity of computing $(f)^{[1/p^e]}$ is proportional to the number of terms in $f$, and is independent of its degree.
@@
 \medskip
-{\small
-   \setstretch{.67}
+{\small\setstretch{.7}
 \begin{MyVerbatim}
@@
 \medskip
-{\small\setstretch{.67}
+{\small\setstretch{.7}
 \begin{MyVerbatim}
@@
 
-i8 : A = matrix entries relations source E2;
-
-             2       3
-o8 : Matrix R  <--- R
-
-i9 : frobeniusRoot(1, U)
-
-o9 = {-2} | 1 0 0 |
+i8 : A = image matrix entries relations source E2;
+
+i9 : frobeniusRoot(1, image U)
+
+o9 = image {-2} | 1 0 0 |
            {0}  | 0 d a |
 
-              2       3
-o9 : Matrix R  <--- R
+                             2
+o9 : R-module, submodule of R
 \end{MyVerbatim}
@@
 \medskip
-{\small\setstretch{.67}
-\begin{MyVerbatim}
-i10 : V = ascendModule(1, A, U)
-
-o10 = | 0   a  bc  |
+{\small\setstretch{.7}
+\begin{MyVerbatim}
+i10 : B = ascendModule(1, A, U)
+
+o10 = image | 0   a  bc  |
             | c+d d2 a2d |
 
-              2       3
-o10 : Matrix R  <--- R
+                              2
+o10 : R-module, submodule of R
 \end{MyVerbatim}
@@
 \medskip
-{\small\setstretch{.67}
+{\small\setstretch{.8}
 \begin{MyVerbatim}
@@
 \medskip
-{\small
-\setstretch{.67}
-\begin{MyVerbatim}
-i2 : T = ZZ/3[x,y];
-
-i3 : S = ZZ/3[a,b,c,d];
-
-i4 : f = map(T, S, {x^3, x^2*y, x*y^2, y^3});
-
-o4 : RingMap T <--- S
-
-i5 : I = ker f;
-
-o5 : Ideal of S
-
-i6 : R = S/I;
-
-i7 : testIdeal R
-
-o7 = ideal 1
-
-o7 : Ideal of R
+{\small\setstretch{.7}
+\begin{MyVerbatim}
+i1 : T = ZZ/3[x,y];
+
+i2 : S = ZZ/3[a,b,c,d];
+
+i3 : f = map(T, S, {x^3, x^2*y, x*y^2, y^3});
+
+i4 : I = ker f;
+
+i5 : R = S/I;
+
+i6 : testIdeal R
+
+o6 = ideal 1
+
+o6 : Ideal of R
 \end{MyVerbatim}
@@
 stabilize for $e \gg 0$.
-The function \texttt{FPureModule} computes the stable submodule in this chain, called the \emph{HSLG module}, and returns a list containing the following items:
+The function \texttt{FPureModule} computes the stable submodule in this chain, called the \emph{HSLG module}, and returns a sequence containing the following items:
 \begin{enumerate}[(1)]
@@
 \medskip
-{\small
-\setstretch{.67}
-\begin{MyVerbatim}
-i2 : R = ZZ/3[x,y,z]/ideal( x^3 + y^4 + z^5 );
-
-i3 : L = FPureModule R;
-
-i4 : L#0
+{\small\setstretch{.7}
+\begin{MyVerbatim}
+i1 : R = ZZ/3[x,y,z]/(x^3 + y^4 + z^5);
+
+i2 : L = FPureModule R;
+
+i3 : L#0
 
                           2        2   3
-o4 = ideal (y*z, x*z, y , x*y, x , z )
+o3 = ideal (0, y*z, x*z, y , x*y, x , z )
+
+o3 : Ideal of R
+
+i4 : L#1
+
+o4 = ideal 1
 
@@
 
-i5 : L#1
-
-o5 = ideal 1
-
-o5 : Ideal of R
-
-i6 : L#3
-
-o6 = 1i2 : R = ZZ/3[x,y,z]/ideal( x^3 + y^4 + z^5 );
-
-i3 : L = FPureModule R;
-
-i4 : L#0
-
-                       2        2   3
-o4 = ideal (y*z, x*z, y , x*y, x , z )
-
-o4 : Ideal of R
-
-i5 : L#1
-
-o5 = ideal 1
-
-o5 : Ideal of R
-
-i6 : L#3
-
-o6 = 1
+i5 : L#3
+
+o5 = 1
 \end{MyVerbatim}
@@
 \medskip
-{\small
-\setstretch{.67}
-\begin{MyVerbatim}
-i2 : R = ZZ/2[x,y,z];
-
-i3 : f = x^3 + y^2*z + y*z^2;
-
-i4 : frobeniusPower(1/2, ideal f)
-
-o4 = ideal (z, y, x)
-
-o4 : Ideal of R
-
-i5 : u=f^3;
-
-i6 : frobeniusPower(1/4, ideal u)
-
-o6 = ideal (z, y, x)
+{\small\setstretch{.7}
+\begin{MyVerbatim}
+i1 : R = ZZ/2[x,y,z];
+
+i2 : f = x^3 + y^2*z + y*z^2;
+
+i3 : frobeniusPower(1/2, ideal f)
+
+o3 = ideal (x, y, z)
+
+o3 : Ideal of R
+
+i4 : u=f^3;
+
+i5 : frobeniusPower(1/4, ideal u)
+
+o6 = ideal (x, y, z)
 
@@
 
-o7 = 2
+o7 : 2
 \end{MyVerbatim}
@@
 \medskip
-{\small
-\setstretch{.67}
-\begin{MyVerbatim}
-i2 : R = ZZ/11[x,y,z];
-
-i3 : f = y^2*z^3 - x^5 - 2*z^5;
-
-i4 : frobeniusPower(1/11, ideal f^10)
+{\small\setstretch{.7}
+\begin{MyVerbatim}
+i1 : R = ZZ/11[x,y,z];
+
+i2 : f = y^2*z^3 - x^5 - 2*z^5;
+
+i3 : frobeniusPower(1/11, ideal f^10)
 
              2        3
-o4 = ideal (z , x*z, x )
-
-o4 : Ideal of R
+o6 = ideal (z , x*z, x )
+
+o3 : Ideal of R
 
@@
              2        3
-o5 = ideal (z , x*z, x )
-
-o5 : Ideal of R
-
-i6 : ((FPureModule(1, f))#3) + 1
-
-o6 = 2
+o6 = ideal (z , x*z, x )
+
+o6 : Ideal of R
+
+i7 : ((FPureModule(1, f))#3) + 1
+
+o7 : 2
 \end{MyVerbatim}
@@
 \medskip
-{\small
-\setstretch{.67}
-\begin{MyVerbatim}
-i2 : R = ZZ/3[u,v];
-
-i3 : u = u^2*v^2;
-
-i4 : compatibleIdeals u
-
-o4 = {ideal v, ideal (v, u), ideal u}
-
-o4 : List
+{\small\setstretch{.7}
+\begin{MyVerbatim}
+i1 : R = ZZ/3[u,v];
+
+i2 : u = u^2*v^2;
+
+i3 : compatibleIdeals u
+
+o3 = {ideal v, ideal (v, u), ideal u}
+
+o3 : List
 \end{MyVerbatim}
@@
 \medskip
-{\small
-\setstretch{.67}
-\begin{MyVerbatim}
-i2 : R = ZZ/2[a..f];
-
-i3 : E = matrix {{a, b, b, e}, {d, d, c, a}};
+{\small\setstretch{.7}
+\begin{MyVerbatim}
+i1 : R = ZZ/2[a..f];
+
+i2 : E = matrix {{a, b, b, e}, {d, d, c, a}};
 
              2       4
-o3 : Matrix R  <--- R
-
-i4 : I = minors(2, E);
-
-o4 : Ideal of R
-
-i5 : S = R/I;
-
-i6 : isCohenMacaulay S
-
-o6 = true
+o2 : Matrix R  <--- R
+
+i3 : I = minors(2, E);
+
+o3 : Ideal of R
+
+i4 : S = R/I;
+
+i5 : isCohenMacaulay S
+
+o5 = true
 \end{MyVerbatim}
@@
 \medskip
-{\small
-\setstretch{.67}
-\begin{MyVerbatim}
-i7 : omega = canonicalIdeal S
-
-o7 = ideal (e, d, a)
-
-o7 : Ideal of S
-
-i8 : omega = substitute(omega, R) + I;
+{\small\setstretch{.7}
+\begin{MyVerbatim}
+i6 : omega = canonicalIdeal S
+
+o6 = ideal (e, d, a)
+
+o6 : Ideal of S
+
+i7 : omega = substitute(omega, R) + I;
+
+o7 : Ideal of R
+
+i8 : u = intersect((frobenius I):I, (frobenius omega) : omega);
 
@@
 
-i9 : u = intersect((frobenius I):I, (frobenius omega) : omega);
-
-o9 : Ideal of R
-
-i10 : u = compress((gens u) % gens(frobenius I))
-
-o10 = | a3bc+a3bd+a2cde+abcde+abd2e+b2d2e+cd2e2+d3e2 |
+i9 : u = compress((gens u) % gens(frobenius I))
+
+o9 = | a3bc+a3bd+a2cde+abcde+abd2e+b2d2e+cd2e2+d3e2 |
 
              1       1
-o10 : Matrix R  <--- R
-
-i11 :  u = first first entries u
+o9 : Matrix R  <--- R
+
+i10 : u = first first entries u
 
        3       3       2                         2     2 2       2 2    3 2
-o11 = a b*c + a b*d + a c*d*e + a*b*c*d*e + a*b*d e + b d e + c*d e  + d e
-
-o11 : R
+o10 = a b*c + a b*d + a c*d*e + a*b*c*d*e + a*b*d e + b d e + c*d e  + d e
+
+o10 : R
 \end{MyVerbatim}
@@
 \medskip
-{\small
-\setstretch{.67}
-\begin{MyVerbatim}
-L = compatibleIdeals u;
-
-i13 : print \ L;
+{\small\setstretch{.7}
+\begin{MyVerbatim}
+i11 : L = compatibleIdeals u;
+
+i12 : print \ L;
+
         3       3       2                         2     2 2       2 2    3 2
-ideal(a b*c + a b*d + a c*d*e + a*b*c*d*e + a*b*d e + b d e + c*d e  + d e )
+ideal (a b*c + a b*d + a c*d*e + a*b*c*d*e + a*b*d e + b d e + c*d e  + d e )
+
                2
 ideal (a + b, a  + d*e)
-ideal (e, a, d)
+
+ideal (d, a)
+
+ideal (d, a, e)
+
 ideal (e, d, a, c)
+
 ideal (e, d, c, b, a)
+
 ideal (e, d, b, a)
-ideal (e, b, a)
-ideal (e, b, a, c + d)
+
+ideal (d, a, c)
+
+ideal (d, c, b, a)
+
+ideal (d, b, a)
+
                       2
 ideal (c + d, a + b, b  + d*e)
-ideal (d, a)
-ideal (d, a, c)
-ideal (d, c, b, a)
-ideal (d, b, a)
+
+ideal (c + d, b, a, e)
+
+ideal (b, a, e)
 \end{MyVerbatim}
@@
 \medskip
-{\small
-\setstretch{.67}
-\begin{MyVerbatim}
- print \ unique apply(L, J -> J : omega);
+{\small\setstretch{.7}
+\begin{MyVerbatim}
+i13 : print \ unique apply(L, J -> J : omega);
+
         3       3       2                         2     2 2       2 2    3 2
-ideal(a b*c + a b*d + a c*d*e + a*b*c*d*e + a*b*d e + b d e + c*d e  + d e )
+ideal (a b*c + a b*d + a c*d*e + a*b*c*d*e + a*b*d e + b d e + c*d e  + d e )
+
                2
 ideal (a + b, b  + d*e)
+
+ideal (d, a)
+
 ideal (e, d, a)
+
 ideal 1
-ideal (e, b, a)
-ideal (e, c + d, b, a)
+
+ideal (d, c, a)
+
+ideal (d, c, b, a)
+
+ideal (d, b, a)
+
                       2
 ideal (c + d, a + b, b  + d*e)
-ideal (d, a)
-ideal (d, c, a)
-ideal (d, c, b, a)
-ideal (d, b, a)
+
+ideal (e, c + d, b, a)
+
+ideal (e, b, a)
 \end{MyVerbatim}

### 2019-04-29 Fsing/TestIdealsPaper/TestIdeals.tex
Minor changes

@@
 \medskip
-{\small\setstretch{.7}
+{\small
+\setstretch{.67}
 \begin{MyVerbatim}
@@
 To access this enhancement, one should try to pass functions like \texttt{ascendIdeal} and \texttt{frobeniusRoot} the elements and their exponents (see the documentation).
-In particular, when computing the $p^e$-th Frobenius root of an ideal of the form $f^n \cdot J$, one should not multiply out $f^n$ and $J$, nor even raise $f$ to the $n^\mathrm{th}$ power, but rather call \texttt{frobeniusRoot(e,n,f,J)}.
+In particular, when computing the $p^e$-th Frobenius root of an ideal of the form $f^n \cdot J$, one should not multiply out $f^n$ and $J$, nor even raise $f$ to the $n^\mathrm{th}$ power, but rather call \texttt{frobeniusRoot(e, n, f, J)}.
 \end{remark}
@@
 etc.
-%
-%\pedro{I am not sure what this last sentence is saying}
-%
 
@@
 
+o3 : RingMap T <--- S
+
 i4 : I = ker f;
 
+o4 : Ideal of S
+
 i5 : R = S/I;
@@
 
-o6 = ideal 1
-
-o6 : Ideal of R
+o7 = ideal 1
+
+o7 : Ideal of R
 \end{MyVerbatim}
@@
 \begin{enumerate}[(1)]
-   \item The HSLGmodule;
+   \item The HSLG module;
    \item The canonical module, embedded (non-uniquely) as an ideal;
@@
                        2        2   3
-o3 = ideal (0, y*z, x*z, y , x*y, x , z )
+o3 = ideal (y*z, x*z, y , x*y, x , z )
 
@@
 o5 = 1
+
+i6 : R = ZZ/3[x,y,z]/(x^3 + y^4 + z^5);
+
+i7 : L = FPureModule R;
+
+i8 : L#0
+
+                       2        2   3
+o8 = ideal (y*z, x*z, y , x*y, x , z )
+
+o8 : Ideal of R
+
+i9 : L#1
+
+o9 = ideal 1
+
+o9 : Ideal of R
+
+i10 : L#3
+
+o10 = 1
 \end{MyVerbatim}
@@
 
-o3 = ideal (x, y, z)
+o3 = ideal (z, y, x)
 
@@
 
-i4 : u=f^3;
+i4 : u = f^3;
 
@@
 
-o6 = ideal (x, y, z)
-
-o6 : Ideal of R
-
-i7 : ((FPureModule(1, f))#3) + 1
-
-o7 : 2
+o5 = ideal (z, y, x)
+
+o5 : Ideal of R
+
+i6 : ((FPureModule(1, f))#3) + 1
+
+o6 = 2
 \end{MyVerbatim}
@@
              2        3
-o6 = ideal (z , x*z, x )
+o3 = ideal (z , x*z, x )
 
@@
 
-i5 : frobeniusPower(1/121, ideal f^120)
+i4 : frobeniusPower(1/121, ideal f^120)
 
              2        3
-o6 = ideal (z , x*z, x )
-
-o6 : Ideal of R
-
-i7 : ((FPureModule(1, f))#3) + 1
-
-o7 : 2
+o4 = ideal (z , x*z, x )
+
+o4 : Ideal of R
+
+i5 : ((FPureModule(1, f))#3) + 1
+
+o5 = 2
 \end{MyVerbatim}
@@
        3       3       2                         2     2 2       2 2    3 2
-ideal (a b*c + a b*d + a c*d*e + a*b*c*d*e + a*b*d e + b d e + c*d e  + d e )
+ideal(a b*c + a b*d + a c*d*e + a*b*c*d*e + a*b*d e + b d e + c*d e  + d e )
 
@@
 
-ideal (d, a)
-
-ideal (d, a, e)
+ideal (e, a, d)
 
@@
 
-ideal (d, a, c)
-
-ideal (d, c, b, a)
-
-ideal (d, b, a)
+ideal (e, b, a)
+
+ideal (e, b, a, c + d)
 
@@
 
-ideal (c + d, b, a, e)
-
-ideal (b, a, e)
+ideal (d, a)
+
+ideal (d, a, c)
+
+ideal (d, c, b, a)
+
+ideal (d, b, a)
 \end{MyVerbatim}
@@
 
-ideal (d, a)
-
 ideal (e, d, a)
@@
 
-ideal (d, c, a)
-
-ideal (d, c, b, a)
-
-ideal (d, b, a)
+ideal (e, b, a)
+
+ideal (e, c + d, b, a)
 
@@
 
-ideal (e, c + d, b, a)
-
-ideal (e, b, a)
+ideal (d, a)
+
+ideal (d, c, a)
+
+ideal (d, c, b, a)
+
+ideal (d, b, a)
 \end{MyVerbatim}

### 2019-05-24 Fsing/TestIdealsPaper/TestIdeals.tex
Made changes requested by referee.

@@
 \begin{document}
-\title{The  {TestIdeals} package for \emph{Macaulay2}}
+\title{The  \emph{TestIdeals} package for \emph{Macaulay2}}
 \author[Alberto F.\ Boix et al.]{Alberto F.\ Boix}
@@
 
-This paper describes methods for computing objects and numerical invariants in prime characteristic commutative algebra, implemented in the \texttt{TestIdeals.m2} package for the computer algebra system \emph{Macaulay2} \cite{M2}.
+This paper describes methods for computing objects and numerical invariants in prime characteristic commutative algebra, implemented in the package \emph{TestIdeals} for the computer algebra system \emph{Macaulay2} \cite{M2}.
 A ring $R$ of prime characteristic $p$ comes equipped with the Frobenius endomorphism
@@
 
-The \texttt{TestIdeals.m2} package was started during a \emph{Macaulay2} development workshop in 2012, hosted by Wake Forest University.
-The package, at that time called \texttt{PosChar.m2}, aimed at providing a unified and efficient set of tools to study singularities in characteristic $p > 0$, and in particular, collecting and implementing several algorithms that had been described in research papers.
-Since then, \texttt{PosChar.m2} was split into two packages, \texttt{TestIdeals.m2} and \texttt{FThresholds.m2}, and
+The \emph{TestIdeals} package was started during a \emph{Macaulay2} development workshop in 2012, hosted by Wake Forest University.
+The package, at that time called \emph{PosChar}, aimed at providing a unified and efficient set of tools to study singularities in characteristic $p > 0$, and in particular, collecting and implementing several algorithms that had been described in research papers.
+Since then, \emph{PosChar} was split into two packages, \emph{TestIdeals} and \emph{FThresholds}, and
 much more functionality has been added by many contributors, during several more \emph{Macaulay2} development workshops.\footnote{Development workshops hosted by the University of California, Berkeley (2014, 2017), Boise State University (2015), and the University of Utah (2016).}
@@
 The methods for computing test ideals and test modules that were used implicitly in papers such as \cite{BlickleSchwedeTakagiZhang,KatzmanLyubeznikZhangOnDiscretenessAndRationality,SchwedeTuckerTestIdealFiniteMaps} became implementable via the Frobenius roots functionality.
-Algorithms for computing $F$-pure thresholds from \cite{HernandezFInvariantsOfDiagonalHyp}, \cite{HernandezFPureThresholdOfBinomial}, and \cite{HernandezTeixeiraFThresholdFunctions} form some of the key methods in the forthcoming \texttt{FThresholds.m2} package.
+Algorithms for computing $F$-pure thresholds from \cite{HernandezFInvariantsOfDiagonalHyp}, \cite{HernandezFPureThresholdOfBinomial}, and \cite{HernandezTeixeiraFThresholdFunctions} form some of the key methods in the forthcoming \emph{FThresholds} package.
 %{\hfill\large\color{red} [Expand: how were the test module methods conceived?]}\\
@@
 \subsection*{Acknowledgements}
-The authors thank other contributors of the \texttt{TestIdeals.m2} package, namely
+The authors thank other contributors of the \emph{TestIdeals} package, namely
 Erin Bela, Juliette Bruce, Drew Ellingson, Matthew Mastroeni, and Maral Mostafazadehfard.
-This paper, and the finishing touches to the package \texttt{TestIdeals.m2}, were made at the University of Utah in 2018, and the visiting authors thank the Department of Mathematics for its hospitality.
+This paper, and the finishing touches to the \emph{TestIdeals} package, were made at the University of Utah in 2018, and the visiting authors thank the Department of Mathematics for its hospitality.
+The authors also thank the referees for their numerous useful comments on both this paper and the code.
 
@@
 \subsubsection{Complexity}
-The computation of Frobenius roots is the workhorse behind many of the methods in \texttt{TestIdeals.m2}.
+The computation of Frobenius roots is the workhorse behind many of the methods in \emph{TestIdeals}.
 Hence it is important to understand how this is implemented, and its computational complexity.
@@
 
-The \texttt{TestIdeals.m2} package includes methods for determining if a ring is $F$-injective, $F$-pure, $F$-rational, or $F$-regular.
+The \emph{TestIdeals} package includes methods for determining if a ring is $F$-injective, $F$-pure, $F$-rational, or $F$-regular.
 
@@
 We begin by computing the map $R
-\rightarrow R^{1/p}$ using the \texttt{PushForward.m2} package \cite{PushForward}.
+\rightarrow R^{1/p}$ using the \emph{PushForward} package \cite{PushForward}.
 Next the algorithm computes
@@
 The Frobenius action on top local cohomology (dual to $\omega_R$) is usually computed in a different (faster) way than the other cohomologies, and this is modified by the \texttt{CanonicalStrategy} option.
-The default value for this option is \texttt{Katzman}, which instead of using the \texttt{PushForward.m2} package, relies on the fact that we already know how to compute the Frobenius action on the canonical module, as described in \autoref{subsec.DualToFrobeniusOnQuotientRings}.
-
-%The \texttt{CanonicalStrategy} tag can be used to modify the strategy the
-%algorithm uses to check the Frobenius action on the top local cohomology.
-%By default the algorithm is set to \texttt{CanonicalStrategy => Katzman} which
-%then uses the strategy of Katzman {\hfill\large\color{red} [Add
-%references]}. If the tag is set to anything else \texttt{CanonicalStrategy =>
-%null} the algorithm checks the top local cohomology using the same brute
-%force strategy used to check the injectivity at lower degrees. The Katzman
-%strategy is typically much faster.
+The default value for this option is \texttt{Katzman}, which instead of using the \emph{PushForward} package, relies on the fact that we already know how to compute the Frobenius action on the canonical module, as described in \autoref{subsec.DualToFrobeniusOnQuotientRings}.
 
@@
 (which is typically much faster, as explained above).
-%The default value for the option \texttt{AssumeCM} is \texttt{false}.
-%Of
-%course, telling the algorithm to assume the ring is Cohen--Macaulay when it
-%is not can lead to an incorrect answer if the non-injective Frobenius
-%occurs in a lower degree. For an example of this see the documentation.
 When studying a reduced ring,  setting \texttt{AssumeReduced => true} (the default value) avoids
@@
 We hope to achieve all these things during a future \emph{Macaulay2} workshop.
-We also want to bring to the reader's attention the package \texttt{FThresholds.m2} which computes $F$-pure thresholds, $F$-thresholds, $F$-jumping numbers and more!
+We also want to bring to the reader's attention the package \emph{FThresholds}, which computes $F$-pure thresholds, $F$-thresholds, $F$-jumping numbers and more!
 

### 2019-06-03 Fsing/FThresholdsPaper/FThresholds.tex
Started the FThresholds paper.

--- 2019-05-24 Fsing/TestIdealsPaper/TestIdeals.tex
@@
 \begin{abstract}
-	This note describes a \emph{Macaulay2} package for computations in prime characteristic commutative algebra.  This includes Frobenius powers and roots, $p^{-e}$-linear and $p^{e}$-linear  maps,
-  singularities defined in terms of these maps, different types of test ideals and modules, and ideals compatible with a given $p^{-e}$-linear map.
+	This note describes a \emph{Macaulay2} package for computations of $F$(-pure) thresholds in characteristic $p > 0$ commutative algebra.  
 \end{abstract}
@@
 
-This paper describes methods for computing objects and numerical invariants in prime characteristic commutative algebra, implemented in the package \emph{TestIdeals} for the computer algebra system \emph{Macaulay2} \cite{M2}.
-A ring $R$ of prime characteristic $p$ comes equipped with the Frobenius endomorphism
-\[ F: R \to R \ \text{ given by } F(x) =  x^p,\]
-which is the basis for many constructions and methods.
-Notably, the Frobenius endomorphism can be used to detect whether a ring is regular \cite{KunzCharacterizationsOfRegularLocalRings}, and further, to quantify how far a ring is from being regular, measuring the severity of a singularity.
+This paper describes a Macaulay2 package which provides tools to compute, $F$-pure thresholds, $F$-thresholds and $F$-jumping numbers.  We begin with some history
 
-In this direction, two notable applications of the Frobenius endomorphism are the theory of tight closure
-(see \cite{HochsterHunekeTC1,HochsterFoundations} for an introduction)
-and the resulting theory of test ideals
-(see the survey \cite{SchwedeTuckerTestIdealSurvey}).  These methods are used by a wide group of commutative algebraists and algebraic geometers.
-%That said, it remains a fundamental tool in the expanding area of prime characteristic commutative algebra.
+{\it Acknowledgements}  The authors thank...
 
-The \emph{TestIdeals} package was started during a \emph{Macaulay2} development workshop in 2012, hosted by Wake Forest University.
-The package, at that time called \emph{PosChar}, aimed at providing a unified and efficient set of tools to study singularities in characteristic $p > 0$, and in particular, collecting and implementing several algorithms that had been described in research papers.
-Since then, \emph{PosChar} was split into two packages, \emph{TestIdeals} and \emph{FThresholds}, and
-much more functionality has been added by many contributors, during several more \emph{Macaulay2} development workshops.\footnote{Development workshops hosted by the University of California, Berkeley (2014, 2017), Boise State University (2015), and the University of Utah (2016).}
+\section{The $F$-pure threshold limit and {\tt nu}}
 
-%{\color{blue} [Maybe we don't need to list all examples?  Several other algorithms were implemented independently and incorporated into the package.]}
-Starting at least with Kunz \cite{KunzCharacterizationsOfRegularLocalRings} and Fedder \cite{FedderFPureRat}, it has been known that the Frobenius endormorphism offers \emph{effective} methods for measuring singularities in positive characteristic.
-However, the algorithms that form the basis of this package are the methods for computing Frobenius roots, $\star$-closures, and parameter test ideals.
-These first appeared in \cite{KatzmanParameterTestIdealOfCMRings,BlickleMustataSmithDiscretenessAndRationalityOfFThresholds,BlickleMustataSmithFThresholdsOfHypersurfaces,KatzmanFrobeniusMapsOnInjectiveHulls}.
-Another algorithm in \cite{KatzmanSchwedeAlgorithm} for computing prime ideals compatible with a given $p^{-e}$-linear map was implemented and used to produce the examples in that paper.
-The methods for computing test ideals and test modules that were used implicitly in papers such as \cite{BlickleSchwedeTakagiZhang,KatzmanLyubeznikZhangOnDiscretenessAndRationality,SchwedeTuckerTestIdealFiniteMaps} became implementable via the Frobenius roots functionality.
-Algorithms for computing $F$-pure thresholds from \cite{HernandezFInvariantsOfDiagonalHyp}, \cite{HernandezFPureThresholdOfBinomial}, and \cite{HernandezTeixeiraFThresholdFunctions} form some of the key methods in the forthcoming \emph{FThresholds} package.
-%{\hfill\large\color{red} [Expand: how were the test module methods conceived?]}\\
+Suppose $R = k[x_1, \dots, x_n]$ is a polynomial ring over a finite field and $f \in R$.
+If $f^a \notin \langle x_1^{p^e}, \dots, x_n^{p^e} \rangle = \fram^{[p^e]}$ then the pair $(R, f^{a/(p^e -1)})$ is $F$-pure at the origin, whereas if $f^a \in \fram^{[p^e]}$, then the pair $(R, f^{a/p^e})$ is not $F$-pure at the origin.
+By finding the $a \in \bZ$ where that transition happens, and then limiting over $e$, one can compute the $F$-pure threshold.
+See \cite{MustataTakagiWatanabeFThresholdsAndBernsteinSato}.
 
-\subsection*{Acknowledgements}
-The authors thank other contributors of the \emph{TestIdeals} package, namely
-Erin Bela, Juliette Bruce, Drew Ellingson, Matthew Mastroeni, and Maral Mostafazadehfard.
-This paper, and the finishing touches to the \emph{TestIdeals} package, were made at the University of Utah in 2018, and the visiting authors thank the Department of Mathematics for its hospitality.
-The authors also thank the referees for their numerous useful comments on both this paper and the code.
-
-\section{Frobenius powers and Frobenius roots}\label{Section: Frobenius powers and Frobenius roots}
-
-Let $R$ denote a commutative ring of prime characteristic $p$.
-
-\begin{definition}
-Given an ideal $I\subseteq R$ and an integer $e\geq 0$, we define the \emph{$p^e$-th Frobenius power of $I$}, denoted $I^{[p^e]}$, to be the ideal
-generated by the $p^e$-th powers of all elements of $I$.
-\end{definition}
-
-It is easy to see that if $I$ is generated by $g_1, \dots, g_\ell$, then $I^{[p^e]}$ is generated by $g_1^{p^e}, \dots, g_\ell^{p^e}$.
-
-\begin{definition}
-Given an ideal $I\subseteq R$ and an integer $e\geq 0$, we define the \emph{$p^e$-th Frobenius root of $I$}, denoted $I^{[1/p^{e}]}$, to be the smallest ideal $J$ such that $I\subseteq J^{[p^e]}$, if such an ideal exists.
-\end{definition}
-
-Frobenius roots always exist in polynomial and power series rings, and in $F$-finite regular rings
-(cf.~\cite[\S 2]{BlickleMustataSmithDiscretenessAndRationalityOfFThresholds} and \cite[\S 5]{KatzmanParameterTestIdealOfCMRings}).
-Below is an example of a computation of a Frobenius root in a polynomial ring.
-In \autoref{ss: math behind} we describe the main ideas behind such computations.
-
+We set $\nu(e, f)$ to be largest $a \in \bZ$ such that $f^a \notin \fram^{[p^e]}$ (note in the literature, it is frequently denoted by $\nu_f(p^e)$.  It immediately follows that 
+\[
+\fpt(f) = \lim_{e \to \infty} {\nu(e, f) \over p^e}.
+\]
+These numbers $\nu(e, f)$ can be computed using the command {\tt nu}, as in the example below.  
 \medskip
@@
 \begin{MyVerbatim}
-i1 : R = ZZ/5[x,y,z];
+i1 : loadPackage "FThresholds"
 
-i2 : I = ideal(x^6*y*z + x^2*y^12*z^3 + x*y*z^18);
+o1 = FThresholds
 
-o2 : Ideal of R
+o1 : Package
 
-i3 : frobeniusPower(1/5, I)
+i2 : R = ZZ/7[x,y]
 
-                2   3
-o3 = ideal (x, y , z )
+o2 = R
 
-o3 : Ideal of R
+o2 : PolynomialRing
+
+i3 : f = y^2 - x^3
+
+        3    2
+o3 = - x  + y
+
+o3 : R
+
+i4 : nu(1, f)
+
+o4 = 5
+
+o4 : QQ
+
+i5 : nu(2, f)
+
+o5 = 40
+
+o5 : QQ
+
+i6 : nu(3, f)
+
+o6 = 285
+
+o6 : QQ
 \end{MyVerbatim}
@@
 \medskip
+The numbers $5/7, 40/49, 285/343$ then approximate the $F$-pure threshold, which in this case happens to equal $5/6$.
+By default, if the function $f$ has a special form (is diagonal or binomial), then the function does not check whether $f^a$ is in  $\langle x_1^{p^e}, \dots, x_n^{p^e} \rangle$, but instead uses general formulas for $\nu$s, see \cite{HernandezFPureThresholdOfBinomial,HernandezFInvariantsOfDiagonalHyp}.
 
-\subsection{The mathematics behind the computation of Frobenius roots}
-\label{ss: math behind}
+In fact, one can make the following more general definition.  If $I$ and $J$ are two ideals (with $I \subseteq \sqrt{J}$), one can define
+\[
+\nu(e, I, J) = \max \{ n \in \bZ \; |\; I^n \not\subseteq J^{[p^e]} \}.
+\]
+This is frequently denoted by $\nu_I^J(p^e)$ in the literature.
+In the case that $I = \langle f \rangle$ and $J = \fram$, this just recovers the $\nu$'s defined above; the limit of which is the $F$-pure threshold.
+For more general $I$ and $J$, the limit
+\[
+\lim_{e \to \infty} {\nu(e, I, J) \over p^e}
+\]
+is called the \emph{$F$-threshold of $I$ with respect to $J$}.
+To compute these values we use a binary search, unless the user specifies that we should use a linear search instead {\tt Search=>Linear}.
 
-We can also describe Frobenius roots as follows:  In a (sufficiently local) regular ring, we have an identification of $R$ with its canonical module $\omega_R$.
-On the other hand, the Grothendieck dual to the $e$-iterated Frobenius map\footnote{In a reduced ring $R$, it is often convenient to express the Frobenius endomorphism $R \to R$ as the inclusion $R \hookrightarrow R^{1/p}$, so that the source and target  are distinguished.} $R \to R^{1/p^e}$ provides a map
-\begin{equation}
-\label{eq.DualToFrobenius}
-T : \omega_{R^{1/p^e}} \to \omega_R,
-\end{equation}
-which using the identification $R \cong \omega_R$ gives us a map
+There is one more option that deserves mentioning, {\tt ContainmentTest}.  There are two ways to check whether $f^a$ (or $I^a$) is contained in $J^{[p^e]}$.  In general it is true that
 \[
-T : R^{1/p^e} \to R.
+I^a \subseteq J^{[p^e]} \text{ $\Leftrightarrow$ } (I^a)^{[1/p^e]} \subseteq J
 \]
-It is not difficult to prove that
-$T(I^{1/p^e})=I^{[1/p^e]}$,
-where $I^{1/p^e} \subseteq R^{1/p^e}$ is simply the ideal of $p^e$-th roots of the elements of $I$.
-In the case that
+where $\bullet^{[1/p^e]}$ is defined as in the {\tt TestIdeals} package.  These are controlled by {\tt ContainmentTest => StandardPower} and {\tt ContainmentTest => FrobeniusRoot} respectively.
+For principal $I$, the command on the right is generally faster (and so {\tt FrobeniusRoot} is the default strategy for computing $\nu$).
+For non-principal $I$, frequently the command on the left is quicker, and so {\tt StandardPower} is default strategy.
+
+Finally, the option {\tt ContainmentTest => FrobeniusPower}, then ${\tt \nu(e, I, A)}$ computes the largest integer $n$ such that
 \[
-R = \mathbb{K}[x_1, \ldots, x_d],
+I^{[p^n]} \subseteq J^{[p^e]}.
 \]
-where $\mathbb{K}$ is a perfect field,
-$R^{1/p^e}$ is a free $R$-module with basis consisting of the monomials
+See \cite{HernandezTeixeiraWittFrobeniusPowers} for more discussion of this.
+
+\section{{\tt isFPT} and {\tt isFJumpingExponent}}
+
+The command {\tt isFPT(t, f)} checks whether $t$ is the $F$-pure threshold of $f$.  In general this does this by computing two test ideals:
 \[
-\mathbf{x}^{\boldsymbol{\lambda}/p^e}= x_1^{\lambda_1/p^e} \cdots x_d^{\lambda_d/p^e},
+\tau(R, f^t) \text{ and } \tau(R, f^{t-\epsilon}).
 \]
-where $0 \leq \lambda_i \leq p^e-1$.
-Furthermore, the map $T : R^{1/p^e} \to R$ is simply the projection defined as follows:
+It follows that $\fpt(f) = t$ if and only if $\tau(R, f^t) \neq R$ and $\tau(R, f^{t-\epsilon}) = R$.
+The function computes these two values by using the {\tt testIdeal} and {\tt FPureModule} commands from the {\tt TestIdeals} package.
+Note that in a strongly $F$-regular Gorenstein ambient ring, {\tt FPureModule(t, f)} computes exactly $\tau(R, f^{t-\epsilon})$.
+These commands work more generally, but they \emph{only} currently work when $R$ is $\bQ$-Gorenstein with index not divisible by the characteristic $p > 0$.
+
+The command {\tt isFJumpingExponent} works similarly, a value $t$ is an $F$-jumping exponent if and only if
 \[
-T(x_1^{\lambda_1/p^e} \cdots x_d^{\lambda_d/p^e}) = \left\{ \begin{array}{rl} 1 &\text{if } \lambda_i = p^{e}-1 \text{ for all }i \\ 0 & \text{otherwise}  \end{array} \right.
+\tau(R, f^t) \neq \tau(R, f^{t-\epsilon}).  
 \]
-Using this, it is not difficult to see that if
-\begin{equation}
-\label{eqn1}
-f^{1/p^e} = \sum_{\boldsymbol{\lambda}} f_{\boldsymbol{\lambda}} \mathbf{x}^{\boldsymbol{\lambda} / p^e},
-\end{equation}
-where $\boldsymbol{\lambda}$ runs over the tuples $(\lambda_1, \dots, \lambda_d)$ with $0 \leq \lambda_j \leq p^e-1$, and $f_{\boldsymbol{\lambda}} \in R$, then
-$(f)^{[1/p^e]} = T( (f)^{1/p^e})$ is the ideal generated by the $f_{\boldsymbol{\lambda}}$.
-We can then compute $I^{[1/p^e]}$ for more general $I$ by linearity: if $I=(f_1,\ldots,f_m)$, then $I^{[1/p^e]}= \sum(f_i)^{[1/p^e]}$.
+Again, this command works as long as $R$ is $\bQ$-Gorenstein with index not divisible by $p$.
 
-\subsubsection{Complexity}
-The computation of Frobenius roots is the workhorse behind many of the methods in \emph{TestIdeals}.
-Hence it is important to understand how this is implemented, and its computational complexity.
+\section{\tt fpt}
 
-The computation of Frobenius roots of ideals reduces to the case of principal ideals, and its complexity grows linearly with the number of generators of the ideal.
-Furthermore the calculation of  $(f)^{[1/p^e]}$ reduces to finding the terms in the right hand side of (\ref{eqn1}), which essentially amounts to
-taking each term in $f$, computing the $p^e$-th root of its coefficient, and dividing the monomial exponent vector by $p^e$ with remainder.
-Hence the complexity of computing $(f)^{[1/p^e]}$ is proportional to the number of terms in $f$, and is independent of its degree.
-We emphasize that the calculation of Frobenius roots \emph{does not involve the calculation of Gr\"obner bases.}
+The core function in this package is the {\tt fpt} function.
 
-\subsection{Dual to Frobenius on quotient rings and Frobenius on top local cohomology}
-\label{subsec.DualToFrobeniusOnQuotientRings}
-For \emph{any} reduced ring $R$ with finite $e$-iterated Frobenius map identified with $R \hookrightarrow R^{1/p^e}$, we always have a map
-\[
-T_R : \omega_{R^{1/p^e}} \to \omega_R.
-\]
-At a maximal ideal $\fram$ of height $d$, this map is Matlis dual to the Frobenius map on $H^d_{\fram}(R)$.
-Hence we can study local cohomology by studying this map.
-If $R = S/I$, where $S$ is a polynomial ring over a finite field, we can implement this map \cite{FedderFPureRat, KatzmanParameterTestIdealOfCMRings}.
-We briefly explain the case of a hypersurface here.
-
-If $I = (f)$, then again $\omega_R \cong R = S/I$, and the action of $T_R$ can be computed on $S$.  In fact, if $\overline{J} \subseteq R \cong \omega_R$ has preimage  $J \subseteq S$,
-then setting $u = f^{p^e-1}$, we have that $T_R({\overline J}^{1/p^e})$ is the image of $(u J)^{[1/p^e]}$ in $R$.
-More generally, for non-hypersurfaces, the analog to $u$ is chosen to be an element that maps onto the generator of the cyclic $R$-module
-\[
-\frac{(I^{[p^e]} : I) \cap (\Omega^{[p^e]} : \Omega)}{ I^{[p^e]}},
-\]
-where $\Omega$ is an ideal of $S$ with $I\subseteq \Omega$ and whose image in $R$ is isomorphic to the canonical module of $R$; see \cite{KatzmanParameterTestIdealOfCMRings} for details.
-Here we compute two examples.
-
-\medskip
-{\small\setstretch{.67}
-\begin{MyVerbatim}
-i1 : S = ZZ/5[x,y,z];
-
-i2 : f = x^3 + y^3 + z^3;
-
-i3 : u = f^(5 - 1);
-
-i4 : frobeniusRoot(1, ideal u)
-
-o4 = ideal (z, y, x)
-
-o4 : Ideal of S
-
-i5 : S = ZZ/7[x,y,z];
-
-i6 : f = x^3 + y^3 + z^3;
-
-i7 : u = f^(7 - 1);
-
-i8 : frobeniusRoot(1, ideal u)
-
-o8 = ideal 1
-
-o8 : Ideal of S
-\end{MyVerbatim}
-}\medskip
-
-The above example has shown that the Frobenius map on top local cohomology of the cone over the Fermat elliptic curve is injective in characteristic $7$ (the dual map $\omega_{R^{1/p}} \to \omega_R$ is surjective) and not injective in characteristic $5$ (the dual map $\omega_{R^{1/p}} \to \omega_R$ is not surjective).
-
-\subsection{A generalization of Frobenius powers and roots}
-
-Let $R$ be an $F$-finite regular ring.
-We can extend the definition of Frobenius powers as follows.
-
-\begin{definition}[\cite{HernandezTeixeiraWittFrobeniusPowers}]
-Let  $I\subseteq R$ be an ideal.
-\begin{enumerate}
- \item[(a)] If $n$ is a positive integer with base $p$ expansion  $n=d_0 + d_1 p +  \dots + d_r p^r$, we define
-\[ I^{[n]}=I^{d_0} (I^{d_1})^{[p]} \cdots  (I^{d_r})^{[p^r]}.\]
- \item[(b)] If $t$ is a nonnegative rational number of the form $t = a/p^e$, we define  $I^{[t]} = {\big(I^{[a]}\big)}^{[1/p^e]}.$
- \item[(c)] If $t$ is any nonnegative rational number, and $\{a_n/p^{e_n}\}_{n\geq 1}$ is a sequence of rational numbers converging to $t$ from above, we define $I^{[t]}$
- to be the stable value of the non-decreasing chain of ideals $\{I^{[a_n/p^{e_n}]}\}_{n\geq 1}$.
-\end{enumerate}
-\end{definition}
-
-\medskip
-{\small\setstretch{.67}
-\begin{MyVerbatim}
-i1 : p = 3;
-
-i2 : R = ZZ/p[x,y];
-
-i3 : m = monomialIdeal(x, y);
-
-o3 : MonomialIdeal of R
-
-i4 : I = m^5;
-
-o4 : MonomialIdeal of R
-
-i5 : t = 3/5 - 1/(5*p^3);
-
-i6 : frobeniusPower(t, I)
-
-             2        2
-o6 = ideal (y , x*y, x )
-
-o6 : Ideal of R
-
-i7 : frobeniusPower(t - 1/p^5, I)
-
-o7 = ideal (y, x)
-
-o7 : Ideal of R
-\end{MyVerbatim}
-}
-\medskip
-
-The generalized Frobenius powers of an ideal are test ideals (see \autoref{Section: Test Ideals}) of sufficiently general linear combinations of generators of that ideal.
-Thus, the ideals computed above are test ideals of generic quintics in two variables in characteristic $p=3$, and these computations suggest that $\frac35-\frac1{5p^3}$ is a higher $F$-jumping exponent of such quintics, which is indeed the case for any $p\equiv 3 \bmod 5$ (see \cite{hernandez+etal.frobenius_examples}).
-To illustrate, compare the computations above with the following.
-
-\medskip
-{\small\setstretch{.67}
-\begin{MyVerbatim}
-i8 : S = ZZ/3[a..f,x,y];
-
-i9 : G = a*x^5 + b*x^4*y + c*x^3*y^2 + d*x^2*y^3 + e*x*y^4 + f*y^5;
-
-i10 : testIdeal(t, G)
-
-              2        2
-o10 = ideal (y , x*y, x )
-
-o10 : Ideal of S
-
-i11 : testIdeal(t - 1/p^5, G)
-
-o11 = ideal (y, x)
-
-o11 : Ideal of S
-\end{MyVerbatim}
-}
-\medskip
-
-\begin{caveat}
-   The computations of Frobenius powers with exponents whose denominators are not powers of the characteristic $p$ are often very slow, and in several instances it is more efficient to introduce more variables and compute the test ideal of a ``very general'' linear combination of the generators of the ideal, as above.
-   The code used for computations of Frobenius powers needs to undergo significant optimization.
-\end{caveat}
-
-\subsection{Frobenius  roots of submodules of free modules}
-
-Let $S$ be a polynomial ring or power series ring.
-Given a submodule $M$ of the free module $S^k$,
-%
-%\pedro{What are the assumptions on $S$ here?}
-%
-there is a smallest submodule $N$ of $S^k$ that contains $M$, for which $M\subseteq N^{[p^e]}$.
-Here,  $N^{[p^e]}$ is the submodule  of $S^k$ generated by the vectors of $N$ with all coordinates raised to the $p^e$-th power. (Cf.~\cite{KatzmanZhangAlgorithm}).
-Extending the previous definitions,
-we call this $N$ the $p^e$-th Frobenius root of $M$, and denote it by $M^{[1/p^e]}$.
-
-\begin{example}
-Let $R=\ZZ/p\ZZ[a,b,c,d]$, and consider the ideals $\mathfrak{m}=(a,b,c,d)$ and
-$$I= (a,b) \cap (a,c) \cap (c,d) \cap (c+d, a^3+b d^2).$$
-Then $R/I$ is a $3$-dimensional non-Cohen--Macaulay ring.
-Matlis Duality applied to $H^2_{\mathfrak{m}} (R/I)$ with its natural Frobenius map
-yields a $p^{-1}$-linear map $U$ on $\Ext^2_R(R/ I, R)$.
-%$\Ext^2(R/ I, R) \xrightarrow{U} \Ext^2(R/I, R)$.
-
-\medskip
-{\small\setstretch{.67}
-\begin{MyVerbatim}
-i1 : R = ZZ/2[a,b,c,d];
-
-i2 : I = intersect(ideal(a,b),ideal(a,c),ideal(c,d),ideal(c+d,a^3+b*d^2));
-
-o2 : Ideal of R
-
-i3 : f = inducedMap(R^1/I, R^1/frobenius(I));
-
-o3 : Matrix
-
-i4 : E2 = Ext^2(f, R^1)
-
-o4 = {-8}  | a4+abc2+abcd a2b            |
-     {-10} | a2cd3        a3cd+a3d2+bcd3 |
-
-o4 : Matrix
-
-i5 : target E2
-
-o5 = cokernel {-8}  | 0     a2 b2c2 |
-              {-10} | c2+d2 d4 a4d2 |
-
-                            2
-o5 : R-module, quotient of R
-
-i6 : source E2
-
-o6 = cokernel {-4} | 0   a  bc  |
-              {-5} | c+d d2 a2d |
-
-                            2
-o6 : R-module, quotient of R
-\end{MyVerbatim}
-}
-\medskip
-
-The Frobenius map on $H^2_{\mathfrak{m}} (R/I)$
-is injective if and only the image of
-$(\Image U)^{[1/p]}$ in $\Ext^2_R(R/ I, R)$
-as computed above is the whole of $R^2$.
-
-\medskip
-{\small\setstretch{.67}
-\begin{MyVerbatim}
-i7 : U = matrix entries E2;
-
-             2       2
-o7 : Matrix R  <--- R
-
-i8 : A = image matrix entries relations source E2;
-
-i9 : frobeniusRoot(1, image U)
-
-o9 = image {-2} | 1 0 0 |
-           {0}  | 0 d a |
-
-                             2
-o9 : R-module, submodule of R
-\end{MyVerbatim}
-}\medskip
-
-The calculation above shows that $R/I$ is not $F$-injective (cf. \autoref{Section: F-singularities}).
-Moreover, it shows that $H^2_{\mathfrak{m}} (R/I)\cong \Ann_{E^2} A^t$,
-where $E$ is the injective hull of $R_{\mathfrak{m}}/ {\mathfrak{m}} R_{\mathfrak{m}}$,
-and the Frobenius map on  $H^2_{\mathfrak{m}} (R/I)$ induced from Frobenius on $R$
-is given by $U^t \Theta$, where $\Theta$ is the induced Frobenius on $E$.
-The submodule of nilpotent elements in  $H^2_{\mathfrak{m}} (R/I)$ is
-given by $\Ann_{E^2} B^t$, where $B$ is the smallest submodule of $R^2$ containing $\Image A + \Image U$ such that $U  B \subseteq B^{[p]}$.
-The method \texttt{ascendModule} can be used to calculate  $B$ (see a detailed description of the similar method \texttt{ascendIdeal} in \autoref{Section: Test Ideals}).
-
-\medskip
-{\small\setstretch{.67}
-\begin{MyVerbatim}
-i10 : B = ascendModule(1, A, U)
-
-o10 = image | 0   a  bc  |
-            | c+d d2 a2d |
-
-                              2
-o10 : R-module, submodule of R
-\end{MyVerbatim}
-}\medskip
-
-\end{example}
-
-%\section{$p^{-e}$- and $p^{e}$-linear maps}\label{Section: p-linear maps}
-
-%\begin{definition}%{\hfill\large\color{red} [Add references]}\\
-%Let $M$ be an $S$-module and $e$ a nonnegative integer.
-%\begin{enumerate}
-% \item[(a)] A $p^{-e}$-linear map $\phi:M \rightarrow M$ is an additive map such that
-% $\phi(s^{p^e} m)= s\phi(m)$ for all $s\in S$ and $m\in M$.
-% \item[(b)] A $p^{e}$-linear map $\psi:M \rightarrow M$ is an additive map such that
-% $\phi(s m)= s^{p^e}\phi(m)$ for all $s\in S$ and $m\in M$.
-%\end{enumerate}
-%\end{definition}
-
-%The following two examples describe  prototypical
-%$p^{-e}$- and $p^{e}$-linear maps.
-%\begin{example}
-%For any $S$-module $M$, we can construct a new $S$-module $M^{1/p^e}$ with elements $\{  m^{1/p^e} \,|\,m\in M\}$ by defining
-%$m_1^{1/p^e} +  m_2^{1/p^e} =  (m_1 +  m_2)^{1/p^e}$ for all $m_1, m_2 \in M$ and
-%$s  m^{1/p^e}=  (s^{p^e} m)^{1/p^e}$ for all $m\in M$ and $s\in S$.
-
-%Consider any $\phi\in \Hom_S(M^{1/p^e}, M)$: if we identify $M^{1/p^e}$ with $M$ we can interpret $\phi$ as a $p^{-e}$-linear map.
-%\end{example}
-
-%\begin{example}
-%The $e$-th Frobenius map $f:S \rightarrow S$  raising elements to their $p^e$-th power is clearly $p^{e}$-linear.
-%Furthermore, for any ideal $I\subseteq S$ and $k\geq 0$, $f$ induces a $p^{e}$-linear map $H_I^k (S) \rightarrow H_I^k (S)$.
-%\end{example}
-
-%Let $R$ be a polynomial ring with irrelevant ideal $\mathfrak{m}$ and let $g$ be a nonzero element of $R$.
-%Let $E=E_{R_{\mathfrak{m}}}(R_{\mathfrak{m}}/\mathfrak{m})$ denote the injective hull of $R_{\mathfrak{m}}/\mathfrak{m}$.
-
-%The Frobenius map on $R$ induces a Frobenius map $S$ and on
-%$H^{\dim R-1}_{\mathfrak{m}} (S)=E_S(S/\mathfrak{m}S)=\Ann_E g$ and the kernel of this map is given by
-%$\Ann_E (g^{p-1}R)^{[1/p]}$ (cf.~\cite[\S 5]{KatzmanParameterTestIdealOfCMRings}).
-
-%Thus we see that the induced $p^{e}$-linear map on $H_{(x,y,z)}^{2} \left( \mathbb{K}[x,y,z]/(x^3+y^3+z^3) \right)$ is injective
-%when the characteristic of $\mathbb{K}$ is $7$ and non-injective when the characteristic is $5$.
-
-%\subsection{Implementation and complexity}
-
-%Let $R=\mathbb{K}[x_1, \dots, x_n]$ and fix $B$ to be $\mathbb{K}$-basis for $\mathbb{K}^{1/p^e}$.
-%It is not hard to see that $R^{1/p^e}$ is a free $R$-module with free basis
-%$$\left\{ b x_1^{\alpha_1/p^e} \dots x_n^{\alpha_n/p^e} \,|\, b \in B, 0\leq \alpha_1, \dots, \alpha_n < p^e \right\}.$$
-
-%\begin{proposition}(cf. \cite[\S 5]{KatzmanParameterTestIdealOfCMRings})
-%\begin{enumerate}
-%\item[(a)] If the ideal $I\subseteq R$ is generated by $g_1, \dots, g_k\in R$, then $I^{[1/p^e]}=\sum_{i=1}^k (g_i R)^{[1/p^e]}$.
-%\item[(b)] If
-%\begin{equation}\label{eqn1}
-%g=\sum_{b\in B, \atop{0\leq \alpha_1, \dots, \alpha_n < p^e}} r_{b, \alpha_1, \dots, \alpha_n} \left(b x_1^{\alpha_1/p^e} \dots x_n^{\alpha_n/p^e}\right),
-%\end{equation}
-%then $(gR)^{[1/p^e]}$ is generated by $\{ r_{b, \alpha_1, \dots, \alpha_n} \,|\, b\in B, 0\leq \alpha_1, \dots, \alpha_n < p^e \}$.
-%\end{enumerate}
-%\end{proposition}
-
-\section{$F$-singularities}\label{Section: F-singularities}
-
-The \emph{TestIdeals} package includes methods for determining if a ring is $F$-injective, $F$-pure, $F$-rational, or $F$-regular.
-
-\subsection{$F$-injectivity}
-
-\begin{definition}
-A local ring $(R, \mathfrak{m})$ is called \emph{F-injective} if the map
-$H^{i}_{\mathfrak{m}}(R) \rightarrow H^{i}_{\mathfrak{m}}(R^{1/p})$ is
-injective for all $i >0$. An arbitrary ring is called \emph{$F$-injective} if its
-localization at each prime ideal of $R$ is $F$-injective.
-\end{definition}
-
-The function \texttt{isFInjective} determines whether the ring $R = S/I$ is
-$F$-injective, where $S$ is a polynomial ring.
-
-\medskip
-{\small\setstretch{.67}
-\begin{MyVerbatim}
-i1 : R = ZZ/7[x,y,z]/(x^3 + y^3 + z^3);
-
-i2 : isFInjective R
-
-o2 = true
-
-i3 : R = ZZ/5[x,y,z]/(x^3 + y^3 + z^3);
-
-i4 : isFInjective R
-
-o4 = false
-\end{MyVerbatim}
-}\medskip
-
-Equivalently, a ring is $F$-injective if the maps on the cohomology of the dualizing complex
-\[
-h^{-i} \omega_{R^{1/p}}^{\mydot} \to h^{-i} \omega_R^{\mydot}
-\]
-surject for all $i$.
-Note that $h^{-i} \omega_R^{\mydot} \cong \Ext^{\dim S - i}(R, S)$, the latter of which \emph{Macaulay2} readily computes.
-The algorithm used by \texttt{isFInjective} works by checking the surjectivity of the dual Frobenius map
-\[
-\Ext^{\dim S - i}(R^{1/p}, S) \to \Ext^{\dim S - i}(R, S).
-\]
-%using the fact that the Matlist dual of \Ext^{i}(\blank, S)$ \cong H^{\dim S -
-%i}_{\mathfrak{m}}(\blank) $.
-We begin by computing the map $R
-\rightarrow R^{1/p}$ using the \emph{PushForward} package \cite{PushForward}.
-Next the algorithm computes
-$\Ext^{i}( \blank, S)$ applied to the map from the previous step.  Then $R$ is $F$-injective precisely when the
-cokernel of $\Ext^{i}( \blank, S)$ is trivial for $i$.
-
-The Frobenius action on top local cohomology (dual to $\omega_R$) is usually computed in a different (faster) way than the other cohomologies, and this is modified by the \texttt{CanonicalStrategy} option.
-The default value for this option is \texttt{Katzman}, which instead of using the \emph{PushForward} package, relies on the fact that we already know how to compute the Frobenius action on the canonical module, as described in \autoref{subsec.DualToFrobeniusOnQuotientRings}.
-
-The performance of the algorithm can be improved if the ring of interest is
-nice enough. If the ring is Cohen--Macaulay, then setting \texttt{AssumeCM =>
-true} (the default value is \texttt{false}) lets the algorithm check the Frobenius action only on top cohomology
-(which is typically much faster, as explained above).
-When studying a reduced ring,  setting \texttt{AssumeReduced => true} (the default value) avoids
-computing the bottom local cohomology, and when studying a normal ring, setting
-\texttt{AssumeNormal => true} (the default is \texttt{false}) avoids computing the bottom two local
-cohomologies.
-
-By default the algorithm checks for $F$-injectivity at all points of $\Spec R$.  However, one
-can choose to check $F$-injectivity only at the origin by setting the
-option \texttt{IsLocal} to  \texttt{true}.
-
-\medskip
-{\small\setstretch{.67}
-\begin{MyVerbatim}
-i1 : R = ZZ/7[x,y,z]/((x - 1)^5 + (y + 1)^5 + z^5);
-
-i2 : isFInjective R -- R is not globally F-injective...
-
-o2 = false
-
-i3 : isFInjective(R, IsLocal => true) -- but is F-injective at the origin
-
-o3 = true
-\end{MyVerbatim}
-}\medskip
-
-\subsection{$F$-regularity}
-
-\begin{definition}[\cite{HochsterHunekeTC1,HaraWatanabeFRegFPure}]
-A ring $R$ is called \emph{strongly $F$-regular} if the (big) test ideal $\tau(R)$ is equal to $R$.  Likewise a pair $(R, f^t)$ is called \emph{strongly $F$-regular} if $\tau(R, f^t) = R$.
-\end{definition}
-
-The command \texttt{isFRegular} checks whether a ring or pair is strongly
-$F$-regular. Below are two examples, one of which is $F$-regular and the other one is not.
-
-\medskip
-{\small\setstretch{.67}
-\begin{MyVerbatim}
-i1 : R = ZZ/5[x,y,z]/(x^2 + y*z);
-
-i2 : isFRegular R
-
-o2 = true
-
-i3 : R = ZZ/7[x,y,z]/(x^3 + y^3 + z^3);
-
-i4 : isFRegular R
-
-o4 = false
-\end{MyVerbatim}
-}\medskip
-
-We can also check whether a pair $(R, f^t)$ is $F$-regular.
-
-\medskip
-{\small\setstretch{.67}
-\begin{MyVerbatim}
-i1 : R = ZZ/5[x,y];
-
-i2 : f = y^2 - x^3;
-
-i3 : isFRegular(1/2, f)
-
-o3 = true
-
-i4 : isFRegular(5/6, f)
-
-o4 = false
-
-i5 : isFRegular(4/5, f)
-
-o5 = false
-
-i6 : isFRegular(4/5 - 1/100000, f)
-
-o6 = true
-\end{MyVerbatim}
-}\medskip
-
-All of these checks are done by actually computing the test ideal, as described in \autoref{Section: Test Ideals}.
-
-If the input ring is $\mathbb{Q}$-Gorenstein, then in each of the cases above, the output is a boolean indicating if the
-ring is strongly $F$-regular. If the input ring is not
-$\mathbb{Q}$-Gorenstein, then the algorithm can be used to determine if a
-ring is strongly $F$-regular, but cannot prove that a ring is not strongly
-$F$-regular (this latter functionality can, however, be enabled by setting \texttt{QGorensteinIndex => infinity}).
-
-In the case that $R$ is $\mathbb{Q}$-Gorenstein, the algorithm works by
-computing the test ideal $\tau$ of the ring  (or the pair) using \texttt{testIdeal}
-and checking whether $\tau=R$.
-In the non-$\mathbb{Q}$-Gorenstein case, the algorithm checks for
-strong $F$-regularity by computing better and
-better approximations of the test ideal, and checking whether any of these is the unit ideal.
-To compute approximations of the
-test ideal, the algorithm computes a test element $c$ with \texttt{testElement}
-and then uses \texttt{frobeniusRoot} to compute the $e$-th root of
-$c(I^{[p^{e}]} : I)$; appropriate modifications are made for pairs. If at
-any step the approximation is the unit ideal, then then the algorithm
-returns \texttt{true}. Otherwise the algorithm continues checking for each $e$
-until a specified limit is reached. The default limit is 2, and can be
-changed using the option \texttt{DepthOfSearch}.
-
-A number of options can be used to speed up the performance of some of the
-internal functions. The option \texttt{AssumeDomain} can be used if $R$ is an
-integral domain, \texttt{FrobeniusRootStrategy} chooses a strategy for
-internal \texttt{frobeniusRoot} calls, \texttt{MaxCartierIndex} sets the
-maximum Gorenstein index to search for when working with a
-$\mathbb{Q}$-Gorenstein ambient ring, and \texttt{QGorensteinIndex}
-allows the user to specify the $\mathbb{Q}$-Gorenstein index of the ring.
-
-The default behavior of \texttt{isFRegular} is that it checks for strong $F$-regularity
-globally. If the option \texttt{IsLocal} is set to \texttt{true}, the algorithm will only
-check $F$-regularity at the origin, by checking whether the computed test ideal is in the irrelevant ideal.
-Below are examples for both a ring and a pair.
-
-\medskip
-{\small\setstretch{.67}
-\begin{MyVerbatim}
-i1 : R = ZZ/7[x,y,z]/((x - 1)^3 + (y + 1)^3 + z^3);
-
-i2 : isFRegular R -- R is not globally F-regular...
-
-o2 = false
-
-i3 : isFRegular(R, IsLocal => true) -- but is F-regular at the origin
-
-o3 = true
-
-i4 : R = ZZ/13[x,y];
-
-i5 : f = (y - 2)^2 - (x - 3)^3;
-
-i6 : isFRegular(5/6, f) -- (R,f^(5/6)) is not F-regular...
-
-o6 = false
-
-i7 : isFRegular(5/6, f, IsLocal => true) -- but is F-regular at the origin
-
-o7 = true
-\end{MyVerbatim}
-}\medskip
-
-\subsection{$F$-purity}
-\begin{definition}
-A ring $R$ is called \emph{$F$-pure} if
-the inclusion $R \hookrightarrow R^{1/p^{e}}$ is a pure map, i.e.,
-the tensor of this map with any $R$-module remains injective.
-If $R^{1/p}$ is a finite $R$-module, this is equivalent to requiring that the inclusion $R \hookrightarrow R^{1/p}$ split as a map of $R$-modules.
-\end{definition}
-
-The function \texttt{isFPure} checks whether a ring is $F$-pure.
-Either a ring or a defining ideal can be input, as seen in the following example.
-
-\medskip
-{\small\setstretch{.67}
-\begin{MyVerbatim}
-i1 : R = ZZ/5[x,y,z]/(x^2 + y*z);
-
-i2 : isFPure R
-
-o2 = true
-
-i3 : R = ZZ/7[x,y,z]/(x^3 + y^3 + z^3);
-
-i4 : isFPure R
-
-o4 = true
-
-i5 : S = ZZ/2[x,y,z];
-
-i5 : isFPure ideal(y^2 - x^3)
-
-o5 = false
-
-i6 : isFPure ideal(z^2 - x*y*z + x*y^2 + x^2*y)
-
-o6 = true
-\end{MyVerbatim}
-}\medskip
-
-The algorithm works by applying Fedder's Criterion {\cite{FedderFPureRat}}, which states that a
-local ring $(R, \mathfrak{m})$ is $F$-pure if and only if $(I^{[p]} : I)
-\not\subseteq \mathfrak{m}^{[p]}$.
-When \texttt{IsLocal} is set to \texttt{true}, the algorithm checks $F$-purity only at the origin, by explicitly checking the above
-containment. When \texttt{IsLocal} is set to \texttt{false}, which is its default value, the
-algorithm computes the non $F$-pure locus, by applying \texttt{frobeniusRoot}
-to $I^{[p]} :I$. If the non $F$-pure locus is the whole ring, the algorithm
-returns \texttt{true}.
-
-\subsection{$F$-rationality}
-
-\begin{definition}
-Suppose that $R$ is a Cohen--Macaulay ring and that $T_{R} :
-\omega_{R^{1/p}} \rightarrow \omega_{R}$ is the canonical dual to the
-Frobenius. We say that $R$ has \emph{$F$-rational singularities}, of simply that \emph{$R$ is $F$-rational}, if there
-are no non-zero proper submodules $M$ of $\omega_{R}$ such that
-$T_{R}(M^{1/p}) \subseteq M$.
-\end{definition}
-
-The command \texttt{isFRational} checks if a ring is $F$-rational.
-
-\medskip
-{\small\setstretch{.67}
-\begin{MyVerbatim}
-i1 : S = ZZ/3[a,b,c,d,t];
-
-i2 : M = matrix{{ a^2 + t^4, b, d }, { c, a^2, b^3 - d }};
-
-             2       3
-o2 : Matrix S  <--- S
-
-i3 : I = minors(2, M);
-
-o3 : Ideal of S
-
-i4 : R = S/I;
-
-i5 : isFRational R
-
-o5 = true
-\end{MyVerbatim}
-}\medskip
-
-The algorithm used by \texttt{isFRational} first checks if the ring is Cohen--Macaulay, unless the option \texttt{AssumeCM} is set to \texttt{true}. If the ring
-is not Cohen--Macaulay then \texttt{false} is returned. Next, the algorithm
-computes the test module $M \subseteq \omega_{R}$ and checks to see if
-$\omega_{R} \subseteq M$;  see the next section for the description of a test module.
-
-The options \texttt{AssumeDomain} and \texttt{FrobeniusRootStrategy} can be
-used to improve the speed of the \texttt{testModule} computation. By default,
-these options are set to \texttt{false} and \texttt{Substitution}, respectively.
-Finally, if \texttt{IsLocal} is set to \texttt{true}, then $F$-rationality is checked only at the origin.
-
-\section{Test ideals}\label{Section: Test Ideals}
-
-In this section, we explain how to compute parameter test modules, parameter test ideals, test ideals, and HSLG modules\footnote{HSLG modules can be used to give a scheme structure to the $F$-injective or $F$-pure locus.}.
-
-\subsection{Parameter test modules}
-%
-%\pedro{Are we assuming here that $R$ is a quotient of a polynomial ring?}
-%
-Given a reduced ring $R$ of finite type over a perfect field $k$, the Frobenius map $R \hookrightarrow R^{1/p^e}$ is dual to $T : \omega_{R^{1/p^e}} \to \omega_R$.
-As in \autoref{subsec.DualToFrobeniusOnQuotientRings}, we can represent the canonical module $\omega_R \subseteq R$ as an ideal, we can write $R = S/I$, and so we can find an element $u \in S^{1/p^e}$ representing the map $T:\omega_{R^{1/p^e}} \to \omega_R$; see \autoref{subsec.DualToFrobeniusOnQuotientRings} or \cite{KatzmanParameterTestIdealOfCMRings}.
-
-\begin{definition}
-   The \emph{parameter test submodule} is the smallest submodule $M \subseteq \omega_R$ (and hence ideal of $R$, since $M \subseteq \omega_R \subseteq R$) that agrees generically with $\omega_R$ and that satisfies
-   %
-   %\pedro{What is the quantifier for $e$ here?}
-   %
-\[
-T (M^{1/p^e}) \subseteq M
-\]
-for some $e > 0$ (or equivalently for all $e > 0$).
-\end{definition}
-
-Using \emph{Macaulay2}, we can compute this using the \texttt{testModule} command as follows.
-
-\medskip
-{\small\setstretch{.67}
-\begin{MyVerbatim}
-i1 : R = ZZ/5[x,y,z]/(x^4 + y^4 + z^4);
-
-i2 : N = testModule R;
-
-i3 : N#0
-
-             2             2        2
-o3 = ideal (z , y*z, x*z, y , x*y, x )
-
-o3 : Ideal of R
-
-i4 : N#1
-
-o4 = ideal 1
-
-o4 : Ideal of R
-\end{MyVerbatim}
-}\medskip
-
-The output of \texttt{testModule} is a sequence, consisting of three items:
-\begin{enumerate}[(1)]
-\item The test module itself, given as an ideal of $R$.
-\item The canonical module that contains the test module, given as an ideal of $R$.
-(Note the representation of the canonical module as an ideal is not unique, it is only unique up to isomorphism, hence it is important to return this module as well).
-\item The element $u$ described above (not displayed above, since it takes a lot of space).
-\end{enumerate}
-
-Note since this ring is Gorenstein, the canonical module is simply represented as the unit ideal. Here is another example, where the ring is not Gorenstein.
-
-\medskip
-{\small\setstretch{.67}
-\begin{MyVerbatim}
-i1 : R = ZZ/5[x,y,z]/(y*z, x*z, x*y);
-
-i2 : N = testModule R;
-
-i3 : N#0
-
-             2   2   2
-o3 = ideal (z , y , x )
-
-o3 : Ideal of R
-
-i4 : N#1
-
-o4 = ideal (y + 2z, x - z)
-
-o4 : Ideal of R
-\end{MyVerbatim}
-}\medskip
-
-We briefly explain how this is computed:  First, we find a \emph{test element}.
-\begin{remark}[Computation of test elements]
-\label{rem.ComputationOfTestElements}
-We recall that, roughly, an element of the Jacobian ideal that is not contained in any minimal prime is a test element \cite{HochsterFoundations}.
-We compute test elements by computing random partial derivatives (and linear combinations thereof) until we find an element that does not vanish at all the minimal primes.
-This method is much faster than computing the entire Jacobian ideal.
-If it is known that the ring is a domain, setting \texttt{AssumeDomain => true} can speed this up further.
-\end{remark}
-
-After the test element $c$ has been identified, we pull back the ideal $\omega_R$ to an ideal $J \subseteq S$.  Next, we compute the following ascending sequence of ideals:
-\begin{equation}
-\label{eq.AscendIdealExplanation}
-\begin{array}{lll}
-J_1 &\colonequals   J + (c J)^{[1/p]} & \\
-J_2 &\colonequals   J_1 + (c J_1)^{[1/p]} & = J + (c J)^{[1/p]} + (c^{1+p} J)^{[1/p^2]} \\
-J_3 &\colonequals    J_2 + (cJ_2)^{[1/p]} & = J + (c J)^{[1/p]} + (c^{1+p} J)^{[1/p^2]} + (c^{1+p+p^2} J)^{[1/p^3]} \\
-\vdots
-\end{array}
-\end{equation}
-As soon as this ascending sequence of ideals stabilizes, we are done.
-In fact, because this strategy is used in several contexts, the user can call it directly for a chosen ideal $J$ and $u$ with the function \texttt{ascendIdeal} (this is done for test ideals below).
-
-We can also compute parameter test modules of pairs $(\omega_R, f^{t})$ with $t \in \mathbb{Q}_{\geq 0}$.
-This is done by modifying the element $u$ when the denominator of $t$ is not divisible by $p$.
-When $t$ has $p$ in its denominator, we rely on the fact (see \cite{BlickleMustataSmithDiscretenessAndRationalityOfFThresholds,SchwedeTuckerTestIdealFiniteMaps}) that
-\[
-\begin{array}{rcl}
-T(\tau(\omega_R, f^a)) & = & \tau(\omega_R, f^{a/p})\\
-{\tt frobeniusRoot(1, u*I_1)} & {\tt =} & {\tt I_2}
-\end{array}
-\]
-where the second line roughly explains how this is accomplished internally.
-Here ${\tt I_1}$ is $\tau(\omega_R, f^a)$ pulled back to $S$ and, likewise, $I_2$ defines $\tau(\omega_R, f^{a/p})$ modulo the defining ideal of $R$.
-
-\begin{remark}[Optimizations in \texttt{ascendIdeal} and other \texttt{testModule} computations]
-Throughout the computations described above, we very frequently use the following fact:
-\[
-(f^p \cdot J)^{[1/p]} = f \cdot (J^{[1/p]}).
-\]
-To access this enhancement, one should try to pass functions like \texttt{ascendIdeal} and \texttt{frobeniusRoot} the elements and their exponents (see the documentation).
-In particular, when computing the $p^e$-th Frobenius root of an ideal of the form $f^n \cdot J$, one should not multiply out $f^n$ and $J$, nor even raise $f$ to the $n^\mathrm{th}$ power, but rather call \texttt{frobeniusRoot(e, n, f, J)}.
-\end{remark}
-
-\subsection{Parameter test ideals}
-
-The parameter test ideal is simply the annihilator of $\omega_R/\tau(\omega_R)$.  In other words, it is
-\[
-( \tau(\omega_R) : \omega_R ).
-\]
-This can also be described as
-\[
-\bigcap_{I} (I^* : I),
-\]
-where $I$ varies over ideals defined by a partial system of parameters, and $I^*$ denotes its tight closure.  This latter description is not computable, however.
-
-\begin{example}\label{Example: parameter test ideal}
-In this example we repeat the calculation in \cite[\S 9]{KatzmanParameterTestIdealOfCMRings}.
-
-\medskip
-{\small\setstretch{.67}
-\begin{MyVerbatim}
-i1 : R = ZZ/2[a..e];
-
-i2 : E = matrix {{a, b, b, e}, {d, d, c, a}};
-
-             2       4
-o2 : Matrix R  <--- R
-
-i3 : I = minors(2, E);
-
-o3 : Ideal of R
-
-i4 : S = R/I;
-
-i5 : J = parameterTestIdeal S
-
-o5 = ideal (c + d, b, a)
-
-o5 : Ideal of S
-
-i6 : J = substitute(J, R);
-
-o6 : Ideal of R
-
-i7 : mingens(J + I)
-
-o7 = | c+d b a de |
-
-             1       4
-o7 : Matrix R  <--- R
-\end{MyVerbatim}
-}\medskip
-
-\end{example}
-
-\subsection{Test ideals}
-
-For an $F$-finite reduced ring $R = S/I$, where $S$ is a regular ring, the (big) test ideal\footnote{The notion of test ideals was originally introduced in \cite{HochsterHunekeTC1} in the context of tight closure in finitely generated modules, whereas our notion of test ideals arises from
-tight closure in possibly non finitely generated (``big'') modules. Confusingly, big test ideals are included in (small) test ideals.}
-of $R$ is the smallest ideal $J$ in $R$, not contained in any minimal prime, such that for all $e > 0$ and all $\phi \in \Hom_R(R^{1/p^e}, R)$ we have
-\[ \phi(J^{1/p^e}) \subseteq J.\]
-In the case that $R$ is Gorenstein,
-$\Hom_R(R^{1/p^e}, R)$ is a cyclic $R^{1/p^e}$-module generated by
-$\Phi_e$, which corresponds with the map $T$ above based on the identification
-$\omega_R \cong R$ \cite{BlickleSchwedeSurveyPMinusE}.
-More generally, if $R$ is $\bQ$-Gorenstein with index not divisible by $p$, then for at least sufficiently divisible $e > 0$, such a generating $\Phi_e$ still exists.
-
-If such a $\Phi_e$ exists, it can be identified to a generator of the module $(I^{[p^e]} : I) / I^{[p^e]}$ by Fedder's Lemma \cite{FedderFPureRat}.
-Hence we can find a corresponding\footnote{This is done via the function \texttt{QGorensteinGenerator}.
-} $u \in I^{[p^e]} : I$.
-In this case, if $c \in S$ is the pre-image of a test element of $R$, then setting $I_0 = cR$, it follows that
-\[
-\tau(R) = {\tt ascendIdeal(e, u, I_0)},
-\]
-where \texttt{ascendIdeal} is the method explained above, in \autoref{eq.AscendIdealExplanation}.
-The $e$ here means all Frobenius roots are taken as multiples of $e$.  In other words, we first compute ${\tt I_0 +  (u \cdot I_0)^{1/p^{[e]}}}$.  Then we compute
-\[
-{\tt I_0 +  (u\cdot I_0)^{1/p^{[e]}} + (u^{p^e + 1} \cdot I_0)^{1/p^{[2e]}} }
-\]
-etc.
-
-Here is an example (a $\bZ/3\bZ$-quotient, where $3 | (7-1)$), where exactly this logic occurs.
-
-\medskip
-{\small\setstretch{.67}
-\begin{MyVerbatim}
-i1 : T = ZZ/7[x,y];
-
-i2 : S = ZZ/7[a,b,c,d];
-
-i3 : f = map(T, S, {x^3, x^2*y, x*y^2, y^3});
-
-i4 : I = ker f;
-
-i5 : R = S/I;
-
-i6 : testIdeal R
-
-o6 = ideal 1
-
-o6 : Ideal of R
-\end{MyVerbatim}
-}\medskip
-
-However, the term $u$ constructed above can be quite complicated if $e > 1$ (which happens exactly when $(p -1)K_R$ is not Cartier).
-For instance, even in the above example we have an extremely complex $u$:
-
-\medskip
-{\small\setstretch{.8}
-\begin{MyVerbatim}
-i7 : toString QGorensteinGenerator(1, R)
-
-o7 = a^2*b^6*c^12+a^3*b^4*c^13+a^3*b^5*c^11*d+a^4*b^3*c^12*d+a^5*b*c^13*d+b^
-     12*c^6*d^2+a^3*b^6*c^9*d^2+a^4*b^4*c^10*d^2+a^5*b^2*c^11*d^2+a^6*c^12*d
-     ^2+b^13*c^4*d^3+a*b^11*c^5*d^3+a^2*b^9*c^6*d^3+a^4*b^5*c^8*d^3+a^5*b^3*
-     c^9*d^3+a^6*b*c^10*d^3+a*b^12*c^3*d^4+a^2*b^10*c^4*d^4+a^3*b^8*c^5*d^4+
-     a^4*b^6*c^6*d^4+a^5*b^4*c^7*d^4+a^6*b^2*c^8*d^4+a^7*c^9*d^4+a*b^13*c*d^
-     5+a^2*b^11*c^2*d^5+a^3*b^9*c^3*d^5+a^4*b^7*c^4*d^5+a^5*b^5*c^5*d^5+a^6*
-     b^3*c^6*d^5+a^7*b*c^7*d^5+a^2*b^12*d^6+a^3*b^10*c*d^6+a^4*b^8*c^2*d^6+a
-     ^5*b^6*c^3*d^6+a^6*b^4*c^4*d^6+a^7*b^2*c^5*d^6+a^8*c^6*d^6+a^4*b^9*d^7+
-     a^5*b^7*c*d^7+a^6*b^5*c^2*d^7+a^7*b^3*c^3*d^7+a^8*b*c^4*d^7+a^6*b^6*d^8
-     +a^7*b^4*c*d^8+a^8*b^2*c^2*d^8+a^9*c^3*d^8+a^8*b^3*d^9+a^9*b*c*d^9+a^10
-     *d^10
-\end{MyVerbatim}
-}\medskip
-
-Therefore, we use a different strategy if either $(p-1)K_R$ is not Cartier or, more generally, if $R$ is $\bQ$-Gorenstein of index divisible by $p$.
-In these situations, this alternate strategy typically appears to be faster.  We rely on the observation (see \cite{BlickleSchwedeTuckerTestAlterations}) that
-\[
-\tau(\omega_R, K_R) \cong \tau(R).
-\]
-In fact, by embedding $\omega_R \subseteq R$, we can compute $g$ so that $\tau(\omega_R, K_R) = g\cdot \tau(R)$.  We can therefore find $\tau(R)$ if we can find $\tau(\omega_R, K_R)$.
-Next, if $K_R$ is $\bQ$-Cartier with $nK_R = \Div_R(f)$ for some $f \in R$ and $n > 0$, then
-\[
-\tau(\omega_R, K_R) =\tau(\omega_R, f^{1/n}).
-\]
-Thus we directly compute $\tau(\omega_R, f^{1/n})$ via the command \texttt{testModule(1/n, f)}.  Consider the following example, a $\mu_3$-quotient, which uses the logic described above.
-
-\medskip
-{\small
-\setstretch{.67}
-\begin{MyVerbatim}
-i1 : T = ZZ/3[x,y];
-
-i2 : S = ZZ/3[a,b,c,d];
-
-i3 : f = map(T, S, {x^3, x^2*y, x*y^2, y^3});
-
-o3 : RingMap T <--- S
-
-i4 : I = ker f;
-
-o4 : Ideal of S
-
-i5 : R = S/I;
-
-i6 : testIdeal R
-
-o7 = ideal 1
-
-o7 : Ideal of R
-\end{MyVerbatim}
-}\medskip
-
-\begin{remark}[Non-graded caveats]
-   It frequently happens that $(I^{[p^e]} : I)/I^{[p^e]}$ is principal but \emph{Macaulay2} cannot identify the principal generator (since \emph{Macaulay2} cannot always find minimal generators of non-graded ideals or modules).
-   The same thing can happen when computing the element $u$ corresponding to the map $T : \omega_{R^{1/p}} \to \omega_R$, as described in \autoref{subsec.DualToFrobeniusOnQuotientRings}.
-   In such situations, instead of a single $u$, \emph{Macaulay2} will produce $u_1, \dots, u_n$ (all multiples of $u$, and $u$ is a linear combination of the $u_i$).  Instead of computing the ideal
-\[
-(u \cdot J)^{[1/p]},
-\]
-we compute
-\[
-(u_1 \cdot J)^{[1/p]} + \dots + (u_n \cdot J)^{[1/p]},
-\]
-which will produce the same answer.
-\end{remark}
-
-We can similarly use the \texttt{testIdeal} command to compute test ideals of pairs, $\tau(R, f^t)$, and even mixed test ideals, $\tau(R, f_1^{t_1} \cdots f_n^{t_n})$.
-
-\subsection{HSLG module; computing $F$-pure submodules of rank-1 Cartier modules}
-
-Again, consider the maps $T^e : \omega_{R^{1/p^e}} \to \omega_R$ we have considered throughout this section.
-It is a theorem of Hartshorne-Speiser, Lyubeznik, and Gabber \cite{HartshorneSpeiserLocalCohomologyInCharacteristicP,LyubeznikFModulesApplicationsToLocalCohomology,Gabber.tStruc} that the descending images
-\begin{equation}\label{eq: descending images}
-\omega_R \supseteq T(\omega_{R^{1/p}}) \supseteq \dots \supseteq T^e(\omega_{R^{1/p^e}}) \supseteq T^{e+1}(\omega_{R^{1/p^{e+1}}}) \supseteq \cdots
-\end{equation}
-stabilize for $e \gg 0$.
-The function \texttt{FPureModule} computes the stable submodule in this chain, called the \emph{HSLG module}, and returns a sequence containing the following items:
-\begin{enumerate}[(1)]
-   \item The HSLG module;
-   \item The canonical module, embedded (non-uniquely) as an ideal;
-   \item The element $u$ representing the map on the canonical module (see
-   \autoref{subsec.DualToFrobeniusOnQuotientRings});
-   \item The value of $e > 0$ at which the descending images in \eqref{eq: descending images} stabilize.  This is sometimes also called the HSLG number of the canonical module as a Cartier module.
-\end{enumerate}
-
-\medskip
-{\small
-\setstretch{.67}
-\begin{MyVerbatim}
-i1 : R = ZZ/3[x,y,z]/(x^3 + y^4 + z^5);
-
-i2 : L = FPureModule R;
-
-i3 : L#0
-
-                       2        2   3
-o3 = ideal (y*z, x*z, y , x*y, x , z )
-
-o3 : Ideal of R
-
-i4 : L#1
-
-o4 = ideal 1
-
-o4 : Ideal of R
-
-i5 : L#3
-
-o5 = 1
-
-i6 : R = ZZ/3[x,y,z]/(x^3 + y^4 + z^5);
-
-i7 : L = FPureModule R;
-
-i8 : L#0
-
-                       2        2   3
-o8 = ideal (y*z, x*z, y , x*y, x , z )
-
-o8 : Ideal of R
-
-i9 : L#1
-
-o9 = ideal 1
-
-o9 : Ideal of R
-
-i10 : L#3
-
-o10 = 1
-\end{MyVerbatim}
-}\medskip
-
-%\bigskip\sout{In a Gorenstein ring, this submodule coincides philosophically with the maximal non-LC ideal of Fujino-Schwede-Takagi.}
-%\marginnote{Can someone explain this without recourse to philosophy or morality?}
-
-More generally, for any ideal $J$ with a map $\phi : J^{1/p^e} \to J$, we have that the images
-\[
-J \supseteq \phi(J^{1/p^e}) \supseteq \phi^2(J^{1/p^{2e}}) \supseteq \cdots
-\]
-stabilize as well (in fact, the analogous result even holds for modules \cite{Gabber.tStruc}).
-
-\subsection{Computing the level of a polynomial}
-Another interesting invariant that can be calculated using this package
-is the so--called \emph{level} of a polynomial; more precisely:
-
-\begin{definition}
-Let $K$ be an $F$--finite field of prime characteristic $p,$ and let
-$f\in R=K[x_1,\ldots, x_d].$ We define the \emph{level of} $f$ as the
-smallest possible integer $e$ where the descending chain
-\[
-R=(f^{p^0-1})^{[1/p^0]}\supseteq (f^{p-1})^{[1/p]}\supseteq
-(f^{p^2-1})^{[1/p^2]}\supseteq\ldots%\supseteq (f^{p^{i-1}-1})^{[1/p^{i-1}]}
-\supseteq (f^{p^i-1})^{[1/p^i]}\supseteq\ldots
-\]
-stabilizes.
-\end{definition}
-This invariant was introduced in \cite{AlvarezBlickleLyubeznik2005}.  It is also essentially the same data as the HSLG number of the pair $(R, f^1)$ as computed in (4) above (it is that number $+1$).
-One interesting particular
-case is when $K=\mathbb{F}_p$ and $f$ is the defining homogeneous polynomial of a hyperelliptic curve
-of genus $g;$ when $g=1,$ it was proved in
-\cite{BoixDeStefaniVanzo2015} that the corresponding elliptic curve defined by $f$
-is ordinary if and only if its level is $1,$ (equivalently, if and only if
-$(R/(f))_{(x,y,z)}$ is $F$--pure, %this was already proved by Takagi and Takahashi in \cite{TakTak08}
-) and supersingular if and only if its level is $2.$ When
-the genus is at least $2,$ level $2$ is a necessary (but not sufficient) condition for the curve
-for being ordinary \cite{BlancoBoixFordhamYilmaz2018}; in this case, one also
-has that, if the curve is supersingular, then its level has to be at least $3,$ so the level can
-always distinguish these two properties in any genus. We illustrate these results by means
-of the following examples.
-
-\medskip
-{\small
-\setstretch{.67}
-\begin{MyVerbatim}
-i1 : R = ZZ/2[x,y,z];
-
-i2 : f = x^3 + y^2*z + y*z^2;
-
-i3 : frobeniusPower(1/2, ideal f)
-
-o3 = ideal (z, y, x)
-
-o3 : Ideal of R
-
-i4 : u = f^3;
-
-i5 : frobeniusPower(1/4, ideal u)
-
-o5 = ideal (z, y, x)
-
-o5 : Ideal of R
-
-i6 : ((FPureModule(1, f))#3) + 1
-
-o6 = 2
-\end{MyVerbatim}
-}\medskip
-
-This shows that this elliptic curve has level $2,$ hence it is supersingular. The next example
-shows a non-ordinary hyperelliptic curve of genus $2$ with level $2$.
-
-\medskip
-{\small
-\setstretch{.67}
-\begin{MyVerbatim}
-i1 : R = ZZ/11[x,y,z];
-
-i2 : f = y^2*z^3 - x^5 - 2*z^5;
-
-i3 : frobeniusPower(1/11, ideal f^10)
-
-             2        3
-o3 = ideal (z , x*z, x )
-
-o3 : Ideal of R
-
-i4 : frobeniusPower(1/121, ideal f^120)
-
-             2        3
-o4 = ideal (z , x*z, x )
-
-o4 : Ideal of R
-
-i5 : ((FPureModule(1, f))#3) + 1
-
-o5 = 2
-\end{MyVerbatim}
-}\medskip
-
-\section{Ideals compatible with a given $p^{-e}$-linear map}\label{Section: compatible ideals}
-
-Throughout this section, let $R$ denote a polynomial $\mathbb{K}[x_1, \dots, x_n]$.
-In this section we address the following question:
-given a $R$-linear map $\phi: R^{1/p^e} \rightarrow R$, what are the ideals $I\subseteq R$ such that $\phi(I^{1/p^e})\subseteq I$?
-We call these ideals $\phi$-compatible.
-
-Recall that  $\Hom_R( R^{1/p^e}, R)$  is a principal $R^{1/p^e}$-module generated
-the \emph{trace map} $T\in \Hom_R(R^{1/p^e}, R)$, constructed as in \autoref{ss: math behind}, (cf. \cite[Lemma 1.6]{FedderFPureRat} and \cite[Example 1.3.1]{BrionKumarFrobeniusSplitting}).
-%If $B$ is a $\mathbb{K}$-basis for $\mathbb{K}^{1/p^e}$, with $1\in B$, then
-%$R^{1/p^e}$ is a free $R$-module with basis
-%$$\left\{ b\,  x_1^{\alpha_1/p^e} \cdots x_n^{\alpha_n/p^e} \,|\, 0\leq \alpha_1, \dots, \alpha_n < p^e, b\in B \right\} ;$$
-%the trace map $T$ is the projection onto the free summand
-%$R x_1^{(p^e-1)/p^e} \cdots x_n^{(p^e-1)/p^e}\cong R$.
-%
-%\pedro{This paragraph is a bit redundant; we could just refer to Section~\ref{ss: math behind}}
-%
-
-We can now write our given $\phi$ as multiplication by some $u^{1/p^e}$ followed by $T$ and it is not hard to see that
-an ideal $I\subseteq R$ is $\phi$-compatible if and only if $u I \subseteq I^{[p^e]}$.
-
-\begin{theorem}\label{Theorem: finitely many compatible primes}
-If $\phi$ is surjective, there are finitely many $\phi$-compatible ideals, consisting of all possible intersections
-of $\phi$-compatible prime ideals \textup(cf.\ \cite{KumarMehtaFiniteness}, \cite{SchwedeFAdjunction},
-\cite{SharpGradedAnnihilatorsOfModulesOverTheFrobeniusSkewPolynomialRing}, \cite{EnescuHochsterTheFrobeniusStructureOfLocalCohomology}\textup).
-In general, there are finitely many $\phi$-compatible prime ideals not containing $\sqrt{\Image \phi}$ \textup(cf.\ \cite{KatzmanSchwedeAlgorithm}\textup).
-
-\end{theorem}
-
-The method \texttt{compatibleIdeals} produces the finite set of $\phi$-compatible prime ideals in the second claim of \autoref{Theorem: finitely many compatible primes}.
-
-\medskip
-{\small
-\setstretch{.67}
-\begin{MyVerbatim}
-i1 : R = ZZ/3[u,v];
-
-i2 : u = u^2*v^2;
-
-i3 : compatibleIdeals u
-
-o3 = {ideal v, ideal (v, u), ideal u}
-
-o3 : List
-\end{MyVerbatim}
-}\medskip
-
-The defining condition $u I \subseteq I^{[p^e]}$ for $\phi$-compatible ideals allows us to
-think of these in a dual form: write $\mathfrak{m}=(x_1, \dots, x_n)$,
-$E=E_{R_\mathfrak{m}}(R_{\mathfrak{m}}/\mathfrak{m})=H^n_{\mathfrak{m}} (R)$, and let
-$\Theta: E \rightarrow E$ be the $p^e$-linear map\footnote{That is, $\Theta$ is additivive and $\Theta (r a)= r^{p^e} \Theta (a)$ for all $a\in E$ and $r\in R$.}
-induced from the Frobenius map on $R$.
-If $\psi=u \Theta$, then $\psi \Ann_E I \subseteq \Ann_E I$ if and only if $u I \subseteq  I^{[p^e]}$.
-Thus finding all $R$-submodules of $E$ compatible with $\psi=u \Theta$ also amounts to finding all
-$\phi$-compatible ideals, where $\phi=T \circ u^{1/p^e}$.
-
-\begin{example}
-We return to \autoref{Example: parameter test ideal}.
-In (cf.~\cite[\S 9]{KatzmanParameterTestIdealOfCMRings}) it is shown that
-there is a surjection $\Ann_E I \rightarrow H^2_{\mathfrak{m}} (R/I)$
-which is compatible  with the induced $p^1$-linear map on $H^2_{\mathfrak{m}} (R/I)$
-and the $p^1$-linear map $u \Theta$ on $\Ann_E I$, where $u$ is computed as follows.
-
-\medskip
-{\small
-\setstretch{.67}
-\begin{MyVerbatim}
-i1 : R = ZZ/2[a..f];
-
-i2 : E = matrix {{a, b, b, e}, {d, d, c, a}};
-
-             2       4
-o2 : Matrix R  <--- R
-
-i3 : I = minors(2, E);
-
-o3 : Ideal of R
-
-i4 : S = R/I;
-
-i5 : isCohenMacaulay S
-
-o5 = true
-\end{MyVerbatim}
-}\medskip
-
-In \cite{KatzmanParameterTestIdealOfCMRings} it is shown that as $R/I$ is Cohen--Macaulay, $u$
-can be taken as the generator of the cyclic module $(I^{[p]}:I) \cap (\Omega^{[p]}:\Omega)/I^{[p]}$
-where $\Omega \subseteq R$ is an ideal whose image in $R/I$ is a canonical module of that ring.
-
-\medskip
-{\small
-\setstretch{.67}
-\begin{MyVerbatim}
-i6 : omega = canonicalIdeal S
-
-o6 = ideal (e, d, a)
-
-o6 : Ideal of S
-
-i7 : omega = substitute(omega, R) + I;
-
-o7 : Ideal of R
-
-i8 : u = intersect((frobenius I):I, (frobenius omega) : omega);
-
-o8 : Ideal of R
-
-i9 : u = compress((gens u) % gens(frobenius I))
-
-o9 = | a3bc+a3bd+a2cde+abcde+abd2e+b2d2e+cd2e2+d3e2 |
-
-             1       1
-o9 : Matrix R  <--- R
-
-i10 :  u = first first entries u
-
-       3       3       2                         2     2 2       2 2    3 2
-o10 = a b*c + a b*d + a c*d*e + a*b*c*d*e + a*b*d e + b d e + c*d e  + d e
-
-o10 : R
-\end{MyVerbatim}
-}
-\medskip
-
-Now we can compute all annihilators of $R$-submodules of $E$ stable under the $p^1$-linear map $uT$.
-
-\medskip
-{\small
-\setstretch{.67}
-\begin{MyVerbatim}
-i11 : L = compatibleIdeals u;
-
-i12 : print \ L;
-
-       3       3       2                         2     2 2       2 2    3 2
-ideal(a b*c + a b*d + a c*d*e + a*b*c*d*e + a*b*d e + b d e + c*d e  + d e )
-
-               2
-ideal (a + b, a  + d*e)
-
-ideal (e, a, d)
-
-ideal (e, d, a, c)
-
-ideal (e, d, c, b, a)
-
-ideal (e, d, b, a)
-
-ideal (e, b, a)
-
-ideal (e, b, a, c + d)
-
-                      2
-ideal (c + d, a + b, b  + d*e)
-
-ideal (d, a)
-
-ideal (d, a, c)
-
-ideal (d, c, b, a)
-
-ideal (d, b, a)
-\end{MyVerbatim}
-}
-\medskip
-
-We can also compute  all annihilators of $R$-submodules of $H^2_{\mathfrak{m}} (R/I)$ stable under the $p^1$-linear map induced from the Frobenius map on $R/I$.
-
-\medskip
-{\small
-\setstretch{.67}
-\begin{MyVerbatim}
-i13 : print \ unique apply(L, J -> J : omega);
-
-       3       3       2                         2     2 2       2 2    3 2
-ideal(a b*c + a b*d + a c*d*e + a*b*c*d*e + a*b*d e + b d e + c*d e  + d e )
-
-               2
-ideal (a + b, b  + d*e)
-
-ideal (e, d, a)
-
-ideal 1
-
-ideal (e, b, a)
-
-ideal (e, c + d, b, a)
-
-                      2
-ideal (c + d, a + b, b  + d*e)
-
-ideal (d, a)
-
-ideal (d, c, a)
-
-ideal (d, c, b, a)
-
-ideal (d, b, a)
-\end{MyVerbatim}
-}
-\medskip
-
-\end{example}
-
-\section{Future plans}
-
-In \cite{KatzmanZhangAlgorithm}, the algorithms behind the methods in \autoref{Section: compatible ideals} were extended
-to compute prime annihilators of submodules of Artinian modules compatible with a given $p^{e}$-linear map.
-This would require, among other things, a faster implementation of our method for finding Frobenius roots of submodules of free modules.
-
-On the other hand, it should be possible to compute test ideals of pairs $(R, \fra^t)$ even when $\fra$ is not principal.
-One strategy to do this is outlined in \cite{SchwedeTuckerTestIdealsOfNonPrincipal} although certain improvement can be made.
-
-We hope to achieve all these things during a future \emph{Macaulay2} workshop.
-We also want to bring to the reader's attention the package \emph{FThresholds}, which computes $F$-pure thresholds, $F$-thresholds, $F$-jumping numbers and more!
+\section{}
 

### 2019-06-03 Fsing/FThresholdsPaper/FThresholds.tex
Small changes to the paper.

@@
 
-This paper describes a Macaulay2 package which provides tools to compute, $F$-pure thresholds, $F$-thresholds and $F$-jumping numbers.  We begin with some history
+This paper describes a Macaulay2 package which provides tools to compute, $F$-pure thresholds, $F$-thresholds and $F$-jumping exponents.
+Recall first that a ring $R$ is $F$-pure if the Frobenius morphism $F : R \to R$ is a pure morphism (under geometric hypotheses, this is equivalent to Frobenius being split).
+The notion of $F$-purity appeared first in the work of Hochster and Roberts in \cite{HochsterRobertsFrobeniusLocalCohomology}, was compared with rational singularities in \cite{FedderFPureRat} and was used globally to study properties of Schubert varieties in \cite{MehtaRamanathanFrobeniusSplittingAndCohomologyVanishing}.
+After the advent of tight closure \cite{HochsterHunekeTC1}, the usage of Frobenius to measure singularities proliferated and based on a tight connection discovered between $F$-pure and log canonical singularities \cite{HaraWatanabeFRegFPure}, the notion of $F$-purity was generalized to pairs $(R, f^t)$ where $f \in R$ and $t \in \bQ_{\geq 0}$ is a formal exponent.
+Along these lines the notion of the \emph{$F$-pure threshold} (or $\fpt$) was defined in analogy with the log canonical threshold (or $\lct$) \cite{TakagiWatanabeFPureThresh,MustataTakagiWatanabeFThresholdsAndBernsteinSato}.
+The $\fpt$ of $(R, f)$ is the supremum over all $t$ such that $(R, f^t)$ is $F$-pure, and the functionality computing this number is the core of this package.
+As a further generalization, the notion of \emph{$F$-threshold} was also introduced.
+All of these \emph{thresholds} have been the focus of intense study over the past 15 years.
 
-{\it Acknowledgements}  The authors thank...
+There are three main sections in this paper
+\begin{itemize}
+\item{} \autoref{sec.Nu} which describes how to first approximate the $\fpt$ and other $F$-thresholds.  
+\item{} \autoref{sec.IsFPT} describes functionality which can determine whether a given number is the FPT (or more generally, an $F$-jumping exponent).
+\item{} \autoref{sec.FPT} describes the {\tt fpt} function and how it works.
+\end{itemize}
+
+This package builds heavily upon the {\tt TestIdeals} package.
+
+{\it Acknowledgements}  The authors thank...  Thank the IMA...
 
 \section{The $F$-pure threshold limit and {\tt nu}}
+\label{sec.Nu}
 
@@
 
-\section{{\tt isFPT} and {\tt isFJumpingExponent}}
+\section{{\tt isFPT}, {\tt compareFPT} and {\tt isFJumpingExponent}}
+\label{sec.IsFPT}
 
@@
 These commands work more generally, but they \emph{only} currently work when $R$ is $\bQ$-Gorenstein with index not divisible by the characteristic $p > 0$.
+A more general version of this command is {\tt compareFPT(t, f)} which returns $-1$ if $t < \fpt(f)$, $0$ if $t = \fpt(f)$ and $1$ if $t > \fpt(f)$.
 
-The command {\tt isFJumpingExponent} works similarly, a value $t$ is an $F$-jumping exponent if and only if
+Consider the following example which has $F$-pure threshold equal to {1/2}, see \cite[Example 4.3]{MustataYoshidaTestIdealVsMultiplierIdeals}.
+\medskip
+{\small
+\setstretch{.67}
+\begin{MyVerbatim}
+i1 : loadPackage "FThresholds"
+
+o1 = FThresholds
+
+o1 : Package
+
+i2 : R = ZZ/2[x,y,z];
+
+i3 : f = x^2+y^5+z^5;
+
+i4 : isFPT(1/2, f)
+
+o4 = true
+
+i5 : isFPT(1/3, f)
+
+o5 = false
+
+i6 : compareFPT(3/4, f)
+
+o6 = 1
+\end{MyVerbatim}
+}
+\medskip
+
+The command {\tt isFJumpingExponent} is implemented similarly, a value $t$ is an $F$-jumping exponent if and only if
 \[
@@
 \section{\tt fpt}
+\label{sec.FPT}
 
 The core function in this package is the {\tt fpt} function.
+Given an element $f \in R = k[x_1, \dots, x_n]$, the {\tt fpt} function tries to compute the $F$-pure threshold of $f$.
+It does this in the following way:
 

### 2019-06-04 Fsing/FThresholdsPaper/FThresholds.tex

@@
 \usepackage{calc,amssymb,amsthm,amsmath,setspace}
-%\usepackage{mathtools}
 \RequirePackage[dvipsnames,usenames]{xcolor}
@@
 \input{kmacros3.sty}
-\usepackage{stmaryrd}
 
@@
 \usepackage{enumerate}
-
 \usepackage[normalem]{ulem}
 %\usepackage{marginnote}
-
-\DeclareMathOperator{\HH}{H}
 \newcommand{\fram}{\mathfrak{m}}
-%\DeclareMathOperator{\Image}{image}
-
 \DefineVerbatimEnvironment%
@@
 
-\renewcommand{\geq}{\geqslant}
-\renewcommand{\leq}{\leqslant}
-\renewcommand{\ge}{\geqslant}
-\renewcommand{\le}{\leqslant}
-
-\newtheorem*{caveat}{Caveat}
-
 \begin{document}
-\title{The  \emph{TestIdeals} package for \emph{Macaulay2}}
-\author[Alberto F.\ Boix et al.]{Alberto F.\ Boix}
-\address{Department of Mathematics, Ben-Gurion University of the Negev, Beer-Sheva 8410501, Israel}
-\email{fernanal@post.bgu.ac.il}
-\thanks{A.F.\,Boix was supported by Israel Science Foundation (grant No. 844/14) and Spanish Ministerio de Econom\'ia y Competitividad MTM2016-7881-P}
+\title{The  \emph{FThresholds} package for \emph{Macaulay2}}
+%\author[Alberto F.\ Boix et al.]{Alberto F.\ Boix}
+%\address{Department of Mathematics, Ben-Gurion University of the Negev, Beer-Sheva 8410501, Israel}
+%\email{fernanal@post.bgu.ac.il}
+%\thanks{A.F.\,Boix was supported by Israel Science Foundation (grant No. 844/14) and Spanish Ministerio de Econom\'ia y Competitividad MTM2016-7881-P}
 
@@
 
-\author[]{Zhibek Kadyrsizova}
-\address{School of Science and Technology, Nazarbayev University, Astana, 010000, Republic of Kazakhstan}
-\email{zhibek.kadyrsizova@nu.edu.kz}
-\thanks{Z. Kadyrsizova was partially supported by NSF DMS \#1401384 and the Barbour Scholarship at the University of Michigan.}
+%\author[]{Zhibek Kadyrsizova}
+%\address{School of Science and Technology, Nazarbayev University, Astana, 010000, Republic of Kazakhstan}
+%\email{zhibek.kadyrsizova@nu.edu.kz}
+%\thanks{Z. Kadyrsizova was partially supported by NSF DMS \#1401384 and the Barbour Scholarship at the University of Michigan.}
 
-\author[]{Mordechai Katzman}
-\address{Department of Pure Mathematics, University of Sheffield, Sheffield S37RH, United Kingdom}
-\email{M.Katzman@sheffield.ac.uk}
+%\author[]{Mordechai Katzman}
+%\address{Department of Pure Mathematics, University of Sheffield, Sheffield S37RH, United Kingdom}
+%\email{M.Katzman@sheffield.ac.uk}
 
-\author[]{Sara Malec}
-\address{Department of Mathematics, Hood College, Frederick, MD 21701}
-\email{malec@hood.edu}
+%\author[]{Sara Malec}
+%\address{Department of Mathematics, Hood College, Frederick, MD 21701}
+%\email{malec@hood.edu}
 
-\author[]{Marcus Robinson}
-\address{Department of Mathematics, University of Utah, Salt Lake City, UT~84112, USA}
-\email{robinson@math.utah.edu}
+%\author[]{Marcus Robinson}
+%\address{Department of Mathematics, University of Utah, Salt Lake City, UT~84112, USA}
+%\email{robinson@math.utah.edu}
 
@@
 
-\author[]{Daniel Smolkin}
-\address{Department of Mathematics, University of Utah, Salt Lake City, UT~84112, USA}
-\email{smolkin@math.utah.edu}
-\thanks{D.~Smolkin was supported by NSF RTG Grant DMS \#1246989, NSF CAREER Grant DMS \#1252860/1501102, and NSF FRG Grant DMS \#1265261/1501115.}
+%\author[]{Daniel Smolkin}
+%\address{Department of Mathematics, University of Utah, Salt Lake City, UT~84112, USA}
+%\email{smolkin@math.utah.edu}
+%\thanks{D.~Smolkin was supported by NSF RTG Grant DMS \#1246989, NSF CAREER Grant DMS \#1252860/1501102, and NSF FRG Grant DMS \#1265261/1501115.}
 
@@
 \begin{abstract}
-	This note describes a \emph{Macaulay2} package for computations of $F$(-pure) thresholds in characteristic $p > 0$ commutative algebra.  
+	This note describes a \emph{Macaulay2} package for computations of $F$-pure thresholds, more general $F$-thresholds, and other related numerical invariants, in prime characteristic commutative algebra.
 \end{abstract}
@@
 \]
-where $\bullet^{[1/p^e]}$ is defined as in the {\tt TestIdeals} package.  These are controlled by {\tt ContainmentTest => StandardPower} and {\tt ContainmentTest => FrobeniusRoot} respectively.
+where $\bullet^{[1/p^e]}$ is defined as in the {\tt TestIdeals} package.
+Which of these two strategies to use is controlled by the option {\tt ContainmentTest => StandardPower} and {\tt ContainmentTest => FrobeniusRoot} respectively.
 For principal $I$, the command on the right is generally faster (and so {\tt FrobeniusRoot} is the default strategy for computing $\nu$).
@@
 
-\section{\tt fpt}
+\newpage
+\section{The {\tt fpt} function}
 \label{sec.FPT}
@@
 The core function in this package is the {\tt fpt} function.
-Given an element $f \in R = k[x_1, \dots, x_n]$, the {\tt fpt} function tries to compute the $F$-pure threshold of $f$.
-It does this in the following way:
+Given a polynomial $f$ with coefficients in a finite field, the function {\tt fpt} attempts to find the exact value for the $F$-pure threshold of $f$ at the origin, and returns that value, if possible.
+Otherwise, it returns lower and upper bounds for the $F$-pure threshold, as demonstrated below.
 
-\section{}
+\medskip
+{\small
+\setstretch{.67}
+\begin{MyVerbatim}
+i1 : ZZ/5[x,y,z];
 
+i2 : fpt( x^3 + y^3 + z^3 + x*y*z )
+
+     4
+o2 = -
+     5
+
+o2 : QQ
+
+i3 : fpt( x^5 + y^6 + z^7 + (x*y*z)^3 )
+
+      1  2
+o3 = {-, -}
+      3  5
+
+o3 : List
+\end{MyVerbatim}
+}
+
+             If the option {\tt UseSpecialAlgorithms} is set to {\tt true} (the default value), then {\tt fpt} first checks whether $f$ is diagonal polynomial, a binomial, or a form in two variables, respectively.
+             If it is one of these, algorithms of Hern\'andez, or Hern\'andez and Teixeira, {\color{red}  References?} are executed to compute the $F$-pure threshold of $f$.
+
+\medskip
+{\small
+\setstretch{.67}
+\begin{MyVerbatim}
+i4 : fpt( x^17 + y^20 + z^24 ) -- a diagonal polynomial
+
+      94
+o4 = ---
+     625
+
+i5 : fpt( x^2*y^6*z^10 + x^10*y^5*z^3 ) -- a binomial
+
+      997
+o5 = ----
+     6250
+
+o5 : QQ
+
+i6 : ZZ/5[x,y];
+
+i7 : fpt( x^2*y^6*(x + y)^9*(x + 3*y)^10 ) -- a binary form in two variables
+
+      5787
+o7 = -----
+     78125
+
+o7 : QQ
+\end{MyVerbatim}
+}
+
+            The computation of the $F$-pure threshold of a binary form $f$ requires factoring $f$ into linear forms, and can sometimes hang when attempting that factorization.
+For this reason, when a factorization is already known, the user can pass to {\tt fpt} a list containing all the pairwise prime linear factors of $f$ and a list containing their respective multiplicities.
+
+\medskip
+{\small
+\setstretch{.67}
+\begin{MyVerbatim}
+i8 : L = {x, y, x + y, x + 3*y};
+
+i9 : m = {2, 6, 9, 10};
+
+i10 : fpt(L, m)==o7
+
+o10 = true
+\end{MyVerbatim}
+}
+
+The behavior of the {\tt fpt} function is more involved when no special algorithm is available, or {\tt UseSpecialAlgorithms} is set to {\tt false}.
+In the remainder of this section, we describe the behavior of the {\tt fpt} function in this case, as well as the roles of the options {\tt DepthOfSearch}, and {\tt Attempts}, both nonnegative integers.
+
+            When no special algorithm is available or , then function {\tt fpt} computes {\tt nu}$(e,f)$, where $e$ is the value of the option {\tt DepthOfSearch}, which conservatively defaults to $1$.
+            At this point, we know that the $F$-pure threshold of $f$ lies in the closed interval {\color{red} Elaborate here} [$\nu/(p^e-1),(\nu+1)/p^e$], and the subroutine {\tt guessFPT} is called to make some "educated guesses" in an attempt to find the $F$-pure threshold, or at least narrow down the above interval.
+	    The number of "guesses" is controlled by the option {\tt Attempts}, which conservatively defaults to 3.
+            If {\tt Attempts} is set to 0, {\tt guessFPT} is bypassed.
+            If  {\tt Attempts} is set to at least 1, then a first check is run to verify whether the right-hand endpoint $(\nu+1)/p^e$ of the above interval is the $F$-pure threshold.
+
+\begin{example}
+\[             f = x^2*(x + y)^3*(x + 3*y^2)^5;
+            fpt( f, Attempts => 0 ) -- a bad estimate
+            fpt( f, Attempts => 0, DepthOfSearch => 3 ) -- a better estimate
+            fpt( f, Attempts => 1, DepthOfSearch => 3 ) -- the right-hand endpoint (nu+1)/p^e is the fpt \] 
+\end{example}
+
+            If  {\tt Attempts} is set to at least 2 and the right-hand endpoint $(\nu+1)/p^e$ is not the $F$-pure threshold, a second check is run to verify whether the left-hand endpoint $\nu/(p^e-1)$ is the $F$-pure threshold.
+
+\begin{example}
+\[
+	    f = x^6*y^4 + x^4*y^9 + (x^2 + y^3)^3;
+            fpt( f, Attempts => 1, DepthOfSearch => 3 )
+            fpt( f, Attempts => 2, DepthOfSearch => 3 ) -- the left-hand endpoint nu/(p^e-1) is the fpt
+\]
+\end{example}
+
+            If neither endpoint is the $F$-pure threshold, and {\tt Attempts} is set to more than 2, additional checks are performed at numbers in the interval.
+            A number in the interval with minimal denominator is selected, and {\tt compareFPT} is used to test that number.
+            If that ``guess" is correct, its value is returned; otherwise, the information returned by {\tt compareFPT} is used to narrow down the interval, and this process is repeated as many times as specified by {\tt Attempts}.
+
+\begin{example}
+\[             f = x^3*y^11*(x + y)^8*(x^2 + y^3)^8;
+            fpt( f, DepthOfSearch => 3, Attempts => 2 )
+            fpt( f, DepthOfSearch => 3, Attempts => 3 ) -- an additional check sharpens the estimate
+            fpt( f, DepthOfSearch => 3, Attempts => 4 ) -- and one more finds the exact answer
+\]
+\end{example}
+
+            If {\tt guessFPT} is unsuccessful and {\tt UseFSignature} is set to {\tt true}, the fpt function proceeds to use the convexity of the $F$-signature function and a secant line argument to attempt to narrow down the interval bounding the $F$-pure threshold.
+
+\begin{example}
+\[             f = x^5*y^6*(x + y)^9*(x^2 + y^3)^4;
+            fpt( f, DepthOfSearch => 3 )
+            fpt( f, DepthOfSearch => 3, UseFSignature => true )
+            numeric ooo
+            numeric ooo -- UseFSignature sharpened the estimate a bit \]
+\end{example}
+
+            When {\tt FRegularityCheck} is set to {\tt true} and no exact answer has been found, a final check is run (if necessary) to verify whether the final lower bound for the $F$-pure threshold is the exact answer.
+
+\begin{example}
+\[             f = (x + y)^4*(x^2 + y^3)^6;
+            fpt( f, Attempts => 2, DepthOfSearch => 3 )
+            fpt( f, Attempts => 2, DepthOfSearch => 3, UseFSignature => true ) -- using FSignatures the answer improves a bit
+	    fpt( f, Attempts => 2, DepthOfSearch => 3, UseFSignature => true, FRegularityCheck => true ) -- FRegularityCheck finds the answer \] 
+\end{example}
+
+            The computations performed when {\tt UseFSignature} and {\tt FRegularityCheck} are set to {\tt true} are often slow, and often fail to improve the estimate, and for this reason, these options should be used sparingly.
+            It is often more effective to increase the values of {\tt Attempts} or {\tt DepthOfSearch}, instead.
+
+\begin{example}            
+\[            f = x^7*y^5*(x + y)^5*(x^2 + y^3)^4;
+	    timing numeric fpt( f, DepthOfSearch => 3, UseFSignature => true, FRegularityCheck => true )
+            timing numeric fpt( f, Attempts => 5, DepthOfSearch => 3 ) -- a better answer in less time
+            timing fpt( f, DepthOfSearch => 4 ) -- the exact answer in even less time
+\]
+\end{example}
+
+            As seen in several examples above, when the exact answer is not found, a list containing the endpoints of an interval containing the $F$-pure threshold of $f$ is returned.
+            Whether that interval is open, closed, or a mixed interval depends on the options passed; if the option {\tt Verbose} is set to {\tt true}, the precise interval will be printed.
+
+\begin{example}
+ \[           f = x^7*y^5*(x + y)^5*(x^2 + y^3)^4;
+            fpt( f, DepthOfSearch => 3, UseFSignature => true, Verbose => true )
+ \]
+  \end{example}
+
+\newpage
 \bibliographystyle{skalpha}

### 2019-06-04 Fsing/FThresholdsPaper/FThresholds.tex

@@
 
-This paper describes a Macaulay2 package which provides tools to compute, $F$-pure thresholds, $F$-thresholds and $F$-jumping exponents.
-Recall first that a ring $R$ is $F$-pure if the Frobenius morphism $F : R \to R$ is a pure morphism (under geometric hypotheses, this is equivalent to Frobenius being split).
-The notion of $F$-purity appeared first in the work of Hochster and Roberts in \cite{HochsterRobertsFrobeniusLocalCohomology}, was compared with rational singularities in \cite{FedderFPureRat} and was used globally to study properties of Schubert varieties in \cite{MehtaRamanathanFrobeniusSplittingAndCohomologyVanishing}.
-After the advent of tight closure \cite{HochsterHunekeTC1}, the usage of Frobenius to measure singularities proliferated and based on a tight connection discovered between $F$-pure and log canonical singularities \cite{HaraWatanabeFRegFPure}, the notion of $F$-purity was generalized to pairs $(R, f^t)$ where $f \in R$ and $t \in \bQ_{\geq 0}$ is a formal exponent.
-Along these lines the notion of the \emph{$F$-pure threshold} (or $\fpt$) was defined in analogy with the log canonical threshold (or $\lct$) \cite{TakagiWatanabeFPureThresh,MustataTakagiWatanabeFThresholdsAndBernsteinSato}.
-The $\fpt$ of $(R, f)$ is the supremum over all $t$ such that $(R, f^t)$ is $F$-pure, and the functionality computing this number is the core of this package.
+This paper describes the \emph{Macaulay2} package \emph{FThresholds}, which provides tools to compute $F$-pure thresholds, $F$-thresholds, and $F$-jumping exponents.
+Recall that a ring $R$ of prime characteristic $p>0$ is $F$-pure if the Frobenius morphism $F : R \to R$ is a pure morphism (under geometric hypotheses, this is equivalent to the Frobenius morphism being split).
+The notion of $F$-purity appeared first in the work of Hochster and Roberts in \cite{HochsterRobertsFrobeniusLocalCohomology}, was compared with rational singularities in \cite{FedderFPureRat}, and was used globally to study properties of Schubert varieties in \cite{MehtaRamanathanFrobeniusSplittingAndCohomologyVanishing}.
+
+After the advent of tight closure \cite{HochsterHunekeTC1}, the usage of Frobenius to measure singularities proliferated, and based on a tight connection discovered between $F$-pure and log canonical singularities \cite{HaraWatanabeFRegFPure}, the notion of $F$-purity was generalized to pairs $(R, f^t)$, where $f$ is an element of a ring $R$, and $t$ is a positive rational number $t$ considered as a formal exponent.
+Along these lines, the notion of the \emph{$F$-pure threshold} (or $\fpt$) was defined in analogy with the log canonical threshold (or $\lct$) \cite{TakagiWatanabeFPureThresh,MustataTakagiWatanabeFThresholdsAndBernsteinSato}.
+The $\fpt$ of $(R, f)$ is the supremum over all $t$ for which $(R, f^t)$ is $F$-pure, and the functionality computing this number is the core of this package.
 As a further generalization, the notion of \emph{$F$-threshold} was also introduced.
@@
 
-There are three main sections in this paper
+There are three main sections in this paper, describing the functionality implemented in the \emph{Macaulay2} package \emph{FThresholds}. 
 \begin{itemize}
-\item{} \autoref{sec.Nu} which describes how to first approximate the $\fpt$ and other $F$-thresholds.  
-\item{} \autoref{sec.IsFPT} describes functionality which can determine whether a given number is the FPT (or more generally, an $F$-jumping exponent).
-\item{} \autoref{sec.FPT} describes the {\tt fpt} function and how it works.
+\item{} \autoref{sec.Nu} describes methods to to approximate the $\fpt$, and other $F$-thresholds.  
+\item{} \autoref{sec.IsFPT} describes functionality that can determine whether a given number is the fpt, or more generally, an $F$-jumping exponent.
+\item{} \autoref{sec.FPT} describes the {\tt fpt} function, and how it works.
 \end{itemize}
 
-This package builds heavily upon the {\tt TestIdeals} package.
+This package builds heavily upon the \emph{TestIdeals} package, focused on computing test ideals and related objects in prime characteristic.
 
-{\it Acknowledgements}  The authors thank...  Thank the IMA...
+\noindent {\it Acknowledgements.}  The authors thank...contributors of the package...organizers of the M2 workshops...Karl's funding that funded the UU visit...
+We also extend an enthusiastic thank you to
 
@@
 Suppose $R = k[x_1, \dots, x_n]$ is a polynomial ring over a finite field and $f \in R$.
-If $f^a \notin \langle x_1^{p^e}, \dots, x_n^{p^e} \rangle = \fram^{[p^e]}$ then the pair $(R, f^{a/(p^e -1)})$ is $F$-pure at the origin, whereas if $f^a \in \fram^{[p^e]}$, then the pair $(R, f^{a/p^e})$ is not $F$-pure at the origin.
+If $f^a \notin \langle x_1^{p^e}, \dots, x_n^{p^e} \rangle = \fram^{[p^e]}$, then the pair $(R, f^{a/(p^e -1)})$ is $F$-pure at the origin, whereas if $f^a \in \fram^{[p^e]}$, then the pair $(R, f^{a/p^e})$ is not $F$-pure at the origin.
 By finding the $a \in \bZ$ where that transition happens, and then limiting over $e$, one can compute the $F$-pure threshold.

### 2019-06-04 Fsing/FThresholdsPaper/FThresholds.tex
updated intro to FThresholds paper

@@
 \begin{abstract}
-	This note describes a \emph{Macaulay2} package for computations of $F$-pure thresholds, more general $F$-thresholds, and other related numerical invariants, in prime characteristic commutative algebra.
+	This note describes a \emph{Macaulay2} package for the computation and estimation of certain numerical invariants arising in prime characteristic commutative algebr.
+Namely, $F$-pure thresholds, more general $F$-thresholds, and other related numerical invariants, in prime characteristic commutative algebra.
 \end{abstract}
@@
 
-This paper describes the \emph{Macaulay2} package \emph{FThresholds}, which provides tools to compute $F$-pure thresholds, $F$-thresholds, and $F$-jumping exponents.
-Recall that a ring $R$ of prime characteristic $p>0$ is $F$-pure if the Frobenius morphism $F : R \to R$ is a pure morphism (under geometric hypotheses, this is equivalent to the Frobenius morphism being split).
+This paper describes the \emph{Macaulay2} package \emph{FThresholds}, which provides tools for computing certain fundamental invariants arising in prime characteristic commutative algebra, namely, \emph{$F$-pure thresholds}, \emph{$F$-thresholds}, and \emph{$F$-jumping exponents}.
+Recall that a ring $R$ of prime characteristic $p>0$ is said to be \emph{$F$-pure} if the Frobenius morphism $F : R \to R$ sending an element to its $p^\text{th}$ power is a pure morphism (under geometric hypotheses, this is equivalent to the condition that the Frobenius morphism is split).
 The notion of $F$-purity appeared first in the work of Hochster and Roberts in \cite{HochsterRobertsFrobeniusLocalCohomology}, was compared with rational singularities in \cite{FedderFPureRat}, and was used globally to study properties of Schubert varieties in \cite{MehtaRamanathanFrobeniusSplittingAndCohomologyVanishing}.
 
-After the advent of tight closure \cite{HochsterHunekeTC1}, the usage of Frobenius to measure singularities proliferated, and based on a tight connection discovered between $F$-pure and log canonical singularities \cite{HaraWatanabeFRegFPure}, the notion of $F$-purity was generalized to pairs $(R, f^t)$, where $f$ is an element of a ring $R$, and $t$ is a positive rational number $t$ considered as a formal exponent.
+After the advent of tight closure \cite{HochsterHunekeTC1}, the usage of the Frobenius endomorphism to measure singularities proliferated, and based on a strong connection discovered between $F$-pure and \emph{log canonical} singularities \cite{HaraWatanabeFRegFPure}, the notion of $F$-purity was generalized to pairs $(R, f^t)$, where $f$ is an element of $R$, and $t$ is a positive rational number $t$ considered as a formal exponent.
 Along these lines, the notion of the \emph{$F$-pure threshold} (or $\fpt$) was defined in analogy with the log canonical threshold (or $\lct$) \cite{TakagiWatanabeFPureThresh,MustataTakagiWatanabeFThresholdsAndBernsteinSato}.
@@
 
-This package builds heavily upon the \emph{TestIdeals} package, focused on computing test ideals and related objects in prime characteristic.
+This package builds heavily upon the \emph{TestIdeals} package, which provides a broad range of functionality in prime characteristic commutative algebra.
 
-\noindent {\it Acknowledgements.}  The authors thank...contributors of the package...organizers of the M2 workshops...Karl's funding that funded the UU visit...
-We also extend an enthusiastic thank you to
+\noindent {\it Acknowledgements.}  First and foremost, the authors enthusiastically thank all contributors to the \emph{FThresholds} package:  Erin Bela, Juliette Bruce, Zhibek Kadyrsizova, Sara Malec, Maral Mostafazadehfard, Marcus Robinson, Dan Smolkin, and Robert Walker.
+We thank the organizers of the five \emph{Macaulay2} workshops where much of the functionality in the package was develope, hosted by Wake Forest University in 2012, the University of California, Berkeley in 2014 and 2017, Boise State University in 2015, and the University of Utah in 2016.
+Finally, we thank the University of Utah for hosting a collaborative development visit in 2018, and the Institute of Mathematics and its Applications for its support for a Coding Sprint in 2019, where the current version of the package was finalized and this paper was completed.
 

### 2019-06-04 Fsing/FThresholdsPaper/FThresholds.tex
More work on The fpt function'' section of the paper

--- 2019-06-04 Fsing/FThresholdsPaper/FThresholds.tex
@@
 The core function in this package is the {\tt fpt} function.
-Given a polynomial $f$ with coefficients in a finite field, the function {\tt fpt} attempts to find the exact value for the $F$-pure threshold of $f$ at the origin, and returns that value, if possible.
+Throughout this section, let $f$ be a polynomial with coefficients in a finite field of characteristic $p$.
+When passed the polynomial $f$, the function {\tt fpt} attempts to find the exact value for the $F$-pure threshold of $f$ at the origin, and returns that value, if possible.
 Otherwise, it returns lower and upper bounds for the $F$-pure threshold, as demonstrated below.
 
-\medskip
 {\small
@@
 \begin{MyVerbatim}
+
 i1 : ZZ/5[x,y,z];
@@
 o3 : List
+
 \end{MyVerbatim}
@@
 
-             If the option {\tt UseSpecialAlgorithms} is set to {\tt true} (the default value), then {\tt fpt} first checks whether $f$ is diagonal polynomial, a binomial, or a form in two variables, respectively.
+             If the option {\tt UseSpecialAlgorithms} is set to {\tt true} (the default value), then {\tt fpt} first checks whether $f$ is diagonal polynomial, a binomial, or a form in two variables, in that order.
              If it is one of these, algorithms of Hern\'andez, or Hern\'andez and Teixeira, {\color{red}  References?} are executed to compute the $F$-pure threshold of $f$.
 
-\medskip
 {\small
@@
 \begin{MyVerbatim}
+
 i4 : fpt( x^17 + y^20 + z^24 ) -- a diagonal polynomial
@@
 
-i7 : fpt( x^2*y^6*(x + y)^9*(x + 3*y)^10 ) -- a binary form in two variables
+i7 : fpt( x^2*y^6*(x + y)^9*(x + 3*y)^10 ) -- a form in two variables
 
@@
 o7 : QQ
+
 \end{MyVerbatim}
@@
 
-            The computation of the $F$-pure threshold of a binary form $f$ requires factoring $f$ into linear forms, and can sometimes hang when attempting that factorization.
-For this reason, when a factorization is already known, the user can pass to {\tt fpt} a list containing all the pairwise prime linear factors of $f$ and a list containing their respective multiplicities.
+            The above noted algorithm for computing the $F$-pure threshold of a binary form $f$ requires factoring $f$ into linear forms, and {\tt fpt} can sometimes hang when attempting that factorization.
+For this reason, when a factorization is already known, the user can pass to {\tt fpt} a list containing all the pairwise prime linear factors of $f$, and a list containing their respective multiplicities.
 
-\medskip
 {\small
@@
 \begin{MyVerbatim}
+
 i8 : L = {x, y, x + y, x + 3*y};
@@
 o10 = true
+
 \end{MyVerbatim}
@@
 
-The behavior of the {\tt fpt} function is more involved when no special algorithm is available, or {\tt UseSpecialAlgorithms} is set to {\tt false}.
-In the remainder of this section, we describe the behavior of the {\tt fpt} function in this case, as well as the roles of the options {\tt DepthOfSearch}, and {\tt Attempts}, both nonnegative integers.
+In the remainder of this section, we describe the {\tt fpt} function when no special algorithm is available, or {\tt UseSpecialAlgorithms} is set to {\tt false},  as well as the roles of the options {\tt DepthOfSearch}, and {\tt Attempts}, both nonnegative integers.
 
-            When no special algorithm is available or , then function {\tt fpt} computes {\tt nu}$(e,f)$, where $e$ is the value of the option {\tt DepthOfSearch}, which conservatively defaults to $1$.
-            At this point, we know that the $F$-pure threshold of $f$ lies in the closed interval {\color{red} Elaborate here} [$\nu/(p^e-1),(\nu+1)/p^e$], and the subroutine {\tt guessFPT} is called to make some "educated guesses" in an attempt to find the $F$-pure threshold, or at least narrow down the above interval.
-	    The number of "guesses" is controlled by the option {\tt Attempts}, which conservatively defaults to 3.
-            If {\tt Attempts} is set to 0, {\tt guessFPT} is bypassed.
-            If  {\tt Attempts} is set to at least 1, then a first check is run to verify whether the right-hand endpoint $(\nu+1)/p^e$ of the above interval is the $F$-pure threshold.
+In this case, very roughly speaking, the {\tt fpt} function will either compute, and output, the exact value of the $F$-pure threshold of $f$, and otherwise recursively compute a finite sequence of upper and lower bounds for this value, and output the last of these, which will be the tightest among all computed.
+The value of the option {\tt DepthOfSearch} determines the precision of the initial set of bounds, and the option {\tt Attempts}, in conjunction with some various subroutines, determines whether, and how, to produce new, tighter bounds from the previous ones.
+%We note that a pair of bounds will be produced only if the exact value of the $F$-pure threshold remains undetermined.
 
-\begin{example}
-\[             f = x^2*(x + y)^3*(x + 3*y^2)^5;
-            fpt( f, Attempts => 0 ) -- a bad estimate
-            fpt( f, Attempts => 0, DepthOfSearch => 3 ) -- a better estimate
-            fpt( f, Attempts => 1, DepthOfSearch => 3 ) -- the right-hand endpoint (nu+1)/p^e is the fpt \] 
-\end{example}
+In more detail, let $e$ denote the value of the option {\tt DepthofSearch}, which conservatively defaults to $1$.
+The {\tt fpt} function first computes $\nu=\nu_f(p^e)$, which agrees with the output of {\tt nu(e,f)}.
+It is well-known that the $F$-pure threshold of $f$ is greater than $\nu/p^e$ and at most $(\nu+1)/p^e$, and applying  {\color{red} \cite[Proposition 4.2]{}} to this lower bound tells us that the $F$-pure threshold of $f$ must be at least $\nu/(p^e-1)$.
+In summary, we know that the $F$-pure threshold of $f$ must lie in the closed interval
+%
+\begin{equation}
+\label{estimating-interval: e}
+\tag{$\dagger$}
+\left[ \frac{\nu}{p^e-1}, \frac{\nu+1}{p^e} \right].
+\end{equation}
 
-            If  {\tt Attempts} is set to at least 2 and the right-hand endpoint $(\nu+1)/p^e$ is not the $F$-pure threshold, a second check is run to verify whether the left-hand endpoint $\nu/(p^e-1)$ is the $F$-pure threshold.
+With these estimates in hand, the subroutine {\tt guessFPT} is called to make some ``educated guesses" in an attempt to identify the $F$-pure threshold within this interval, or at least narrow down this interval to produce improved estimates.
+The number of ``guesses" is controlled by the option {\tt Attempts}, which conservatively defaults to 3.
+If {\tt Attempts} is set to 0, then {\tt guessFPT} is bypassed.
+If  {\tt Attempts} is set to at least 1, then a first check is run to verify whether the right-hand endpoint $(\nu+1)/p^e$ of the above interval \eqref{estimating-interval: e} the $F$-pure threshold.
 
-\begin{example}
-\[
-	    f = x^6*y^4 + x^4*y^9 + (x^2 + y^3)^3;
-            fpt( f, Attempts => 1, DepthOfSearch => 3 )
-            fpt( f, Attempts => 2, DepthOfSearch => 3 ) -- the left-hand endpoint nu/(p^e-1) is the fpt
-\]
-\end{example}
+ We illustrate this below.
 
-            If neither endpoint is the $F$-pure threshold, and {\tt Attempts} is set to more than 2, additional checks are performed at numbers in the interval.
-            A number in the interval with minimal denominator is selected, and {\tt compareFPT} is used to test that number.
+{\small
+\setstretch{.67}
+\begin{MyVerbatim}
+
+i11 : f = x^2*(x + y)^3*(x + 3*y^2)^5;
+
+i12 : fpt( f, Attempts => 0 ) -- a bad estimate
+
+          1
+o12 = {0, -}
+          5
+
+o12 : List
+
+i13 : fpt( f, Attempts => 0, DepthOfSearch => 3 ) -- a better estimate
+
+        21   22
+o13 = {---, ---}
+       124  125
+
+o13 : List
+
+i14 : fpt( f, Attempts => 1, DepthOfSearch => 3 ) -- the right-hand endpoint (nu+1)/p^e is the fpt
+
+       22
+o14 = ---
+      125
+
+o14 : QQ
+
+\end{MyVerbatim}
+
+If  {\tt Attempts} is set to at least 2, and the right-hand endpoint $(\nu+1)/p^e$ of the interval \eqref{estimating-interval: e} is not the $F$-pure threshold, then a second check is run to verify whether the left-hand endpoint $\nu/(p^e-1)$ of this interval is the $F$-pure threshold.
+
+{\small
+\setstretch{.67}
+\begin{MyVerbatim}
+
+i15 : f = x^6*y^4 + x^4*y^9 + (x^2 + y^3)^3;
+
+i16 : fpt( f, Attempts => 1, DepthOfSearch => 3 )
+
+       17   7
+o16 = {--, --}
+       62  25
+
+o16 : List
+
+i17 : fpt( f, Attempts => 2, DepthOfSearch => 3 ) -- the left-hand endpoint nu/(p^e-1) is the fpt
+
+      17
+o17 = --
+      62
+
+o17 : QQ
+
+\end{MyVerbatim}
+}
+
+            If neither endpoint is the $F$-pure threshold, and {\tt Attempts} is set to more than 2, additional checks are performed at certain numbers within the interval .
+A number in the interval \eqref{estimating-interval: e} with minimal denominator is selected, and {\tt compareFPT} is used to test that number.
 If that ``guess" is correct, its value is returned; otherwise, the information returned by {\tt compareFPT} is used to narrow down the interval, and this process is repeated as many times as specified by {\tt Attempts}.
 
-\begin{example}
-\[             f = x^3*y^11*(x + y)^8*(x^2 + y^3)^8;
-            fpt( f, DepthOfSearch => 3, Attempts => 2 )
-            fpt( f, DepthOfSearch => 3, Attempts => 3 ) -- an additional check sharpens the estimate
-            fpt( f, DepthOfSearch => 3, Attempts => 4 ) -- and one more finds the exact answer
-\]
-\end{example}
+{\small
+\setstretch{.67}
+\begin{MyVerbatim}
+
+i18 : f = x^3*y^11*(x + y)^8*(x^2 + y^3)^8;
+
+i19 : fpt( f, DepthOfSearch => 3, Attempts => 2 )
+
+        3   7
+o19 = {--, ---}
+       62  125
+
+o19 : List
+
+i20 : fpt( f, DepthOfSearch => 3, Attempts => 3 ) -- an additional check sharpens the estimate
+
+        3   1
+o20 = {--, --}
+       62  18
+
+o20 : List
+
+i21 : fpt( f, DepthOfSearch => 3, Attempts => 4 ) -- and one more finds the exact answer
+
+       1
+o21 = --
+      19
+
+o21 : QQ
+
+\end{MyVerbatim}
+}
 
@@
 
-\begin{example}
-\[             f = x^5*y^6*(x + y)^9*(x^2 + y^3)^4;
-            fpt( f, DepthOfSearch => 3 )
-            fpt( f, DepthOfSearch => 3, UseFSignature => true )
-            numeric ooo
-            numeric ooo -- UseFSignature sharpened the estimate a bit \]
-\end{example}
+{\small
+\setstretch{.67}
+\begin{MyVerbatim}
+
+i22 : f = x^5*y^6*(x + y)^9*(x^2 + y^3)^4;
+
+i23 : fpt( f, DepthOfSearch => 3 )
+
+        2   1
+o23 = {--, --}
+       31  14
+
+o23 : List
+
+i24 : fpt( f, DepthOfSearch => 3, UseFSignature => true )
+
+        181   1
+o24 = {----, --}
+       2750  14
+
+o24 : List
+
+i25 : numeric o23
+
+o25 = {.0645161, .0714286}
+
+o25 : List
+
+i26 : numeric o24 -- UseFSignature sharpened the estimate a bit
+
+o26 = {.0658182, .0714286}
+
+o26 : List
+
+\end{MyVerbatim}
+}
 
@@
 
-\begin{example}
-\[             f = (x + y)^4*(x^2 + y^3)^6;
-            fpt( f, Attempts => 2, DepthOfSearch => 3 )
-            fpt( f, Attempts => 2, DepthOfSearch => 3, UseFSignature => true ) -- using FSignatures the answer improves a bit
-	    fpt( f, Attempts => 2, DepthOfSearch => 3, UseFSignature => true, FRegularityCheck => true ) -- FRegularityCheck finds the answer \] 
-\end{example}
+{\small
+\setstretch{.67}
+\begin{MyVerbatim}
+
+i27 : f = (x + y)^4*(x^2 + y^3)^6;
+
+i28 : fpt( f, Attempts => 2, DepthOfSearch => 3 )
+
+        3   13
+o28 = {--, ---}
+       31  125
+
+o28 : List
+
+i29 : fpt( f, Attempts => 2, DepthOfSearch => 3, UseFSignature => true ) -- using FSignatures the answer improves a bit
+
+        1   13
+o29 = {--, ---}
+       10  125
+
+o29 : List
+
+i30 : fpt( f, Attempts => 2, DepthOfSearch => 3, UseFSignature => true, FRegularityCheck => true ) -- FRegularityCheck finds the answer
+
+       1
+o30 = --
+      10
+
+o30 : QQ
+
+\end{MyVerbatim}
+}
 
@@
 
-\begin{example}            
-\[            f = x^7*y^5*(x + y)^5*(x^2 + y^3)^4;
-	    timing numeric fpt( f, DepthOfSearch => 3, UseFSignature => true, FRegularityCheck => true )
-            timing numeric fpt( f, Attempts => 5, DepthOfSearch => 3 ) -- a better answer in less time
-            timing fpt( f, DepthOfSearch => 4 ) -- the exact answer in even less time
-\]
-\end{example}
+{\small
+\setstretch{.67}
+\begin{MyVerbatim}
+
+i31: f = x^7*y^5*(x + y)^5*(x^2 + y^3)^4;
+
+i32 : timing numeric fpt( f, DepthOfSearch => 3, UseFSignature => true, FRegularityCheck => true )
+
+o32 = {.0733061, .0769231}
+      -- 2.68899 seconds
+
+o32 : Time
+
+i33 : timing numeric fpt( f, Attempts => 5, DepthOfSearch => 3 ) -- a better answer in less time
+
+o33 = {.075, .0769231}
+      -- .893389 seconds
+
+o33 : Time
+
+i34 : timing fpt( f, DepthOfSearch => 4 ) -- the exact answer in even less time
+
+       48
+o34 = ---
+      625
+      -- .361882 seconds
+
+o34 : Time
+
+\end{MyVerbatim}
+}
 
@@
 
-\begin{example}
- \[           f = x^7*y^5*(x + y)^5*(x^2 + y^3)^4;
-            fpt( f, DepthOfSearch => 3, UseFSignature => true, Verbose => true )
- \]
-  \end{example}
+{\small
+\setstretch{.67}
+\begin{MyVerbatim}
+
+i35 : f = x^7*y^5*(x + y)^5*(x^2 + y^3)^4;
+
+i36 :  fpt( f, DepthOfSearch => 3, UseFSignature => true, Verbose => true )
+
+Starting fpt ...
+
+fpt is not 1 ...
+
+Verifying if special algorithms apply...
+
+Special fpt algorithms were not used ...
+
+nu has been computed: nu = nu(3,f) = 9 ...
+
+fpt lies in the interval [ nu/(p^e-1), (nu+1)/p^e ] = [ 9/124, 2/25 ] ...
+
+Starting guessFPT ...
+
+The right-hand endpoint is not the fpt ...
+
+The left-hand endpoint is not the fpt ...
+
+guessFPT narrowed the interval down to ( 9/124, 1/13 ) ...
+
+Beginning F-signature computation ...
+
+First F-signature computed: s(f,(nu-1)/p^e) = 456/15625 ...
+
+Second F-signature computed: s(f,nu/p^e) = 64/15625 ...
+
+Computed F-signature secant line intercept: 449/6125 ...
+
+F-signature intercept is an improved lower bound ...
+
+fpt failed to find the exact answer; try increasing the value of DepthOfSearch or Attempts.
+
+fpt lies in the interval [ 449/6125, 1/13 ).
+
+        449   1
+o36 = {----, --}
+       6125  13
+
+o36 : List
+
+\end{MyVerbatim}
+}
 

### 2019-06-04 Fsing/FThresholdsPaper/FThresholds.tex
updates to FThresholds paper introduction

--- 2019-06-04 Fsing/FThresholdsPaper/FThresholds.tex
@@
 As a further generalization, the notion of \emph{$F$-threshold} was also introduced.
-All of these \emph{thresholds} have been the focus of intense study over the past 15 years.
+All of these \emph{thresholds} have been the focus of intense study over the past fifteen years.
 
@@
 
-\noindent {\it Acknowledgements.}  First and foremost, the authors enthusiastically thank all contributors to the \emph{FThresholds} package:  Erin Bela, Juliette Bruce, Zhibek Kadyrsizova, Sara Malec, Maral Mostafazadehfard, Marcus Robinson, Dan Smolkin, and Robert Walker.
-We thank the organizers of the five \emph{Macaulay2} workshops where much of the functionality in the package was develope, hosted by Wake Forest University in 2012, the University of California, Berkeley in 2014 and 2017, Boise State University in 2015, and the University of Utah in 2016.
+\subsection*{Acknowledgements.}  First and foremost, the authors enthusiastically thank all contributors to the \emph{FThresholds} package:  Erin Bela, Juliette Bruce, Zhibek Kadyrsizova, Sara Malec, Maral Mostafazadehfard, Marcus Robinson, Dan Smolkin, and Robert Walker.
+We are also grateful the organizers of the \emph{Macaulay2} workshops where much of the functionality described herein was developed, hosted by Wake Forest University in 2012, the University of California, Berkeley in 2014 and 2017, Boise State University in 2015, and the University of Utah in 2016.
 Finally, we thank the University of Utah for hosting a collaborative development visit in 2018, and the Institute of Mathematics and its Applications for its support for a Coding Sprint in 2019, where the current version of the package was finalized and this paper was completed.

### 2019-06-04 Fsing/FThresholdsPaper/FThresholds.tex
Added references to the paper

--- 2019-06-04 Fsing/FThresholdsPaper/FThresholds.tex
@@
              If the option {\tt UseSpecialAlgorithms} is set to {\tt true} (the default value), then {\tt fpt} first checks whether $f$ is diagonal polynomial, a binomial, or a form in two variables, in that order.
-             If it is one of these, algorithms of Hern\'andez, or Hern\'andez and Teixeira, {\color{red}  References?} are executed to compute the $F$-pure threshold of $f$.
+             If it is one of these, algorithms of Hern\'andez \cite{HernandezFInvariantsOfDiagonalHyp, HernandezFPureThresholdOfBinomial}, or Hern\'andez and Teixeira \cite{HernandezTeixeiraFThresholdFunctions},  are executed to compute the $F$-pure threshold.
 
@@
 The {\tt fpt} function first computes $\nu=\nu_f(p^e)$, which agrees with the output of {\tt nu(e,f)}.
-It is well-known that the $F$-pure threshold of $f$ is greater than $\nu/p^e$ and at most $(\nu+1)/p^e$, and applying  {\color{red} \cite[Proposition 4.2]{}} to this lower bound tells us that the $F$-pure threshold of $f$ must be at least $\nu/(p^e-1)$.
+It is well-known that the $F$-pure threshold of $f$ is greater than $\nu/p^e$ and at most $(\nu+1)/p^e$, and applying  \cite[Proposition 4.2]{HernandezFPurityOfHypersurfaces} to this lower bound tells us that the $F$-pure threshold of $f$ must be at least $\nu/(p^e-1)$.
 In summary, we know that the $F$-pure threshold of $f$ must lie in the closed interval

### 2019-06-04 Fsing/FThresholdsPaper/FThresholds.tex
Manually wrapped lines in verbose in the fpt section of the paper

@@
 
-i14 : fpt( f, Attempts => 1, DepthOfSearch => 3 ) -- the right-hand endpoint (nu+1)/p^e is the fpt
+i14 : fpt( f, Attempts => 1, DepthOfSearch => 3 ) -- the right-hand
+
+      endpoint (nu+1)/p^e is the F-pure threshold
 
@@
 
-i17 : fpt( f, Attempts => 2, DepthOfSearch => 3 ) -- the left-hand endpoint nu/(p^e-1) is the fpt
+i17 : fpt( f, Attempts => 2, DepthOfSearch => 3 ) -- the left-hand endpoint
+
+      nu/(p^e-1) is the F-pure threshold
 
@@
 
-i20 : fpt( f, DepthOfSearch => 3, Attempts => 3 ) -- an additional check sharpens the estimate
+i20 : fpt( f, DepthOfSearch => 3, Attempts => 3 ) -- an additional check
+
+      sharpens the estimate
 
@@
 
-i21 : fpt( f, DepthOfSearch => 3, Attempts => 4 ) -- and one more finds the exact answer
+i21 : fpt( f, DepthOfSearch => 3, Attempts => 4 ) -- and one more finds
+
+      the answer
 
@@
 
-i29 : fpt( f, Attempts => 2, DepthOfSearch => 3, UseFSignature => true ) -- using FSignatures the answer improves a bit
+i29 : fpt( f, Attempts => 2, DepthOfSearch => 3, UseFSignature => true ) --
+
+      UseFSignature improves the answer a bit
 
@@
 
-i30 : fpt( f, Attempts => 2, DepthOfSearch => 3, UseFSignature => true, FRegularityCheck => true ) -- FRegularityCheck finds the answer
+i30 : fpt( f, Attempts => 2, DepthOfSearch => 3, UseFSignature => true,
+
+      FRegularityCheck => true ) -- FRegularityCheck finds the answer
 
@@
 
-i32 : timing numeric fpt( f, DepthOfSearch => 3, UseFSignature => true, FRegularityCheck => true )
+i32 : timing numeric fpt( f, DepthOfSearch => 3, UseFSignature => true,
+
+      FRegularityCheck => true )
 
@@
 
-i33 : timing numeric fpt( f, Attempts => 5, DepthOfSearch => 3 ) -- a better answer in less time
+i33 : timing numeric fpt( f, Attempts => 5, DepthOfSearch => 3 ) -- a better
+
+      answer in less time
 
@@
 
-i34 : timing fpt( f, DepthOfSearch => 4 ) -- the exact answer in even less time
+i34 : timing fpt( f, DepthOfSearch => 4 ) -- the exact answer in even less 
+      time
 
@@
 
-fpt failed to find the exact answer; try increasing the value of DepthOfSearch or Attempts.
+fpt failed to find the exact answer; try increasing the value of
+
+DepthOfSearch or Attempts.
 

### 2019-06-04 Fsing/FThresholdsPaper/FThresholds.tex
updated introduction to FThresholds paper

--- 2019-06-04 Fsing/FThresholdsPaper/FThresholds.tex
@@
 \begin{abstract}
-	This note describes a \emph{Macaulay2} package for the computation and estimation of certain numerical invariants arising in prime characteristic commutative algebr.
-Namely, $F$-pure thresholds, more general $F$-thresholds, and other related numerical invariants, in prime characteristic commutative algebra.
+	This note describes the \emph{Macaulay2} package \emph{FThresholds}.
+This package is designed to compute and estimate $F$-pure thresholds, more general $F$-thresholds, and related numerical invariants arising in the study of regularity conditions in prime characteristic commutative algebra.
 \end{abstract}
@@
 
-\keywords{Macaulay2}
+\keywords{Macaulay2, Frobenius, $F$-singularity, $F$-pure threshold, $F$-threshold}
 
@@
 Recall that a ring $R$ of prime characteristic $p>0$ is said to be \emph{$F$-pure} if the Frobenius morphism $F : R \to R$ sending an element to its $p^\text{th}$ power is a pure morphism (under geometric hypotheses, this is equivalent to the condition that the Frobenius morphism is split).
-The notion of $F$-purity appeared first in the work of Hochster and Roberts in \cite{HochsterRobertsFrobeniusLocalCohomology}, was compared with rational singularities in \cite{FedderFPureRat}, and was used globally to study properties of Schubert varieties in \cite{MehtaRamanathanFrobeniusSplittingAndCohomologyVanishing}.
+The notion of $F$-purity first appeared in the work of Hochster and Roberts in \cite{HochsterRobertsFrobeniusLocalCohomology}, was compared with rational singularities in \cite{FedderFPureRat}, and was used globally to study properties of Schubert varieties in \cite{MehtaRamanathanFrobeniusSplittingAndCohomologyVanishing}.
 
-After the advent of tight closure \cite{HochsterHunekeTC1}, the usage of the Frobenius endomorphism to measure singularities proliferated, and based on a strong connection discovered between $F$-pure and \emph{log canonical} singularities \cite{HaraWatanabeFRegFPure}, the notion of $F$-purity was generalized to pairs $(R, f^t)$, where $f$ is an element of $R$, and $t$ is a positive rational number $t$ considered as a formal exponent.
-Along these lines, the notion of the \emph{$F$-pure threshold} (or $\fpt$) was defined in analogy with the log canonical threshold (or $\lct$) \cite{TakagiWatanabeFPureThresh,MustataTakagiWatanabeFThresholdsAndBernsteinSato}.
-The $\fpt$ of $(R, f)$ is the supremum over all $t$ for which $(R, f^t)$ is $F$-pure, and the functionality computing this number is the core of this package.
-As a further generalization, the notion of \emph{$F$-threshold} was also introduced.
-All of these \emph{thresholds} have been the focus of intense study over the past fifteen years.
+After the advent of tight closure \cite{HochsterHunekeTC1}, the usage of the Frobenius endomorphism to measure regularity conditions proliferated, and based on a strong connection discovered between $F$-pure and \emph{log canonical} singularities \cite{HaraWatanabeFRegFPure}, the notion of $F$-purity was generalized to pairs $(R, f^t)$, where $f$ is an element of $R$, and $t$ is a positive rational number $t$ considered as a formal exponent.
+
+Along these lines, the notion of the \emph{$F$-pure threshold} was defined in analogy with the \emph{log canonical threshold} \cite{TakagiWatanabeFPureThresh,MustataTakagiWatanabeFThresholdsAndBernsteinSato}.
+The $F$-pure threshold of the pair $(R, f)$ is the supremum over all $t$ for which $(R, f^t)$ is $F$-pure.  
+This value is typically very difficult to calculate in general, and computing and estimating its value is the core of this \emph{Macaulay2} package.
+
+Moreover, the more general family of \emph{$F$-thresholds} was also introduced. 
+This family of numerical invariants have been the focus of intense study over the past fifteen years, with
 
@@
 \begin{itemize}
-\item{} \autoref{sec.Nu} describes methods to to approximate the $\fpt$, and other $F$-thresholds.  
-\item{} \autoref{sec.IsFPT} describes functionality that can determine whether a given number is the fpt, or more generally, an $F$-jumping exponent.
-\item{} \autoref{sec.FPT} describes the {\tt fpt} function, and how it works.
+\item{} \autoref{sec.Nu} describes the methods implemented for approximating the $F$-pure threshold and other $F$-thresholds.  
+\item{} \autoref{sec.IsFPT} describes functionality for determining whether a given number is the $F$-pure threshold, or more generally, an $F$-jumping exponent.
+\item{} \autoref{sec.FPT} describes the function {\tt fpt} for estimating and computing $F$-pure thresholds, and how it works.
 \end{itemize}
@@
 
-\subsection*{Acknowledgements.}  First and foremost, the authors enthusiastically thank all contributors to the \emph{FThresholds} package:  Erin Bela, Juliette Bruce, Zhibek Kadyrsizova, Sara Malec, Maral Mostafazadehfard, Marcus Robinson, Dan Smolkin, and Robert Walker.
+\subsection*{Acknowledgements.}  First and foremost, the authors enthusiastically thank all contributors to the \emph{FThresholds} package: (INSERT NAMES HERE).
+%Erin Bela, Juliette Bruce, Zhibek Kadyrsizova, Sara Malec, Maral Mostafazadehfard, Marcus Robinson, Dan Smolkin, and Robert Walker.
 We are also grateful the organizers of the \emph{Macaulay2} workshops where much of the functionality described herein was developed, hosted by Wake Forest University in 2012, the University of California, Berkeley in 2014 and 2017, Boise State University in 2015, and the University of Utah in 2016.
-Finally, we thank the University of Utah for hosting a collaborative development visit in 2018, and the Institute of Mathematics and its Applications for its support for a Coding Sprint in 2019, where the current version of the package was finalized and this paper was completed.
+We are also grateful to the University of Utah for hosting a collaborative development visit in 2018, and to the Institute of Mathematics and its Applications for its support for the Coding Sprint \emph{F-thresholds in Macaulay2} in 2019, where the current version of the package was finalized and this paper was completed.
 
@@
              If the option {\tt UseSpecialAlgorithms} is set to {\tt true} (the default value), then {\tt fpt} first checks whether $f$ is diagonal polynomial, a binomial, or a form in two variables, in that order.
-             If it is one of these, algorithms of Hern\'andez \cite{HernandezFInvariantsOfDiagonalHyp, HernandezFPureThresholdOfBinomial}, or Hern\'andez and Teixeira \cite{HernandezTeixeiraFThresholdFunctions},  are executed to compute the $F$-pure threshold.
+             If it is one of these, algorithms of Hern\'andez, or Hern\'andez and Teixeira, {\color{red}  References?} are executed to compute the $F$-pure threshold of $f$.
 
@@
 The {\tt fpt} function first computes $\nu=\nu_f(p^e)$, which agrees with the output of {\tt nu(e,f)}.
-It is well-known that the $F$-pure threshold of $f$ is greater than $\nu/p^e$ and at most $(\nu+1)/p^e$, and applying  \cite[Proposition 4.2]{HernandezFPurityOfHypersurfaces} to this lower bound tells us that the $F$-pure threshold of $f$ must be at least $\nu/(p^e-1)$.
+It is well-known that the $F$-pure threshold of $f$ is greater than $\nu/p^e$ and at most $(\nu+1)/p^e$, and applying  {\color{red} \cite[Proposition 4.2]{}} to this lower bound tells us that the $F$-pure threshold of $f$ must be at least $\nu/(p^e-1)$.
 In summary, we know that the $F$-pure threshold of $f$ must lie in the closed interval

### 2019-06-04 Fsing/FThresholdsPaper/FThresholds.tex
updated introduction to FThresholds paper

--- 2019-06-04 Fsing/FThresholdsPaper/FThresholds.tex
@@
 \begin{abstract}
-	This note describes the \emph{Macaulay2} package \emph{FThresholds}.
+	This note describes the functionality implemented in the \emph{Macaulay2} package \emph{FThresholds}.
 This package is designed to compute and estimate $F$-pure thresholds, more general $F$-thresholds, and related numerical invariants arising in the study of regularity conditions in prime characteristic commutative algebra.
@@
 The $F$-pure threshold of the pair $(R, f)$ is the supremum over all $t$ for which $(R, f^t)$ is $F$-pure.  
-This value is typically very difficult to calculate in general, and computing and estimating its value is the core of this \emph{Macaulay2} package.
-
-Moreover, the more general family of \emph{$F$-thresholds} was also introduced. 
-This family of numerical invariants have been the focus of intense study over the past fifteen years, with
+Furthermore, the more general \emph{$F$-thresholds} was also introduced, a family that contains the $F$-pure threshold. 
+These numerical invariants are typically very difficult to calculate in general, and have been the 
+focus of intense study over the past fifteen years.
+This \emph{Macaulay2} package is centered around calculating 
+and estimating the $F$-pure threshold and other $F$-thresholds.
 
@@
 \begin{itemize}
-\item{} \autoref{sec.Nu} describes the methods implemented for approximating the $F$-pure threshold and other $F$-thresholds.  
-\item{} \autoref{sec.IsFPT} describes functionality for determining whether a given number is the $F$-pure threshold, or more generally, an $F$-jumping exponent.
-\item{} \autoref{sec.FPT} describes the function {\tt fpt} for estimating and computing $F$-pure thresholds, and how it works.
+\item \autoref{sec.Nu} describes the methods implemented for approximating the $F$-pure threshold and other $F$-thresholds.  
+\item \autoref{sec.IsFPT} describes functionality for determining whether a given number is the $F$-pure threshold, or more generally, an $F$-jumping exponent.
+\item \autoref{sec.FPT} describes the function {\tt fpt} for estimating and computing $F$-pure thresholds, and how it works.
 \end{itemize}
 
-This package builds heavily upon the \emph{TestIdeals} package, which provides a broad range of functionality in prime characteristic commutative algebra.
+This package builds heavily upon the \emph{TestIdeals} package for \emph{Macaulay2}, which provides a broad range of functionality in prime characteristic commutative algebra.
 

### 2019-06-04 Fsing/FThresholdsPaper/FThresholds.tex
Minor changes to the paper

--- 2019-06-04 Fsing/FThresholdsPaper/FThresholds.tex
@@
 \begin{abstract}
-	This note describes the \emph{Macaulay2} package \emph{FThresholds}.
-This package is designed to compute and estimate $F$-pure thresholds, more general $F$-thresholds, and related numerical invariants arising in the study of regularity conditions in prime characteristic commutative algebra.
+	This note describes a \emph{Macaulay2} package for the computation and estimation of certain numerical invariants arising in prime characteristic commutative algebr.
+Namely, $F$-pure thresholds, more general $F$-thresholds, and other related numerical invariants, in prime characteristic commutative algebra.
 \end{abstract}
@@
 
-\keywords{Macaulay2, Frobenius, $F$-singularity, $F$-pure threshold, $F$-threshold}
+\keywords{Macaulay2}
 
@@
 Recall that a ring $R$ of prime characteristic $p>0$ is said to be \emph{$F$-pure} if the Frobenius morphism $F : R \to R$ sending an element to its $p^\text{th}$ power is a pure morphism (under geometric hypotheses, this is equivalent to the condition that the Frobenius morphism is split).
-The notion of $F$-purity first appeared in the work of Hochster and Roberts in \cite{HochsterRobertsFrobeniusLocalCohomology}, was compared with rational singularities in \cite{FedderFPureRat}, and was used globally to study properties of Schubert varieties in \cite{MehtaRamanathanFrobeniusSplittingAndCohomologyVanishing}.
+The notion of $F$-purity appeared first in the work of Hochster and Roberts in \cite{HochsterRobertsFrobeniusLocalCohomology}, was compared with rational singularities in \cite{FedderFPureRat}, and was used globally to study properties of Schubert varieties in \cite{MehtaRamanathanFrobeniusSplittingAndCohomologyVanishing}.
 
-After the advent of tight closure \cite{HochsterHunekeTC1}, the usage of the Frobenius endomorphism to measure regularity conditions proliferated, and based on a strong connection discovered between $F$-pure and \emph{log canonical} singularities \cite{HaraWatanabeFRegFPure}, the notion of $F$-purity was generalized to pairs $(R, f^t)$, where $f$ is an element of $R$, and $t$ is a positive rational number $t$ considered as a formal exponent.
-
-Along these lines, the notion of the \emph{$F$-pure threshold} was defined in analogy with the \emph{log canonical threshold} \cite{TakagiWatanabeFPureThresh,MustataTakagiWatanabeFThresholdsAndBernsteinSato}.
-The $F$-pure threshold of the pair $(R, f)$ is the supremum over all $t$ for which $(R, f^t)$ is $F$-pure.  
-This value is typically very difficult to calculate in general, and computing and estimating its value is the core of this \emph{Macaulay2} package.
-
-Moreover, the more general family of \emph{$F$-thresholds} was also introduced. 
-This family of numerical invariants have been the focus of intense study over the past fifteen years, with
+After the advent of tight closure \cite{HochsterHunekeTC1}, the usage of the Frobenius endomorphism to measure singularities proliferated, and based on a strong connection discovered between $F$-pure and \emph{log canonical} singularities \cite{HaraWatanabeFRegFPure}, the notion of $F$-purity was generalized to pairs $(R, f^t)$, where $f$ is an element of $R$, and $t$ is a positive rational number $t$ considered as a formal exponent.
+Along these lines, the notion of the \emph{$F$-pure threshold} (or $\fpt$) was defined in analogy with the log canonical threshold (or $\lct$) \cite{TakagiWatanabeFPureThresh,MustataTakagiWatanabeFThresholdsAndBernsteinSato}.
+The $\fpt$ of $(R, f)$ is the supremum over all $t$ for which $(R, f^t)$ is $F$-pure, and the functionality computing this number is the core of this package.
+As a further generalization, the notion of \emph{$F$-threshold} was also introduced.
+All of these \emph{thresholds} have been the focus of intense study over the past fifteen years.
 
@@
 \begin{itemize}
-\item{} \autoref{sec.Nu} describes the methods implemented for approximating the $F$-pure threshold and other $F$-thresholds.  
-\item{} \autoref{sec.IsFPT} describes functionality for determining whether a given number is the $F$-pure threshold, or more generally, an $F$-jumping exponent.
-\item{} \autoref{sec.FPT} describes the function {\tt fpt} for estimating and computing $F$-pure thresholds, and how it works.
+\item{} \autoref{sec.Nu} describes methods to to approximate the $\fpt$, and other $F$-thresholds.  
+\item{} \autoref{sec.IsFPT} describes functionality that can determine whether a given number is the fpt, or more generally, an $F$-jumping exponent.
+\item{} \autoref{sec.FPT} describes the {\tt fpt} function, and how it works.
 \end{itemize}
@@
 
-\subsection*{Acknowledgements.}  First and foremost, the authors enthusiastically thank all contributors to the \emph{FThresholds} package: (INSERT NAMES HERE).
-%Erin Bela, Juliette Bruce, Zhibek Kadyrsizova, Sara Malec, Maral Mostafazadehfard, Marcus Robinson, Dan Smolkin, and Robert Walker.
+\subsection*{Acknowledgements.}  First and foremost, the authors enthusiastically thank all contributors to the \emph{FThresholds} package:  Erin Bela, Juliette Bruce, Zhibek Kadyrsizova, Sara Malec, Maral Mostafazadehfard, Marcus Robinson, Dan Smolkin, and Robert Walker.
 We are also grateful the organizers of the \emph{Macaulay2} workshops where much of the functionality described herein was developed, hosted by Wake Forest University in 2012, the University of California, Berkeley in 2014 and 2017, Boise State University in 2015, and the University of Utah in 2016.
-We are also grateful to the University of Utah for hosting a collaborative development visit in 2018, and to the Institute of Mathematics and its Applications for its support for the Coding Sprint \emph{F-thresholds in Macaulay2} in 2019, where the current version of the package was finalized and this paper was completed.
+Finally, we thank the University of Utah for hosting a collaborative development visit in 2018, and the Institute of Mathematics and its Applications for its support for a Coding Sprint in 2019, where the current version of the package was finalized and this paper was completed.
 
@@
 
-In this case, very roughly speaking, the {\tt fpt} function will either compute, and output, the exact value of the $F$-pure threshold of $f$, and otherwise recursively compute a finite sequence of upper and lower bounds for this value, and output the last of these, which will be the tightest among all computed.
+In this case, very roughly speaking, the {\tt fpt} function will either compute, and output, the exact value of the $F$-pure threshold of $f$, and will otherwise recursively compute a finite sequence of lower and upper bounds for this value, and output the last of these, which will be the tightest among all computed.
 The value of the option {\tt DepthOfSearch} determines the precision of the initial set of bounds, and the option {\tt Attempts}, in conjunction with some various subroutines, determines whether, and how, to produce new, tighter bounds from the previous ones.
-%We note that a pair of bounds will be produced only if the exact value of the $F$-pure threshold remains undetermined.
 
@@
 If {\tt Attempts} is set to 0, then {\tt guessFPT} is bypassed.
-If  {\tt Attempts} is set to at least 1, then a first check is run to verify whether the right-hand endpoint $(\nu+1)/p^e$ of the above interval \eqref{estimating-interval: e} the $F$-pure threshold.
-
+If  {\tt Attempts} is set to at least 1, then a first check is run to verify whether the right-hand endpoint $(\nu+1)/p^e$ of the interval \eqref{estimating-interval: e} the $F$-pure threshold.
 We illustrate this below.

### 2019-06-04 Fsing/FThresholdsPaper/FThresholds.tex
minor changes to intro of FThresholds paper

--- 2019-06-04 Fsing/FThresholdsPaper/FThresholds.tex
@@
 Furthermore, the more general \emph{$F$-thresholds} was also introduced, a family that contains the $F$-pure threshold. 
-These numerical invariants are typically very difficult to calculate in general, and have been the 
+These numerical invariants are typically very difficult to calculate, and due to their significance, have been the 
 focus of intense study over the past fifteen years.
 This \emph{Macaulay2} package is centered around calculating 
-and estimating the $F$-pure threshold and other $F$-thresholds.
+and estimating the $F$-pure threshold and other $F$-thresholds, with the function {\tt fpt} at its core.
 
-There are three main sections in this paper, describing the functionality implemented in the \emph{Macaulay2} package \emph{FThresholds}. 
+There are three main sections in this paper, which describe and illustrate the functionality implemented in the package \emph{FThresholds}. 
 \begin{itemize}
 \item \autoref{sec.Nu} describes the methods implemented for approximating the $F$-pure threshold and other $F$-thresholds.  
-\item \autoref{sec.IsFPT} describes functionality for determining whether a given number is the $F$-pure threshold, or more generally, an $F$-jumping exponent.
-\item \autoref{sec.FPT} describes the function {\tt fpt} for estimating and computing $F$-pure thresholds, and how it works.
+\item \autoref{sec.IsFPT} explains the package's functionality for determining whether a given number is the $F$-pure threshold, or more generally, an $F$-jumping exponent.
+\item \autoref{sec.FPT} is focused on the features of the function {\tt fpt} for estimating and computing $F$-pure thresholds, and how it works. 
 \end{itemize}

### 2019-06-05 Fsing/FThresholdsPaper/FThresholds.tex

--- 2019-06-04 Fsing/FThresholdsPaper/FThresholds.tex
@@
 
-In this case, very roughly speaking, the {\tt fpt} function will either compute, and output, the exact value of the $F$-pure threshold of $f$, and otherwise recursively compute a finite sequence of upper and lower bounds for this value, and output the last of these, which will be the tightest among all computed.
+In this case, very roughly speaking, the {\tt fpt} function will either compute, and output, the exact value of the $F$-pure threshold of $f$, and otherwise recursively compute a finite sequence of lower and upper bounds for this value, and output the last of these, which will be the tightest among all computed.
 The value of the option {\tt DepthOfSearch} determines the precision of the initial set of bounds, and the option {\tt Attempts}, in conjunction with some various subroutines, determines whether, and how, to produce new, tighter bounds from the previous ones.
-%We note that a pair of bounds will be produced only if the exact value of the $F$-pure threshold remains undetermined.
 
@@
 If  {\tt Attempts} is set to at least 1, then a first check is run to verify whether the right-hand endpoint $(\nu+1)/p^e$ of the above interval \eqref{estimating-interval: e} the $F$-pure threshold.
-
 We illustrate this below.

### 2019-06-05 Fsing/FThresholdsPaper/FThresholds.tex
Minor changes to paper

@@
    This note describes the functionality implemented in the \emph{Macaulay2} package \emph{FThresholds}.
-This package is designed to compute and estimate $F$-pure thresholds, more general $F$-thresholds, and related numerical invariants arising in the study of regularity conditions in prime characteristic commutative algebra.
+   This package is designed to compute and estimate $F$-pure thresholds, more general $F$-thresholds, and related numerical invariants arising in the study of regularity conditions in positive characteristic commutative algebra.
 \end{abstract}
@@
 
-This paper describes the \emph{Macaulay2} package \emph{FThresholds}, which provides tools for computing certain fundamental invariants arising in prime characteristic commutative algebra, namely, \emph{$F$-pure thresholds}, \emph{$F$-thresholds}, and \emph{$F$-jumping exponents}.
-Recall that a ring $R$ of prime characteristic $p>0$ is said to be \emph{$F$-pure} if the Frobenius morphism $F : R \to R$ sending an element to its $p^\text{th}$ power is a pure morphism (under geometric hypotheses, this is equivalent to the condition that the Frobenius morphism is split).
-The notion of $F$-purity first appeared in the work of Hochster and Roberts in \cite{HochsterRobertsFrobeniusLocalCohomology}, was compared with rational singularities in \cite{FedderFPureRat}, and was used globally to study properties of Schubert varieties in \cite{MehtaRamanathanFrobeniusSplittingAndCohomologyVanishing}.
+This paper describes the \emph{Macaulay2} \cite{M2} package \emph{FThresholds}, which provides tools for computing certain fundamental invariants arising in positive characteristic commutative algebra, namely, \emph{$F$-pure thresholds}, \emph{$F$-thresholds}, and \emph{$F$-jumping exponents}.
+Recall that a ring $R$ of prime characteristic $p>0$ is said to be \emph{$F$-pure} if the Frobenius morphism $F \: R \to R$ sending an element to its $p^\text{th}$ power is a pure morphism (under geometric hypotheses, this is equivalent to the condition that the Frobenius morphism is split).
+The notion of $F$-purity first appeared in the work of Hochster and Roberts \cite{HochsterRobertsFrobeniusLocalCohomology}, was compared with rational singularities \cite{FedderFPureRat}, and was used globally to study properties of Schubert varieties in \cite{MehtaRamanathanFrobeniusSplittingAndCohomologyVanishing}.
 
-After the advent of tight closure \cite{HochsterHunekeTC1}, the usage of the Frobenius endomorphism to measure regularity conditions proliferated, and based on a strong connection discovered between $F$-pure and \emph{log canonical} singularities \cite{HaraWatanabeFRegFPure}, the notion of $F$-purity was generalized to pairs $(R, f^t)$, where $f$ is an element of $R$, and $t$ is a positive rational number $t$ considered as a formal exponent.
+After the advent of tight closure \cite{HochsterHunekeTC1}, the usage of the Frobenius endomorphism to measure regularity conditions proliferated, and based on a strong connection discovered between $F$-pure and \emph{log canonical} singularities \cite{HaraWatanabeFRegFPure}, the notion of $F$-purity was generalized to pairs $(R, f^t)$, where $f$ is an element of $R$, and $t$ is a nonnegative real number considered a formal exponent.
 
@@
 The $F$-pure threshold of the pair $(R, f)$ is the supremum over all $t$ for which $(R, f^t)$ is $F$-pure.  
-Furthermore, the more general \emph{$F$-thresholds} was also introduced, a family that contains the $F$-pure threshold. 
-These numerical invariants are typically very difficult to calculate, and due to their significance, have been the 
-focus of intense study over the past fifteen years.
-This \emph{Macaulay2} package is centered around calculating 
-and estimating the $F$-pure threshold and other $F$-thresholds, with the function {\tt fpt} at its core.
+Furthermore, the more general notion of \emph{$F$-thresholds}, which includes the $F$-pure threshold, was also introduced. 
+These numerical invariants are typically very difficult to calculate, and due to their significance, have been the focus of intense study over the past fifteen years.
+This \emph{Macaulay2} package is centered around calculating and estimating the $F$-pure threshold and other $F$-thresholds, with the function {\tt fpt} at its core.
 
@@
 \end{MyVerbatim}
+}
 

### 2019-06-05 Fsing/FThresholdsPaper/FThresholds.tex
updates to FThresholds paper intro

@@
 Recall that a ring $R$ of prime characteristic $p>0$ is said to be \emph{$F$-pure} if the Frobenius morphism $F \: R \to R$ sending an element to its $p^\text{th}$ power is a pure morphism (under geometric hypotheses, this is equivalent to the condition that the Frobenius morphism is split).
-The notion of $F$-purity first appeared in the work of Hochster and Roberts \cite{HochsterRobertsFrobeniusLocalCohomology}, was compared with rational singularities \cite{FedderFPureRat}, and was used globally to study properties of Schubert varieties in \cite{MehtaRamanathanFrobeniusSplittingAndCohomologyVanishing}.
+The notion of $F$-purity first appeared in the work \cite{HochsterRobertsFrobeniusLocalCohomology}  of Hochster and Roberts to study local cohomology \cite{HochsterRobertsFrobeniusLocalCohomology}, was compared with rational singularities in  \cite{FedderFPureRat}, and was used globally to study properties of Schubert varieties in \cite{MehtaRamanathanFrobeniusSplittingAndCohomologyVanishing}.
 
@@
 The $F$-pure threshold of the pair $(R, f)$ is the supremum over all $t$ for which $(R, f^t)$ is $F$-pure.  
-Furthermore, the more general notion of \emph{$F$-thresholds}, which includes the $F$-pure threshold, was also introduced. 
-These numerical invariants are typically very difficult to calculate, and due to their significance, have been the focus of intense study over the past fifteen years.
-This \emph{Macaulay2} package is centered around calculating and estimating the $F$-pure threshold and other $F$-thresholds, with the function {\tt fpt} at its core.
+Furthermore, \emph{$F$-threholds} were introduced, a family of invariants that naturally extends the notion of an $F$-pure threshold.
 
-There are three main sections in this paper, which describe and illustrate the functionality implemented in the package \emph{FThresholds}.
+These numerical invariants are typically difficult to calculate,
+and due to their significance, have been the focus of intense study over the past fifteen years.
+To this end, the \emph{Macaulay2} package \emph{FThresholds} is centered around calculating and estimating the $F$-pure threshold and other $F$-thresholds, with the function {\tt fpt} at its core.
+
+There are three main sections in this paper, which describe and illustrate the main functionality implemented in the package \emph{FThresholds}.
 \begin{itemize}
 \item \autoref{sec.Nu} describes the methods implemented for approximating the $F$-pure threshold and other $F$-thresholds.  
-\item \autoref{sec.IsFPT} explains the package's functionality for determining whether a given number is the $F$-pure threshold, or more generally, an $F$-jumping exponent.
-\item \autoref{sec.FPT} is focused on the features of the function {\tt fpt} for estimating and computing $F$-pure thresholds, and how it works. 
+\item \autoref{sec.IsFPT} explains the package's functionality for determining whether a given number is the $F$-pure threshold, or more generally, an \emph{$F$-jumping exponent}.
+\item \autoref{sec.FPT} summarizes the features of the function {\tt fpt} and how it works. 
 \end{itemize}
@@
 
-\subsection*{Acknowledgements.}  First and foremost, the authors enthusiastically thank all contributors to the \emph{FThresholds} package: (INSERT NAMES HERE).
+\subsection*{Acknowledgements.}  First and foremost, the authors enthusiastically thank all authors and contributors to the \emph{FThresholds} package: (INSERT NAMES HERE).
 %Erin Bela, Juliette Bruce, Zhibek Kadyrsizova, Sara Malec, Maral Mostafazadehfard, Marcus Robinson, Dan Smolkin, and Robert Walker.

### 2019-06-05 Fsing/FThresholdsPaper/FThresholds.tex
updates to section 4 of paper FThresholds

@@
 \item \autoref{sec.IsFPT} explains the package's functionality for determining whether a given number is the $F$-pure threshold, or more generally, an \emph{$F$-jumping exponent}.
-\item \autoref{sec.FPT} summarizes the features of the function {\tt fpt} and how it works. 
+\item \autoref{sec.FPT} describes the features of the central function of the package, {\tt fpt}. 
 \end{itemize}
@@
 
-In more detail, let $e$ denote the value of the option {\tt DepthofSearch}, which conservatively defaults to $1$.
+In more detail, let $e$ denote the value of the option {\tt DepthOfSearch}, which conservatively defaults to {\tt 1}.
 The {\tt fpt} function first computes $\nu=\nu_f(p^e)$, which agrees with the output of {\tt nu(e,f)}.
-It is well-known that the $F$-pure threshold of $f$ is greater than $\nu/p^e$ and at most $(\nu+1)/p^e$, and applying  \cite[Proposition 4.2]{HernandezFPurityOfHypersurfaces} to this lower bound tells us that the $F$-pure threshold of $f$ must be at least $\nu/(p^e-1)$.
+It is well known that the $F$-pure threshold of $f$ is greater than $\nu/p^e$ and at most $(\nu+1)/p^e$, and applying  \cite[Proposition 4.2]{HernandezFPurityOfHypersurfaces} to this lower bound tells us that the $F$-pure threshold of $f$ must be at least $\nu/(p^e-1)$.
 In summary, we know that the $F$-pure threshold of $f$ must lie in the closed interval
@@
 With these estimates in hand, the subroutine {\tt guessFPT} is called to make some ``educated guesses" in an attempt to identify the $F$-pure threshold within this interval, or at least narrow down this interval to produce improved estimates.
-The number of ``guesses" is controlled by the option {\tt Attempts}, which conservatively defaults to 3.
-If {\tt Attempts} is set to 0, then {\tt guessFPT} is bypassed.
-If  {\tt Attempts} is set to at least 1, then a first check is run to verify whether the right-hand endpoint $(\nu+1)/p^e$ of the above interval \eqref{estimating-interval: e} the $F$-pure threshold.
+The number of ``guesses" is controlled by the option {\tt Attempts}, which conservatively defaults to {\tt 3}.
+If {\tt Attempts} is set to {\tt 0}, then {\tt guessFPT} is bypassed.
+If  {\tt Attempts} is set to at least {\tt 1}, then a first check is run to verify whether the right-hand endpoint $(\nu+1)/p^e$ of the above interval \eqref{estimating-interval: e} is the $F$-pure threshold.
 We illustrate this below.
@@
 
-If  {\tt Attempts} is set to at least 2, and the right-hand endpoint $(\nu+1)/p^e$ of the interval \eqref{estimating-interval: e} is not the $F$-pure threshold, then a second check is run to verify whether the left-hand endpoint $\nu/(p^e-1)$ of this interval is the $F$-pure threshold.
+If  {\tt Attempts} is set to at least {\tt 2} and the right-hand endpoint $(\nu+1)/p^e$ of the interval \eqref{estimating-interval: e} is not the $F$-pure threshold, then a second check is run to verify whether the left-hand endpoint $\nu/(p^e-1)$ of this interval is the $F$-pure threshold.
 
@@
 
-            If neither endpoint is the $F$-pure threshold, and {\tt Attempts} is set to more than 2, additional checks are performed at certain numbers within the interval .
+            If neither endpoint is the $F$-pure threshold and {\tt Attempts} is set to more than {\tt 2}, then  additional checks are performed at certain numbers within the interval .
 A number in the interval \eqref{estimating-interval: e} with minimal denominator is selected, and {\tt compareFPT} is used to test that number.
@@
 
-If {\tt guessFPT} is unsuccessful and {\tt UseFSignature} is set to {\tt true}, the fpt function proceeds to use the convexity of the $F$-signature function and a secant line argument to attempt to narrow down the interval bounding the $F$-pure threshold.
+If {\tt guessFPT} is unsuccessful and {\tt UseFSignature} is set to {\tt true}, then the {\tt fpt} function proceeds to use the convexity of the $F$-signature function and a secant line argument to attempt to narrow down the interval bounding the $F$-pure threshold.
 
@@
 
-When {\tt FRegularityCheck} is set to {\tt true} and no exact answer has been found, a final check is run (if necessary) to verify whether the final lower bound for the $F$-pure threshold is the exact answer.
+When {\tt FRegularityCheck} is set to {\tt true} and no exact answer has been found, a final check is run to verify whether the final lower bound for the $F$-pure threshold is the exact answer (if it has not already been eliminated as a possibility).
 
@@
 The computations performed when {\tt UseFSignature} and {\tt FRegularityCheck} are set to {\tt true} are often slow, and often fail to improve the estimate, and for this reason, these options should be used sparingly.
-            It is often more effective to increase the values of {\tt Attempts} or {\tt DepthOfSearch}, instead.
+            It is often more effective to increase the values of {\tt Attempts} or {\tt DepthOfSearch} instead.
 
@@
 
-i31: f = x^7*y^5*(x + y)^5*(x^2 + y^3)^4;
+i31 : f = x^7*y^5*(x + y)^5*(x^2 + y^3)^4;
 
@@
 
-As seen in several examples above, when the exact answer is not found, a list containing the endpoints of an interval containing the $F$-pure threshold of $f$ is returned.
+As seen in several examples above, when the exact  $F$-pure threshold of $f$ is not found, a list containing the endpoints of an interval containing its value is returned.
 Whether that interval is open, closed, or a mixed interval depends on the options passed; if the option {\tt Verbose} is set to {\tt true}, the precise interval will be printed.

### 2019-06-05 Fsing/FThresholdsPaper/FThresholds.tex

@@
              If the option {\tt UseSpecialAlgorithms} is set to {\tt true} (the default value), then {\tt fpt} first checks whether $f$ is diagonal polynomial, a binomial, or a form in two variables, in that order.
-             If it is one of these, algorithms of Hern\'andez \cite{HernandezFInvariantsOfDiagonalHyp, HernandezFPureThresholdOfBinomial}, or Hern\'andez and Teixeira \cite{HernandezTeixeiraFThresholdFunctions},  are executed to compute the $F$-pure threshold.
+             If it is one of these, algorithms of Hern\'andez \cite{HernandezFInvariantsOfDiagonalHyp, HernandezFPureThresholdOfBinomial}, or Hern\'andez and Teixeira \cite{HernandezTeixeiraFThresholdFunctions},  are executed to compute the $F$-pure threshold (cf.
+\cite{ShibutaTakagiLCThresholds}).
 

### 2019-06-05 Fsing/FThresholdsPaper/FThresholds.tex
Minor changes

@@
 
-This package builds heavily upon the \emph{TestIdeals} package for \emph{Macaulay2}, which provides a broad range of functionality in prime characteristic commutative algebra.
+This package builds heavily upon the \emph{TestIdeals} package for \emph{Macaulay2}, which provides a broad range of functionality in positive characteristic commutative algebra.
 
@@
 %Erin Bela, Juliette Bruce, Zhibek Kadyrsizova, Sara Malec, Maral Mostafazadehfard, Marcus Robinson, Dan Smolkin, and Robert Walker.
-We are also grateful the organizers of the \emph{Macaulay2} workshops where much of the functionality described herein was developed, hosted by Wake Forest University in 2012, the University of California, Berkeley in 2014 and 2017, Boise State University in 2015, and the University of Utah in 2016.
+We are also grateful to the organizers of the \emph{Macaulay2} workshops where much of the functionality described herein was developed, hosted by Wake Forest University in 2012, the University of California, Berkeley in 2014 and 2017, Boise State University in 2015, and the University of Utah in 2016.
 We are also grateful to the University of Utah for hosting a collaborative development visit in 2018, and to the Institute of Mathematics and its Applications for its support for the Coding Sprint \emph{F-thresholds in Macaulay2} in 2019, where the current version of the package was finalized and this paper was completed.
@@
 
-             If the option {\tt UseSpecialAlgorithms} is set to {\tt true} (the default value), then {\tt fpt} first checks whether $f$ is diagonal polynomial, a binomial, or a form in two variables, in that order.
+If the option {\tt UseSpecialAlgorithms} is set to {\tt true} (the default value), then {\tt fpt} first checks whether $f$ is a diagonal polynomial, a binomial, or a form in two variables, in that order.
 If it is one of these, algorithms of Hern\'andez \cite{HernandezFInvariantsOfDiagonalHyp, HernandezFPureThresholdOfBinomial}, or Hern\'andez and Teixeira \cite{HernandezTeixeiraFThresholdFunctions},  are executed to compute the $F$-pure threshold (cf.

### 2019-06-05 Fsing/FThresholdsPaper/FThresholds.tex
Added note indicating paper will need to change depending on how guessFPT changes

--- 2019-06-05 Fsing/FThresholdsPaper/FThresholds.tex
@@
 A number in the interval \eqref{estimating-interval: e} with minimal denominator is selected, and {\tt compareFPT} is used to test that number.
-If that ``guess" is correct, its value is returned; otherwise, the information returned by {\tt compareFPT} is used to narrow down the interval, and this process is repeated as many times as specified by {\tt Attempts}.
+{\color{red} This will need to get updated} If that ``guess" is correct, its value is returned; otherwise, the information returned by {\tt compareFPT} is used to narrow down the interval, and this process is repeated as many times as specified by {\tt Attempts}.
 

### 2019-06-05 Fsing/FThresholdsPaper/FThresholds.tex
minor rewording in the first page of the paper

@@
    This note describes the functionality implemented in the \emph{Macaulay2} package \emph{FThresholds}.
-   This package is designed to compute and estimate $F$-pure thresholds, more general $F$-thresholds, and related numerical invariants arising in the study of regularity conditions in positive characteristic commutative algebra.
+   This package is designed to compute and estimate $F$-pure thresholds, more general $F$-thresholds, and related numerical invariants arising in the study of singularities in positive characteristic commutative algebra.
 \end{abstract}
@@
 Recall that a ring $R$ of prime characteristic $p>0$ is said to be \emph{$F$-pure} if the Frobenius morphism $F \: R \to R$ sending an element to its $p^\text{th}$ power is a pure morphism (under geometric hypotheses, this is equivalent to the condition that the Frobenius morphism is split).
+Regular rings are always $F$-pure, but not conversely.
 The notion of $F$-purity first appeared in the work \cite{HochsterRobertsFrobeniusLocalCohomology}  of Hochster and Roberts to study local cohomology \cite{HochsterRobertsFrobeniusLocalCohomology}, was compared with rational singularities in  \cite{FedderFPureRat}, and was used globally to study properties of Schubert varieties in \cite{MehtaRamanathanFrobeniusSplittingAndCohomologyVanishing}.
 
-After the advent of tight closure \cite{HochsterHunekeTC1}, the usage of the Frobenius endomorphism to measure regularity conditions proliferated, and based on a strong connection discovered between $F$-pure and \emph{log canonical} singularities \cite{HaraWatanabeFRegFPure}, the notion of $F$-purity was generalized to pairs $(R, f^t)$, where $f$ is an element of $R$, and $t$ is a nonnegative real number considered a formal exponent.
+After the advent of tight closure \cite{HochsterHunekeTC1}, the usage of the Frobenius endomorphism to measure singularities proliferated, and based on a strong connection discovered between $F$-pure and \emph{log canonical} singularities \cite{HaraWatanabeFRegFPure}, the notion of $F$-purity was generalized to pairs $(R, f^t)$, where $f$ is an element of $R$, and $t$ is a nonnegative real number considered a formal exponent.
 

### 2019-06-05 Fsing/FThresholdsPaper/FThresholds.tex
Minor change to FThresholds paper
Minor changes to abstract of FThresholds

--- 2019-06-05 Fsing/FThresholdsPaper/FThresholds.tex
@@
 \email{witt@ku.edu}
-\thanks{E.E.~Witt was partially supported by NSF DMS \#1623035.}
+\thanks{E.~E.~Witt was partially supported by NSF DMS \#1623035.}
 \date{\today}
@@
    This note describes the functionality implemented in the \emph{Macaulay2} package \emph{FThresholds}.
-   This package is designed to compute and estimate $F$-pure thresholds, more general $F$-thresholds, and related numerical invariants arising in the study of regularity conditions in positive characteristic commutative algebra.
+   This package is designed to compute and estimate $F$-pure thresholds, more general $F$-thresholds, and related numerical invariants used to study singularities in positive characteristic.
 \end{abstract}

### 2019-06-05 Fsing/FThresholdsPaper/FThresholds.tex
Fixed a merge.

--- 2019-06-05 Fsing/FThresholdsPaper/FThresholds.tex
@@
+<<<<<<< HEAD
 \documentclass{amsart}
@@
 \thanks{E.E.~Witt was partially supported by NSF DMS \#1623035.}
+\date{\today}
+
+\begin{abstract}
+   This note describes the functionality implemented in the \emph{Macaulay2} package \emph{FThresholds}.
+   This package is designed to compute and estimate $F$-pure thresholds, more general $F$-thresholds, and related numerical invariants arising in the study of regularity conditions in positive characteristic commutative algebra.
+\end{abstract}
+
+\subjclass[2010]{13A35}%=
+
+\keywords{Macaulay2, Frobenius, $F$-singularity, $F$-pure threshold, $F$-threshold}
+
+\maketitle
+
+\section{Introduction}
+
+This paper describes the \emph{Macaulay2} \cite{M2} package \emph{FThresholds}, which provides tools for computing certain fundamental invariants arising in positive characteristic commutative algebra, namely, \emph{$F$-pure thresholds}, \emph{$F$-thresholds}, and \emph{$F$-jumping exponents}.
+Recall that a ring $R$ of prime characteristic $p>0$ is said to be \emph{$F$-pure} if the Frobenius morphism $F \: R \to R$ sending an element to its $p^\text{th}$ power is a pure morphism (under geometric hypotheses, this is equivalent to the condition that the Frobenius morphism is split).
+The notion of $F$-purity first appeared in the work \cite{HochsterRobertsFrobeniusLocalCohomology}  of Hochster and Roberts to study local cohomology \cite{HochsterRobertsFrobeniusLocalCohomology}, was compared with rational singularities in  \cite{FedderFPureRat}, and was used globally to study properties of Schubert varieties in \cite{MehtaRamanathanFrobeniusSplittingAndCohomologyVanishing}.
+
+After the advent of tight closure \cite{HochsterHunekeTC1}, the usage of the Frobenius endomorphism to measure regularity conditions proliferated, and based on a strong connection discovered between $F$-pure and \emph{log canonical} singularities \cite{HaraWatanabeFRegFPure}, the notion of $F$-purity was generalized to pairs $(R, f^t)$, where $f$ is an element of $R$, and $t$ is a nonnegative real number considered a formal exponent.
+
+Along these lines, the notion of the \emph{$F$-pure threshold} was defined in analogy with the \emph{log canonical threshold} \cite{TakagiWatanabeFPureThresh,MustataTakagiWatanabeFThresholdsAndBernsteinSato}.
+The $F$-pure threshold of the pair $(R, f)$ is the supremum over all $t$ for which $(R, f^t)$ is $F$-pure.  
+Furthermore, \emph{$F$-threholds} were introduced, a family of invariants that naturally extends the notion of an $F$-pure threshold.
+
+These numerical invariants are typically difficult to calculate,
+and due to their significance, have been the focus of intense study over the past fifteen years.
+To this end, the \emph{Macaulay2} package \emph{FThresholds} is centered around calculating and estimating the $F$-pure threshold and other $F$-thresholds, with the function {\tt fpt} at its core.
+
+There are three main sections in this paper, which describe and illustrate the main functionality implemented in the package \emph{FThresholds}.
+\begin{itemize}
+\item \autoref{sec.Nu} describes the methods implemented for approximating the $F$-pure threshold and other $F$-thresholds.  
+\item \autoref{sec.IsFPT} explains the package's functionality for determining whether a given number is the $F$-pure threshold, or more generally, an \emph{$F$-jumping exponent}.
+\item \autoref{sec.FPT} describes the features of the central function of the package, {\tt fpt}. 
+\end{itemize}
+
+This package builds heavily upon the \emph{TestIdeals} package for \emph{Macaulay2}, which provides a broad range of functionality in positive characteristic commutative algebra.
+
+\subsection*{Acknowledgements.}  First and foremost, the authors enthusiastically thank all authors and contributors to the \emph{FThresholds} package: (INSERT NAMES HERE).
+%Erin Bela, Juliette Bruce, Zhibek Kadyrsizova, Sara Malec, Maral Mostafazadehfard, Marcus Robinson, Dan Smolkin, and Robert Walker.
+We are also grateful to the organizers of the \emph{Macaulay2} workshops where much of the functionality described herein was developed, hosted by Wake Forest University in 2012, the University of California, Berkeley in 2014 and 2017, Boise State University in 2015, and the University of Utah in 2016.
+We are also grateful to the University of Utah for hosting a collaborative development visit in 2018, and to the Institute of Mathematics and its Applications for its support for the Coding Sprint \emph{F-thresholds in Macaulay2} in 2019, where the current version of the package was finalized and this paper was completed.
+
+\section{The $F$-pure threshold limit and {\tt nu}}
+\label{sec.Nu}
+
+Suppose $R = k[x_1, \dots, x_n]$ is a polynomial ring over a finite field and $f \in R$.
+If $f^a \notin \langle x_1^{p^e}, \dots, x_n^{p^e} \rangle = \fram^{[p^e]}$, then the pair $(R, f^{a/(p^e -1)})$ is $F$-pure at the origin, whereas if $f^a \in \fram^{[p^e]}$, then the pair $(R, f^{a/p^e})$ is not $F$-pure at the origin.
+By finding the $a \in \bZ$ where that transition happens, and then limiting over $e$, one can compute the $F$-pure threshold.
+See \cite{MustataTakagiWatanabeFThresholdsAndBernsteinSato}.
+
+We set $\nu(e, f)$ to be largest $a \in \bZ$ such that $f^a \notin \fram^{[p^e]}$ (note in the literature, it is frequently denoted by $\nu_f(p^e)$.  It immediately follows that 
+\[
+\fpt(f) = \lim_{e \to \infty} {\nu(e, f) \over p^e}.
+\]
+These numbers $\nu(e, f)$ can be computed using the command {\tt nu}, as in the example below.  
+\medskip
+{\small
+\setstretch{.67}
+\begin{MyVerbatim}
+i1 : loadPackage "FThresholds"
+
+o1 = FThresholds
+
+o1 : Package
+
+i2 : R = ZZ/7[x,y]
+
+o2 = R
+
+o2 : PolynomialRing
+
+i3 : f = y^2 - x^3
+
+        3    2
+o3 = - x  + y
+
+o3 : R
+
+i4 : nu(1, f)
+
+o4 = 5
+
+o4 : QQ
+
+i5 : nu(2, f)
+
+o5 = 40
+
+o5 : QQ
+
+i6 : nu(3, f)
+
+o6 = 285
+
+o6 : QQ
+\end{MyVerbatim}
+}
+\medskip
+The numbers $5/7, 40/49, 285/343$ then approximate the $F$-pure threshold, which in this case happens to equal $5/6$.
+By default, if the function $f$ has a special form (is diagonal or binomial), then the function does not check whether $f^a$ is in  $\langle x_1^{p^e}, \dots, x_n^{p^e} \rangle$, but instead uses general formulas for $\nu$s, see \cite{HernandezFPureThresholdOfBinomial,HernandezFInvariantsOfDiagonalHyp}.
+
+In fact, one can make the following more general definition.  If $I$ and $J$ are two ideals (with $I \subseteq \sqrt{J}$), one can define
+\[
+\nu(e, I, J) = \max \{ n \in \bZ \; |\; I^n \not\subseteq J^{[p^e]} \}.
+\]
+This is frequently denoted by $\nu_I^J(p^e)$ in the literature.
+In the case that $I = \langle f \rangle$ and $J = \fram$, this just recovers the $\nu$'s defined above; the limit of which is the $F$-pure threshold.
+For more general $I$ and $J$, the limit
+\[
+\lim_{e \to \infty} {\nu(e, I, J) \over p^e}
+\]
+is called the \emph{$F$-threshold of $I$ with respect to $J$}.
+To compute these values we use a binary search, unless the user specifies that we should use a linear search instead {\tt Search=>Linear}.
+
+There is one more option that deserves mentioning, {\tt ContainmentTest}.  There are two ways to check whether $f^a$ (or $I^a$) is contained in $J^{[p^e]}$.  In general it is true that
+\[
+I^a \subseteq J^{[p^e]} \text{ $\Leftrightarrow$ } (I^a)^{[1/p^e]} \subseteq J
+\]
+where $\bullet^{[1/p^e]}$ is defined as in the {\tt TestIdeals} package.
+Which of these two strategies to use is controlled by the option {\tt ContainmentTest => StandardPower} and {\tt ContainmentTest => FrobeniusRoot} respectively.
+For principal $I$, the command on the right is generally faster (and so {\tt FrobeniusRoot} is the default strategy for computing $\nu$).
+For non-principal $I$, frequently the command on the left is quicker, and so {\tt StandardPower} is default strategy.
+
+Finally, the option {\tt ContainmentTest => FrobeniusPower}, then ${\tt \nu(e, I, A)}$ computes the largest integer $n$ such that
+\[
+I^{[p^n]} \subseteq J^{[p^e]}.
+\]
+See \cite{HernandezTeixeiraWittFrobeniusPowers} for more discussion of this.
+
+\section{{\tt isFPT}, {\tt compareFPT} and {\tt isFJumpingExponent}}
+\label{sec.IsFPT}
+
+The command {\tt isFPT(t, f)} checks whether $t$ is the $F$-pure threshold of $f$.  In general this does this by computing two test ideals:
+\[
+\tau(R, f^t) \text{ and } \tau(R, f^{t-\epsilon}).
+\]
+It follows that $\fpt(f) = t$ if and only if $\tau(R, f^t) \neq R$ and $\tau(R, f^{t-\epsilon}) = R$.
+The function computes these two values by using the {\tt testIdeal} and {\tt FPureModule} commands from the {\tt TestIdeals} package.
+Note that in a strongly $F$-regular Gorenstein ambient ring, {\tt FPureModule(t, f)} computes exactly $\tau(R, f^{t-\epsilon})$.
+These commands work more generally, but they \emph{only} currently work when $R$ is $\bQ$-Gorenstein with index not divisible by the characteristic $p > 0$.
+A more general version of this command is {\tt compareFPT(t, f)} which returns $-1$ if $t < \fpt(f)$, $0$ if $t = \fpt(f)$ and $1$ if $t > \fpt(f)$.
+
+Consider the following example which has $F$-pure threshold equal to {1/2}, see \cite[Example 4.3]{MustataYoshidaTestIdealVsMultiplierIdeals}.
+\medskip
+{\small
+\setstretch{.67}
+\begin{MyVerbatim}
+i1 : loadPackage "FThresholds"
+
+o1 = FThresholds
+
+o1 : Package
+
+i2 : R = ZZ/2[x,y,z];
+
+i3 : f = x^2+y^5+z^5;
+
+i4 : isFPT(1/2, f)
+
+o4 = true
+
+i5 : isFPT(1/3, f)
+
+o5 = false
+
+i6 : compareFPT(3/4, f)
+
+o6 = 1
+\end{MyVerbatim}
+}
+\medskip
+
+The command {\tt isFJumpingExponent} is implemented similarly, a value $t$ is an $F$-jumping exponent if and only if
+\[
+\tau(R, f^t) \neq \tau(R, f^{t-\epsilon}).  
+\]
+Again, this command works as long as $R$ is $\bQ$-Gorenstein with index not divisible by $p$.
+
+\newpage
+\section{The {\tt fpt} function}
+\label{sec.FPT}
+
+The core function in this package is the {\tt fpt} function.
+Throughout this section, let $f$ be a polynomial with coefficients in a finite field of characteristic $p$.
+When passed the polynomial $f$, the function {\tt fpt} attempts to find the exact value for the $F$-pure threshold of $f$ at the origin, and returns that value, if possible.
+Otherwise, it returns lower and upper bounds for the $F$-pure threshold, as demonstrated below.
+
+{\small
+\setstretch{.67}
+\begin{MyVerbatim}
+
+i1 : ZZ/5[x,y,z];
+
+i2 : fpt( x^3 + y^3 + z^3 + x*y*z )
+
+     4
+o2 = -
+     5
+
+o2 : QQ
+
+i3 : fpt( x^5 + y^6 + z^7 + (x*y*z)^3 )
+
+      1  2
+o3 = {-, -}
+      3  5
+
+o3 : List
+
+\end{MyVerbatim}
+}
+
+If the option {\tt UseSpecialAlgorithms} is set to {\tt true} (the default value), then {\tt fpt} first checks whether $f$ is a diagonal polynomial, a binomial, or a form in two variables, in that order.
+If it is one of these, algorithms of Hern\'andez \cite{HernandezFInvariantsOfDiagonalHyp, HernandezFPureThresholdOfBinomial}, or Hern\'andez and Teixeira \cite{HernandezTeixeiraFThresholdFunctions},  are executed to compute the $F$-pure threshold (cf.
+\cite{ShibutaTakagiLCThresholds}).
+
+{\small
+\setstretch{.67}
+\begin{MyVerbatim}
+
+i4 : fpt( x^17 + y^20 + z^24 ) -- a diagonal polynomial
+
+      94
+o4 = ---
+     625
+
+i5 : fpt( x^2*y^6*z^10 + x^10*y^5*z^3 ) -- a binomial
+
+      997
+o5 = ----
+     6250
+
+o5 : QQ
+
+i6 : ZZ/5[x,y];
+
+i7 : fpt( x^2*y^6*(x + y)^9*(x + 3*y)^10 ) -- a form in two variables
+
+      5787
+o7 = -----
+     78125
+
+o7 : QQ
+
+\end{MyVerbatim}
+}
+
+The above noted algorithm for computing the $F$-pure threshold of a binary form $f$ requires factoring $f$ into linear forms, and {\tt fpt} can sometimes hang when attempting that factorization.
+For this reason, when a factorization is already known, the user can pass to {\tt fpt} a list containing all the pairwise prime linear factors of $f$, and a list containing their respective multiplicities.
+
+{\small
+\setstretch{.67}
+\begin{MyVerbatim}
+
+i8 : L = {x, y, x + y, x + 3*y};
+
+i9 : m = {2, 6, 9, 10};
+
+i10 : fpt(L, m)==o7
+
+o10 = true
+
+\end{MyVerbatim}
+}
+
+In the remainder of this section, we describe the {\tt fpt} function when no special algorithm is available, or {\tt UseSpecialAlgorithms} is set to {\tt false},  as well as the roles of the options {\tt DepthOfSearch}, and {\tt Attempts}, both nonnegative integers.
+
+In this case, very roughly speaking, the {\tt fpt} function will either compute, and output, the exact value of the $F$-pure threshold of $f$, and otherwise recursively compute a finite sequence of lower and upper bounds for this value, and output the last of these, which will be the tightest among all computed.
+The value of the option {\tt DepthOfSearch} determines the precision of the initial set of bounds, and the option {\tt Attempts}, in conjunction with some various subroutines, determines whether, and how, to produce new, tighter bounds from the previous ones.
+
+In more detail, let $e$ denote the value of the option {\tt DepthOfSearch}, which conservatively defaults to {\tt 1}.
+The {\tt fpt} function first computes $\nu=\nu_f(p^e)$, which agrees with the output of {\tt nu(e,f)}.
+It is well known that the $F$-pure threshold of $f$ is greater than $\nu/p^e$ and at most $(\nu+1)/p^e$, and applying  \cite[Proposition 4.2]{HernandezFPurityOfHypersurfaces} to this lower bound tells us that the $F$-pure threshold of $f$ must be at least $\nu/(p^e-1)$.
+In summary, we know that the $F$-pure threshold of $f$ must lie in the closed interval
+%
+\begin{equation}
+\label{estimating-interval: e}
+\tag{$\dagger$}
+\left[ \frac{\nu}{p^e-1}, \frac{\nu+1}{p^e} \right].
+\end{equation}
+
+With these estimates in hand, the subroutine {\tt guessFPT} is called to make some ``educated guesses" in an attempt to identify the $F$-pure threshold within this interval, or at least narrow down this interval to produce improved estimates.
+The number of ``guesses" is controlled by the option {\tt Attempts}, which conservatively defaults to {\tt 3}.
+If {\tt Attempts} is set to {\tt 0}, then {\tt guessFPT} is bypassed.
+If  {\tt Attempts} is set to at least {\tt 1}, then a first check is run to verify whether the right-hand endpoint $(\nu+1)/p^e$ of the above interval \eqref{estimating-interval: e} is the $F$-pure threshold.
+We illustrate this below.
+
+{\small
+\setstretch{.67}
+\begin{MyVerbatim}
+
+i11 : f = x^2*(x + y)^3*(x + 3*y^2)^5;
+
+i12 : fpt( f, Attempts => 0 ) -- a bad estimate
+
+          1
+o12 = {0, -}
+          5
+
+o12 : List
+
+i13 : fpt( f, Attempts => 0, DepthOfSearch => 3 ) -- a better estimate
+
+        21   22
+o13 = {---, ---}
+       124  125
+
+o13 : List
+
+i14 : fpt( f, Attempts => 1, DepthOfSearch => 3 ) -- the right-hand
+
+      endpoint (nu+1)/p^e is the F-pure threshold
+
+       22
+o14 = ---
+      125
+
+o14 : QQ
+
+\end{MyVerbatim}
+}
+
+If  {\tt Attempts} is set to at least {\tt 2} and the right-hand endpoint $(\nu+1)/p^e$ of the interval \eqref{estimating-interval: e} is not the $F$-pure threshold, then a second check is run to verify whether the left-hand endpoint $\nu/(p^e-1)$ of this interval is the $F$-pure threshold.
+
+{\small
+\setstretch{.67}
+\begin{MyVerbatim}
+
+i15 : f = x^6*y^4 + x^4*y^9 + (x^2 + y^3)^3;
+
+i16 : fpt( f, Attempts => 1, DepthOfSearch => 3 )
+
+       17   7
+o16 = {--, --}
+       62  25
+
+o16 : List
+
+i17 : fpt( f, Attempts => 2, DepthOfSearch => 3 ) -- the left-hand endpoint
+
+      nu/(p^e-1) is the F-pure threshold
+
+      17
+o17 = --
+      62
+
+o17 : QQ
+
+\end{MyVerbatim}
+}
+
+            If neither endpoint is the $F$-pure threshold and {\tt Attempts} is set to more than {\tt 2}, then  additional checks are performed at certain numbers within the interval .
+A number in the interval \eqref{estimating-interval: e} with minimal denominator is selected, and {\tt compareFPT} is used to test that number.
+If that ``guess" is correct, its value is returned; otherwise, the information returned by {\tt compareFPT} is used to narrow down the interval, and this process is repeated as many times as specified by {\tt Attempts}.
+
+{\small
+\setstretch{.67}
+\begin{MyVerbatim}
+
+i18 : f = x^3*y^11*(x + y)^8*(x^2 + y^3)^8;
+
+i19 : fpt( f, DepthOfSearch => 3, Attempts => 2 )
+
+        3   7
+o19 = {--, ---}
+       62  125
+
+o19 : List
+
+i20 : fpt( f, DepthOfSearch => 3, Attempts => 3 ) -- an additional check
+
+      sharpens the estimate
+
+        3   1
+o20 = {--, --}
+       62  18
+
+o20 : List
+
+i21 : fpt( f, DepthOfSearch => 3, Attempts => 4 ) -- and one more finds
+
+      the answer
+
+       1
+o21 = --
+      19
+
+o21 : QQ
+
+\end{MyVerbatim}
+}
+
+If {\tt guessFPT} is unsuccessful and {\tt UseFSignature} is set to {\tt true}, then the {\tt fpt} function proceeds to use the convexity of the $F$-signature function and a secant line argument to attempt to narrow down the interval bounding the $F$-pure threshold.
+
+{\small
+\setstretch{.67}
+\begin{MyVerbatim}
+
+i22 : f = x^5*y^6*(x + y)^9*(x^2 + y^3)^4;
+
+i23 : fpt( f, DepthOfSearch => 3 )
+
+        2   1
+o23 = {--, --}
+       31  14
+
+o23 : List
+
+i24 : fpt( f, DepthOfSearch => 3, UseFSignature => true )
+
+        181   1
+o24 = {----, --}
+       2750  14
+
+o24 : List
+
+i25 : numeric o23
+
+o25 = {.0645161, .0714286}
+
+o25 : List
+
+i26 : numeric o24 -- UseFSignature sharpened the estimate a bit
+
+o26 = {.0658182, .0714286}
+
+o26 : List
+
+\end{MyVerbatim}
+}
+
+When {\tt FRegularityCheck} is set to {\tt true} and no exact answer has been found, a final check is run to verify whether the final lower bound for the $F$-pure threshold is the exact answer (if it has not already been eliminated as a possibility).
+
+{\small
+\setstretch{.67}
+\begin{MyVerbatim}
+
+i27 : f = (x + y)^4*(x^2 + y^3)^6;
+
+i28 : fpt( f, Attempts => 2, DepthOfSearch => 3 )
+
+        3   13
+o28 = {--, ---}
+       31  125
+
+o28 : List
+
+i29 : fpt( f, Attempts => 2, DepthOfSearch => 3, UseFSignature => true ) --
+
+      UseFSignature improves the answer a bit
+
+        1   13
+o29 = {--, ---}
+       10  125
+
+o29 : List
+
+i30 : fpt( f, Attempts => 2, DepthOfSearch => 3, UseFSignature => true,
+
+      FRegularityCheck => true ) -- FRegularityCheck finds the answer
+
+       1
+o30 = --
+      10
+
+o30 : QQ
+
+\end{MyVerbatim}
+}
+
+The computations performed when {\tt UseFSignature} and {\tt FRegularityCheck} are set to {\tt true} are often slow, and often fail to improve the estimate, and for this reason, these options should be used sparingly.
+            It is often more effective to increase the values of {\tt Attempts} or {\tt DepthOfSearch} instead.
+
+{\small
+\setstretch{.67}
+\begin{MyVerbatim}
+
+i31 : f = x^7*y^5*(x + y)^5*(x^2 + y^3)^4;
+
+i32 : timing numeric fpt( f, DepthOfSearch => 3, UseFSignature => true,
+
+      FRegularityCheck => true )
+
+o32 = {.0733061, .0769231}
+      -- 2.68899 seconds
+
+o32 : Time
+
+i33 : timing numeric fpt( f, Attempts => 5, DepthOfSearch => 3 ) -- a better
+
+      answer in less time
+
+o33 = {.075, .0769231}
+      -- .893389 seconds
+
+o33 : Time
+
+i34 : timing fpt( f, DepthOfSearch => 4 ) -- the exact answer in even less 
+      time
+
+       48
+o34 = ---
+      625
+      -- .361882 seconds
+
+o34 : Time
+
+\end{MyVerbatim}
+}
+
+As seen in several examples above, when the exact  $F$-pure threshold of $f$ is not found, a list containing the endpoints of an interval containing its value is returned.
+Whether that interval is open, closed, or a mixed interval depends on the options passed; if the option {\tt Verbose} is set to {\tt true}, the precise interval will be printed.
+
+{\small
+\setstretch{.67}
+\begin{MyVerbatim}
+
+i35 : f = x^7*y^5*(x + y)^5*(x^2 + y^3)^4;
+
+i36 : fpt( f, DepthOfSearch => 3, UseFSignature => true, Verbose => true )
+
+Starting fpt ...
+
+fpt is not 1 ...
+
+Verifying if special algorithms apply...
+
+Special fpt algorithms were not used ...
+
+nu has been computed: nu = nu(3,f) = 9 ...
+
+fpt lies in the interval [ nu/(p^e-1), (nu+1)/p^e ] = [ 9/124, 2/25 ] ...
+
+Starting guessFPT ...
+
+The right-hand endpoint is not the fpt ...
+
+The left-hand endpoint is not the fpt ...
+
+guessFPT narrowed the interval down to ( 9/124, 1/13 ) ...
+
+Beginning F-signature computation ...
+
+First F-signature computed: s(f,(nu-1)/p^e) = 456/15625 ...
+
+Second F-signature computed: s(f,nu/p^e) = 64/15625 ...
+
+Computed F-signature secant line intercept: 449/6125 ...
+
+F-signature intercept is an improved lower bound ...
+
+fpt failed to find the exact answer; try increasing the value of
+
+DepthOfSearch or Attempts.
+
+fpt lies in the interval [ 449/6125, 1/13 ).
+
+        449   1
+o36 = {----, --}
+       6125  13
+
+o36 : List
+
+\end{MyVerbatim}
+}
+
+\newpage
+\bibliographystyle{skalpha}
+\bibliography{MainBib}
+
+\end{document}
+=======
+\documentclass{amsart}
+\usepackage{calc,amssymb,amsthm,amsmath,setspace}
+\RequirePackage[dvipsnames,usenames]{xcolor}
+
+\usepackage{fancyvrb}
+\usepackage{hyperref}
+\hypersetup{
+bookmarks,
+bookmarksdepth=3,
+bookmarksopen,
+bookmarksnumbered,
+pdfstartview=FitH,
+colorlinks,backref,hyperindex,
+linkcolor=Sepia,
+anchorcolor=BurntOrange,
+citecolor=MidnightBlue,
+citecolor=OliveGreen,
+filecolor=BlueViolet,
+menucolor=Yellow,
+urlcolor=OliveGreen
+}
+\usepackage{xspace}
+%\usepackage{rotating}
+\interfootnotelinepenalty=100000
+
+\usepackage{mabliautoref}
+\usepackage{colonequals}
+\frenchspacing
+\input{kmacros3.sty}
+
+\usepackage{verbatim}
+\usepackage{enumerate}
+\usepackage[normalem]{ulem}
+%\usepackage{marginnote}
+\newcommand{\fram}{\mathfrak{m}}
+\DefineVerbatimEnvironment%
+{MyVerbatim}{Verbatim}
+{formatcom=\color{Violet}}
+
+\begin{document}
+\title{The  \emph{FThresholds} package for \emph{Macaulay2}}
+%\author[Alberto F.\ Boix et al.]{Alberto F.\ Boix}
+%\address{Department of Mathematics, Ben-Gurion University of the Negev, Beer-Sheva 8410501, Israel}
+%\email{fernanal@post.bgu.ac.il}
+%\thanks{A.F.\,Boix was supported by Israel Science Foundation (grant No. 844/14) and Spanish Ministerio de Econom\'ia y Competitividad MTM2016-7881-P}
+
+\author[]{Daniel J.\ Hern\'andez}
+\address{Department of Mathematics, University of Kansas, Lawrence, KS~66045, USA}
+\email{hernandez@ku.edu}
+\thanks{D.~J.~Hern\'andez was partially supported by NSF DMS \#1600702.}
+
+%\author[]{Zhibek Kadyrsizova}
+%\address{School of Science and Technology, Nazarbayev University, Astana, 010000, Republic of Kazakhstan}
+%\email{zhibek.kadyrsizova@nu.edu.kz}
+%\thanks{Z. Kadyrsizova was partially supported by NSF DMS \#1401384 and the Barbour Scholarship at the University of Michigan.}
+
+%\author[]{Mordechai Katzman}
+%\address{Department of Pure Mathematics, University of Sheffield, Sheffield S37RH, United Kingdom}
+%\email{M.Katzman@sheffield.ac.uk}
+
+%\author[]{Sara Malec}
+%\address{Department of Mathematics, Hood College, Frederick, MD 21701}
+%\email{malec@hood.edu}
+
+%\author[]{Marcus Robinson}
+%\address{Department of Mathematics, University of Utah, Salt Lake City, UT~84112, USA}
+%\email{robinson@math.utah.edu}
+
+\author[]{Karl Schwede}
+\address{Department of Mathematics, University of Utah, Salt Lake City, UT~84112, USA}
+\thanks{K.~Schwede was supported by NSF CAREER Grant DMS \#1252860/1501102, NSF FRG Grant DMS \#1265261/1501115, NSF grant \#1801849 and a Sloan Fellowship.}
+\email{schwede@math.utah.edu}
+
+%\author[]{Daniel Smolkin}
+%\address{Department of Mathematics, University of Utah, Salt Lake City, UT~84112, USA}
+%\email{smolkin@math.utah.edu}
+%\thanks{D.~Smolkin was supported by NSF RTG Grant DMS \#1246989, NSF CAREER Grant DMS \#1252860/1501102, and NSF FRG Grant DMS \#1265261/1501115.}
+
+\author[]{Pedro Teixeira}
+\address{Department of Mathematics, Knox College, Galesburg, IL~61401, USA}
+\email{pteixeir@knox.edu}
+
+\author[]{Emily E.\ Witt}
+\address{Department of Mathematics, University of Kansas, Lawrence, KS~66045, USA}
+\email{witt@ku.edu}
+\thanks{E.~E.~Witt was partially supported by NSF DMS \#1623035.}
 \date{\today}
@@
 \end{document}
+>>>>>>> 2e306beb6cc1089c385fac71a648f6eb591d9508

### 2019-06-06 Fsing/FThresholdsPaper/FThresholds.tex
minor updates to paper

--- 2019-06-05 Fsing/FThresholdsPaper/FThresholds.tex
@@
    This note describes the functionality implemented in the \emph{Macaulay2} package \emph{FThresholds}.
-   This package is designed to compute and estimate $F$-pure thresholds, more general $F$-thresholds, and related numerical invariants arising in the study of singularities in positive characteristic commutative algebra.
+   This package is designed to compute and estimate $F$-pure thresholds, more general $F$-thresholds, and related numerical invariants arising in the study of singularities in prime characteristic commutative algebra.
 \end{abstract}
@@
 The numbers $5/7, 40/49, 285/343$ then approximate the $F$-pure threshold, which in this case happens to equal $5/6$.
-By default, if the function $f$ has a special form (is diagonal or binomial), then the function does not check whether $f^a$ is in  $\langle x_1^{p^e}, \dots, x_n^{p^e} \rangle$, but instead uses general formulas for $\nu$s, see \cite{HernandezFPureThresholdOfBinomial,HernandezFInvariantsOfDiagonalHyp}.
+By default, if the function $f$ has a special form (is a diagonal polynomial or a binomial), then the function does not check whether $f^a$ is in  $\langle x_1^{p^e}, \dots, x_n^{p^e} \rangle$, but instead uses general formulas for $\nu$s, see \cite{HernandezFPureThresholdOfBinomial,HernandezFInvariantsOfDiagonalHyp}.
 
@@
 
-The command {\tt isFPT(t, f)} checks whether $t$ is the $F$-pure threshold of $f$.  In general this does this by computing two test ideals:
-\[
-\tau(R, f^t) \text{ and } \tau(R, f^{t-\epsilon}).
-\]
-It follows that $\fpt(f) = t$ if and only if $\tau(R, f^t) \neq R$ and $\tau(R, f^{t-\epsilon}) = R$.
+Given a rational number $t$ and  an element $f$ of a $\mathbb{Q}$-Gorenstein ring $R$ of characteristic $p>0$, 
+the command {\tt isFPT(t, f)} checks whether $t$ is the $F$-pure threshold of $f$.  In general, this is done by computing the \emph{test ideals}
+$\tau(R, f^t)$ and $\tau(R, f^{t-\epsilon})$; 
+the $F$-pure threshold equals $t$ if and only if $\tau(R, f^{t-\epsilon}) = R$, but  $\tau(R, f^t)$ is proper.
 The function computes these two values by using the {\tt testIdeal} and {\tt FPureModule} commands from the {\tt TestIdeals} package.
@@
 
-             If the option {\tt UseSpecialAlgorithms} is set to {\tt true} (the default value), then {\tt fpt} first checks whether $f$ is diagonal polynomial, a binomial, or a form in two variables, in that order.
+             If the option {\tt UseSpecialAlgorithms} is set to {\tt true} (the default value), then {\tt fpt} first checks whether $f$ is a diagonal polynomial, a binomial, or a form in two variables, in that order.
              If it is one of these, algorithms of Hern\'andez \cite{HernandezFInvariantsOfDiagonalHyp, HernandezFPureThresholdOfBinomial}, or Hern\'andez and Teixeira \cite{HernandezTeixeiraFThresholdFunctions},  are executed to compute the $F$-pure threshold (cf.

### 2019-06-06 Fsing/FThresholdsPaper/FThresholds.tex
Updates to Section 3 of paper

@@
 Given a rational number $t$ and  an element $f$ of a $\mathbb{Q}$-Gorenstein ring $R$ of characteristic $p>0$, 
-the command {\tt isFPT(t, f)} checks whether $t$ is the $F$-pure threshold of $f$.  In general, this is done by computing the \emph{test ideals}
-$\tau(R, f^t)$ and $\tau(R, f^{t-\epsilon})$; 
-the $F$-pure threshold equals $t$ if and only if $\tau(R, f^{t-\epsilon}) = R$, but  $\tau(R, f^t)$ is proper.
-The function computes these two values by using the {\tt testIdeal} and {\tt FPureModule} commands from the {\tt TestIdeals} package.
-Note that in a strongly $F$-regular Gorenstein ambient ring, {\tt FPureModule(t, f)} computes exactly $\tau(R, f^{t-\epsilon})$.
-These commands work more generally, but they \emph{only} currently work when $R$ is $\bQ$-Gorenstein with index not divisible by the characteristic $p > 0$.
-A more general version of this command is {\tt compareFPT(t, f)} which returns $-1$ if $t < \fpt(f)$, $0$ if $t = \fpt(f)$ and $1$ if $t > \fpt(f)$.
+the command {\tt isFPT(t, f)} checks whether $t$ is the $F$-pure threshold of $f$.  
+In general, this is done by computing the \emph{test ideal} associated to the pair $(R, f^t)$, and that associated when $t$ is replaced with a value less than $t$ that is very close to $t$, that associated to the pair $(R, f^{t-\epsilon}s)$.
+These values are computed using the functions 
+{\tt testIdeal} and {\tt FPureModule} from the \emph{TestIdeals} package
+(CITE THE TEST IDEALS PACKAGE PAPER).
+In fact, $t$ is the $F$-pure threshold of $f$ if and only if $\tau(R, f^{t-\epsilon})$ is $R$, but  $\tau(R, f^t)$ is a proper ideal.  
+Note that when $R$ is a strongly $F$-regular Gorenstein ring, {\tt FPureModule(t, f)} precisely computes $\tau(R, f^{t-\epsilon})$.
+\textcolor{red}{These commands work more generally, but they \emph{only} currently work when $R$ is $\bQ$-Gorenstein, with index not divisible by $p$.}
+
+The function {\tt compareFPT} provides further information about the relationship between $t$ and the $F$-pure threshold of $f$.  Namely, 
+{\tt compareFPT(t, f)} returns {\tt-1} when $t < \fpt(f)$, $0$ when $t = \fpt(f)$ and $1$ when $t > \fpt(f)$.
 

### 2019-06-06 Fsing/FThresholdsPaper/FThresholds.tex
Edits to Section 3 of the FThresholds paper

@@
 
-Consider the following example which has $F$-pure threshold equal to {1/2}, see \cite[Example 4.3]{MustataYoshidaTestIdealVsMultiplierIdeals}.
+Consider the following example.  Here, the $F$-pure threshold of $f$ equals to $1/2$; see \cite[Example 4.3]{MustataYoshidaTestIdealVsMultiplierIdeals}.
 \medskip
@@
 
-The command {\tt isFJumpingExponent} is implemented similarly, a value $t$ is an $F$-jumping exponent if and only if
-\[
-\tau(R, f^t) \neq \tau(R, f^{t-\epsilon}).
-\]
-Again, this command works as long as $R$ is $\bQ$-Gorenstein with index not divisible by $p$.
+The function {\tt isFJumpingExponent} is implemented in a similar way, using the fact that a value $t$ is an $F$-jumping exponent if and only if the test ideals 
+$\tau(R, f^t)$ and $\tau(R, f^{t-\epsilon})$ differ. 
+Again, this command is implemented in rings that are $\bQ$-Gorenstein with index not divisible by $p$.
 

### 2019-06-06 Fsing/FThresholdsPaper/FThresholds.tex
More updates to Section 3 -- still in progress

@@
 %\thanks{Z. Kadyrsizova was partially supported by NSF DMS \#1401384 and the Barbour Scholarship at the University of Michigan.}
-
-%\author[]{Mordechai Katzman}
-%\address{Department of Pure Mathematics, University of Sheffield, Sheffield S37RH, United Kingdom}
-%\email{M.Katzman@sheffield.ac.uk}
 
@@
 
-\subsection*{Acknowledgements.}  First and foremost, the authors enthusiastically thank all authors and contributors to the \emph{FThresholds} package: (INSERT NAMES HERE).
+\subsection*{Acknowledgements.}  First and foremost, the authors enthusiastically thank all authors 
+and contributors to the \emph{FThresholds} package: (INSERT NAMES HERE).
 %Erin Bela, Juliette Bruce, Zhibek Kadyrsizova, Sara Malec, Maral Mostafazadehfard, Marcus Robinson, Dan Smolkin, and Robert Walker.
@@
 
-Given a rational number $t$ and  an element $f$ of a $\mathbb{Q}$-Gorenstein ring $R$ of characteristic $p>0$, 
-the command {\tt isFPT(t, f)} checks whether $t$ is the $F$-pure threshold of $f$.  
+The function {\tt isFPT} determines whether a rational number is the $F$-pure threshold of a specified polynomial. 
+Given a rational number $t$ and an element $f$ of a $\mathbb{Q}$-Gorenstein ring of characteristic $p>0$, the command {\tt isFPT(t,f)} outputs {\tt true} if $t$ is the $F$-pure threshold of $f$, and {\tt false} otherwise.
+The function {\tt compareFPT} provides further information about the relationship between $t$ and the $F$-pure threshold of $f$; namely, 
+{\tt compareFPT(t, f)} returns {\tt-1} when $t < \fpt(f)$, $0$ when $t = \fpt(f)$ and $1$ when $t > \fpt(f)$.
+Consider the following example, that illustrates this functionality.
+
+\medskip
+{\small
+\setstretch{.67}
+\begin{MyVerbatim}
+i14 :             R = ZZ/11[x,y];
+
+i15 :             f = x^3 + y^2;
+
+i16 :             isFPT(9/11, f)
+
+o16 = true
+
+\end{MyVerbatim}
+}
+\medskip
+
 In general, this is done by computing the \emph{test ideal} associated to the pair $(R, f^t)$, and that associated when $t$ is replaced with a value less than $t$ that is very close to $t$, that associated to the pair $(R, f^{t-\epsilon}s)$.

### 2019-06-06 Fsing/FThresholdsPaper/FThresholds.tex
Updates to Section 3 of FThresholds paper

--- 2019-06-06 Fsing/FThresholdsPaper/FThresholds.tex
@@
 
-Given a rational number $t$ and  an element $f$ of a $\mathbb{Q}$-Gorenstein ring $R$ of characteristic $p>0$, 
-the command {\tt isFPT(t, f)} checks whether $t$ is the $F$-pure threshold of $f$.  
-In general, this is done by computing the \emph{test ideal} associated to the pair $(R, f^t)$, and that associated when $t$ is replaced with a value less than $t$ that is very close to $t$, that associated to the pair $(R, f^{t-\epsilon}s)$.
-These values are computed using the functions 
-{\tt testIdeal} and {\tt FPureModule} from the \emph{TestIdeals} package
-(CITE THE TEST IDEALS PACKAGE PAPER).
-In fact, $t$ is the $F$-pure threshold of $f$ if and only if $\tau(R, f^{t-\epsilon})$ is $R$, but  $\tau(R, f^t)$ is a proper ideal.  
-Note that when $R$ is a strongly $F$-regular Gorenstein ring, {\tt FPureModule(t, f)} precisely computes $\tau(R, f^{t-\epsilon})$.
-\textcolor{red}{These commands work more generally, but they \emph{only} currently work when $R$ is $\bQ$-Gorenstein, with index not divisible by $p$.}
+The \emph{FThresholds} package contains methods to 
+ test candidate values for an $F$-pure threshold, and even $F$-jumping numbers, even in some singular rings.  
+Consider a  $\mathbb{Q}$-Gorenstein ring $R$ of characteristic $p>0$, whose index not divisible by $p$.
+Given a rational number $t$ and an element $f$ of $R$, the command {\tt isFPT(t,f)} outputs {\tt true} if $t$ is the $F$-pure threshold of $f$, and {\tt false} otherwise. 
+Moreover, the function {\tt compareFPT} provides further information about the relationship between $t$ and the $F$-pure threshold of $f$; namely, 
+{\tt compareFPT(t, f)} returns {\tt-1} when $t < \fpt(f)$, {\tt 0} when $t = \fpt(f)$ and {\tt 1} when $t > \fpt(f)$.
+Setting the option {\tt IsLocal} to {\tt true} tells the function to consider the $F$-pure threshold at the origin.
+The following example illustrates this functionality.
 
-The function {\tt compareFPT} provides further information about the relationship between $t$ and the $F$-pure threshold of $f$.  Namely, 
-{\tt compareFPT(t, f)} returns {\tt-1} when $t < \fpt(f)$, $0$ when $t = \fpt(f)$ and $1$ when $t > \fpt(f)$.
-
-Consider the following example which has $F$-pure threshold equal to {1/2}, see \cite[Example 4.3]{MustataYoshidaTestIdealVsMultiplierIdeals}.
-\medskip
 {\small
@@
 \begin{MyVerbatim}
-i1 : loadPackage "FThresholds"
 
-o1 = FThresholds
+i1 : R = ZZ/11[x, y, z]/( x^2 - y*( z - 1 ) );
 
-o1 : Package
+i2 : compareFPT( 5/11, z - 1 )
 
-i2 : R = ZZ/2[x,y,z];
+o2 = -1
 
-i3 : f = x^2+y^5+z^5;
+i3 : isFPT( 1/2, z - 1 )
 
-i4 : isFPT(1/2, f)
+o3 = true
 
-o4 = true
+i4 : isFPT( 1/2, z - 1, IsLocal => true )
 
-i5 : isFPT(1/3, f)
+o4 : false
 
-o5 = false
-
-i6 : compareFPT(3/4, f)
-
-o6 = 1
 \end{MyVerbatim}
 }
-\medskip
 
-The command {\tt isFJumpingExponent} is implemented similarly, a value $t$ is an $F$-jumping exponent if and only if
-\[
-\tau(R, f^t) \neq \tau(R, f^{t-\epsilon}).
-\]
-Again, this command works as long as $R$ is $\bQ$-Gorenstein with index not divisible by $p$.
+The general method applied calls upon functionality from the \emph{TestIdeals} package (CITE).  The functions {\tt testIdeal} and {\tt FPureModule} therein are used
+to compute the test ideals of $f$ with respect to the parameter $t$, and that with respect to $t - \varepsilon$, for $\varepsilon>0$ very small.
+For instance, as noted in the introduction, when $R$ is a polynomial ring, $t$ is the $F$-pure threshold of $f$ if and only if $\tau(R, f^t)$ is contained in the homogeneous maximal ideal, but
+$\tau(R, f^{t-\varepsilon})$ is not. 
+Note that when $R$ is a strongly $F$-regular Gorenstein ring, {\tt FPureModule(t, f)} precisely computes $\tau(R, f^{t-\varepsilon})$.  
+%These commands work more generally, but they \emph{only} currently work when $R$ is $\bQ$-Gorenstein, with index not divisible by $p$.
+
+Since not only the $F$-pure thresholds, but also the higher $F$-jumping numbers, are determined by containment conditions on test ideals, the functionality is extended to determine whether a given number is an $F$-jumping number.
+Analogous syntax is used, as shown in the following example.
+
+{\small
+\setstretch{.67}
+\begin{MyVerbatim}
+
+i49 : R = ZZ/13[x, y];
+
+i50 : f = y*( ( y + 1 ) - ( x - 1 )^2 )*( x - 2 )*( x + y - 2 );
+
+i51 : isFJumpingExponent( 3/4, f )
+
+o51 = true
+
+\end{MyVerbatim}
+}
 

### 2019-06-06 Fsing/FThresholdsPaper/FThresholds.tex
Updates to Section 3 of FThresholds paper

@@
 
-The general method applied calls upon functionality from the \emph{TestIdeals} package (CITE).  The functions {\tt testIdeal} and {\tt FPureModule} therein are used
+The general method applied calls upon functionality from the \emph{TestIdeals} package \cite{TestIdealsPackage, TestIdealsPaper}.  The functions {\tt testIdeal} and {\tt FPureModule} therein are used
 to compute the test ideals of $f$ with respect to the parameter $t$, and that with respect to $t - \varepsilon$, for $\varepsilon>0$ very small.
@@
 $\tau(R, f^{t-\varepsilon})$ is not. 
-Note that when $R$ is a strongly $F$-regular Gorenstein ring, {\tt FPureModule(t, f)} precisely computes $\tau(R, f^{t-\varepsilon})$.  
+(Note that for $R$ strongly $F$-regular and Gorenstein, {\tt FPureModule(t, f)} precisely computes $\tau(R, f^{t-\varepsilon})$.)  
 %These commands work more generally, but they \emph{only} currently work when $R$ is $\bQ$-Gorenstein, with index not divisible by $p$.

### 2019-06-06 Fsing/FThresholdsPaper/FThresholds.tex
Minor edits to paper

@@
 
+\newenvironment{nouppercase}{%
+  \let\uppercase\relax%
+  \renewcommand{\uppercasenonmath}[1]{}}{}
+
 \begin{document}
-\title{The  \emph{FThresholds} package for \emph{Macaulay2}}
-%\author[Alberto F.\ Boix et al.]{Alberto F.\ Boix}
-%\address{Department of Mathematics, Ben-Gurion University of the Negev, Beer-Sheva 8410501, Israel}
-%\email{fernanal@post.bgu.ac.il}
-%\thanks{A.F.\,Boix was supported by Israel Science Foundation (grant No. 844/14) and Spanish Ministerio de Econom\'ia y Competitividad MTM2016-7881-P}
+\title{The \emph{FrobeniusThresholds} package for \emph{Macaulay2}}
 
@@
 \thanks{D.~J.~Hern\'andez was partially supported by NSF DMS \#1600702.}
-
-%\author[]{Zhibek Kadyrsizova}
-%\address{School of Science and Technology, Nazarbayev University, Astana, 010000, Republic of Kazakhstan}
-%\email{zhibek.kadyrsizova@nu.edu.kz}
-%\thanks{Z. Kadyrsizova was partially supported by NSF DMS \#1401384 and the Barbour Scholarship at the University of Michigan.}
 
@@
 
-%\author[]{Daniel Smolkin}
-%\address{Department of Mathematics, University of Utah, Salt Lake City, UT~84112, USA}
-%\email{smolkin@math.utah.edu}
-%\thanks{D.~Smolkin was supported by NSF RTG Grant DMS \#1246989, NSF CAREER Grant DMS \#1252860/1501102, and NSF FRG Grant DMS \#1265261/1501115.}
-
 \author[]{Pedro Teixeira}
@@
    This note describes the functionality implemented in the \emph{Macaulay2} package \emph{FThresholds}.
-   This package is designed to compute and estimate $F$-pure thresholds, more general $F$-thresholds, and related numerical invariants arising in the study of singularities in prime characteristic commutative algebra.
+   This package is designed to estimate and calculate $F$-pure thresholds, more general $F$-thresholds, and related numerical invariants arising in the study of singularities in prime characteristic commutative algebra.
 \end{abstract}
 
-\subjclass[2010]{13A35}%=
+\subjclass[2010]{13A35}
 
@@
 
+\begin{nouppercase}
 \maketitle
+\end{nouppercase}
 

### 2019-06-06 Fsing/FThresholdsPaper/FThresholds.tex
Major changes to the introduction and nu section of the paper.  Past versions were heavily incorporated

@@
 
+\newcommand{\ft}{\operatorname{c}}
+\newcommand{\idealm}{\mathfrak{m}}
+
 \begin{document}
@@
 \begin{abstract}
-   This note describes the functionality implemented in the \emph{Macaulay2} package \emph{FThresholds}.
+   This note describes the \emph{Macaulay2} package \emph{FrobeniusThresholds}.
    This package is designed to estimate and calculate $F$-pure thresholds, more general $F$-thresholds, and related numerical invariants arising in the study of singularities in prime characteristic commutative algebra.
@@
 
-This paper describes the \emph{Macaulay2} \cite{M2} package \emph{FThresholds}, which provides tools for computing certain fundamental invariants arising in positive characteristic commutative algebra, namely, \emph{$F$-pure thresholds}, \emph{$F$-thresholds}, and \emph{$F$-jumping exponents}.
-Recall that a ring $R$ of prime characteristic $p>0$ is said to be \emph{$F$-pure} if the Frobenius morphism $F \: R \to R$ sending an element to its $p^\text{th}$ power is a pure morphism (under geometric hypotheses, this is equivalent to the condition that the Frobenius morphism is split).
-Regular rings are always $F$-pure, but not conversely.
-The notion of $F$-purity first appeared in the work \cite{HochsterRobertsFrobeniusLocalCohomology}  of Hochster and Roberts to study local cohomology \cite{HochsterRobertsFrobeniusLocalCohomology}, was compared with rational singularities in  \cite{FedderFPureRat}, and was used globally to study properties of Schubert varieties in \cite{MehtaRamanathanFrobeniusSplittingAndCohomologyVanishing}.
+This paper describes the \emph{Macaulay2} \cite{M2} package \emph{FrobeniusThresholds}, which provides tools for computing certain fundamental invariants arising in positive characteristic commutative algebra.
+More precisely, this package concerns the effective computation of \emph{$F$-pure thresholds}, \emph{$F$-thresholds}, and \emph{$F$-jumping exponents}.
 
-After the advent of tight closure \cite{HochsterHunekeTC1}, the usage of the Frobenius endomorphism to measure singularities proliferated, and based on a strong connection discovered between $F$-pure and \emph{log canonical} singularities \cite{HaraWatanabeFRegFPure}, the notion of $F$-purity was generalized to pairs $(R, f^t)$, where $f$ is an element of $R$, and $t$ is a nonnegative real number considered a formal exponent.
+Recall that a ring of prime characteristic $p>0$ is said to be \emph{$F$-pure} if the Frobenius map | that is, ring endomorphism sending an element to its $p$-th power | is a pure morphism;  under natural geometric hypotheses, this is equivalent to the condition that the Frobenius morphism splits as a map of rings.
 
-Along these lines, the notion of the \emph{$F$-pure threshold} was defined in analogy with the \emph{log canonical threshold} \cite{TakagiWatanabeFPureThresh,MustataTakagiWatanabeFThresholdsAndBernsteinSato}.
-The $F$-pure threshold of the pair $(R, f)$ is the supremum over all $t$ for which $(R, f^t)$ is $F$-pure.
-Furthermore, \emph{$F$-threholds} were introduced, a family of invariants that naturally extends the notion of an $F$-pure threshold.
+The concept of $F$-purity has proven to be important in commutative algebra, and has a rich history.
+Indeed, it first appeared in the work \cite{HochsterRobertsFrobeniusLocalCohomology}  of Hochster and Roberts to study local cohomology \cite{HochsterRobertsFrobeniusLocalCohomology}, was compared with rational singularities in  \cite{FedderFPureRat}, and was used to study global properties of Schubert varieties in \cite{MehtaRamanathanFrobeniusSplittingAndCohomologyVanishing}.
 
-These numerical invariants are typically difficult to calculate,
-and due to their significance, have been the focus of intense study over the past fifteen years.
-To this end, the \emph{Macaulay2} package \emph{FThresholds} is centered around calculating and estimating the $F$-pure threshold and other $F$-thresholds, with the function {\tt fpt} at its core.
+After the advent of tight closure \cite{HochsterHunekeTC1}, the usage of Frobenius to quantify singularity | that is, deviation from regularity | proliferated, and based on a connection discovered between $F$-pure and \emph{log canonical} singularities \cite{HaraWatanabeFRegFPure}, the concept of $F$-purity was generalized to the context of \emph{pairs}.
+% $(R, f^t)$, where $f$ is an element of $R$, and $t$ is a nonnegative real number considered a formal exponent.
+
+Along these lines, the \emph{$F$-pure threshold} %associated to an element of $R$ 
+was defined in analogy with the \emph{log canonical threshold} \cite{TakagiWatanabeFPureThresh}, and     
+%The $F$-pure threshold of the pair $(R, f)$ is the supremum over all $t$ for which $(R, f^t)$ is $F$-pure.  
+\emph{$F$-threholds} were then introduced as a family of invariants that naturally extend the notion of an $F$-pure threshold \cite{MustataTakagiWatanabeFThresholdsAndBernsteinSato}.
+
+Unfortunately, the $F$-pure threshold is typically difficult to calculate, even in many concrete cases.
+It is also not so well-understood from the perspective of reduction to prime characteristic.
+Nevertheless, $F$-pure thresholds have been the focus of intense study over the past fifteen years, and the \emph{Macaulay2} package \emph{FThresholds} is centered around calculating and estimating the $F$-pure threshold and other $F$-thresholds, with the function {\tt fpt} at its core.
+
+\subsection*{Some background and notation}  For most of article, we work in a polynomial ring over a finite field of  characteristic $p>0$.
+Unless otherwise stated, all polynomials and ideals under consideration are regarded as elements in this ambient ring.
+The ideal of this ring generated by the ambient variables is denoted $\idealm$.
+
+Let us roughly outline how many natural numerical invariants in prime characteristic commutative algebra are constructed:  For every natural number $e$, associate to some fixed set of data | often, a collection of polynomials and ideals | an integer describing something of relevance (e.g., the dimension of some interesting vector space constructed in terms of your initial data).
+Finally, normalize this integer by dividing by some power of $p^e$, and then take the limit as $e \to \infty$.
+
+Consider a nonzero polynomial $f$ and a natural number $e$.  If $f$ does not vanish at the origin, then set set $\nu_f^{\idealm}(p^e) := \infty$.  Otherwise, $f \in \idealm$, and we instead define
+\[ \nu_f^{\idealm}(p^e) := \max \{ n : f^n \notin \idealm^{[p^e]} \} \] 
+where $\idealm^{[p^e]}$ denotes the $p^e$-th Frobenius power of $\idealm$, that is, the ideal generated by the $p^e$-th powers of the elements of $\idealm$.
+It is not very hard to see that this number is exactly the largest power of $f$ that is part of a free basis for the localization of the ambient polynomial ring at the origin over its subring of $p^e$-th powers.
+As noted earlier, this number also has a natural interpretation in terms of $F$-purity of pairs.
+
+Following our outline, we define 
+\[ \ft^{\idealm}(f) := \lim_{e \to \infty} \frac{ \nu_f^{\idealm}(p^e)}{p^e} \]
+
+Inspired by the connections with $F$-purity of pairs,  this limit is called the \emph{$F$-pure threshold} of $f$ at the origin.
+This limit exists, and is finite when $f \in \idealm$.
+In the latter case, the limit is also rational, but this is far from obvious  \cite{BlickleMustataSmithDiscretenessAndRationalityOfFThresholds}.
+
+The $F$-pure threshold is closely related to a many other fundamental concepts in prime characteristic commutative algebra.   For instance, 
+\[ \ft^{\idealm}(f) = \inf \{ t : \tau(f^t)  \subseteq \idealm \} = \sup \{ t : \sigma(R, f^t) \neq 0 \} \]
+where $\tau(f^t)$ and $\sigma(f^t)$ are the \emph{test ideal} and \emph{$F$-signature}, respectively, associated to $f$, and the formal nonnegative real exponent $t$.
+The former is an ideal in the ambient ring of $f$, and the latter is a real number;  both depend on the parameter $t$ and prime $p$ in subtle ways \cite{BlickleMustataSmithDiscretenessAndRationalityOfFThresholds, BlickleSchwedeTuckerFSigPairs1}.
+Though we will not elaborate much on these topics,  we stress that the \emph{Macaulay2} package {\tt TestIdeals} provides functionality for the effective computation of test ideals in many cases \cite{TestIdealsPackage, TestIdealsPaper}.
+
+In the literature, the $F$-pure threshold $\ft^{\idealm}(f)$ is often denoted $\fpt(f)$, for obvious reasons.
+However, in this note, we adopt the former notation to avoid any possible confusion with the function {\tt fpt} described in Section \ref{sec.FPT}.
+Indeed, the command {\tt fpt(f)} need not always output the number $\ft^{\idealm}(f) = \fpt(f)$, though in the case that it cannot, it will provide a reasonably good estimate of this number.
+
+It turns out that the sequence $\{ \nu_f^{\idealm}(p^e) \}_{e=1}^{\infty}$ itself, and not just its limit, also encodes interesting information about $f$.
+For example, it is closely related to the so-called \emph{Bernstein-Sato polynomial} \cite{MustataTakagiWatanabeFThresholdsAndBernsteinSato}.
+It is then natural to ask whether one can recover the sequence $\{ \nu_f^{\idealm}(p^e) \}_{e=1}^{\infty}$ from the limit $\ft^{\idealm}(f)$.
+Fortunately, the answer to this question is yes \cite{MustataTakagiWatanabeFThresholdsAndBernsteinSato, HernandezFPurityOfHypersurfaces}.
+More precisely,
+\begin{equation}
+\label{sequence-from-limit}
+\nu_f^{\idealm}(p^e) = \lceil p^e \cdot \ft^{\idealm}(f) \rceil - 1.  
+\end{equation}
+
+We conclude this subsection by briefly reviewing some natural generalizations.  Suppose that $I$ and $J$ are ideals.  If $I$ is contained in the radical of $J$, then we set
+%
+\[ \nu_I^J(p^e) = \max \{ n : I^n \notin J^{[p^e]} \}. \]  
+Otherwise, we set $\nu_I^J(p^e) = \infty$.
+
+This clearly generalizes the quantity $\nu_f^{\idealm}(p^e)$ considered earlier, and we call 
+\[ \ft^J(I) := \lim_{e \to \infty} \frac{ \nu_f^{\idealm}(p^e)}{p^e} \]
+the \emph{$F$-threshold of $I$ with respect to $J$}.
+These numbers are also rational, when finite, and we call the quantity $\ft^{\idealm}(I)$ the $F$-pure threshold of the ideal $I$.
+Like $F$-pure thresholds, the $F$-thresholds of $I$ can also be defined in terms of its test ideals.
+
+\subsection*{Organization}
 
@@
 
-\subsection*{Acknowledgements.}  First and foremost, the authors enthusiastically thank all authors 
-and contributors to the \emph{FThresholds} package: (INSERT NAMES HERE).
+\subsection*{Acknowledgements.}  First and foremost, the authors enthusiastically thank all authors and contributors to the \emph{FThresholds} package: (INSERT NAMES HERE).
 %Erin Bela, Juliette Bruce, Zhibek Kadyrsizova, Sara Malec, Maral Mostafazadehfard, Marcus Robinson, Dan Smolkin, and Robert Walker.
@@
 
-\section{The $F$-pure threshold limit and {\tt nu}}
+\newpage
+
+\section{The {\tt nu} function}
 \label{sec.Nu}
 
-Suppose $R = k[x_1, \dots, x_n]$ is a polynomial ring over a finite field and $f \in R$.
+{\color{red} This section will need to be modified so that it is consistent with the introduction section.  The point is that a lot of the notation repeated here was introduced earlier there.}
+
+We now consider the {\tt nu} function, which plays a fundamental role in this package.
+In addition to describing its basic functionality, we also discuss its theoretical foundations, including its relationship the {\tt fpt} function consider in Section \ref{sec.FPT}.
+
+Here, we work in a polynomial ring over a finite field of characteristic $p>0$.  All ideals and polynomials under consideration are regarded in this ambient ring.
+
+If $f$ is a polynomial contained in the radical of an ideal $J$, and $e$ is a natural number, then the command {\tt nu(e,f,J)} outputs the maximal integer exponent $n$ such that $f^{ n}$ is not contained in $J^{[p^e]}$.
+Here, $J^{[p^e]}$ denotes the $p^e$-th Frobenius power of $J$, that is, the ideal generated by the $p^e$-th powers of the elements of $J$.
+
+More generally, if $I$ is an ideal contained in the radical of $J$, then {\tt nu(e,I,J)} outputs the maximal integer exponent $n$ such that $I^n$ is not contained in $J^{[p^e]}$.
+
+The outputs of {\tt nu(e,f,J)} and {\tt nu(e,I,J)} are denoted $\nu_f^J(p^e)$ and $\nu_I^J(p^e)$, respectively, in the literature, and were originally defined in the paper \cite{MustataTakagiWatanabeFThresholdsAndBernsteinSato}.
+
+{\small
+\setstretch{.67}
+\begin{MyVerbatim}
+
+i1 : R = ZZ/11[x,y];
+
+i2 : I = ideal(x^2 + y^3, x*y);
+
+o2 : Ideal of R
+
+i3 : J = ideal(x^2, y^3);
+
+o3 : Ideal of R
+
+i4 : nu(1, I, J)
+
+o4 = 24
+
+i5 : f = x*y*(x^2 + y^2);
+
+i6 : nu(1, f, J)
+
+o6 = 10
+\end{MyVerbatim}
+}
+
+%R = ZZ/11[x,y];
+%I = ideal(x^2 + y^3, x*y);
+%J = ideal(x^2, y^3);
+%nu(1, I, J)
+%f = x*y*(x^2 + y^2);
+%nu(1, f, J)
+
+We highlight some degenerate cases:  Suppose that $e$ is a natural number.
+If $f$ is zero, then the output of {\tt nu(e,f,J)} is {\tt 0}, and if $f$ is not contained in the radical of $J$, then the output is instead {\tt infinity}.
+These degenerate cases extend analogously to the outputs of {\tt nu(e,I,J)} when $I$ is an ideal.
+
+{\small
+\setstretch{.67}
+\begin{MyVerbatim}
+
+i7 : nu(1, 0_R, J)
+
+o7 = 0
+
+i8 : nu(1, 1_R, J)
+
+o8 = infinity
+
+o8 : InfiniteNumber
+\end{MyVerbatim}
+}
+
+%nu(1, 0_R, J)
+%nu(1, 1_R, J)
+
+It is possible to omit the third argument from the function {\tt nu};  in this case, the function assumes that the omitted third argument is the maximal generated by the variables in the ambient polynomial ring.
+
+{\small
+\setstretch{.67}
+\begin{MyVerbatim}
+
+i9 : R = ZZ/17[x,y,z];
+
+i10 : f = x^3 + y^4 + z^5;
+
+i11 : M = ideal(x, y, z);
+
+o11 : Ideal of R
+
+i12 : nu(2, f) == nu(2, f, M)
+
+o12 = true
+\end{MyVerbatim}
+}
+
+%R = ZZ/17[x,y,z];
+%f = x^3 + y^4 + z^5;
+%M = ideal(x, y, z);
+%nu(2, f) == nu(2, f, M)
+
+It is well-known that if $q=p^e$ for some nonnegative integer $e$, then \[ \nu_I^J(qp) = \nu_I^J(q)\cdot p + L\]  where the error term $L$ is nonnegative, and can be explicitly bounded from above in terms of $p$ and the number of generators of $I$ and $J$.
+For instance, the error term $L$ is at most $p-1$ when $I$ is principal and $J$ is arbitrary.
+
+This implies that when searching for the maximal exponent defining {\tt nu(e,I,J)} when $e$ is positive, it is always safe to start at $p$ times the output of {\tt nu(e-1,I,J)}, and one needn't search too far past this number.
+This also suggests that the most efficient way to compute {\tt nu(e,I,J)} is to compute, successively, {\tt nu(s,I,J)}, for each {\tt s = 0,\ldots,e}.
+This is indeed how the computation is done in most cases.
+
+{\color{red} Make this consistent with the introduction.  The point is that we have already described how to get the {\tt nu}-s from their limit.  Maybe we should directly cite }.  
+If $M$ is the homogeneous maximal ideal of $R$ and $f$ is an element of $R$, the numbers $\nu_f^M(p^e)$ determine and are determined by the $F$-pure threshold of $f$ at the origin.
+Indeed, $\nu_f^M(p^e)$ is $p^e$ times the truncation of the non-terminating base $p$ expansion of fpt($f$) at its $e^{\textrm{th}}$ spot.
+This fact is used to speed up the computations for certain polynomials whose $F$-pure thresholds can be quickly computed via special algorithms, namely diagonal polynomials and binomials.
+This feature can be disabled by setting the option {\tt UseSpecialAlgorithms} (default value {\tt true}) to {\tt false}.
+
+%R = ZZ/17[x,y,z];
+%f = x^3 + y^4 + z^5; -- a diagonal polynomial
+%time nu(3, f)
+%time nu(3, f, UseSpecialAlgorithms => false)
+
+The valid values for the option {\tt ContainmentTest} are {\tt FrobeniusPower}, {\tt FrobeniusRoot}, and {\tt StandardPower}.
+The default value of this option depends on what is passed to {\tt nu}.
+Indeed, by default, {\tt ContainmentTest} is set to {\tt FrobeniusRoot} if {\tt nu} is passed a ring element $f$, and is set to {\tt StandardPower} if {\tt nu} is passed an ideal $I$.
+We describe the consequences of setting {\tt ContainmentTest} to each of these values below.
+
+First, if {\tt ContainmentTest} is set to {\tt StandardPower}, then the ideal containments checked when computing {\tt nu(e,I,J)} are verified directly.
+That is, the standard power $I^n$ is first computed, and a check is then run to see if it lies in the $p^e$-th Frobenius power of $J$.
+
+Alternately, if {\tt ContainmentTest} is set to {\tt FrobeniusRoot}, then the ideal containments are verified using Frobenius Roots.
+That is, the $p^e$-th Frobenius root of $I^n$ is first computed, and a check is then run to see if it lies in $J$.
+The output is unaffected, but this option often speeds up computations, specially when a polynomial or principal ideal is passed as the second argument.
+
+%R = ZZ/11[x,y,z];
+%f = x^3 + y^3 + z^3 + x*y*z;
+%time nu(3, f) -- ContainmentTest is set to FrobeniusRoot, by default
+%time nu(3, f, ContainmentTest => StandardPower)
+
+Finally, when {\tt ContainmentTest} is set to {\tt FrobeniusPower}, then instead of producing the invariant $\nu_I^J(p^e)$ as defined above, {\tt nu(e,I,J,ContainmentTest=>FrobeniusPower)} instead outputs the maximal integer $n$ such that the $n^{\textrm{th}}$ (generalized) Frobenius power of $I$ is not contained in the $p^e$-th Frobenius power of $J$.
+
+Here, the $n^{\textrm{th}}$ Frobenius power of $I$, when $n$ is a nonnegative integer, is as defined in the paper {\it Frobenius Powers} by Hernández, Teixeira, and Witt.
+In particular, {\tt nu(e,I,J)} and {\tt nu(e,I,J,ContainmentTest=>FrobeniusPower)} need not agree.  However, they will agree when $I$ is a principal ideal.
+
+%R = ZZ/3[x,y];
+%M = ideal(x, y);
+%nu(3, M^5)
+%nu(3, M^5, ContainmentTest => FrobeniusPower)
+
+The function {\tt nu} works by searching through the list of potential integers $n$ and checking containments of $I^n$ in a specified Frobenius power of $J$.
+The way this search is approached is specified by the option {\tt Search}, which can be set to {\tt Binary} (the default value) or {\tt Linear}.
+
+%R = ZZ/5[x,y,z];
+%f = x^2*y^4 + y^2*z^7 + z^2*x^8;
+%time nu(5, f) -- uses binary search (default)
+%time nu(5, f, Search => Linear)
+%M = ideal(x, y, z);
+%time nu(2, M, M^2) -- uses binary search (default)
+%time nu(2, M, M^2, Search => Linear) -- but linear seach gets luckier
+
+The option {\tt ReturnList} (default value {\tt false}) can be used to request that the output be not only $\nu_I^J(p^e)$, but a list contaning $\nu_I^J(p^i)$, for $i=0,\ldots,e$.
+
+%nu(5, f, ReturnList => true)
+
+Alternatively, the option {\tt Verbose} (default value {\tt false}) can be used to request that the values $\nu_I^J(p^i)$ ($i=0,\ldots,e$) be printed as they are computed, to monitor the progress of the computation.
+
+%nu(5, f, Verbose => true)
+
+%%Below is the original version of the section describing the nu function
+
+%\section{The $F$-pure threshold limit and {\tt nu}}
+%\label{sec.Nu}
+%
+%Suppose $R = k[x_1, \dots, x_n]$ is a polynomial ring over a finite field and $f \in R$.
 If $f^a \notin \langle x_1^{p^e}, \dots, x_n^{p^e} \rangle = \fram^{[p^e]}$, then the pair $(R, f^{a/(p^e -1)})$ is $F$-pure at the origin, whereas if $f^a \in \fram^{[p^e]}$, then the pair $(R, f^{a/p^e})$ is not $F$-pure at the origin.
@@
 See \cite{MustataTakagiWatanabeFThresholdsAndBernsteinSato}.
-
-We set $\nu(e, f)$ to be largest $a \in \bZ$ such that $f^a \notin \fram^{[p^e]}$ (note in the literature, it is frequently denoted by $\nu_f(p^e)$.  It immediately follows that
-\[
-\fpt(f) = \lim_{e \to \infty} {\nu(e, f) \over p^e}.
-\]
-These numbers $\nu(e, f)$ can be computed using the command {\tt nu}, as in the example below.
-\medskip
-{\small
-\setstretch{.67}
-\begin{MyVerbatim}
-i1 : loadPackage "FThresholds"
-
-o1 = FThresholds
-
-o1 : Package
-
-i2 : R = ZZ/7[x,y]
-
-o2 = R
-
-o2 : PolynomialRing
-
-i3 : f = y^2 - x^3
-
-        3    2
-o3 = - x  + y
-
-o3 : R
-
-i4 : nu(1, f)
-
-o4 = 5
-
-o4 : QQ
-
-i5 : nu(2, f)
-
-o5 = 40
-
-o5 : QQ
-
-i6 : nu(3, f)
-
-o6 = 285
-
-o6 : QQ
-\end{MyVerbatim}
-}
-\medskip
-The numbers $5/7, 40/49, 285/343$ then approximate the $F$-pure threshold, which in this case happens to equal $5/6$.
+%
+%We set $\nu(e, f)$ to be largest $a \in \bZ$ such that $f^a \notin \fram^{[p^e]}$ (note in the literature, it is frequently denoted by $\nu_f(p^e)$.  It immediately follows that
+%\[
+%\fpt(f) = \lim_{e \to \infty} {\nu(e, f) \over p^e}.
+%\]
+%These numbers $\nu(e, f)$ can be computed using the command {\tt nu}, as in the example below.
+%\medskip
+%{\small
+%\setstretch{.67}
+%\begin{MyVerbatim}
+%i1 : loadPackage "FThresholds"
+%
+%o1 = FThresholds
+%
+%o1 : Package
+%
+%i2 : R = ZZ/7[x,y]
+%
+%o2 = R
+%
+%o2 : PolynomialRing
+%
+%i3 : f = y^2 - x^3
+%
+%        3    2
+%o3 = - x  + y
+%
+%o3 : R
+%
+%i4 : nu(1, f)
+%
+%o4 = 5
+%
+%o4 : QQ
+%
+%i5 : nu(2, f)
+%
+%o5 = 40
+%
+%o5 : QQ
+%
+%i6 : nu(3, f)
+%
+%o6 = 285
+%
+%o6 : QQ
+%\end{MyVerbatim}
+%}
+%\medskip
+%The numbers $5/7, 40/49, 285/343$ then approximate the $F$-pure threshold, which in this case happens to equal $5/6$.
 By default, if the function $f$ has a special form (is a diagonal polynomial or a binomial), then the function does not check whether $f^a$ is in  $\langle x_1^{p^e}, \dots, x_n^{p^e} \rangle$, but instead uses general formulas for $\nu$s, see \cite{HernandezFPureThresholdOfBinomial,HernandezFInvariantsOfDiagonalHyp}.
-
-In fact, one can make the following more general definition.  If $I$ and $J$ are two ideals (with $I \subseteq \sqrt{J}$), one can define
-\[
-\nu(e, I, J) = \max \{ n \in \bZ \; |\; I^n \not\subseteq J^{[p^e]} \}.
-\]
-This is frequently denoted by $\nu_I^J(p^e)$ in the literature.
+%
+%In fact, one can make the following more general definition.  If $I$ and $J$ are two ideals (with $I \subseteq \sqrt{J}$), one can define
+%\[
+%\nu(e, I, J) = \max \{ n \in \bZ \; |\; I^n \not\subseteq J^{[p^e]} \}.
+%\]
+%This is frequently denoted by $\nu_I^J(p^e)$ in the literature.
 In the case that $I = \langle f \rangle$ and $J = \fram$, this just recovers the $\nu$'s defined above; the limit of which is the $F$-pure threshold.
 For more general $I$ and $J$, the limit
-\[
-\lim_{e \to \infty} {\nu(e, I, J) \over p^e}
-\]
-is called the \emph{$F$-threshold of $I$ with respect to $J$}.
+%\[
+%\lim_{e \to \infty} {\nu(e, I, J) \over p^e}
+%\]
+%is called the \emph{$F$-threshold of $I$ with respect to $J$}.
 To compute these values we use a binary search, unless the user specifies that we should use a linear search instead {\tt Search=>Linear}.
-
-There is one more option that deserves mentioning, {\tt ContainmentTest}.  There are two ways to check whether $f^a$ (or $I^a$) is contained in $J^{[p^e]}$.  In general it is true that
-\[
-I^a \subseteq J^{[p^e]} \text{ $\Leftrightarrow$ } (I^a)^{[1/p^e]} \subseteq J
-\]
-where $\bullet^{[1/p^e]}$ is defined as in the {\tt TestIdeals} package.
+%
+%There is one more option that deserves mentioning, {\tt ContainmentTest}.  There are two ways to check whether $f^a$ (or $I^a$) is contained in $J^{[p^e]}$.  In general it is true that
+%\[
+%I^a \subseteq J^{[p^e]} \text{ $\Leftrightarrow$ } (I^a)^{[1/p^e]} \subseteq J
+%\]
+%where $\bullet^{[1/p^e]}$ is defined as in the {\tt TestIdeals} package.
 Which of these two strategies to use is controlled by the option {\tt ContainmentTest => StandardPower} and {\tt ContainmentTest => FrobeniusRoot} respectively.
-For principal $I$, the command on the right is generally faster (and so {\tt FrobeniusRoot} is the default strategy for computing $\nu$).
+%For principal $I$, the command on the right is generally faster (and so {\tt FrobeniusRoot} is the default strategy for computing $\nu$).
 For non-principal $I$, frequently the command on the left is quicker, and so {\tt StandardPower} is default strategy.
-
-Finally, the option {\tt ContainmentTest => FrobeniusPower}, then ${\tt \nu(e, I, A)}$ computes the largest integer $n$ such that
-\[
-I^{[p^n]} \subseteq J^{[p^e]}.
-\]
-See \cite{HernandezTeixeiraWittFrobeniusPowers} for more discussion of this.
+%
+%Finally, the option {\tt ContainmentTest => FrobeniusPower}, then ${\tt \nu(e, I, A)}$ computes the largest integer $n$ such that
+%\[
+%I^{[p^n]} \subseteq J^{[p^e]}.
+%\]
+%See \cite{HernandezTeixeiraWittFrobeniusPowers} for more discussion of this.
 
@@
 
-The \emph{FThresholds} package contains methods to 
+The \emph{FrobeniusThresholds} package contains methods to 
  test candidate values for an $F$-pure threshold, and even $F$-jumping numbers, even in some singular rings.  
@@
 
-            If neither endpoint is the $F$-pure threshold and {\tt Attempts} is set to more than {\tt 2}, then  additional checks are performed at certain numbers within the interval .
-A number in the interval \eqref{estimating-interval: e} with minimal denominator is selected, and {\tt compareFPT} is used to test that number.
-{\color{red} This will need to get updated} If that ``guess" is correct, its value is returned; otherwise, the information returned by {\tt compareFPT} is used to narrow down the interval, and this process is repeated as many times as specified by {\tt Attempts}.
+            If neither endpoint is the $F$-pure threshold and {\tt Attempts} is set to more than {\tt 2}, then  additional checks are performed at certain numbers within the interval, chosen according to the criteria determined by the value of the option {\tt GuessStrategy}.
+We refer the reader for the documentation of this strategy for more details.
+
+{\color{red}  This will need to be updated.  Maybe look at Pedro's new documentation.}
 

### 2019-06-06 Fsing/FThresholdsPaper/FThresholds.tex
Changes the the nu section of the paper

@@
 
-We now consider the {\tt nu} function, which plays a fundamental role in this package.
-In addition to describing its basic functionality, we also discuss its theoretical foundations, including its relationship the {\tt fpt} function consider in Section \ref{sec.FPT}.
+We now consider the {\tt nu} function, which is fundamental.   As in the introduction, we work in a polynomial ring over a finite field of characteristic $p>0$.
 
-Here, we work in a polynomial ring over a finite field of characteristic $p>0$.  All ideals and polynomials under consideration are regarded in this ambient ring.
-
-If $f$ is a polynomial contained in the radical of an ideal $J$, and $e$ is a natural number, then the command {\tt nu(e,f,J)} outputs the maximal integer exponent $n$ such that $f^{ n}$ is not contained in $J^{[p^e]}$.
-Here, $J^{[p^e]}$ denotes the $p^e$-th Frobenius power of $J$, that is, the ideal generated by the $p^e$-th powers of the elements of $J$.
-
-More generally, if $I$ is an ideal contained in the radical of $J$, then {\tt nu(e,I,J)} outputs the maximal integer exponent $n$ such that $I^n$ is not contained in $J^{[p^e]}$.
-
-The outputs of {\tt nu(e,f,J)} and {\tt nu(e,I,J)} are denoted $\nu_f^J(p^e)$ and $\nu_I^J(p^e)$, respectively, in the literature, and were originally defined in the paper \cite{MustataTakagiWatanabeFThresholdsAndBernsteinSato}.
+Fix a natural number $e$.
+If $f$ is polynomial contained in the radical of an ideal $J$, then the command {\tt nu(e,f,J)} outputs $\nu_f^J(p^e)$, the maximal integer exponent such that $f^n$ is not contained in $J^{[p^e]}$.
+More generally, if $I$ is an ideal contained in the radical of $J$, then {\tt nu(e,I,J)} outputs $\nu_I^J(p^e)$, the maximal integer exponent $n$ such that $I^n$ is not contained in $J^{[p^e]}$.
 
@@
 
-We highlight some degenerate cases:  Suppose that $e$ is a natural number.
-If $f$ is zero, then the output of {\tt nu(e,f,J)} is {\tt 0}, and if $f$ is not contained in the radical of $J$, then the output is instead {\tt infinity}.
-These degenerate cases extend analogously to the outputs of {\tt nu(e,I,J)} when $I$ is an ideal.
+We highlight some degenerate cases:  If $f$ is zero, then the output of {\tt nu(e,f,J)} is {\tt 0}, and if $f$ is not contained in the radical of $J$, then the output is instead {\tt infinity}.
+These degenerate cases extend analogously to {\tt nu(e,I,J)} when $I$ is an ideal.
 

### 2019-06-06 Fsing/FThresholdsPaper/FThresholds.tex
Edits to introduction of FThresholds paper

--- 2019-06-06 Fsing/FThresholdsPaper/FThresholds.tex
@@
 
-Recall that a ring of prime characteristic $p>0$ is said to be \emph{$F$-pure} if the Frobenius map | that is, ring endomorphism sending an element to its $p$-th power | is a pure morphism;  under natural geometric hypotheses, this is equivalent to the condition that the Frobenius morphism splits as a map of rings.
+Recall that a ring of prime characteristic $p>0$ is said to be \emph{$F$-pure} if the Frobenius map|that is, the ring endomorphism sending an element to its $p$-th power|is a pure morphism;  under natural geometric hypotheses, this is equivalent to the condition that the Frobenius morphism splits as a map of rings.
 
@@
 
-After the advent of tight closure \cite{HochsterHunekeTC1}, the usage of Frobenius to quantify singularity | that is, deviation from regularity | proliferated, and based on a connection discovered between $F$-pure and \emph{log canonical} singularities \cite{HaraWatanabeFRegFPure}, the concept of $F$-purity was generalized to the context of \emph{pairs}.
+After the advent of tight closure \cite{HochsterHunekeTC1}, the usage of Frobenius to quantify singularity|that is, deviation from regularity|proliferated, and based on a connection discovered between $F$-pure and \emph{log canonical} singularities \cite{HaraWatanabeFRegFPure}, the concept of $F$-purity was generalized to the context of \emph{pairs}.
 % $(R, f^t)$, where $f$ is an element of $R$, and $t$ is a nonnegative real number considered a formal exponent.
@@
 Unfortunately, the $F$-pure threshold is typically difficult to calculate, even in many concrete cases.
-It is also not so well-understood from the perspective of reduction to prime characteristic.
-Nevertheless, $F$-pure thresholds have been the focus of intense study over the past fifteen years, and the \emph{Macaulay2} package \emph{FThresholds} is centered around calculating and estimating the $F$-pure threshold and other $F$-thresholds, with the function {\tt fpt} at its core.
+It is also not so well understood from the perspective of reduction to prime characteristic.
+Nevertheless, $F$-pure thresholds have been the focus of intense study over the past fifteen years, and the \emph{Macaulay2} package \emph{FrobeniusThresholds} is centered around calculating and estimating the $F$-pure threshold and other $F$-thresholds, with the function {\tt fpt} at its core.
 
-\subsection*{Some background and notation}  For most of article, we work in a polynomial ring over a finite field of  characteristic $p>0$.
+\subsection*{Some background and notation}  For most of this article, we work in a polynomial ring over a finite field of  characteristic $p>0$.
 Unless otherwise stated, all polynomials and ideals under consideration are regarded as elements in this ambient ring.
-The ideal of this ring generated by the ambient variables is denoted $\idealm$.
+The ideal of this ring generated by the ring's variables is denoted $\idealm$.
 
-Let us roughly outline how many natural numerical invariants in prime characteristic commutative algebra are constructed:  For every natural number $e$, associate to some fixed set of data | often, a collection of polynomials and ideals | an integer describing something of relevance (e.g., the dimension of some interesting vector space constructed in terms of your initial data).
+Let us roughly outline how many natural numerical invariants in prime characteristic commutative algebra are constructed:  For every natural number $e$, associate to some fixed set of data|often, a collection of polynomials and ideals|an integer describing something of relevance that depends on $e$ (e.g., the dimension of some interesting vector space constructed in terms of your initial data).
 Finally, normalize this integer by dividing by some power of $p^e$, and then take the limit as $e \to \infty$.
@@
 Consider a nonzero polynomial $f$ and a natural number $e$.  If $f$ does not vanish at the origin, then set set $\nu_f^{\idealm}(p^e) := \infty$.  Otherwise, $f \in \idealm$, and we instead define
-\[ \nu_f^{\idealm}(p^e) := \max \{ n : f^n \notin \idealm^{[p^e]} \} \] 
+\[ \nu_f^{\idealm}(p^e) := \max \{ n>0 : f^n \notin \idealm^{[p^e]} \} \] 
 where $\idealm^{[p^e]}$ denotes the $p^e$-th Frobenius power of $\idealm$, that is, the ideal generated by the $p^e$-th powers of the elements of $\idealm$.
@@
 
-Inspired by the connections with $F$-purity of pairs,  this limit is called the \emph{$F$-pure threshold} of $f$ at the origin.
+Inspired by its connections with the $F$-purity of pairs,  this limit is called the \emph{$F$-pure threshold} of $f$ at the origin.
 This limit exists, and is finite when $f \in \idealm$.
@@
 
-The $F$-pure threshold is closely related to a many other fundamental concepts in prime characteristic commutative algebra.   For instance, 
-\[ \ft^{\idealm}(f) = \inf \{ t : \tau(f^t)  \subseteq \idealm \} = \sup \{ t : \sigma(R, f^t) \neq 0 \} \]
-where $\tau(f^t)$ and $\sigma(f^t)$ are the \emph{test ideal} and \emph{$F$-signature}, respectively, associated to $f$, and the formal nonnegative real exponent $t$.
+The $F$-pure threshold is closely related to many other fundamental concepts in prime characteristic commutative algebra.   For instance, 
+\[ \ft^{\idealm}(f) = \inf \{ t>0 : \tau(f^t)  \subseteq \idealm \} = \sup \{ t>0 : \sigma( f^t) \neq 0 \} \]
+where $\tau(f^t)$ and $\sigma(f^t)$ are the \emph{test ideal} and \emph{$F$-signature}, respectively, associated to $f$ and the formal nonnegative real exponent $t$.
 The former is an ideal in the ambient ring of $f$, and the latter is a real number;  both depend on the parameter $t$ and prime $p$ in subtle ways \cite{BlickleMustataSmithDiscretenessAndRationalityOfFThresholds, BlickleSchwedeTuckerFSigPairs1}.
-Though we will not elaborate much on these topics,  we stress that the \emph{Macaulay2} package {\tt TestIdeals} provides functionality for the effective computation of test ideals in many cases \cite{TestIdealsPackage, TestIdealsPaper}.
+Though we will not elaborate much on these topics,  we stress that the \emph{Macaulay2} package \emph{TestIdeals} provides functionality for the effective computation of test ideals in many cases \cite{TestIdealsPackage, TestIdealsPaper}.
 
 In the literature, the $F$-pure threshold $\ft^{\idealm}(f)$ is often denoted $\fpt(f)$, for obvious reasons.
-However, in this note, we adopt the former notation to avoid any possible confusion with the function {\tt fpt} described in Section \ref{sec.FPT}.
+However, in this note, we adopt the former notation to avoid any possible confusion with the \emph{Macaulay2} function {\tt fpt} described in Section \ref{sec.FPT}.
 Indeed, the command {\tt fpt(f)} need not always output the number $\ft^{\idealm}(f) = \fpt(f)$, though in the case that it cannot, it will provide a reasonably good estimate of this number.
@@
 For example, it is closely related to the so-called \emph{Bernstein-Sato polynomial} \cite{MustataTakagiWatanabeFThresholdsAndBernsteinSato}.
-It is then natural to ask whether one can recover the sequence $\{ \nu_f^{\idealm}(p^e) \}_{e=1}^{\infty}$ from the limit $\ft^{\idealm}(f)$.
+Thus, it is natural to ask whether one can recover the sequence $\{ \nu_f^{\idealm}(p^e) \}_{e=1}^{\infty}$ from the limit $\ft^{\idealm}(f)$.
 Fortunately, the answer to this question is yes \cite{MustataTakagiWatanabeFThresholdsAndBernsteinSato, HernandezFPurityOfHypersurfaces}.
@@
 
-There are three main sections in this paper, which describe and illustrate the main functionality implemented in the package \emph{FThresholds}.
+There are three main sections in this paper, which describe and illustrate the main functionality implemented in the package \emph{FrobeniusThresholds}.
 \begin{itemize}
@@
 
-\subsection*{Acknowledgements.}  First and foremost, the authors enthusiastically thank all authors and contributors to the \emph{FThresholds} package: (INSERT NAMES HERE).
+\subsection*{Acknowledgements.}  First and foremost, the authors enthusiastically thank all authors and contributors to the \emph{FrobeniusThresholds} package.
+Our package coauthors are (LIST NAMES), and others who contributed code are (LIST OTHER NAMES).
 %Erin Bela, Juliette Bruce, Zhibek Kadyrsizova, Sara Malec, Maral Mostafazadehfard, Marcus Robinson, Dan Smolkin, and Robert Walker.

### 2019-06-06 Fsing/FThresholdsPaper/FThresholds.tex

@@
 
-\subsection*{Some background and notation}  For most of this article, we work in a polynomial ring over a finite field of  characteristic $p>0$.
-Unless otherwise stated, all polynomials and ideals under consideration are regarded as elements in this ambient ring.
-The ideal of this ring generated by the ring's variables is denoted $\idealm$.
+\subsection*{Some background and notation}  
+The functionality implemented in the \emph{FrobeniusThresholds} is not restricted to nonsingular ambient rings (see Section \ref{sec.IsFPT}).
+However, for most of this article, we work in a polynomial ring over a finite field of  characteristic $p>0$, and we remain in this case throughout the introduction for the sake of clarity.  
+Unless otherwise stated, all polynomials and ideals under consideration are regarded as elements in such a ring.  The ideal of this ring generated by the ring's variables is denoted $\idealm$.
 
-Let us roughly outline how many natural numerical invariants in prime characteristic commutative algebra are constructed:  For every natural number $e$, associate to some fixed set of data|often, a collection of polynomials and ideals|an integer describing something of relevance that depends on $e$ (e.g., the dimension of some interesting vector space constructed in terms of your initial data).
-Finally, normalize this integer by dividing by some power of $p^e$, and then take the limit as $e \to \infty$.
+Let us roughly outline the way in which many natural numerical invariants in prime characteristic commutative algebra are constructed:  For every natural number $e$, associate to some fixed set of data|often, a collection of polynomials and ideals|an integer describing something of relevance that depends on $e$ (e.g., the dimension of some interesting vector space constructed in terms of your initial data).
+Finally, normalize this integer by dividing by some power of $p^e$, and take the limit as $e$ approaches infinity.
 
@@
 \begin{itemize}
-\item \autoref{sec.Nu} describes the methods implemented for approximating the $F$-pure threshold and other $F$-thresholds.  
-\item \autoref{sec.IsFPT} explains the package's functionality for determining whether a given number is the $F$-pure threshold, or more generally, an \emph{$F$-jumping exponent}.
+\item \autoref{sec.Nu} describes the methods for approximating the $F$-pure threshold and other $F$-thresholds.  
+\item \autoref{sec.IsFPT} explains the functionality for determining whether a given number is the $F$-pure threshold, or more generally, an \emph{$F$-jumping exponent}.
 \item \autoref{sec.FPT} describes the features of the central function of the package, {\tt fpt}. 
 \end{itemize}
-
 This package builds heavily upon the \emph{TestIdeals} package for \emph{Macaulay2}, which provides a broad range of functionality in prime characteristic commutative algebra.
@@
 \subsection*{Acknowledgements.}  First and foremost, the authors enthusiastically thank all authors and contributors to the \emph{FrobeniusThresholds} package.
-Our package coauthors are (LIST NAMES), and others who contributed code are (LIST OTHER NAMES).
-%Erin Bela, Juliette Bruce, Zhibek Kadyrsizova, Sara Malec, Maral Mostafazadehfard, Marcus Robinson, Dan Smolkin, and Robert Walker.
-We are also grateful the organizers of the \emph{Macaulay2} workshops where much of the functionality described herein was developed, hosted by Wake Forest University in 2012, the University of California, Berkeley in 2014 and 2017, Boise State University in 2015, and the University of Utah in 2016.
-We are also grateful to the University of Utah for hosting a collaborative development visit in 2018, and to the Institute of Mathematics and its Applications for its support for the Coding Sprint \emph{F-thresholds in Macaulay2} in 2019, where the current version of the package was finalized and this paper was completed.
+Our package coauthors are Dan Smolkin (LIST MORE NAMES), and Zhibek Kadyrsizova, Moty Katzman (LIST MORE NAMES) contributed valuable code to the package. 
+%Erin Bela, Juliette Bruce, Sara Malec, Maral Mostafazadehfard, Marcus Robinson, Matthew Mastroeni
 
-\newpage
+Many thanks go to the organizers of the \emph{Macaulay2} workshops where much of the functionality described herein was developed, hosted by Wake Forest University in 2012, the University of California, Berkeley in 2014 and 2017, Boise State University in 2015, and the University of Utah in 2016.
+
+Finally, we are also grateful to the University of Utah for hosting a collaborative development visit in 2018, and to the Institute of Mathematics and its Applications for its generous support for our 2019 Coding Sprint.
+The current version of the package was finalized during these events.
 

### 2019-06-06 Fsing/FThresholdsPaper/FThresholds.tex
Updates to Section 2 of the paper

@@
 \usepackage{xspace}
-%\usepackage{rotating}
 \interfootnotelinepenalty=100000
@@
 \end{nouppercase}
+
+% \begin{center}
+% {\large \textbf{The \emph{FrobeniusThresholds} package for \emph{Macaulay2}}}
+% \end{center}
 
@@
 Otherwise, we set $\nu_I^J(p^e) = \infty$.  
-
 This clearly generalizes the quantity $\nu_f^{\idealm}(p^e)$ considered earlier, and we call 
 \[ \ft^J(I) := \lim_{e \to \infty} \frac{ \nu_f^{\idealm}(p^e)}{p^e} \]
-the \emph{$F$-threshold of $I$ with respect to $J$}.
-These numbers are also rational, when finite, and we call the quantity $\ft^{\idealm}(I)$ the $F$-pure threshold of the ideal $I$.
+the \emph{$F$-threshold of $I$ with respect to $J$}.  These numbers are also rational, when they are finite.
+If $I = (f)$ is principal, then we call $\ft^{J}(f) := \ft^J(I)$  the \emph{$F$-threshold of $f$ with respect to $J$}, 
+and $\ft^{\idealm}(I)$ is the \emph{$F$-pure threshold of $I$}. 
 Like $F$-pure thresholds, the $F$-thresholds of $I$ can also be defined in terms of its test ideals.
@@
 \begin{itemize}
-\item \autoref{sec.Nu} describes the methods for approximating the $F$-pure threshold and other $F$-thresholds.  
-\item \autoref{sec.IsFPT} explains the functionality for determining whether a given number is the $F$-pure threshold, or more generally, an \emph{$F$-jumping exponent}.
-\item \autoref{sec.FPT} describes the features of the central function of the package, {\tt fpt}. 
+\item[$\circ$] \autoref{sec.Nu} describes the methods for approximating the $F$-pure threshold and other $F$-thresholds.  
+\item[$\circ$] \autoref{sec.IsFPT} explains the functionality for determining whether a given number is the $F$-pure threshold, or more generally, an \emph{$F$-jumping exponent}.
+\item[$\circ$] \autoref{sec.FPT} describes the features of the central function of the package, {\tt fpt}. 
 \end{itemize}
@@
 
-Many thanks go to the organizers of the \emph{Macaulay2} workshops where much of the functionality described herein was developed, hosted by Wake Forest University in 2012, the University of California, Berkeley in 2014 and 2017, Boise State University in 2015, and the University of Utah in 2016.
+Thanks go to the organizers of the \emph{Macaulay2} workshops where much of the functionality described herein was developed, hosted by Wake Forest University in 2012, the University of California, Berkeley in 2014 and 2017, Boise State University in 2015, and the University of Utah in 2016.
 
-Finally, we are also grateful to the University of Utah for hosting a collaborative development visit in 2018, and to the Institute of Mathematics and its Applications for its generous support for our 2019 Coding Sprint.
+Finally, we are grateful to the University of Utah for hosting a collaborative development visit in 2018, and to the Institute of Mathematics and its Applications for its generous support for our 2019 Coding Sprint.
 The current version of the package was finalized during these events.
@@
 
-We now consider the {\tt nu} function, which is fundamental.   As in the introduction, we work in a polynomial ring over a finite field of characteristic $p>0$.
+We first consider the {\tt nu} function, a fundamental component of the package \emph{FrobeniusThresholds}.
+As in the introduction, in this section we work in a polynomial ring over a finite field of characteristic $p>0$.
 
 Fix a natural number $e$.
-If $f$ is polynomial contained in the radical of an ideal $J$, then the command {\tt nu(e,f,J)} outputs $\nu_f^J(p^e)$, the maximal integer exponent such that $f^n$ is not contained in $J^{[p^e]}$.
-More generally, if $I$ is an ideal contained in the radical of $J$, then {\tt nu(e,I,J)} outputs $\nu_I^J(p^e)$, the maximal integer exponent $n$ such that $I^n$ is not contained in $J^{[p^e]}$.
+If $f$ is a nonzero polynomial contained in the radical of an ideal $J$, then the command {\tt nu(e,f,J)} outputs the integer $\nu_f^J(p^e)$ defined in the introduction, and
+%, the maximal integer exponent such that $f^n$ is not contained in $J^{[p^e]}$.  
+more generally, if a nonzero ideal $I$ is contained in the radical of $J$, then {\tt nu(e,I,J)} outputs $\nu_I^J(p^e)$.
+Consider the following example.
+%, the maximal integer exponent $n$ such that $I^n$ is not contained in $J^{[p^e]}$.
 
@@
 }
+\medspace
 
@@
 
-We highlight some degenerate cases:  If $f$ is zero, then the output of {\tt nu(e,f,J)} is {\tt 0}, and if $f$ is not contained in the radical of $J$, then the output is instead {\tt infinity}.
-These degenerate cases extend analogously to {\tt nu(e,I,J)} when $I$ is an ideal.
+We highlight some degenerate cases:  If $f$ is the zero polynomial, then {\tt nu(e,f,J)} outputs {\tt 0}, and if $f$ is \emph{not} contained in the radical of $J$, then the output is instead {\tt infinity}.
+These degenerate cases extend analogously to the command {\tt nu(e,I,J)}.
 
@@
 
-It is possible to omit the third argument from the function {\tt nu};  in this case, the function assumes that the omitted third argument is the maximal generated by the variables in the ambient polynomial ring.
+If the third argument is omitted from the function {\tt nu}, the third argument is assumed to be the homogeneous maximal ideal of the polynomial ring.
 
@@
 
-It is well-known that if $q=p^e$ for some nonnegative integer $e$, then \[ \nu_I^J(qp) = \nu_I^J(q)\cdot p + L\]  where the error term $L$ is nonnegative, and can be explicitly bounded from above in terms of $p$ and the number of generators of $I$ and $J$.
+It is well known that if $q=p^e$ for some nonnegative integer $e$, then \[ \nu_I^J(qp) = \nu_I^J(q)\cdot p + L\]  where the error term $L$ is nonnegative, and can be explicitly bounded from above in terms of $p$ and the number of generators of $I$ and $J$.
 For instance, the error term $L$ is at most $p-1$ when $I$ is principal and $J$ is arbitrary.
 
-This implies that when searching for the maximal exponent defining {\tt nu(e,I,J)} when $e$ is positive, it is always safe to start at $p$ times the output of {\tt nu(e-1,I,J)}, and one needn't search too far past this number.
-This also suggests that the most efficient way to compute {\tt nu(e,I,J)} is to compute, successively, {\tt nu(s,I,J)}, for each {\tt s = 0,\ldots,e}.
+This implies that when searching for the maximal exponent defining {\tt nu(e,I,J)} for positive $e$, it is safe to start at $p$ times the output of {\tt nu(e-1,I,J)}, and one needn't search too far past this number.
+This also suggests that the most efficient way to compute {\tt nu(e,I,J)} is to compute, successively, {\tt nu(s,I,J)}, for each $s = 0,\ldots,e$.
 This is indeed how the computation is done in most cases.
@@
 {\color{red} Make this consistent with the introduction.  The point is that we have already described how to get the {\tt nu}-s from their limit.  Maybe we should directly cite }.
-If $M$ is the homogeneous maximal ideal of $R$ and $f$ is an element of $R$, the numbers $\nu_f^M(p^e)$ determine and are determined by the $F$-pure threshold of $f$ at the origin.
-Indeed, $\nu_f^M(p^e)$ is $p^e$ times the truncation of the non-terminating base $p$ expansion of fpt($f$) at its $e^{\textrm{th}}$ spot.
-This fact is used to speed up the computations for certain polynomials whose $F$-pure thresholds can be quickly computed via special algorithms, namely diagonal polynomials and binomials.
+
+As pointed out in the introduction, if $\mathfrak{m}$ is the homogeneous maximal ideal and $f \in \mathfrak{m}$, then for all $e$, the values $\nu^{\mathfrak{m}}_f(p^e)$ can be recovered from the $F$-pure threshold of $f$.
+This fact is used to speed up computations for certain polynomials whose $F$-pure thresholds can be computed quickly via specialized algorithms, namely diagonal polynomials, binomials, and forms in two variables (see Section \ref{sec.FPT}).
 This feature can be disabled by setting the option {\tt UseSpecialAlgorithms} (default value {\tt true}) to {\tt false}.
@@
 
-The valid values for the option {\tt ContainmentTest} are {\tt FrobeniusPower}, {\tt FrobeniusRoot}, and {\tt StandardPower}.
+The option {\tt ContainmentTest} for the function {\tt nu} can be set to {\tt FrobeniusPower}, {\tt FrobeniusRoot}, or {\tt StandardPower}.
 The default value of this option depends on what is passed to {\tt nu}.
-Indeed, by default, {\tt ContainmentTest} is set to {\tt FrobeniusRoot} if {\tt nu} is passed a ring element $f$, and is set to {\tt StandardPower} if {\tt nu} is passed an ideal $I$.
-We describe the consequences of setting {\tt ContainmentTest} to each of these values below.
+Indeed, by default, {\tt ContainmentTest} is set to {\tt FrobeniusRoot} if the second argument passed to {\tt nu} is a polynomial, and is set to {\tt StandardPower} if it is an ideal.
+We describe the consequences of setting {\tt ContainmentTest} to each of these values below, using an ideal $I$ as the second argument of $\nu$, since the option works analogously when $I$ is replaced with a polynomial $f$.
 
 First, if {\tt ContainmentTest} is set to {\tt StandardPower}, then the ideal containments checked when computing {\tt nu(e,I,J)} are verified directly.
-That is, the standard power $I^n$ is first computed, and a check is then run to see if it lies in the $p^e$-th Frobenius power of $J$.
-
-Alternately, if {\tt ContainmentTest} is set to {\tt FrobeniusRoot}, then the ideal containments are verified using Frobenius Roots.
+That is, a standard power of $I$ is first computed, say $I^n$, and a check is then run to see if the resulting ideal lies in the $p^e$-th Frobenius power of $J$.
+Alternately, if {\tt ContainmentTest} is set to {\tt FrobeniusRoot}, then the ideal containments are verified through the computation of Frobenius roots.
 That is, the $p^e$-th Frobenius root of $I^n$ is first computed, and a check is then run to see if it lies in $J$.
-The output is unaffected, but this option often speeds up computations, specially when a polynomial or principal ideal is passed as the second argument.
+The output is unaffected, but this option often speeds up computations, especially when a polynomial or principal ideal is passed as the second argument.
 
@@
 
-Finally, when {\tt ContainmentTest} is set to {\tt FrobeniusPower}, then instead of producing the invariant $\nu_I^J(p^e)$ as defined above, {\tt nu(e,I,J,ContainmentTest=>FrobeniusPower)} instead outputs the maximal integer $n$ such that the $n^{\textrm{th}}$ (generalized) Frobenius power of $I$ is not contained in the $p^e$-th Frobenius power of $J$.
+Finally, suppose that {\tt ContainmentTest} is set to {\tt FrobeniusPower}.
+Instead of producing the invariant $\nu_I^J(p^e)$, in this case the {\tt nu} function instead outputs the maximal integer $n$ such that the $n^{\textrm{th}}$ (generalized) Frobenius power of $I$ is not contained in the $p^e$-th Frobenius power of $J$ \cite{hernandez+etal.frobenius_powers}.
+Note that this coincides with $\nu_I^J(p^e)$ when $I$ is replaced with a polynomial, or is a principal ideal.
+After appropriately normalizing and taking the limit of these values as $e$ approaches infinity, these new values limit to certain \emph{critical exponents} (see \emph{loc.~cit.}).
 
@@
 
-i1 : R = ZZ/11[x, y, z]/( x^2 - y*( z - 1 ) );
+i1 : R = ZZ/11[x, y, z]/(x^2 - y*(z - 1));
 
-i2 : compareFPT( 5/11, z - 1 )
+i2 : compareFPT(5/11, z - 1)
 
@@
 
-i3 : isFPT( 1/2, z - 1 )
+i3 : isFPT(1/2, z - 1)
 
@@
 
-i4 : isFPT( 1/2, z - 1, IsLocal => true )
+i4 : isFPT(1/2, z - 1, IsLocal => true)
 
-o4 : false
-
+o4 = false
 \end{MyVerbatim}
 }
+\medspace
 
@@
 
-i50 : f = y*( ( y + 1 ) - ( x - 1 )^2 )*( x - 2 )*( x + y - 2 );
+i50 : f = y*((y + 1) - (x - 1)^2)*(x - 2)*(x + y - 2);
 
-i51 : isFJumpingExponent( 3/4, f )
+i51 : isFJumpingExponent(3/4, f)
 
 o51 = true
-
 \end{MyVerbatim}
 }
+\medspace
 
-\newpage
 \section{The {\tt fpt} function}
@@
 
-i2 : fpt( x^3 + y^3 + z^3 + x*y*z )
+i2 : fpt(x^3 + y^3 + z^3 + x*y*z)
 
@@
 
-i3 : fpt( x^5 + y^6 + z^7 + (x*y*z)^3 )
+i3 : fpt(x^5 + y^6 + z^7 + (x*y*z)^3)
 
@@
 o3 : List
-
 \end{MyVerbatim}
 }
+\medspace
 
@@
 
-i4 : fpt( x^17 + y^20 + z^24 ) -- a diagonal polynomial
+i4 : fpt(x^17 + y^20 + z^24) -- a diagonal polynomial
 
@@
 
-i5 : fpt( x^2*y^6*z^10 + x^10*y^5*z^3 ) -- a binomial
+i5 : fpt(x^2*y^6*z^10 + x^10*y^5*z^3) -- a binomial
 
@@
 
-i7 : fpt( x^2*y^6*(x + y)^9*(x + 3*y)^10 ) -- a form in two variables
+i7 : fpt(x^2*y^6*(x + y)^9*(x + 3*y)^10) -- a form in two variables
 
@@
 o7 : QQ
-
 \end{MyVerbatim}
 }
+\medspace
 
@@
 
-i10 : fpt(L, m)==o7
+i10 : fpt(L, m) == o7
 
 o10 = true
-
 \end{MyVerbatim}
 }
+\medspace
 
@@
 
-i12 : fpt( f, Attempts => 0 ) -- a bad estimate
+i12 : fpt(f, Attempts => 0) -- a bad estimate
 
@@
 
-i13 : fpt( f, Attempts => 0, DepthOfSearch => 3 ) -- a better estimate
+i13 : fpt(f, Attempts => 0, DepthOfSearch => 3) -- a better estimate
 
@@
 
-i14 : fpt( f, Attempts => 1, DepthOfSearch => 3 ) -- the right-hand
+i14 : fpt(f, Attempts => 1, DepthOfSearch => 3) -- the right-hand
 
@@
 
-i16 : fpt( f, Attempts => 1, DepthOfSearch => 3 )
+i16 : fpt(f, Attempts => 1, DepthOfSearch => 3)
 
@@
 
-i17 : fpt( f, Attempts => 2, DepthOfSearch => 3 ) -- the left-hand endpoint
+i17 : fpt(f, Attempts => 2, DepthOfSearch => 3) -- the left-hand endpoint
 
@@
 
-i19 : fpt( f, DepthOfSearch => 3, Attempts => 2 )
+i19 : fpt(f, DepthOfSearch => 3, Attempts => 2)
 
@@
 
-i20 : fpt( f, DepthOfSearch => 3, Attempts => 3 ) -- an additional check
+i20 : fpt(f, DepthOfSearch => 3, Attempts => 3) -- an additional check
 
@@
 
-i21 : fpt( f, DepthOfSearch => 3, Attempts => 4 ) -- and one more finds
+i21 : fpt(f, DepthOfSearch => 3, Attempts => 4) -- and one more finds
 
@@
 o21 : QQ
-
 \end{MyVerbatim}
 }
+\medspace
 
@@
 
-i23 : fpt( f, DepthOfSearch => 3 )
+i23 : fpt(f, DepthOfSearch => 3)
 
@@
 
-i24 : fpt( f, DepthOfSearch => 3, UseFSignature => true )
+i24 : fpt(f, DepthOfSearch => 3, UseFSignature => true)
 
@@
 o26 : List
-
 \end{MyVerbatim}
 }
+\medspace
 
@@
 
-i29 : fpt( f, Attempts => 2, DepthOfSearch => 3, UseFSignature => true ) --
+i29 : fpt(f, Attempts => 2, DepthOfSearch => 3, UseFSignature => true)
 
-      UseFSignature improves the answer a bit
+      -- UseFSignature improves the answer a bit
 
@@
 
-i30 : fpt( f, Attempts => 2, DepthOfSearch => 3, UseFSignature => true,
+i30 : fpt(f, Attempts => 2, DepthOfSearch => 3, UseFSignature => true,
 
-      FRegularityCheck => true ) -- FRegularityCheck finds the answer
+      FRegularityCheck => true) -- FRegularityCheck finds the answer
 
@@
 o30 : QQ
-
 \end{MyVerbatim}
 }
+\medspace
 
@@
 
-i32 : timing numeric fpt( f, DepthOfSearch => 3, UseFSignature => true,
+i32 : timing numeric fpt(f, DepthOfSearch => 3, UseFSignature => true,
 
-      FRegularityCheck => true )
+      FRegularityCheck => true)
 
@@
 
-i33 : timing numeric fpt( f, Attempts => 5, DepthOfSearch => 3 ) -- a better
+i33 : timing numeric fpt(f, Attempts => 5, DepthOfSearch => 3) -- a better
 
@@
 
-i34 : timing fpt( f, DepthOfSearch => 4 ) -- the exact answer in even less
+i34 : timing fpt(f, DepthOfSearch => 4) -- the exact answer in even less
       time
@@
 o34 : Time
-
 \end{MyVerbatim}
 }
+\medspace
 
@@
 
-i36 : fpt( f, DepthOfSearch => 3, UseFSignature => true, Verbose => true )
+i36 : fpt(f, DepthOfSearch => 3, UseFSignature => true, Verbose => true)
 
@@
 o36 : List
-
 \end{MyVerbatim}
 }
+\medspace
 
-\newpage
 \bibliographystyle{skalpha}

### 2019-06-06 Fsing/FThresholdsPaper/FThresholds.tex
Edits to Section 2 of paper

@@
 the \emph{$F$-threshold of $I$ with respect to $J$}.  These numbers are also rational, when they are finite.
-If $I = (f)$ is principal, then we call $\ft^{J}(f) := \ft^J(I)$  the \emph{$F$-threshold of $f$ with respect to $J$}, 
-and $\ft^{\idealm}(I)$ is the \emph{$F$-pure threshold of $I$}. 
-Like $F$-pure thresholds, the $F$-thresholds of $I$ can also be defined in terms of its test ideals.
+The value $\ft^{\idealm}(I)$ is called the \emph{$F$-pure threshold of $I$}, and if $I = (f)$ is principal,  $\ft^{J}(f) := \ft^J(I)$ is called the \emph{$F$-threshold of $f$ with respect to $J$}.
+Like $F$-pure thresholds, $F$-thresholds can also be defined in terms of its test ideals.
 
@@
 
-{\color{red} Make this consistent with the introduction.  The point is that we have already described how to get the {\tt nu}-s from their limit.  Maybe we should directly cite }.
-
 As pointed out in the introduction, if $\mathfrak{m}$ is the homogeneous maximal ideal and $f \in \mathfrak{m}$, then for all $e$, the values $\nu^{\mathfrak{m}}_f(p^e)$ can be recovered from the $F$-pure threshold of $f$.
@@
 
-The option {\tt ContainmentTest} for the function {\tt nu} can be set to {\tt FrobeniusPower}, {\tt FrobeniusRoot}, or {\tt StandardPower}.
+The function {\tt nu} works by searching through the list of potential integers $n$ and checking containments of the $n^\text{the}$ power of $I$ in a specified Frobenius power of $J$.  
+The user can specify how this search is approached through the  option {\tt Search}.
+Namely, a binary search is used when {\tt Search} is set to {\tt Binary} (and this is the default value), and a linear search is run when it is set to {\tt Linear}.
+
+The option {\tt ReturnList} for {\tt nu} (whose default value is {\tt false}) can be set to {\tt true} so that instead of outputting $\nu_I^J(p^e)$, but a list contaning $\nu_I^J(p^i)$, for $i=0,\ldots,e$.
+Alternatively, the option {\tt Verbose} can be set to  to request that the values $\nu_I^J(p^i)$ ($i=0,\ldots,e$) be printed as they are computed, to monitor the progress of the computation.
+
+Finally, we describe the option {\tt ContainmentTest} for the function {\tt nu}.
+This option can be set to {\tt FrobeniusPower}, {\tt FrobeniusRoot}, or {\tt StandardPower}.
 The default value of this option depends on what is passed to {\tt nu}.
@@
 Finally, suppose that {\tt ContainmentTest} is set to {\tt FrobeniusPower}.
-Instead of producing the invariant $\nu_I^J(p^e)$, in this case the {\tt nu} function instead outputs the maximal integer $n$ such that the $n^{\textrm{th}}$ (generalized) Frobenius power of $I$ is not contained in the $p^e$-th Frobenius power of $J$ \cite{hernandez+etal.frobenius_powers}.
-Note that this coincides with $\nu_I^J(p^e)$ when $I$ is replaced with a polynomial, or is a principal ideal.
-After appropriately normalizing and taking the limit of these values as $e$ approaches infinity, these new values limit to certain \emph{critical exponents} (see \emph{loc.~cit.}).
-
-Here, the $n^{\textrm{th}}$ Frobenius power of $I$, when $n$ is a nonnegative integer, is as defined in the paper {\it Frobenius Powers} by Hernández, Teixeira, and Witt.
-In particular, {\tt nu(e,I,J)} and {\tt nu(e,I,J,ContainmentTest=>FrobeniusPower)} need not agree.  However, they will agree when $I$ is a principal ideal.
+Instead of producing the invariant $\nu_I^J(p^e)$, in this case the {\tt nu} function instead outputs the maximal integer $n$ such that the $n^{\textrm{th}}$ \emph{(generalized) Frobenius power} of $I$ is not contained in the $p^e$-th Frobenius power of $J$ \cite{hernandez+etal.frobenius_powers}.
+Note that the resulting value coincides with $\nu_I^J(p^e)$ when $I$ is replaced with a polynomial, or is a principal ideal, but need not coincide in general.
+In line with the philosophy described in the introduction, after appropriately normalizing and taking the limit of these values as $e$ approaches infinity, these new values limit to certain invariants of interest called \emph{critical exponents} (see \emph{loc.~cit.}).
 
@@
 %nu(3, M^5, ContainmentTest => FrobeniusPower)
-
-The function {\tt nu} works by searching through the list of potential integers $n$ and checking containments of $I^n$ in a specified Frobenius power of $J$.
-The way this search is approached is specified by the option {\tt Search}, which can be set to {\tt Binary} (the default value) or {\tt Linear}.
 
@@
 %time nu(2, M, M^2, Search => Linear) -- but linear seach gets luckier
-
-The option {\tt ReturnList} (default value {\tt false}) can be used to request that the output be not only $\nu_I^J(p^e)$, but a list contaning $\nu_I^J(p^i)$, for $i=0,\ldots,e$.
-
-%nu(5, f, ReturnList => true)
-
-Alternatively, the option {\tt Verbose} (default value {\tt false}) can be used to request that the values $\nu_I^J(p^i)$ ($i=0,\ldots,e$) be printed as they are computed, to monitor the progress of the computation.
 

### 2019-06-06 Fsing/FThresholdsPaper/FThresholds.tex
Minor changes to intro

--- 2019-06-06 Fsing/FThresholdsPaper/FThresholds.tex
@@
 \subsection*{Some background and notation}  
-The functionality implemented in the \emph{FrobeniusThresholds} is not restricted to nonsingular ambient rings (see Section \ref{sec.IsFPT}).
-However, for most of this article, we work in a polynomial ring over a finite field of  characteristic $p>0$, and we remain in this case throughout the introduction for the sake of clarity.  
-Unless otherwise stated, all polynomials and ideals under consideration are regarded as elements in such a ring.  The ideal of this ring generated by the ring's variables is denoted $\idealm$.
+It is important to note that much of the functionality implemented in the \emph{FrobeniusThresholds} is not restricted to regular ambient rings; see Section \ref{sec.IsFPT} for a prominent example of this.
 
-Let us roughly outline the way in which many natural numerical invariants in prime characteristic commutative algebra are constructed:  For every natural number $e$, associate to some fixed set of data|often, a collection of polynomials and ideals|an integer describing something of relevance that depends on $e$ (e.g., the dimension of some interesting vector space constructed in terms of your initial data).
-Finally, normalize this integer by dividing by some power of $p^e$, and take the limit as $e$ approaches infinity.
+However, for the sake of concreteness, we will mostly work in a polynomial ring over a finite field of  characteristic $p>0$.
+In fact,  we will work in this context exclusively in this introduction.
+Thus, unless otherwise stated, all polynomials and ideals under consideration are regarded as elements in such a ring.
+The ideal of this ring generated by its variables is denoted $\idealm$.
+
+Let us outline a common way in which natural numerical invariants in prime characteristic commutative algebra are constructed:  For every natural number $e$, associate to some fixed set of data|often, a collection of polynomials and ideals|an integer describing something of relevance that depends on $e$ (e.g., the dimension of some interesting vector space constructed in terms of your initial data).
+Finally, normalize this integer by dividing by some power of $p^e$, and then take the limit as the integer $e$ tends to infinity.
+The resulting limit, should it exist, should then encode some interesting information about your initial set of data.
 

### 2019-06-06 Fsing/FThresholdsPaper/FThresholds.tex
Updates to Section 2 of paper

--- 2019-06-06 Fsing/FThresholdsPaper/FThresholds.tex
@@
 
-{\color{red} This section will need to be modified so that it is consistent with the introduction section.  The point is that a lot of the notation repeated here was introduced earlier there.}
-
 We first consider the {\tt nu} function, a fundamental component of the package \emph{FrobeniusThresholds}.
@@
 This feature can be disabled by setting the option {\tt UseSpecialAlgorithms} (default value {\tt true}) to {\tt false}.
+Consider the following example, where $f$ is a diagonal polynomial.
 
-%R = ZZ/17[x,y,z];
-%f = x^3 + y^4 + z^5; -- a diagonal polynomial
-%time nu(3, f)
-%time nu(3, f, UseSpecialAlgorithms => false)
+{\small
+\setstretch{.67}
+\begin{MyVerbatim}
 
-The function {\tt nu} works by searching through the list of potential integers $n$ and checking containments of the $n^\text{the}$ power of $I$ in a specified Frobenius power of $J$.  
+i1 : R = ZZ/17[x,y,z];
+
+i2 : f = x^3 + y^4 + z^5; -- a diagonal polynomial
+
+i3 : time nu(3, f)
+     -- used 0.00552312 seconds
+
+o3 = 3756
+
+o4 : QQ
+
+i4 : time nu(3, f, UseSpecialAlgorithms => false)
+     -- used 0.155826 seconds
+
+o4 = 3756
+\end{MyVerbatim}
+}
+\medspace
+
+% R = ZZ/17[x,y,z];
+% f = x^3 + y^4 + z^5; -- a diagonal polynomial
+% time nu(3, f)
+% time nu(3, f, UseSpecialAlgorithms => false)
+
+We now describe the options available for the function {\tt nu}, and we focus primarily on the case where the second input is an ideal $I$, since the options work analogously when the second input is instead a polynomial $f$.
+
+In general, the function {\tt nu} works by searching through the list of integers $n$, and checking containments of the $n^\text{th}$ power of $I$ in a specified Frobenius power of $J$.  
 The user can specify how this search is approached through the  option {\tt Search}.
-Namely, a binary search is used when {\tt Search} is set to {\tt Binary} (and this is the default value), and a linear search is run when it is set to {\tt Linear}.
+Namely, a binary search is used when {\tt Search} is set to {\tt Binary} (and this is the option's default value), and a linear search is run when it is set to {\tt Linear}.
 
-The option {\tt ReturnList} for {\tt nu} (whose default value is {\tt false}) can be set to {\tt true} so that instead of outputting $\nu_I^J(p^e)$, but a list contaning $\nu_I^J(p^i)$, for $i=0,\ldots,e$.
-Alternatively, the option {\tt Verbose} can be set to  to request that the values $\nu_I^J(p^i)$ ($i=0,\ldots,e$) be printed as they are computed, to monitor the progress of the computation.
+{\small
+\setstretch{.67}
+\begin{MyVerbatim}
+
+i1 : R = ZZ/5[x,y,z];
+
+i2 : f = x^2*y^4 + y^2*z^7 + z^2*x^8;
+
+i3 : time nu(5, f) -- uses binary search (default)
+     -- used 0.313778 seconds
+
+o3 = 1124
+
+i4 : time nu(5, f, Search => Linear)
+     -- used 0.441903 seconds
+
+o4 = 1124
+
+i5 : m = ideal(x, y, z);
+
+o5 : Ideal of R
+
+i6 : time nu(2, m, m^2) -- uses binary search (default)
+     -- used 1.58258 seconds
+
+o6 = 97
+
+i7 : time nu(2, m, m^2, Search => Linear) -- but linear seach gets luckier
+     -- used 0.531175 seconds
+
+o7 = 97
+\end{MyVerbatim}
+}
+\medspace
+
+%R = ZZ/5[x,y,z];
+%f = x^2*y^4 + y^2*z^7 + z^2*x^8;
+% time nu(5, f) -- uses binary search (default)
+% time nu(5, f, Search => Linear)
+% M = ideal(x, y, z);
+% time nu(2, M, M^2) -- uses binary search (default)
+% time nu(2, M, M^2, Search => Linear) -- but linear seach gets luckier
+
+If the option {\tt ReturnList} is changed from its default value of {\tt false} to {\tt true}, instead of simply outputting $\nu_I^J(p^e)$, {\tt nu} outputs a list of the values $\nu_I^J(p^s)$, for $s=0,\ldots,e$.
+Alternatively, the same information can be found by setting the option {\tt Verbose} to {\tt true} (its default value is {\tt false}), to request that each of these values $\nu_I^J(p^s)$ is printed as they are iteratively computed.
+This can also serve a way to monitor the progress of the computation.
+
+{\small
+\setstretch{.67}
+\begin{MyVerbatim}
+
+i8 : nu(5, f, ReturnList => true)
+
+o8 = {0, 1, 8, 44, 224, 1124}
+
+o8 : List
+
+i9 : nu(5, f, Verbose => true)
+nu(1) = 0
+nu(p^1) = 1
+nu(p^2) = 8
+nu(p^3) = 44
+nu(p^4) = 224
+nu(p^5) = 1124
+\end{MyVerbatim}
+}
+
+%nu(5, f, ReturnList => true)
+%nu(5, f, Verbose => true)
 
@@
 Note that the resulting value coincides with $\nu_I^J(p^e)$ when $I$ is replaced with a polynomial, or is a principal ideal, but need not coincide in general. 
-In line with the philosophy described in the introduction, after appropriately normalizing and taking the limit of these values as $e$ approaches infinity, these new values limit to certain invariants of interest called \emph{critical exponents} (see \emph{loc.~cit.}).
+For example, the two commands below give different output values. 
+{\small
+\setstretch{.67}
+\begin{MyVerbatim}
 
-%R = ZZ/3[x,y];
-%M = ideal(x, y);
-%nu(3, M^5)
-%nu(3, M^5, ContainmentTest => FrobeniusPower)
+i1 : R = ZZ/3[x,y];
 
-%R = ZZ/5[x,y,z];
-%f = x^2*y^4 + y^2*z^7 + z^2*x^8;
-%time nu(5, f) -- uses binary search (default)
-%time nu(5, f, Search => Linear)
-%M = ideal(x, y, z);
-%time nu(2, M, M^2) -- uses binary search (default)
-%time nu(2, M, M^2, Search => Linear) -- but linear seach gets luckier
+i2 : m = ideal(x, y);
 
-%nu(5, f, Verbose => true)
+o2 : Ideal of R
+
+i3 : nu(3, m^5)
+
+o3 = 10
+
+i4 : nu(3, m^5, ContainmentTest => FrobeniusPower)
+
+o4 = 8
+\end{MyVerbatim}
+}
+\medspace
+\noindent In line with the philosophy described in the introduction, after appropriately normalizing and taking the limit of these values as $e$ approaches infinity, the values computed when {\tt ContainmentTest} is set to {\tt FrobeniusPower}
+limit to certain invariants of interest called \emph{critical exponents} (see \cite{hernandez+etal.frobenius_powers}).
+
+% R = ZZ/3[x,y];
+% m = ideal(x, y);
+% nu(3, m^5)
+% nu(3, m^5, ContainmentTest => FrobeniusPower)
 

### 2019-06-06 Fsing/FThresholdsPaper/FThresholds.tex
Changed how title appears in paper
Minor changes to intro of paper

@@
 
-\newenvironment{nouppercase}{%
-\let\uppercase\relax%
-\renewcommand{\uppercasenonmath}[1]{}}{}
+\usepackage{fancyhdr}
+
+\pagestyle{fancy}
+\fancyhead[RO, LE]{\thepage}
+\fancyhead[C]{The \emph{FrobeniusThresholds} package for \emph{Macaulay2}}
+\fancyfoot{}
+\renewcommand{\headrulewidth}{0pt}
+
+\makeatletter
+\def\@settitle{\begin{center}%
+  \baselineskip14\p@\relax
+    \bfseries
+    \normalfont\LARGE%<- NEW
+\@title
+  \end{center}%
+}
+\makeatother
 
@@
 \begin{document}
-\title{The \emph{FrobeniusThresholds} package for \emph{Macaulay2}}
+\title[]{The \emph{FrobeniusThresholds} package for \emph{Macaulay2}}
 
@@
 
-\begin{nouppercase}
 \maketitle
-\end{nouppercase}
 
@@
 \begin{itemize}
-\item[$\circ$] \autoref{sec.Nu} describes the methods for approximating the $F$-pure threshold and other $F$-thresholds.  
+\item[$\circ$] \autoref{sec.Nu} describes the fundamental function {\tt nu}.  As its name suggests, this function is concerned with computing the integers $\nu_I^J(p^e)$ described above.  
 \item[$\circ$] \autoref{sec.IsFPT} explains the functionality for determining whether a given number is the $F$-pure threshold, or more generally, an \emph{$F$-jumping exponent}.
@@
 \subsection*{Acknowledgements.}  First and foremost, the authors enthusiastically thank all authors and contributors to the \emph{FrobeniusThresholds} package.
-Our package coauthors are Dan Smolkin (LIST MORE NAMES), and Zhibek Kadyrsizova, Moty Katzman (LIST MORE NAMES) contributed valuable code to the package. 
+Our package coauthors are Dan Smolkin {\color{red}(LIST MORE NAMES)}, and Zhibek Kadyrsizova, Moty Katzman {\color{red} (LIST MORE NAMES)} contributed valuable code to the package. 
 %Erin Bela, Juliette Bruce, Sara Malec, Maral Mostafazadehfard, Marcus Robinson, Matthew Mastroeni
@@
 That is, a standard power of $I$ is first computed, say $I^n$, and a check is then run to see if the resulting ideal lies in the $p^e$-th Frobenius power of $J$.
+
+%{\color{red} \[ I \subseteq J^{[p^e]} \iff I \subseteq I^{[1/p^e]} \subseteq J.\]}
+
 Alternately, if {\tt ContainmentTest} is set to {\tt FrobeniusRoot}, then the ideal containments are verified through the computation of Frobenius roots.

### 2019-06-06 Fsing/FThresholdsPaper/FThresholds.tex
Tiny changes to paper

--- 2019-06-06 Fsing/FThresholdsPaper/FThresholds.tex
@@
 \begin{abstract}
-   This note describes the \emph{Macaulay2} package \emph{FrobeniusThresholds}.
+   This article describes the \emph{Macaulay2} package \emph{FrobeniusThresholds}.
    This package is designed to estimate and calculate $F$-pure thresholds, more general $F$-thresholds, and related numerical invariants arising in the study of singularities in prime characteristic commutative algebra.
@@
 It is also not so well understood from the perspective of reduction to prime characteristic.
-Nevertheless, $F$-pure thresholds have been the focus of intense study over the past fifteen years, and the \emph{Macaulay2} package \emph{FrobeniusThresholds} is centered around calculating and estimating the $F$-pure threshold and other $F$-thresholds, with the function {\tt fpt} at its core.
+Nevertheless, $F$-pure thresholds have been the focus of intense study over the past 15 years, and the \emph{Macaulay2} package \emph{FrobeniusThresholds} is centered around calculating and estimating the $F$-pure threshold and other $F$-thresholds, with the function {\tt fpt} at its core.
 
@@
 In fact,  we will work in this context exclusively in this introduction.
-Thus, unless otherwise stated, all polynomials and ideals under consideration are regarded as elements in such a ring.
+Thus, unless otherwise stated, all ring elements and ideals under consideration are regarded as elements in such a ring.
 The ideal of this ring generated by its variables is denoted $\idealm$.

### 2019-06-06 Fsing/FThresholdsPaper/FThresholds.tex
Started a section on future work, added some todo notes, other minor changes

--- 2019-06-06 Fsing/FThresholdsPaper/FThresholds.tex
@@
 
+\section{Future work}
+
+\begin{enumerate}
+\item Add more cases to {\tt UseSpecialAlgorithms}.  
+\item Write a function that will extract from this sequences $\{ \nu_f^{\idealm}(p^e) \}_{e=1}^{\infty}$ roots of Bernstein-Sato polynomials.  Especially, strata.
+\item  Add functionality to handle non-principal ideals.  The theoretical foundation for this is the paper of Karl and Kevin \cite{SchwedeTuckerTestIdealsOfNonPrincipal}.
+\item Extend binary forms functions to handle more general $F$-thresholds (that is, with respect to diagonal ideals).
+There is one tricky theoretical things, we don't know when this process would stop.
+If we can do this, then we can compute $F$-pure thresholds of binary forms in non-standard gradings.
+Cite the paper by Daniel and Pedro \cite{HernandezTeixeiraFThresholdFunctions}.
+\end{enumerate}
+
+{\color{red}  Point out for people interested in computing log canonical thresholds:  Zhixian Zhou apparently proved in her thesis that the $F$-pure threshold for hypersurfaces is always a lower bound for the log canonical threshold.
+Therefore, this package effectively computes such lower bounds, and is much faster than the \emph{Dmodules} package, which appears to be the only package in Macaulay2 that computes log canonical thresholds.}
+
 \bibliographystyle{skalpha}

### 2019-06-06 Fsing/FThresholdsPaper/FThresholds.tex

@@
 More precisely,
-\begin{equation}
-\label{sequence-from-limit}
+\begin{equation*}
 \nu_f^{\idealm}(p^e) = \lceil p^e \cdot \ft^{\idealm}(f) \rceil - 1.  
-\end{equation}
+\end{equation*}
 
@@
 
-%R = ZZ/11[x,y];
-%I = ideal(x^2 + y^3, x*y);
-%J = ideal(x^2, y^3);
-%nu(1, I, J)
-%f = x*y*(x^2 + y^2);
-%nu(1, f, J)
+% R = ZZ/11[x,y];
+% I = ideal(x^2 + y^3, x*y);
+% J = ideal(x^2, y^3);
+% nu(1, I, J)
+% f = x*y*(x^2 + y^2);
+% nu(1, f, J)
 
@@
 
-i11 : M = ideal(x, y, z);
+i11 : m = ideal(x, y, z);
 
@@
 
-i12 : nu(2, f) == nu(2, f, M)
+i12 : nu(2, f) == nu(2, f, m)
 

### 2019-06-06 Fsing/FThresholdsPaper/FThresholds.tex
Changes to Section 2 of the paper

--- 2019-06-06 Fsing/FThresholdsPaper/FThresholds.tex
@@
 \documentclass{amsart}
-\usepackage{calc,amssymb,amsthm,amsmath,setspace}
+\usepackage{calc,amssymb,amsthm,amsmath,amsfonts,setspace}
 \RequirePackage[dvipsnames,usenames]{xcolor}
@@
 As in the introduction, in this section we work in a polynomial ring over a finite field of characteristic $p>0$.
+As in the introduction, $\idealm$ will denote the ideal of this ring generated by the variables.
 
@@
 
-If the third argument is omitted from the function {\tt nu}, the third argument is assumed to be the homogeneous maximal ideal of the polynomial ring.
+If the third argument is omitted from the function {\tt nu}, it is assumed to be the maximal ideal $\idealm$.
 
@@
 
-As pointed out in the introduction, if $\mathfrak{m}$ is the homogeneous maximal ideal and $f \in \mathfrak{m}$, then for all $e$, the values $\nu^{\mathfrak{m}}_f(p^e)$ can be recovered from the $F$-pure threshold of $f$.
+As pointed out in the introduction, if $f \in \mathfrak{m}$, the values $\nu^{\mathfrak{m}}_f(p^e)$ can be recovered from the $F$-pure threshold of $f$.  
 This fact is used to speed up computations for certain polynomials whose $F$-pure thresholds can be computed quickly via specialized algorithms, namely diagonal polynomials, binomials, and forms in two variables (see Section \ref{sec.FPT}).
@@
 
-In general, the function {\tt nu} works by searching through the list of integers $n$, and checking containments of the $n^\text{th}$ power of $I$ in a specified Frobenius power of $J$.  
+In general, the function {\tt nu} works by searching through the list of integers $n$, and checking containments of the $n$-th power of $I$ in a specified Frobenius power of $J$.  
 The user can specify how this search is approached through the  option {\tt Search}.
@@
 
-If the option {\tt ReturnList} is changed from its default value of {\tt false} to {\tt true}, instead of simply outputting $\nu_I^J(p^e)$, {\tt nu} outputs a list of the values $\nu_I^J(p^s)$, for $s=0,\ldots,e$.
+If the option {\tt ReturnList} is changed from its default value of {\tt false} to {\tt true}, rather than simply outputting $\nu_I^J(p^e)$, {\tt nu} outputs a list of the values $\nu_I^J(p^s)$, for $s=0,\ldots,e$.
 Alternatively, the same information can be found by setting the option {\tt Verbose} to {\tt true} (its default value is {\tt false}), to request that each of these values $\nu_I^J(p^s)$ is printed as they are iteratively computed.
@@
 
-Finally, we describe the option {\tt ContainmentTest} for the function {\tt nu}.
-This option can be set to {\tt FrobeniusPower}, {\tt FrobeniusRoot}, or {\tt StandardPower}.
-The default value of this option depends on what is passed to {\tt nu}.
-Indeed, by default, {\tt ContainmentTest} is set to {\tt FrobeniusRoot} if the second argument passed to {\tt nu} is a polynomial, and is set to {\tt StandardPower} if it is an ideal.
-We describe the consequences of setting {\tt ContainmentTest} to each of these values below, using an ideal $I$ as the second argument of $\nu$, since the option works analogously when $I$ is replaced with a polynomial $f$.
-
-First, if {\tt ContainmentTest} is set to {\tt StandardPower}, then the ideal containments checked when computing {\tt nu(e,I,J)} are verified directly.
-That is, a standard power of $I$ is first computed, say $I^n$, and a check is then run to see if the resulting ideal lies in the $p^e$-th Frobenius power of $J$.
-
-%{\color{red} \[ I \subseteq J^{[p^e]} \iff I \subseteq I^{[1/p^e]} \subseteq J.\]}
-
-Alternately, if {\tt ContainmentTest} is set to {\tt FrobeniusRoot}, then the ideal containments are verified through the computation of Frobenius roots.
-That is, the $p^e$-th Frobenius root of $I^n$ is first computed, and a check is then run to see if it lies in $J$.
-The output is unaffected, but this option often speeds up computations, especially when a polynomial or principal ideal is passed as the second argument.
-
-%R = ZZ/11[x,y,z];
-%f = x^3 + y^3 + z^3 + x*y*z;
-%time nu(3, f) -- ContainmentTest is set to FrobeniusRoot, by default
-%time nu(3, f, ContainmentTest => StandardPower)
-
-Finally, suppose that {\tt ContainmentTest} is set to {\tt FrobeniusPower}.
-Instead of producing the invariant $\nu_I^J(p^e)$, in this case the {\tt nu} function instead outputs the maximal integer $n$ such that the $n^{\textrm{th}}$ \emph{(generalized) Frobenius power} of $I$ is not contained in the $p^e$-th Frobenius power of $J$ \cite{hernandez+etal.frobenius_powers}.
-Note that the resulting value coincides with $\nu_I^J(p^e)$ when $I$ is replaced with a polynomial, or is a principal ideal, but need not coincide in general. 
+As described in the introduction, the integer $\nu_I^J(p^e)$ is defined in terms of the containment conditions on powers of ideals. 
+For positive integers $n$ and $e$, and an ideal $I$ contained in the radical of another ideal $J$, we have that 
+\begin{equation*}
+  I^n \subseteq J^{[p^e]} \Longleftrightarrow (I^n)^{[1/p^e]} \subseteq J 
+\end{equation*}
+where $(I^n)^{[1/p^e]}$ denotes the $p^e$-th \emph{Frobenius root} of $I^n$, as defined in \cite{BlickleMustataSmithDiscretenessAndRationalityOfFThresholds}.
+The option {\tt ContainmentTest} for {\tt nu} allows the user to choose which of the two types of containment statements appearing above to use toward the calculation of $\nu_I^J(p^e)$.
+
+If {\tt ContainmentTest} is set to {\tt StandardPower}, then {\tt nu(e,I,J)} is computed by testing the left-hand containment above, and when it is set to {\tt FrobeniusRoot}, the right-hand containment is checked.
+For efficiency reasons, the default value for {\tt ContainmentTest} is set to  {\tt FrobeniusRoot} if the second argument passed to {\tt nu} is a polynomial, and is set to {\tt StandardPower} if it is an ideal.
+
+{\small
+\setstretch{.67}
+\begin{MyVerbatim}
+
+i1 : R = ZZ/11[x,y,z];
+
+i2 : f = x^3 + y^3 + z^3 + x*y*z;
+
+i3 : time nu(3, f) -- ContainmentTest is set to FrobeniusRoot, by default
+     -- used 0.116697 seconds
+
+o3 = 1209
+
+i4 : time nu(3, f, ContainmentTest => StandardPower)
+     -- used 9.65013 seconds
+
+o4 = 1209
+\end{MyVerbatim}
+}
+\medspace
+
+% R = ZZ/11[x,y,z];
+% f = x^3 + y^3 + z^3 + x*y*z;
+% time nu(3, f) -- ContainmentTest is set to FrobeniusRoot, by default
+% time nu(3, f, ContainmentTest => StandardPower)
+
+The option {\tt ContainmentTest} has a third possible value, {\tt FrobeniusPower}, which may produce a different result than the other two values.  
+Given an ideal $I$, the first, third, and fourth authors introduced the notion of a (generalized) Frobenius power $I^{[n]}$ of $I$, when $n$ is an arbitrary positive integer, not necessarily of the form $n = p^e$ \cite{hernandez+etal.frobenius_powers}.
+When {\tt ContainmentTest} is set to {\tt FrobeniusPower}, rather than  computing $\nu_I^J(p^e)$, the function {\tt nu} computes the 
+maximal integer $n$ for which $I^{[n]}$ is not contained in $J^{[p^e]}$.
+This number is denoted $\mu_I^J(p^e)$ in \emph{loc.\ cit.}, and equals $\nu_I^J(p^e)$ when $I$ is replaced with a polynomial, or is a principal ideal, but need not coincide in general.
 For example, the two commands below give different output values.
+
 {\small
@@
 }
-\medspace
-\noindent In line with the philosophy described in the introduction, after appropriately normalizing and taking the limit of these values as $e$ approaches infinity, the values computed when {\tt ContainmentTest} is set to {\tt FrobeniusPower}
-limit to certain invariants of interest called \emph{critical exponents} (see \cite{hernandez+etal.frobenius_powers}).
+
+\medspace
+\noindent In line with the philosophy described in the introduction, after appropriately normalizing and taking the limit as $e$ approaches infinity, the values $\mu_I^J(p^e)$ determine certain invariants of interest called \emph{critical exponents}.
 

### 2019-06-06 Fsing/FThresholdsPaper/FThresholds.tex
Minor changes to the paper (adding SNC stuff).

--- 2019-06-06 Fsing/FThresholdsPaper/FThresholds.tex
@@
 
-Fix a natural number $e$.
-If $f$ is a nonzero polynomial contained in the radical of an ideal $J$, then the command {\tt nu(e,f,J)} outputs the integer $\nu_f^J(p^e)$ defined in the introduction, and
+Fix a natural number $e$.  If $f$ is a nonzero polynomial contained in the radical of an ideal $J$, then the command {\tt nu(e,f,J)} outputs the integer $\nu_f^J(p^e)$ defined in the introduction, and
 %, the maximal integer exponent such that $f^n$ is not contained in $J^{[p^e]}$.
@@
 
-If the option {\tt UseSpecialAlgorithms} is set to {\tt true} (the default value), then {\tt fpt} first checks whether $f$ is a diagonal polynomial, a binomial, or a form in two variables, in that order.
-If it is one of these, algorithms of Hern\'andez \cite{HernandezFInvariantsOfDiagonalHyp, HernandezFPureThresholdOfBinomial}, or Hern\'andez and Teixeira \cite{HernandezTeixeiraFThresholdFunctions},  are executed to compute the $F$-pure threshold (cf.
+If the option {\tt UseSpecialAlgorithms} is set to {\tt true} (the default value), then {\tt fpt} first checks whether $f$ is a monomial, a diagonal polynomial, a binomial, a form in two variables, or a product of factors in simple normal crossing, in that order.
+The monomials and the simple normal crossing cases are computed as the reciprocal of maximal exponent of the factors.
+Outside of that simple case, algorithms of Hern\'andez \cite{HernandezFInvariantsOfDiagonalHyp, HernandezFPureThresholdOfBinomial}, or Hern\'andez and Teixeira \cite{HernandezTeixeiraFThresholdFunctions},  are executed to compute the $F$-pure threshold (cf.
 \cite{ShibutaTakagiLCThresholds}).
@@
 \medspace
+There is one other relevant special algorithm which checks whether the polynomial $f$ factors as a product of functions $f = \prod_i f_i^(a_i)$ that are in simple normal crossing with each other (in which case, the $F$-pure threshold is just the minimum of the $1/a_i$ as mentioned above).
+Recall that a set of elements $\{f_i\}$ are said to be in simple normal crossing at a point, if locally, the $f_i$ form part of a regular system of parameters.
+We check this looking at the jacobian matrix of each the subsets of the $f_i$ (evaluated at the origin) and checking that these matrices have the expected rank.
+We also verify that these subsets generate ideals of the correct height.
+Note, this calls {\tt factor f}, which may be slow.
+The user can turn off this factorization call with {\tt UseSpecialAlgorithms => false}
+
+This calls the function {\tt isSimpleNormalCrossing} which is also exposed to the user.
+Note, if one sets the {\tt IsLocal => true} option, the {\tt isSimpleNormalCrossing} function checks that the $f_i$ are in simple normal crossing everywhere, which can be much slower (as jacobian ideals are computed).
 
@@
 
-\section{Future work}
-
-\begin{enumerate}
-\item Add more cases to {\tt UseSpecialAlgorithms}.  
-\item Write a function that will extract from this sequences $\{ \nu_f^{\idealm}(p^e) \}_{e=1}^{\infty}$ roots of Bernstein-Sato polynomials.  Especially, strata.
-\item  Add functionality to handle non-principal ideals.  The theoretical foundation for this is the paper of Karl and Kevin \cite{SchwedeTuckerTestIdealsOfNonPrincipal}.
-\item Extend binary forms functions to handle more general $F$-thresholds (that is, with respect to diagonal ideals).
-There is one tricky theoretical things, we don't know when this process would stop.
-If we can do this, then we can compute $F$-pure thresholds of binary forms in non-standard gradings.
-Cite the paper by Daniel and Pedro \cite{HernandezTeixeiraFThresholdFunctions}.
-\end{enumerate}
-
-{\color{red}  Point out for people interested in computing log canonical thresholds:  Zhixian Zhou apparently proved in her thesis that the $F$-pure threshold for hypersurfaces is always a lower bound for the log canonical threshold.
-Therefore, this package effectively computes such lower bounds, and is much faster than the \emph{Dmodules} package, which appears to be the only package in Macaulay2 that computes log canonical thresholds.}
-
 \bibliographystyle{skalpha}

### 2019-06-06 Fsing/FThresholdsPaper/FThresholds.tex
Minor changes
Typos fixed.

--- 2019-06-06 Fsing/FThresholdsPaper/FThresholds.tex
@@
 \medspace
+There is one other relevant special algorithm which checks whether the polynomial $f$ factors as a product of functions $f = \prod_i f_i^{a_i}$ that are in simple normal crossing with each other (in which case, the $F$-pure threshold is just the minimum of the $1/a_i$ as mentioned above).
+Recall that a set of elements $\{f_i\}$ are said to be in simple normal crossing at a point, if locally, the $f_i$ form part of a regular system of parameters.
+We verify this by looking at the jacobian matrix of each the subsets of the $f_i$ (evaluated at the origin) and checking that these matrices have the expected rank.
+We also verify that these subsets generate ideals of the correct height.
+Note, this calls {\tt factor f}, which may be slow.
+The user can turn off this factorization call with {\tt UseSpecialAlgorithms => false}.
+
+This calls the function {\tt isSimpleNormalCrossing} which is also exposed to the user.
+Note, if one sets the {\tt IsLocal => true} option, the {\tt isSimpleNormalCrossing} function checks that the $f_i$ are in simple normal crossing everywhere, which can be much slower (as jacobian ideals are computed).
 

### 2019-06-06 Fsing/FThresholdsPaper/FThresholds.tex
Rewording the paper (snc section) slightly.

@@
 i9 : nu(5, f, Verbose => true)
+
      nu(1) = 0
@@
 \medspace
-There is one other relevant special algorithm which checks whether the polynomial $f$ factors as a product of functions $f = \prod_i f_i^{a_i}$ that are in simple normal crossing with each other (in which case, the $F$-pure threshold is just the minimum of the $1/a_i$ as mentioned above).
+We also briefly describe the algorithm which checks whether the polynomial $f$ factors as a product of functions $f = \prod_i f_i^{a_i}$ that are in simple normal crossing with each other (in which case, the $F$-pure threshold is just the minimum of the $1/a_i$ as mentioned above).
 Recall that a set of elements $\{f_i\}$ are said to be in simple normal crossing at a point, if locally, the $f_i$ form part of a regular system of parameters.

### 2019-06-06 Fsing/FThresholdsPaper/FThresholds.tex
Minor changes to paper

--- 2019-06-06 Fsing/FThresholdsPaper/FThresholds.tex
@@
 
-Fix a natural number $e$.  If $f$ is a nonzero polynomial contained in the radical of an ideal $J$, then the command {\tt nu(e,f,J)} outputs the integer $\nu_f^J(p^e)$ defined in the introduction, and
+Fix a natural number $e$.
+If $f$ is a nonzero polynomial contained in the radical of an ideal $J$, then the command {\tt nu(e,f,J)} outputs the integer $\nu_f^J(p^e)$ defined in the introduction, and
 %, the maximal integer exponent such that $f^n$ is not contained in $J^{[p^e]}$.  
@@
 
-If the option {\tt UseSpecialAlgorithms} is set to {\tt true} (the default value), then {\tt fpt} first checks whether $f$ is a monomial, a diagonal polynomial, a binomial, a form in two variables, or a product of factors in simple normal crossing, in that order.
-The monomials and the simple normal crossing cases are computed as the reciprocal of maximal exponent of the factors.
-Outside of that simple case, algorithms of Hern\'andez \cite{HernandezFInvariantsOfDiagonalHyp, HernandezFPureThresholdOfBinomial}, or Hern\'andez and Teixeira \cite{HernandezTeixeiraFThresholdFunctions},  are executed to compute the $F$-pure threshold (cf.
+If the option {\tt UseSpecialAlgorithms} is set to {\tt true} (the default value), then {\tt fpt} first checks whether $f$ is a diagonal polynomial, a binomial, or a form in two variables, in that order.
+If it is one of these, algorithms of Hern\'andez \cite{HernandezFInvariantsOfDiagonalHyp, HernandezFPureThresholdOfBinomial}, or Hern\'andez and Teixeira \cite{HernandezTeixeiraFThresholdFunctions},  are executed to compute the $F$-pure threshold (cf.
 \cite{ShibutaTakagiLCThresholds}).
@@
 \medspace
-There is one other relevant special algorithm which checks whether the polynomial $f$ factors as a product of functions $f = \prod_i f_i^{a_i}$ that are in simple normal crossing with each other (in which case, the $F$-pure threshold is just the minimum of the $1/a_i$ as mentioned above).
-Recall that a set of elements $\{f_i\}$ are said to be in simple normal crossing at a point, if locally, the $f_i$ form part of a regular system of parameters.
-We verify this by looking at the jacobian matrix of each the subsets of the $f_i$ (evaluated at the origin) and checking that these matrices have the expected rank.
-We also verify that these subsets generate ideals of the correct height.
-Note, this calls {\tt factor f}, which may be slow.
-The user can turn off this factorization call with {\tt UseSpecialAlgorithms => false}.
-
-This calls the function {\tt isSimpleNormalCrossing} which is also exposed to the user.
-Note, if one sets the {\tt IsLocal => true} option, the {\tt isSimpleNormalCrossing} function checks that the $f_i$ are in simple normal crossing everywhere, which can be much slower (as jacobian ideals are computed).
 

### 2019-06-06 Fsing/FThresholdsPaper/FThresholds.tex
More rewording of the paper.

--- 2019-06-06 Fsing/FThresholdsPaper/FThresholds.tex
@@
 \end{itemize}
-This package builds heavily upon the \emph{TestIdeals} package for \emph{Macaulay2}, which provides a broad range of functionality in prime characteristic commutative algebra.
+
+This package builds heavily upon the \emph{TestIdeals} package for \emph{Macaulay2} \cite{TestIdealsPackage, TestIdealsPaper}, which provides a broad range of functionality for effective computation in prime characteristic commutative algebra.
 
@@
 
-This calls the function {\tt isSimpleNormalCrossing} which is also exposed to the user.
+To verify whether $f$ factors into simple normal crossing factors, the function {\tt isSimpleNormalCrossing} is called.
+This function is also exposed to the user.
 Note, if one sets the {\tt IsLocal => true} option, the {\tt isSimpleNormalCrossing} function checks that the $f_i$ are in simple normal crossing everywhere, which can be much slower (as jacobian ideals are computed).
@@
 
+\newpage
 \section{Future work}
+
+We conclude this note with some comments on possible future improvements to the package.
 

### 2019-06-06 Fsing/FThresholdsPaper/FThresholds.tex
Added red note for Karl sd sd
Minor changes to paper

@@
 \medspace
-We also briefly describe the algorithm which checks whether the polynomial $f$ factors as a product of functions $f = \prod_i f_i^{a_i}$ that are in simple normal crossing with each other (in which case, the $F$-pure threshold is just the minimum of the $1/a_i$ as mentioned above).
+
+If $f$ does not fall into any of the forementioned cases,
+{\tt UseSpecialAlgorithms} next checks whether the polynomial $f$ has simple normal crossings, in which case its $F$-pure threshold can easily be computed.   
+We briefly describe the algorithm which checks whether the polynomial $f$ factors as a product of functions $f = \prod_i f_i^{a_i}$ that are in simple normal crossing with each other (in which case, the $F$-pure threshold is just the minimum of the $1/a_i$ as mentioned above).
 Recall that a set of elements $\{f_i\}$ are said to be in simple normal crossing at a point, if locally, the $f_i$ form part of a regular system of parameters.

### 2019-06-06 Fsing/FThresholdsPaper/FThresholds.tex
Minor edits to paper

--- 2019-06-06 Fsing/FThresholdsPaper/FThresholds.tex
@@
 
+%This is for Karl
+{\color{red}  Point out for people interested in computing log canonical thresholds:  Zhixian Zhou apparently proved in her thesis that the $F$-pure threshold for hypersurfaces is always a lower bound for the log canonical threshold.
+Therefore, this package effectively computes such lower bounds, and is much faster than the \emph{Dmodules} package, which appears to be the only package in Macaulay2 that computes log canonical thresholds.}
+
 This paper describes the \emph{Macaulay2} \cite{M2} package \emph{FrobeniusThresholds}, which provides tools for computing certain fundamental invariants arising in positive characteristic commutative algebra.
@@
 \medspace
-We also briefly describe the algorithm which checks whether the polynomial $f$ factors as a product of functions $f = \prod_i f_i^{a_i}$ that are in simple normal crossing with each other (in which case, the $F$-pure threshold is just the minimum of the $1/a_i$ as mentioned above).
-Recall that a set of elements $\{f_i\}$ are said to be in simple normal crossing at a point, if locally, the $f_i$ form part of a regular system of parameters.
-We verify this by looking at the jacobian matrix of each the subsets of the $f_i$ (evaluated at the origin) and checking that these matrices have the expected rank.
-We also verify that these subsets generate ideals of the correct height.
-Note, this calls {\tt factor f}, which may be slow.
-The user can turn off this factorization call with {\tt UseSpecialAlgorithms => false}.
-
-To verify whether $f$ factors into simple normal crossing factors, the function {\tt isSimpleNormalCrossing} is called.
-This function is also exposed to the user.
-Note, if one sets the {\tt IsLocal => true} option, the {\tt isSimpleNormalCrossing} function checks that the $f_i$ are in simple normal crossing everywhere, which can be much slower (as jacobian ideals are computed).
+
+If {\tt UseSpecialAlgorithms} is set to {\tt true} and $f$ does not fall into any of the three forementioned cases, then the function {\tt fpt} next checks whether the polynomial $f$ has simple normal crossings, in which case its $F$-pure threshold is easily computed.
+
+We briefly describe the algorithm which checks whether the polynomial $f$ factors as a product of functions $f = \prod_i f_i^{a_i}$ that are in simple normal crossing with each other, in which case, the $F$-pure threshold is just the minimum of the $1/a_i$.
+Recall that a set of elements $\{f_i\}$ is said to be in simple normal crossing at a point, if locally, the $f_i$ form part of a regular system of parameters.
+The functionality verifies this by computing the Jacobian matrix of each subset of the $f_i$ (evaluated at the origin), and checking that these matrices have the expected rank.
+It is also verified that these subsets generate ideals of the correct height.
+Note that {\tt factor f} is called, which may be slow.
+The user can avoid this factorization call by setting {\tt UseSpecialAlgorithms} to {\tt false}.
+
+This method for determining whether $f$ is in simple normal crossing is implemented in the function {\tt isSimpleNormalCrossing}, which is also exposed to the user.
+Note that if one sets the option {\tt IsLocal} for this function to {\tt true}, then {\tt isSimpleNormalCrossing} checks that the $f_i$ are in simple normal crossing \emph{everywhere}, which can be much slower (as Jacobian ideals are computed).
 
@@
 
-{\color{red}  Point out for people interested in computing log canonical thresholds:  Zhixian Zhou apparently proved in her thesis that the $F$-pure threshold for hypersurfaces is always a lower bound for the log canonical threshold.
-Therefore, this package effectively computes such lower bounds, and is much faster than the \emph{Dmodules} package, which appears to be the only package in Macaulay2 that computes log canonical thresholds.}
-
 \bibliographystyle{skalpha}

### 2019-06-06 Fsing/FThresholdsPaper/FThresholds.tex
Some minor changes to the paper

--- 2019-06-06 Fsing/FThresholdsPaper/FThresholds.tex
@@
 \item[$\circ$] \autoref{sec.FPT} describes the features of the central function of the package, {\tt fpt}.
+\item[$\circ$]  {\color{red} Add a description of the last section}
 \end{itemize}
-
-This package builds heavily upon the \emph{TestIdeals} package for \emph{Macaulay2} \cite{TestIdealsPackage, TestIdealsPaper}, which provides a broad range of functionality for effective computation in prime characteristic commutative algebra.
+{\color{red} Move this later}
+The \emph{FrobeniusThresholds} package builds heavily upon the \emph{TestIdeals} package for \emph{Macaulay2} \cite{TestIdealsPackage, TestIdealsPaper}, which provides a broad range of functionality for effective computation in prime characteristic commutative algebra.
 
@@
 \newpage
-\section{Future work}
-
-We conclude this note with some comments on possible future improvements to the package.
+\section{Future Directions}
+
+{\color{red} Should we add this section to the \textbf{Organization} part of the intro?}
+
+We conclude with some comments on possible improvements to the package.
+
+One natural candidate for improvement would be to extend functionality to better handle nonprincipal ideals.
+In particular, the package could be improved if it could use the test ideals $\tau(I^t)$ when $I$ is not necessarily principal.
+Fortunately, the theoretical foundation for computing such ideals has already largely been worked out in the paper \cite{SchwedeTuckerTestIdealsOfNonPrincipal}.
+However, such an improvement would necessarily require an update to the \emph{TestIdeals} package.
 
@@
 \item Write a function that will extract from this sequences $\{ \nu_f^{\idealm}(p^e) \}_{e=1}^{\infty}$ roots of Bernstein-Sato polynomials.  Especially, strata.
-\item  Add functionality to handle non-principal ideals.  The theoretical foundation for this is the paper of Karl and Kevin \cite{SchwedeTuckerTestIdealsOfNonPrincipal}.
+
 \item Extend binary forms functions to handle more general $F$-thresholds (that is, with respect to diagonal ideals).

### 2019-06-06 Fsing/FThresholdsPaper/FThresholds.tex
Edits to paper and documentation

--- 2019-06-06 Fsing/FThresholdsPaper/FThresholds.tex
@@
 
-If {\tt UseSpecialAlgorithms} is set to {\tt true} and $f$ does not fall into any of the three forementioned cases, then the function {\tt fpt} next checks whether the polynomial $f$ has simple normal crossings, in which case its $F$-pure threshold is easily computed.
-
-We briefly describe the algorithm which checks whether the polynomial $f$ factors as a product of functions $f = \prod_i f_i^{a_i}$ that are in simple normal crossing with each other, in which case, the $F$-pure threshold is just the minimum of the $1/a_i$.
+If {\tt UseSpecialAlgorithms} is set to {\tt true} and $f$ does not fall into any of the three forementioned cases, then the function {\tt fpt} next checks whether the polynomial $f$ is a product of factors that are in simple normal crossing, in which case its $F$-pure threshold is easily computed.
+
+We briefly describe the algorithm that checks whether the polynomial $f$ factors as a product of functions $f = \prod_i f_i^{a_i}$ that are in simple normal crossing with each other, in which case, the $F$-pure threshold is just the minimum of the $1/a_i$.
 Recall that a set of elements $\{f_i\}$ is said to be in simple normal crossing at a point, if locally, the $f_i$ form part of a regular system of parameters.
@@
 
-This method for determining whether $f$ is in simple normal crossing is implemented in the function {\tt isSimpleNormalCrossing}, which is also exposed to the user.
+This method for determining whether $f$ is a product of factors that are in simple normal crossing is implemented in the function {\tt isSimpleNormalCrossing}, which is also exposed to the user.
 Note that if one sets the option {\tt IsLocal} for this function to {\tt true}, then {\tt isSimpleNormalCrossing} checks that the $f_i$ are in simple normal crossing \emph{everywhere}, which can be much slower (as Jacobian ideals are computed).

### 2019-06-06 Fsing/FThresholdsPaper/FThresholds.tex
Added a paragraph to the introduction.

--- 2019-06-06 Fsing/FThresholdsPaper/FThresholds.tex
@@
 %This is for Karl
-{\color{red}  Point out for people interested in computing log canonical thresholds:  Zhixian Zhou apparently proved in her thesis that the $F$-pure threshold for hypersurfaces is always a lower bound for the log canonical threshold.
+%{\color{red}  Point out for people interested in computing log canonical thresholds:  Zhixian Zhou apparently proved in her thesis that the $F$-pure threshold for hypersurfaces is always a lower bound for the log canonical threshold.
 Therefore, this package effectively computes such lower bounds, and is much faster than the \emph{Dmodules} package, which appears to be the only package in Macaulay2 that computes log canonical thresholds.}
 
-This paper describes the \emph{Macaulay2} \cite{M2} package \emph{FrobeniusThresholds}, which provides tools for computing certain fundamental invariants arising in positive characteristic commutative algebra.
+This paper describes the \emph{Macaulay2} \cite{M2} package \emph{FrobeniusThresholds} \cite{FThresholdsPackage}, which provides tools for computing certain fundamental invariants arising in positive characteristic commutative algebra.
 More precisely, this package concerns the effective computation of \emph{$F$-pure thresholds}, \emph{$F$-thresholds}, and \emph{$F$-jumping exponents}.
@@
 
-Along these lines, the \emph{$F$-pure threshold} %associated to an element of $R$
-was defined in analogy with the \emph{log canonical threshold} \cite{TakagiWatanabeFPureThresh}, and
+Along these lines, the \emph{$F$-pure threshold} (fpt)%associated to an element of $R$
+was defined in analogy with the \emph{log canonical threshold} (lct) \cite{TakagiWatanabeFPureThresh}, and
 %The $F$-pure threshold of the pair $(R, f)$ is the supremum over all $t$ for which $(R, f^t)$ is $F$-pure.
@@
 Nevertheless, $F$-pure thresholds have been the focus of intense study over the past 15 years, and the \emph{Macaulay2} package \emph{FrobeniusThresholds} is centered around calculating and estimating the $F$-pure threshold and other $F$-thresholds, with the function {\tt fpt} at its core.
+
+The $F$-pure threshold can also be used to provide a lower bound for the log canonical threshold in characteristic zero.
+Indeed, Z.~Zhu showed in \cite[Corollary 4.2]{ZhuLogCanoincalThresholdsInPositiveChar} that if $f \in \bQ[x_1, \dots, x_n]$ is reduced modulo $p > 0$ to obtain $f_p = f\;\mathrm{mod}\;p \in \bF_p[x_1, \dots, x_n]$, then $\fpt(f_p) \leq \lct(f)$.
+There is a general purpose implementation of log canonical thresholds in the \emph{Dmodules} package by A.~Leykin and H.~Tsai \cite{DmodulesSource} and a package \emph{MultiplierIdeals} by Z.~Teitler, B.~Snapp and C.~Raicu \cite{MultiplierIdealsPackage}, which computes log canonical thresholds for special cases (monomial ideals, hyperplane arrangements, generic determinantal ideals, and certain binomial ideals), see also the paper \cite{MultiplierIdealsArticle}.
+However, our general purpose implementation of ${\tt fpt}$ in small characteristic is typically much faster than {\tt lct}, the general purpose function from \emph{Dmodules} which computes the log canonical threshold.
 
@@
 \medspace
-
-If {\tt UseSpecialAlgorithms} is set to {\tt true} and $f$ does not fall into any of the three forementioned cases, then the function {\tt fpt} next checks whether the polynomial $f$ is a product of factors that are in simple normal crossing, in which case its $F$-pure threshold is easily computed.
-
-We briefly describe the algorithm that checks whether the polynomial $f$ factors as a product of functions $f = \prod_i f_i^{a_i}$ that are in simple normal crossing with each other, in which case, the $F$-pure threshold is just the minimum of the $1/a_i$.
-Recall that a set of elements $\{f_i\}$ is said to be in simple normal crossing at a point, if locally, the $f_i$ form part of a regular system of parameters.
-The functionality verifies this by computing the Jacobian matrix of each subset of the $f_i$ (evaluated at the origin), and checking that these matrices have the expected rank.
-It is also verified that these subsets generate ideals of the correct height.
-Note that {\tt factor f} is called, which may be slow.
-The user can avoid this factorization call by setting {\tt UseSpecialAlgorithms} to {\tt false}.
-
-This method for determining whether $f$ is a product of factors that are in simple normal crossing is implemented in the function {\tt isSimpleNormalCrossing}, which is also exposed to the user.
-Note that if one sets the option {\tt IsLocal} for this function to {\tt true}, then {\tt isSimpleNormalCrossing} checks that the $f_i$ are in simple normal crossing \emph{everywhere}, which can be much slower (as Jacobian ideals are computed).
+We also briefly describe the algorithm which checks whether the polynomial $f$ factors as a product of functions $f = \prod_i f_i^{a_i}$ that are in simple normal crossing with each other (in which case, the $F$-pure threshold is just the minimum of the $1/a_i$ as mentioned above).
+Recall that a set of elements $\{f_i\}$ are said to be in simple normal crossing at a point, if locally, the $f_i$ form part of a regular system of parameters.
+We verify this by looking at the jacobian matrix of each the subsets of the $f_i$ (evaluated at the origin) and checking that these matrices have the expected rank.
+We also verify that these subsets generate ideals of the correct height.
+Note, this calls {\tt factor f}, which may be slow.
+The user can turn off this factorization call with {\tt UseSpecialAlgorithms => false}.
+
+To verify whether $f$ factors into simple normal crossing factors, the function {\tt isSimpleNormalCrossing} is called.
+This function is also exposed to the user.
+Note, if one sets the {\tt IsLocal => true} option, the {\tt isSimpleNormalCrossing} function checks that the $f_i$ are in simple normal crossing everywhere, which can be much slower (as jacobian ideals are computed).
 

### 2019-06-06 Fsing/FThresholdsPaper/FThresholds.tex
Small changes to the paper.

@@
 \item[$\circ$] \autoref{sec.FPT} describes the features of the central function of the package, {\tt fpt}.
-\item[$\circ$]  {\color{red} Add a description of the last section}
+\item[$\circ$]  \autoref{sec.FutureDirections} describes our plans for future improvements to this package.
 \end{itemize}
-{\color{red} Move this later}
-The \emph{FrobeniusThresholds} package builds heavily upon the \emph{TestIdeals} package for \emph{Macaulay2} \cite{TestIdealsPackage, TestIdealsPaper}, which provides a broad range of functionality for effective computation in prime characteristic commutative algebra.
+%{\color{red} Move this later}
 
@@
 %Erin Bela, Juliette Bruce, Sara Malec, Maral Mostafazadehfard, Marcus Robinson, Matthew Mastroeni
+
+The \emph{FrobeniusThresholds} package builds heavily upon the \emph{TestIdeals} package for \emph{Macaulay2} \cite{TestIdealsPackage, TestIdealsPaper,M2}, which provides a broad range of functionality for effective computation in prime characteristic commutative algebra.
+In fact, both this package and \emph{TestIdeals} are derived from an older package \emph{PosChar}.
 
@@
 \section{Future Directions}
-
-{\color{red} Should we add this section to the \textbf{Organization} part of the intro?}
+\label{sec.FutureDirections}
 

### 2019-06-07 Fsing/FThresholdsPaper/FThresholds.tex
Minor changes to package and paper

@@
 
-% \begin{center}
-% {\large \textbf{The \emph{FrobeniusThresholds} package for \emph{Macaulay2}}}
-% \end{center}
-
 \section{Introduction}
@@
 
+Finally, we point out that the  \emph{FrobeniusThresholds} package builds heavily upon the \emph{TestIdeals} package for \emph{Macaulay2} \cite{TestIdealsPackage, TestIdealsPaper,M2}, which provides a broad range of functionality for effective computation in prime characteristic commutative algebra.
+In fact, both this package and \emph{TestIdeals} are derived from an older package \emph{PosChar}.
+
 \subsection*{Organization}
@@
 
-\subsection*{Acknowledgements.}  First and foremost, the authors enthusiastically thank all authors and contributors to the \emph{FrobeniusThresholds} package.
-Our package coauthors are Dan Smolkin {\color{red}(LIST MORE NAMES)}, and Zhibek Kadyrsizova, Moty Katzman {\color{red} (LIST MORE NAMES)} contributed valuable code to the package.
-%Erin Bela, Juliette Bruce, Sara Malec, Maral Mostafazadehfard, Marcus Robinson, Matthew Mastroeni
-
-The \emph{FrobeniusThresholds} package builds heavily upon the \emph{TestIdeals} package for \emph{Macaulay2} \cite{TestIdealsPackage, TestIdealsPaper,M2}, which provides a broad range of functionality for effective computation in prime characteristic commutative algebra.
-In fact, both this package and \emph{TestIdeals} are derived from an older package \emph{PosChar}.
+\subsection*{Acknowledgements.}  First and foremost, the authors enthusiastically thank all authors and contributors to the
+\emph{FrobeniusThresholds} package.  {\color{red} (CHECK THESE NAMES)}
+Our package coauthors are Juliette Bruce and Daniel Smolkin.  Erin Bela, Zhibek Kadyrsizova, Moty Katzman, Sara Malec, and Marcus Robinson also contributed valuable code to the package.
 
@@
 \item Add more cases to {\tt UseSpecialAlgorithms}.
+\item Add the capability to compute non-local {\tt fpt} and non-local {\tt nu} via an option.
 \item Write a function that will extract from this sequences $\{ \nu_f^{\idealm}(p^e) \}_{e=1}^{\infty}$ roots of Bernstein-Sato polynomials.  Especially, strata.

### 2019-06-07 Fsing/FThresholdsPaper/FThresholds.tex
Reorganization of fpt section of paper

@@
 
-We now describe the options available for the function {\tt nu}, and we focus primarily on the case where the second input is an ideal $I$, since the options work analogously when the second input is instead a polynomial $f$.
+\subsection*{Options for the {\tt nu} function}
+
+We now describe the options available for the function {\tt nu}.
+We focus primarily on the case where the second input is an ideal $I$, since the options work analogously when the second input is instead a polynomial $f$.
 
@@
 
-If {\tt UseSpecialAlgorithms} is set to {\tt true} and $f$ does not fall into any of the three forementioned cases, then the function {\tt fpt} next checks whether the polynomial $f$ is a product of factors that are in simple normal crossing, in which case its $F$-pure threshold is easily computed.
+If {\tt UseSpecialAlgorithms} is set to {\tt true} and $f$ does not fall into any of the three forementioned cases, then the function {\tt fpt} next calls {\tt isSimpleNormalCrossing(f)} to check whether the polynomial $f$ is a product of factors that are in simple normal crossing.
+If this command returns {\tt true}, the $F$-pure threshold can easily be computed, and {\tt fpt} returns this value.
+For more detail on the function {\tt isSimpleNormalCrossing} and on computing the $F$-pure threshold of a polynomial with simple normal crossings, please see the end of this section.
+
+In the remainder of this section, we describe the {\tt fpt} function when no special algorithm is available, or {\tt UseSpecialAlgorithms} is set to {\tt false},  as well as the roles of the options {\tt DepthOfSearch}, and {\tt Attempts}, both nonnegative integers.
+
+In this case, very roughly speaking, the {\tt fpt} function will either compute, and output, the exact value of the $F$-pure threshold of $f$, and otherwise recursively compute a finite sequence of lower and upper bounds for this value, and output the last of these, which will be the tightest among all computed.
+The value of the option {\tt DepthOfSearch} determines the precision of the initial set of bounds, and the option {\tt Attempts}, in conjunction with some various subroutines, determines whether, and how, to produce new, tighter bounds from the previous ones.
+
+In more detail, let $e$ denote the value of the option {\tt DepthOfSearch}, which conservatively defaults to {\tt 1}.
+The {\tt fpt} function first computes $\nu=\nu_f(p^e)$, which agrees with the output of {\tt nu(e,f)}.
+It is well known that the $F$-pure threshold of $f$ is greater than $\nu/p^e$ and at most $(\nu+1)/p^e$, and applying  \cite[Proposition 4.2]{HernandezFPurityOfHypersurfaces} to this lower bound tells us that the $F$-pure threshold of $f$ must be at least $\nu/(p^e-1)$.
+In summary, we know that the $F$-pure threshold of $f$ must lie in the closed interval
+%
+\begin{equation}
+\label{estimating-interval: e}
+\tag{$\dagger$}
+\left[ \frac{\nu}{p^e-1}, \frac{\nu+1}{p^e} \right].
+\end{equation}
+
+With these estimates in hand, the subroutine {\tt guessFPT} is called to make some ``educated guesses" in an attempt to identify the $F$-pure threshold within this interval, or at least narrow down this interval to produce improved estimates.
+The number of ``guesses" is controlled by the option {\tt Attempts}, which conservatively defaults to {\tt 3}.
+If {\tt Attempts} is set to {\tt 0}, then {\tt guessFPT} is bypassed.
+If  {\tt Attempts} is set to at least {\tt 1}, then a first check is run to verify whether the right-hand endpoint $(\nu+1)/p^e$ of the above interval \eqref{estimating-interval: e} is the $F$-pure threshold.
+We illustrate this below.
+
+{\small
+\setstretch{.67}
+\begin{MyVerbatim}
+
+i11 : f = x^2*(x + y)^3*(x + 3*y^2)^5;
+
+i12 : fpt(f, Attempts => 0) -- a bad estimate
+
+          1
+o12 = {0, -}
+          5
+
+o12 : List
+
+i13 : fpt(f, Attempts => 0, DepthOfSearch => 3) -- a better estimate
+
+        21   22
+o13 = {---, ---}
+       124  125
+
+o13 : List
+
+i14 : fpt(f, Attempts => 1, DepthOfSearch => 3) -- the right-hand
+
+      endpoint (nu+1)/p^e is the F-pure threshold
+
+       22
+o14 = ---
+      125
+
+o14 : QQ
+
+\end{MyVerbatim}
+}
+
+If  {\tt Attempts} is set to at least {\tt 2} and the right-hand endpoint $(\nu+1)/p^e$ of the interval \eqref{estimating-interval: e} is not the $F$-pure threshold, then a second check is run to verify whether the left-hand endpoint $\nu/(p^e-1)$ of this interval is the $F$-pure threshold.
+
+{\small
+\setstretch{.67}
+\begin{MyVerbatim}
+
+i15 : f = x^6*y^4 + x^4*y^9 + (x^2 + y^3)^3;
+
+i16 : fpt(f, Attempts => 1, DepthOfSearch => 3)
+
+       17   7
+o16 = {--, --}
+       62  25
+
+o16 : List
+
+i17 : fpt(f, Attempts => 2, DepthOfSearch => 3) -- the left-hand endpoint
+
+      nu/(p^e-1) is the F-pure threshold
+
+      17
+o17 = --
+      62
+
+o17 : QQ
+
+\end{MyVerbatim}
+}
+
+If neither endpoint is the $F$-pure threshold and {\tt Attempts} is set to more than {\tt 2}, then  additional checks are performed at certain numbers within the interval, chosen according to the criteria determined by the value of the option {\tt GuessStrategy}.
+We refer the reader for the documentation of this strategy for more details.
+
+{\color{red}  This will need to be updated.  Maybe look at Pedro's new documentation.}
+
+{\small
+\setstretch{.67}
+\begin{MyVerbatim}
+
+i18 : f = x^3*y^11*(x + y)^8*(x^2 + y^3)^8;
+
+i19 : fpt(f, DepthOfSearch => 3, Attempts => 2)
+
+        3   7
+o19 = {--, ---}
+       62  125
+
+o19 : List
+
+i20 : fpt(f, DepthOfSearch => 3, Attempts => 3) -- an additional check
+
+      sharpens the estimate
+
+        3   1
+o20 = {--, --}
+       62  18
+
+o20 : List
+
+i21 : fpt(f, DepthOfSearch => 3, Attempts => 4) -- and one more finds
+
+      the answer
+
+       1
+o21 = --
+      19
+
+o21 : QQ
+\end{MyVerbatim}
+}
+\medspace
+
+If {\tt guessFPT} is unsuccessful and {\tt UseFSignature} is set to {\tt true}, then the {\tt fpt} function proceeds to use the convexity of the $F$-signature function and a secant line argument to attempt to narrow down the interval bounding the $F$-pure threshold.
+
+{\small
+\setstretch{.67}
+\begin{MyVerbatim}
+
+i22 : f = x^5*y^6*(x + y)^9*(x^2 + y^3)^4;
+
+i23 : fpt(f, DepthOfSearch => 3)
+
+        2   1
+o23 = {--, --}
+       31  14
+
+o23 : List
+
+i24 : fpt(f, DepthOfSearch => 3, UseFSignature => true)
+
+        181   1
+o24 = {----, --}
+       2750  14
+
+o24 : List
+
+i25 : numeric o23
+
+o25 = {.0645161, .0714286}
+
+o25 : List
+
+i26 : numeric o24 -- UseFSignature sharpened the estimate a bit
+
+o26 = {.0658182, .0714286}
+
+o26 : List
+\end{MyVerbatim}
+}
+\medspace
+
+When {\tt FRegularityCheck} is set to {\tt true} and no exact answer has been found, a final check is run to verify whether the final lower bound for the $F$-pure threshold is the exact answer (if it has not already been eliminated as a possibility).
+
+{\small
+\setstretch{.67}
+\begin{MyVerbatim}
+
+i27 : f = (x + y)^4*(x^2 + y^3)^6;
+
+i28 : fpt( f, Attempts => 2, DepthOfSearch => 3 )
+
+        3   13
+o28 = {--, ---}
+       31  125
+
+o28 : List
+
+i29 : fpt(f, Attempts => 2, DepthOfSearch => 3, UseFSignature => true)
+
+      -- UseFSignature improves the answer a bit
+
+        1   13
+o29 = {--, ---}
+       10  125
+
+o29 : List
+
+i30 : fpt(f, Attempts => 2, DepthOfSearch => 3, UseFSignature => true,
+
+      FRegularityCheck => true) -- FRegularityCheck finds the answer
+
+       1
+o30 = --
+      10
+
+o30 : QQ
+\end{MyVerbatim}
+}
+\medspace
+
+The computations performed when {\tt UseFSignature} and {\tt FRegularityCheck} are set to {\tt true} are often slow, and often fail to improve the estimate, and for this reason, these options should be used sparingly.
+            It is often more effective to increase the values of {\tt Attempts} or {\tt DepthOfSearch} instead.
+
+{\small
+\setstretch{.67}
+\begin{MyVerbatim}
+
+i31 : f = x^7*y^5*(x + y)^5*(x^2 + y^3)^4;
+
+i32 : timing numeric fpt(f, DepthOfSearch => 3, UseFSignature => true,
+
+      FRegularityCheck => true)
+
+o32 = {.0733061, .0769231}
+      -- 2.68899 seconds
+
+o32 : Time
+
+i33 : timing numeric fpt(f, Attempts => 5, DepthOfSearch => 3) -- a better
+
+      answer in less time
+
+o33 = {.075, .0769231}
+      -- .893389 seconds
+
+o33 : Time
+
+i34 : timing fpt(f, DepthOfSearch => 4) -- the exact answer in even less
+      time
+
+       48
+o34 = ---
+      625
+      -- .361882 seconds
+
+o34 : Time
+\end{MyVerbatim}
+}
+\medspace
+
+As seen in several examples above, when the exact  $F$-pure threshold of $f$ is not found, a list containing the endpoints of an interval containing its value is returned.
+Whether that interval is open, closed, or a mixed interval depends on the options passed; if the option {\tt Verbose} is set to {\tt true}, the precise interval will be printed.
+
+{\small
+\setstretch{.67}
+\begin{MyVerbatim}
+
+i35 : f = x^7*y^5*(x + y)^5*(x^2 + y^3)^4;
+
+i36 : fpt(f, DepthOfSearch => 3, UseFSignature => true, Verbose => true)
+
+Starting fpt ...
+
+fpt is not 1 ...
+
+Verifying if special algorithms apply...
+
+Special fpt algorithms were not used ...
+
+nu has been computed: nu = nu(3,f) = 9 ...
+
+fpt lies in the interval [ nu/(p^e-1), (nu+1)/p^e ] = [ 9/124, 2/25 ] ...
+
+Starting guessFPT ...
+
+The right-hand endpoint is not the fpt ...
+
+The left-hand endpoint is not the fpt ...
+
+guessFPT narrowed the interval down to ( 9/124, 1/13 ) ...
+
+Beginning F-signature computation ...
+
+First F-signature computed: s(f,(nu-1)/p^e) = 456/15625 ...
+
+Second F-signature computed: s(f,nu/p^e) = 64/15625 ...
+
+Computed F-signature secant line intercept: 449/6125 ...
+
+F-signature intercept is an improved lower bound ...
+
+fpt failed to find the exact answer; try increasing the value of
+
+DepthOfSearch or Attempts.
+
+fpt lies in the interval [ 449/6125, 1/13 ).
+
+        449   1
+o36 = {----, --}
+       6125  13
+
+o36 : List
+\end{MyVerbatim}
+}
+\medspace
+
+\subsection*{The function {\tt isSimpleNormalCrossings}}
 
@@
 
-In the remainder of this section, we describe the {\tt fpt} function when no special algorithm is available, or {\tt UseSpecialAlgorithms} is set to {\tt false},  as well as the roles of the options {\tt DepthOfSearch}, and {\tt Attempts}, both nonnegative integers.
-
-In this case, very roughly speaking, the {\tt fpt} function will either compute, and output, the exact value of the $F$-pure threshold of $f$, and otherwise recursively compute a finite sequence of lower and upper bounds for this value, and output the last of these, which will be the tightest among all computed.
-The value of the option {\tt DepthOfSearch} determines the precision of the initial set of bounds, and the option {\tt Attempts}, in conjunction with some various subroutines, determines whether, and how, to produce new, tighter bounds from the previous ones.
-
-In more detail, let $e$ denote the value of the option {\tt DepthOfSearch}, which conservatively defaults to {\tt 1}.
-The {\tt fpt} function first computes $\nu=\nu_f(p^e)$, which agrees with the output of {\tt nu(e,f)}.
-It is well known that the $F$-pure threshold of $f$ is greater than $\nu/p^e$ and at most $(\nu+1)/p^e$, and applying  \cite[Proposition 4.2]{HernandezFPurityOfHypersurfaces} to this lower bound tells us that the $F$-pure threshold of $f$ must be at least $\nu/(p^e-1)$.
-In summary, we know that the $F$-pure threshold of $f$ must lie in the closed interval
-%
-\begin{equation}
-\label{estimating-interval: e}
-\tag{$\dagger$}
-\left[ \frac{\nu}{p^e-1}, \frac{\nu+1}{p^e} \right].
-\end{equation}
-
-With these estimates in hand, the subroutine {\tt guessFPT} is called to make some ``educated guesses" in an attempt to identify the $F$-pure threshold within this interval, or at least narrow down this interval to produce improved estimates.
-The number of ``guesses" is controlled by the option {\tt Attempts}, which conservatively defaults to {\tt 3}.
-If {\tt Attempts} is set to {\tt 0}, then {\tt guessFPT} is bypassed.
-If  {\tt Attempts} is set to at least {\tt 1}, then a first check is run to verify whether the right-hand endpoint $(\nu+1)/p^e$ of the above interval \eqref{estimating-interval: e} is the $F$-pure threshold.
-We illustrate this below.
-
-{\small
-\setstretch{.67}
-\begin{MyVerbatim}
-
-i11 : f = x^2*(x + y)^3*(x + 3*y^2)^5;
-
-i12 : fpt(f, Attempts => 0) -- a bad estimate
-
-          1
-o12 = {0, -}
-          5
-
-o12 : List
-
-i13 : fpt(f, Attempts => 0, DepthOfSearch => 3) -- a better estimate
-
-        21   22
-o13 = {---, ---}
-       124  125
-
-o13 : List
-
-i14 : fpt(f, Attempts => 1, DepthOfSearch => 3) -- the right-hand
-
-      endpoint (nu+1)/p^e is the F-pure threshold
-
-       22
-o14 = ---
-      125
-
-o14 : QQ
-
-\end{MyVerbatim}
-}
-
-If  {\tt Attempts} is set to at least {\tt 2} and the right-hand endpoint $(\nu+1)/p^e$ of the interval \eqref{estimating-interval: e} is not the $F$-pure threshold, then a second check is run to verify whether the left-hand endpoint $\nu/(p^e-1)$ of this interval is the $F$-pure threshold.
-
-{\small
-\setstretch{.67}
-\begin{MyVerbatim}
-
-i15 : f = x^6*y^4 + x^4*y^9 + (x^2 + y^3)^3;
-
-i16 : fpt(f, Attempts => 1, DepthOfSearch => 3)
-
-       17   7
-o16 = {--, --}
-       62  25
-
-o16 : List
-
-i17 : fpt(f, Attempts => 2, DepthOfSearch => 3) -- the left-hand endpoint
-
-      nu/(p^e-1) is the F-pure threshold
-
-      17
-o17 = --
-      62
-
-o17 : QQ
-
-\end{MyVerbatim}
-}
-
-If neither endpoint is the $F$-pure threshold and {\tt Attempts} is set to more than {\tt 2}, then  additional checks are performed at certain numbers within the interval, chosen according to the criteria determined by the value of the option {\tt GuessStrategy}.
-We refer the reader for the documentation of this strategy for more details.
-
-{\color{red}  This will need to be updated.  Maybe look at Pedro's new documentation.}
-
-{\small
-\setstretch{.67}
-\begin{MyVerbatim}
-
-i18 : f = x^3*y^11*(x + y)^8*(x^2 + y^3)^8;
-
-i19 : fpt(f, DepthOfSearch => 3, Attempts => 2)
-
-        3   7
-o19 = {--, ---}
-       62  125
-
-o19 : List
-
-i20 : fpt(f, DepthOfSearch => 3, Attempts => 3) -- an additional check
-
-      sharpens the estimate
-
-        3   1
-o20 = {--, --}
-       62  18
-
-o20 : List
-
-i21 : fpt(f, DepthOfSearch => 3, Attempts => 4) -- and one more finds
-
-      the answer
-
-       1
-o21 = --
-      19
-
-o21 : QQ
-\end{MyVerbatim}
-}
-\medspace
-
-If {\tt guessFPT} is unsuccessful and {\tt UseFSignature} is set to {\tt true}, then the {\tt fpt} function proceeds to use the convexity of the $F$-signature function and a secant line argument to attempt to narrow down the interval bounding the $F$-pure threshold.
-
-{\small
-\setstretch{.67}
-\begin{MyVerbatim}
-
-i22 : f = x^5*y^6*(x + y)^9*(x^2 + y^3)^4;
-
-i23 : fpt(f, DepthOfSearch => 3)
-
-        2   1
-o23 = {--, --}
-       31  14
-
-o23 : List
-
-i24 : fpt(f, DepthOfSearch => 3, UseFSignature => true)
-
-        181   1
-o24 = {----, --}
-       2750  14
-
-o24 : List
-
-i25 : numeric o23
-
-o25 = {.0645161, .0714286}
-
-o25 : List
-
-i26 : numeric o24 -- UseFSignature sharpened the estimate a bit
-
-o26 = {.0658182, .0714286}
-
-o26 : List
-\end{MyVerbatim}
-}
-\medspace
-
-When {\tt FRegularityCheck} is set to {\tt true} and no exact answer has been found, a final check is run to verify whether the final lower bound for the $F$-pure threshold is the exact answer (if it has not already been eliminated as a possibility).
-
-{\small
-\setstretch{.67}
-\begin{MyVerbatim}
-
-i27 : f = (x + y)^4*(x^2 + y^3)^6;
-
-i28 : fpt( f, Attempts => 2, DepthOfSearch => 3 )
-
-        3   13
-o28 = {--, ---}
-       31  125
-
-o28 : List
-
-i29 : fpt(f, Attempts => 2, DepthOfSearch => 3, UseFSignature => true)
-
-      -- UseFSignature improves the answer a bit
-
-        1   13
-o29 = {--, ---}
-       10  125
-
-o29 : List
-
-i30 : fpt(f, Attempts => 2, DepthOfSearch => 3, UseFSignature => true,
-
-      FRegularityCheck => true) -- FRegularityCheck finds the answer
-
-       1
-o30 = --
-      10
-
-o30 : QQ
-\end{MyVerbatim}
-}
-\medspace
-
-The computations performed when {\tt UseFSignature} and {\tt FRegularityCheck} are set to {\tt true} are often slow, and often fail to improve the estimate, and for this reason, these options should be used sparingly.
-            It is often more effective to increase the values of {\tt Attempts} or {\tt DepthOfSearch} instead.
-
-{\small
-\setstretch{.67}
-\begin{MyVerbatim}
-
-i31 : f = x^7*y^5*(x + y)^5*(x^2 + y^3)^4;
-
-i32 : timing numeric fpt(f, DepthOfSearch => 3, UseFSignature => true,
-
-      FRegularityCheck => true)
-
-o32 = {.0733061, .0769231}
-      -- 2.68899 seconds
-
-o32 : Time
-
-i33 : timing numeric fpt(f, Attempts => 5, DepthOfSearch => 3) -- a better
-
-      answer in less time
-
-o33 = {.075, .0769231}
-      -- .893389 seconds
-
-o33 : Time
-
-i34 : timing fpt(f, DepthOfSearch => 4) -- the exact answer in even less
-      time
-
-       48
-o34 = ---
-      625
-      -- .361882 seconds
-
-o34 : Time
-\end{MyVerbatim}
-}
-\medspace
-
-As seen in several examples above, when the exact  $F$-pure threshold of $f$ is not found, a list containing the endpoints of an interval containing its value is returned.
-Whether that interval is open, closed, or a mixed interval depends on the options passed; if the option {\tt Verbose} is set to {\tt true}, the precise interval will be printed.
-
-{\small
-\setstretch{.67}
-\begin{MyVerbatim}
-
-i35 : f = x^7*y^5*(x + y)^5*(x^2 + y^3)^4;
-
-i36 : fpt(f, DepthOfSearch => 3, UseFSignature => true, Verbose => true)
-
-Starting fpt ...
-
-fpt is not 1 ...
-
-Verifying if special algorithms apply...
-
-Special fpt algorithms were not used ...
-
-nu has been computed: nu = nu(3,f) = 9 ...
-
-fpt lies in the interval [ nu/(p^e-1), (nu+1)/p^e ] = [ 9/124, 2/25 ] ...
-
-Starting guessFPT ...
-
-The right-hand endpoint is not the fpt ...
-
-The left-hand endpoint is not the fpt ...
-
-guessFPT narrowed the interval down to ( 9/124, 1/13 ) ...
-
-Beginning F-signature computation ...
-
-First F-signature computed: s(f,(nu-1)/p^e) = 456/15625 ...
-
-Second F-signature computed: s(f,nu/p^e) = 64/15625 ...
-
-Computed F-signature secant line intercept: 449/6125 ...
-
-F-signature intercept is an improved lower bound ...
-
-fpt failed to find the exact answer; try increasing the value of
-
-DepthOfSearch or Attempts.
-
-fpt lies in the interval [ 449/6125, 1/13 ).
-
-        449   1
-o36 = {----, --}
-       6125  13
-
-o36 : List
-\end{MyVerbatim}
-}
-\medspace
-
 \newpage

### 2019-06-07 Fsing/FThresholdsPaper/FThresholds.tex
Updates to SNC subsection of paper

@@
 \subsection*{The function {\tt isSimpleNormalCrossings}}
-
-We briefly describe the algorithm that checks whether the polynomial $f$ factors as a product of functions $f = \prod_i f_i^{a_i}$ that are in simple normal crossing with each other, in which case, the $F$-pure threshold is just the minimum of the $1/a_i$.
-Recall that a set of elements $\{f_i\}$ is said to be in simple normal crossing at a point, if locally, the $f_i$ form part of a regular system of parameters.
-The functionality verifies this by computing the Jacobian matrix of each subset of the $f_i$ (evaluated at the origin), and checking that these matrices have the expected rank.
-It is also verified that these subsets generate ideals of the correct height.
-Note that {\tt factor f} is called, which may be slow.
-The user can avoid this factorization call by setting {\tt UseSpecialAlgorithms} to {\tt false}.
-
-This method for determining whether $f$ is a product of factors that are in simple normal crossing is implemented in the function {\tt isSimpleNormalCrossing}, which is also exposed to the user.
-Note that if one sets the option {\tt IsLocal} for this function to {\tt true}, then {\tt isSimpleNormalCrossing} checks that the $f_i$ are in simple normal crossing \emph{everywhere}, which can be much slower (as Jacobian ideals are computed).
+As mentioned earlier, 
+when the option {\tt useSpecialFunctions} for the function {\tt fpt} is set to {\tt true}, if the polynomial $f$ is neither a diagonal polynomial, a binomial, or a form in two variables, there is a final check to verify whether $f$ is a product of factors in simple normal crossing.
+
+Suppose that $f$ has factorization $f_1^{a_i} f_2^{a_2} \cdots f_n^{a_n}$.  Recall that its factors $f_i$ are said to be in 
+\emph{simple normal crossing} at a point if, locally, they form part of a regular system of parameters.
+The function {\tt isSimpleNormalCrossings} determines whether $f$ has simple normal crossings by computing the Jacobian matrix of each subset of $\{ f_i \}_{i=1}^n$ (evaluated at the origin), and checking that these matrices have the expected rank, and that these subsets generate ideals of the appropriate height.
+
+{\small
+\setstretch{.67}
+\begin{MyVerbatim}
+
+i1 : R = ZZ/7[x, y, z];
+
+i2 : isSimpleNormalCrossing(x^3*y^2)
+
+o2 = true
+
+i3 : isSimpleNormalCrossing(x^2-y^2)
+
+o3 = true
+
+i4 : isSimpleNormalCrossing(x*y*(x-y))
+
+o4 = false
+
+i5 : isSimpleNormalCrossing(x^2-y*z)
+
+o5 = false
+\end{MyVerbatim}
+}
+\medspace
+
+%             R = ZZ/7[x,y,z];
+%             isSimpleNormalCrossing(x^3*y^2)
+%             isSimpleNormalCrossing(x^2-y^2)
+%             isSimpleNormalCrossing(x*y*(x-y))
+%             isSimpleNormalCrossing(x^2-y*z)
+
+If {\tt isSimpleNormalCrossing(f)} outputs true, then the $F$-pure threshold is easily computed, since is just the minimum of the values $1/a_i$, for $1 \leq i \leq n$.
+Note that the function {\tt factor} is called whenever {\tt isSimpleNormalCrossing} is used, which can sometimes make the verification slow.
+The user can avoid this when using {\tt fpt} by setting {\tt UseSpecialAlgorithms} to {\tt false}.
+
+The function {\tt isSimpleNormalCrossing} is exposed to the user, so can be used independent of any $F$-pure threshold calculation.  
+If the user sets its option {\tt IsLocal} to {\tt true} (its default value is {\tt false}), then the function checks whether the $f_i$ are in simple normal crossing \emph{everywhere}, which can be much slower since Jacobian ideals are computed.
+Consider the following example illustrating this functionality.
+
+{\small
+\setstretch{.67}
+\begin{MyVerbatim}
+
+i1 : R = QQ[x, y, z];
+
+i2 : f = (y - (x-1)^2)*y^2; --SNC at the origin, but not globally
+
+i3 : isSimpleNormalCrossing(f)
+
+o3 = true
+
+i4 : isSimpleNormalCrossing(f, IsLocal=>false)
+
+o4 = false
+
+i5 : g = (y-1)^2+(x-7)^2 --doesn't even pass through the origin
+
+       2    2
+o5 = x  + y  - 14x - 2y + 50
+
+o5 : R
+
+i6 : isSimpleNormalCrossing(g)
+
+o6 = true
+
+i7 : isSimpleNormalCrossing(g, IsLocal=>false)
+
+o7 = false
+
+i8 : h = x*y^2*(x+1)^3*(y-1)^4; --SNC everywhere
+
+i9 : isSimpleNormalCrossing(h)
+
+o9 = true
+
+i10 : isSimpleNormalCrossing(h, IsLocal=>false)
+
+o10 = true
+\end{MyVerbatim}
+}
+\medspace
+
+%             R = QQ[x,y,z];
+
+%             f = (y - (x-1)^2)*y^2; --SNC at the origin, but not globally
+
+%             isSimpleNormalCrossing(f)
+
+%             isSimpleNormalCrossing(f, IsLocal=>false)
+
+%             g = (y-1)^2+(x-7)^2 --doesn't even pass through the origin
+
+%             isSimpleNormalCrossing(g)
+
+%             isSimpleNormalCrossing(g, IsLocal=>false)
+
+%             h = x*y^2*(x+1)^3*(y-1)^4; --SNC everywhere
+
+%             isSimpleNormalCrossing(h)
+
+%             isSimpleNormalCrossing(h, IsLocal=>false)
 

### 2019-06-07 Fsing/FThresholdsPaper/FThresholds.tex
Minor addition to SpecialFThresholds documentation
Minor changes

@@
  test candidate values for an $F$-pure threshold, and even $F$-jumping numbers, even in some singular rings.
+
 Consider a  $\mathbb{Q}$-Gorenstein ring $R$ of characteristic $p>0$, whose index not divisible by $p$.
-Given a rational number $t$ and an element $f$ of $R$, the command {\tt isFPT(t,f)} outputs {\tt true} if $t$ is the $F$-pure threshold of $f$, and {\tt false} otherwise.
+Given a parameter $t \in \mathbb{Q}$ and an element $f$ of $R$, the command {\tt isFPT(t,f)} outputs {\tt true} if $t$ is the $F$-pure threshold of $f$, and {\tt false} otherwise.
 Moreover, the function {\tt compareFPT} provides further information about the relationship between $t$ and the $F$-pure threshold of $f$; namely,
-{\tt compareFPT(t, f)} returns {\tt-1} when $t < \fpt(f)$, {\tt 0} when $t = \fpt(f)$ and {\tt 1} when $t > \fpt(f)$.
+{\tt compareFPT(t, f)} returns {\tt-1} , {\tt 0}, {\tt 1} when $t$ is less than, equal to, or greater than, respectively, the $F$-pure threshold of $f$.
 Setting the option {\tt IsLocal} to {\tt true} tells the function to consider the $F$-pure threshold at the origin.
@@
 
-The core function in this package is the {\tt fpt} function.
+The core function in the package \emph{FrobeniusThresholds} is called {\tt fpt}.
 Throughout this section, let $f$ be a polynomial with coefficients in a finite field of characteristic $p$.
@@
 
-If the option {\tt UseSpecialAlgorithms} is set to {\tt true} (the default value), then {\tt fpt} first checks whether $f$ is a monomial, a diagonal polynomial, a binomial, a form in two variables, or a product of factors in simple normal crossing, in that order.
-The monomials and the simple normal crossing cases are computed as the reciprocal of maximal exponent of the factors.
-Outside of that simple case, algorithms of Hern\'andez \cite{HernandezFInvariantsOfDiagonalHyp, HernandezFPureThresholdOfBinomial}, or Hern\'andez and Teixeira \cite{HernandezTeixeiraFThresholdFunctions},  are executed to compute the $F$-pure threshold (cf.
-\cite{ShibutaTakagiLCThresholds}).
-
-{\small
-\setstretch{.67}
-\begin{MyVerbatim}
-
-i4 : fpt(x^17 + y^20 + z^24) -- a diagonal polynomial
+\subsection*{The option {\tt UseSpecialAlgorithms} for the {\tt fpt} function}
+
+The {\tt fpt} function has the option {\tt UseSpecialAlgorithms}.  When
+set to {\tt true} (the default value), {\tt fpt} first checks whether $f$ is a monomial, a diagonal polynomial, a binomial, a form in two variables, or a product of factors in simple normal crossing, in that order.
+
+If $f = x_1^{a_n}\cdots x_n^{a_n}$, then its $F$-pure threshold is simply $\min \{ 1/a_1, \ldots, 1/a_n \}$.  When $f$ is a diagonal polynomial, a binomial, or a form in two variables, 
+algorithms of Hern\'andez \cite{HernandezFInvariantsOfDiagonalHyp, HernandezFPureThresholdOfBinomial}, or Hern\'andez and Teixeira \cite{HernandezTeixeiraFThresholdFunctions},  are executed to compute the $F$-pure threshold.
+We note that algorithms for computing $F$-pure thresholds of binomials in certain special characteristics appear in \cite{ShibutaTakagiLCThresholds}.
+
+{\small
+\setstretch{.67}
+\begin{MyVerbatim}
+
+i4 : fpt(x^3*y^4*z^5) -- a monomial
+
+      1
+o4 = -
+      5
+
+o4 : QQ
+
+i5 : fpt(x^17 + y^20 + z^24) -- a diagonal polynomial
 
       94
-o4 = ---
+o5 = ---
      625
 
-i5 : fpt(x^2*y^6*z^10 + x^10*y^5*z^3) -- a binomial
+i6 : fpt(x^2*y^6*z^10 + x^10*y^5*z^3) -- a binomial
 
       997
-o5 = ----
+o6 = ----
      6250
 
-o5 : QQ
-
-i6 : ZZ/5[x,y];
-
-i7 : fpt(x^2*y^6*(x + y)^9*(x + 3*y)^10) -- a form in two variables
+o6 : QQ
+
+i7 : ZZ/5[x,y];
+
+i8 : fpt(x^2*y^6*(x + y)^9*(x + 3*y)^10) -- a form in two variables
 
       5787
-o7 = -----
+o8 = -----
      78125
 
-o7 : QQ
+o8 : QQ
 \end{MyVerbatim}
@@
 
-i8 : L = {x, y, x + y, x + 3*y};
-
-i9 : m = {2, 6, 9, 10};
-
-i10 : fpt(L, m) == o7
-
-o10 = true
-\end{MyVerbatim}
-}
-\medspace
-
-If {\tt UseSpecialAlgorithms} is set to {\tt true} and $f$ does not fall into any of the three forementioned cases, then the function {\tt fpt} next calls {\tt isSimpleNormalCrossing(f)} to check whether the polynomial $f$ is a product of factors that are in simple normal crossing.
+i9 : L = {x, y, x + y, x + 3*y};
+
+i10 : m = {2, 6, 9, 10};
+
+i11 : fpt(L, m) == o7
+
+o11 = true
+\end{MyVerbatim}
+}
+\medspace
+
+If {\tt UseSpecialAlgorithms} is set to {\tt true} and $f$ does not fall into any of the four forementioned cases, then the function {\tt fpt} next calls {\tt isSimpleNormalCrossing(f)} to check whether the polynomial $f$ is a product of factors that are in simple normal crossing.
 If this command returns {\tt true}, the $F$-pure threshold can easily be computed, and {\tt fpt} returns this value.
 For more detail on the function {\tt isSimpleNormalCrossing} and on computing the $F$-pure threshold of a polynomial with simple normal crossings, please see the end of this section.
+
+\subsection*{Searching for the $F$-pure threshold when no special algorithm applies}
 

### 2019-06-07 Fsing/FThresholdsPaper/FThresholds.tex
Updates to paper, and to fpt documentation

@@
  test candidate values for an $F$-pure threshold, and even $F$-jumping numbers, even in some singular rings.
-
 Consider a  $\mathbb{Q}$-Gorenstein ring $R$ of characteristic $p>0$, whose index not divisible by $p$.
-Given a parameter $t \in \mathbb{Q}$ and an element $f$ of $R$, the command {\tt isFPT(t,f)} outputs {\tt true} if $t$ is the $F$-pure threshold of $f$, and {\tt false} otherwise.
+Given a rational number $t$ and an element $f$ of $R$, the command {\tt isFPT(t,f)} outputs {\tt true} if $t$ is the $F$-pure threshold of $f$, and {\tt false} otherwise.
 Moreover, the function {\tt compareFPT} provides further information about the relationship between $t$ and the $F$-pure threshold of $f$; namely,
-{\tt compareFPT(t, f)} returns {\tt-1} , {\tt 0}, {\tt 1} when $t$ is less than, equal to, or greater than, respectively, the $F$-pure threshold of $f$.
+{\tt compareFPT(t, f)} returns {\tt-1} when $t < \fpt(f)$, {\tt 0} when $t = \fpt(f)$ and {\tt 1} when $t > \fpt(f)$.
 Setting the option {\tt IsLocal} to {\tt true} tells the function to consider the $F$-pure threshold at the origin.
@@
 set to {\tt true} (the default value), {\tt fpt} first checks whether $f$ is a monomial, a diagonal polynomial, a binomial, a form in two variables, or a product of factors in simple normal crossing, in that order.
-
-If $f = x_1^{a_n}\cdots x_n^{a_n}$, then its $F$-pure threshold is simply $\min \{ 1/a_1, \ldots, 1/a_n \}$.  When $f$ is a diagonal polynomial, a binomial, or a form in two variables, 
-algorithms of Hern\'andez \cite{HernandezFInvariantsOfDiagonalHyp, HernandezFPureThresholdOfBinomial}, or Hern\'andez and Teixeira \cite{HernandezTeixeiraFThresholdFunctions},  are executed to compute the $F$-pure threshold.
-We note that algorithms for computing $F$-pure thresholds of binomials in certain special characteristics appear in \cite{ShibutaTakagiLCThresholds}.
+When $f$ is a monomial, say, $x_1^{a_n}\cdots x_n^{a_n}$, then its $F$-pure threshold is quickly computed as the minimum among the $1/a_i$.
+When $f$ is a a diagonal polynomial, a binomial, a form in two variables, 
+algorithms of Hern\'andez \cite{HernandezFInvariantsOfDiagonalHyp, HernandezFPureThresholdOfBinomial}, or Hern\'andez and Teixeira \cite{HernandezTeixeiraFThresholdFunctions},  are executed to compute the $F$-pure threshold (cf.
+\cite{ShibutaTakagiLCThresholds}).
+Consider examples of each of these cases below.
 
@@
 
-\subsection*{Searching for the $F$-pure threshold when no special algorithm applies}
+\subsection*{How {\tt fpt} proceeds when no special algorithm applies}
 
@@
 i14 : fpt(f, Attempts => 1, DepthOfSearch => 3) -- the right-hand
-
       endpoint (nu+1)/p^e is the F-pure threshold
@@
 i17 : fpt(f, Attempts => 2, DepthOfSearch => 3) -- the left-hand endpoint
-
       nu/(p^e-1) is the F-pure threshold
@@
 
-If neither endpoint is the $F$-pure threshold and {\tt Attempts} is set to more than {\tt 2}, then  additional checks are performed at certain numbers within the interval, chosen according to the criteria determined by the value of the option {\tt GuessStrategy}.
-We refer the reader for the documentation of this strategy for more details.
+If neither endpoint is the $F$-pure threshold and {\tt Attempts} is set to more than {\tt 2}, then  additional checks are performed at certain numbers within the interval.
+A number in the interval is selected, according to criteria specified by the option \textcolor{red}{{\tt GuessStrategy}}, and the function {\tt compareFPT} is used to test that number.
+If this ``guess'' is correct, its value is returned.
+Otherwise, the information returned by {\tt  compareFPT} is used to narrow down the interval, and this process is repeated as many times as specified by the value of {\tt Attempts}.
 
@@
 
-i20 : fpt(f, DepthOfSearch => 3, Attempts => 3) -- an additional check
-
-      sharpens the estimate
-
-        3   1
+i20 : fpt(f, DepthOfSearch => 3, Attempts => 4) -- more attempts *always*
+      improve the estimate
+
+        1   4
 o20 = {--, --}
-       62  18
+       20  75
 
@@
 
-i21 : fpt(f, DepthOfSearch => 3, Attempts => 4) -- and one more finds
-
-      the answer
+i21 : fpt(f, DepthOfSearch => 3, Attempts => 4, GuessStrategy => denominator) 
+      -- the exact answer, after a change of strategy
 
@@
 
-If {\tt guessFPT} is unsuccessful and {\tt UseFSignature} is set to {\tt true}, then the {\tt fpt} function proceeds to use the convexity of the $F$-signature function and a secant line argument to attempt to narrow down the interval bounding the $F$-pure threshold.
-
-{\small
-\setstretch{.67}
-\begin{MyVerbatim}
-
-i22 : f = x^5*y^6*(x + y)^9*(x^2 + y^3)^4;
-
-i23 : fpt(f, DepthOfSearch => 3)
-
-        2   1
-o23 = {--, --}
-       31  14
-
-o23 : List
-
-i24 : fpt(f, DepthOfSearch => 3, UseFSignature => true)
-
-        181   1
-o24 = {----, --}
-       2750  14
-
-o24 : List
-
-i25 : numeric o23
-
-o25 = {.0645161, .0714286}
-
-o25 : List
-
-i26 : numeric o24 -- UseFSignature sharpened the estimate a bit
-
-o26 = {.0658182, .0714286}
-
-o26 : List
-\end{MyVerbatim}
-}
-\medspace
-
-When {\tt FRegularityCheck} is set to {\tt true} and no exact answer has been found, a final check is run to verify whether the final lower bound for the $F$-pure threshold is the exact answer (if it has not already been eliminated as a possibility).
-
-{\small
-\setstretch{.67}
-\begin{MyVerbatim}
-
-i27 : f = (x + y)^4*(x^2 + y^3)^6;
-
-i28 : fpt( f, Attempts => 2, DepthOfSearch => 3 )
-
-        3   13
-o28 = {--, ---}
-       31  125
-
-o28 : List
-
-i29 : fpt(f, Attempts => 2, DepthOfSearch => 3, UseFSignature => true)
-
-      -- UseFSignature improves the answer a bit
-
-        1   13
-o29 = {--, ---}
-       10  125
-
-o29 : List
-
-i30 : fpt(f, Attempts => 2, DepthOfSearch => 3, UseFSignature => true,
-
-      FRegularityCheck => true) -- FRegularityCheck finds the answer
-
-       1
-o30 = --
-      10
-
-o30 : QQ
-\end{MyVerbatim}
-}
-\medspace
-
-The computations performed when {\tt UseFSignature} and {\tt FRegularityCheck} are set to {\tt true} are often slow, and often fail to improve the estimate, and for this reason, these options should be used sparingly.
-            It is often more effective to increase the values of {\tt Attempts} or {\tt DepthOfSearch} instead.
-
-{\small
-\setstretch{.67}
-\begin{MyVerbatim}
-
-i31 : f = x^7*y^5*(x + y)^5*(x^2 + y^3)^4;
-
-i32 : timing numeric fpt(f, DepthOfSearch => 3, UseFSignature => true,
-
-      FRegularityCheck => true)
-
-o32 = {.0733061, .0769231}
-      -- 2.68899 seconds
-
-o32 : Time
-
-i33 : timing numeric fpt(f, Attempts => 5, DepthOfSearch => 3) -- a better
-
-      answer in less time
-
-o33 = {.075, .0769231}
-      -- .893389 seconds
-
-o33 : Time
-
-i34 : timing fpt(f, DepthOfSearch => 4) -- the exact answer in even less
-      time
+The option {\tt Bounds} allows the user to specify known lower and upper bounds for the $F$-pure threshold of $f$, in order to speed up computations or to refine previously obtained estimates.
+
+{\small
+\setstretch{.67}
+\begin{MyVerbatim}
+
+i67 : f = x^7*y^5*(x + y)^5*(x^2 + y^3)^4;
+
+i68 : fpt(f, DepthOfSearch => 3, Attempts => 5)
+
+        3   1
+o68 = {--, --}
+       40  13
+
+o68 : List
+
+i69 : fpt(f, DepthOfSearch => 3, Attempts => 5, Bounds => oo)
 
        48
-o34 = ---
+o69 = ---
       625
-      -- .361882 seconds
-
-o34 : Time
-\end{MyVerbatim}
-}
-\medspace
+
+o69 : QQ
+\end{MyVerbatim}
+}
+\medspace
+
+% f = x^7*y^5*(x + y)^5*(x^2 + y^3)^4;
+% fpt(f, DepthOfSearch => 3, Attempts => 5)
+% fpt(f, DepthOfSearch => 3, Attempts => 5, Bounds => oo)
+
+% If {\tt guessFPT} is unsuccessful and {\tt UseFSignature} is set to {\tt true}, then the {\tt fpt} function proceeds to use the convexity of the $F$-signature function and a secant line argument to attempt to narrow down the interval bounding the $F$-pure threshold.
+% 
+% {\small
+% \setstretch{.67}
+% \begin{MyVerbatim}
+% 
+% i22 : f = x^5*y^6*(x + y)^9*(x^2 + y^3)^4;
+% 
+% i23 : fpt(f, DepthOfSearch => 3)
+% 
+%         2   1
+% o23 = {--, --}
+%        31  14
+% 
+% o23 : List
+% 
+% i24 : fpt(f, DepthOfSearch => 3, UseFSignature => true)
+% 
+%         181   1
+% o24 = {----, --}
+%        2750  14
+% 
+% o24 : List
+% 
+% i25 : numeric o23
+% 
+% o25 = {.0645161, .0714286}
+% 
+% o25 : List
+% 
+% i26 : numeric o24 -- UseFSignature sharpened the estimate a bit
+% 
+% o26 = {.0658182, .0714286}
+% 
+% o26 : List
+% \end{MyVerbatim}
+% }
+% \medspace
+% 
+% When {\tt FRegularityCheck} is set to {\tt true} and no exact answer has been found, a final check is run to verify whether the final lower bound for the $F$-pure threshold is the exact answer (if it has not already been eliminated as a possibility).
+% 
+% {\small
+% \setstretch{.67}
+% \begin{MyVerbatim}
+% 
+% i27 : f = (x + y)^4*(x^2 + y^3)^6;
+% 
+% i28 : fpt( f, Attempts => 2, DepthOfSearch => 3 )
+% 
+%         3   13
+% o28 = {--, ---}
+%        31  125
+% 
+% o28 : List
+% 
+% i29 : fpt(f, Attempts => 2, DepthOfSearch => 3, UseFSignature => true)
+% 
+%       -- UseFSignature improves the answer a bit
+% 
+%         1   13
+% o29 = {--, ---}
+%        10  125
+% 
+% o29 : List
+% 
+% i30 : fpt(f, Attempts => 2, DepthOfSearch => 3, UseFSignature => true,
+% 
+%       FRegularityCheck => true) -- FRegularityCheck finds the answer
+% 
+%        1
+% o30 = --
+%       10
+% 
+% o30 : QQ
+% \end{MyVerbatim}
+% }
+% \medspace
+% 
+% The computations performed when {\tt UseFSignature} and {\tt FRegularityCheck} are set to {\tt true} are often slow, and often fail to improve the estimate, and for this reason, these options should be used sparingly.
+%             It is often more effective to increase the values of {\tt Attempts} or {\tt DepthOfSearch} instead.
+% 
+% {\small
+% \setstretch{.67}
+% \begin{MyVerbatim}
+% 
+% i31 : f = x^7*y^5*(x + y)^5*(x^2 + y^3)^4;
+% 
+% i32 : timing numeric fpt(f, DepthOfSearch => 3, UseFSignature => true,
+% 
+%       FRegularityCheck => true)
+% 
+% o32 = {.0733061, .0769231}
+%       -- 2.68899 seconds
+% 
+% o32 : Time
+% 
+% i33 : timing numeric fpt(f, Attempts => 5, DepthOfSearch => 3) -- a better
+% 
+%       answer in less time
+% 
+% o33 = {.075, .0769231}
+%       -- .893389 seconds
+% 
+% o33 : Time
+% 
+% i34 : timing fpt(f, DepthOfSearch => 4) -- the exact answer in even less
+%       time
+% 
+%        48
+% o34 = ---
+%       625
+%       -- .361882 seconds
+% 
+% o34 : Time
+% \end{MyVerbatim}
+% }
+% \medspace
+
+If {\tt guessFPT} is unsuccessful and {\tt FinalAttempt} is set to {\tt true}, the fpt function proceeds to use the convexity of the $F$-signature function and a secant line argument to attempt to narrow down the interval bounding the $F$-pure threshold.
+If successful, the new lower bound may coincide with the upper bound, in which case we can conclude that it is the desired $F$-pure threshold.
+If that is not the case, an $F$-regularity check is done at the new lower bound, to verify if it is the $F$-pure threshold.
 
@@
 
-i2 : f = (y - (x-1)^2)*y^2; --SNC at the origin, but not globally
+i2 : f = (y - (x-1)^2)*y^2; -- SNC at the origin, but not globally
 
@@
 
-i4 : isSimpleNormalCrossing(f, IsLocal=>false)
-
-o4 = false
-
-i5 : g = (y-1)^2+(x-7)^2 --doesn't even pass through the origin
+i4 : fpt(f)
+
+     1
+o4 = -
+     2
+
+i5 : isSimpleNormalCrossing(f, IsLocal=>false)
+
+o5 = false
+
+i6 : g = (y-1)^2 + (x-7)^2 -- doesn't even pass through the origin
 
        2    2
-o5 = x  + y  - 14x - 2y + 50
-
-o5 : R
-
-i6 : isSimpleNormalCrossing(g)
-
-o6 = true
-
-i7 : isSimpleNormalCrossing(g, IsLocal=>false)
-
-o7 = false
-
-i8 : h = x*y^2*(x+1)^3*(y-1)^4; --SNC everywhere
-
-i9 : isSimpleNormalCrossing(h)
-
-o9 = true
-
-i10 : isSimpleNormalCrossing(h, IsLocal=>false)
+o6 = x  + y  - 14x - 2y + 50
+
+o6 : R
+
+i7 : isSimpleNormalCrossing(g)
+
+o7 = true
+
+i8 : isSimpleNormalCrossing(g, IsLocal=>false)
+
+o8 = false
+
+i9 : h = x*y^2*(x+1)^3*(y-1)^4; --SNC everywhere
+
+i10 : isSimpleNormalCrossing(h)
 
 o10 = true
+
+i11 : isSimpleNormalCrossing(h, IsLocal=>false)
+
+o11 = true
 \end{MyVerbatim}

### 2019-06-07 Fsing/FThresholdsPaper/FThresholds.tex

@@
 \end{document}
+=======
+\documentclass{amsart}
+\usepackage{calc,amssymb,amsthm,amsmath,amsfonts,setspace}
+\RequirePackage[dvipsnames,usenames]{xcolor}
+
+\usepackage{fancyvrb}
+\usepackage{hyperref}
+\hypersetup{
+bookmarks,
+bookmarksdepth=3,
+bookmarksopen,
+bookmarksnumbered,
+pdfstartview=FitH,
+colorlinks,backref,hyperindex,
+linkcolor=Sepia,
+anchorcolor=BurntOrange,
+citecolor=MidnightBlue,
+citecolor=OliveGreen,
+filecolor=BlueViolet,
+menucolor=Yellow,
+urlcolor=OliveGreen
+}
+\usepackage{xspace}
+\interfootnotelinepenalty=100000
+
+\usepackage{mabliautoref}
+\usepackage{colonequals}
+\frenchspacing
+\input{kmacros3.sty}
+
+\usepackage{verbatim}
+\usepackage{enumerate}
+\usepackage[normalem]{ulem}
+%\usepackage{marginnote}
+\newcommand{\fram}{\mathfrak{m}}
+\DefineVerbatimEnvironment%
+{MyVerbatim}{Verbatim}
+{formatcom=\color{Violet}}
+
+\usepackage{fancyhdr}
+
+\pagestyle{fancy}
+\fancyhead[RO, LE]{\thepage}
+\fancyhead[C]{The \emph{FrobeniusThresholds} package for \emph{Macaulay2}}
+\fancyfoot{}
+\renewcommand{\headrulewidth}{0pt}
+
+\makeatletter
+\def\@settitle{\begin{center}%
+  \baselineskip14\p@\relax
+    \bfseries
+    \normalfont\LARGE%<- NEW
+\@title
+  \end{center}%
+}
+\makeatother
+
+\newcommand{\ft}{\operatorname{c}}
+\newcommand{\idealm}{\mathfrak{m}}
+
+\begin{document}
+\title[]{The \emph{FrobeniusThresholds} package for \emph{Macaulay2}}
+
+\author[]{Daniel J.\ Hern\'andez}
+\address{Department of Mathematics, University of Kansas, Lawrence, KS~66045, USA}
+\email{hernandez@ku.edu}
+\thanks{D.~J.~Hern\'andez was partially supported by NSF DMS \#1600702.}
+
+%\author[]{Sara Malec}
+%\address{Department of Mathematics, Hood College, Frederick, MD 21701}
+%\email{malec@hood.edu}
+
+%\author[]{Marcus Robinson}
+%\address{Department of Mathematics, University of Utah, Salt Lake City, UT~84112, USA}
+%\email{robinson@math.utah.edu}
+
+\author[]{Karl Schwede}
+\address{Department of Mathematics, University of Utah, Salt Lake City, UT~84112, USA}
+\thanks{K.~Schwede was supported by NSF CAREER Grant DMS \#1252860/1501102, NSF FRG Grant DMS \#1265261/1501115, NSF grant \#1801849 and a Sloan Fellowship.}
+\email{schwede@math.utah.edu}
+
+\author[]{Pedro Teixeira}
+\address{Department of Mathematics, Knox College, Galesburg, IL~61401, USA}
+\email{pteixeir@knox.edu}
+
+\author[]{Emily E.\ Witt}
+\address{Department of Mathematics, University of Kansas, Lawrence, KS~66045, USA}
+\email{witt@ku.edu}
+\thanks{E.~E.~Witt was partially supported by NSF DMS \#1623035.}
+\date{\today}
+
+\begin{abstract}
+   This article describes the \emph{Macaulay2} package \emph{FrobeniusThresholds}.
+   This package is designed to estimate and calculate $F$-pure thresholds, more general $F$-thresholds, and related numerical invariants arising in the study of singularities in prime characteristic commutative algebra.
+\end{abstract}
+
+\subjclass[2010]{13A35}
+
+\keywords{Macaulay2, Frobenius, $F$-singularity, $F$-pure threshold, $F$-threshold}
+
+\maketitle
+
+\section{Introduction}
+
+%This is for Karl
+%{\color{red}  Point out for people interested in computing log canonical thresholds:  Zhixian Zhou apparently proved in her thesis that the $F$-pure threshold for hypersurfaces is always a lower bound for the log canonical threshold.
+Therefore, this package effectively computes such lower bounds, and is much faster than the \emph{Dmodules} package, which appears to be the only package in Macaulay2 that computes log canonical thresholds.}
+
+This paper describes the \emph{Macaulay2} \cite{M2} package \emph{FrobeniusThresholds} \cite{FThresholdsPackage}, which provides tools for computing certain fundamental invariants arising in positive characteristic commutative algebra.
+More precisely, this package concerns the effective computation of \emph{$F$-pure thresholds}, \emph{$F$-thresholds}, and \emph{$F$-jumping exponents}.
+
+Recall that a ring of prime characteristic $p>0$ is said to be \emph{$F$-pure} if the Frobenius map|that is, the ring endomorphism sending an element to its $p$-th power|is a pure morphism;  under natural geometric hypotheses, this is equivalent to the condition that the Frobenius morphism splits as a map of rings.
+
+The concept of $F$-purity has proven to be important in commutative algebra, and has a rich history.
+Indeed, it first appeared in the work \cite{HochsterRobertsFrobeniusLocalCohomology}  of Hochster and Roberts to study local cohomology \cite{HochsterRobertsFrobeniusLocalCohomology}, was compared with rational singularities in  \cite{FedderFPureRat}, and was used to study global properties of Schubert varieties in \cite{MehtaRamanathanFrobeniusSplittingAndCohomologyVanishing}.
+
+After the advent of tight closure \cite{HochsterHunekeTC1}, the usage of Frobenius to quantify singularity|that is, deviation from regularity|proliferated, and based on a connection discovered between $F$-pure and \emph{log canonical} singularities \cite{HaraWatanabeFRegFPure}, the concept of $F$-purity was generalized to the context of \emph{pairs}.
+% $(R, f^t)$, where $f$ is an element of $R$, and $t$ is a nonnegative real number considered a formal exponent.
+
+Along these lines, the \emph{$F$-pure threshold} (fpt)%associated to an element of $R$
+was defined in analogy with the \emph{log canonical threshold} (lct) \cite{TakagiWatanabeFPureThresh}, and
+%The $F$-pure threshold of the pair $(R, f)$ is the supremum over all $t$ for which $(R, f^t)$ is $F$-pure.
+\emph{$F$-threholds} were then introduced as a family of invariants that naturally extend the notion of an $F$-pure threshold \cite{MustataTakagiWatanabeFThresholdsAndBernsteinSato}.
+
+Unfortunately, the $F$-pure threshold is typically difficult to calculate, even in many concrete cases.
+It is also not so well understood from the perspective of reduction to prime characteristic.
+Nevertheless, $F$-pure thresholds have been the focus of intense study over the past 15 years, and the \emph{Macaulay2} package \emph{FrobeniusThresholds} is centered around calculating and estimating the $F$-pure threshold and other $F$-thresholds, with the function {\tt fpt} at its core.
+
+The $F$-pure threshold can also be used to provide a lower bound for the log canonical threshold in characteristic zero.
+Indeed, Z.~Zhu showed in \cite[Corollary 4.2]{ZhuLogCanoincalThresholdsInPositiveChar} that if $f \in \bQ[x_1, \dots, x_n]$ is reduced modulo $p > 0$ to obtain $f_p = f\;\mathrm{mod}\;p \in \bF_p[x_1, \dots, x_n]$, then $\fpt(f_p) \leq \lct(f)$.
+There is a general purpose implementation of log canonical thresholds in the \emph{Dmodules} package by A.~Leykin and H.~Tsai \cite{DmodulesSource} and a package \emph{MultiplierIdeals} by Z.~Teitler, B.~Snapp and C.~Raicu \cite{MultiplierIdealsPackage}, which computes log canonical thresholds for special cases (monomial ideals, hyperplane arrangements, generic determinantal ideals, and certain binomial ideals), see also the paper \cite{MultiplierIdealsArticle}.
+However, our general purpose implementation of ${\tt fpt}$ in small characteristic is typically much faster than {\tt lct}, the general purpose function from \emph{Dmodules} which computes the log canonical threshold.
+
+\subsection*{Some background and notation}
+It is important to note that much of the functionality implemented in the \emph{FrobeniusThresholds} is not restricted to regular ambient rings; see Section \ref{sec.IsFPT} for a prominent example of this.
+
+However, for the sake of concreteness, we will mostly work in a polynomial ring over a finite field of  characteristic $p>0$.
+In fact,  we will work in this context exclusively in this introduction.
+Thus, unless otherwise stated, all ring elements and ideals under consideration are regarded as elements in such a ring.
+The ideal of this ring generated by its variables is denoted $\idealm$.
+
+Let us outline a common way in which natural numerical invariants in prime characteristic commutative algebra are constructed:  For every natural number $e$, associate to some fixed set of data|often, a collection of polynomials and ideals|an integer describing something of relevance that depends on $e$ (e.g., the dimension of some interesting vector space constructed in terms of your initial data).
+Finally, normalize this integer by dividing by some power of $p^e$, and then take the limit as the integer $e$ tends to infinity.
+The resulting limit, should it exist, should then encode some interesting information about your initial set of data.
+
+Consider a nonzero polynomial $f$ and a natural number $e$.  If $f$ does not vanish at the origin, then set set $\nu_f^{\idealm}(p^e) := \infty$.  Otherwise, $f \in \idealm$, and we instead define
+\[ \nu_f^{\idealm}(p^e) := \max \{ n>0 : f^n \notin \idealm^{[p^e]} \} \]
+where $\idealm^{[p^e]}$ denotes the $p^e$-th Frobenius power of $\idealm$, that is, the ideal generated by the $p^e$-th powers of the elements of $\idealm$.
+It is not very hard to see that this number is exactly the largest power of $f$ that is part of a free basis for the localization of the ambient polynomial ring at the origin over its subring of $p^e$-th powers.
+As noted earlier, this number also has a natural interpretation in terms of $F$-purity of pairs.
+
+Following our outline, we define
+\[ \ft^{\idealm}(f) := \lim_{e \to \infty} \frac{ \nu_f^{\idealm}(p^e)}{p^e} \]
+
+Inspired by its connections with the $F$-purity of pairs,  this limit is called the \emph{$F$-pure threshold} of $f$ at the origin.
+This limit exists, and is finite when $f \in \idealm$.
+In the latter case, the limit is also rational, but this is far from obvious  \cite{BlickleMustataSmithDiscretenessAndRationalityOfFThresholds}.
+
+The $F$-pure threshold is closely related to many other fundamental concepts in prime characteristic commutative algebra.   For instance,
+\[ \ft^{\idealm}(f) = \inf \{ t>0 : \tau(f^t)  \subseteq \idealm \} = \sup \{ t>0 : \sigma( f^t) \neq 0 \} \]
+where $\tau(f^t)$ and $\sigma(f^t)$ are the \emph{test ideal} and \emph{$F$-signature}, respectively, associated to $f$ and the formal nonnegative real exponent $t$.
+The former is an ideal in the ambient ring of $f$, and the latter is a real number;  both depend on the parameter $t$ and prime $p$ in subtle ways \cite{BlickleMustataSmithDiscretenessAndRationalityOfFThresholds, BlickleSchwedeTuckerFSigPairs1}.
+Though we will not elaborate much on these topics,  we stress that the \emph{Macaulay2} package \emph{TestIdeals} provides functionality for the effective computation of test ideals in many cases \cite{TestIdealsPackage, TestIdealsPaper}.
+
+In the literature, the $F$-pure threshold $\ft^{\idealm}(f)$ is often denoted $\fpt(f)$, for obvious reasons.
+However, in this note, we adopt the former notation to avoid any possible confusion with the \emph{Macaulay2} function {\tt fpt} described in Section \ref{sec.FPT}.
+Indeed, the command {\tt fpt(f)} need not always output the number $\ft^{\idealm}(f) = \fpt(f)$, though in the case that it cannot, it will provide a reasonably good estimate of this number.
+
+It turns out that the sequence $\{ \nu_f^{\idealm}(p^e) \}_{e=1}^{\infty}$ itself, and not just its limit, also encodes interesting information about $f$.
+For example, it is closely related to the so-called \emph{Bernstein-Sato polynomial} \cite{MustataTakagiWatanabeFThresholdsAndBernsteinSato}.
+Thus, it is natural to ask whether one can recover the sequence $\{ \nu_f^{\idealm}(p^e) \}_{e=1}^{\infty}$ from the limit $\ft^{\idealm}(f)$.
+Fortunately, the answer to this question is yes \cite{MustataTakagiWatanabeFThresholdsAndBernsteinSato, HernandezFPurityOfHypersurfaces}.
+More precisely,
+\begin{equation*}
+\nu_f^{\idealm}(p^e) = \lceil p^e \cdot \ft^{\idealm}(f) \rceil - 1.
+\end{equation*}
+
+We conclude this subsection by briefly reviewing some natural generalizations.  Suppose that $I$ and $J$ are ideals.  If $I$ is contained in the radical of $J$, then we set
+%
+\[ \nu_I^J(p^e) = \max \{ n : I^n \notin J^{[p^e]} \}. \]
+Otherwise, we set $\nu_I^J(p^e) = \infty$.
+This clearly generalizes the quantity $\nu_f^{\idealm}(p^e)$ considered earlier, and we call
+\[ \ft^J(I) := \lim_{e \to \infty} \frac{ \nu_f^{\idealm}(p^e)}{p^e} \]
+the \emph{$F$-threshold of $I$ with respect to $J$}.  These numbers are also rational, when they are finite.
+The value $\ft^{\idealm}(I)$ is called the \emph{$F$-pure threshold of $I$}, and if $I = (f)$ is principal,  $\ft^{J}(f) := \ft^J(I)$ is called the \emph{$F$-threshold of $f$ with respect to $J$}.
+Like $F$-pure thresholds, $F$-thresholds can also be defined in terms of its test ideals.
+
+Finally, we point out that the  \emph{FrobeniusThresholds} package builds heavily upon the \emph{TestIdeals} package for \emph{Macaulay2} \cite{TestIdealsPackage, TestIdealsPaper,M2}, which provides a broad range of functionality for effective computation in prime characteristic commutative algebra.
+In fact, both this package and \emph{TestIdeals} are derived from an older package \emph{PosChar}.
+
+\subsection*{Organization}
+
+There are three main sections in this paper, which describe and illustrate the main functionality implemented in the package \emph{FrobeniusThresholds}.
+\begin{itemize}
+\item[$\circ$] \autoref{sec.Nu} describes the fundamental function {\tt nu}.  As its name suggests, this function is concerned with computing the integers $\nu_I^J(p^e)$ described above.
+\item[$\circ$] \autoref{sec.IsFPT} explains the functionality for determining whether a given number is the $F$-pure threshold, or more generally, an \emph{$F$-jumping exponent}.
+\item[$\circ$] \autoref{sec.FPT} describes the features of the central function of the package, {\tt fpt}.
+\item[$\circ$]  \autoref{sec.FutureDirections} describes our plans for future improvements to this package.
+\end{itemize}
+%{\color{red} Move this later}
+
+\subsection*{Acknowledgements.}  First and foremost, the authors enthusiastically thank all authors and contributors to the
+\emph{FrobeniusThresholds} package.  {\color{red} (CHECK THESE NAMES)}
+Our package coauthors are Juliette Bruce and Daniel Smolkin.  Erin Bela, Zhibek Kadyrsizova, Moty Katzman, Sara Malec, and Marcus Robinson also contributed valuable code to the package.
+
+Thanks go to the organizers of the \emph{Macaulay2} workshops where much of the functionality described herein was developed, hosted by Wake Forest University in 2012, the University of California, Berkeley in 2014 and 2017, Boise State University in 2015, and the University of Utah in 2016.
+
+Finally, we are grateful to the University of Utah for hosting a collaborative development visit in 2018, and to the Institute of Mathematics and its Applications for its generous support for our 2019 Coding Sprint.
+The current version of the package was finalized during these events.
+
+\section{The {\tt nu} function}
+\label{sec.Nu}
+
+We first consider the {\tt nu} function, a fundamental component of the package \emph{FrobeniusThresholds}.
+As in the introduction, in this section we work in a polynomial ring over a finite field of characteristic $p>0$.
+As in the introduction, $\idealm$ will denote the ideal of this ring generated by the variables.
+
+Fix a natural number $e$.  If $f$ is a nonzero polynomial contained in the radical of an ideal $J$, then the command {\tt nu(e,f,J)} outputs the integer $\nu_f^J(p^e)$ defined in the introduction, and
+%, the maximal integer exponent such that $f^n$ is not contained in $J^{[p^e]}$.
+more generally, if a nonzero ideal $I$ is contained in the radical of $J$, then {\tt nu(e,I,J)} outputs $\nu_I^J(p^e)$.
+Consider the following example.
+%, the maximal integer exponent $n$ such that $I^n$ is not contained in $J^{[p^e]}$.
+
+{\small
+\setstretch{.67}
+\begin{MyVerbatim}
+
+i1 : R = ZZ/11[x,y];
+
+i2 : I = ideal(x^2 + y^3, x*y);
+
+o2 : Ideal of R
+
+i3 : J = ideal(x^2, y^3);
+
+o3 : Ideal of R
+
+i4 : nu(1, I, J)
+
+o4 = 24
+
+i5 : f = x*y*(x^2 + y^2);
+
+i6 : nu(1, f, J)
+
+o6 = 10
+\end{MyVerbatim}
+}
+\medspace
+
+% R = ZZ/11[x,y];
+% I = ideal(x^2 + y^3, x*y);
+% J = ideal(x^2, y^3);
+% nu(1, I, J)
+% f = x*y*(x^2 + y^2);
+% nu(1, f, J)
+
+We highlight some degenerate cases:  If $f$ is the zero polynomial, then {\tt nu(e,f,J)} outputs {\tt 0}, and if $f$ is \emph{not} contained in the radical of $J$, then the output is instead {\tt infinity}.
+These degenerate cases extend analogously to the command {\tt nu(e,I,J)}.
+
+{\small
+\setstretch{.67}
+\begin{MyVerbatim}
+
+i7 : nu(1, 0_R, J)
+
+o7 = 0
+
+i8 : nu(1, 1_R, J)
+
+o8 = infinity
+
+o8 : InfiniteNumber
+\end{MyVerbatim}
+}
+\medspace
+
+%nu(1, 0_R, J)
+%nu(1, 1_R, J)
+
+If the third argument is omitted from the function {\tt nu}, it is assumed to be the maximal ideal $\idealm$.
+
+{\small
+\setstretch{.67}
+\begin{MyVerbatim}
+
+i9 : R = ZZ/17[x,y,z];
+
+i10 : f = x^3 + y^4 + z^5;
+
+i11 : m = ideal(x, y, z);
+
+o11 : Ideal of R
+
+i12 : nu(2, f) == nu(2, f, m)
+
+o12 = true
+\end{MyVerbatim}
+}
+\medspace
+
+%R = ZZ/17[x,y,z];
+%f = x^3 + y^4 + z^5;
+%M = ideal(x, y, z);
+%nu(2, f) == nu(2, f, M)
+
+It is well known that if $q=p^e$ for some nonnegative integer $e$, then \[ \nu_I^J(qp) = \nu_I^J(q)\cdot p + L\]  where the error term $L$ is nonnegative, and can be explicitly bounded from above in terms of $p$ and the number of generators of $I$ and $J$.
+For instance, the error term $L$ is at most $p-1$ when $I$ is principal and $J$ is arbitrary.
+
+This implies that when searching for the maximal exponent defining {\tt nu(e,I,J)} for positive $e$, it is safe to start at $p$ times the output of {\tt nu(e-1,I,J)}, and one needn't search too far past this number.
+This also suggests that the most efficient way to compute {\tt nu(e,I,J)} is to compute, successively, {\tt nu(s,I,J)}, for each $s = 0,\ldots,e$.
+This is indeed how the computation is done in most cases.
+
+As pointed out in the introduction, if $f \in \mathfrak{m}$, the values $\nu^{\mathfrak{m}}_f(p^e)$ can be recovered from the $F$-pure threshold of $f$.
+This fact is used to speed up computations for certain polynomials whose $F$-pure thresholds can be computed quickly via specialized algorithms, namely diagonal polynomials, binomials, and forms in two variables (see Section \ref{sec.FPT}).
+This feature can be disabled by setting the option {\tt UseSpecialAlgorithms} (default value {\tt true}) to {\tt false}.
+Consider the following example, where $f$ is a diagonal polynomial.
+
+{\small
+\setstretch{.67}
+\begin{MyVerbatim}
+
+i1 : R = ZZ/17[x,y,z];
+
+i2 : f = x^3 + y^4 + z^5; -- a diagonal polynomial
+
+i3 : time nu(3, f)
+     -- used 0.00552312 seconds
+
+o3 = 3756
+
+o4 : QQ
+
+i4 : time nu(3, f, UseSpecialAlgorithms => false)
+     -- used 0.155826 seconds
+
+o4 = 3756
+\end{MyVerbatim}
+}
+\medspace
+
+% R = ZZ/17[x,y,z];
+% f = x^3 + y^4 + z^5; -- a diagonal polynomial
+% time nu(3, f)
+% time nu(3, f, UseSpecialAlgorithms => false)
+
+\subsection*{Options for the {\tt nu} function}
+
+We now describe the options available for the function {\tt nu}.
+We focus primarily on the case where the second input is an ideal $I$, since the options work analogously when the second input is instead a polynomial $f$.
+
+In general, the function {\tt nu} works by searching through the list of integers $n$, and checking containments of the $n$-th power of $I$ in a specified Frobenius power of $J$.
+The user can specify how this search is approached through the  option {\tt Search}.
+Namely, a binary search is used when {\tt Search} is set to {\tt Binary} (and this is the option's default value), and a linear search is run when it is set to {\tt Linear}.
+
+{\small
+\setstretch{.67}
+\begin{MyVerbatim}
+
+i1 : R = ZZ/5[x,y,z];
+
+i2 : f = x^2*y^4 + y^2*z^7 + z^2*x^8;
+
+i3 : time nu(5, f) -- uses binary search (default)
+     -- used 0.313778 seconds
+
+o3 = 1124
+
+i4 : time nu(5, f, Search => Linear)
+     -- used 0.441903 seconds
+
+o4 = 1124
+
+i5 : m = ideal(x, y, z);
+
+o5 : Ideal of R
+
+i6 : time nu(2, m, m^2) -- uses binary search (default)
+     -- used 1.58258 seconds
+
+o6 = 97
+
+i7 : time nu(2, m, m^2, Search => Linear) -- but linear seach gets luckier
+     -- used 0.531175 seconds
+
+o7 = 97
+\end{MyVerbatim}
+}
+\medspace
+
+%R = ZZ/5[x,y,z];
+%f = x^2*y^4 + y^2*z^7 + z^2*x^8;
+% time nu(5, f) -- uses binary search (default)
+% time nu(5, f, Search => Linear)
+% M = ideal(x, y, z);
+% time nu(2, M, M^2) -- uses binary search (default)
+% time nu(2, M, M^2, Search => Linear) -- but linear seach gets luckier
+
+If the option {\tt ReturnList} is changed from its default value of {\tt false} to {\tt true}, rather than simply outputting $\nu_I^J(p^e)$, {\tt nu} outputs a list of the values $\nu_I^J(p^s)$, for $s=0,\ldots,e$.
+Alternatively, the same information can be found by setting the option {\tt Verbose} to {\tt true} (its default value is {\tt false}), to request that each of these values $\nu_I^J(p^s)$ is printed as they are iteratively computed.
+This can also serve a way to monitor the progress of the computation.
+
+{\small
+\setstretch{.67}
+\begin{MyVerbatim}
+
+i8 : nu(5, f, ReturnList => true)
+
+o8 = {0, 1, 8, 44, 224, 1124}
+
+o8 : List
+
+i9 : nu(5, f, Verbose => true)
+
+     nu(1) = 0
+     nu(p^1) = 1
+     nu(p^2) = 8
+     nu(p^3) = 44
+     nu(p^4) = 224
+     nu(p^5) = 1124
+\end{MyVerbatim}
+}
+\medspace
+
+%nu(5, f, ReturnList => true)
+%nu(5, f, Verbose => true)
+
+As described in the introduction, the integer $\nu_I^J(p^e)$ is defined in terms of the containment conditions on powers of ideals.
+For positive integers $n$ and $e$, and an ideal $I$ contained in the radical of another ideal $J$, we have that
+\begin{equation*}
+  I^n \subseteq J^{[p^e]} \Longleftrightarrow (I^n)^{[1/p^e]} \subseteq J
+\end{equation*}
+where $(I^n)^{[1/p^e]}$ denotes the $p^e$-th \emph{Frobenius root} of $I^n$, as defined in \cite{BlickleMustataSmithDiscretenessAndRationalityOfFThresholds}.
+The option {\tt ContainmentTest} for {\tt nu} allows the user to choose which of the two types of containment statements appearing above to use toward the calculation of $\nu_I^J(p^e)$.
+
+If {\tt ContainmentTest} is set to {\tt StandardPower}, then {\tt nu(e,I,J)} is computed by testing the left-hand containment above, and when it is set to {\tt FrobeniusRoot}, the right-hand containment is checked.
+For efficiency reasons, the default value for {\tt ContainmentTest} is set to  {\tt FrobeniusRoot} if the second argument passed to {\tt nu} is a polynomial, and is set to {\tt StandardPower} if it is an ideal.
+
+{\small
+\setstretch{.67}
+\begin{MyVerbatim}
+
+i1 : R = ZZ/11[x,y,z];
+
+i2 : f = x^3 + y^3 + z^3 + x*y*z;
+
+i3 : time nu(3, f) -- ContainmentTest is set to FrobeniusRoot, by default
+     -- used 0.116697 seconds
+
+o3 = 1209
+
+i4 : time nu(3, f, ContainmentTest => StandardPower)
+     -- used 9.65013 seconds
+
+o4 = 1209
+\end{MyVerbatim}
+}
+\medspace
+
+% R = ZZ/11[x,y,z];
+% f = x^3 + y^3 + z^3 + x*y*z;
+% time nu(3, f) -- ContainmentTest is set to FrobeniusRoot, by default
+% time nu(3, f, ContainmentTest => StandardPower)
+
+The option {\tt ContainmentTest} has a third possible value, {\tt FrobeniusPower}, which may produce a different result than the other two values.
+Given an ideal $I$, the first, third, and fourth authors introduced the notion of a (generalized) Frobenius power $I^{[n]}$ of $I$, when $n$ is an arbitrary positive integer, not necessarily of the form $n = p^e$ \cite{hernandez+etal.frobenius_powers}.
+When {\tt ContainmentTest} is set to {\tt FrobeniusPower}, rather than  computing $\nu_I^J(p^e)$, the function {\tt nu} computes the
+maximal integer $n$ for which $I^{[n]}$ is not contained in $J^{[p^e]}$.
+This number is denoted $\mu_I^J(p^e)$ in \emph{loc.\ cit.}, and equals $\nu_I^J(p^e)$ when $I$ is replaced with a polynomial, or is a principal ideal, but need not coincide in general.
+For example, the two commands below give different output values.
+
+{\small
+\setstretch{.67}
+\begin{MyVerbatim}
+
+i1 : R = ZZ/3[x,y];
+
+i2 : m = ideal(x, y);
+
+o2 : Ideal of R
+
+i3 : nu(3, m^5)
+
+o3 = 10
+
+i4 : nu(3, m^5, ContainmentTest => FrobeniusPower)
+
+o4 = 8
+\end{MyVerbatim}
+}
+
+\medspace
+\noindent In line with the philosophy described in the introduction, after appropriately normalizing and taking the limit as $e$ approaches infinity, the values $\mu_I^J(p^e)$ determine certain invariants of interest called \emph{critical exponents}.
+
+% R = ZZ/3[x,y];
+% m = ideal(x, y);
+% nu(3, m^5)
+% nu(3, m^5, ContainmentTest => FrobeniusPower)
+
+%%Below is the original version of the section describing the nu function
+
+%\section{The $F$-pure threshold limit and {\tt nu}}
+%\label{sec.Nu}
+%
+%Suppose $R = k[x_1, \dots, x_n]$ is a polynomial ring over a finite field and $f \in R$.
+If $f^a \notin \langle x_1^{p^e}, \dots, x_n^{p^e} \rangle = \fram^{[p^e]}$, then the pair $(R, f^{a/(p^e -1)})$ is $F$-pure at the origin, whereas if $f^a \in \fram^{[p^e]}$, then the pair $(R, f^{a/p^e})$ is not $F$-pure at the origin.
+By finding the $a \in \bZ$ where that transition happens, and then limiting over $e$, one can compute the $F$-pure threshold.
+See \cite{MustataTakagiWatanabeFThresholdsAndBernsteinSato}.
+%
+%We set $\nu(e, f)$ to be largest $a \in \bZ$ such that $f^a \notin \fram^{[p^e]}$ (note in the literature, it is frequently denoted by $\nu_f(p^e)$.  It immediately follows that
+%\[
+%\fpt(f) = \lim_{e \to \infty} {\nu(e, f) \over p^e}.
+%\]
+%These numbers $\nu(e, f)$ can be computed using the command {\tt nu}, as in the example below.
+%\medskip
+%{\small
+%\setstretch{.67}
+%\begin{MyVerbatim}
+%i1 : loadPackage "FThresholds"
+%
+%o1 = FThresholds
+%
+%o1 : Package
+%
+%i2 : R = ZZ/7[x,y]
+%
+%o2 = R
+%
+%o2 : PolynomialRing
+%
+%i3 : f = y^2 - x^3
+%
+%        3    2
+%o3 = - x  + y
+%
+%o3 : R
+%
+%i4 : nu(1, f)
+%
+%o4 = 5
+%
+%o4 : QQ
+%
+%i5 : nu(2, f)
+%
+%o5 = 40
+%
+%o5 : QQ
+%
+%i6 : nu(3, f)
+%
+%o6 = 285
+%
+%o6 : QQ
+%\end{MyVerbatim}
+%}
+%\medskip
+%The numbers $5/7, 40/49, 285/343$ then approximate the $F$-pure threshold, which in this case happens to equal $5/6$.
+By default, if the function $f$ has a special form (is a diagonal polynomial or a binomial), then the function does not check whether $f^a$ is in  $\langle x_1^{p^e}, \dots, x_n^{p^e} \rangle$, but instead uses general formulas for $\nu$s, see \cite{HernandezFPureThresholdOfBinomial,HernandezFInvariantsOfDiagonalHyp}.
+%
+%In fact, one can make the following more general definition.  If $I$ and $J$ are two ideals (with $I \subseteq \sqrt{J}$), one can define
+%\[
+%\nu(e, I, J) = \max \{ n \in \bZ \; |\; I^n \not\subseteq J^{[p^e]} \}.
+%\]
+%This is frequently denoted by $\nu_I^J(p^e)$ in the literature.
+In the case that $I = \langle f \rangle$ and $J = \fram$, this just recovers the $\nu$'s defined above; the limit of which is the $F$-pure threshold.
+For more general $I$ and $J$, the limit
+%\[
+%\lim_{e \to \infty} {\nu(e, I, J) \over p^e}
+%\]
+%is called the \emph{$F$-threshold of $I$ with respect to $J$}.
+To compute these values we use a binary search, unless the user specifies that we should use a linear search instead {\tt Search=>Linear}.
+%
+%There is one more option that deserves mentioning, {\tt ContainmentTest}.  There are two ways to check whether $f^a$ (or $I^a$) is contained in $J^{[p^e]}$.  In general it is true that
+%\[
+%I^a \subseteq J^{[p^e]} \text{ $\Leftrightarrow$ } (I^a)^{[1/p^e]} \subseteq J
+%\]
+%where $\bullet^{[1/p^e]}$ is defined as in the {\tt TestIdeals} package.
+Which of these two strategies to use is controlled by the option {\tt ContainmentTest => StandardPower} and {\tt ContainmentTest => FrobeniusRoot} respectively.
+%For principal $I$, the command on the right is generally faster (and so {\tt FrobeniusRoot} is the default strategy for computing $\nu$).
+For non-principal $I$, frequently the command on the left is quicker, and so {\tt StandardPower} is default strategy.
+%
+%Finally, the option {\tt ContainmentTest => FrobeniusPower}, then ${\tt \nu(e, I, A)}$ computes the largest integer $n$ such that
+%\[
+%I^{[p^n]} \subseteq J^{[p^e]}.
+%\]
+%See \cite{HernandezTeixeiraWittFrobeniusPowers} for more discussion of this.
+
+\section{{\tt isFPT}, {\tt compareFPT} and {\tt isFJumpingExponent}}
+\label{sec.IsFPT}
+
+The \emph{FrobeniusThresholds} package contains methods to
+ test candidate values for an $F$-pure threshold, and even $F$-jumping numbers, even in some singular rings.
+
+Consider a  $\mathbb{Q}$-Gorenstein ring $R$ of characteristic $p>0$, whose index not divisible by $p$.
+Given a parameter $t \in \mathbb{Q}$ and an element $f$ of $R$, the command {\tt isFPT(t,f)} outputs {\tt true} if $t$ is the $F$-pure threshold of $f$, and {\tt false} otherwise.
+Moreover, the function {\tt compareFPT} provides further information about the relationship between $t$ and the $F$-pure threshold of $f$; namely,
+{\tt compareFPT(t, f)} returns {\tt-1} , {\tt 0}, {\tt 1} when $t$ is less than, equal to, or greater than, respectively, the $F$-pure threshold of $f$.
+Setting the option {\tt IsLocal} to {\tt true} tells the function to consider the $F$-pure threshold at the origin.
+The following example illustrates this functionality.
+
+{\small
+\setstretch{.67}
+\begin{MyVerbatim}
+
+i1 : R = ZZ/11[x, y, z]/(x^2 - y*(z - 1));
+
+i2 : compareFPT(5/11, z - 1)
+
+o2 = -1
+
+i3 : isFPT(1/2, z - 1)
+
+o3 = true
+
+i4 : isFPT(1/2, z - 1, IsLocal => true)
+
+o4 = false
+\end{MyVerbatim}
+}
+\medspace
+
+The general method applied calls upon functionality from the \emph{TestIdeals} package \cite{TestIdealsPackage, TestIdealsPaper}.  The functions {\tt testIdeal} and {\tt FPureModule} therein are used
+to compute the test ideals of $f$ with respect to the parameter $t$, and that with respect to $t - \varepsilon$, for $\varepsilon>0$ very small.
+For instance, as noted in the introduction, when $R$ is a polynomial ring, $t$ is the $F$-pure threshold of $f$ if and only if $\tau(R, f^t)$ is contained in the homogeneous maximal ideal, but
+$\tau(R, f^{t-\varepsilon})$ is not.
+(Note that for $R$ strongly $F$-regular and Gorenstein, {\tt FPureModule(t, f)} precisely computes $\tau(R, f^{t-\varepsilon})$.)
+%These commands work more generally, but they \emph{only} currently work when $R$ is $\bQ$-Gorenstein, with index not divisible by $p$.
+
+Since not only the $F$-pure thresholds, but also the higher $F$-jumping numbers, are determined by containment conditions on test ideals, the functionality is extended to determine whether a given number is an $F$-jumping number.
+Analogous syntax is used, as shown in the following example.
+
+{\small
+\setstretch{.67}
+\begin{MyVerbatim}
+
+i49 : R = ZZ/13[x, y];
+
+i50 : f = y*((y + 1) - (x - 1)^2)*(x - 2)*(x + y - 2);
+
+i51 : isFJumpingExponent(3/4, f)
+
+o51 = true
+\end{MyVerbatim}
+}
+\medspace
+
+\section{The {\tt fpt} function}
+\label{sec.FPT}
+
+The core function in the package \emph{FrobeniusThresholds} is called {\tt fpt}.
+Throughout this section, let $f$ be a polynomial with coefficients in a finite field of characteristic $p$.
+When passed the polynomial $f$, the function {\tt fpt} attempts to find the exact value for the $F$-pure threshold of $f$ at the origin, and returns that value, if possible.
+Otherwise, it returns lower and upper bounds for the $F$-pure threshold, as demonstrated below.
+
+{\small
+\setstretch{.67}
+\begin{MyVerbatim}
+
+i1 : ZZ/5[x,y,z];
+
+i2 : fpt(x^3 + y^3 + z^3 + x*y*z)
+
+     4
+o2 = -
+     5
+
+o2 : QQ
+
+i3 : fpt(x^5 + y^6 + z^7 + (x*y*z)^3)
+
+      1  2
+o3 = {-, -}
+      3  5
+
+o3 : List
+\end{MyVerbatim}
+}
+\medspace
+
+\subsection*{The option {\tt UseSpecialAlgorithms} for the {\tt fpt} function}
+
+The {\tt fpt} function has the option {\tt UseSpecialAlgorithms}.  When
+set to {\tt true} (the default value), {\tt fpt} first checks whether $f$ is a monomial, a diagonal polynomial, a binomial, a form in two variables, or a product of factors in simple normal crossing, in that order.
+
+If $f = x_1^{a_n}\cdots x_n^{a_n}$, then its $F$-pure threshold is simply $\min \{ 1/a_1, \ldots, 1/a_n \}$.  When $f$ is a diagonal polynomial, a binomial, or a form in two variables, 
+algorithms of Hern\'andez \cite{HernandezFInvariantsOfDiagonalHyp, HernandezFPureThresholdOfBinomial}, or Hern\'andez and Teixeira \cite{HernandezTeixeiraFThresholdFunctions},  are executed to compute the $F$-pure threshold.
+We note that algorithms for computing $F$-pure thresholds of binomials in certain special characteristics appear in \cite{ShibutaTakagiLCThresholds}.
+
+{\small
+\setstretch{.67}
+\begin{MyVerbatim}
+
+i4 : fpt(x^3*y^4*z^5) -- a monomial
+
+      1
+o4 = -
+      5
+
+o4 : QQ
+
+i5 : fpt(x^17 + y^20 + z^24) -- a diagonal polynomial
+
+      94
+o5 = ---
+     625
+
+i6 : fpt(x^2*y^6*z^10 + x^10*y^5*z^3) -- a binomial
+
+      997
+o6 = ----
+     6250
+
+o6 : QQ
+
+i7 : ZZ/5[x,y];
+
+i8 : fpt(x^2*y^6*(x + y)^9*(x + 3*y)^10) -- a form in two variables
+
+      5787
+o8 = -----
+     78125
+
+o8 : QQ
+\end{MyVerbatim}
+}
+\medspace
+
+The above noted algorithm for computing the $F$-pure threshold of a binary form $f$ requires factoring $f$ into linear forms, and {\tt fpt} can sometimes hang when attempting that factorization.
+For this reason, when a factorization is already known, the user can pass to {\tt fpt} a list containing all the pairwise prime linear factors of $f$, and a list containing their respective multiplicities.
+
+{\small
+\setstretch{.67}
+\begin{MyVerbatim}
+
+i9 : L = {x, y, x + y, x + 3*y};
+
+i10 : m = {2, 6, 9, 10};
+
+i11 : fpt(L, m) == o7
+
+o11 = true
+\end{MyVerbatim}
+}
+\medspace
+
+If {\tt UseSpecialAlgorithms} is set to {\tt true} and $f$ does not fall into any of the four forementioned cases, then the function {\tt fpt} next calls {\tt isSimpleNormalCrossing(f)} to check whether the polynomial $f$ is a product of factors that are in simple normal crossing.
+If this command returns {\tt true}, the $F$-pure threshold can easily be computed, and {\tt fpt} returns this value.
+For more detail on the function {\tt isSimpleNormalCrossing} and on computing the $F$-pure threshold of a polynomial with simple normal crossings, please see the end of this section.
+
+\subsection*{Searching for the $F$-pure threshold when no special algorithm applies}
+
+In the remainder of this section, we describe the {\tt fpt} function when no special algorithm is available, or {\tt UseSpecialAlgorithms} is set to {\tt false},  as well as the roles of the options {\tt DepthOfSearch}, and {\tt Attempts}, both nonnegative integers.
+
+In this case, very roughly speaking, the {\tt fpt} function will either compute, and output, the exact value of the $F$-pure threshold of $f$, and otherwise recursively compute a finite sequence of lower and upper bounds for this value, and output the last of these, which will be the tightest among all computed.
+The value of the option {\tt DepthOfSearch} determines the precision of the initial set of bounds, and the option {\tt Attempts}, in conjunction with some various subroutines, determines whether, and how, to produce new, tighter bounds from the previous ones.
+
+In more detail, let $e$ denote the value of the option {\tt DepthOfSearch}, which conservatively defaults to {\tt 1}.
+The {\tt fpt} function first computes $\nu=\nu_f(p^e)$, which agrees with the output of {\tt nu(e,f)}.
+It is well known that the $F$-pure threshold of $f$ is greater than $\nu/p^e$ and at most $(\nu+1)/p^e$, and applying  \cite[Proposition 4.2]{HernandezFPurityOfHypersurfaces} to this lower bound tells us that the $F$-pure threshold of $f$ must be at least $\nu/(p^e-1)$.
+In summary, we know that the $F$-pure threshold of $f$ must lie in the closed interval
+%
+\begin{equation}
+\label{estimating-interval: e}
+\tag{$\dagger$}
+\left[ \frac{\nu}{p^e-1}, \frac{\nu+1}{p^e} \right].
+\end{equation}
+
+With these estimates in hand, the subroutine {\tt guessFPT} is called to make some ``educated guesses" in an attempt to identify the $F$-pure threshold within this interval, or at least narrow down this interval to produce improved estimates.
+The number of ``guesses" is controlled by the option {\tt Attempts}, which conservatively defaults to {\tt 3}.
+If {\tt Attempts} is set to {\tt 0}, then {\tt guessFPT} is bypassed.
+If  {\tt Attempts} is set to at least {\tt 1}, then a first check is run to verify whether the right-hand endpoint $(\nu+1)/p^e$ of the above interval \eqref{estimating-interval: e} is the $F$-pure threshold.
+We illustrate this below.
+
+{\small
+\setstretch{.67}
+\begin{MyVerbatim}
+
+i11 : f = x^2*(x + y)^3*(x + 3*y^2)^5;
+
+i12 : fpt(f, Attempts => 0) -- a bad estimate
+
+          1
+o12 = {0, -}
+          5
+
+o12 : List
+
+i13 : fpt(f, Attempts => 0, DepthOfSearch => 3) -- a better estimate
+
+        21   22
+o13 = {---, ---}
+       124  125
+
+o13 : List
+
+i14 : fpt(f, Attempts => 1, DepthOfSearch => 3) -- the right-hand
+
+      endpoint (nu+1)/p^e is the F-pure threshold
+
+       22
+o14 = ---
+      125
+
+o14 : QQ
+
+\end{MyVerbatim}
+}
+
+If  {\tt Attempts} is set to at least {\tt 2} and the right-hand endpoint $(\nu+1)/p^e$ of the interval \eqref{estimating-interval: e} is not the $F$-pure threshold, then a second check is run to verify whether the left-hand endpoint $\nu/(p^e-1)$ of this interval is the $F$-pure threshold.
+
+{\small
+\setstretch{.67}
+\begin{MyVerbatim}
+
+i15 : f = x^6*y^4 + x^4*y^9 + (x^2 + y^3)^3;
+
+i16 : fpt(f, Attempts => 1, DepthOfSearch => 3)
+
+       17   7
+o16 = {--, --}
+       62  25
+
+o16 : List
+
+i17 : fpt(f, Attempts => 2, DepthOfSearch => 3) -- the left-hand endpoint
+
+      nu/(p^e-1) is the F-pure threshold
+
+      17
+o17 = --
+      62
+
+o17 : QQ
+
+\end{MyVerbatim}
+}
+
+If neither endpoint is the $F$-pure threshold and {\tt Attempts} is set to more than {\tt 2}, then  additional checks are performed at certain numbers within the interval, chosen according to the criteria determined by the value of the option {\tt GuessStrategy}.
+We refer the reader for the documentation of this strategy for more details.
+
+{\color{red}  This will need to be updated.  Maybe look at Pedro's new documentation.}
+
+{\small
+\setstretch{.67}
+\begin{MyVerbatim}
+
+i18 : f = x^3*y^11*(x + y)^8*(x^2 + y^3)^8;
+
+i19 : fpt(f, DepthOfSearch => 3, Attempts => 2)
+
+        3   7
+o19 = {--, ---}
+       62  125
+
+o19 : List
+
+i20 : fpt(f, DepthOfSearch => 3, Attempts => 3) -- an additional check
+
+      sharpens the estimate
+
+        3   1
+o20 = {--, --}
+       62  18
+
+o20 : List
+
+i21 : fpt(f, DepthOfSearch => 3, Attempts => 4) -- and one more finds
+
+      the answer
+
+       1
+o21 = --
+      19
+
+o21 : QQ
+\end{MyVerbatim}
+}
+\medspace
+
+If {\tt guessFPT} is unsuccessful and {\tt UseFSignature} is set to {\tt true}, then the {\tt fpt} function proceeds to use the convexity of the $F$-signature function and a secant line argument to attempt to narrow down the interval bounding the $F$-pure threshold.
+
+{\small
+\setstretch{.67}
+\begin{MyVerbatim}
+
+i22 : f = x^5*y^6*(x + y)^9*(x^2 + y^3)^4;
+
+i23 : fpt(f, DepthOfSearch => 3)
+
+        2   1
+o23 = {--, --}
+       31  14
+
+o23 : List
+
+i24 : fpt(f, DepthOfSearch => 3, UseFSignature => true)
+
+        181   1
+o24 = {----, --}
+       2750  14
+
+o24 : List
+
+i25 : numeric o23
+
+o25 = {.0645161, .0714286}
+
+o25 : List
+
+i26 : numeric o24 -- UseFSignature sharpened the estimate a bit
+
+o26 = {.0658182, .0714286}
+
+o26 : List
+\end{MyVerbatim}
+}
+\medspace
+
+When {\tt FRegularityCheck} is set to {\tt true} and no exact answer has been found, a final check is run to verify whether the final lower bound for the $F$-pure threshold is the exact answer (if it has not already been eliminated as a possibility).
+
+{\small
+\setstretch{.67}
+\begin{MyVerbatim}
+
+i27 : f = (x + y)^4*(x^2 + y^3)^6;
+
+i28 : fpt( f, Attempts => 2, DepthOfSearch => 3 )
+
+        3   13
+o28 = {--, ---}
+       31  125
+
+o28 : List
+
+i29 : fpt(f, Attempts => 2, DepthOfSearch => 3, UseFSignature => true)
+
+      -- UseFSignature improves the answer a bit
+
+        1   13
+o29 = {--, ---}
+       10  125
+
+o29 : List
+
+i30 : fpt(f, Attempts => 2, DepthOfSearch => 3, UseFSignature => true,
+
+      FRegularityCheck => true) -- FRegularityCheck finds the answer
+
+       1
+o30 = --
+      10
+
+o30 : QQ
+\end{MyVerbatim}
+}
+\medspace
+
+The computations performed when {\tt UseFSignature} and {\tt FRegularityCheck} are set to {\tt true} are often slow, and often fail to improve the estimate, and for this reason, these options should be used sparingly.
+            It is often more effective to increase the values of {\tt Attempts} or {\tt DepthOfSearch} instead.
+
+{\small
+\setstretch{.67}
+\begin{MyVerbatim}
+
+i31 : f = x^7*y^5*(x + y)^5*(x^2 + y^3)^4;
+
+i32 : timing numeric fpt(f, DepthOfSearch => 3, UseFSignature => true,
+
+      FRegularityCheck => true)
+
+o32 = {.0733061, .0769231}
+      -- 2.68899 seconds
+
+o32 : Time
+
+i33 : timing numeric fpt(f, Attempts => 5, DepthOfSearch => 3) -- a better
+
+      answer in less time
+
+o33 = {.075, .0769231}
+      -- .893389 seconds
+
+o33 : Time
+
+i34 : timing fpt(f, DepthOfSearch => 4) -- the exact answer in even less
+      time
+
+       48
+o34 = ---
+      625
+      -- .361882 seconds
+
+o34 : Time
+\end{MyVerbatim}
+}
+\medspace
+
+As seen in several examples above, when the exact  $F$-pure threshold of $f$ is not found, a list containing the endpoints of an interval containing its value is returned.
+Whether that interval is open, closed, or a mixed interval depends on the options passed; if the option {\tt Verbose} is set to {\tt true}, the precise interval will be printed.
+
+{\small
+\setstretch{.67}
+\begin{MyVerbatim}
+
+i35 : f = x^7*y^5*(x + y)^5*(x^2 + y^3)^4;
+
+i36 : fpt(f, DepthOfSearch => 3, UseFSignature => true, Verbose => true)
+
+Starting fpt ...
+
+fpt is not 1 ...
+
+Verifying if special algorithms apply...
+
+Special fpt algorithms were not used ...
+
+nu has been computed: nu = nu(3,f) = 9 ...
+
+fpt lies in the interval [ nu/(p^e-1), (nu+1)/p^e ] = [ 9/124, 2/25 ] ...
+
+Starting guessFPT ...
+
+The right-hand endpoint is not the fpt ...
+
+The left-hand endpoint is not the fpt ...
+
+guessFPT narrowed the interval down to ( 9/124, 1/13 ) ...
+
+Beginning F-signature computation ...
+
+First F-signature computed: s(f,(nu-1)/p^e) = 456/15625 ...
+
+Second F-signature computed: s(f,nu/p^e) = 64/15625 ...
+
+Computed F-signature secant line intercept: 449/6125 ...
+
+F-signature intercept is an improved lower bound ...
+
+fpt failed to find the exact answer; try increasing the value of
+
+DepthOfSearch or Attempts.
+
+fpt lies in the interval [ 449/6125, 1/13 ).
+
+        449   1
+o36 = {----, --}
+       6125  13
+
+o36 : List
+\end{MyVerbatim}
+}
+\medspace
+
+\subsection*{The function {\tt isSimpleNormalCrossings}}
+As mentioned earlier, 
+when the option {\tt useSpecialFunctions} for the function {\tt fpt} is set to {\tt true}, if the polynomial $f$ is neither a diagonal polynomial, a binomial, or a form in two variables, there is a final check to verify whether $f$ is a product of factors in simple normal crossing.
+
+Suppose that $f$ has factorization $f_1^{a_i} f_2^{a_2} \cdots f_n^{a_n}$.  Recall that its factors $f_i$ are said to be in 
+\emph{simple normal crossing} at a point if, locally, they form part of a regular system of parameters.
+The function {\tt isSimpleNormalCrossings} determines whether $f$ has simple normal crossings by computing the Jacobian matrix of each subset of $\{ f_i \}_{i=1}^n$ (evaluated at the origin), and checking that these matrices have the expected rank, and that these subsets generate ideals of the appropriate height.
+
+{\small
+\setstretch{.67}
+\begin{MyVerbatim}
+
+i1 : R = ZZ/7[x, y, z];
+
+i2 : isSimpleNormalCrossing(x^3*y^2)
+
+o2 = true
+
+i3 : isSimpleNormalCrossing(x^2-y^2)
+
+o3 = true
+
+i4 : isSimpleNormalCrossing(x*y*(x-y))
+
+o4 = false
+
+i5 : isSimpleNormalCrossing(x^2-y*z)
+
+o5 = false
+\end{MyVerbatim}
+}
+\medspace
+
+%             R = ZZ/7[x,y,z];
+%             isSimpleNormalCrossing(x^3*y^2)
+%             isSimpleNormalCrossing(x^2-y^2)
+%             isSimpleNormalCrossing(x*y*(x-y))
+%             isSimpleNormalCrossing(x^2-y*z)
+
+If {\tt isSimpleNormalCrossing(f)} outputs true, then the $F$-pure threshold is easily computed, since is just the minimum of the values $1/a_i$, for $1 \leq i \leq n$.
+Note that the function {\tt factor} is called whenever {\tt isSimpleNormalCrossing} is used, which can sometimes make the verification slow.
+The user can avoid this when using {\tt fpt} by setting {\tt UseSpecialAlgorithms} to {\tt false}.
+
+The function {\tt isSimpleNormalCrossing} is exposed to the user, so can be used independent of any $F$-pure threshold calculation.  
+If the user sets its option {\tt IsLocal} to {\tt true} (its default value is {\tt false}), then the function checks whether the $f_i$ are in simple normal crossing \emph{everywhere}, which can be much slower since Jacobian ideals are computed.
+Consider the following example illustrating this functionality.
+
+{\small
+\setstretch{.67}
+\begin{MyVerbatim}
+
+i1 : R = QQ[x, y, z];
+
+i2 : f = (y - (x-1)^2)*y^2; --SNC at the origin, but not globally
+
+i3 : isSimpleNormalCrossing(f)
+
+o3 = true
+
+i4 : isSimpleNormalCrossing(f, IsLocal=>false)
+
+o4 = false
+
+i5 : g = (y-1)^2+(x-7)^2 --doesn't even pass through the origin
+
+       2    2
+o5 = x  + y  - 14x - 2y + 50
+
+o5 : R
+
+i6 : isSimpleNormalCrossing(g)
+
+o6 = true
+
+i7 : isSimpleNormalCrossing(g, IsLocal=>false)
+
+o7 = false
+
+i8 : h = x*y^2*(x+1)^3*(y-1)^4; --SNC everywhere
+
+i9 : isSimpleNormalCrossing(h)
+
+o9 = true
+
+i10 : isSimpleNormalCrossing(h, IsLocal=>false)
+
+o10 = true
+\end{MyVerbatim}
+}
+\medspace
+
+%             R = QQ[x,y,z];
+
+%             f = (y - (x-1)^2)*y^2; --SNC at the origin, but not globally
+
+%             isSimpleNormalCrossing(f)
+
+%             isSimpleNormalCrossing(f, IsLocal=>false)
+
+%             g = (y-1)^2+(x-7)^2 --doesn't even pass through the origin
+
+%             isSimpleNormalCrossing(g)
+
+%             isSimpleNormalCrossing(g, IsLocal=>false)
+
+%             h = x*y^2*(x+1)^3*(y-1)^4; --SNC everywhere
+
+%             isSimpleNormalCrossing(h)
+
+%             isSimpleNormalCrossing(h, IsLocal=>false)
+
+\newpage
+\section{Future Directions}
+\label{sec.FutureDirections}
+
+We conclude with some comments on possible improvements to the package.
+
+One natural candidate for improvement would be to extend functionality to better handle nonprincipal ideals.
+In particular, the package could be improved if it could use the test ideals $\tau(I^t)$ when $I$ is not necessarily principal.
+Fortunately, the theoretical foundation for computing such ideals has already largely been worked out in the paper \cite{SchwedeTuckerTestIdealsOfNonPrincipal}.
+However, such an improvement would necessarily require an update to the \emph{TestIdeals} package.
+
+\begin{enumerate}
+\item Add more cases to {\tt UseSpecialAlgorithms}.
+\item Add the capability to compute non-local {\tt fpt} and non-local {\tt nu} via an option.
+\item Write a function that will extract from this sequences $\{ \nu_f^{\idealm}(p^e) \}_{e=1}^{\infty}$ roots of Bernstein-Sato polynomials.  Especially, strata.
+
+\item Extend binary forms functions to handle more general $F$-thresholds (that is, with respect to diagonal ideals).
+There is one tricky theoretical things, we don't know when this process would stop.
+If we can do this, then we can compute $F$-pure thresholds of binary forms in non-standard gradings.
+Cite the paper by Daniel and Pedro \cite{HernandezTeixeiraFThresholdFunctions}.
+\end{enumerate}
+
+\bibliographystyle{skalpha}
+\bibliography{MainBib}
+
+\end{document}
+>>>>>>> c768df2d40aceec6dd5553f80fb91ea3776825d8

### 2019-06-07 Fsing/FThresholdsPaper/FThresholds.tex

--- 2019-06-07 Fsing/FThresholdsPaper/FThresholds.tex
@@
 set to {\tt true} (the default value), {\tt fpt} first checks whether $f$ is a monomial, a diagonal polynomial, a binomial, a form in two variables, or a product of factors in simple normal crossing, in that order.
-
-If $f = x_1^{a_n}\cdots x_n^{a_n}$, then its $F$-pure threshold is simply $\min \{ 1/a_1, \ldots, 1/a_n \}$.  When $f$ is a diagonal polynomial, a binomial, or a form in two variables, 
-algorithms of Hern\'andez \cite{HernandezFInvariantsOfDiagonalHyp, HernandezFPureThresholdOfBinomial}, or Hern\'andez and Teixeira \cite{HernandezTeixeiraFThresholdFunctions},  are executed to compute the $F$-pure threshold.
-We note that algorithms for computing $F$-pure thresholds of binomials in certain special characteristics appear in \cite{ShibutaTakagiLCThresholds}.
+When $f$ is a monomial, say, $x_1^{a_n}\cdots x_n^{a_n}$, then its $F$-pure threshold is quickly computed as the minimum among the $1/a_i$.
+When $f$ is a a diagonal polynomial, a binomial, a form in two variables, 
+algorithms of Hern\'andez \cite{HernandezFInvariantsOfDiagonalHyp, HernandezFPureThresholdOfBinomial}, or Hern\'andez and Teixeira \cite{HernandezTeixeiraFThresholdFunctions},  are executed to compute the $F$-pure threshold (cf.
+\cite{ShibutaTakagiLCThresholds}).
 

### 2019-06-07 Fsing/FThresholdsPaper/FThresholds.tex
Sanity check
updates
Test
Updates to Section 3 of the paper

@@
 
+SANITY TEST FOR DANIEL
+DANIEL MODIFYING THE PAPER AFTER EMILY
+
 This paper describes the \emph{Macaulay2} \cite{M2} package \emph{FrobeniusThresholds} \cite{FThresholdsPackage}, which provides tools for computing certain fundamental invariants arising in positive characteristic commutative algebra.
@@
 
-\subsection*{The option {\tt UseSpecialAlgorithms} for the {\tt fpt} function}
+\subsection{The option {\tt UseSpecialAlgorithms} for the {\tt fpt} function}
 
@@
 If this command returns {\tt true}, the $F$-pure threshold can easily be computed, and {\tt fpt} returns this value.
-For more detail on the function {\tt isSimpleNormalCrossing} and on computing the $F$-pure threshold of a polynomial with simple normal crossings, please see the end of this section.
-
-\subsection*{Searching for the $F$-pure threshold when no special algorithm applies}
+For more detail on the function {\tt isSimpleNormalCrossing} and on computing the $F$-pure threshold of a polynomial with simple normal crossings, please see Section \ref{subsec.SNC}.
+
+\subsection{How {\tt fpt} proceeds when no special algorithm applies}
 
@@
 
-\subsection*{The function {\tt isSimpleNormalCrossings}}
+\subsection{The function {\tt isSimpleNormalCrossings}} \label{subsec.SNC}
 As mentioned earlier, 

### 2019-06-07 Fsing/FThresholdsPaper/FThresholds.tex
Changes to Sectio 4 of the paper

--- 2019-06-07 Fsing/FThresholdsPaper/FThresholds.tex
@@
 set to {\tt true} (the default value), {\tt fpt} first checks whether $f$ is a monomial, a diagonal polynomial, a binomial, a form in two variables, or a product of factors in simple normal crossing, in that order.
-When $f$ is a monomial, say, $x_1^{a_n}\cdots x_n^{a_n}$, then its $F$-pure threshold is quickly computed as the minimum among the $1/a_i$.
-When $f$ is a a diagonal polynomial, a binomial, a form in two variables, 
-algorithms of Hern\'andez \cite{HernandezFInvariantsOfDiagonalHyp, HernandezFPureThresholdOfBinomial}, or Hern\'andez and Teixeira \cite{HernandezTeixeiraFThresholdFunctions},  are executed to compute the $F$-pure threshold (cf.
-\cite{ShibutaTakagiLCThresholds}).
+
+If $f$ is a monomial, then its $F$-pure threshold is simply the minimum of the reciprocal of the exponent of each variable in $f$.
+When $f$ is a diagonal polynomial, a binomial, or a form in two variables, 
+algorithms of Hern\'andez \cite{HernandezFInvariantsOfDiagonalHyp, HernandezFPureThresholdOfBinomial}, or Hern\'andez and Teixeira \cite{HernandezTeixeiraFThresholdFunctions},  are executed to compute the $F$-pure threshold.
+Algorithms for computing $F$-pure thresholds of binomials also appear in \cite{ShibutaTakagiLCThresholds}, though they are only valid in certain special characteristics.
 
@@
 
-\subsection*{Searching for the $F$-pure threshold when no special algorithm applies}
+\subsection*{The {\tt fpt} function when no special algorithm applies}
 

### 2019-06-07 Fsing/FThresholdsPaper/FThresholds.tex
Edits to Section 3 of paper

--- 2019-06-07 Fsing/FThresholdsPaper/FThresholds.tex
@@
 
-In the remainder of this section, we describe the {\tt fpt} function when no special algorithm is available, or {\tt UseSpecialAlgorithms} is set to {\tt false},  as well as the roles of the options {\tt DepthOfSearch}, and {\tt Attempts}, both nonnegative integers.
-
-In this case, very roughly speaking, the {\tt fpt} function will either compute, and output, the exact value of the $F$-pure threshold of $f$, and otherwise recursively compute a finite sequence of lower and upper bounds for this value, and output the last of these, which will be the tightest among all computed.
+In the remainder of this section, we explain how the {\tt fpt} function proceeds when no special algorithm is available, or when {\tt UseSpecialAlgorithms} is set to {\tt false}, and describe the roles of the options {\tt DepthOfSearch} and {\tt Attempts}, whose values are both nonnegative integers.
+
+In this case, the {\tt fpt} function either computes, and outputs, the exact value of the $F$-pure threshold of $f$, or otherwise recursively computes a finite sequence of lower and upper bounds for this value, and outputs the last of these, which will be the tightest among all computed.
 The value of the option {\tt DepthOfSearch} determines the precision of the initial set of bounds, and the option {\tt Attempts}, in conjunction with some various subroutines, determines whether, and how, to produce new, tighter bounds from the previous ones.
 
-In more detail, let $e$ denote the value of the option {\tt DepthOfSearch}, which conservatively defaults to {\tt 1}.
+More specifically, let $e$ denote the value of the option {\tt DepthOfSearch}, which conservatively defaults to {\tt 1}.
 The {\tt fpt} function first computes $\nu=\nu_f(p^e)$, which agrees with the output of {\tt nu(e,f)}.

### 2019-06-07 Fsing/FThresholdsPaper/FThresholds.tex
Changes to documentation.
Updates to Section 3 of paper

@@
 
-The {\tt fpt} function has the option {\tt UseSpecialAlgorithms}.  When
+The {\tt fpt} function has the option {\tt UseSpecialAlgorithms}, which, when
 set to {\tt true} (the default value), {\tt fpt} first checks whether $f$ is a monomial, a diagonal polynomial, a binomial, a form in two variables, or a product of factors in simple normal crossing, in that order.
@@
 
-i11 : fpt(L, m) == o7
+i11 : fpt(L, m) == o8
 
@@
 
-In the remainder of this section, we explain how the {\tt fpt} function proceeds when no special algorithm is available, or when {\tt UseSpecialAlgorithms} is set to {\tt false}, and describe the roles of the options {\tt DepthOfSearch} and {\tt Attempts}, whose values are both nonnegative integers.
+In the remainder of this section, we explain how the function  {\tt fpt} proceeds when no special algorithm is available, or when {\tt UseSpecialAlgorithms} is set to {\tt false}, and describe the roles of the options {\tt DepthOfSearch} and {\tt Attempts}, whose values are both nonnegative integers.
 
@@
 
-i11 : f = x^2*(x + y)^3*(x + 3*y^2)^5;
-
-i12 : fpt(f, Attempts => 0) -- a bad estimate
+i12 : f = x^2*(x + y)^3*(x + 3*y^2)^5;
+
+i13 : fpt(f, Attempts => 0) -- a bad estimate
 
           1
-o12 = {0, -}
+o13 = {0, -}
           5
 
-o12 : List
-
-i13 : fpt(f, Attempts => 0, DepthOfSearch => 3) -- a better estimate
+o13 : List
+
+i14 : fpt(f, Attempts => 0, DepthOfSearch => 3) -- a better estimate
 
         21   22
-o13 = {---, ---}
+o14 = {---, ---}
        124  125
 
-o13 : List
-
-i14 : fpt(f, Attempts => 1, DepthOfSearch => 3) -- the right-hand
+o14 : List
+
+i15 : fpt(f, Attempts => 1, DepthOfSearch => 3) -- the right-hand
 
@@
        22
-o14 = ---
+o15 = ---
       125
 
-o14 : QQ
+o15 : QQ
 
@@
 
-i15 : f = x^6*y^4 + x^4*y^9 + (x^2 + y^3)^3;
-
-i16 : fpt(f, Attempts => 1, DepthOfSearch => 3)
+i16 : f = x^6*y^4 + x^4*y^9 + (x^2 + y^3)^3;
+
+i17 : fpt(f, Attempts => 1, DepthOfSearch => 3)
 
        17   7
-o16 = {--, --}
+o17 = {--, --}
        62  25
 
-o16 : List
-
-i17 : fpt(f, Attempts => 2, DepthOfSearch => 3) -- the left-hand endpoint
-
+o17 : List
+
+i18 : fpt(f, Attempts => 2, DepthOfSearch => 3) -- the left-hand endpoint
       nu/(p^e-1) is the F-pure threshold
@@
       17
-o17 = --
+o18 = --
       62
 
-o17 : QQ
-
-\end{MyVerbatim}
-}
-
-If neither endpoint is the $F$-pure threshold and {\tt Attempts} is set to more than {\tt 2}, then  additional checks are performed at certain numbers within the interval, chosen according to the criteria determined by the value of the option {\tt GuessStrategy}.
-We refer the reader for the documentation of this strategy for more details.
-
-{\color{red}  This will need to be updated.  Maybe look at Pedro's new documentation.}
-
-{\small
-\setstretch{.67}
-\begin{MyVerbatim}
-
-i18 : f = x^3*y^11*(x + y)^8*(x^2 + y^3)^8;
-
-i19 : fpt(f, DepthOfSearch => 3, Attempts => 2)
+o18 : QQ
+
+\end{MyVerbatim}
+}
+
+If neither endpoint is the $F$-pure threshold and {\tt Attempts} is set to more than {\tt 2}, then  additional checks are performed at certain numbers within the interval.
+First, a number in the interval is selected, according to criteria specified by the value of the option {\tt GuessStrategy}; we refer the reader for the documentation of this option for more details.
+Then the function {\tt compareFPT} is used to test that number.
+If that "guess" is correct, its value is returned; otherwise, the data returned by {\tt compareFPT} is used to narrow down the interval, and this process is repeated as many times as specified by {\tt Attempts}.
+
+{\small
+\setstretch{.67}
+\begin{MyVerbatim}
+
+i19 : f = x^3*y^11*(x + y)^8*(x^2 + y^3)^8;
+
+i20 : fpt(f, DepthOfSearch => 3, Attempts => 2)
 
         3   7
-o19 = {--, ---}
+o20 = {--, ---}
        62  125
 
-o19 : List
-
-i20 : fpt(f, DepthOfSearch => 3, Attempts => 3) -- an additional check
-
-      sharpens the estimate
-
-        3   1
-o20 = {--, --}
-       62  18
-
 o20 : List
 
-i21 : fpt(f, DepthOfSearch => 3, Attempts => 4) -- and one more finds
-
-      the answer
+i21 : fpt(f, DepthOfSearch => 3, Attempts => 4) -- more attempts *always* 
+      improve the estimate
+
+        1   4
+o21 = {--, --}
+       20  75
+
+o21 : List
+
+i22 : fpt(f, DepthOfSearch => 3, Attempts => 4, GuessStrategy => denominator) 
+      -- the exact answer, after a change of strategy
 
        1
-o21 = --
+o22 = --
       19
 
-o21 : QQ
+o22 : QQ
 \end{MyVerbatim}

### 2019-06-07 Fsing/FThresholdsPaper/FThresholds.tex
Started to write IsLocal for nu.

--- 2019-06-07 Fsing/FThresholdsPaper/FThresholds.tex
@@
 
+The last option we describe for {\tt nu} is {\tt IsLocal}.
+When {\tt IsLocal => false} (the default is {\tt true}), then {\tt nu} ignores the option {\tt ContainmentTest} and the input ideal {\tt I}, and instead computes
+\[
+\min_{J \in \mathfrak{m}-\Spec R} (\nu_I^J(p^e))
+\]
+This is done by instead of computing for which $n$ we have $I^{n} \subseteq J^{[p^e]}$ (or equivalently, $(I^n)^{[1/p^e]} \subseteq J$), it computes for which $n$ we have $(I^n)^{[1/p^e]}$ is a unit ideal.
+
 % R = ZZ/3[x,y];

### 2019-06-07 Fsing/FThresholdsPaper/FThresholds.tex
Work on the paper

@@
 
-%This is for Karl
-%{\color{red}  Point out for people interested in computing log canonical thresholds:  Zhixian Zhou apparently proved in her thesis that the $F$-pure threshold for hypersurfaces is always a lower bound for the log canonical threshold.
-Therefore, this package effectively computes such lower bounds, and is much faster than the \emph{Dmodules} package, which appears to be the only package in Macaulay2 that computes log canonical thresholds.}
-
-SANITY TEST FOR DANIEL
-DANIEL MODIFYING THE PAPER AFTER EMILY
-
 This paper describes the \emph{Macaulay2} \cite{M2} package \emph{FrobeniusThresholds} \cite{FThresholdsPackage}, which provides tools for computing certain fundamental invariants arising in positive characteristic commutative algebra.
@@
 
-Along these lines, the \emph{$F$-pure threshold} (fpt)%associated to an element of $R$
-was defined in analogy with the \emph{log canonical threshold} (lct) \cite{TakagiWatanabeFPureThresh}, and
+Along these lines, the \emph{$F$-pure threshold} %associated to an element of $R$
+was defined in analogy with the \emph{log canonical threshold} \cite{TakagiWatanabeFPureThresh}, and
 %The $F$-pure threshold of the pair $(R, f)$ is the supremum over all $t$ for which $(R, f^t)$ is $F$-pure.
@@
 
-Unfortunately, the $F$-pure threshold is typically difficult to calculate, even in many concrete cases.
-It is also not so well understood from the perspective of reduction to prime characteristic.
-Nevertheless, $F$-pure thresholds have been the focus of intense study over the past 15 years, and the \emph{Macaulay2} package \emph{FrobeniusThresholds} is centered around calculating and estimating the $F$-pure threshold and other $F$-thresholds, with the function {\tt fpt} at its core.
-
-The $F$-pure threshold can also be used to provide a lower bound for the log canonical threshold in characteristic zero.
-Indeed, Z.~Zhu showed in \cite[Corollary 4.2]{ZhuLogCanoincalThresholdsInPositiveChar} that if $f \in \bQ[x_1, \dots, x_n]$ is reduced modulo $p > 0$ to obtain $f_p = f\;\mathrm{mod}\;p \in \bF_p[x_1, \dots, x_n]$, then $\fpt(f_p) \leq \lct(f)$.
-There is a general purpose implementation of log canonical thresholds in the \emph{Dmodules} package by A.~Leykin and H.~Tsai \cite{DmodulesSource} and a package \emph{MultiplierIdeals} by Z.~Teitler, B.~Snapp and C.~Raicu \cite{MultiplierIdealsPackage}, which computes log canonical thresholds for special cases (monomial ideals, hyperplane arrangements, generic determinantal ideals, and certain binomial ideals), see also the paper \cite{MultiplierIdealsArticle}.
-However, our general purpose implementation of ${\tt fpt}$ in small characteristic is typically much faster than {\tt lct}, the general purpose function from \emph{Dmodules} which computes the log canonical threshold.
+Though the $F$-pure threshold is defined in analogy with the log canonical threshold, their connection extends beyond mere analogy.
+For example, suppose $h$ is a polynomial with integer coefficients, and that $h_p$ is the polynomial obtained by reducing the coefficients of $h$ modulo a prime $p$.
+Then, the $F$-pure thresholds of the reductions $h_p$ limit to the log canonical threshold of $h$ as $p$ tends to infinity \cite{HaraYoshidaGeneralizationOfTightClosure}.
+A related result is that of Z.~Zhu, who proved in  \cite[Corollary 4.2]{ZhuLogCanoincalThresholdsInPositiveChar} that the log canical threshold of $h$ at least the $F$-pure threshold of any reduction $h_p$.
+
+This latter result is interesting from a computational perspective, in that it provides lower bounds for log canonical thresholds.
+Furthermore, though there is a general purpose implementation of an algorithm for computing log canonical thresholds in the \emph{Dmodules} package by A.~Leykin and H.~Tsai \cite{DmodulesSource}, it happens that the function for computing $F$-pure thresholds contained in the \emph{FrobeniusThresholds} package is typically much faster, especially so in lower characteristic.
+Note that the  \emph{MultiplierIdeals}  package  by Z.~Teitler, B.~Snapp and C.~Raicu also computes log canonical thresholds in many special cases, including monomial ideals, hyperplane arrangements, generic determinantal ideals, and certain binomial ideals \cite{MultiplierIdealsPackage, MultiplierIdealsArticle}.
+
+In summary,  the $F$-pure threshold is an interesting numerical invariant, and is related to many other such measures of singularity across all characteristics.
+Unfortunately, it is typically difficult to calculate, even in many concrete cases.
+Nevertheless, $F$-pure thresholds have been the focus of intense study over the past 15 years, and the package \emph{FrobeniusThresholds} is centered on calculating and estimating the $F$-pure threshold and other $F$-thresholds, with the function {\tt fpt} at its core.
 

### 2019-06-07 Fsing/FThresholdsPaper/FThresholds.tex
Try to fix crlf
Added a paragraph.
Fixed a dumb issue.
Replaced Section 3 with updated version

@@
       17
-o17 = --
+o18 = --
       62
 
-o17 : QQ
-
-\end{MyVerbatim}
-}
-
-If neither endpoint is the $F$-pure threshold and {\tt Attempts} is set to more than {\tt 2}, then  additional checks are performed at certain numbers within the interval, chosen according to the criteria determined by the value of the option {\tt GuessStrategy}.
-We refer the reader for the documentation of this strategy for more details.
-
-{\color{red}  This will need to be updated.  Maybe look at Pedro's new documentation.}
-
-{\small
-\setstretch{.67}
-\begin{MyVerbatim}
-
-i18 : f = x^3*y^11*(x + y)^8*(x^2 + y^3)^8;
-
-i19 : fpt(f, DepthOfSearch => 3, Attempts => 2)
+o18 : QQ
+
+\end{MyVerbatim}
+}
+
+If neither endpoint is the $F$-pure threshold and {\tt Attempts} is set to more than {\tt 2}, then  additional checks are performed at certain numbers within the interval.
+First, a number in the interval is selected, according to criteria specified by the value of the option {\tt GuessStrategy}; we refer the reader for the documentation of this option for more details.
+Then the function {\tt compareFPT} is used to test that number.
+If that "guess" is correct, its value is returned; otherwise, the data returned by {\tt compareFPT} is used to narrow down the interval, and this process is repeated as many times as specified by {\tt Attempts}.
+
+{\small
+\setstretch{.67}
+\begin{MyVerbatim}
+
+i19 : f = x^3*y^11*(x + y)^8*(x^2 + y^3)^8;
+
+i20 : fpt(f, DepthOfSearch => 3, Attempts => 2)
 
         3   7
-o19 = {--, ---}
+o20 = {--, ---}
        62  125
 
-o19 : List
-
-i20 : fpt(f, DepthOfSearch => 3, Attempts => 3) -- an additional check
-
-      sharpens the estimate
+o20 : List
+
+i21 : fpt(f, DepthOfSearch => 3, Attempts => 4) -- more attempts *always* 
+      improve the estimate
+
+        1   4
+o21 = {--, --}
+       20  75
+
+o21 : List
+
+i22 : fpt(f, DepthOfSearch => 3, Attempts => 4, GuessStrategy => denominator) 
+      -- the exact answer, after a change of strategy
+
+       1
+o22 = --
+      19
+
+o22 : QQ
+\end{MyVerbatim}
+}
+\medspace
+
+The option {\tt Bounds} allows the user to specify known lower and upper bounds for the $F$-pure threshold of $f$, in order to speed up computations or to refine previously obtained estimates.
+
+{\small
+\setstretch{.67}
+\begin{MyVerbatim}
+
+i23 : f = x^7*y^5*(x + y)^5*(x^2 + y^3)^4;
+
+i24 : fpt(f, DepthOfSearch => 3, Attempts => 5)
 
         3   1
-o20 = {--, --}
-       62  18
-
-o20 : List
-
-i21 : fpt(f, DepthOfSearch => 3, Attempts => 4) -- and one more finds
-
-      the answer
-
-       1
-o21 = --
-      19
-
-o21 : QQ
-\end{MyVerbatim}
-}
-\medspace
-
-If {\tt guessFPT} is unsuccessful and {\tt UseFSignature} is set to {\tt true}, then the {\tt fpt} function proceeds to use the convexity of the $F$-signature function and a secant line argument to attempt to narrow down the interval bounding the $F$-pure threshold.
-
-{\small
-\setstretch{.67}
-\begin{MyVerbatim}
-
-i22 : f = x^5*y^6*(x + y)^9*(x^2 + y^3)^4;
-
-i23 : fpt(f, DepthOfSearch => 3)
-
-        2   1
-o23 = {--, --}
-       31  14
-
-o23 : List
-
-i24 : fpt(f, DepthOfSearch => 3, UseFSignature => true)
-
-        181   1
-o24 = {----, --}
-       2750  14
+o24 = {--, --}
+       40  13
 
@@
 
-i25 : numeric o23
-
-o25 = {.0645161, .0714286}
+i25 : fpt(f, DepthOfSearch => 3, Attempts => 5, Bounds => oo)
+
+        24   1
+o25 = {---, --}
+       313  13
 
 o25 : List
-
-i26 : numeric o24 -- UseFSignature sharpened the estimate a bit
-
-o26 = {.0658182, .0714286}
-
-o26 : List
-\end{MyVerbatim}
-}
-\medspace
-
-When {\tt FRegularityCheck} is set to {\tt true} and no exact answer has been found, a final check is run to verify whether the final lower bound for the $F$-pure threshold is the exact answer (if it has not already been eliminated as a possibility).
-
-{\small
-\setstretch{.67}
-\begin{MyVerbatim}
-
-i27 : f = (x + y)^4*(x^2 + y^3)^6;
-
-i28 : fpt( f, Attempts => 2, DepthOfSearch => 3 )
-
-        3   13
-o28 = {--, ---}
-       31  125
+\end{MyVerbatim}
+}
+\medspace
+
+% f = x^7*y^5*(x + y)^5*(x^2 + y^3)^4;
+% fpt(f, DepthOfSearch => 3, Attempts => 5)
+% fpt(f, DepthOfSearch => 3, Attempts => 5, Bounds => oo)
+
+If {\tt guessFPT} is unsuccessful and {\tt FinalAttempt} is set to {\tt true}, the {\tt fpt} function proceeds to use the convexity of the $F$-signature function and a secant line argument to attempt to narrow down the interval bounding the $F$-pure threshold.
+If successful, the new lower bound may coincide with the upper bound, in which case we can conclude that it is the desired $F$-pure threshold.
+If this is not the case, an $F$-regularity check is done at the new lower bound, to verify if it is the $F$-pure threshold.
+
+{\small
+\setstretch{.67}
+\begin{MyVerbatim}
+
+i26 : f = -2*x^10*y^5 - x^5*y^9 - 2*x^3*y^10 + 2*x^2*y^8 - 2*x*y^9;
+
+i27 : numeric fpt(f, DepthOfSearch => 3)
+
+o27 = {.153226, .158333}
+
+o27 : List
+
+i28 : numeric fpt(f, DepthOfSearch => 3, FinalAttempt => true)
+      -- FinalAttempt improves the estimate slightly
+
+o28 = {.153461, .158333}
 
 o28 : List
-
-i29 : fpt(f, Attempts => 2, DepthOfSearch => 3, UseFSignature => true)
-
-      -- UseFSignature improves the answer a bit
-
-        1   13
-o29 = {--, ---}
-       10  125
-
-o29 : List
-
-i30 : fpt(f, Attempts => 2, DepthOfSearch => 3, UseFSignature => true,
-
-      FRegularityCheck => true) -- FRegularityCheck finds the answer
-
-       1
-o30 = --
-      10
-
-o30 : QQ
-\end{MyVerbatim}
-}
-\medspace
-
-The computations performed when {\tt UseFSignature} and {\tt FRegularityCheck} are set to {\tt true} are often slow, and often fail to improve the estimate, and for this reason, these options should be used sparingly.
-            It is often more effective to increase the values of {\tt Attempts} or {\tt DepthOfSearch} instead.
-
-{\small
-\setstretch{.67}
-\begin{MyVerbatim}
-
-i31 : f = x^7*y^5*(x + y)^5*(x^2 + y^3)^4;
-
-i32 : timing numeric fpt(f, DepthOfSearch => 3, UseFSignature => true,
-
-      FRegularityCheck => true)
-
-o32 = {.0733061, .0769231}
-      -- 2.68899 seconds
+\end{MyVerbatim}
+}
+\medspace
+
+% f = -2*x^10*y^5 - x^5*y^9 - 2*x^3*y^10 + 2*x^2*y^8 - 2*x*y^9;
+% numeric fpt(f, DepthOfSearch => 3)
+% numeric fpt(f, DepthOfSearch => 3, FinalAttempt => true) -- FinalAttempt improves the estimate slightly
+
+The computations performed when {\tt FinalAttempt} is set to {\tt true} are often slow, and often fail to improve the estimate, and for this reason, this option should be used sparingly.
+It is often more effective to increase the values of {\tt Attempts} or {\tt DepthOfSearch}, instead.
+
+{\small
+\setstretch{.67}
+\begin{MyVerbatim}
+
+i29 : f = -2*x^10*y^5 - x^5*y^9 - 2*x^3*y^10 + 2*x^2*y^8 - 2*x*y^9;
+
+i30 : timing numeric fpt(f, DepthOfSearch => 3, FinalAttempt => true)
+
+o30 = {.153461, .158333}
+      -- 1.29156 seconds
+
+o30 : Time
+
+i31 : timing numeric fpt(f, DepthOfSearch => 3, Attempts => 4) -- a better 
+      answer in less time
+
+o31 = {.153333, .158333}
+      -- .554321 seconds
+
+o31 : Time
+
+i32 : timing fpt(f, DepthOfSearch => 4) -- the exact answer in even less 
+      time
+
+       98
+o32 = ---
+      625
+      -- .274657 seconds
 
 o32 : Time
-
-i33 : timing numeric fpt(f, Attempts => 5, DepthOfSearch => 3) -- a better
-
-      answer in less time
-
-o33 = {.075, .0769231}
-      -- .893389 seconds
-
-o33 : Time
-
-i34 : timing fpt(f, DepthOfSearch => 4) -- the exact answer in even less
-      time
-
-       48
-o34 = ---
-      625
-      -- .361882 seconds
-
-o34 : Time
-\end{MyVerbatim}
-}
-\medspace
-
-As seen in several examples above, when the exact  $F$-pure threshold of $f$ is not found, a list containing the endpoints of an interval containing its value is returned.
-Whether that interval is open, closed, or a mixed interval depends on the options passed; if the option {\tt Verbose} is set to {\tt true}, the precise interval will be printed.
-
-{\small
-\setstretch{.67}
-\begin{MyVerbatim}
-
-i35 : f = x^7*y^5*(x + y)^5*(x^2 + y^3)^4;
-
-i36 : fpt(f, DepthOfSearch => 3, UseFSignature => true, Verbose => true)
+\end{MyVerbatim}
+}
+\medspace
+
+% f = -2*x^10*y^5 - x^5*y^9 - 2*x^3*y^10 + 2*x^2*y^8 - 2*x*y^9;
+% timing numeric fpt(f, DepthOfSearch => 3, FinalAttempt => true)
+% timing numeric fpt(f, DepthOfSearch => 3, Attempts => 4) -- a better answer in less time
+% timing fpt(f, DepthOfSearch => 4) -- the exact answer in even less time
+
+As seen in several examples above, when the exact answer is not found, a list containing the endpoints of an interval containing the $F$-pure threshold of $f$ is returned.
+Whether that interval is open, closed, or a mixed interval depends on the options passed; if the option {\tt Verbose} is set to true, the precise interval will be printed.
+{\small
+\setstretch{.67}
+\begin{MyVerbatim}
+
+i33 : f = x^7*y^5*(x + y)^5*(x^2 + y^3)^4;
+
+i34 : fpt(f, DepthOfSearch => 3, FinalAttempt => true, Verbose => true)
 
@@
 
-guessFPT narrowed the interval down to ( 9/124, 1/13 ) ...
+guessFPT narrowed the interval down to ( 3/40, 2/25 ) ...
 
@@
 
-F-signature intercept is an improved lower bound ...
+F-signature computation failed to find an improved lower bound ...
 
 fpt failed to find the exact answer; try increasing the value of 
-
 DepthOfSearch or Attempts.
 
-fpt lies in the interval [ 449/6125, 1/13 ).
-
-        449   1
-o36 = {----, --}
-       6125  13
-
-o36 : List
-\end{MyVerbatim}
-}
-\medspace
+fpt lies in the interval ( 3/40, 2/25 ).
+
+        3   2
+o34 = {--, --}
+       40  25
+
+o34 : List
+\end{MyVerbatim}
+}
+\medspace
+
+Finally, we point out that one can set the option {\tt IsLocal} from its default value of {\tt true} to {\tt false}, to compute the $F$-pure threshold globally.
+In other words, it computes the minimum of the $F$-pure threshold at all maximal ideals.
+
+{\small
+\setstretch{.67}
+\begin{MyVerbatim}
+
+i1 : R = ZZ/7[x,y];
+
+i2 : f = (y-1)^2-(x-1)^3;
+
+i3 : fpt(f, IsLocal => false)
+
+     5
+o3 = -
+     6
+
+o3 : QQ
+
+i4 : fpt(f)
+
+o4 = infinity
+
+o4 : InfiniteNumber
+\end{MyVerbatim}
+}
+\medspace
+% R = ZZ/7[x,y];
+% f = (y-1)^2-(x-1)^3;
+% fpt(f, IsLocal => false)
+% fpt(f)
+
+\noindent In this case, most options enabled by {\tt UseSpecialAlgorithms => true}
+are ignored except for the check for simple normal crossings.  {\tt FinalCheck => true}
+is also ignored.
 

### 2019-06-07 Fsing/FThresholdsPaper/FThresholds.tex
added an example
Saving files before refresh
Small changes.

@@
 
+\medspace
 {\small
@@
 This is done by instead of computing for which $n$ we have $I^{n} \subseteq J^{[p^e]}$ (or equivalently, $(I^n)^{[1/p^e]} \subseteq J$), it computes for which $n$ we have $(I^n)^{[1/p^e]}$ is a unit ideal.
+
+\medspace
+{\small
+\setstretch{.67}
+\begin{MyVerbatim}
+    i1 : R = ZZ/7[x,y];
+
+    i2 : f = (x-1)^3 - (y-2)^2;
+
+    i3 : nu(1, f)
+
+    o3 = infinity
+
+    o3 : InfiniteNumber
+
+    i4 : nu(1, f, IsLocal => false)
+
+    o4 = 5
+
+    i5 : nu(1, x^3-y^2)
+
+    o5 = 5
+
+    o5 : QQ
+\end{MyVerbatim}
+}
 
@@
 
-The {\tt fpt} function has the option {\tt UseSpecialAlgorithms}, which, when
-set to {\tt true} (the default value), {\tt fpt} first checks whether $f$ is a monomial, a diagonal polynomial, a binomial, a form in two variables, or a product of factors in simple normal crossing, in that order.
-
-If $f$ is a monomial, then its $F$-pure threshold is simply the minimum of the reciprocal of the exponent of each variable in $f$.
-When $f$ is a diagonal polynomial, a binomial, or a form in two variables, 
-algorithms of Hern\'andez \cite{HernandezFInvariantsOfDiagonalHyp, HernandezFPureThresholdOfBinomial}, or Hern\'andez and Teixeira \cite{HernandezTeixeiraFThresholdFunctions},  are executed to compute the $F$-pure threshold.
+The {\tt fpt} function has the option {\tt UseSpecialAlgorithms}, which, when set to {\tt true} (its default value), tells {\tt fpt} to first check whether $f$ is a diagonal polynomial, a binomial, a form in two variables, or a product of factors in simple normal crossing, in that order.
+
+%If $f$ is a monomial, then its $F$-pure threshold is simply the minimum of the reciprocal of the exponent of each variable in $f$.
+When $f$ is a diagonal polynomial, a binomial, or a form in two variables, algorithms of Hern\'andez \cite{HernandezFInvariantsOfDiagonalHyp, HernandezFPureThresholdOfBinomial}, or Hern\'andez and Teixeira \cite{HernandezTeixeiraFThresholdFunctions},  are executed to compute the $F$-pure threshold.
 Algorithms for computing $F$-pure thresholds of binomials also appear in \cite{ShibutaTakagiLCThresholds}, though they are only valid in certain special characteristics.
 
-{\small
-\setstretch{.67}
-\begin{MyVerbatim}
-
-i4 : fpt(x^3*y^4*z^5) -- a monomial
-
-      1
-o4 = -
-      5
+\medspace
+{\small
+\setstretch{.67}
+\begin{MyVerbatim}
+i4 : fpt(x^17 + y^20 + z^24) -- a diagonal polynomial
+
+      94
+o4 = ---
+     625
 
@@
 
-i5 : fpt(x^17 + y^20 + z^24) -- a diagonal polynomial
-
-      94
-o5 = ---
-     625
-
-i6 : fpt(x^2*y^6*z^10 + x^10*y^5*z^3) -- a binomial
+i5 : fpt(x^2*y^6*z^10 + x^10*y^5*z^3) -- a binomial
 
       997
-o6 = ----
+o5 = ----
      6250
 
-o6 : QQ
-
-i7 : ZZ/5[x,y];
-
-i8 : fpt(x^2*y^6*(x + y)^9*(x + 3*y)^10) -- a form in two variables
+o5 : QQ
+
+i6 : ZZ/5[x,y];
+
+i7 : fpt(x^2*y^6*(x + y)^9*(x + 3*y)^10) -- a form in two variables
 
       5787
-o8 = -----
+o7 = -----
      78125
 
-o8 : QQ
-\end{MyVerbatim}
-}
-\medspace
-
-The above noted algorithm for computing the $F$-pure threshold of a binary form $f$ requires factoring $f$ into linear forms, and {\tt fpt} can sometimes hang when attempting that factorization.
-For this reason, when a factorization is already known, the user can pass to {\tt fpt} a list containing all the pairwise prime linear factors of $f$, and a list containing their respective multiplicities.
-
-{\small
-\setstretch{.67}
-\begin{MyVerbatim}
-
-i9 : L = {x, y, x + y, x + 3*y};
-
-i10 : m = {2, 6, 9, 10};
-
-i11 : fpt(L, m) == o8
-
-o11 = true
+o7 : QQ
+\end{MyVerbatim}
+}
+\medspace
+
+The above noted algorithm for computing the $F$-pure threshold of a binary form $f$ requires factoring $f$ into linear forms, and {\tt fpt} can sometimes hang when attempting that factorization, when it happens in a Galois field of excessively large order.
+This is a situation when the user will want to set the option \texttt{UseSpecialAlgorithms} to \texttt{false}.
+However, when a factorization is already known, the user can pass to {\tt fpt} a list containing all the pairwise prime linear factors of $f$, and a list containing their respective multiplicities.
+
+\medspace
+{\small
+\setstretch{.67}
+\begin{MyVerbatim}
+i8 : fpt({x, y, x + y, x + 3*y}, {2, 6, 9, 10}) == oo
+
+o8 = true
 \end{MyVerbatim}
@@
 Whether that interval is open, closed, or a mixed interval depends on the options passed; if the option {\tt Verbose} is set to true, the precise interval will be printed.
+
+\medspace
 {\small
@@
 
-\newpage
+%\newpage
 \section{Future Directions}

### 2019-06-07 Fsing/FThresholdsPaper/FThresholds.tex

@@
 This implies that when searching for the maximal exponent defining {\tt nu(e,I,J)} for positive $e$, it is safe to start at $p$ times the output of {\tt nu(e-1,I,J)}, and one needn't search too far past this number.
-This also suggests that the most efficient way to compute {\tt nu(e,I,J)} is to compute, successively, {\tt nu(s,I,J)}, for each $s = 0,\ldots,e$.
+This also suggests that the most efficient way to compute {\tt nu(e,I,J)} is to compute, successively, {\tt nu(s,I,J)}, for each integer $s = 0,\ldots,e$.
 This is indeed how the computation is done in most cases.
@@
 
-%\newpage
+\newpage
 \section{Future Directions}
@@
 \item Add more cases to {\tt UseSpecialAlgorithms}.
-\item Add the capability to compute non-local {\tt fpt} and non-local {\tt nu} via an option.
+%\item Add the capability to compute non-local {\tt fpt} and non-local {\tt nu} via an option.
 \item Write a function that will extract from this sequences $\{ \nu_f^{\idealm}(p^e) \}_{e=1}^{\infty}$ roots of Bernstein-Sato polynomials.  Especially, strata.
@@
 
+\newpage
 \bibliographystyle{skalpha}

### 2019-06-07 Fsing/FThresholdsPaper/FThresholds.tex
Minor changes

@@
 The last option we describe for {\tt nu} is {\tt IsLocal}.
-When {\tt IsLocal => false} (the default is {\tt true}), then {\tt nu} ignores the option {\tt ContainmentTest} and the input ideal {\tt I}, and instead computes
+When the value of {\tt IsLocal} is set to false (the default is {\tt true}), then {\tt nu} ignores the option {\tt ContainmentTest} and the input ideal {\tt I}, and instead computes
 \[
@@
 Moreover, the function {\tt compareFPT} provides further information about the relationship between $t$ and the $F$-pure threshold of $f$; namely,
-{\tt compareFPT(t, f)} returns {\tt-1} , {\tt 0}, {\tt 1} when $t$ is less than, equal to, or greater than, respectively, the $F$-pure threshold of $f$.
+{\tt compareFPT(t, f)} returns {\tt-1}, {\tt 0}, or {\tt 1} when $t$ is less than, equal to, or greater than, respectively, the $F$-pure threshold of $f$.
 Setting the option {\tt IsLocal} to {\tt true} tells the function to consider the $F$-pure threshold at the origin.

### 2019-06-07 Fsing/FThresholdsPaper/FThresholds.tex
fixed typo noted by Emily

@@
 %The $F$-pure threshold of the pair $(R, f)$ is the supremum over all $t$ for which $(R, f^t)$ is $F$-pure.
-\emph{$F$-threholds} were then introduced as a family of invariants that naturally extend the notion of an $F$-pure threshold \cite{MustataTakagiWatanabeFThresholdsAndBernsteinSato}.
+\emph{$F$-thresholds} were then introduced as a family of invariants that naturally extend the notion of an $F$-pure threshold \cite{MustataTakagiWatanabeFThresholdsAndBernsteinSato}.
 

### 2019-06-07 Fsing/FThresholdsPaper/FThresholds.tex
Small changes to paper

--- 2019-06-07 Fsing/FThresholdsPaper/FThresholds.tex
@@
 This implies that when searching for the maximal exponent defining {\tt nu(e,I,J)} for positive $e$, it is safe to start at $p$ times the output of {\tt nu(e-1,I,J)}, and one needn't search too far past this number.
-This also suggests that the most efficient way to compute {\tt nu(e,I,J)} is to compute, successively, {\tt nu(s,I,J)}, for each integer $s = 0,\ldots,e$.
+This also suggests that the most efficient way to compute {\tt nu(e,I,J)} is to compute, successively, {\tt nu(s,I,J)}, for each $s = 0,\ldots,e$.
 This is indeed how the computation is done in most cases.
@@
 
-If {\tt UseSpecialAlgorithms} is set to {\tt true} and $f$ does not fall into any of the four forementioned cases, then the function {\tt fpt} next calls {\tt isSimpleNormalCrossing(f)} to check whether the polynomial $f$ is a product of factors that are in simple normal crossing.
-If this command returns {\tt true}, the $F$-pure threshold can easily be computed, and {\tt fpt} returns this value.
+If {\tt UseSpecialAlgorithms} is set to {\tt true} and $f$ does not fall into any of the aforementioned cases, then the function {\tt fpt} next calls {\tt isSimpleNormalCrossing(f)} to check whether the polynomial $f$ is a product of factors that are in simple normal crossing, in which case the $F$-pure threshold can easily be computed.
 For more detail on the function {\tt isSimpleNormalCrossing} and on computing the $F$-pure threshold of a polynomial with simple normal crossings, please see Section \ref{subsec.SNC}.
 
-\subsection{How {\tt fpt} proceeds when no special algorithm applies}
+\subsection{When no special algorithm applies}
 
@@
 Then the function {\tt compareFPT} is used to test that number.
-If that "guess" is correct, its value is returned; otherwise, the data returned by {\tt compareFPT} is used to narrow down the interval, and this process is repeated as many times as specified by {\tt Attempts}.
+If that ``guess'' is correct, its value is returned; otherwise, the data returned by {\tt compareFPT} is used to narrow down the interval, and this process is repeated as many times as specified by {\tt Attempts}.
 
@@
 \subsection{The function {\tt isSimpleNormalCrossings}} \label{subsec.SNC}
-As mentioned earlier,
-when the option {\tt useSpecialFunctions} for the function {\tt fpt} is set to {\tt true}, if the polynomial $f$ is neither a diagonal polynomial, a binomial, or a form in two variables, there is a final check to verify whether $f$ is a product of factors in simple normal crossing.
-
+As mentioned earlier, the function {\tt isSimpleNormalCrossings} verifies whether $f$ is a product of factors in simple normal crossing.
 Suppose that $f$ has factorization $f_1^{a_i} f_2^{a_2} \cdots f_n^{a_n}$.  Recall that its factors $f_i$ are said to be in
@@
 \item Add more cases to {\tt UseSpecialAlgorithms}.
-%\item Add the capability to compute non-local {\tt fpt} and non-local {\tt nu} via an option.
+\item Add the capability to compute non-local {\tt fpt} and non-local {\tt nu} via an option.
 \item Write a function that will extract from this sequences $\{ \nu_f^{\idealm}(p^e) \}_{e=1}^{\infty}$ roots of Bernstein-Sato polynomials.  Especially, strata.
@@
 
-\newpage
 \bibliographystyle{skalpha}

### 2019-06-07 Fsing/FThresholdsPaper/FThresholds.tex
Minor change to subsection title

@@
 
-\subsection{The option {\tt UseSpecialAlgorithms} for the {\tt fpt} function}
+\subsection{The option {\tt UseSpecialAlgorithms}}
 

### 2019-06-07 Fsing/FThresholdsPaper/FThresholds.tex
Edits to introduction of paper

--- 2019-06-07 Fsing/FThresholdsPaper/FThresholds.tex
@@
 Furthermore, though there is a general purpose implementation of an algorithm for computing log canonical thresholds in the \emph{Dmodules} package by A.~Leykin and H.~Tsai \cite{DmodulesSource}, it happens that the function for computing $F$-pure thresholds contained in the \emph{FrobeniusThresholds} package is typically much faster, especially so in lower characteristic.
-Note that the  \emph{MultiplierIdeals}  package  by Z.~Teitler, B.~Snapp and C.~Raicu also computes log canonical thresholds in many special cases, including monomial ideals, hyperplane arrangements, generic determinantal ideals, and certain binomial ideals \cite{MultiplierIdealsPackage, MultiplierIdealsArticle}.
+Note that the  \emph{MultiplierIdeals}  package  by Z.~Teitler, B.~Snapp, and C.~Raicu also computes log canonical thresholds in many special cases, including monomial ideals, hyperplane arrangements, generic determinantal ideals, and certain binomial ideals \cite{MultiplierIdealsPackage, MultiplierIdealsArticle}.
 
@@
 
-\subsection*{Some background and notation}
+\subsection{Some background and notation}
 It is important to note that much of the functionality implemented in the \emph{FrobeniusThresholds} is not restricted to regular ambient rings; see Section \ref{sec.IsFPT} for a prominent example of this.
@@
 Finally, normalize this integer by dividing by some power of $p^e$, and then take the limit as the integer $e$ tends to infinity.
-The resulting limit, should it exist, should then encode some interesting information about your initial set of data.
+The resulting limit, if it exists, should then encode some interesting information about your initial set of data.
 
@@
 where $\idealm^{[p^e]}$ denotes the $p^e$-th Frobenius power of $\idealm$, that is, the ideal generated by the $p^e$-th powers of the elements of $\idealm$.
-It is not very hard to see that this number is exactly the largest power of $f$ that is part of a free basis for the localization of the ambient polynomial ring at the origin over its subring of $p^e$-th powers.
+It is not very hard to see that this number is exactly the largest power of $f$ that is part of a free basis for the localization of the ambient polynomial ring at the origin, over its subring of $p^e$-th powers.
 As noted earlier, this number also has a natural interpretation in terms of $F$-purity of pairs.
@@
 Following our outline, we define
-\[ \ft^{\idealm}(f) := \lim_{e \to \infty} \frac{ \nu_f^{\idealm}(p^e)}{p^e} \]
+\[ \ft^{\idealm}(f) := \lim_{e \to \infty} \frac{ \nu_f^{\idealm}(p^e)}{p^e}. \]
 
@@
 However, in this note, we adopt the former notation to avoid any possible confusion with the \emph{Macaulay2} function {\tt fpt} described in Section \ref{sec.FPT}.
-Indeed, the command {\tt fpt(f)} need not always output the number $\ft^{\idealm}(f) = \fpt(f)$, though in the case that it cannot, it will provide a reasonably good estimate of this number.
+Indeed, the command {\tt fpt(f)} need not always output the number $\ft^{\idealm}(f) = \fpt(f)$, though in the case that it cannot, it will provide a reasonably good estimate for this number.
 
@@
 This clearly generalizes the quantity $\nu_f^{\idealm}(p^e)$ considered earlier, and we call
-\[ \ft^J(I) := \lim_{e \to \infty} \frac{ \nu_f^{\idealm}(p^e)}{p^e} \]
+\[ \ft^J(I) := \lim_{e \to \infty} \frac{ \nu_I^J(p^e)}{p^e} \]
 the \emph{$F$-threshold of $I$ with respect to $J$}.  These numbers are also rational, when they are finite.
@@
 Finally, we point out that the  \emph{FrobeniusThresholds} package builds heavily upon the \emph{TestIdeals} package for \emph{Macaulay2} \cite{TestIdealsPackage, TestIdealsPaper,M2}, which provides a broad range of functionality for effective computation in prime characteristic commutative algebra.
-In fact, both this package and \emph{TestIdeals} are derived from an older package \emph{PosChar}.
+In fact, both this package and \emph{TestIdeals} are derived (and have greatly grown) from an older package \emph{PosChar}.
 
@@
 \begin{itemize}
-\item[$\circ$] \autoref{sec.Nu} describes the fundamental function {\tt nu}.  As its name suggests, this function is concerned with computing the integers $\nu_I^J(p^e)$ described above.
+\item[$\circ$] \autoref{sec.Nu} describes the fundamental function {\tt nu}.  As its name suggests, this function is concerned with computing the integers $\nu_I^J(p^e)$ mentioned above.
 \item[$\circ$] \autoref{sec.IsFPT} explains the functionality for determining whether a given number is the $F$-pure threshold, or more generally, an \emph{$F$-jumping exponent}.
 \item[$\circ$] \autoref{sec.FPT} describes the features of the central function of the package, {\tt fpt}.
-\item[$\circ$]  \autoref{sec.FutureDirections} describes our plans for future improvements to this package.
+\item[$\circ$]  \autoref{sec.FutureDirections} outlines our plans for future improvements to this package.
 \end{itemize}
@@
 
-\subsection*{Acknowledgements.}  First and foremost, the authors enthusiastically thank all authors and contributors to the
-\emph{FrobeniusThresholds} package.  {\color{red} (CHECK THESE NAMES)}
+\subsection*{Acknowledgements.}  First and foremost, we enthusiastically thank everyone who helped complete the \emph{FrobeniusThresholds} package. 
 Our package coauthors are Juliette Bruce and Daniel Smolkin.  Erin Bela, Zhibek Kadyrsizova, Moty Katzman, Sara Malec, and Marcus Robinson also contributed valuable code to the package.

### 2019-06-07 Fsing/FThresholdsPaper/FThresholds.tex
Edits to nu section of paper

@@
 We now describe the options available for the function {\tt nu}.
-We focus primarily on the case where the second input is an ideal $I$, since the options work analogously when the second input is instead a polynomial $f$.
-
-In general, the function {\tt nu} works by searching through the list of integers $n$, and checking containments of the $n$-th power of $I$ in a specified Frobenius power of $J$.
+We focus primarily on the case where the second input is an ideal $I$, since the options work analogously when it is instead a polynomial $f$.
+
+In general, the function {\tt nu} works by searching through a list of integers $n$, and checking containments of the $n$-th power of $I$ in a specified Frobenius power of $J$.
 The user can specify how this search is approached through the  option {\tt Search}.
@@
 
-As described in the introduction, the integer $\nu_I^J(p^e)$ is defined in terms of the containment conditions on powers of ideals.
+As described in the introduction, the integer $\nu_I^J(p^e)$ is defined in terms of containment conditions on powers of ideals.
 For positive integers $n$ and $e$, and an ideal $I$ contained in the radical of another ideal $J$, we have that
@@
 maximal integer $n$ for which $I^{[n]}$ is not contained in $J^{[p^e]}$.
-This number is denoted $\mu_I^J(p^e)$ in \emph{loc.\ cit.}, and equals $\nu_I^J(p^e)$ when $I$ is replaced with a polynomial, or is a principal ideal, but need not coincide in general.
+This number is denoted $\mu_I^J(p^e)$ in \emph{loc.\ cit.}, and equals $\nu_I^J(p^e)$ when $I$ is replaced with a polynomial, or is a principal ideal, but need not agree in general.
 For example, the two commands below give different output values.
@@
 }
-
-\medspace
+\medspace
+
 \noindent In line with the philosophy described in the introduction, after appropriately normalizing and taking the limit as $e$ approaches infinity, the values $\mu_I^J(p^e)$ determine certain invariants of interest called \emph{critical exponents}.
@@
 The last option we describe for {\tt nu} is {\tt IsLocal}.
-When the value of {\tt IsLocal} is set to false (the default is {\tt true}), then {\tt nu} ignores the option {\tt ContainmentTest} and the input ideal {\tt I}, and instead computes
+When the value of {\tt IsLocal} is set to {\tt false} (the default is {\tt true}), then {\tt nu} ignores the option {\tt ContainmentTest} and the input ideal {\tt I}, and instead calculates
 \[
@@
 \]
-This is done by instead of computing for which $n$ we have $I^{n} \subseteq J^{[p^e]}$ (or equivalently, $(I^n)^{[1/p^e]} \subseteq J$), it computes for which $n$ we have $(I^n)^{[1/p^e]}$ is a unit ideal.
-
-\medspace
-{\small
-\setstretch{.67}
-\begin{MyVerbatim}
+% This is done by instead of computing for which $n$ we have $I^{n} \subseteq J^{[p^e]}$ (or equivalently, $(I^n)^{[1/p^e]} \subseteq J$), it 
+by determining the values $n$ for which $(I^n)^{[1/p^e]}$ is a unit ideal.
+
+\medspace
+{\small
+\setstretch{.67}
+\begin{MyVerbatim}
+
 i1 : R = ZZ/7[x,y];

### 2019-06-07 Fsing/FThresholdsPaper/FThresholds.tex
Edits to intro and nu section of paper
Work on Future Directions

--- 2019-06-07 Fsing/FThresholdsPaper/FThresholds.tex
@@
 Furthermore, though there is a general purpose implementation of an algorithm for computing log canonical thresholds in the \emph{Dmodules} package by A.~Leykin and H.~Tsai \cite{DmodulesSource}, it happens that the function for computing $F$-pure thresholds contained in the \emph{FrobeniusThresholds} package is typically much faster, especially so in lower characteristic.
-Note that the  \emph{MultiplierIdeals}  package  by Z.~Teitler, B.~Snapp, and C.~Raicu also computes log canonical thresholds in many special cases, including monomial ideals, hyperplane arrangements, generic determinantal ideals, and certain binomial ideals \cite{MultiplierIdealsPackage, MultiplierIdealsArticle}.
+Note that the  \emph{MultiplierIdeals}  package  by Z.~Teitler, B.~Snapp and C.~Raicu also computes log canonical thresholds in many special cases, including monomial ideals, hyperplane arrangements, generic determinantal ideals, and certain binomial ideals \cite{MultiplierIdealsPackage, MultiplierIdealsArticle}.
 
@@
 
-\subsection{Some background and notation}
+\subsection*{Some background and notation}
 It is important to note that much of the functionality implemented in the \emph{FrobeniusThresholds} is not restricted to regular ambient rings; see Section \ref{sec.IsFPT} for a prominent example of this.
@@
 Finally, normalize this integer by dividing by some power of $p^e$, and then take the limit as the integer $e$ tends to infinity.
-The resulting limit, if it exists, should then encode some interesting information about your initial set of data.
+The resulting limit, should it exist, should then encode some interesting information about your initial set of data.
 
@@
 where $\idealm^{[p^e]}$ denotes the $p^e$-th Frobenius power of $\idealm$, that is, the ideal generated by the $p^e$-th powers of the elements of $\idealm$.
-It is not very hard to see that this number is exactly the largest power of $f$ that is part of a free basis for the localization of the ambient polynomial ring at the origin, over its subring of $p^e$-th powers.
+It is not very hard to see that this number is exactly the largest power of $f$ that is part of a free basis for the localization of the ambient polynomial ring at the origin over its subring of $p^e$-th powers.
 As noted earlier, this number also has a natural interpretation in terms of $F$-purity of pairs.
@@
 Following our outline, we define
-\[ \ft^{\idealm}(f) := \lim_{e \to \infty} \frac{ \nu_f^{\idealm}(p^e)}{p^e}. \]
+\[ \ft^{\idealm}(f) := \lim_{e \to \infty} \frac{ \nu_f^{\idealm}(p^e)}{p^e} \]
 
@@
 However, in this note, we adopt the former notation to avoid any possible confusion with the \emph{Macaulay2} function {\tt fpt} described in Section \ref{sec.FPT}.
-Indeed, the command {\tt fpt(f)} need not always output the number $\ft^{\idealm}(f) = \fpt(f)$, though in the case that it cannot, it will provide a reasonably good estimate for this number.
+Indeed, the command {\tt fpt(f)} need not always output the number $\ft^{\idealm}(f) = \fpt(f)$, though in the case that it cannot, it will provide a reasonably good estimate of this number.
 
@@
 This clearly generalizes the quantity $\nu_f^{\idealm}(p^e)$ considered earlier, and we call
-\[ \ft^J(I) := \lim_{e \to \infty} \frac{ \nu_I^J(p^e)}{p^e} \]
+\[ \ft^J(I) := \lim_{e \to \infty} \frac{ \nu_f^{\idealm}(p^e)}{p^e} \]
 the \emph{$F$-threshold of $I$ with respect to $J$}.  These numbers are also rational, when they are finite.
@@
 Finally, we point out that the  \emph{FrobeniusThresholds} package builds heavily upon the \emph{TestIdeals} package for \emph{Macaulay2} \cite{TestIdealsPackage, TestIdealsPaper,M2}, which provides a broad range of functionality for effective computation in prime characteristic commutative algebra.
-In fact, both this package and \emph{TestIdeals} are derived (and have greatly grown) from an older package \emph{PosChar}.
+In fact, both this package and \emph{TestIdeals} are derived from an older package \emph{PosChar}.
 
@@
 \begin{itemize}
-\item[$\circ$] \autoref{sec.Nu} describes the fundamental function {\tt nu}.  As its name suggests, this function is concerned with computing the integers $\nu_I^J(p^e)$ mentioned above.
+\item[$\circ$] \autoref{sec.Nu} describes the fundamental function {\tt nu}.  As its name suggests, this function is concerned with computing the integers $\nu_I^J(p^e)$ described above.
 \item[$\circ$] \autoref{sec.IsFPT} explains the functionality for determining whether a given number is the $F$-pure threshold, or more generally, an \emph{$F$-jumping exponent}.
 \item[$\circ$] \autoref{sec.FPT} describes the features of the central function of the package, {\tt fpt}.
-\item[$\circ$]  \autoref{sec.FutureDirections} outlines our plans for future improvements to this package.
+\item[$\circ$]  \autoref{sec.FutureDirections} describes our plans for future improvements to this package.
 \end{itemize}
@@
 
-\subsection*{Acknowledgements.}  First and foremost, we enthusiastically thank everyone who helped complete the \emph{FrobeniusThresholds} package. 
+\subsection*{Acknowledgements.}  First and foremost, the authors enthusiastically thank all authors and contributors to the
+\emph{FrobeniusThresholds} package.  {\color{red} (CHECK THESE NAMES)}
 Our package coauthors are Juliette Bruce and Daniel Smolkin.  Erin Bela, Zhibek Kadyrsizova, Moty Katzman, Sara Malec, and Marcus Robinson also contributed valuable code to the package.
@@
 
-\newpage
-\section{Future Directions}
+\section{Possible Future Directions}
 \label{sec.FutureDirections}
 
-We conclude with some comments on possible improvements to the package.
-
-One natural candidate for improvement would be to extend functionality to better handle nonprincipal ideals.
-In particular, the package could be improved if it could use the test ideals $\tau(I^t)$ when $I$ is not necessarily principal.
-Fortunately, the theoretical foundation for computing such ideals has already largely been worked out in the paper \cite{SchwedeTuckerTestIdealsOfNonPrincipal}.
-However, such an improvement would necessarily require an update to the \emph{TestIdeals} package.
-
-\begin{enumerate}
-\item Add more cases to {\tt UseSpecialAlgorithms}.
-%\item Add the capability to compute non-local {\tt fpt} and non-local {\tt nu} via an option.
-\item Write a function that will extract from this sequences $\{ \nu_f^{\idealm}(p^e) \}_{e=1}^{\infty}$ roots of Bernstein-Sato polynomials.  Especially, strata.
-
-\item Extend binary forms functions to handle more general $F$-thresholds (that is, with respect to diagonal ideals).
-There is one tricky theoretical things, we don't know when this process would stop.
-If we can do this, then we can compute $F$-pure thresholds of binary forms in non-standard gradings.
-Cite the paper by Daniel and Pedro \cite{HernandezTeixeiraFThresholdFunctions}.
-\end{enumerate}
-
-\newpage
+One natural future direction would be to better incorporate the test ideals $\tau(I^t)$ when computing $F$-thresholds in the case that the ideal $I$ is not necessarily principal.
+The theoretical foundation for computing such ideals has already largely been worked out in the paper \cite{SchwedeTuckerTestIdealsOfNonPrincipal}, but such an update to the \emph{FrobeniusThresholds} package would likely the
+\emph{TestIdeals} package to be updated first.
+
+At the moment, the specialized algorithm called by the {\tt fpt} function for computing the $F$-pure threshold of a homogeneous polynomial in two variables limits us to working with the standard grading on the ambient polynomial ring.
+Clearly, it is desirable to be able to work with non-standard gradings as well, and results in the paper \cite{HernandezTeixeiraFThresholdFunctions} suggest an algorithm for doing so.
+Thus, the package could be improved by finalizing, and implementing, such an algorithm.
+
+Finally, it would be natural to to develop, and implement,  additional algorithms for computing $F$-pure threshold and $F$-jumping numbers in specialized situations apart from monomials, diagonals, binomials, and simple normal crossings.
+The first, third, and fourth authors, along with Josep \'Alvarez Montaner and Jack Jeffries,  are currently working on developing such algorithms.
+The theoretical foundation of these algorithms lies in polyhedral geometry and integer programming, and as such, should be able to be implemented in \emph{Macaualy2}.
+
 \bibliographystyle{skalpha}

### 2019-06-07 Fsing/FThresholdsPaper/FThresholds.tex

--- 2019-06-07 Fsing/FThresholdsPaper/FThresholds.tex
@@
 
-\subsection*{Organization}
+\subsection{Organization}
 
@@
 
-\subsection*{Options for the {\tt nu} function}
+\subsection{Options for {\tt nu}}
 
@@
 \[
-\min_{J \in \mathfrak{m}-\Spec R} (\nu_I^J(p^e))
+\min_{J \in \mathfrak{m}-\Spec R} \nu_I^J(p^e)
 \]
@@
 o4 = 5
+
+o4 : QQ
 

### 2019-06-07 Fsing/FThresholdsPaper/FThresholds.tex
Minor changes

@@
 
-Let us outline a common way in which natural numerical invariants in prime characteristic commutative algebra are constructed:  For every natural number $e$, associate to some fixed set of data|often, a collection of polynomials and ideals|an integer describing something of relevance that depends on $e$ (e.g., the dimension of some interesting vector space constructed in terms of your initial data).
+Let us outline a common way in which natural numerical invariants in prime characteristic commutative algebra are often constructed:  For every natural number $e$, associate to some fixed set of data|often, a collection of polynomials and ideals|an integer describing something of relevance that depends on $e$ (e.g., the dimension of some interesting vector space constructed in terms of your initial data).
 Finally, normalize this integer by dividing by some power of $p^e$, and then take the limit as the integer $e$ tends to infinity.

### 2019-06-07 Fsing/FThresholdsPaper/FThresholds.tex
minor changes to paper

--- 2019-06-07 Fsing/FThresholdsPaper/FThresholds.tex
@@
 
-There are three main sections in this paper, which describe and illustrate the main functionality implemented in the package \emph{FrobeniusThresholds}.
+The overarching goal of this paper is paper is to describe and illustrate the main functionality implemented in the \emph{FrobeniusThresholds} package.
+We break this down into sections, and then conclude by pointing out some potential future directions for the package.
+
 \begin{itemize}
@@
 The last option we describe for {\tt nu} is {\tt IsLocal}.
-When the value of {\tt IsLocal} is set to {\tt false} (the default is {\tt true}), then {\tt nu} ignores the option {\tt ContainmentTest} and the input ideal {\tt I}, and instead calculates
+Notice that $\nu_I^\idealm(p^e)$ can be interpreted as the maximum integer $n>0$ for which $(I^n)^{[1/p^e]} \not\subseteq \idealm$.
+When computing its value globally, it is the maximum $n>0$ for which $(I^n)^{[1/p^e]} \neq R$, and when 
+the value of {\tt IsLocal} is set to {\tt false} (from its default {\tt true}), then {\tt nu} ignores the option {\tt ContainmentTest} and instead calculates determines this value $n$.
+
 \[
@@
 o4 : QQ
-
-i5 : nu(1, x^3-y^2)
-
-o5 = 5
-
-o5 : QQ
 \end{MyVerbatim}
@@
 
-The {\tt fpt} function has the option {\tt UseSpecialAlgorithms}, which, when set to {\tt true} (its default value), tells {\tt fpt} to first check whether $f$ is a diagonal polynomial, a binomial, a form in two variables, or a product of factors in simple normal crossing, in that order.
-
-%If $f$ is a monomial, then its $F$-pure threshold is simply the minimum of the reciprocal of the exponent of each variable in $f$.
+The {\tt fpt} function has an option called {\tt UseSpecialAlgorithms}, which, when set to {\tt true} (its default value), tells {\tt fpt} to first check whether $f$ is a diagonal polynomial, a binomial, a form in two variables, or a product of factors in simple normal crossing, in that order.
+
 When $f$ is a diagonal polynomial, a binomial, or a form in two variables, algorithms of Hern\'andez \cite{HernandezFInvariantsOfDiagonalHyp, HernandezFPureThresholdOfBinomial}, or Hern\'andez and Teixeira \cite{HernandezTeixeiraFThresholdFunctions},  are executed to compute the $F$-pure threshold.
@@
 \begin{MyVerbatim}
+
 i4 : fpt(x^17 + y^20 + z^24) -- a diagonal polynomial
@@
 
-The above noted algorithm for computing the $F$-pure threshold of a binary form $f$ requires factoring $f$ into linear forms, and {\tt fpt} can sometimes hang when attempting that factorization, when it happens in a Galois field of excessively large order.
+The above noted algorithm for computing the $F$-pure threshold of a binary form $f$ requires factoring $f$ into linear forms, and {\tt fpt} can sometimes hang when attempting that factorization, when the factorization occurs in a Galois field of excessively large order.
 This is a situation when the user will want to set the option \texttt{UseSpecialAlgorithms} to \texttt{false}.
-However, when a factorization is already known, the user can pass to {\tt fpt} a list containing all the pairwise prime linear factors of $f$, and a list containing their respective multiplicities.
-
-\medspace
-{\small
-\setstretch{.67}
-\begin{MyVerbatim}
+However, when a factorization is already known, instead of passing {\tt f} to {\tt fpt}, the user can pass a list containing all the pairwise coprime linear factors of $f$ to {\tt fpt}, and a list containing their respective multiplicities.
+
+\medspace
+{\small
+\setstretch{.67}
+\begin{MyVerbatim}
+
 i8 : fpt({x, y, x + y, x + 3*y}, {2, 6, 9, 10}) == oo
@@
 
-\section{Possible Future Directions}
+\newpage
+\section{Future Directions}
 \label{sec.FutureDirections}
 
-One natural future direction would be to better incorporate the test ideals $\tau(I^t)$ when computing $F$-thresholds in the case that the ideal $I$ is not necessarily principal.
-The theoretical foundation for computing such ideals has already largely been worked out in the paper \cite{SchwedeTuckerTestIdealsOfNonPrincipal}, but such an update to the \emph{FrobeniusThresholds} package would likely the
-\emph{TestIdeals} package to be updated first.
-
-At the moment, the specialized algorithm called by the {\tt fpt} function for computing the $F$-pure threshold of a homogeneous polynomial in two variables limits us to working with the standard grading on the ambient polynomial ring.
-Clearly, it is desirable to be able to work with non-standard gradings as well, and results in the paper \cite{HernandezTeixeiraFThresholdFunctions} suggest an algorithm for doing so.
-Thus, the package could be improved by finalizing, and implementing, such an algorithm.
-
-Finally, it would be natural to to develop, and implement,  additional algorithms for computing $F$-pure threshold and $F$-jumping numbers in specialized situations apart from monomials, diagonals, binomials, and simple normal crossings.
-The first, third, and fourth authors, along with Josep \'Alvarez Montaner and Jack Jeffries,  are currently working on developing such algorithms.
-The theoretical foundation of these algorithms lies in polyhedral geometry and integer programming, and as such, should be able to be implemented in \emph{Macaualy2}.
-
+We conclude with some comments on possible improvements to the package.
+
+One natural candidate for improvement would be to extend functionality to better handle nonprincipal ideals.
+In particular, the package could be improved if it could use the test ideals $\tau(I^t)$ when $I$ is not necessarily principal.
+Fortunately, the theoretical foundation for computing such ideals has already largely been worked out in the paper \cite{SchwedeTuckerTestIdealsOfNonPrincipal}.
+However, such an improvement would necessarily require an update to the \emph{TestIdeals} package.
+
+\begin{enumerate}
+\item Add more cases to {\tt UseSpecialAlgorithms}.
+%\item Add the capability to compute non-local {\tt fpt} and non-local {\tt nu} via an option.
+\item Write a function that will extract from this sequences $\{ \nu_f^{\idealm}(p^e) \}_{e=1}^{\infty}$ roots of Bernstein-Sato polynomials.  Especially, strata.
+
+\item Extend binary forms functions to handle more general $F$-thresholds (that is, with respect to diagonal ideals).
+There is one tricky theoretical things, we don't know when this process would stop.
+If we can do this, then we can compute $F$-pure thresholds of binary forms in non-standard gradings.
+Cite the paper by Daniel and Pedro \cite{HernandezTeixeiraFThresholdFunctions}.
+\end{enumerate}
+
+\newpage
 \bibliographystyle{skalpha}

### 2019-06-07 Fsing/FThresholdsPaper/FThresholds.tex
Minor changes

--- 2019-06-07 Fsing/FThresholdsPaper/FThresholds.tex
@@
 The former is an ideal in the ambient ring of $f$, and the latter is a real number;  both depend on the parameter $t$ and prime $p$ in subtle ways \cite{BlickleMustataSmithDiscretenessAndRationalityOfFThresholds, BlickleSchwedeTuckerFSigPairs1}.
-Though we will not elaborate much on these topics,  we stress that the \emph{Macaulay2} package \emph{TestIdeals} provides functionality for the effective computation of test ideals in many cases \cite{TestIdealsPackage, TestIdealsPaper}.
+%Though we will not elaborate much on these topics,  we stress that the \emph{Macaulay2} package \emph{TestIdeals} provides functionality for the effective computation of test ideals in many cases \cite{TestIdealsPackage, TestIdealsPaper}.
 
@@
 the \emph{$F$-threshold of $I$ with respect to $J$}.  These numbers are also rational, when they are finite.
-The value $\ft^{\idealm}(I)$ is called the \emph{$F$-pure threshold of $I$}, and if $I = (f)$ is principal,  $\ft^{J}(f) := \ft^J(I)$ is called the \emph{$F$-threshold of $f$ with respect to $J$}.
+The value $\ft^{\idealm}(I)$ is called the \emph{$F$-pure threshold of $I$}, and if $I = \langle f \rangle$ is principal,  $\ft^{J}(f) := \ft^J(I)$ is called the \emph{$F$-threshold of $f$ with respect to $J$}.
 Like $F$-pure thresholds, $F$-thresholds can also be defined in terms of its test ideals.

### 2019-06-07 Fsing/FThresholdsPaper/FThresholds.tex
minor changes to the paper

--- 2019-06-07 Fsing/FThresholdsPaper/FThresholds.tex
@@
 
-The concept of $F$-purity has proven to be important in commutative algebra, and has a rich history.
-Indeed, it first appeared in the work \cite{HochsterRobertsFrobeniusLocalCohomology}  of Hochster and Roberts to study local cohomology \cite{HochsterRobertsFrobeniusLocalCohomology}, was compared with rational singularities in  \cite{FedderFPureRat}, and was used to study global properties of Schubert varieties in \cite{MehtaRamanathanFrobeniusSplittingAndCohomologyVanishing}.
+The concept of $F$-purity has proven to be important in commutative algebra, and has a rich history.  Indeed, it first appeared in the work
+of Hochster and Roberts to study local cohomology \cite{HochsterRobertsFrobeniusLocalCohomology}, was compared with rational singularities in  \cite{FedderFPureRat}, and was used to study global properties of Schubert varieties in \cite{MehtaRamanathanFrobeniusSplittingAndCohomologyVanishing}.
 
@@
 Given an ideal $I$, the first, third, and fourth authors introduced the notion of a (generalized) Frobenius power $I^{[n]}$ of $I$, when $n$ is an arbitrary positive integer, not necessarily of the form $n = p^e$ \cite{hernandez+etal.frobenius_powers}.
-When {\tt ContainmentTest} is set to {\tt FrobeniusPower}, rather than  computing $\nu_I^J(p^e)$, the function {\tt nu} computes the
-maximal integer $n$ for which $I^{[n]}$ is not contained in $J^{[p^e]}$.
+When {\tt ContainmentTest} is set to {\tt FrobeniusPower}, rather than  computing $\nu_I^J(p^e)$, the function {\tt nu} computes the maximal integer $n$ for which $I^{[n]}$ is not contained in $J^{[p^e]}$.
 This number is denoted $\mu_I^J(p^e)$ in \emph{loc.\ cit.}, and equals $\nu_I^J(p^e)$ when $I$ is replaced with a polynomial, or is a principal ideal, but need not agree in general.
@@
 The last option we describe for {\tt nu} is {\tt IsLocal}.
-Notice that $\nu_I^\idealm(p^e)$ can be interpreted as the maximum integer $n>0$ for which $(I^n)^{[1/p^e]} \not\subseteq \idealm$.
-When computing its value globally, it is the maximum $n>0$ for which $(I^n)^{[1/p^e]} \neq R$, and when 
-the value of {\tt IsLocal} is set to {\tt false} (from its default {\tt true}), then {\tt nu} ignores the option {\tt ContainmentTest} and instead calculates determines this value $n$.
-
-\[
-\min_{J \in \mathfrak{m}-\Spec R} \nu_I^J(p^e)
-\]
+Notice that $\nu_I^\idealm(p^e)$ can be interpreted as the maximum integer $n$ for which $(I^n)^{[1/p^e]}$ is not contained in $\idealm$. 
+When computing its value globally, it is the maximum integer $n$ for which $(I^n)^{[1/p^e]} \neq R$, and when 
+the value of {\tt IsLocal} is set to {\tt false} (from its default value {\tt true}), then {\tt nu} instead determines this value $n$.
+Note that this value is also the minimum $\nu_I^\mathfrak{n}(p^e)$ among all maximal ideals $\mathfrak{n}$ of $R$.
+
+% 
+% \[
+% \min_{J \in \mathfrak{m}-\Spec R} \nu_I^J(p^e)
+% \]
 % This is done by instead of computing for which $n$ we have $I^{n} \subseteq J^{[p^e]}$ (or equivalently, $(I^n)^{[1/p^e]} \subseteq J$), it 
-by determining the values $n$ for which $(I^n)^{[1/p^e]}$ is a unit ideal.
+%by determining the values $n$ for which $(I^n)^{[1/p^e]}$ is a unit ideal.
 
@@
 
-The general method applied calls upon functionality from the \emph{TestIdeals} package \cite{TestIdealsPackage, TestIdealsPaper}.  The functions {\tt testIdeal} and {\tt FPureModule} therein are used
+The general method applied calls upon functionality from the \emph{TestIdeals} package.  The functions {\tt testIdeal} and {\tt FPureModule} therein are used
 to compute the test ideals of $f$ with respect to the parameter $t$, and that with respect to $t - \varepsilon$, for $\varepsilon>0$ very small.
@@
 $\tau(R, f^{t-\varepsilon})$ is not.
-(Note that for $R$ strongly $F$-regular and Gorenstein, {\tt FPureModule(t, f)} precisely computes $\tau(R, f^{t-\varepsilon})$.)
-%These commands work more generally, but they \emph{only} currently work when $R$ is $\bQ$-Gorenstein, with index not divisible by $p$.
+Note that for $R$ strongly $F$-regular and Gorenstein, {\tt FPureModule(t, f)} precisely computes $\tau(R, f^{t-\varepsilon})$.
 

### 2019-06-07 Fsing/FThresholdsPaper/FThresholds.tex
Minor edits to the paper

@@
 
-This paper describes the \emph{Macaulay2} \cite{M2} package \emph{FrobeniusThresholds} \cite{FThresholdsPackage}, which provides tools for computing certain fundamental invariants arising in positive characteristic commutative algebra.
+This paper describes the \emph{Macaulay2} package \emph{FrobeniusThresholds} \cite{M2, FThresholdsPackage}.
+This package provides tools for computing certain fundamental invariants in positive characteristic commutative algebra.
 More precisely, this package concerns the effective computation of \emph{$F$-pure thresholds}, \emph{$F$-thresholds}, and \emph{$F$-jumping exponents}.
@@
 
-Finally, we point out that the  \emph{FrobeniusThresholds} package builds heavily upon the \emph{TestIdeals} package for \emph{Macaulay2} \cite{TestIdealsPackage, TestIdealsPaper,M2}, which provides a broad range of functionality for effective computation in prime characteristic commutative algebra.
-In fact, both this package and \emph{TestIdeals} are derived (and have greatly grown) from an older package \emph{PosChar}.
+Finally, we point out that the  \emph{FrobeniusThresholds} package builds heavily upon the \emph{TestIdeals} package for \emph{Macaulay2} \cite{TestIdealsPackage, TestIdealsPaper}, which provides a broad range of functionality for effective computation in prime characteristic commutative algebra.
+In fact, both this package and \emph{TestIdeals} are derived from, and have greatly expanded, the older package \emph{PosChar}.
 
@@
 
-The overarching goal of this paper is paper is to describe and illustrate the main functionality implemented in the \emph{FrobeniusThresholds} package.
-We break this down into sections, and then conclude by pointing out some potential future directions for the package.
+The goal of this paper is paper is to describe and illustrate the main functionality implemented in the \emph{FrobeniusThresholds} package.  We describe the organization of this paper below.
 
@@
 
-\subsection*{Acknowledgements.}  First and foremost, we enthusiastically thank everyone who helped complete the \emph{FrobeniusThresholds} package. 
+\subsection*{Acknowledgements.}  The authors enthusiastically thank everyone who helped complete the \emph{FrobeniusThresholds} package. 
 Our package coauthors are Juliette Bruce and Daniel Smolkin.  Erin Bela, Zhibek Kadyrsizova, Moty Katzman, Sara Malec, and Marcus Robinson also contributed valuable code to the package.
@@
 
-Finally, we are grateful to the University of Utah for hosting a collaborative development visit in 2018, and to the Institute of Mathematics and its Applications for its generous support for our 2019 Coding Sprint.
+Finally, the authors are grateful to the University of Utah for hosting a collaborative development visit in 2018, and to the Institute of Mathematics and its Applications for its generous support for our 2019 Coding Sprint.
 The current version of the package was finalized during these events.
@@
 We first consider the {\tt nu} function, a fundamental component of the package \emph{FrobeniusThresholds}.
-As in the introduction, in this section we work in a polynomial ring over a finite field of characteristic $p>0$.
-As in the introduction, $\idealm$ will denote the ideal of this ring generated by the variables.
-
-Fix a natural number $e$.  If $f$ is a nonzero polynomial contained in the radical of an ideal $J$, then the command {\tt nu(e,f,J)} outputs the integer $\nu_f^J(p^e)$ defined in the introduction, and
+In this section, we adopt the notation established in the introduction.
+Namely, we work in a polynomial ring over a finite field of characteristic $p>0$,  $\idealm$ denotes the ideal generated by the variables, and $e$ is a natural number.
+
+If $f$ is a nonzero polynomial contained in the radical of an ideal $J$, then the command {\tt nu(e,f,J)} outputs the integer $\nu_f^J(p^e)$ defined in the introduction, and
 %, the maximal integer exponent such that $f^n$ is not contained in $J^{[p^e]}$.
@@
 
-As described in the introduction, the integer $\nu_I^J(p^e)$ is defined in terms of containment conditions on powers of ideals.
-For positive integers $n$ and $e$, and an ideal $I$ contained in the radical of another ideal $J$, we have that
+As described in the introduction, the integer $\nu_I^J(p^e)$ is the maximal integer $n$ such that the $n$-th power of $I$ does not lie in the $p^e$-th Frobenius power of $J$.  However, 
 \begin{equation*}
@@
 When {\tt ContainmentTest} is set to {\tt FrobeniusPower}, rather than  computing $\nu_I^J(p^e)$, the function {\tt nu} computes the maximal integer $n$ for which $I^{[n]}$ is not contained in $J^{[p^e]}$.
-This number is denoted $\mu_I^J(p^e)$ in \emph{loc.\ cit.}, and equals $\nu_I^J(p^e)$ when $I$ is replaced with a polynomial, or is a principal ideal, but need not agree in general.
-For example, the two commands below give different output values.
+This number is denoted $\mu_I^J(p^e)$ in \emph{loc.\ cit.}, and equals $\nu_I^J(p^e)$ when $I$ is replaced with a polynomial, or is a principal ideal.
+However, these number need not agree in general, as we see below.
 
@@
 
-\noindent In line with the philosophy described in the introduction, after appropriately normalizing and taking the limit as $e$ approaches infinity, the values $\mu_I^J(p^e)$ determine certain invariants of interest called \emph{critical exponents}.
+ In line with the philosophy described in the introduction, after appropriately normalizing and taking the limit as $e$ approaches infinity, the values $\mu_I^J(p^e)$ determine certain invariants of interest called \emph{critical exponents}.
 
 The last option we describe for {\tt nu} is {\tt IsLocal}.
-Notice that $\nu_I^\idealm(p^e)$ can be interpreted as the maximum integer $n$ for which $(I^n)^{[1/p^e]}$ is not contained in $\idealm$. 
-When computing its value globally, it is the maximum integer $n$ for which $(I^n)^{[1/p^e]} \neq R$, and when 
-the value of {\tt IsLocal} is set to {\tt false} (from its default value {\tt true}), then {\tt nu} instead determines this value $n$.
-Note that this value is also the minimum $\nu_I^\mathfrak{n}(p^e)$ among all maximal ideals $\mathfrak{n}$ of $R$.
+Recall that $\nu_I^\idealm(p^e)$ can be interpreted as the maximum integer $n$ for which $(I^n)^{[1/p^e]}$ is not contained in $\idealm$. 
+When computing its value globally, it is the maximum integer $n$ for which $(I^n)^{[1/p^e]} \neq R$.  When 
+the value of {\tt IsLocal} is set to {\tt false} (from its default value {\tt true}), then {\tt nu} instead determines this maximal integer $n$, which can also be characterized as the minimal integer $\nu_I^\mathfrak{n}(p^e)$ as $\mathfrak{n}$ varies among all maximal ideals of $R$.
 
@@
 This is a situation when the user will want to set the option \texttt{UseSpecialAlgorithms} to \texttt{false}.
-However, when a factorization is already known, instead of passing {\tt f} to {\tt fpt}, the user can pass a list containing all the pairwise coprime linear factors of $f$ to {\tt fpt}, and a list containing their respective multiplicities.
+However, when a factorization is already known, instead of passing $f$ to {\tt fpt}, the user can pass a list containing all the pairwise coprime linear factors of $f$ to {\tt fpt}, and a list containing their respective multiplicities.
 

### 2019-06-08 Fsing/FThresholdsPaper/FThresholds.tex
Changes to paper

@@
 \RequirePackage[dvipsnames,usenames]{xcolor}
+\usepackage{textgreek}
+\usepackage[utf8x]{inputenc}
+\DeclareUnicodeCharacter{957}{\textnu}
 
@@
 Unfortunately, it is typically difficult to calculate, even in many concrete cases.
-Nevertheless, $F$-pure thresholds have been the focus of intense study over the past 15 years, and the package \emph{FrobeniusThresholds} is centered on calculating and estimating the $F$-pure threshold and other $F$-thresholds, with the function {\tt fpt} at its core.
+Nevertheless, $F$-pure thresholds have been the focus of intense study over the past 15 years, and the package \emph{FrobeniusThresholds} is centered on calculating and estimating the $F$-pure threshold and other $F$-thresholds, with the function \texttt{fpt} at its core.
 
@@
 In the literature, the $F$-pure threshold $\ft^{\idealm}(f)$ is often denoted $\fpt(f)$, for obvious reasons.
-However, in this note, we adopt the former notation to avoid any possible confusion with the \emph{Macaulay2} function {\tt fpt} described in Section \ref{sec.FPT}.
-Indeed, the command {\tt fpt(f)} need not always output the number $\ft^{\idealm}(f) = \fpt(f)$, though in the case that it cannot, it will provide a reasonably good estimate for this number.
+However, in this note, we adopt the former notation to avoid any possible confusion with the \emph{Macaulay2} function \texttt{fpt} described in Section \ref{sec.FPT}.
+Indeed, the command \texttt{fpt(f)} need not always output the number $\ft^{\idealm}(f) = \fpt(f)$, though in the case that it cannot, it will provide a reasonably good estimate for this number.
 
@@
 \begin{itemize}
-\item[$\circ$] \autoref{sec.Nu} describes the fundamental function {\tt nu}.  As its name suggests, this function is concerned with computing the integers $\nu_I^J(p^e)$ mentioned above.
+\item[$\circ$] \autoref{sec.Nu} describes the fundamental function \texttt{nu}.  As its name suggests, this function is concerned with computing the integers $\nu_I^J(p^e)$ mentioned above.
 \item[$\circ$] \autoref{sec.IsFPT} explains the functionality for determining whether a given number is the $F$-pure threshold, or more generally, an \emph{$F$-jumping exponent}.
-\item[$\circ$] \autoref{sec.FPT} describes the features of the central function of the package, {\tt fpt}.
+\item[$\circ$] \autoref{sec.FPT} describes the features of the central function of the package, \texttt{fpt}.
 \item[$\circ$]  \autoref{sec.FutureDirections} outlines our plans for future improvements to this package.
@@
 
-\section{The {\tt nu} function}
+\section{The \texttt{nu} function}
 \label{sec.Nu}
 
-We first consider the {\tt nu} function, a fundamental component of the package \emph{FrobeniusThresholds}.
+We first consider the \texttt{nu} function, a fundamental component of the package \emph{FrobeniusThresholds}.
 In this section, we adopt the notation established in the introduction.
@@
 
-If $f$ is a nonzero polynomial contained in the radical of an ideal $J$, then the command {\tt nu(e,f,J)} outputs the integer $\nu_f^J(p^e)$ defined in the introduction, and
+If $f$ is a nonzero polynomial contained in the radical of an ideal $J$, then the command \texttt{nu(e,f,J)} outputs the integer $\nu_f^J(p^e)$ defined in the introduction, and
 %, the maximal integer exponent such that $f^n$ is not contained in $J^{[p^e]}$.
-more generally, if a nonzero ideal $I$ is contained in the radical of $J$, then {\tt nu(e,I,J)} outputs $\nu_I^J(p^e)$.
+more generally, if a nonzero ideal $I$ is contained in the radical of $J$, then \texttt{nu(e,I,J)} outputs $\nu_I^J(p^e)$.
 Consider the following example.
@@
 
-We highlight some degenerate cases:  If $f$ is the zero polynomial, then {\tt nu(e,f,J)} outputs {\tt 0}, and if $f$ is \emph{not} contained in the radical of $J$, then the output is instead {\tt infinity}.
-These degenerate cases extend analogously to the command {\tt nu(e,I,J)}.
+We highlight some degenerate cases:  If $f$ is the zero polynomial, then \texttt{nu(e,f,J)} outputs \texttt{0}, and if $f$ is \emph{not} contained in the radical of $J$, then the output is instead \texttt{infinity}.
+These degenerate cases extend analogously to the command \texttt{nu(e,I,J)}.
 
@@
 
-If the third argument is omitted from the function {\tt nu}, it is assumed to be the maximal ideal $\idealm$.
+If the third argument is omitted from the function \texttt{nu}, it is assumed to be the maximal ideal $\idealm$.
 
@@
 
-This implies that when searching for the maximal exponent defining {\tt nu(e,I,J)} for positive $e$, it is safe to start at $p$ times the output of {\tt nu(e-1,I,J)}, and one needn't search too far past this number.
-This also suggests that the most efficient way to compute {\tt nu(e,I,J)} is to compute, successively, {\tt nu(s,I,J)}, for each integer $s = 0,\ldots,e$.
+This implies that when searching for the maximal exponent defining \texttt{nu(e,I,J)} for positive $e$, it is safe to start at $p$ times the output of \texttt{nu(e-1,I,J)}, and one needn't search too far past this number.
+This also suggests that the most efficient way to compute \texttt{nu(e,I,J)} is to compute, successively, \texttt{nu(s,I,J)}, for each integer $s = 0,\ldots,e$.
 This is indeed how the computation is done in most cases.
@@
 This fact is used to speed up computations for certain polynomials whose $F$-pure thresholds can be computed quickly via specialized algorithms, namely diagonal polynomials, binomials, and forms in two variables (see Section \ref{sec.FPT}).
-This feature can be disabled by setting the option {\tt UseSpecialAlgorithms} (default value {\tt true}) to {\tt false}.
+This feature can be disabled by setting the option \texttt{UseSpecialAlgorithms} (default value \texttt{true}) to \texttt{false}.
 Consider the following example, where $f$ is a diagonal polynomial.
@@
 
-\subsection{Options for {\tt nu}}
-
-We now describe the options available for the function {\tt nu}.
+\subsection{Options for \texttt{nu}}
+
+We now describe the options available for the function \texttt{nu}.
 We focus primarily on the case where the second input is an ideal $I$, since the options work analogously when it is instead a polynomial $f$.
 
-In general, the function {\tt nu} works by searching through a list of integers $n$, and checking containments of the $n$-th power of $I$ in a specified Frobenius power of $J$.
-The user can specify how this search is approached through the  option {\tt Search}.
-Namely, a binary search is used when {\tt Search} is set to {\tt Binary} (and this is the option's default value), and a linear search is run when it is set to {\tt Linear}.
+In general, the function \texttt{nu} works by searching through a list of integers $n$, and checking containments of the $n$-th power of $I$ in a specified Frobenius power of $J$.
+The user can specify how this search is approached through the  option \texttt{Search}.
+Namely, a binary search is used when \texttt{Search} is set to \texttt{Binary} (and this is the option's default value), and a linear search is run when it is set to \texttt{Linear}.
 
@@
 
-If the option {\tt ReturnList} is changed from its default value of {\tt false} to {\tt true}, rather than simply outputting $\nu_I^J(p^e)$, {\tt nu} outputs a list of the values $\nu_I^J(p^s)$, for $s=0,\ldots,e$.
-Alternatively, the same information can be found by setting the option {\tt Verbose} to {\tt true} (its default value is {\tt false}), to request that each of these values $\nu_I^J(p^s)$ is printed as they are iteratively computed.
+If the option \texttt{ReturnList} is changed from its default value of \texttt{false} to \texttt{true}, rather than simply outputting $\nu_I^J(p^e)$, \texttt{nu} outputs a list of the values $\nu_I^J(p^s)$, for $s=0,\ldots,e$.
+Alternatively, the same information can be found by setting the option \texttt{Verbose} to \texttt{true} (its default value is \texttt{false}), to request that each of these values $\nu_I^J(p^s)$ is printed as they are iteratively computed.
 This can also serve a way to monitor the progress of the computation.
@@
 \begin{MyVerbatim}
-
 i8 : nu(5, f, ReturnList => true)
@@
 i9 : nu(5, f, Verbose => true)
-
-     nu(1) = 0
-     nu(p^1) = 1
-     nu(p^2) = 8
-     nu(p^3) = 44
-     nu(p^4) = 224
-     nu(p^5) = 1124
+nuInternal: using comparison test FrobeniusRoot
+ν(1) = 0
+ν(p^1) = 1
+ν(p^2) = 8
+ν(p^3) = 44
+ν(p^4) = 224
+ν(p^5) = 1124
+
+o9 = 1124
 \end{MyVerbatim}
@@
 where $(I^n)^{[1/p^e]}$ denotes the $p^e$-th \emph{Frobenius root} of $I^n$, as defined in \cite{BlickleMustataSmithDiscretenessAndRationalityOfFThresholds}.
-The option {\tt ContainmentTest} for {\tt nu} allows the user to choose which of the two types of containment statements appearing above to use toward the calculation of $\nu_I^J(p^e)$.
-
-If {\tt ContainmentTest} is set to {\tt StandardPower}, then {\tt nu(e,I,J)} is computed by testing the left-hand containment above, and when it is set to {\tt FrobeniusRoot}, the right-hand containment is checked.
-For efficiency reasons, the default value for {\tt ContainmentTest} is set to  {\tt FrobeniusRoot} if the second argument passed to {\tt nu} is a polynomial, and is set to {\tt StandardPower} if it is an ideal.
+The option \texttt{ContainmentTest} for \texttt{nu} allows the user to choose which of the two types of containment statements appearing above to use toward the calculation of $\nu_I^J(p^e)$.
+
+If \texttt{ContainmentTest} is set to \texttt{StandardPower}, then \texttt{nu(e,I,J)} is computed by testing the left-hand containment above, and when it is set to \texttt{FrobeniusRoot}, the right-hand containment is checked.
+For efficiency reasons, the default value for \texttt{ContainmentTest} is set to  \texttt{FrobeniusRoot} if the second argument passed to \texttt{nu} is a polynomial, and is set to \texttt{StandardPower} if it is an ideal.
 
@@
 
-The option {\tt ContainmentTest} has a third possible value, {\tt FrobeniusPower}, which may produce a different result than the other two values.
+The option \texttt{ContainmentTest} has a third possible value, \texttt{FrobeniusPower}, which may produce a different result than the other two values.
 Given an ideal $I$, the first, third, and fourth authors introduced the notion of a (generalized) Frobenius power $I^{[n]}$ of $I$, when $n$ is an arbitrary positive integer, not necessarily of the form $n = p^e$ \cite{hernandez+etal.frobenius_powers}.
-When {\tt ContainmentTest} is set to {\tt FrobeniusPower}, rather than  computing $\nu_I^J(p^e)$, the function {\tt nu} computes the maximal integer $n$ for which $I^{[n]}$ is not contained in $J^{[p^e]}$.
+When \texttt{ContainmentTest} is set to \texttt{FrobeniusPower}, rather than  computing $\nu_I^J(p^e)$, the function \texttt{nu} computes the maximal integer $n$ for which $I^{[n]}$ is not contained in $J^{[p^e]}$.
 This number is denoted $\mu_I^J(p^e)$ in \emph{loc.\ cit.}, and equals $\nu_I^J(p^e)$ when $I$ is replaced with a polynomial, or is a principal ideal.
@@
 
-The last option we describe for {\tt nu} is {\tt IsLocal}.
+The last option we describe for \texttt{nu} is \texttt{IsLocal}.
 Recall that $\nu_I^\idealm(p^e)$ can be interpreted as the maximum integer $n$ for which $(I^n)^{[1/p^e]}$ is not contained in $\idealm$. 
 When computing its value globally, it is the maximum integer $n$ for which $(I^n)^{[1/p^e]} \neq R$.  When 
-the value of {\tt IsLocal} is set to {\tt false} (from its default value {\tt true}), then {\tt nu} instead determines this maximal integer $n$, which can also be characterized as the minimal integer $\nu_I^\mathfrak{n}(p^e)$ as $\mathfrak{n}$ varies among all maximal ideals of $R$.
+the value of \texttt{IsLocal} is set to \texttt{false} (from its default value \texttt{true}), then \texttt{nu} instead determines this maximal integer $n$, which can also be characterized as the minimal integer $\nu_I^\mathfrak{n}(p^e)$ as $\mathfrak{n}$ varies among all maximal ideals of $R$.
 
@@
 
-%%Below is the original version of the section describing the nu function
-
-%\section{The $F$-pure threshold limit and {\tt nu}}
-%\label{sec.Nu}
-%
-%Suppose $R = k[x_1, \dots, x_n]$ is a polynomial ring over a finite field and $f \in R$.
-If $f^a \notin \langle x_1^{p^e}, \dots, x_n^{p^e} \rangle = \fram^{[p^e]}$, then the pair $(R, f^{a/(p^e -1)})$ is $F$-pure at the origin, whereas if $f^a \in \fram^{[p^e]}$, then the pair $(R, f^{a/p^e})$ is not $F$-pure at the origin.
-By finding the $a \in \bZ$ where that transition happens, and then limiting over $e$, one can compute the $F$-pure threshold.
-See \cite{MustataTakagiWatanabeFThresholdsAndBernsteinSato}.
-%
-%We set $\nu(e, f)$ to be largest $a \in \bZ$ such that $f^a \notin \fram^{[p^e]}$ (note in the literature, it is frequently denoted by $\nu_f(p^e)$.  It immediately follows that
-%\[
-%\fpt(f) = \lim_{e \to \infty} {\nu(e, f) \over p^e}.
-%\]
-%These numbers $\nu(e, f)$ can be computed using the command {\tt nu}, as in the example below.
-%\medskip
-%{\small
-%\setstretch{.67}
-%\begin{MyVerbatim}
-%i1 : loadPackage "FThresholds"
-%
-%o1 = FThresholds
-%
-%o1 : Package
-%
-%i2 : R = ZZ/7[x,y]
-%
-%o2 = R
-%
-%o2 : PolynomialRing
-%
-%i3 : f = y^2 - x^3
-%
-%        3    2
-%o3 = - x  + y
-%
-%o3 : R
-%
-%i4 : nu(1, f)
-%
-%o4 = 5
-%
-%o4 : QQ
-%
-%i5 : nu(2, f)
-%
-%o5 = 40
-%
-%o5 : QQ
-%
-%i6 : nu(3, f)
-%
-%o6 = 285
-%
-%o6 : QQ
-%\end{MyVerbatim}
-%}
-%\medskip
-%The numbers $5/7, 40/49, 285/343$ then approximate the $F$-pure threshold, which in this case happens to equal $5/6$.
-By default, if the function $f$ has a special form (is a diagonal polynomial or a binomial), then the function does not check whether $f^a$ is in  $\langle x_1^{p^e}, \dots, x_n^{p^e} \rangle$, but instead uses general formulas for $\nu$s, see \cite{HernandezFPureThresholdOfBinomial,HernandezFInvariantsOfDiagonalHyp}.
-%
-%In fact, one can make the following more general definition.  If $I$ and $J$ are two ideals (with $I \subseteq \sqrt{J}$), one can define
-%\[
-%\nu(e, I, J) = \max \{ n \in \bZ \; |\; I^n \not\subseteq J^{[p^e]} \}.
-%\]
-%This is frequently denoted by $\nu_I^J(p^e)$ in the literature.
-In the case that $I = \langle f \rangle$ and $J = \fram$, this just recovers the $\nu$'s defined above; the limit of which is the $F$-pure threshold.
-For more general $I$ and $J$, the limit
-%\[
-%\lim_{e \to \infty} {\nu(e, I, J) \over p^e}
-%\]
-%is called the \emph{$F$-threshold of $I$ with respect to $J$}.
-To compute these values we use a binary search, unless the user specifies that we should use a linear search instead {\tt Search=>Linear}.
-%
-%There is one more option that deserves mentioning, {\tt ContainmentTest}.  There are two ways to check whether $f^a$ (or $I^a$) is contained in $J^{[p^e]}$.  In general it is true that
-%\[
-%I^a \subseteq J^{[p^e]} \text{ $\Leftrightarrow$ } (I^a)^{[1/p^e]} \subseteq J
-%\]
-%where $\bullet^{[1/p^e]}$ is defined as in the {\tt TestIdeals} package.
-Which of these two strategies to use is controlled by the option {\tt ContainmentTest => StandardPower} and {\tt ContainmentTest => FrobeniusRoot} respectively.
-%For principal $I$, the command on the right is generally faster (and so {\tt FrobeniusRoot} is the default strategy for computing $\nu$).
-For non-principal $I$, frequently the command on the left is quicker, and so {\tt StandardPower} is default strategy.
-%
-%Finally, the option {\tt ContainmentTest => FrobeniusPower}, then ${\tt \nu(e, I, A)}$ computes the largest integer $n$ such that
-%\[
-%I^{[p^n]} \subseteq J^{[p^e]}.
-%\]
-%See \cite{HernandezTeixeiraWittFrobeniusPowers} for more discussion of this.
-
-\section{{\tt isFPT}, {\tt compareFPT} and {\tt isFJumpingExponent}}
+\section{\texttt{isFPT}, \texttt{compareFPT} and \texttt{isFJumpingExponent}}
 \label{sec.IsFPT}
@@
 Consider a  $\mathbb{Q}$-Gorenstein ring $R$ of characteristic $p>0$, whose index not divisible by $p$.
-Given a parameter $t \in \mathbb{Q}$ and an element $f$ of $R$, the command {\tt isFPT(t,f)} outputs {\tt true} if $t$ is the $F$-pure threshold of $f$, and {\tt false} otherwise.
-Moreover, the function {\tt compareFPT} provides further information about the relationship between $t$ and the $F$-pure threshold of $f$; namely,
-{\tt compareFPT(t, f)} returns {\tt-1}, {\tt 0}, or {\tt 1} when $t$ is less than, equal to, or greater than, respectively, the $F$-pure threshold of $f$.
-Setting the option {\tt IsLocal} to {\tt true} tells the function to consider the $F$-pure threshold at the origin.
+Given a parameter $t \in \mathbb{Q}$ and an element $f$ of $R$, the command \texttt{isFPT(t,f)} outputs \texttt{true} if $t$ is the $F$-pure threshold of $f$, and \texttt{false} otherwise.
+Moreover, the function \texttt{compareFPT} provides further information about the relationship between $t$ and the $F$-pure threshold of $f$; namely,
+\texttt{compareFPT(t, f)} returns {\tt-1}, \texttt{0}, or \texttt{1} when $t$ is less than, equal to, or greater than, respectively, the $F$-pure threshold of $f$.
+Setting the option \texttt{IsLocal} to \texttt{true} tells the function to consider the $F$-pure threshold at the origin.
 The following example illustrates this functionality.
@@
 
-The general method applied calls upon functionality from the \emph{TestIdeals} package.  The functions {\tt testIdeal} and {\tt FPureModule} therein are used
+The general method applied calls upon functionality from the \emph{TestIdeals} package.  The functions \texttt{testIdeal} and \texttt{FPureModule} therein are used
 to compute the test ideals of $f$ with respect to the parameter $t$, and that with respect to $t - \varepsilon$, for $\varepsilon>0$ very small.
@@
 $\tau(R, f^{t-\varepsilon})$ is not.
-Note that for $R$ strongly $F$-regular and Gorenstein, {\tt FPureModule(t, f)} precisely computes $\tau(R, f^{t-\varepsilon})$.
+Note that for $R$ strongly $F$-regular and Gorenstein, \texttt{FPureModule(t, f)} precisely computes $\tau(R, f^{t-\varepsilon})$.
 
@@
 
-\section{The {\tt fpt} function}
+\section{The \texttt{fpt} function}
 \label{sec.FPT}
 
-The core function in the package \emph{FrobeniusThresholds} is called {\tt fpt}.
+The core function in the package \emph{FrobeniusThresholds} is called \texttt{fpt}.
 Throughout this section, let $f$ be a polynomial with coefficients in a finite field of characteristic $p$.
-When passed the polynomial $f$, the function {\tt fpt} attempts to find the exact value for the $F$-pure threshold of $f$ at the origin, and returns that value, if possible.
+When passed the polynomial $f$, the function \texttt{fpt} attempts to find the exact value for the $F$-pure threshold of $f$ at the origin, and returns that value, if possible.
 Otherwise, it returns lower and upper bounds for the $F$-pure threshold, as demonstrated below.
@@
 
-\subsection{The option {\tt UseSpecialAlgorithms}}
-
-The {\tt fpt} function has an option called {\tt UseSpecialAlgorithms}, which, when set to {\tt true} (its default value), tells {\tt fpt} to first check whether $f$ is a diagonal polynomial, a binomial, a form in two variables, or a product of factors in simple normal crossing, in that order.
+\subsection{The option \texttt{UseSpecialAlgorithms}}
+
+The \texttt{fpt} function has an option called \texttt{UseSpecialAlgorithms}, which, when set to \texttt{true} (its default value), tells \texttt{fpt} to first check whether $f$ is a diagonal polynomial, a binomial, a form in two variables, or a product of factors in simple normal crossing, in that order.
 
@@
 
-The above noted algorithm for computing the $F$-pure threshold of a binary form $f$ requires factoring $f$ into linear forms, and {\tt fpt} can sometimes hang when attempting that factorization, when the factorization occurs in a Galois field of excessively large order.
+The above noted algorithm for computing the $F$-pure threshold of a binary form $f$ requires factoring $f$ into linear forms, and \texttt{fpt} can sometimes hang when attempting that factorization, when the factorization occurs in a Galois field of excessively large order.
 This is a situation when the user will want to set the option \texttt{UseSpecialAlgorithms} to \texttt{false}.
-However, when a factorization is already known, instead of passing $f$ to {\tt fpt}, the user can pass a list containing all the pairwise coprime linear factors of $f$ to {\tt fpt}, and a list containing their respective multiplicities.
+However, when a factorization is already known, instead of passing $f$ to \texttt{fpt}, the user can pass a list containing all the pairwise coprime linear factors of $f$ to \texttt{fpt}, and a list containing their respective multiplicities.
 
@@
 
-If {\tt UseSpecialAlgorithms} is set to {\tt true} and $f$ does not fall into any of the aforementioned cases, then the function {\tt fpt} next calls {\tt isSimpleNormalCrossing(f)} to check whether the polynomial $f$ is a product of factors that are in simple normal crossing, in which case the $F$-pure threshold can easily be computed.
-For more detail on the function {\tt isSimpleNormalCrossing} and on computing the $F$-pure threshold of a polynomial with simple normal crossings, please see Section \ref{subsec.SNC}.
+If \texttt{UseSpecialAlgorithms} is set to \texttt{true} and $f$ does not fall into any of the aforementioned cases, then the function \texttt{fpt} next calls \texttt{isSimpleNormalCrossing(f)} to check whether the polynomial $f$ is a product of factors that are in simple normal crossing, in which case the $F$-pure threshold can easily be computed.
+For more detail on the function \texttt{isSimpleNormalCrossing} and on computing the $F$-pure threshold of a polynomial with simple normal crossings, please see Section \ref{subsec.SNC}.
 
@@
 
-In the remainder of this section, we explain how the function  {\tt fpt} proceeds when no special algorithm is available, or when {\tt UseSpecialAlgorithms} is set to {\tt false}, and describe the roles of the options {\tt DepthOfSearch} and {\tt Attempts}, whose values are both nonnegative integers.
-
-In this case, the {\tt fpt} function either computes, and outputs, the exact value of the $F$-pure threshold of $f$, or otherwise recursively computes a finite sequence of lower and upper bounds for this value, and outputs the last of these, which will be the tightest among all computed.
-The value of the option {\tt DepthOfSearch} determines the precision of the initial set of bounds, and the option {\tt Attempts}, in conjunction with some various subroutines, determines whether, and how, to produce new, tighter bounds from the previous ones.
-
-More specifically, let $e$ denote the value of the option {\tt DepthOfSearch}, which conservatively defaults to {\tt 1}.
-The {\tt fpt} function first computes $\nu=\nu_f(p^e)$, which agrees with the output of {\tt nu(e,f)}.
+In the remainder of this section, we explain how the function  \texttt{fpt} proceeds when no special algorithm is available, or when \texttt{UseSpecialAlgorithms} is set to \texttt{false}, and describe the roles of the options \texttt{DepthOfSearch} and \texttt{Attempts}, whose values are both nonnegative integers.
+
+In this case, the \texttt{fpt} function either computes, and outputs, the exact value of the $F$-pure threshold of $f$, or otherwise recursively computes a finite sequence of lower and upper bounds for this value, and outputs the last of these, which will be the tightest among all computed.
+The value of the option \texttt{DepthOfSearch} determines the precision of the initial set of bounds, and the option \texttt{Attempts}, in conjunction with some various subroutines, determines whether, and how, to produce new, tighter bounds from the previous ones.
+
+More specifically, let $e$ denote the value of the option \texttt{DepthOfSearch}, which conservatively defaults to \texttt{1}.
+The \texttt{fpt} function first computes $\nu=\nu_f(p^e)$, which agrees with the output of \texttt{nu(e,f)}.
 It is well known that the $F$-pure threshold of $f$ is greater than $\nu/p^e$ and at most $(\nu+1)/p^e$, and applying  \cite[Proposition 4.2]{HernandezFPurityOfHypersurfaces} to this lower bound tells us that the $F$-pure threshold of $f$ must be at least $\nu/(p^e-1)$.
@@
 
-With these estimates in hand, the subroutine {\tt guessFPT} is called to make some ``educated guesses" in an attempt to identify the $F$-pure threshold within this interval, or at least narrow down this interval to produce improved estimates.
-The number of ``guesses" is controlled by the option {\tt Attempts}, which conservatively defaults to {\tt 3}.
-If {\tt Attempts} is set to {\tt 0}, then {\tt guessFPT} is bypassed.
-If  {\tt Attempts} is set to at least {\tt 1}, then a first check is run to verify whether the right-hand endpoint $(\nu+1)/p^e$ of the above interval \eqref{estimating-interval: e} is the $F$-pure threshold.
+With these estimates in hand, the subroutine \texttt{guessFPT} is called to make some ``educated guesses" in an attempt to identify the $F$-pure threshold within this interval, or at least narrow down this interval to produce improved estimates.
+The number of ``guesses" is controlled by the option \texttt{Attempts}, which conservatively defaults to \texttt{3}.
+If \texttt{Attempts} is set to \texttt{0}, then \texttt{guessFPT} is bypassed.
+If  \texttt{Attempts} is set to at least \texttt{1}, then a first check is run to verify whether the right-hand endpoint $(\nu+1)/p^e$ of the above interval \eqref{estimating-interval: e} is the $F$-pure threshold.
 We illustrate this below.
@@
 
-If  {\tt Attempts} is set to at least {\tt 2} and the right-hand endpoint $(\nu+1)/p^e$ of the interval \eqref{estimating-interval: e} is not the $F$-pure threshold, then a second check is run to verify whether the left-hand endpoint $\nu/(p^e-1)$ of this interval is the $F$-pure threshold.
+If  \texttt{Attempts} is set to at least \texttt{2} and the right-hand endpoint $(\nu+1)/p^e$ of the interval \eqref{estimating-interval: e} is not the $F$-pure threshold, then a second check is run to verify whether the left-hand endpoint $\nu/(p^e-1)$ of this interval is the $F$-pure threshold.
 
@@
 
-If neither endpoint is the $F$-pure threshold and {\tt Attempts} is set to more than {\tt 2}, then  additional checks are performed at certain numbers within the interval.
-First, a number in the interval is selected, according to criteria specified by the value of the option {\tt GuessStrategy}; we refer the reader for the documentation of this option for more details.
-Then the function {\tt compareFPT} is used to test that number.
-If that ``guess'' is correct, its value is returned; otherwise, the data returned by {\tt compareFPT} is used to narrow down the interval, and this process is repeated as many times as specified by {\tt Attempts}.
+If neither endpoint is the $F$-pure threshold and \texttt{Attempts} is set to more than \texttt{2}, then  additional checks are performed at certain numbers within the interval.
+First, a number in the interval is selected, according to criteria specified by the value of the option \texttt{GuessStrategy}; we refer the reader for the documentation of this option for more details.
+Then the function \texttt{compareFPT} is used to test that number.
+If that ``guess'' is correct, its value is returned; otherwise, the data returned by \texttt{compareFPT} is used to narrow down the interval, and this process is repeated as many times as specified by \texttt{Attempts}.
 
@@
 
-The option {\tt Bounds} allows the user to specify known lower and upper bounds for the $F$-pure threshold of $f$, in order to speed up computations or to refine previously obtained estimates.
+The option \texttt{Bounds} allows the user to specify known lower and upper bounds for the $F$-pure threshold of $f$, in order to speed up computations or to refine previously obtained estimates.
 
@@
 
-If {\tt guessFPT} is unsuccessful and {\tt FinalAttempt} is set to {\tt true}, the {\tt fpt} function proceeds to use the convexity of the $F$-signature function and a secant line argument to attempt to narrow down the interval bounding the $F$-pure threshold.
+If \texttt{guessFPT} is unsuccessful and \texttt{FinalAttempt} is set to \texttt{true}, the \texttt{fpt} function proceeds to use the convexity of the $F$-signature function and a secant line argument to attempt to narrow down the interval bounding the $F$-pure threshold.
 If successful, the new lower bound may coincide with the upper bound, in which case we can conclude that it is the desired $F$-pure threshold.
@@
 
-The computations performed when {\tt FinalAttempt} is set to {\tt true} are often slow, and often fail to improve the estimate, and for this reason, this option should be used sparingly.
-It is often more effective to increase the values of {\tt Attempts} or {\tt DepthOfSearch}, instead.
+The computations performed when \texttt{FinalAttempt} is set to \texttt{true} are often slow, and often fail to improve the estimate, and for this reason, this option should be used sparingly.
+It is often more effective to increase the values of \texttt{Attempts} or \texttt{DepthOfSearch}, instead.
 
@@
 As seen in several examples above, when the exact answer is not found, a list containing the endpoints of an interval containing the $F$-pure threshold of $f$ is returned.
-Whether that interval is open, closed, or a mixed interval depends on the options passed; if the option {\tt Verbose} is set to true, the precise interval will be printed.
+Whether that interval is open, closed, or a mixed interval depends on the options passed (it will be \emph{open} whenever \texttt{Attempts} is set to at least \texttt{3}); if the option \texttt{Verbose} is set to true, the precise interval will be printed.
 
@@
 
-Finally, we point out that one can set the option {\tt IsLocal} from its default value of {\tt true} to {\tt false}, to compute the $F$-pure threshold globally.
+Finally, we point out that one can set the option \texttt{IsLocal} from its default value of \texttt{true} to \texttt{false}, to compute the $F$-pure threshold globally.
 In other words, it computes the minimum of the $F$-pure threshold at all maximal ideals.
@@
 
-\noindent In this case, most options enabled by {\tt UseSpecialAlgorithms => true}
-are ignored except for the check for simple normal crossings.  {\tt FinalCheck => true}
+\noindent In this case, most options enabled by \texttt{UseSpecialAlgorithms => true}
+are ignored except for the check for simple normal crossings.  \texttt{FinalCheck => true}
 is also ignored.
 
-\subsection{The function {\tt isSimpleNormalCrossings}} \label{subsec.SNC}
-As mentioned earlier, the function {\tt isSimpleNormalCrossings} verifies whether $f$ is a product of factors in simple normal crossing.
+\subsection{The function \texttt{isSimpleNormalCrossings}} \label{subsec.SNC}
+As mentioned earlier, the function \texttt{isSimpleNormalCrossings} verifies whether $f$ is a product of factors in simple normal crossing.
 Suppose that $f$ has factorization $f_1^{a_i} f_2^{a_2} \cdots f_n^{a_n}$.  Recall that its factors $f_i$ are said to be in
 \emph{simple normal crossing} at a point if, locally, they form part of a regular system of parameters.
-The function {\tt isSimpleNormalCrossings} determines whether $f$ has simple normal crossings by computing the Jacobian matrix of each subset of $\{ f_i \}_{i=1}^n$ (evaluated at the origin), and checking that these matrices have the expected rank, and that these subsets generate ideals of the appropriate height.
+The function \texttt{isSimpleNormalCrossings} determines whether $f$ has simple normal crossings by computing the Jacobian matrix of each subset of $\{ f_i \}_{i=1}^n$ (evaluated at the origin), and checking that these matrices have the expected rank, and that these subsets generate ideals of the appropriate height.
 
@@
 
-If {\tt isSimpleNormalCrossing(f)} outputs true, then the $F$-pure threshold is easily computed, since is just the minimum of the values $1/a_i$, for $1 \leq i \leq n$.
-Note that the function {\tt factor} is called whenever {\tt isSimpleNormalCrossing} is used, which can sometimes make the verification slow.
-The user can avoid this when using {\tt fpt} by setting {\tt UseSpecialAlgorithms} to {\tt false}.
-
-The function {\tt isSimpleNormalCrossing} is exposed to the user, so can be used independent of any $F$-pure threshold calculation.
-If the user sets its option {\tt IsLocal} to {\tt true} (its default value is {\tt false}), then the function checks whether the $f_i$ are in simple normal crossing \emph{everywhere}, which can be much slower since Jacobian ideals are computed.
+If \texttt{isSimpleNormalCrossing(f)} outputs true, then the $F$-pure threshold is easily computed, since is just the minimum of the values $1/a_i$, for $1 \leq i \leq n$.
+Note that the function \texttt{factor} is called whenever \texttt{isSimpleNormalCrossing} is used, which can sometimes make the verification slow.
+The user can avoid this when using \texttt{fpt} by setting \texttt{UseSpecialAlgorithms} to \texttt{false}.
+
+The function \texttt{isSimpleNormalCrossing} is exposed to the user, so can be used independent of any $F$-pure threshold calculation.
+If the user sets its option \texttt{IsLocal} to \texttt{true} (its default value is \texttt{false}), then the function checks whether the $f_i$ are in simple normal crossing \emph{everywhere}, which can be much slower since Jacobian ideals are computed.
 Consider the following example illustrating this functionality.
@@
 
-At the moment, the specialized algorithm called by the {\tt fpt} function for computing the $F$-pure threshold of a homogeneous polynomial in two variables limits us to working with the standard grading on the ambient polynomial ring.
+At the moment, the specialized algorithm called by the \texttt{fpt} function for computing the $F$-pure threshold of a homogeneous polynomial in two variables limits us to working with the standard grading on the ambient polynomial ring.
 Clearly, it is desirable to be able to work with non-standard gradings as well, and results in the paper \cite{HernandezTeixeiraFThresholdFunctions} suggest an algorithm for doing so.

### 2019-06-08 Fsing/FThresholdsPaper/FThresholds.tex
minor changes to paper
Changes to paper: rerun examples

@@
 
-\medspace
-{\small
-\setstretch{.67}
-\begin{MyVerbatim}
-
+\bigskip
+{\small
+\setstretch{.67}
+\begin{MyVerbatim}
 i1 : R = ZZ/11[x,y];
@@
 }
-\medspace
+\bigskip
 
@@
 
-\medspace
-{\small
-\setstretch{.67}
-\begin{MyVerbatim}
-
+\bigskip
+{\small
+\setstretch{.67}
+\begin{MyVerbatim}
 i7 : nu(1, 0_R, J)
@@
 
-\medspace
-{\small
-\setstretch{.67}
-\begin{MyVerbatim}
-
+\bigskip
+{\small
+\setstretch{.67}
+\begin{MyVerbatim}
 i9 : R = ZZ/17[x,y,z];
@@
 
-\medspace
-{\small
-\setstretch{.67}
-\begin{MyVerbatim}
-
-i1 : R = ZZ/17[x,y,z];
-
-i2 : f = x^3 + y^4 + z^5; -- a diagonal polynomial
-
-i3 : time nu(3, f)
-     -- used 0.00552312 seconds
-
-o3 = 3756
-
-o4 : QQ
-
-i4 : time nu(3, f, UseSpecialAlgorithms => false)
-     -- used 0.155826 seconds
-
-o4 = 3756
-\end{MyVerbatim}
-}
-\medspace
+\bigskip
+{\small
+\setstretch{.67}
+\begin{MyVerbatim}
+i13 : R = ZZ/17[x,y,z];
+
+i14 : f = x^3 + y^4 + z^5; -- a diagonal polynomial
+
+i15 : time nu(3, f)
+     -- used 0.0108065 seconds
+
+o15 = 3756
+
+o15 : QQ
+
+i16 : time nu(3, f, UseSpecialAlgorithms => false)
+     -- used 0.209325 seconds
+
+o16 = 3756
+\end{MyVerbatim}
+}
+\bigskip
 
@@
 
-\medspace
-{\small
-\setstretch{.67}
-\begin{MyVerbatim}
-
-i1 : R = ZZ/5[x,y,z];
-
-i2 : f = x^2*y^4 + y^2*z^7 + z^2*x^8;
-
-i3 : time nu(5, f) -- uses binary search (default)
-     -- used 0.313778 seconds
-
-o3 = 1124
-
-i4 : time nu(5, f, Search => Linear)
-     -- used 0.441903 seconds
-
-o4 = 1124
-
-i5 : m = ideal(x, y, z);
-
-o5 : Ideal of R
-
-i6 : time nu(2, m, m^2) -- uses binary search (default)
-     -- used 1.58258 seconds
-
-o6 = 97
-
-i7 : time nu(2, m, m^2, Search => Linear) -- but linear seach gets luckier
-     -- used 0.531175 seconds
-
-o7 = 97
-\end{MyVerbatim}
-}
-\medspace
+\bigskip
+{\small
+\setstretch{.67}
+\begin{MyVerbatim}
+i17 : R = ZZ/5[x,y,z];
+
+i18 : f = x^2*y^4 + y^2*z^7 + z^2*x^8;
+
+i19 : time nu(5, f) -- uses binary search (default)
+     -- used 0.350179 seconds
+
+o19 = 1124
+
+i20 : time nu(5, f, Search => Linear)
+     -- used 0.485823 seconds
+
+o20 = 1124
+
+i21 : m = ideal(x, y, z);
+
+o21 : Ideal of R
+
+i22 : time nu(2, m, m^2) -- uses binary search (default)
+     -- used 1.71206 seconds
+
+o22 = 97
+
+i23 : time nu(2, m, m^2, Search => Linear) -- but linear seach gets luckier
+     -- used 0.536135 seconds
+
+o23 = 97
+\end{MyVerbatim}
+}
+\bigskip
 
@@
 
-\medspace
-{\small
-\setstretch{.67}
-\begin{MyVerbatim}
-i8 : nu(5, f, ReturnList => true)
-
-o8 = {0, 1, 8, 44, 224, 1124}
-
-o8 : List
-
-i9 : nu(5, f, Verbose => true)
+\bigskip
+{\small
+\setstretch{.67}
+\begin{MyVerbatim}
+i24 : nu(5, f, ReturnList => true)
+
+o24 = {0, 1, 8, 44, 224, 1124}
+
+o24 : List
+
+i25 : nu(5, f, Verbose => true)
+
 nuInternal: using comparison test FrobeniusRoot
+
 ν(1) = 0
@@
 
-o9 = 1124
-\end{MyVerbatim}
-}
-\medspace
+o25 = 1124
+\end{MyVerbatim}
+}
+\bigskip
 
@@
 
-\medspace
-{\small
-\setstretch{.67}
-\begin{MyVerbatim}
-
-i1 : R = ZZ/11[x,y,z];
-
-i2 : f = x^3 + y^3 + z^3 + x*y*z;
-
-i3 : time nu(3, f) -- ContainmentTest is set to FrobeniusRoot, by default
-     -- used 0.116697 seconds
-
-o3 = 1209
-
-i4 : time nu(3, f, ContainmentTest => StandardPower)
-     -- used 9.65013 seconds
-
-o4 = 1209
-\end{MyVerbatim}
-}
-\medspace
+\bigskip
+{\small
+\setstretch{.67}
+\begin{MyVerbatim}
+i26 : R = ZZ/11[x,y,z];
+
+i27 : f = x^3 + y^3 + z^3 + x*y*z;
+
+i28 : time nu(3, f) -- ContainmentTest is set to FrobeniusRoot, by default
+     -- used 0.127375 seconds
+
+o28 = 1209
+
+i29 : time nu(3, f, ContainmentTest => StandardPower)
+     -- used 9.57149 seconds
+
+o29 = 1209
+\end{MyVerbatim}
+}
+\bigskip
 
@@
 
-\medspace
-{\small
-\setstretch{.67}
-\begin{MyVerbatim}
-
-i1 : R = ZZ/3[x,y];
-
-i2 : m = ideal(x, y);
-
-o2 : Ideal of R
-
-i3 : nu(3, m^5)
-
-o3 = 10
-
-i4 : nu(3, m^5, ContainmentTest => FrobeniusPower)
-
-o4 = 8
-\end{MyVerbatim}
-}
-\medspace
+\bigskip
+{\small
+\setstretch{.67}
+\begin{MyVerbatim}
+i30 : R = ZZ/3[x,y];
+
+i31 : m = ideal(x, y);
+
+o31 : Ideal of R
+
+i32 : nu(3, m^5)
+
+o32 = 10
+
+i33 : nu(3, m^5, ContainmentTest => FrobeniusPower)
+
+o33 = 8
+\end{MyVerbatim}
+}
+\bigskip
 
@@
 
-\medspace
-{\small
-\setstretch{.67}
-\begin{MyVerbatim}
-
-i1 : R = ZZ/7[x,y];
-
-i2 : f = (x-1)^3 - (y-2)^2;
-
-i3 : nu(1, f)
-
-o3 = infinity
-
-o3 : InfiniteNumber
-
-i4 : nu(1, f, IsLocal => false)
-
-o4 = 5
-
-o4 : QQ
+\bigskip
+{\small
+\setstretch{.67}
+\begin{MyVerbatim}
+i34 : R = ZZ/7[x,y];
+
+i35 : f = (x - 1)^3 - (y - 2)^2;
+
+i36 : nu(1, f)
+
+o36 = infinity
+
+o36 : InfiniteNumber
+
+i37 : nu(1, f, IsLocal => false)
+
+o37 = 5
 \end{MyVerbatim}
@@
 
-\medspace
-{\small
-\setstretch{.67}
-\begin{MyVerbatim}
-
+\bigskip
+{\small
+\setstretch{.67}
+\begin{MyVerbatim}
 i1 : R = ZZ/11[x, y, z]/(x^2 - y*(z - 1));
@@
 
-\medspace
-{\small
-\setstretch{.67}
-\begin{MyVerbatim}
-
-i49 : R = ZZ/13[x, y];
-
-i50 : f = y*((y + 1) - (x - 1)^2)*(x - 2)*(x + y - 2);
-
-i51 : isFJumpingExponent(3/4, f)
-
-o51 = true
-\end{MyVerbatim}
-}
-\medspace
+\bigskip
+{\small
+\setstretch{.67}
+\begin{MyVerbatim}
+i1 : R = ZZ/11[x, y, z]/(x^2 - y*(z - 1));
+
+i2 : compareFPT(5/11, z - 1)
+
+o2 = -1
+
+i3 : isFPT(1/2, z - 1)
+
+o3 = true
+
+i4 : isFPT(1/2, z - 1, IsLocal => true)
+
+o4 = false
+\end{MyVerbatim}
+}
+\bigskip
 
@@
 
-\medspace
-{\small
-\setstretch{.67}
-\begin{MyVerbatim}
-
-i1 : ZZ/5[x,y,z];
+\bigskip
+{\small
+\setstretch{.67}
+\begin{MyVerbatim}
+i1 : R = ZZ/5[x,y,z];
 
@@
 
-      1  2
-o3 = {-, -}
-      3  5
+       7  2
+o3 = {--, -}
+      25  5
 
@@
 
-\medspace
-{\small
-\setstretch{.67}
-\begin{MyVerbatim}
-
+\bigskip
+{\small
+\setstretch{.67}
+\begin{MyVerbatim}
 i4 : fpt(x^17 + y^20 + z^24) -- a diagonal polynomial
@@
 
-i6 : ZZ/5[x,y];
+i6 : R = ZZ/5[x,y];
 
@@
 
-\medspace
-{\small
-\setstretch{.67}
-\begin{MyVerbatim}
-
+\bigskip
+{\small
+\setstretch{.67}
+\begin{MyVerbatim}
 i8 : fpt({x, y, x + y, x + 3*y}, {2, 6, 9, 10}) == oo
@@
 
-\medspace
-{\small
-\setstretch{.67}
-\begin{MyVerbatim}
-
-i12 : f = x^2*(x + y)^3*(x + 3*y^2)^5;
-
-i13 : fpt(f, Attempts => 0) -- a bad estimate
+\bigskip
+{\small
+\setstretch{.67}
+\begin{MyVerbatim}
+i9 : f = x^2*(x + y)^3*(x + 3*y^2)^5;
+
+i10 : fpt(f, Attempts => 0) -- a bad estimate
 
           1
-o13 = {0, -}
+o10 = {0, -}
           5
 
-o13 : List
-
-i14 : fpt(f, Attempts => 0, DepthOfSearch => 3) -- a better estimate
+o10 : List
+
+i11 : fpt(f, Attempts => 0, DepthOfSearch => 3) -- a better estimate
 
         21   22
-o14 = {---, ---}
+o11 = {---, ---}
        124  125
 
+o11 : List
+
+i12 : fpt(f, Attempts => 1, DepthOfSearch => 3) -- the right-hand
+      endpoint (nu+1)/p^e is the F-pure threshold
+
+       22
+o12 = ---
+      125
+
+o12 : QQ
+\end{MyVerbatim}
+}
+
+If  \texttt{Attempts} is set to at least \texttt{2} and the right-hand endpoint $(\nu+1)/p^e$ of the interval \eqref{estimating-interval: e} is not the $F$-pure threshold, then a second check is run to verify whether the left-hand endpoint $\nu/(p^e-1)$ of this interval is the $F$-pure threshold.
+
+\bigskip
+{\small
+\setstretch{.67}
+\begin{MyVerbatim}
+i13 : f = x^6*y^4 + x^4*y^9 + (x^2 + y^3)^3;
+
+i14 : fpt(f, Attempts => 1, DepthOfSearch => 3)
+
+       17   7
+o14 = {--, --}
+       62  25
+
 o14 : List
 
-i15 : fpt(f, Attempts => 1, DepthOfSearch => 3) -- the right-hand
-
-      endpoint (nu+1)/p^e is the F-pure threshold
-
-       22
-o15 = ---
-      125
+i15 : fpt(f, Attempts => 2, DepthOfSearch => 3) -- the left-hand endpoint
+      nu/(p^e-1) is the F-pure threshold
+
+      17
+o15 = --
+      62
 
 o15 : QQ
-
-\end{MyVerbatim}
-}
-
-If  \texttt{Attempts} is set to at least \texttt{2} and the right-hand endpoint $(\nu+1)/p^e$ of the interval \eqref{estimating-interval: e} is not the $F$-pure threshold, then a second check is run to verify whether the left-hand endpoint $\nu/(p^e-1)$ of this interval is the $F$-pure threshold.
-
-\medspace
-{\small
-\setstretch{.67}
-\begin{MyVerbatim}
-
-i16 : f = x^6*y^4 + x^4*y^9 + (x^2 + y^3)^3;
-
-i17 : fpt(f, Attempts => 1, DepthOfSearch => 3)
-
-       17   7
-o17 = {--, --}
-       62  25
-
-o17 : List
-
-i18 : fpt(f, Attempts => 2, DepthOfSearch => 3) -- the left-hand endpoint
-      nu/(p^e-1) is the F-pure threshold
-
-      17
-o18 = --
-      62
-
-o18 : QQ
-
 \end{MyVerbatim}
@@
 
-\medspace
-{\small
-\setstretch{.67}
-\begin{MyVerbatim}
-
-i19 : f = x^3*y^11*(x + y)^8*(x^2 + y^3)^8;
-
-i20 : fpt(f, DepthOfSearch => 3, Attempts => 2)
+\bigskip
+{\small
+\setstretch{.67}
+\begin{MyVerbatim}
+i16 : f = x^3*y^11*(x + y)^8*(x^2 + y^3)^8;
+
+i17 : fpt(f, DepthOfSearch => 3, Attempts => 2)
 
         3   7
-o20 = {--, ---}
+o17 = {--, ---}
        62  125
 
-o20 : List
-
-i21 : fpt(f, DepthOfSearch => 3, Attempts => 4) -- more attempts *always*
+o17 : List
+
+i18 : fpt(f, DepthOfSearch => 3, Attempts => 4) -- more attempts *always*
       improve the estimate
@@
         1   4
+o18 = {--, --}
+       20  75
+
+o18 : List
+
+i19 : fpt(f, DepthOfSearch => 3, Attempts => 4, GuessStrategy => denominator)
+      -- the exact answer, after a change of strategy
+
+       1
+o19 = --
+      19
+
+o19 : QQ
+\end{MyVerbatim}
+}
+\bigskip
+
+The option \texttt{Bounds} allows the user to specify known lower and upper bounds for the $F$-pure threshold of $f$, in order to speed up computations or to refine previously obtained estimates.
+
+\bigskip
+{\small
+\setstretch{.67}
+\begin{MyVerbatim}
+i20 : f = x^7*y^5*(x + y)^5*(x^2 + y^3)^4;
+
+i21 : fpt(f, DepthOfSearch => 3, Attempts => 5)
+
+        3   1
 o21 = {--, --}
-       20  75
+       40  13
 
@@
 
-i22 : fpt(f, DepthOfSearch => 3, Attempts => 4, GuessStrategy => denominator)
-      -- the exact answer, after a change of strategy
-
-       1
-o22 = --
-      19
-
-o22 : QQ
-\end{MyVerbatim}
-}
-\medspace
-
-The option \texttt{Bounds} allows the user to specify known lower and upper bounds for the $F$-pure threshold of $f$, in order to speed up computations or to refine previously obtained estimates.
-
-\medspace
-{\small
-\setstretch{.67}
-\begin{MyVerbatim}
-
-i23 : f = x^7*y^5*(x + y)^5*(x^2 + y^3)^4;
-
-i24 : fpt(f, DepthOfSearch => 3, Attempts => 5)
-
-        3   1
-o24 = {--, --}
-       40  13
-
-o24 : List
-
-i25 : fpt(f, DepthOfSearch => 3, Attempts => 5, Bounds => oo)
+i22 : fpt(f, DepthOfSearch => 3, Attempts => 5, Bounds => oo)
 
         24   1
-o25 = {---, --}
+o22 = {---, --}
        313  13
 
-o25 : List
-\end{MyVerbatim}
-}
-\medspace
+o22 : List
+\end{MyVerbatim}
+}
+\bigskip
 
@@
 
-\medspace
-{\small
-\setstretch{.67}
-\begin{MyVerbatim}
-
-i26 : f = -2*x^10*y^5 - x^5*y^9 - 2*x^3*y^10 + 2*x^2*y^8 - 2*x*y^9;
-
-i27 : numeric fpt(f, DepthOfSearch => 3)
-
-o27 = {.153226, .158333}
-
-o27 : List
-
-i28 : numeric fpt(f, DepthOfSearch => 3, FinalAttempt => true)
+\bigskip
+{\small
+\setstretch{.67}
+\begin{MyVerbatim}
+i23 : f = -2*x^10*y^5 - x^5*y^9 - 2*x^3*y^10 + 2*x^2*y^8 - 2*x*y^9;
+
+i24 : numeric fpt(f, DepthOfSearch => 3)
+
+o24 = {.153226, .158333}
+
+o24 : List
+
+i25 : numeric fpt(f, DepthOfSearch => 3, FinalAttempt => true)
       -- FinalAttempt improves the estimate slightly
 
-o28 = {.153461, .158333}
-
-o28 : List
-\end{MyVerbatim}
-}
-\medspace
+o25 = {.153461, .158333}
+
+o25 : List
+\end{MyVerbatim}
+}
+\bigskip
 
@@
 
-\medspace
-{\small
-\setstretch{.67}
-\begin{MyVerbatim}
-
-i29 : f = -2*x^10*y^5 - x^5*y^9 - 2*x^3*y^10 + 2*x^2*y^8 - 2*x*y^9;
-
-i30 : timing numeric fpt(f, DepthOfSearch => 3, FinalAttempt => true)
-
-o30 = {.153461, .158333}
-      -- 1.29156 seconds
-
-o30 : Time
-
-i31 : timing numeric fpt(f, DepthOfSearch => 3, Attempts => 4) -- a better
+\bigskip
+{\small
+\setstretch{.67}
+\begin{MyVerbatim}
+i26 : f = -2*x^10*y^5 - x^5*y^9 - 2*x^3*y^10 + 2*x^2*y^8 - 2*x*y^9;
+
+i27 : timing numeric fpt(f, DepthOfSearch => 3, FinalAttempt => true)
+
+o27 = {.153461, .158333}
+      -- 1.37902 seconds
+
+o27 : Time
+
+i28 : timing numeric fpt(f, DepthOfSearch => 3, Attempts => 4) -- a better
       answer in less time
 
-o31 = {.153333, .158333}
-      -- .554321 seconds
-
-o31 : Time
-
-i32 : timing fpt(f, DepthOfSearch => 4) -- the exact answer in even less
+o28 = {.153333, .158333}
+      -- .614248 seconds
+
+o28 : Time
+
+i29 : timing fpt(f, DepthOfSearch => 4) -- the exact answer in even less
       time
@@
        98
-o32 = ---
+o29 = ---
       625
-      -- .274657 seconds
-
-o32 : Time
-\end{MyVerbatim}
-}
-\medspace
+      -- .297493 seconds
+
+o29 : Time
+\end{MyVerbatim}
+}
+\bigskip
 
@@
 
-\medspace
-{\small
-\setstretch{.67}
-\begin{MyVerbatim}
-
-i33 : f = x^7*y^5*(x + y)^5*(x^2 + y^3)^4;
-
-i34 : fpt(f, DepthOfSearch => 3, FinalAttempt => true, Verbose => true)
+\bigskip
+{\small
+\setstretch{.67}
+\begin{MyVerbatim}
+i30 : f = x^7*y^5*(x + y)^5*(x^2 + y^3)^4;
+
+i31 : fpt(f, DepthOfSearch => 3, FinalAttempt => true, Verbose => true)
 
@@
 
-nu has been computed: nu = nu(3,f) = 9 ...
-
-fpt lies in the interval [ nu/(p^e-1), (nu+1)/p^e ] = [ 9/124, 2/25 ] ...
+ν has been computed: ν = ν(3,f) = 9 ...
+
+fpt lies in the interval [ν/(p^e-1),(ν+1)/p^e] = [9/124,2/25] ...
 
@@
 
-guessFPT narrowed the interval down to ( 3/40, 2/25 ) ...
+guessFPT narrowed the interval down to (3/40,2/25) ...
 
@@
 
-First F-signature computed: s(f,(nu-1)/p^e) = 456/15625 ...
-
-Second F-signature computed: s(f,nu/p^e) = 64/15625 ...
+First F-signature computed: s(f,(ν-1)/p^e) = 456/15625 ...
+
+Second F-signature computed: s(f,ν/p^e) = 64/15625 ...
 
@@
 
-fpt lies in the interval ( 3/40, 2/25 ).
+fpt lies in the interval (3/40,2/25).
 
         3   2
-o34 = {--, --}
+o31 = {--, --}
        40  25
 
-o34 : List
-\end{MyVerbatim}
-}
-\medspace
+o31 : List
+\end{MyVerbatim}
+}
+\bigskip
 
@@
 
-\medspace
-{\small
-\setstretch{.67}
-\begin{MyVerbatim}
-
-i1 : R = ZZ/7[x,y];
-
-i2 : f = (y-1)^2-(x-1)^3;
-
-i3 : fpt(f, IsLocal => false)
+\bigskip
+{\small
+\setstretch{.67}
+\begin{MyVerbatim}
+i32 : R = ZZ/7[x,y];
+
+i33 : f = (y - 1)^2-(x - 1)^3;
+
+i34 : fpt(f, IsLocal => false)
 
       5
-o3 = -
+o34 = -
       6
 
-o3 : QQ
-
-i4 : fpt(f)
-
-o4 = infinity
-
-o4 : InfiniteNumber
-\end{MyVerbatim}
-}
-\medspace
+o34 : QQ
+
+i35 : fpt(f)
+
+o35 = infinity
+
+o35 : InfiniteNumber
+\end{MyVerbatim}
+}
+\bigskip
 % R = ZZ/7[x,y];
@@
 
-\medspace
-{\small
-\setstretch{.67}
-\begin{MyVerbatim}
-
-i1 : R = ZZ/7[x, y, z];
-
-i2 : isSimpleNormalCrossing(x^3*y^2)
-
-o2 = true
-
-i3 : isSimpleNormalCrossing(x^2-y^2)
-
-o3 = true
-
-i4 : isSimpleNormalCrossing(x*y*(x-y))
-
-o4 = false
-
-i5 : isSimpleNormalCrossing(x^2-y*z)
-
-o5 = false
-\end{MyVerbatim}
-}
-\medspace
+\bigskip
+{\small
+\setstretch{.67}
+\begin{MyVerbatim}
+i36 : R = ZZ/7[x, y, z];
+
+i37 : isSimpleNormalCrossing(x^2 - y^2)
+
+o37 = true
+
+i38 : isSimpleNormalCrossing(x^2 - y*z)
+
+o38 = false
+\end{MyVerbatim}
+}
+\bigskip
 
 %             R = ZZ/7[x,y,z];
-%             isSimpleNormalCrossing(x^3*y^2)
 %             isSimpleNormalCrossing(x^2-y^2)
-%             isSimpleNormalCrossing(x*y*(x-y))
 %             isSimpleNormalCrossing(x^2-y*z)
@@
 
-\medspace
-{\small
-\setstretch{.67}
-\begin{MyVerbatim}
-
-i1 : R = QQ[x, y, z];
-
-i2 : f = (y - (x-1)^2)*y^2; --SNC at the origin, but not globally
-
-i3 : isSimpleNormalCrossing(f)
-
-o3 = true
-
-i4 : isSimpleNormalCrossing(f, IsLocal=>false)
-
-o4 = false
-
-i5 : g = (y-1)^2+(x-7)^2 --doesn't even pass through the origin
-
-       2    2
-o5 = x  + y  - 14x - 2y + 50
-
-o5 : R
-
-i6 : isSimpleNormalCrossing(g)
-
-o6 = true
-
-i7 : isSimpleNormalCrossing(g, IsLocal=>false)
-
-o7 = false
-
-i8 : h = x*y^2*(x+1)^3*(y-1)^4; --SNC everywhere
-
-i9 : isSimpleNormalCrossing(h)
-
-o9 = true
-
-i10 : isSimpleNormalCrossing(h, IsLocal=>false)
-
-o10 = true
-\end{MyVerbatim}
-}
-\medspace
+\bigskip
+{\small
+\setstretch{.67}
+\begin{MyVerbatim}
+i39 : R = QQ[x, y, z];
+
+i40 : f = (y - (x - 1)^2)*y^2; --SNC at the origin, but not globally
+
+i41 : isSimpleNormalCrossing(f)
+
+o41 = true
+
+i42 : isSimpleNormalCrossing(f, IsLocal => false)
+
+o42 = false
+
+i43 : g = x*y^2*(x + 1)^3*(y - 1)^4; --SNC everywhere
+
+i44 : isSimpleNormalCrossing(g)
+
+o44 = true
+
+i45 : isSimpleNormalCrossing(g, IsLocal => false)
+
+o45 = true
+\end{MyVerbatim}
+}
+\bigskip
 
@@
 
-%             g = (y-1)^2+(x-7)^2 --doesn't even pass through the origin
+%             g = x*y^2*(x+1)^3*(y-1)^4; --SNC everywhere
 
@@
 %             isSimpleNormalCrossing(g, IsLocal=>false)
-
-%             h = x*y^2*(x+1)^3*(y-1)^4; --SNC everywhere
-
-%             isSimpleNormalCrossing(h)
-
-%             isSimpleNormalCrossing(h, IsLocal=>false)
 

### 2019-06-11 Fsing/TestIdealsPaper/TestIdeals.tex
Fixed a typo in the TestIdeals paper.
Cleaned up that typo in the TestIdeals paper further.
Added new acknolwedgements to the TestIdeals paper.

@@
 The authors thank other contributors of the \emph{TestIdeals} package, namely
-Erin Bela, Juliette Bruce, Drew Ellingson, Matthew Mastroeni, and Maral Mostafazadehfard.
+Erin Bela, Juliette Bruce, Drew Ellingson, Matthew Mastroeni, and Maral Mostafazadehfard.  We also thank Thomas Polstra for pointing out typos in a previous version of this paper.
 This paper, and the finishing touches to the \emph{TestIdeals} package, were made at the University of Utah in 2018, and the visiting authors thank the Department of Mathematics for its hospitality.
 The authors also thank the referees for their numerous useful comments on both this paper and the code.
+Additional work on the package was also done at the Institute of Mathematics and its Applications for its generous support for a 2019 Coding Sprint on the \emph{FThresholds} package.
 
@@
 
-After the test element $c$ has been identified, we pull back the ideal $\omega_R$ to an ideal $J \subseteq S$.  Next, we compute the following ascending sequence of ideals:
+After the test element $c$ has been identified, we pull back the ideal $\omega_R$ to an ideal $J \subseteq S$.
+Next, we compute the following ascending sequence of ideals where $u$ represents $T:\omega_{R^{1/p^e}} \to \omega_R$ as above:
 \begin{equation}
+{\arraycolsep=1.4pt
 \label{eq.AscendIdealExplanation}
 \begin{array}{lll}
-J_1 &\colonequals   J + (c J)^{[1/p]} & \\
-J_2 &\colonequals   J_1 + (c J_1)^{[1/p]} & = J + (c J)^{[1/p]} + (c^{1+p} J)^{[1/p^2]} \\
-J_3 &\colonequals    J_2 + (cJ_2)^{[1/p]} & = J + (c J)^{[1/p]} + (c^{1+p} J)^{[1/p^2]} + (c^{1+p+p^2} J)^{[1/p^3]} \\
+J_0 & \colonequals  cJ \\
+J_1 &\colonequals   J_0 + (u J_0)^{[1/p]} & \\
+J_2 &\colonequals   J_1 + (u J_1)^{[1/p]} & = J_0 + (u J_0)^{[1/p]} + (u^{1+p} J_0)^{[1/p^2]} \\
+J_3 &\colonequals    J_2 + (uJ_2)^{[1/p]} & = J_0 + (u J_0)^{[1/p]} + (u^{1+p} J_0)^{[1/p^2]} + (u^{1+p+p^2} J_0)^{[1/p^3]} \\
 \vdots
 \end{array}
+}
 \end{equation}

### 2019-06-11 Fsing/FThresholdsPaper/FThresholds.tex
Added new acknolwedgements to the TestIdeals paper.
Changes (mostly) to paper

@@
 \documentclass{amsart}
-\usepackage{calc,amssymb,amsthm,amsmath,amsfonts,setspace}
+\usepackage{calc,amssymb,amsthm,amsmath,amsfonts,setspace,mathtools}
 \RequirePackage[dvipsnames,usenames]{xcolor}
@@
 
+%%%%%%%%%%%%%%%%%% To-Do %%%%%%%%%%%%%%%%%%
+\usepackage[textwidth=3.3 cm,textsize=small,shadow
+%disable
+%%option disable removes the notes
+]{todonotes}
+
+\newcommand{\warning}[2][] 
+{\todo[color=red,caption={},#1]{#2}} 
+\newcommand{\postit}[2][] 
+{\todo[linecolor=orange,backgroundcolor=yellow!40, caption={},#1]{#2}} 
+\newcommand{\daniel}[2][] 
+{\todo[linecolor=green,backgroundcolor=green!10,caption={}, #1]{#2}} 
+\newcommand{\pedro}[2][] 
+{\todo[linecolor=blue,backgroundcolor=blue!10,caption={}, #1]{#2}} 
+\newcommand{\emily}[2][] 
+{\todo[linecolor=gray,backgroundcolor=gray!20,caption={}, #1]{#2}} 
+\newcommand{\karl}[2][] 
+{\todo[linecolor=niceblue,backgroundcolor=niceblue!20,caption={}, #1]{#2}}
+
 \begin{document}
@@
 
-After the advent of tight closure \cite{HochsterHunekeTC1}, the usage of Frobenius to quantify singularity|that is, deviation from regularity|proliferated, and based on a connection discovered between $F$-pure and \emph{log canonical} singularities \cite{HaraWatanabeFRegFPure}, the concept of $F$-purity was generalized to the context of \emph{pairs}.
+After the advent of tight closure \cite{HochsterHunekeTC1}, the use of Frobenius to quantify singularity|that is, deviation from regularity|proliferated, and based on a connection discovered between $F$-pure and \emph{log canonical} singularities \cite{HaraWatanabeFRegFPure}, the concept of $F$-purity was generalized to the context of \emph{pairs}.
 % $(R, f^t)$, where $f$ is an element of $R$, and $t$ is a nonnegative real number considered a formal exponent.
@@
 For example, suppose $h$ is a polynomial with integer coefficients, and that $h_p$ is the polynomial obtained by reducing the coefficients of $h$ modulo a prime $p$.
-Then, the $F$-pure thresholds of the reductions $h_p$ limit to the log canonical threshold of $h$ as $p$ tends to infinity \cite{HaraYoshidaGeneralizationOfTightClosure}.
-A related result is that of Z.~Zhu, who proved in  \cite[Corollary 4.2]{ZhuLogCanoincalThresholdsInPositiveChar} that the log canical threshold of $h$ at least the $F$-pure threshold of any reduction $h_p$.
+Then, the $F$-pure thresholds of the reductions $h_p$ converge to the log canonical threshold of $h$ as $p$ tends to infinity \cite{HaraYoshidaGeneralizationOfTightClosure}.
+A related result is that of Zhu, who proved that the log canonical threshold of $h$ is at least the $F$-pure threshold of any reduction $h_p$ \cite[Corollary 4.2]{ZhuLogCanoincalThresholdsInPositiveChar}.
 
 This latter result is interesting from a computational perspective, in that it provides lower bounds for log canonical thresholds.
-Furthermore, though there is a general purpose implementation of an algorithm for computing log canonical thresholds in the \emph{Dmodules} package by A.~Leykin and H.~Tsai \cite{DmodulesSource}, it happens that the function for computing $F$-pure thresholds contained in the \emph{FrobeniusThresholds} package is typically much faster, especially so in lower characteristic.
-Note that the  \emph{MultiplierIdeals}  package  by Z.~Teitler, B.~Snapp, and C.~Raicu also computes log canonical thresholds in many special cases, including monomial ideals, hyperplane arrangements, generic determinantal ideals, and certain binomial ideals \cite{MultiplierIdealsPackage, MultiplierIdealsArticle}.
-
-In summary,  the $F$-pure threshold is an interesting numerical invariant, and is related to many other such measures of singularity across all characteristics.
-Unfortunately, it is typically difficult to calculate, even in many concrete cases.
-Nevertheless, $F$-pure thresholds have been the focus of intense study over the past 15 years, and the package \emph{FrobeniusThresholds} is centered on calculating and estimating the $F$-pure threshold and other $F$-thresholds, with the function \texttt{fpt} at its core.
+Furthermore, though there is a general purpose implementation of an algorithm for computing log canonical thresholds in the \emph{Dmodules} package \cite{DmodulesSource}, it happens that the function for computing $F$-pure thresholds contained in the \emph{FrobeniusThresholds} package is typically much faster, especially so in low characteristic.
+Note that the  \emph{MultiplierIdeals}  package also computes log canonical thresholds in many special cases, including monomial ideals, hyperplane arrangements, generic determinantal ideals, and certain binomial ideals \cite{MultiplierIdealsPackage, MultiplierIdealsArticle}.
+
+In summary,  the $F$-pure threshold is an interesting numerical invariant, and is related to many other measures of singularity across all characteristics.
+Unfortunately, it is typically difficult to calculate.
+Nevertheless, $F$-pure thresholds have been the focus of intense study over the past fifteen years, and the package \emph{FrobeniusThresholds} is centered on calculating and estimating the $F$-pure threshold and other $F$-thresholds, with the function \texttt{fpt} at its core.
 
 \subsection{Some background and notation}
-It is important to note that much of the functionality implemented in the \emph{FrobeniusThresholds} is not restricted to regular ambient rings; see Section \ref{sec.IsFPT} for a prominent example of this.
-
-However, for the sake of concreteness, we will mostly work in a polynomial ring over a finite field of  characteristic $p>0$.
-In fact,  we will work in this context exclusively in this introduction.
-Thus, unless otherwise stated, all ring elements and ideals under consideration are regarded as elements in such a ring.
+Although much of the functionality implemented in \emph{FrobeniusThresholds} is not restricted to regular ambient rings (see Section~\ref{sec.IsFPT}), for the sake of concreteness, in this introduction  we will work in a polynomial ring over a finite field of  characteristic $p$.
+% In fact,  we will work in this context exclusively in this introduction.
+% Thus, unless otherwise stated, all ring elements and ideals under consideration are regarded as elements in such a ring.
 The ideal of this ring generated by its variables is denoted $\idealm$.
 
-Let us outline a common way in which natural numerical invariants in prime characteristic commutative algebra are often constructed:  For every natural number $e$, associate to some fixed set of data|often, a collection of polynomials and ideals|an integer describing something of relevance that depends on $e$ (e.g., the dimension of some interesting vector space constructed in terms of your initial data).
+Let us outline a way in which natural numerical invariants in prime characteristic commutative algebra are often constructed:  For every natural number $e$, associate to some fixed set of data|often, a collection of polynomials and ideals|an integer describing something of relevance that depends on $e$ (e.g., the dimension of some interesting vector space constructed in terms of your initial data).
 Finally, normalize this integer by dividing by some power of $p^e$, and then take the limit as the integer $e$ tends to infinity.
@@
 
-Consider a nonzero polynomial $f$ and a natural number $e$.  If $f$ does not vanish at the origin, then set set $\nu_f^{\idealm}(p^e) := \infty$.  Otherwise, $f \in \idealm$, and we instead define
-\[ \nu_f^{\idealm}(p^e) := \max \{ n>0 : f^n \notin \idealm^{[p^e]} \} \]
+Consider a nonzero polynomial $f$ and a natural number $e$.  If $f$ does not vanish at the origin, then set $\nu_f^{\idealm}(p^e) := \infty$.  Otherwise, $f \in \idealm$, and we instead define
+\[ \nu_f^{\idealm}(p^e) \coloneqq  \max \{ n>0 : f^n \notin \idealm^{[p^e]} \} \]
 where $\idealm^{[p^e]}$ denotes the $p^e$-th Frobenius power of $\idealm$, that is, the ideal generated by the $p^e$-th powers of the elements of $\idealm$.
-It is not very hard to see that this number is exactly the largest power of $f$ that is part of a free basis for the localization of the ambient polynomial ring at the origin, over its subring of $p^e$-th powers.
+It is not hard to see that this number is the largest power of $f$ that is part of a free basis for the localization of the ambient polynomial ring at the origin, over its subring of $p^e$-th powers.
 As noted earlier, this number also has a natural interpretation in terms of $F$-purity of pairs.
-
 Following our outline, we define
-\[ \ft^{\idealm}(f) := \lim_{e \to \infty} \frac{ \nu_f^{\idealm}(p^e)}{p^e}. \]
+\[ \ft^{\idealm}(f) \coloneqq  \lim_{e \to \infty} \frac{ \nu_f^{\idealm}(p^e)}{p^e}. \]
 
@@
 where $\tau(f^t)$ and $\sigma(f^t)$ are the \emph{test ideal} and \emph{$F$-signature}, respectively, associated to $f$ and the formal nonnegative real exponent $t$.
-The former is an ideal in the ambient ring of $f$, and the latter is a real number;  both depend on the parameter $t$ and prime $p$ in subtle ways \cite{BlickleMustataSmithDiscretenessAndRationalityOfFThresholds, BlickleSchwedeTuckerFSigPairs1}.
+The former is an ideal in the ambient ring of $f$, and the latter is a real number;  both depend on the parameter $t$ and the characteristic $p$ in subtle ways \cite{BlickleMustataSmithDiscretenessAndRationalityOfFThresholds, BlickleSchwedeTuckerFSigPairs1}.
 %Though we will not elaborate much on these topics,  we stress that the \emph{Macaulay2} package \emph{TestIdeals} provides functionality for the effective computation of test ideals in many cases \cite{TestIdealsPackage, TestIdealsPaper}.
@@
 In the literature, the $F$-pure threshold $\ft^{\idealm}(f)$ is often denoted $\fpt(f)$, for obvious reasons.
-However, in this note, we adopt the former notation to avoid any possible confusion with the \emph{Macaulay2} function \texttt{fpt} described in Section \ref{sec.FPT}.
-Indeed, the command \texttt{fpt(f)} need not always output the number $\ft^{\idealm}(f) = \fpt(f)$, though in the case that it cannot, it will provide a reasonably good estimate for this number.
+However, in this note we adopt the former notation to avoid any possible confusion with the function \texttt{fpt} described in Section~\ref{sec.FPT}, which some times does not output the number $\ft^{\idealm}(f) = \fpt(f)$, but returns, instead, lower and upper bounds for that number.
+% However, in this note we adopt the former notation to avoid any possible confusion with the function \texttt{fpt} described in Section~\ref{sec.FPT}.
+% Indeed, the command \texttt{fpt(f)} need not always output the number $\ft^{\idealm}(f) = \fpt(f)$, though in the case that it cannot, it will provide a reasonably good estimate for this number.
 
 It turns out that the sequence $\{ \nu_f^{\idealm}(p^e) \}_{e=1}^{\infty}$ itself, and not just its limit, also encodes interesting information about $f$.
-For example, it is closely related to the so-called \emph{Bernstein-Sato polynomial} \cite{MustataTakagiWatanabeFThresholdsAndBernsteinSato}.
+For example, it is closely related to the so-called \emph{Bernstein--Sato polynomial} \cite{MustataTakagiWatanabeFThresholdsAndBernsteinSato}.
 Thus, it is natural to ask whether one can recover the sequence $\{ \nu_f^{\idealm}(p^e) \}_{e=1}^{\infty}$ from the limit $\ft^{\idealm}(f)$.
@@
 %
-\[ \nu_I^J(p^e) = \max \{ n : I^n \notin J^{[p^e]} \}. \]
-Otherwise, we set $\nu_I^J(p^e) = \infty$.
+\[ \nu_I^J(p^e) \coloneqq \max \{ n : I^n \notin J^{[p^e]} \}. \]
+Otherwise, we set $\nu_I^J(p^e) \coloneqq \infty$.
 This clearly generalizes the quantity $\nu_f^{\idealm}(p^e)$ considered earlier, and we call
-\[ \ft^J(I) := \lim_{e \to \infty} \frac{ \nu_I^J(p^e)}{p^e} \]
+\[ \ft^J(I) \coloneqq  \lim_{e \to \infty} \frac{ \nu_I^J(p^e)}{p^e} \]
 the \emph{$F$-threshold of $I$ with respect to $J$}.  These numbers are also rational, when they are finite.
-The value $\ft^{\idealm}(I)$ is called the \emph{$F$-pure threshold of $I$}, and if $I = \langle f \rangle$ is principal,  $\ft^{J}(f) := \ft^J(I)$ is called the \emph{$F$-threshold of $f$ with respect to $J$}.
-Like $F$-pure thresholds, $F$-thresholds can also be defined in terms of its test ideals.
+The value $\ft^{\idealm}(I)$ is called the \emph{$F$-pure threshold of $I$}, and if $I = \langle f \rangle$ is principal,  $\ft^{J}(f) \coloneqq  \ft^J(I)$ is called the \emph{$F$-threshold of $f$ with respect to $J$}.
+Like $F$-pure thresholds, $F$-thresholds can also be defined in terms of test ideals.
 
@@
 
-\subsection{Organization}
-
-The goal of this paper is paper is to describe and illustrate the main functionality implemented in the \emph{FrobeniusThresholds} package.  We describe the organization of this paper below.
-
-\begin{itemize}
-\item[$\circ$] \autoref{sec.Nu} describes the fundamental function \texttt{nu}.  As its name suggests, this function is concerned with computing the integers $\nu_I^J(p^e)$ mentioned above.
-\item[$\circ$] \autoref{sec.IsFPT} explains the functionality for determining whether a given number is the $F$-pure threshold, or more generally, an \emph{$F$-jumping exponent}.
-\item[$\circ$] \autoref{sec.FPT} describes the features of the central function of the package, \texttt{fpt}.
-\item[$\circ$]  \autoref{sec.FutureDirections} outlines our plans for future improvements to this package.
-\end{itemize}
-%{\color{red} Move this later}
+% \subsection{Organization}
+
+% The goal of this paper is paper is to describe and illustrate the main functionality implemented in the \emph{FrobeniusThresholds} package.  We describe the organization of this paper below.
+
+% \begin{itemize}
+% \item[$\circ$] \autoref{sec.Nu} describes the fundamental function \texttt{nu}.  As its name suggests, this function is concerned with computing the integers $\nu_I^J(p^e)$ mentioned above.
+% \item[$\circ$] \autoref{sec.IsFPT} explains the functionality for determining whether a given number is the $F$-pure threshold, or more generally, an \emph{$F$-jumping exponent}.
+% \item[$\circ$] \autoref{sec.FPT} describes the features of the central function of the package, \texttt{fpt}.
+% \item[$\circ$]  \autoref{sec.FutureDirections} outlines our plans for future improvements to this package.
+% \end{itemize}
+% %{\color{red} Move this later}
 
@@
 
-\section{The \texttt{nu} function}
+\section{The {\tt nu} function}
 \label{sec.Nu}
@@
 
-We highlight some degenerate cases:  If $f$ is the zero polynomial, then \texttt{nu(e,f,J)} outputs \texttt{0}, and if $f$ is \emph{not} contained in the radical of $J$, then the output is instead \texttt{infinity}.
+% \pedro{Maybe these can be omitted.}
+% We highlight some degenerate cases:
+% If $f$ is the zero polynomial, then \texttt{nu(e,f,J)} outputs \texttt{0}, and if $f$ is \emph{not} contained in the radical of $J$, then the output is instead \texttt{infinity}.
 These degenerate cases extend analogously to the command \texttt{nu(e,I,J)}.
 
-\bigskip
-{\small
-\setstretch{.67}
-\begin{MyVerbatim}
-i7 : nu(1, 0_R, J)
-
-o7 = 0
-
-i8 : nu(1, 1_R, J)
-
-o8 = infinity
-
-o8 : InfiniteNumber
-\end{MyVerbatim}
-}
-\bigskip
+% \bigskip
+% {\small
+% \setstretch{.67}
+% \begin{MyVerbatim}
+% i7 : nu(1, 0_R, J)
+
+% o7 = 0
+
+% i8 : nu(1, 1_R, J)
+
+% o8 = infinity
+
+% o8 : InfiniteNumber
+% \end{MyVerbatim}
+% }
+% \bigskip
 
@@
 
-\bigskip
-{\small
-\setstretch{.67}
-\begin{MyVerbatim}
-i9 : R = ZZ/17[x,y,z];
-
-i10 : f = x^3 + y^4 + z^5;
-
-i11 : m = ideal(x, y, z);
-
-o11 : Ideal of R
-
-i12 : nu(2, f) == nu(2, f, m)
-
-o12 = true
-\end{MyVerbatim}
-}
-\bigskip
+% \bigskip
+% {\small
+% \setstretch{.67}
+% \begin{MyVerbatim}
+% i9 : R = ZZ/17[x,y,z];
+
+% i10 : f = x^3 + y^4 + z^5;
+
+% i11 : m = ideal(x, y, z);
+
+% o11 : Ideal of R
+
+% i12 : nu(2, f) == nu(2, f, m)
+
+% o12 = true
+% \end{MyVerbatim}
+% }
+% \bigskip
 
@@
 
-It is well known that if $q=p^e$ for some nonnegative integer $e$, then \[ \nu_I^J(qp) = \nu_I^J(q)\cdot p + L\]  where the error term $L$ is nonnegative, and can be explicitly bounded from above in terms of $p$ and the number of generators of $I$ and $J$.
-For instance, the error term $L$ is at most $p-1$ when $I$ is principal and $J$ is arbitrary.
-
-This implies that when searching for the maximal exponent defining \texttt{nu(e,I,J)} for positive $e$, it is safe to start at $p$ times the output of \texttt{nu(e-1,I,J)}, and one needn't search too far past this number.
-This also suggests that the most efficient way to compute \texttt{nu(e,I,J)} is to compute, successively, \texttt{nu(s,I,J)}, for each integer $s = 0,\ldots,e$.
-This is indeed how the computation is done in most cases.
-
+\subsection{Options for \texttt{nu}}
+
+We now describe the options available for the function \texttt{nu}.
 As pointed out in the introduction, if $f \in \mathfrak{m}$, the values $\nu^{\mathfrak{m}}_f(p^e)$ can be recovered from the $F$-pure threshold of $f$.
-This fact is used to speed up computations for certain polynomials whose $F$-pure thresholds can be computed quickly via specialized algorithms, namely diagonal polynomials, binomials, and forms in two variables (see Section \ref{sec.FPT}).
+This is used to speed up computations for certain polynomials whose $F$-pure thresholds can be computed quickly via specialized algorithms, namely diagonal polynomials, binomials, and forms in two variables (see Section \ref{sec.FPT}).
 This feature can be disabled by setting the option \texttt{UseSpecialAlgorithms} (default value \texttt{true}) to \texttt{false}.
 Consider the following example, where $f$ is a diagonal polynomial.
-
+\todo{Explain why the user might want to disable this.}
 \bigskip
@@
 
-i15 : time nu(3, f)
-     -- used 0.0108065 seconds
-
-o15 = 3756
-
-o15 : QQ
-
-i16 : time nu(3, f, UseSpecialAlgorithms => false)
-     -- used 0.209325 seconds
-
-o16 = 3756
+i15 : time nu(5, f)
+     -- used 0.00573794 seconds
+
+o15 = 1085772
+
+i16 : time nu(5, f, UseSpecialAlgorithms => false)
+     -- used 0.492965 seconds
+
+o16 = 1085772
 \end{MyVerbatim}
@@
 
-\subsection{Options for \texttt{nu}}
-
-We now describe the options available for the function \texttt{nu}.
-We focus primarily on the case where the second input is an ideal $I$, since the options work analogously when it is instead a polynomial $f$.
+% \subsection{Options for \texttt{nu}}
+
+% We now describe the options available for the function \texttt{nu}.
+%We focus primarily on the case where the second input is an ideal $I$, since the options work analogously when it is instead a polynomial $f$.
 
 In general, the function \texttt{nu} works by searching through a list of integers $n$, and checking containments of the $n$-th power of $I$ in a specified Frobenius power of $J$.
-The user can specify how this search is approached through the  option \texttt{Search}.
+It is well known that if $q=p^e$ for some nonnegative integer $e$, then \[ \nu_I^J(qp) = \nu_I^J(q)\cdot p + L,\]  where the error term $L$ is nonnegative, and can be explicitly bounded from above in terms of $p$ and the number of generators of $I$ and $J$.
+For instance, the error term $L$ is at most $p-1$ when $I$ is principal and $J$ is arbitrary.
+This implies that when searching for the maximal exponent defining \texttt{nu(e,I,J)} for positive $e$, it is safe to start at $p$ times the output of \texttt{nu(e-1,I,J)}, and one needn't search too far past this number.
+This also suggests that the most efficient way to compute \texttt{nu(e,I,J)} is to compute, successively, \texttt{nu(s,I,J)}, for each integer $s = 0,\ldots,e$.
+This is indeed how the computation is done in most cases.
+
+The user can specify how the search is approached through the  option \texttt{Search}.
 Namely, a binary search is used when \texttt{Search} is set to \texttt{Binary} (and this is the option's default value), and a linear search is run when it is set to \texttt{Linear}.
@@
 i17 : R = ZZ/5[x,y,z];
-
-i18 : f = x^2*y^4 + y^2*z^7 + z^2*x^8;
-
-i19 : time nu(5, f) -- uses binary search (default)
-     -- used 0.350179 seconds
-
-o19 = 1124
-
-i20 : time nu(5, f, Search => Linear)
-     -- used 0.485823 seconds
-
-o20 = 1124
 
@@
 %R = ZZ/5[x,y,z];
-%f = x^2*y^4 + y^2*z^7 + z^2*x^8;
-% time nu(5, f) -- uses binary search (default)
-% time nu(5, f, Search => Linear)
+%--f = x^2*y^4 + y^2*z^7 + z^2*x^8;
+%-- time nu(5, f) -- uses binary search (default)
+%-- time nu(5, f, Search => Linear)
 % M = ideal(x, y, z);
@@
 
-If the option \texttt{ReturnList} is changed from its default value of \texttt{false} to \texttt{true}, rather than simply outputting $\nu_I^J(p^e)$, \texttt{nu} outputs a list of the values $\nu_I^J(p^s)$, for $s=0,\ldots,e$.
-Alternatively, the same information can be found by setting the option \texttt{Verbose} to \texttt{true} (its default value is \texttt{false}), to request that each of these values $\nu_I^J(p^s)$ is printed as they are iteratively computed.
+If the option \texttt{ReturnList} is changed from its default value of \texttt{false} to \texttt{true}, rather than simply outputting $\nu_I^J(p^e)$, \texttt{nu} outputs a list of the values $\nu_I^J(p^s)$, for $s=0,\ldots,e$, at no additional computational cost.
+Alternatively, the same information can be found by setting the option \texttt{Verbose} to \texttt{true} (its default value is \texttt{false}), to request that each of these values $\nu_I^J(p^s)$ be printed as they are iteratively computed.
 This can also serve a way to monitor the progress of the computation.
@@
 Recall that $\nu_I^\idealm(p^e)$ can be interpreted as the maximum integer $n$ for which $(I^n)^{[1/p^e]}$ is not contained in $\idealm$. 
-When computing its value globally, it is the maximum integer $n$ for which $(I^n)^{[1/p^e]} \neq R$.  When 
-the value of \texttt{IsLocal} is set to \texttt{false} (from its default value \texttt{true}), then \texttt{nu} instead determines this maximal integer $n$, which can also be characterized as the minimal integer $\nu_I^\mathfrak{n}(p^e)$ as $\mathfrak{n}$ varies among all maximal ideals of $R$.
+When computing its value globally, it is the maximum integer $n$ for which $(I^n)^{[1/p^e]}$ is not the unit ideal.  When 
+the value of \texttt{IsLocal} is set to \texttt{false} (from its default value \texttt{true}), then \texttt{nu} instead determines this maximal integer $n$, which can also be characterized as the minimal integer $\nu_I^\mathfrak{n}(p^e)$ as $\mathfrak{n}$ varies among all maximal ideals of the ring.
 
@@
 
-\section{\texttt{isFPT}, \texttt{compareFPT} and \texttt{isFJumpingExponent}}
+\section{{\tt isFPT}, {\tt compareFPT} and {\tt isFJumpingExponent}}
 \label{sec.IsFPT}
@@
 
-\section{The \texttt{fpt} function}
+\section{The {\tt fpt} function}
 \label{sec.FPT}
@@
 If neither endpoint is the $F$-pure threshold and \texttt{Attempts} is set to more than \texttt{2}, then  additional checks are performed at certain numbers within the interval.
-First, a number in the interval is selected, according to criteria specified by the value of the option \texttt{GuessStrategy}; we refer the reader for the documentation of this option for more details.
+First, a number in the interval is selected, according to criteria specified by the value of the option \texttt{GuessStrategy}; we refer the reader to the documentation of this option for more details.
 Then the function \texttt{compareFPT} is used to test that number.
-If that ``guess'' is correct, its value is returned; otherwise, the data returned by \texttt{compareFPT} is used to narrow down the interval, and this process is repeated as many times as specified by \texttt{Attempts}.
+If that ``guess'' is correct, its value is returned; otherwise, the information returned by \texttt{compareFPT} is used to narrow down the interval, and this process is repeated as many times as specified by \texttt{Attempts}.
 
@@
 
-i40 : f = (y - (x - 1)^2)*y^2; --SNC at the origin, but not globally
+i40 : f = (y - (x - 1)^2)*y^2;
 
@@
 o42 = false
-
-i43 : g = x*y^2*(x + 1)^3*(y - 1)^4; --SNC everywhere
-
-i44 : isSimpleNormalCrossing(g)
-
-o44 = true
-
-i45 : isSimpleNormalCrossing(g, IsLocal => false)
-
-o45 = true
 \end{MyVerbatim}
@@
 
-One natural future direction would be to better incorporate the test ideals $\tau(I^t)$ when computing $F$-thresholds in the case that the ideal $I$ is not necessarily principal.
-The theoretical foundation for computing such ideals has already largely been worked out in the paper \cite{SchwedeTuckerTestIdealsOfNonPrincipal}, but such an update to the \emph{FrobeniusThresholds} package would likely the
-\emph{TestIdeals} package to be updated first.
-
-At the moment, the specialized algorithm called by the \texttt{fpt} function for computing the $F$-pure threshold of a homogeneous polynomial in two variables limits us to working with the standard grading on the ambient polynomial ring.
-Clearly, it is desirable to be able to work with non-standard gradings as well, and results in the paper \cite{HernandezTeixeiraFThresholdFunctions} suggest an algorithm for doing so.
-Thus, the package could be improved by finalizing, and implementing, such an algorithm.
-
-Finally, it would be natural to to develop, and implement,  additional algorithms for computing $F$-pure threshold and $F$-jumping numbers in specialized situations apart from monomials, diagonals, binomials, and simple normal crossings.
-The first, third, and fourth authors, along with Josep \'Alvarez Montaner and Jack Jeffries,  are currently working on developing such algorithms.
-The theoretical foundation of these algorithms lies in polyhedral geometry and integer programming, and as such, should be able to be implemented in \emph{Macaualy2}.
+One natural direction of development would be to better incorporate the test ideals $\tau(I^t)$ when computing $F$-thresholds when the ideal $I$ is nonprincipal.
+The theoretical foundation for computing such test ideals has already been laid out in \cite{SchwedeTuckerTestIdealsOfNonPrincipal}, but such an update to the \emph{FrobeniusThresholds} package would require the  \emph{TestIdeals} package to be updated first.
+
+At the moment, the specialized algorithms called by the \texttt{fpt} function for computing the $F$-pure threshold of a homogeneous polynomial in two variables limits us to working with the standard grading on the ambient polynomial ring.
+Clearly, it is desirable to be able to work with nonstandard gradings as well, and results of \cite{HernandezTeixeiraFThresholdFunctions} suggest an algorithm for doing so.
+Thus, the package could be improved by finalizing and implementing such an algorithm.
+
+Finally, it would be desirable to develop and implement additional algorithms for computing $F$-pure threshold and $F$-jumping numbers for additional classes of polynomials.
+The first, third, and fourth authors, along with Josep \'Alvarez Montaner, Jack Jeffries, and Luis N\'u\~nez-Betancourt,  are currently working on developing such algorithms.
+The theoretical foundation of these algorithms lies in polyhedral geometry and integer programming, making them natural candidates for  implementation in \emph{Macaulay2}.
 

### 2019-06-11 Fsing/FThresholdsPaper/FThresholds.tex

@@
 
-One natural direction of development would be to better incorporate the test ideals $\tau(I^t)$ when computing $F$-thresholds when the ideal $I$ is nonprincipal.
-The theoretical foundation for computing such test ideals has already been laid out in \cite{SchwedeTuckerTestIdealsOfNonPrincipal}, but such an update to the \emph{FrobeniusThresholds} package would require the  \emph{TestIdeals} package to be updated first.
+One natural direction of development would be to better incorporate the test ideals $\tau(I^t)$ when computing $F$-thresholds in the case where the ideal $I$ is nonprincipal.
+The theoretical foundation for computing such test ideals has already largely been worked out in \cite{SchwedeTuckerTestIdealsOfNonPrincipal}, but such an update to the \emph{FrobeniusThresholds} package would require the  \emph{TestIdeals} package to be updated first.
 

### 2019-06-13 Fsing/FThresholdsPaper/FThresholds.tex
Small changes to paper
Changed some examples

@@
 \begin{MyVerbatim}
-i16 : f = x^3*y^11*(x + y)^8*(x^2 + y^3)^8;
-
-i17 : fpt(f, DepthOfSearch => 3, Attempts => 2)
-
-        3   7
-o17 = {--, ---}
-       62  125
-
-o17 : List
-
-i18 : fpt(f, DepthOfSearch => 3, Attempts => 4) -- more attempts *always*
-      improve the estimate
+i12 : f = x^3*y^11*(x + y)^8*(x^2 + y^3)^8;
+
+i13 : fpt(f, DepthOfSearch => 3, Attempts => 4)
 
         1   4
-o18 = {--, --}
+o13 = {--, --}
        20  75
 
-o18 : List
-
-i19 : fpt(f, DepthOfSearch => 3, Attempts => 4, GuessStrategy => denominator)
-      -- the exact answer, after a change of strategy
+o13 : List
+
+i14 : fpt(f, DepthOfSearch => 3, Attempts => 6)
+
+        13   4
+o14 = {---, --}
+       250  75
+
+o14 : List
+
+i15 : fpt(f, DepthOfSearch => 3, Attempts => 8)
 
        1
-o19 = --
+o15 = --
       19
 
-o19 : QQ
+o15 : QQ
 \end{MyVerbatim}
@@
 \begin{MyVerbatim}
-i23 : f = -2*x^10*y^5 - x^5*y^9 - 2*x^3*y^10 + 2*x^2*y^8 - 2*x*y^9;
-
-i24 : numeric fpt(f, DepthOfSearch => 3)
-
-o24 = {.153226, .158333}
-
-o24 : List
-
-i25 : numeric fpt(f, DepthOfSearch => 3, FinalAttempt => true)
+i2 : f = 2*x^10*y^8+x^4*y^7-2*x^3*y^8;
+
+i3 : numeric fpt(f, DepthOfSearch => 3)
+
+o3 = {.14, .144}
+
+o3 : List
+
+i4 : numeric fpt(f, DepthOfSearch => 3, FinalAttempt => true)
      -- FinalAttempt improves the estimate slightly
 
-o25 = {.153461, .158333}
-
-o25 : List
-\end{MyVerbatim}
-}
-\bigskip
-
-% f = -2*x^10*y^5 - x^5*y^9 - 2*x^3*y^10 + 2*x^2*y^8 - 2*x*y^9;
-% numeric fpt(f, DepthOfSearch => 3)
-% numeric fpt(f, DepthOfSearch => 3, FinalAttempt => true) -- FinalAttempt improves the estimate slightly
+o4 = {.142067, .144}
+
+o4 : List
+\end{MyVerbatim}
+}
+\bigskip
 
@@
 \begin{MyVerbatim}
-i26 : f = -2*x^10*y^5 - x^5*y^9 - 2*x^3*y^10 + 2*x^2*y^8 - 2*x*y^9;
-
-i27 : timing numeric fpt(f, DepthOfSearch => 3, FinalAttempt => true)
-
-o27 = {.153461, .158333}
-      -- 1.37902 seconds
-
-o27 : Time
-
-i28 : timing numeric fpt(f, DepthOfSearch => 3, Attempts => 4) -- a better
-      answer in less time
-
-o28 = {.153333, .158333}
-      -- .614248 seconds
-
-o28 : Time
-
-i29 : timing fpt(f, DepthOfSearch => 4) -- the exact answer in even less
-      time
-
-       98
-o29 = ---
-      625
-      -- .297493 seconds
-
-o29 : Time
-\end{MyVerbatim}
-}
-\bigskip
-
-% f = -2*x^10*y^5 - x^5*y^9 - 2*x^3*y^10 + 2*x^2*y^8 - 2*x*y^9;
-% timing numeric fpt(f, DepthOfSearch => 3, FinalAttempt => true)
-% timing numeric fpt(f, DepthOfSearch => 3, Attempts => 4) -- a better answer in less time
-% timing fpt(f, DepthOfSearch => 4) -- the exact answer in even less time
+i35 : time numeric fpt(f, DepthOfSearch => 3, FinalAttempt => true)
+     -- used 0.684759 seconds
+
+o35 = {.142067, .144}
+
+o35 : List
+
+i36 : time fpt(f, DepthOfSearch => 3, Attempts => 7) 
+     -- used 0.405148 seconds
+
+      1
+o36 = -
+      7
+
+o36 : QQ
+
+i37 : time fpt(f, DepthOfSearch => 4) 
+     -- used 0.365025 seconds
+
+      1
+o37 = -
+      7
+
+o37 : QQ
+\end{MyVerbatim}
+}
+\bigskip
 
@@
 
-\bigskip
-{\small
-\setstretch{.67}
-\begin{MyVerbatim}
-i30 : f = x^7*y^5*(x + y)^5*(x^2 + y^3)^4;
-
-i31 : fpt(f, DepthOfSearch => 3, FinalAttempt => true, Verbose => true)
+\pedro[inline]{
+   Maybe the example below could be omitted, to shorten the paper.
+   I think that just telling the reader that the interval is printed when Verbose is activated is enough.
+}
+
+\bigskip
+{\small
+\setstretch{.67}
+\begin{MyVerbatim}
+i39 : fpt(f, DepthOfSearch => 3, FinalAttempt => true, Verbose => true)
 
@@
 
-ν has been computed: ν = ν(3,f) = 9 ...
-
-fpt lies in the interval [ν/(p^e-1),(ν+1)/p^e] = [9/124,2/25] ...
+ν has been computed: ν = ν(3,f) = 17 ...
+
+fpt lies in the interval [ν/(p^e-1),(ν+1)/p^e] = [17/124,18/125] ...
 
@@
 
-guessFPT narrowed the interval down to (3/40,2/25) ...
+guessFPT narrowed the interval down to (7/50,18/125) ...
 
@@
 
-First F-signature computed: s(f,(ν-1)/p^e) = 456/15625 ...
-
-Second F-signature computed: s(f,ν/p^e) = 64/15625 ...
-
-Computed F-signature secant line intercept: 449/6125 ...
-
-F-signature computation failed to find an improved lower bound ...
+First F-signature computed: s(f,(ν-1)/p^e) = 793/15625 ...
+
+Second F-signature computed: s(f,ν/p^e) = 342/15625 ...
+
+Computed F-signature secant line intercept: 8009/56375 ...
+
+F-signature intercept is an improved lower bound;
+Using F-regularity to check if it is the fpt ...
+
+The new lower bound is not the fpt ...
 
@@
 
-fpt lies in the interval (3/40,2/25).
-
-        3   2
-o31 = {--, --}
-       40  25
-
-o31 : List
+fpt lies in the interval (8009/56375,18/125).
+
+        8009   18
+o39 = {-----, ---}
+       56375  125
+
+o39 : List
 \end{MyVerbatim}

### 2019-06-16 Fsing/FrobeniusThresholdsPaper/FrobeniusThresholds.tex
Did universal change IsLocal => AtOrigin.

--- 2019-06-13 Fsing/FThresholdsPaper/FThresholds.tex
@@
 
-The last option we describe for \texttt{nu} is \texttt{IsLocal}.
+The last option we describe for \texttt{nu} is \texttt{AtOrigin}.
 Recall that $\nu_I^\idealm(p^e)$ can be interpreted as the maximum integer $n$ for which $(I^n)^{[1/p^e]}$ is not contained in $\idealm$. 
 When computing its value globally, it is the maximum integer $n$ for which $(I^n)^{[1/p^e]}$ is not the unit ideal.  When 
-the value of \texttt{IsLocal} is set to \texttt{false} (from its default value \texttt{true}), then \texttt{nu} instead determines this maximal integer $n$, which can also be characterized as the minimal integer $\nu_I^\mathfrak{n}(p^e)$ as $\mathfrak{n}$ varies among all maximal ideals of the ring.
+the value of \texttt{AtOrigin} is set to \texttt{false} (from its default value \texttt{true}), then \texttt{nu} instead determines this maximal integer $n$, which can also be characterized as the minimal integer $\nu_I^\mathfrak{n}(p^e)$ as $\mathfrak{n}$ varies among all maximal ideals of the ring.
 
@@
 
-i37 : nu(1, f, IsLocal => false)
+i37 : nu(1, f, AtOrigin => false)
 
@@
 \texttt{compareFPT(t, f)} returns {\tt-1}, \texttt{0}, or \texttt{1} when $t$ is less than, equal to, or greater than, respectively, the $F$-pure threshold of $f$.
-Setting the option \texttt{IsLocal} to \texttt{true} tells the function to consider the $F$-pure threshold at the origin.
+Setting the option \texttt{AtOrigin} to \texttt{true} tells the function to consider the $F$-pure threshold at the origin.
 The following example illustrates this functionality.
@@
 
-i4 : isFPT(1/2, z - 1, IsLocal => true)
+i4 : isFPT(1/2, z - 1, AtOrigin => true)
 
@@
 
-Finally, we point out that one can set the option \texttt{IsLocal} from its default value of \texttt{true} to \texttt{false}, to compute the $F$-pure threshold globally.
+Finally, we point out that one can set the option \texttt{AtOrigin} from its default value of \texttt{true} to \texttt{false}, to compute the $F$-pure threshold globally.
 In other words, it computes the minimum of the $F$-pure threshold at all maximal ideals.
@@
 
-i34 : fpt(f, IsLocal => false)
+i34 : fpt(f, AtOrigin => false)
 
@@
 % f = (y-1)^2-(x-1)^3;
-% fpt(f, IsLocal => false)
+% fpt(f, AtOrigin => false)
 % fpt(f)
@@
 The function \texttt{isSimpleNormalCrossing} is exposed to the user, so can be used independent of any $F$-pure threshold calculation.
-If the user sets its option \texttt{IsLocal} to \texttt{true} (its default value is \texttt{false}), then the function checks whether the $f_i$ are in simple normal crossing \emph{everywhere}, which can be much slower since Jacobian ideals are computed.
+If the user sets its option \texttt{AtOrigin} to \texttt{true} (its default value is \texttt{false}), then the function checks whether the $f_i$ are in simple normal crossing \emph{everywhere}, which can be much slower since Jacobian ideals are computed.
 Consider the following example illustrating this functionality.
@@
 
-i42 : isSimpleNormalCrossing(f, IsLocal => false)
+i42 : isSimpleNormalCrossing(f, AtOrigin => false)
 
@@
 
-%             isSimpleNormalCrossing(f, IsLocal=>false)
+%             isSimpleNormalCrossing(f, AtOrigin=>false)
 
@@
 
-%             isSimpleNormalCrossing(g, IsLocal=>false)
+%             isSimpleNormalCrossing(g, AtOrigin=>false)
 

### 2019-06-16 Fsing/TestIdealsPaper/TestIdeals.tex
Added a thank to the referees as we ll.
Did universal change IsLocal => AtOrigin.

@@
 The authors thank other contributors of the \emph{TestIdeals} package, namely
-Erin Bela, Juliette Bruce, Drew Ellingson, Matthew Mastroeni, and Maral Mostafazadehfard.  We also thank Thomas Polstra for pointing out typos in a previous version of this paper.
+Erin Bela, Juliette Bruce, Drew Ellingson, Matthew Mastroeni, and Maral Mostafazadehfard.
+We also thank the referees as well as Thomas Polstra for pointing out typos in a previous version of this paper.
+We also thank the referees for numerous useful comments on the package.
 This paper, and the finishing touches to the \emph{TestIdeals} package, were made at the University of Utah in 2018, and the visiting authors thank the Department of Mathematics for its hospitality.
@@
 can choose to check $F$-injectivity only at the origin by setting the
-option \texttt{IsLocal} to  \texttt{true}.
+option \texttt{AtOrigin} to  \texttt{true}.
 
@@
 
-i3 : isFInjective(R, IsLocal => true) -- but is F-injective at the origin
+i3 : isFInjective(R, AtOrigin => true) -- but is F-injective at the origin
 
@@
 The default behavior of \texttt{isFRegular} is that it checks for strong $F$-regularity
-globally. If the option \texttt{IsLocal} is set to \texttt{true}, the algorithm will only
+globally. If the option \texttt{AtOrigin} is set to \texttt{true}, the algorithm will only
 check $F$-regularity at the origin, by checking whether the computed test ideal is in the irrelevant ideal.
@@
 
-i3 : isFRegular(R, IsLocal => true) -- but is F-regular at the origin
+i3 : isFRegular(R, AtOrigin => true) -- but is F-regular at the origin
 
@@
 
-i7 : isFRegular(5/6, f, IsLocal => true) -- but is F-regular at the origin
+i7 : isFRegular(5/6, f, AtOrigin => true) -- but is F-regular at the origin
 
@@
 \not\subseteq \mathfrak{m}^{[p]}$.
-When \texttt{IsLocal} is set to \texttt{true}, the algorithm checks $F$-purity only at the origin, by explicitly checking the above
-containment. When \texttt{IsLocal} is set to \texttt{false}, which is its default value, the
+When \texttt{AtOrigin} is set to \texttt{true}, the algorithm checks $F$-purity only at the origin, by explicitly checking the above
+containment. When \texttt{AtOrigin} is set to \texttt{false}, which is its default value, the
 algorithm computes the non $F$-pure locus, by applying \texttt{frobeniusRoot}
@@
 these options are set to \texttt{false} and \texttt{Substitution}, respectively.
-Finally, if \texttt{IsLocal} is set to \texttt{true}, then $F$-rationality is checked only at the origin.
+Finally, if \texttt{AtOrigin} is set to \texttt{true}, then $F$-rationality is checked only at the origin.
 

### 2019-06-16 Fsing/TestIdealsPaper/TestIdeals_BACKUP_5127.tex
Did universal change IsLocal => AtOrigin.

@@
 
-By default the algorithm checks for $F$-injectivity everywhere however one can choose to check $F$-injectivity only at the origin by setting the option {\tt IsLocal => true}.
+By default the algorithm checks for $F$-injectivity everywhere however one can choose to check $F$-injectivity only at the origin by setting the option {\tt AtOrigin => true}.
 \begin{verbatim}
@@
 o3 = false
-i4 : isFinjective(R, IsLocal=>true)
+i4 : isFinjective(R, AtOrigin=>true)
 o4 = true
@@
 The default behavior of {\tt isFregular} checks for strong $F$-regularity everywhere.
-If the option {\tt IsLocal => true}, the algorithm will only check at the origin (this uses a similar computation but checks for the containment of $(1)$ instead of the test ideal plus the maximal ideal at the origin).
+If the option {\tt AtOrigin => true}, the algorithm will only check at the origin (this uses a similar computation but checks for the containment of $(1)$ instead of the test ideal plus the maximal ideal at the origin).
 Below is an example for both a ring and a pair.
@@
 o3 = false
-i4 : isFregular(R, IsLocal=>true)
+i4 : isFregular(R, AtOrigin=>true)
 o4 = true
@@
 o7 = false
-i8 : isFregular(5/6, f, IsLocal=>true)
+i8 : isFregular(5/6, f, AtOrigin=>true)
 o8 = true

### 2019-06-16 Fsing/TestIdealsPaper/TestIdeals_REMOTE_5127.tex
Did universal change IsLocal => AtOrigin.

@@
 
-By default the algorithm checks for $F$-injectivity everywhere however one can choose to check $F$-injectivity only at the origin by setting the option {\tt IsLocal => true}. 
+By default the algorithm checks for $F$-injectivity everywhere however one can choose to check $F$-injectivity only at the origin by setting the option {\tt AtOrigin => true}. 
 \begin{verbatim}

### 2019-06-16 Fsing/FrobeniusThresholdsPaper/FrobeniusThresholds.tex
Added/responded to some comments in the paper .tex file

@@
 \todo{Explain why the user might want to disable this.}
+\daniel{Why would one want to do this?}
+
 \bigskip
@@
 
+\daniel[inline]{I like the explanation provided by activating Verbose, and so I kind of think that it would be cool to show this off.
+However, I also understand if others want to omit it, and I wouldn't object if anyone has a strong preference.}
+
+\daniel[inline]{Should the line 
+\begin{center}
+ν has been computed: ν = ν(3,f) = 17 ...
+\end{center}
+instead be
+\begin{center}
+ν has been computed: ν = nu(3,f) = 17 ...
+\end{center}
+on the 5th line of the Verbose output?  I think this would be consistent with the paper, but whoever wrote this might have had a specific reason for doing it this way.
+}
+
 \bigskip

### 2019-06-17 Fsing/FrobeniusThresholdsPaper/FrobeniusThresholds.tex
Changes to paper

@@
 \begin{abstract}
-   This article describes the \emph{Macaulay2} package \emph{FrobeniusThresholds}.
-   This package is designed to estimate and calculate $F$-pure thresholds, more general $F$-thresholds, and related numerical invariants arising in the study of singularities in prime characteristic commutative algebra.
+   This article describes the \emph{Macaulay2} package \emph{FrobeniusThresholds}, designed to estimate and calculate $F$-pure thresholds, more general $F$-thresholds, and related numerical invariants arising in the study of singularities in prime characteristic commutative algebra.
 \end{abstract}
@@
 
-\keywords{Macaulay2, Frobenius, $F$-singularity, $F$-pure threshold, $F$-threshold}
+\keywords{\emph{Macaulay2}, Frobenius, $F$-singularity, $F$-pure threshold, $F$-threshold}
 
@@
 
-This paper describes the \emph{Macaulay2} package \emph{FrobeniusThresholds} \cite{M2, FThresholdsPackage}.
-This package provides tools for computing certain fundamental invariants in positive characteristic commutative algebra.
-More precisely, this package concerns the effective computation of \emph{$F$-pure thresholds}, \emph{$F$-thresholds}, and \emph{$F$-jumping exponents}.
-
-Recall that a ring of prime characteristic $p>0$ is said to be \emph{$F$-pure} if the Frobenius map|that is, the ring endomorphism sending an element to its $p$-th power|is a pure morphism;  under natural geometric hypotheses, this is equivalent to the condition that the Frobenius morphism splits as a map of rings.
-
-The concept of $F$-purity has proven to be important in commutative algebra, and has a rich history.  Indeed, it first appeared in the work
-of Hochster and Roberts to study local cohomology \cite{HochsterRobertsFrobeniusLocalCohomology}, was compared with rational singularities in  \cite{FedderFPureRat}, and was used to study global properties of Schubert varieties in \cite{MehtaRamanathanFrobeniusSplittingAndCohomologyVanishing}.
-
-After the advent of tight closure \cite{HochsterHunekeTC1}, the use of Frobenius to quantify singularity|that is, deviation from regularity|proliferated, and based on a connection discovered between $F$-pure and \emph{log canonical} singularities \cite{HaraWatanabeFRegFPure}, the concept of $F$-purity was generalized to the context of \emph{pairs}.
+This paper describes the \emph{Macaulay2} package \emph{FrobeniusThresholds} \cite{M2, FThresholdsPackage}, which provides tools for computing or estimating certain fundamental invariants in positive characteristic commutative algebra, namely \emph{$F$-pure thresholds}, \emph{$F$-thresholds}, and \emph{$F$-jumping exponents}.
+Recall that a ring of prime characteristic $p>0$ is \emph{$F$-pure} if the Frobenius map|that is, the ring endomorphism sending an element to its $p$-th power|is a pure morphism;  under natural geometric hypotheses, this is equivalent to the condition that the Frobenius morphism splits as a map of rings.
+The concept of $F$-purity has proven to be important in commutative algebra, and has a rich history.
+Indeed, it first appeared in the work of Hochster and Roberts to study local cohomology \cite{HochsterRobertsFrobeniusLocalCohomology}, was compared with rational singularities in  \cite{FedderFPureRat}, and was used to study global properties of Schubert varieties in \cite{MehtaRamanathanFrobeniusSplittingAndCohomologyVanishing}.
+
+After the advent of tight closure \cite{HochsterHunekeTC1}, the use of the Frobenius map to quantify singularity|that is, deviation from regularity|proliferated, and based on a connection discovered between $F$-pure and \emph{log canonical} singularities \cite{HaraWatanabeFRegFPure}, the concept of $F$-purity was generalized to the context of \emph{pairs}.
 % $(R, f^t)$, where $f$ is an element of $R$, and $t$ is a nonnegative real number considered a formal exponent.
-
-Along these lines, the \emph{$F$-pure threshold} %associated to an element of $R$
-was defined in analogy with the \emph{log canonical threshold} \cite{TakagiWatanabeFPureThresh}, and
-%The $F$-pure threshold of the pair $(R, f)$ is the supremum over all $t$ for which $(R, f^t)$ is $F$-pure.
-\emph{$F$-thresholds} were then introduced as a family of invariants that naturally extend the notion of an $F$-pure threshold \cite{MustataTakagiWatanabeFThresholdsAndBernsteinSato}.
-
-Though the $F$-pure threshold is defined in analogy with the log canonical threshold, their connection extends beyond mere analogy.
+Along these lines, the \emph{$F$-pure threshold} was defined in analogy with the \emph{log canonical threshold} \cite{TakagiWatanabeFPureThresh}, and \emph{$F$-thresholds} were introduced as a natural extension \cite{MustataTakagiWatanabeFThresholdsAndBernsteinSato}.
+
+The connection between the $F$-pure threshold and the log canonical threshold, however, extends beyond mere analogy.
 For example, suppose $h$ is a polynomial with integer coefficients, and that $h_p$ is the polynomial obtained by reducing the coefficients of $h$ modulo a prime $p$.
@@
 This latter result is interesting from a computational perspective, in that it provides lower bounds for log canonical thresholds.
-Furthermore, though there is a general purpose implementation of an algorithm for computing log canonical thresholds in the \emph{Dmodules} package \cite{DmodulesSource}, it happens that the function for computing $F$-pure thresholds contained in the \emph{FrobeniusThresholds} package is typically much faster, especially so in low characteristic.
-Note that the  \emph{MultiplierIdeals}  package also computes log canonical thresholds in many special cases, including monomial ideals, hyperplane arrangements, generic determinantal ideals, and certain binomial ideals \cite{MultiplierIdealsPackage, MultiplierIdealsArticle}.
-
-In summary,  the $F$-pure threshold is an interesting numerical invariant, and is related to many other measures of singularity across all characteristics.
+Though there is a general purpose implementation of an algorithm for computing log canonical thresholds in the \emph{Dmodules} package \cite{DmodulesSource}\footnote{The  \emph{MultiplierIdeals}  package also computes log canonical thresholds in many special cases, including monomial ideals, hyperplane arrangements, generic determinantal ideals, and certain binomial ideals \cite{MultiplierIdealsPackage, MultiplierIdealsArticle}.
+}, the function for computing $F$-pure thresholds contained in the \emph{FrobeniusThresholds} package is typically much faster, especially so in low characteristic.
+
+In summary,  the $F$-pure threshold is an interesting numerical invariant, related to many other measures of singularity across all characteristics, and has been the focus of intense study over the past fifteen years.
 Unfortunately, it is typically difficult to calculate.
-Nevertheless, $F$-pure thresholds have been the focus of intense study over the past fifteen years, and the package \emph{FrobeniusThresholds} is centered on calculating and estimating the $F$-pure threshold and other $F$-thresholds, with the function \texttt{fpt} at its core.
+The package \emph{FrobeniusThresholds} is centered on calculating and estimating the $F$-pure threshold and other $F$-thresholds, with the function \texttt{fpt} at its core.
+It builds heavily upon the \emph{TestIdeals} package for \emph{Macaulay2} \cite{TestIdealsPackage, TestIdealsPaper}, which provides a broad range of functionality for effective computation in prime characteristic commutative algebra.
+In fact, both this package and \emph{TestIdeals} are derived from, and have greatly expanded, the older package \emph{PosChar}.
 
 \subsection{Some background and notation}
-Although much of the functionality implemented in \emph{FrobeniusThresholds} is not restricted to regular ambient rings (see Section~\ref{sec.IsFPT}), for the sake of concreteness, in this introduction  we will work in a polynomial ring over a finite field of  characteristic $p$.
+Although some of the functionality implemented in \emph{FrobeniusThresholds} is not restricted to regular ambient rings (see Section~\ref{sec.IsFPT}), for the sake of concreteness, in this introduction  we will work in a polynomial ring over a finite field of  characteristic $p$.
 % In fact,  we will work in this context exclusively in this introduction.
@@
 
-Let us outline a way in which natural numerical invariants in prime characteristic commutative algebra are often constructed:  For every natural number $e$, associate to some fixed set of data|often, a collection of polynomials and ideals|an integer describing something of relevance that depends on $e$ (e.g., the dimension of some interesting vector space constructed in terms of your initial data).
-Finally, normalize this integer by dividing by some power of $p^e$, and then take the limit as the integer $e$ tends to infinity.
-The resulting limit, if it exists, should then encode some interesting information about your initial set of data.
+Let us outline a way in which natural numerical invariants in prime characteristic commutative algebra are often constructed:  For every natural number $e$, associate to some fixed data---often, a collection of polynomials or ideals---an integer describing something of relevance that depends on $e$ (e.g., the dimension of some interesting vector space constructed in terms of your initial data).
+Normalize this integer by dividing by some power of $p^e$, and then take the limit as the integer $e$ tends to infinity.
+The resulting limit, if it exists, should then encode some interesting information about your initial data.
 
@@
 It is not hard to see that this number is the largest power of $f$ that is part of a free basis for the localization of the ambient polynomial ring at the origin, over its subring of $p^e$-th powers.
-As noted earlier, this number also has a natural interpretation in terms of $F$-purity of pairs.
+%As noted earlier, this number also has a natural interpretation in terms of $F$-purity of pairs.
 Following our outline, we define
@@
 
+This limit exists, and is a rational number when $f\in \idealm$, but this is far from obvious  \cite{BlickleMustataSmithDiscretenessAndRationalityOfFThresholds}.
 Inspired by its connections with the $F$-purity of pairs,  this limit is called the \emph{$F$-pure threshold} of $f$ at the origin.
-This limit exists, and is finite when $f \in \idealm$.
-In the latter case, the limit is also rational, but this is far from obvious  \cite{BlickleMustataSmithDiscretenessAndRationalityOfFThresholds}.
 
@@
 
-Finally, we point out that the  \emph{FrobeniusThresholds} package builds heavily upon the \emph{TestIdeals} package for \emph{Macaulay2} \cite{TestIdealsPackage, TestIdealsPaper}, which provides a broad range of functionality for effective computation in prime characteristic commutative algebra.
-In fact, both this package and \emph{TestIdeals} are derived from, and have greatly expanded, the older package \emph{PosChar}.
-
 % \subsection{Organization}
@@
 
-\subsection*{Acknowledgements.}  The authors enthusiastically thank everyone who helped complete the \emph{FrobeniusThresholds} package.
-Our package coauthors are Juliette Bruce and Daniel Smolkin.  Erin Bela, Zhibek Kadyrsizova, Moty Katzman, Sara Malec, and Marcus Robinson also contributed valuable code to the package.
+\subsection*{Acknowledgements.}  The authors enthusiastically thank everyone who helped complete the \emph{FrobeniusThresholds} package: the package coauthors Juliette Bruce and Daniel Smolkin, and contributors  Erin Bela, Zhibek Kadyrsizova, Moty Katzman, Sara Malec, and Marcus Robinson.
 
@@
 more generally, if a nonzero ideal $I$ is contained in the radical of $J$, then \texttt{nu(e,I,J)} outputs $\nu_I^J(p^e)$.
-Consider the following example.
-%, the maximal integer exponent $n$ such that $I^n$ is not contained in $J^{[p^e]}$.
+%Consider the following example.  %, the maximal integer exponent $n$ such that $I^n$ is not contained in $J^{[p^e]}$.
 

### 2019-06-18 Fsing/FrobeniusThresholdsPaper/FrobeniusThresholds.tex
Small changes to paper

@@
 
-\usepackage{fancyvrb}
+\usepackage{microtype}
+
 \usepackage{hyperref}
@@
 \frenchspacing
-\input{kmacros3.sty}
+%\input{kmacros3.sty}
+
+\setlength{\parskip}{0.4em}
 
@@
 \usepackage{enumerate}
-\usepackage[normalem]{ulem}
+%\usepackage[normalem]{ulem}
 %\usepackage{marginnote}
-\newcommand{\fram}{\mathfrak{m}}
+%\newcommand{\fram}{\mathfrak{m}}
+
+\usepackage{fancyvrb}
 \DefineVerbatimEnvironment%
@@
 \newcommand{\idealm}{\mathfrak{m}}
+\DeclareMathOperator{\fpt}{fpt}
 
@@
 
-This limit exists, and is a rational number when $f\in \idealm$, but this is far from obvious  \cite{BlickleMustataSmithDiscretenessAndRationalityOfFThresholds}.
+This limit exists, and is a rational number when $f\in \idealm$, though the latter is far from obvious  \cite{BlickleMustataSmithDiscretenessAndRationalityOfFThresholds}.
 Inspired by its connections with the $F$-purity of pairs,  this limit is called the \emph{$F$-pure threshold} of $f$ at the origin.
@@
 
-It turns out that the sequence $\{ \nu_f^{\idealm}(p^e) \}_{e=1}^{\infty}$ itself, and not just its limit, also encodes interesting information about $f$.
+It turns out that the sequence $\{ \nu_f^{\idealm}(p^e) \}_{e=0}^{\infty}$ itself, and not just its limit, also encodes interesting information about $f$.
 For example, it is closely related to the so-called \emph{Bernstein--Sato polynomial} \cite{MustataTakagiWatanabeFThresholdsAndBernsteinSato}.
-Thus, it is natural to ask whether one can recover the sequence $\{ \nu_f^{\idealm}(p^e) \}_{e=1}^{\infty}$ from the limit $\ft^{\idealm}(f)$.
-Fortunately, the answer to this question is yes \cite{MustataTakagiWatanabeFThresholdsAndBernsteinSato, HernandezFPurityOfHypersurfaces}.
-More precisely,
+Thus, it is natural to ask whether one can recover the sequence $\{ \nu_f^{\idealm}(p^e) \}_{e=0}^{\infty}$ from the limit $\ft^{\idealm}(f)$.
+Fortunately, the answer to this question is yes \cite{MustataTakagiWatanabeFThresholdsAndBernsteinSato, HernandezFPurityOfHypersurfaces}; for each $e$ we have
 \begin{equation*}
@@
 %Consider the following example.  %, the maximal integer exponent $n$ such that $I^n$ is not contained in $J^{[p^e]}$.
-
-\bigskip
+If the third argument is omitted from the function \texttt{nu}, it is assumed to be the maximal ideal $\idealm$.
+
+\medskip
 {\small
@@
 }
-\bigskip
-
-% R = ZZ/11[x,y];
-% I = ideal(x^2 + y^3, x*y);
-% J = ideal(x^2, y^3);
-% nu(1, I, J)
-% f = x*y*(x^2 + y^2);
-% nu(1, f, J)
-
-% \pedro{Maybe these can be omitted.}
-% We highlight some degenerate cases:
-% If $f$ is the zero polynomial, then \texttt{nu(e,f,J)} outputs \texttt{0}, and if $f$ is \emph{not} contained in the radical of $J$, then the output is instead \texttt{infinity}.
-These degenerate cases extend analogously to the command \texttt{nu(e,I,J)}.
-
-% \bigskip
-% {\small
-% \setstretch{.67}
-% \begin{MyVerbatim}
-% i7 : nu(1, 0_R, J)
-
-% o7 = 0
-
-% i8 : nu(1, 1_R, J)
-
-% o8 = infinity
-
-% o8 : InfiniteNumber
-% \end{MyVerbatim}
-% }
-% \bigskip
-
-%nu(1, 0_R, J)
-%nu(1, 1_R, J)
-
-If the third argument is omitted from the function \texttt{nu}, it is assumed to be the maximal ideal $\idealm$.
-
-% \bigskip
+\medskip
+
+% \medskip
 % {\small
@@
 % }
-% \bigskip
+% \medskip
 
@@
 As pointed out in the introduction, if $f \in \mathfrak{m}$, the values $\nu^{\mathfrak{m}}_f(p^e)$ can be recovered from the $F$-pure threshold of $f$.
-This is used to speed up computations for certain polynomials whose $F$-pure thresholds can be computed quickly via specialized algorithms, namely diagonal polynomials, binomials, and forms in two variables (see Section \ref{sec.FPT}).
-This feature can be disabled by setting the option \texttt{UseSpecialAlgorithms} (default value \texttt{true}) to \texttt{false}.
-Consider the following example, where $f$ is a diagonal polynomial.
+This is used to speed up computations for certain polynomials whose $F$-pure thresholds can be computed quickly via specialized algorithms or formulas, namely diagonal polynomials, binomials, forms in two variables, and products of factors in simple normal crossing (see Section~\ref{sec.FPT}).
+This feature can be disabled by setting the option \texttt{UseSpecialAlgorithms} (default value \texttt{true}) to \texttt{false}; in Section~\ref{ss: UseSpecialAlgorithms} we give discuss situations where the user might want to do that.
+%Consider the following example, where $f$ is a diagonal polynomial.
 \todo{Explain why the user might want to disable this.}
 \daniel{Why would one want to do this?}
-
-\bigskip
+\pedro{In Section~\ref{ss: UseSpecialAlgorithms} we give a couple of examples, so I'm pointing the reader to that section.}
+
+\medskip
 {\small
@@
 }
-\bigskip
-
-% R = ZZ/17[x,y,z];
-% f = x^3 + y^4 + z^5; -- a diagonal polynomial
-% time nu(3, f)
-% time nu(3, f, UseSpecialAlgorithms => false)
-
-% \subsection{Options for \texttt{nu}}
-
-% We now describe the options available for the function \texttt{nu}.
-%We focus primarily on the case where the second input is an ideal $I$, since the options work analogously when it is instead a polynomial $f$.
+\medskip
 
 In general, the function \texttt{nu} works by searching through a list of integers $n$, and checking containments of the $n$-th power of $I$ in a specified Frobenius power of $J$.
-It is well known that if $q=p^e$ for some nonnegative integer $e$, then \[ \nu_I^J(qp) = \nu_I^J(q)\cdot p + L,\]  where the error term $L$ is nonnegative, and can be explicitly bounded from above in terms of $p$ and the number of generators of $I$ and $J$.
+It is well known that if $q=p^e$ for some nonnegative integer $e$, then \[ \nu_I^J(qp) = \nu_I^J(q)\cdot p + L,\]  where the error term $L$ is nonnegative and can be explicitly bounded from above in terms of $p$ and the number of generators of $I$ and $J$.
 For instance, the error term $L$ is at most $p-1$ when $I$ is principal and $J$ is arbitrary.
-This implies that when searching for the maximal exponent defining \texttt{nu(e,I,J)} for positive $e$, it is safe to start at $p$ times the output of \texttt{nu(e-1,I,J)}, and one needn't search too far past this number.
-This also suggests that the most efficient way to compute \texttt{nu(e,I,J)} is to compute, successively, \texttt{nu(s,I,J)}, for each integer $s = 0,\ldots,e$.
-This is indeed how the computation is done in most cases.
-
-The user can specify how the search is approached through the  option \texttt{Search}.
-Namely, a binary search is used when \texttt{Search} is set to \texttt{Binary} (and this is the option's default value), and a linear search is run when it is set to \texttt{Linear}.
-
-\bigskip
+This implies that when searching for the maximal exponent defining \texttt{nu(e,I,J)} for positive $e$, it is safe to start at $p$ times the output of \texttt{nu(e-1,I,J)}, and one need not search too far past this number.
+This also suggests that the most efficient way to compute \texttt{nu(e,I,J)} is to compute, successively, \texttt{nu(s,I,J)}, for each integer $s = 0,\ldots,e$, and this is indeed how the computation is done in most cases.
+
+The user can specify how the search is approached through the option \texttt{Search}, which can take two values: 
+ \texttt{Binary} (the default value) and  \texttt{Linear}.
+
+\medskip
 {\small
@@
 }
-\bigskip
+\medskip
 
@@
 
-If the option \texttt{ReturnList} is changed from its default value of \texttt{false} to \texttt{true}, rather than simply outputting $\nu_I^J(p^e)$, \texttt{nu} outputs a list of the values $\nu_I^J(p^s)$, for $s=0,\ldots,e$, at no additional computational cost.
-Alternatively, the same information can be found by setting the option \texttt{Verbose} to \texttt{true} (its default value is \texttt{false}), to request that each of these values $\nu_I^J(p^s)$ be printed as they are iteratively computed.
-This can also serve a way to monitor the progress of the computation.
-
-\bigskip
+If the option \texttt{ReturnList} is changed from its default value of \texttt{false} to \texttt{true},
+% rather than simply outputting $\nu_I^J(p^e)$,
+\texttt{nu} outputs a list of the values $\nu_I^J(p^s)$, for $s=0,\ldots,e$, at no additional computational cost.
+
+\medskip
 {\small
@@
 o24 : List
-
-i25 : nu(5, f, Verbose => true)
-
-nuInternal: using comparison test FrobeniusRoot
-
-ν(1) = 0
-ν(p^1) = 1
-ν(p^2) = 8
-ν(p^3) = 44
-ν(p^4) = 224
-ν(p^5) = 1124
-
-o25 = 1124
-\end{MyVerbatim}
-}
-\bigskip
-
-%nu(5, f, ReturnList => true)
-%nu(5, f, Verbose => true)
+\end{MyVerbatim}
+}
+\medskip
+
+\noindent The same information can be found by setting the option \texttt{Verbose} to \texttt{true}, to request that the values $\nu_I^J(p^s)$ be printed as they are iteratively computed (serving also as a way to monitor the progress of the computation).
 
@@
 
-\bigskip
+\medskip
 {\small
@@
 
-The option \texttt{ContainmentTest} has a third possible value, \texttt{FrobeniusPower}, which may produce a different result than the other two values.
-Given an ideal $I$, the first, third, and fourth authors introduced the notion of a (generalized) Frobenius power $I^{[n]}$ of $I$, when $n$ is an arbitrary positive integer, not necessarily of the form $n = p^e$ \cite{hernandez+etal.frobenius_powers}.
+The option \texttt{ContainmentTest} has a third possible value, \texttt{FrobeniusPower}, which allows \texttt{nu} to compute a different but analogous invariant.
+%may produce a different result than the other two values.
+The first, third, and fourth authors introduced the notion of a (generalized) Frobenius power $I^{[n]}$ of an ideal $I$, when $n$ is an arbitrary positive integer, not necessarily of the form $n = p^e$ \cite{hernandez+etal.frobenius_powers}.
 When \texttt{ContainmentTest} is set to \texttt{FrobeniusPower}, rather than  computing $\nu_I^J(p^e)$, the function \texttt{nu} computes the maximal integer $n$ for which $I^{[n]}$ is not contained in $J^{[p^e]}$.
-This number is denoted $\mu_I^J(p^e)$ in \emph{loc.\ cit.}, and equals $\nu_I^J(p^e)$ when $I$ is replaced with a polynomial, or is a principal ideal.
+This number is denoted $\mu_I^J(p^e)$ in \emph{loc.~cit.}, and equals $\nu_I^J(p^e)$ when $I$ is a principal ideal.
 However, these number need not agree in general, as we see below.
 
-\bigskip
+\medskip
 {\small
@@
 }
-\bigskip
-
- In line with the philosophy described in the introduction, after appropriately normalizing and taking the limit as $e$ approaches infinity, the values $\mu_I^J(p^e)$ determine certain invariants of interest called \emph{critical exponents}.
+\medskip
+
+%In line with the philosophy described in the introduction, after appropriately normalizing and taking the limit as $e$ approaches infinity, the values $\mu_I^J(p^e)$ determine certain invariants of interest called \emph{critical exponents}.
 
@@
 Recall that $\nu_I^\idealm(p^e)$ can be interpreted as the maximum integer $n$ for which $(I^n)^{[1/p^e]}$ is not contained in $\idealm$. 
-When computing its value globally, it is the maximum integer $n$ for which $(I^n)^{[1/p^e]}$ is not the unit ideal.  When 
-the value of \texttt{AtOrigin} is set to \texttt{false} (from its default value \texttt{true}), then \texttt{nu} instead determines this maximal integer $n$, which can also be characterized as the minimal integer $\nu_I^\mathfrak{n}(p^e)$ as $\mathfrak{n}$ varies among all maximal ideals of the ring.
+When computing its value globally, it is the maximum integer $n$ for which $(I^n)^{[1/p^e]}$ is not the unit ideal.
+When the option \texttt{AtOrigin} is set to \texttt{false} (from its default value \texttt{true}), \texttt{nu} instead determines this maximal integer $n$, which can also be characterized as the minimal integer $\nu_I^\mathfrak{n}(p^e)$ as $\mathfrak{n}$ varies among all maximal ideals of the ring.
 
@@
 
-The \emph{FrobeniusThresholds} package contains methods to
- test candidate values for an $F$-pure threshold, and even $F$-jumping numbers, even in some singular rings.
-
+The \emph{FrobeniusThresholds} package contains methods to test candidate values for $F$-pure thresholds and $F$-jumping numbers, even in some singular rings.
 Consider a  $\mathbb{Q}$-Gorenstein ring $R$ of characteristic $p>0$, whose index not divisible by $p$.
-Given a parameter $t \in \mathbb{Q}$ and an element $f$ of $R$, the command \texttt{isFPT(t,f)} outputs \texttt{true} if $t$ is the $F$-pure threshold of $f$, and \texttt{false} otherwise.
-Moreover, the function \texttt{compareFPT} provides further information about the relationship between $t$ and the $F$-pure threshold of $f$; namely,
-\texttt{compareFPT(t, f)} returns {\tt-1}, \texttt{0}, or \texttt{1} when $t$ is less than, equal to, or greater than, respectively, the $F$-pure threshold of $f$.
+Given a parameter $t\in \mathbb{Q}$ and an element $f$ of $R$, the command \texttt{isFPT(t, f)} checks whether $t$ is the $F$-pure threshold of $f$, while \texttt{compareFPT(t, f)} provides further information, returning {\tt-1}, \texttt{0}, or \texttt{1} when $t$ is less than, equal to, or greater than the $F$-pure threshold of $f$.
 Setting the option \texttt{AtOrigin} to \texttt{true} tells the function to consider the $F$-pure threshold at the origin.
-The following example illustrates this functionality.
-
-\bigskip
+% The following example illustrates this functionality.
+
+\medskip
 {\small
@@
 }
-\bigskip
-
-The general method applied calls upon functionality from the \emph{TestIdeals} package.  The functions \texttt{testIdeal} and \texttt{FPureModule} therein are used
-to compute the test ideals of $f$ with respect to the parameter $t$, and that with respect to $t - \varepsilon$, for $\varepsilon>0$ very small.
+\medskip
+
+% The general method applied calls upon functionality from the \emph{TestIdeals} package.
+% The functions \texttt{testIdeal} and \texttt{FPureModule} therein are used to compute the test ideals of $f$ with respect to the parameter $t$, and that with respect to $t - \varepsilon$, for $0<\varepsilon\ll 1$.
 For instance, as noted in the introduction, when $R$ is a polynomial ring, $t$ is the $F$-pure threshold of $f$ if and only if $\tau(R, f^t)$ is contained in the homogeneous maximal ideal, but
-$\tau(R, f^{t-\varepsilon})$ is not.
-Note that for $R$ strongly $F$-regular and Gorenstein, \texttt{FPureModule(t, f)} precisely computes $\tau(R, f^{t-\varepsilon})$.
+% $\tau(R, f^{t-\varepsilon})$ is not.
+% Note that for $R$ strongly $F$-regular and Gorenstein, \texttt{FPureModule(t, f)} precisely computes $\tau(R, f^{t-\varepsilon})$.
+
+The general method applied calls upon functionality from the \emph{TestIdeals} package.
+The functions \texttt{testIdeal} and \texttt{FPureModule} therein are used to compute the test ideals of $f$ with respect to the parameter $t$, and that with respect to $t - \varepsilon$, for $0<\varepsilon\ll 1$.
+By comparing these test ideals, we can decide whether $t$ is the $F$-pure threshold of $f$.
+For instance, as noted in the introduction, when $R$ is a polynomial ring, $t$ is the $F$-pure threshold of $f$ at the origin if and only if $\tau(R, f^t)$ is contained in the homogeneous maximal ideal, but $\tau(R, f^{t-\varepsilon})$ is not.
+%Note that for $R$ strongly $F$-regular and Gorenstein, \texttt{FPureModule(t, f)} precisely computes $\tau(R, f^{t-\varepsilon})$.
 
@@
 
-\bigskip
-{\small
-\setstretch{.67}
-\begin{MyVerbatim}
-i1 : R = ZZ/11[x, y, z]/(x^2 - y*(z - 1));
-
-i2 : compareFPT(5/11, z - 1)
-
-o2 = -1
-
-i3 : isFPT(1/2, z - 1)
-
-o3 = true
-
-i4 : isFPT(1/2, z - 1, AtOrigin => true)
-
-o4 = false
-\end{MyVerbatim}
-}
-\bigskip
+\medskip
+{\small
+\setstretch{.67}
+\begin{MyVerbatim}
+i5 : R = ZZ/13[x, y];
+
+i6 : f = y*((y + 1) - (x - 1)^2)*(x - 2)*(x + y - 2);
+
+i7 : isFJumpingExponent(3/4, f)
+
+o7 = true
+\end{MyVerbatim}
+}
 
@@
 }
-\bigskip
-
-\subsection{The option \texttt{UseSpecialAlgorithms}}
+
+\subsection{The option \texttt{UseSpecialAlgorithms}}\label{ss: UseSpecialAlgorithms}
 
@@
 When $f$ is a diagonal polynomial, a binomial, or a form in two variables, algorithms of Hern\'andez \cite{HernandezFInvariantsOfDiagonalHyp, HernandezFPureThresholdOfBinomial}, or Hern\'andez and Teixeira \cite{HernandezTeixeiraFThresholdFunctions},  are executed to compute the $F$-pure threshold.
-Algorithms for computing $F$-pure thresholds of binomials also appear in \cite{ShibutaTakagiLCThresholds}, though they are only valid in certain special characteristics.
-
-\bigskip
+%Algorithms for computing $F$-pure thresholds of binomials also appear in \cite{ShibutaTakagiLCThresholds}, though they are only valid in certain special characteristics.
+
+\medskip
 {\small
@@
 }
-\bigskip
-
-The above noted algorithm for computing the $F$-pure threshold of a binary form $f$ requires factoring $f$ into linear forms, and \texttt{fpt} can sometimes hang when attempting that factorization, when the factorization occurs in a Galois field of excessively large order.
+\medskip
+
+The algorithm for computing the $F$-pure threshold of a binary form $f$ requires factoring $f$ into linear forms, and that may be difficult or impossible when that factorization occurs in a Galois field of excessively large order.
 This is a situation when the user will want to set the option \texttt{UseSpecialAlgorithms} to \texttt{false}.
@@
 }
-\bigskip
-
-If \texttt{UseSpecialAlgorithms} is set to \texttt{true} and $f$ does not fall into any of the aforementioned cases, then the function \texttt{fpt} next calls \texttt{isSimpleNormalCrossing(f)} to check whether the polynomial $f$ is a product of factors that are in simple normal crossing, in which case the $F$-pure threshold can easily be computed.
-For more detail on the function \texttt{isSimpleNormalCrossing} and on computing the $F$-pure threshold of a polynomial with simple normal crossings, please see Section \ref{subsec.SNC}.
+\medskip
+
+If \texttt{UseSpecialAlgorithms} is set to \texttt{true} and $f$ does not fall into any of the aforementioned cases, then the function \texttt{fpt} next calls \texttt{isSimpleNormalCrossing(f)} (see Section~\ref{subsec.SNC}) to check whether the polynomial $f$ is a product of factors that are in simple normal crossing, in which case the $F$-pure threshold is simply the reciprocal of the largest multiplicity occurring in that factorization.
+% If \texttt{isSimpleNormalCrossing(f)} outputs true, then the $F$-pure threshold is easily computed, since is just the minimum of the values $1/a_i$, for $1 \leq i \leq n$.
+Note that the function \texttt{factor} is called whenever \texttt{isSimpleNormalCrossing} is used, which can sometimes make the verification slow.
+The user can avoid this by setting \texttt{UseSpecialAlgorithms} to \texttt{false}.
 
@@
 }
+\medskip
 
@@
 }
-
-\bigskip
+\pedro[inline]{I modified the code, to produce the output you suggested.}
+
+\medskip
 {\small
@@
 
-\bigskip
-{\small
-\setstretch{.67}
-\begin{MyVerbatim}
-i32 : R = ZZ/7[x,y];
-
-i33 : f = (y - 1)^2-(x - 1)^3;
-
-i34 : fpt(f, AtOrigin => false)
+\medskip
+{\small
+\setstretch{.67}
+\begin{MyVerbatim}
+i31 : R = ZZ/7[x,y];
+
+i32 : f = x*(y - 1)^2 - y*(x - 1)^3;
+
+i33 : fpt(f, AtOrigin => false)
 
       5
-o34 = -
+o33 = -
       6
 
-o34 : QQ
-
-i35 : fpt(f)
-
-o35 = infinity
-
-o35 : InfiniteNumber
-\end{MyVerbatim}
-}
-\bigskip
-% R = ZZ/7[x,y];
-% f = (y-1)^2-(x-1)^3;
-% fpt(f, AtOrigin => false)
-% fpt(f)
+o33 : QQ
+
+i34 : fpt(f)
+
+o34 = 1
+\end{MyVerbatim}
+}
+\medskip
 
@@
 
-If \texttt{isSimpleNormalCrossing(f)} outputs true, then the $F$-pure threshold is easily computed, since is just the minimum of the values $1/a_i$, for $1 \leq i \leq n$.
-Note that the function \texttt{factor} is called whenever \texttt{isSimpleNormalCrossing} is used, which can sometimes make the verification slow.
+% If \texttt{isSimpleNormalCrossing(f)} outputs true, then the $F$-pure threshold is easily computed, since is just the minimum of the values $1/a_i$, for $1 \leq i \leq n$.
+% Note that the function \texttt{factor} is called whenever \texttt{isSimpleNormalCrossing} is used, which can sometimes make the verification slow.
 The user can avoid this when using \texttt{fpt} by setting \texttt{UseSpecialAlgorithms} to \texttt{false}.

### 2019-06-18 Fsing/FrobeniusThresholdsPaper/FrobeniusThresholds.tex
Minor changes to sncFPT

@@
 
-If \texttt{UseSpecialAlgorithms} is set to \texttt{true} and $f$ does not fall into any of the aforementioned cases, then the function \texttt{fpt} next calls \texttt{isSimpleNormalCrossing(f)} (see Section~\ref{subsec.SNC}) to check whether the polynomial $f$ is a product of factors that are in simple normal crossing, in which case the $F$-pure threshold is simply the reciprocal of the largest multiplicity occurring in that factorization.
+If \texttt{UseSpecialAlgorithms} is set to \texttt{true} and $f$ does not fall into any of the aforementioned cases, then the function \texttt{fpt} next calls \texttt{isSimpleNormalCrossing(f)} (see Section~\ref{subsec.SNC}) to check whether the polynomial $f$ is (locally, at the origin) a product of factors that are in simple normal crossing, in which case the $F$-pure threshold is simply the reciprocal of the largest multiplicity occurring in that factorization.
 % If \texttt{isSimpleNormalCrossing(f)} outputs true, then the $F$-pure threshold is easily computed, since is just the minimum of the values $1/a_i$, for $1 \leq i \leq n$.

### 2019-06-19 Fsing/FrobeniusThresholdsPaper/FrobeniusThresholds.tex
Added todo note
Changes to bibliography

@@
 
-\usepackage{hyperref}
-\hypersetup{
-bookmarks,
-bookmarksdepth=3,
-bookmarksopen,
-bookmarksnumbered,
-pdfstartview=FitH,
-colorlinks,backref,hyperindex,
-linkcolor=Sepia,
-anchorcolor=BurntOrange,
-citecolor=MidnightBlue,
-citecolor=OliveGreen,
-filecolor=BlueViolet,
-menucolor=Yellow,
-urlcolor=OliveGreen
-}
-\usepackage{xspace}
+\usepackage{hyperref} \hypersetup{ bookmarks, bookmarksdepth=3,
+   bookmarksopen, bookmarksnumbered, pdfstartview=FitH,
+   colorlinks,backref,hyperindex, linkcolor=Sepia,
+   anchorcolor=BurntOrange, citecolor=MidnightBlue,
+   citecolor=OliveGreen, filecolor=BlueViolet, menucolor=Yellow,
+   urlcolor=OliveGreen } \usepackage{xspace}
 \interfootnotelinepenalty=100000
@@
 \pedro[inline]{I modified the code, to produce the output you suggested.}
+\daniel[inline]{OK.  I will just manually make this change in the verbatim environment below then, in case we decide to keep it here.}
 
@@
 
-ν has been computed: ν = ν(3,f) = 17 ...
+ν has been computed: ν = nu(3,f) = 17 ...
 

### 2019-06-19 Fsing/FrobeniusThresholdsPaper/FrobeniusThresholds.tex
Deleted notes; left the Verbose output, as discussed via email

@@
 
-\pedro[inline]{
-   Maybe the example below could be omitted, to shorten the paper.
-   I think that just telling the reader that the interval is printed when Verbose is activated is enough.
-}
-
-\daniel[inline]{I like the explanation provided by activating Verbose, and so I kind of think that it would be cool to show this off.
-However, I also understand if others want to omit it, and I wouldn't object if anyone has a strong preference.}
-
-\daniel[inline]{Should the line 
-\begin{center}
-ν has been computed: ν = ν(3,f) = 17 ...
-\end{center}
-instead be
-\begin{center}
-ν has been computed: ν = nu(3,f) = 17 ...
-\end{center}
-on the 5th line of the Verbose output?  I think this would be consistent with the paper, but whoever wrote this might have had a specific reason for doing it this way.
-}
-\pedro[inline]{I modified the code, to produce the output you suggested.}
-\daniel[inline]{OK.  I will just manually make this change in the verbatim environment below then, in case we decide to keep it here.}
-
 \medskip
@@
 
-%             R = ZZ/7[x,y,z];
-%             isSimpleNormalCrossing(x^2-y^2)
-%             isSimpleNormalCrossing(x^2-y*z)
-
-% If \texttt{isSimpleNormalCrossing(f)} outputs true, then the $F$-pure threshold is easily computed, since is just the minimum of the values $1/a_i$, for $1 \leq i \leq n$.
-% Note that the function \texttt{factor} is called whenever \texttt{isSimpleNormalCrossing} is used, which can sometimes make the verification slow.
-The user can avoid this when using \texttt{fpt} by setting \texttt{UseSpecialAlgorithms} to \texttt{false}.
-
 The function \texttt{isSimpleNormalCrossing} is exposed to the user, so can be used independent of any $F$-pure threshold calculation.
@@
 
-%             R = QQ[x,y,z];
-
-%             f = (y - (x-1)^2)*y^2; --SNC at the origin, but not globally
-
-%             isSimpleNormalCrossing(f)
-
-%             isSimpleNormalCrossing(f, AtOrigin=>false)
-
-%             g = x*y^2*(x+1)^3*(y-1)^4; --SNC everywhere
-
-%             isSimpleNormalCrossing(g)
-
-%             isSimpleNormalCrossing(g, AtOrigin=>false)
-
 \section{Possible Future Directions}

### 2019-06-19 Fsing/FrobeniusThresholdsPaper/FrobeniusThresholds.tex
Minor changes to paper

@@
 This latter result is interesting from a computational perspective, in that it provides lower bounds for log canonical thresholds.
-Though there is a general purpose implementation of an algorithm for computing log canonical thresholds in the \emph{Dmodules} package \cite{DmodulesSource}\footnote{The  \emph{MultiplierIdeals}  package also computes log canonical thresholds in many special cases, including monomial ideals, hyperplane arrangements, generic determinantal ideals, and certain binomial ideals \cite{MultiplierIdealsPackage, MultiplierIdealsArticle}.
+Though there is a general purpose implementation of an algorithm for computing log canonical thresholds in the \emph{Dmodules} package \cite{DmodulesSource}\footnote{The \emph{MultiplierIdeals} package \cite{MultiplierIdealsPackage, MultiplierIdealsArticle} also computes log canonical thresholds in many special cases, including monomial ideals, hyperplane arrangements, generic determinantal ideals, and certain binomial ideals.
 }, the function for computing $F$-pure thresholds contained in the \emph{FrobeniusThresholds} package is typically much faster, especially so in low characteristic.
@@
 It builds heavily upon the \emph{TestIdeals} package for \emph{Macaulay2} \cite{TestIdealsPackage, TestIdealsPaper}, which provides a broad range of functionality for effective computation in prime characteristic commutative algebra.
-In fact, both this package and \emph{TestIdeals} are derived from, and have greatly expanded, the older package \emph{PosChar}.
+%In fact, both this package and \emph{TestIdeals} are derived from, and have greatly expanded, the older package \emph{PosChar}.
 
@@
 
-Let us outline a way in which natural numerical invariants in prime characteristic commutative algebra are often constructed:  For every natural number $e$, associate to some fixed data---often, a collection of polynomials or ideals---an integer describing something of relevance that depends on $e$ (e.g., the dimension of some interesting vector space constructed in terms of your initial data).
+Let us outline a way in which natural numerical invariants in prime characteristic commutative algebra are often constructed:  For every natural number $e$, associate to some fixed data---often, a collection of polynomials or ideals---an integer describing something of relevance that depends on $e$ (e.g., the dimension of some interesting vector space constructed in terms of the initial data).
 Normalize this integer by dividing by some power of $p^e$, and then take the limit as the integer $e$ tends to infinity.
-The resulting limit, if it exists, should then encode some interesting information about your initial data.
+The resulting limit, if it exists, should then encode some interesting information about the initial data.
 
 Consider a nonzero polynomial $f$ and a natural number $e$.  If $f$ does not vanish at the origin, then set $\nu_f^{\idealm}(p^e) := \infty$.  Otherwise, $f \in \idealm$, and we instead define
-\[ \nu_f^{\idealm}(p^e) \coloneqq  \max \{ n>0 : f^n \notin \idealm^{[p^e]} \} \]
+\[ \nu_f^{\idealm}(p^e) \coloneqq  \max \{ n>0 : f^n \notin \idealm^{[p^e]} \}, \]
 where $\idealm^{[p^e]}$ denotes the $p^e$-th Frobenius power of $\idealm$, that is, the ideal generated by the $p^e$-th powers of the elements of $\idealm$.
-It is not hard to see that this number is the largest power of $f$ that is part of a free basis for the localization of the ambient polynomial ring at the origin, over its subring of $p^e$-th powers.
+%It is not hard to see that this number is the largest power of $f$ that is part of a free basis for the localization of the ambient polynomial ring at the origin, over its subring of $p^e$-th powers.
 %As noted earlier, this number also has a natural interpretation in terms of $F$-purity of pairs.
@@
 The $F$-pure threshold is closely related to many other fundamental concepts in prime characteristic commutative algebra.   For instance,
-\[ \ft^{\idealm}(f) = \inf \{ t>0 : \tau(f^t)  \subseteq \idealm \} = \sup \{ t>0 : \sigma( f^t) \neq 0 \} \]
+\[ \ft^{\idealm}(f) = \inf \{ t>0 : \tau(f^t)  \subseteq \idealm \} = \sup \{ t>0 : \sigma( f^t) \neq 0 \}, \]
 where $\tau(f^t)$ and $\sigma(f^t)$ are the \emph{test ideal} and \emph{$F$-signature}, respectively, associated to $f$ and the formal nonnegative real exponent $t$.
@@
 
-It turns out that the sequence $\{ \nu_f^{\idealm}(p^e) \}_{e=0}^{\infty}$ itself, and not just its limit, also encodes interesting information about $f$.
-For example, it is closely related to the so-called \emph{Bernstein--Sato polynomial} \cite{MustataTakagiWatanabeFThresholdsAndBernsteinSato}.
-Thus, it is natural to ask whether one can recover the sequence $\{ \nu_f^{\idealm}(p^e) \}_{e=0}^{\infty}$ from the limit $\ft^{\idealm}(f)$.
+It turns out that the sequence $\big(\nu_f^{\idealm}(p^e) \big)_{e=0}^{\infty}$ itself, and not just its limit, encodes interesting information about $f$.
+For example, it is closely related to the \emph{Bernstein--Sato polynomial} of $f$ \cite{MustataTakagiWatanabeFThresholdsAndBernsteinSato}.
+Thus, it is natural to ask whether one can recover the sequence $\big( \nu_f^{\idealm}(p^e) \big)_{e=0}^{\infty}$ from the limit $\ft^{\idealm}(f)$.
 Fortunately, the answer to this question is yes \cite{MustataTakagiWatanabeFThresholdsAndBernsteinSato, HernandezFPurityOfHypersurfaces}; for each $e$ we have
@@
 %
-\[ \nu_I^J(p^e) \coloneqq \max \{ n : I^n \notin J^{[p^e]} \}. \]
+\[ \nu_I^J(p^e) \coloneqq \max \{ n : I^n \not\subseteq J^{[p^e]} \}. \]
 Otherwise, we set $\nu_I^J(p^e) \coloneqq \infty$.
@@
 \[ \ft^J(I) \coloneqq  \lim_{e \to \infty} \frac{ \nu_I^J(p^e)}{p^e} \]
-the \emph{$F$-threshold of $I$ with respect to $J$}.  These numbers are also rational, when they are finite.
-The value $\ft^{\idealm}(I)$ is called the \emph{$F$-pure threshold of $I$}, and if $I = \langle f \rangle$ is principal,  $\ft^{J}(f) \coloneqq  \ft^J(I)$ is called the \emph{$F$-threshold of $f$ with respect to $J$}.
-Like $F$-pure thresholds, $F$-thresholds can also be defined in terms of test ideals.
-
-% \subsection{Organization}
-
-% The goal of this paper is paper is to describe and illustrate the main functionality implemented in the \emph{FrobeniusThresholds} package.  We describe the organization of this paper below.
-
-% \begin{itemize}
-% \item[$\circ$] \autoref{sec.Nu} describes the fundamental function \texttt{nu}.  As its name suggests, this function is concerned with computing the integers $\nu_I^J(p^e)$ mentioned above.
-% \item[$\circ$] \autoref{sec.IsFPT} explains the functionality for determining whether a given number is the $F$-pure threshold, or more generally, an \emph{$F$-jumping exponent}.
-% \item[$\circ$] \autoref{sec.FPT} describes the features of the central function of the package, \texttt{fpt}.
-% \item[$\circ$]  \autoref{sec.FutureDirections} outlines our plans for future improvements to this package.
-% \end{itemize}
-% %{\color{red} Move this later}
+the \emph{$F$-threshold of $I$ with respect to $J$}. 
+The value $\ft^{\idealm}(I)$ is called the \emph{$F$-pure threshold of $I$} at the origin, and if $I = \langle f \rangle$ is principal,  $\ft^{J}(f) \coloneqq  \ft^J(I)$ is called the \emph{$F$-threshold of $f$ with respect to $J$}.
+Like $F$-pure thresholds, $F$-thresholds are rational (when finite), and can be characterized in terms of test ideals.
 
@@
 We first consider the \texttt{nu} function, a fundamental component of the package \emph{FrobeniusThresholds}.
-In this section, we adopt the notation established in the introduction.
-Namely, we work in a polynomial ring over a finite field of characteristic $p>0$,  $\idealm$ denotes the ideal generated by the variables, and $e$ is a natural number.
-
-If $f$ is a nonzero polynomial contained in the radical of an ideal $J$, then the command \texttt{nu(e,f,J)} outputs the integer $\nu_f^J(p^e)$ defined in the introduction, and
-%, the maximal integer exponent such that $f^n$ is not contained in $J^{[p^e]}$.
-more generally, if a nonzero ideal $I$ is contained in the radical of $J$, then \texttt{nu(e,I,J)} outputs $\nu_I^J(p^e)$.
-%Consider the following example.  %, the maximal integer exponent $n$ such that $I^n$ is not contained in $J^{[p^e]}$.
-If the third argument is omitted from the function \texttt{nu}, it is assumed to be the maximal ideal $\idealm$.
+We adopt the setup established in the introduction: we work in a polynomial ring $R$ over a finite field of characteristic $p>0$,  $\idealm$ denotes the ideal generated by the variables, and $e$ is a natural number.
+If $I$ and $J$ are ideals of $R$, the command \texttt{nu(e,I,J)} outputs the extended integer $\nu_I^J(p^e)$ defined in the introduction; if $f$ is an element of $R$, \texttt{nu(e,f,J)} outputs $\nu_f^J(p^e) \coloneqq \nu_{\langle f \rangle}^J(p^e)$.
+When the third argument is omitted from the function \texttt{nu}, it is assumed to be the maximal ideal $\idealm$.
 
@@
 }
-\medskip
-
-% \medskip
-% {\small
-% \setstretch{.67}
-% \begin{MyVerbatim}
-% i9 : R = ZZ/17[x,y,z];
-
-% i10 : f = x^3 + y^4 + z^5;
-
-% i11 : m = ideal(x, y, z);
-
-% o11 : Ideal of R
-
-% i12 : nu(2, f) == nu(2, f, m)
-
-% o12 = true
-% \end{MyVerbatim}
-% }
-% \medskip
-
-%R = ZZ/17[x,y,z];
-%f = x^3 + y^4 + z^5;
-%M = ideal(x, y, z);
-%nu(2, f) == nu(2, f, M)
 
@@
 This is used to speed up computations for certain polynomials whose $F$-pure thresholds can be computed quickly via specialized algorithms or formulas, namely diagonal polynomials, binomials, forms in two variables, and products of factors in simple normal crossing (see Section~\ref{sec.FPT}).
-This feature can be disabled by setting the option \texttt{UseSpecialAlgorithms} (default value \texttt{true}) to \texttt{false}; in Section~\ref{ss: UseSpecialAlgorithms} we give discuss situations where the user might want to do that.
-%Consider the following example, where $f$ is a diagonal polynomial.
-\todo{Explain why the user might want to disable this.}
-\daniel{Why would one want to do this?}
-\pedro{In Section~\ref{ss: UseSpecialAlgorithms} we give a couple of examples, so I'm pointing the reader to that section.}
+This feature can be disabled by setting the option \texttt{UseSpecialAlgorithms} (default value \texttt{true}) to \texttt{false}; in Section~\ref{ss: UseSpecialAlgorithms} we discuss situations in which this may be desirable.
 
@@
 
-In general, the function \texttt{nu} works by searching through a list of integers $n$, and checking containments of the $n$-th power of $I$ in a specified Frobenius power of $J$.
-It is well known that if $q=p^e$ for some nonnegative integer $e$, then \[ \nu_I^J(qp) = \nu_I^J(q)\cdot p + L,\]  where the error term $L$ is nonnegative and can be explicitly bounded from above in terms of $p$ and the number of generators of $I$ and $J$.
+In general, the function \texttt{nu} works by searching through a list of integers $n$, and checking containments of the $n$-th power of $I$ in the specified Frobenius power of $J$.
+It is well known that, for any positive integer $e$,
+\[ \nu_I^J(p^e) = \nu_I^J(p^{e-1})\cdot p + L,\]
+where the error term $L$ is nonnegative and can be explicitly bounded from above in terms of $p$ and the number of generators of $I$ and $J$.
 For instance, the error term $L$ is at most $p-1$ when $I$ is principal and $J$ is arbitrary.
@@
 
-%R = ZZ/5[x,y,z];
-%--f = x^2*y^4 + y^2*z^7 + z^2*x^8;
-%-- time nu(5, f) -- uses binary search (default)
-%-- time nu(5, f, Search => Linear)
-% M = ideal(x, y, z);
-% time nu(2, M, M^2) -- uses binary search (default)
-% time nu(2, M, M^2, Search => Linear) -- but linear seach gets luckier
-
-If the option \texttt{ReturnList} is changed from its default value of \texttt{false} to \texttt{true},
-% rather than simply outputting $\nu_I^J(p^e)$,
-\texttt{nu} outputs a list of the values $\nu_I^J(p^s)$, for $s=0,\ldots,e$, at no additional computational cost.
+If the option \texttt{ReturnList} is changed from its default value of \texttt{false} to \texttt{true}, \texttt{nu} outputs a list of the values $\nu_I^J(p^s)$, for $s=0,\ldots,e$, at no additional computational cost.
 
@@
 
-As described in the introduction, the integer $\nu_I^J(p^e)$ is the maximal integer $n$ such that the $n$-th power of $I$ does not lie in the $p^e$-th Frobenius power of $J$.  However,
+As described in the introduction, the integer $\nu_I^J(p^e)$ is the maximal integer $n$ such that the $n$-th power of $I$ is not contained in the $p^e$-th Frobenius power of $J$.  However,
 \begin{equation*}
-  I^n \subseteq J^{[p^e]} \Longleftrightarrow (I^n)^{[1/p^e]} \subseteq J
+  I^n \subseteq J^{[p^e]} \Longleftrightarrow (I^n)^{[1/p^e]} \subseteq J,
 \end{equation*}
@@
 If \texttt{ContainmentTest} is set to \texttt{StandardPower}, then \texttt{nu(e,I,J)} is computed by testing the left-hand containment above, and when it is set to \texttt{FrobeniusRoot}, the right-hand containment is checked.
-For efficiency reasons, the default value for \texttt{ContainmentTest} is set to  \texttt{FrobeniusRoot} if the second argument passed to \texttt{nu} is a polynomial, and is set to \texttt{StandardPower} if it is an ideal.
+For efficiency reasons, the default value for \texttt{ContainmentTest} is set to  \texttt{FrobeniusRoot} if the second argument passed to \texttt{nu} is a polynomial, and is set to \texttt{StandardPower} if the second argument is an ideal.
 
@@
 
-% R = ZZ/11[x,y,z];
-% f = x^3 + y^3 + z^3 + x*y*z;
-% time nu(3, f) -- ContainmentTest is set to FrobeniusRoot, by default
-% time nu(3, f, ContainmentTest => StandardPower)
-
 The option \texttt{ContainmentTest} has a third possible value, \texttt{FrobeniusPower}, which allows \texttt{nu} to compute a different but analogous invariant.
-%may produce a different result than the other two values.
-The first, third, and fourth authors introduced the notion of a (generalized) Frobenius power $I^{[n]}$ of an ideal $I$, when $n$ is an arbitrary positive integer, not necessarily of the form $n = p^e$ \cite{hernandez+etal.frobenius_powers}.
+The first, third, and fourth authors introduced the notion of a (generalized) Frobenius power $I^{[n]}$ of an ideal $I$, when $n$ is an arbitrary nonnegative integer \cite{hernandez+etal.frobenius_powers}.
 When \texttt{ContainmentTest} is set to \texttt{FrobeniusPower}, rather than  computing $\nu_I^J(p^e)$, the function \texttt{nu} computes the maximal integer $n$ for which $I^{[n]}$ is not contained in $J^{[p^e]}$.
 This number is denoted $\mu_I^J(p^e)$ in \emph{loc.~cit.}, and equals $\nu_I^J(p^e)$ when $I$ is a principal ideal.
-However, these number need not agree in general, as we see below.
+However, these numbers need not agree in general, as we see below.
 
@@
 
-%In line with the philosophy described in the introduction, after appropriately normalizing and taking the limit as $e$ approaches infinity, the values $\mu_I^J(p^e)$ determine certain invariants of interest called \emph{critical exponents}.
-
 The last option we describe for \texttt{nu} is \texttt{AtOrigin}.
 Recall that $\nu_I^\idealm(p^e)$ can be interpreted as the maximum integer $n$ for which $(I^n)^{[1/p^e]}$ is not contained in $\idealm$. 
-When computing its value globally, it is the maximum integer $n$ for which $(I^n)^{[1/p^e]}$ is not the unit ideal.
-When the option \texttt{AtOrigin} is set to \texttt{false} (from its default value \texttt{true}), \texttt{nu} instead determines this maximal integer $n$, which can also be characterized as the minimal integer $\nu_I^\mathfrak{n}(p^e)$ as $\mathfrak{n}$ varies among all maximal ideals of the ring.
-
-%
-% \[
-% \min_{J \in \mathfrak{m}-\Spec R} \nu_I^J(p^e)
-% \]
-% This is done by instead of computing for which $n$ we have $I^{n} \subseteq J^{[p^e]}$ (or equivalently, $(I^n)^{[1/p^e]} \subseteq J$), it
-%by determining the values $n$ for which $(I^n)^{[1/p^e]}$ is a unit ideal.
+When the option \texttt{AtOrigin} is set to \texttt{false} (from its default value \texttt{true}), the function \texttt{nu} determines, instead, the maximum integer $n$ for which $(I^n)^{[1/p^e]}$ is the unit ideal, which can also be characterized as the minimal integer $\nu_I^\mathfrak{n}(p^e)$ as $\mathfrak{n}$ varies among all maximal ideals of the ring.
 
@@
 
-% R = ZZ/3[x,y];
-% m = ideal(x, y);
-% nu(3, m^5)
-% nu(3, m^5, ContainmentTest => FrobeniusPower)
-
 \section{{\tt isFPT}, {\tt compareFPT} and {\tt isFJumpingExponent}}
@@
 The \emph{FrobeniusThresholds} package contains methods to test candidate values for $F$-pure thresholds and $F$-jumping numbers, even in some singular rings.
-Consider a  $\mathbb{Q}$-Gorenstein ring $R$ of characteristic $p>0$, whose index not divisible by $p$.
+Consider a  $\mathbb{Q}$-Gorenstein ring $R$ of characteristic $p>0$, whose index is not divisible by $p$.
 Given a parameter $t\in \mathbb{Q}$ and an element $f$ of $R$, the command \texttt{isFPT(t, f)} checks whether $t$ is the $F$-pure threshold of $f$, while \texttt{compareFPT(t, f)} provides further information, returning {\tt-1}, \texttt{0}, or \texttt{1} when $t$ is less than, equal to, or greater than the $F$-pure threshold of $f$.

### 2019-06-20 Fsing/FrobeniusThresholdsPaper/FrobeniusThresholds.tex
Changes to paper

@@
 Consider a nonzero polynomial $f$ and a natural number $e$.  If $f$ does not vanish at the origin, then set $\nu_f^{\idealm}(p^e) := \infty$.  Otherwise, $f \in \idealm$, and we instead define
-\[ \nu_f^{\idealm}(p^e) \coloneqq  \max \{ n>0 : f^n \notin \idealm^{[p^e]} \}, \]
+\[ \nu_f^{\idealm}(p^e) \coloneqq  \max \{ n \in \mathbb{N} : f^n \notin \idealm^{[p^e]} \}, \]
 where $\idealm^{[p^e]}$ denotes the $p^e$-th Frobenius power of $\idealm$, that is, the ideal generated by the $p^e$-th powers of the elements of $\idealm$.
@@
 
-We conclude this subsection by briefly reviewing some natural generalizations.  Suppose that $I$ and $J$ are ideals.  If $I$ is contained in the radical of $J$, then we set
+We conclude this subsection by briefly reviewing some natural generalizations.
+Suppose that $I$ and $J$ are ideals.
+If $I$ is contained in the radical of $J$, then we set
 %
-\[ \nu_I^J(p^e) \coloneqq \max \{ n : I^n \not\subseteq J^{[p^e]} \}. \]
+\[ \nu_I^J(p^e) \coloneqq \max \{ n \in \mathbb{N}: I^n \not\subseteq J^{[p^e]} \}, \]
+or $\nu_I^J(p^e) \coloneqq 0$, when the set on the right-hand side is empty.
 Otherwise, we set $\nu_I^J(p^e) \coloneqq \infty$.
@@
 
-\medskip
+\smallskip
 {\small
@@
 
-i4 : nu(1, I, J)
+i4 : nu(2, I, J)
 
-o4 = 24
+o4 = 281
 
@@
 
-i6 : nu(1, f, J)
+i6 : nu(2, f, J)
 
-o6 = 10
+o6 = 120
 \end{MyVerbatim}
@@
 This is used to speed up computations for certain polynomials whose $F$-pure thresholds can be computed quickly via specialized algorithms or formulas, namely diagonal polynomials, binomials, forms in two variables, and products of factors in simple normal crossing (see Section~\ref{sec.FPT}).
-This feature can be disabled by setting the option \texttt{UseSpecialAlgorithms} (default value \texttt{true}) to \texttt{false}; in Section~\ref{ss: UseSpecialAlgorithms} we discuss situations in which this may be desirable.
+This feature can be disabled by setting the option \texttt{UseSpecialAlgorithms} (default value \texttt{true}) to \texttt{false}.\footnote{In Section~\ref{ss: UseSpecialAlgorithms} we discuss a couple of situations in which this may be desirable.}
 
-\medskip
+\smallskip
 {\small
@@
 \begin{MyVerbatim}
-i13 : R = ZZ/17[x,y,z];
+i7 : R = ZZ/17[x,y,z];
 
-i14 : f = x^3 + y^4 + z^5; -- a diagonal polynomial
+i8 : f = x^3 + y^4 + z^5; -- a diagonal polynomial
 
-i15 : time nu(5, f)
-     -- used 0.00573794 seconds
+i9 : time nu(10, f)
+     -- used 0.0161622 seconds
 
-o15 = 1085772
+o9 = 1541642394460
 
-i16 : time nu(5, f, UseSpecialAlgorithms => false)
-     -- used 0.492965 seconds
+i10 : time nu(10, f, UseSpecialAlgorithms => false)
+     -- used 2.06877 seconds
 
-o16 = 1085772
+o10 = 1541642394460
 \end{MyVerbatim}
 }
-\medskip
+\smallskip
 
@@
 \begin{MyVerbatim}
-i17 : R = ZZ/5[x,y,z];
+i11 : R = ZZ/5[x,y,z];
 
-i21 : m = ideal(x, y, z);
+i12 : m = ideal(x, y, z);
 
-o21 : Ideal of R
+o12 : Ideal of R
 
-i22 : time nu(2, m, m^2) -- uses binary search (default)
-     -- used 1.71206 seconds
+i13 : time nu(2, m, m^2) -- uses binary search (default)
+     -- used 1.82479 seconds
 
-o22 = 97
+o13 = 97
 
-i23 : time nu(2, m, m^2, Search => Linear) -- but linear seach gets luckier
-     -- used 0.536135 seconds
+i14 : time nu(2, m, m^2, Search => Linear) -- but linear seach gets luckier
+     -- used 0.597035 seconds
 
-o23 = 97
+o14 = 97
 \end{MyVerbatim}
 }
-\medskip
+%\medskip
+\smallskip
 
@@
 
-\medskip
+% \medskip
+\smallskip
 {\small
@@
 \begin{MyVerbatim}
-i24 : nu(5, f, ReturnList => true)
+i15 : nu(5, x^2*y^4 + y^2*z^7 + z^2*x^8, ReturnList => true)
 
-o24 = {0, 1, 8, 44, 224, 1124}
+o15 = {0, 1, 8, 44, 224, 1124}
 
-o24 : List
+o15 : List
 \end{MyVerbatim}
 }
-\medskip
+%\medskip
+\smallskip
 
@@
 \begin{MyVerbatim}
-i26 : R = ZZ/11[x,y,z];
+i16 : R = ZZ/11[x,y,z];
 
-i27 : f = x^3 + y^3 + z^3 + x*y*z;
+i17 : f = x^3 + y^3 + z^3 + x*y*z;
 
-i28 : time nu(3, f) -- ContainmentTest is set to FrobeniusRoot, by default
-     -- used 0.127375 seconds
+i18 : time nu(3, f) -- ContainmentTest is set to FrobeniusRoot, by default
+     -- used 0.153691 seconds
 
-o28 = 1209
+o18 = 1209
 
-i29 : time nu(3, f, ContainmentTest => StandardPower)
-     -- used 9.57149 seconds
+i19 : time nu(3, f, ContainmentTest => StandardPower)
+     -- used 10.1343 seconds
 
-o29 = 1209
+o19 = 1209
 \end{MyVerbatim}
 }
-\medskip
+%\medskip
 
@@
 \begin{MyVerbatim}
-i30 : R = ZZ/3[x,y];
+i20 : R = ZZ/3[x,y];
 
-i31 : m = ideal(x, y);
+i21 : m = ideal(x, y);
 
-o31 : Ideal of R
+o21 : Ideal of R
 
-i32 : nu(3, m^5)
+i22 : nu(4, m^5)
 
-o32 = 10
+o22 = 32
 
-i33 : nu(3, m^5, ContainmentTest => FrobeniusPower)
+i23 : nu(4, m^5, ContainmentTest => FrobeniusPower)
 
-o33 = 8
+o23 = 26
 \end{MyVerbatim}
 }
-\medskip
+\smallskip
 
@@
 \begin{MyVerbatim}
-i34 : R = ZZ/7[x,y];
+i24 : R = ZZ/7[x,y];
 
-i35 : f = (x - 1)^3 - (y - 2)^2;
+i25 : f = (x - 1)^3 - (y - 2)^2;
 
-i36 : nu(1, f)
+i26 : nu(3, f)
 
-o36 = infinity
+o26 = infinity
 
-o36 : InfiniteNumber
+o26 : InfiniteNumber
 
-i37 : nu(1, f, AtOrigin => false)
+i27 : nu(3, f, AtOrigin => false)
 
-o37 = 5
+o27 = 285
 \end{MyVerbatim}
@@
 Consider a  $\mathbb{Q}$-Gorenstein ring $R$ of characteristic $p>0$, whose index is not divisible by $p$.
-Given a parameter $t\in \mathbb{Q}$ and an element $f$ of $R$, the command \texttt{isFPT(t, f)} checks whether $t$ is the $F$-pure threshold of $f$, while \texttt{compareFPT(t, f)} provides further information, returning {\tt-1}, \texttt{0}, or \texttt{1} when $t$ is less than, equal to, or greater than the $F$-pure threshold of $f$.
+Given a parameter $t\in \mathbb{Q}$ and an element $f$ of $R$, the command \texttt{isFPT(t, f)} checks whether $t$ is the $F$-pure threshold of $f$, while \texttt{compareFPT(t, f)} provides further information, returning {\tt-1}, \texttt{0}, or \texttt{1} when $t$ is, respectively, less than, equal to, or greater than the $F$-pure threshold of $f$.
 Setting the option \texttt{AtOrigin} to \texttt{true} tells the function to consider the $F$-pure threshold at the origin.
@@
 \begin{MyVerbatim}
-i1 : R = ZZ/11[x, y, z]/(x^2 - y*(z - 1));
+i1 : R = ZZ/11[x,y,z]/(x^2 - y*(z - 1));
 
@@
 }
-\medskip
-
-% The general method applied calls upon functionality from the \emph{TestIdeals} package.
-% The functions \texttt{testIdeal} and \texttt{FPureModule} therein are used to compute the test ideals of $f$ with respect to the parameter $t$, and that with respect to $t - \varepsilon$, for $0<\varepsilon\ll 1$.
-For instance, as noted in the introduction, when $R$ is a polynomial ring, $t$ is the $F$-pure threshold of $f$ if and only if $\tau(R, f^t)$ is contained in the homogeneous maximal ideal, but
-% $\tau(R, f^{t-\varepsilon})$ is not.
-% Note that for $R$ strongly $F$-regular and Gorenstein, \texttt{FPureModule(t, f)} precisely computes $\tau(R, f^{t-\varepsilon})$.
+\smallskip
 
 The general method applied calls upon functionality from the \emph{TestIdeals} package.
-The functions \texttt{testIdeal} and \texttt{FPureModule} therein are used to compute the test ideals of $f$ with respect to the parameter $t$, and that with respect to $t - \varepsilon$, for $0<\varepsilon\ll 1$.
+The functions \texttt{testIdeal} and \texttt{FPureModule} therein are used to compute the test ideals $\tau(f^t)$ and $\tau(f^{t-\varepsilon})$, for $0<\varepsilon\ll 1$.
 By comparing these test ideals, we can decide whether $t$ is the $F$-pure threshold of $f$.
-For instance, as noted in the introduction, when $R$ is a polynomial ring, $t$ is the $F$-pure threshold of $f$ at the origin if and only if $\tau(R, f^t)$ is contained in the homogeneous maximal ideal, but $\tau(R, f^{t-\varepsilon})$ is not.
-%Note that for $R$ strongly $F$-regular and Gorenstein, \texttt{FPureModule(t, f)} precisely computes $\tau(R, f^{t-\varepsilon})$.
+For instance, when $R$ is a polynomial ring, $t$ is the $F$-pure threshold of $f$ at the origin if and only if $\tau(f^t)$ is contained in the homogeneous maximal ideal, but $\tau(f^{t-\varepsilon})$ is not.
 
 Since not only the $F$-pure thresholds, but also the higher $F$-jumping numbers, are determined by containment conditions on test ideals, the functionality is extended to determine whether a given number is an $F$-jumping number.
-Analogous syntax is used, as shown in the following example.
 
-\medskip
+\smallskip
 {\small
@@
 \begin{MyVerbatim}
-i5 : R = ZZ/13[x, y];
+i5 : R = ZZ/13[x,y];
 
@@
 o7 = true
+
+i8 : isFPT(3/4, f)
+
+o8 = false
 \end{MyVerbatim}
@@
 The \texttt{fpt} function has an option called \texttt{UseSpecialAlgorithms}, which, when set to \texttt{true} (its default value), tells \texttt{fpt} to first check whether $f$ is a diagonal polynomial, a binomial, a form in two variables, or a product of factors in simple normal crossing, in that order.
-
-When $f$ is a diagonal polynomial, a binomial, or a form in two variables, algorithms of Hern\'andez \cite{HernandezFInvariantsOfDiagonalHyp, HernandezFPureThresholdOfBinomial}, or Hern\'andez and Teixeira \cite{HernandezTeixeiraFThresholdFunctions},  are executed to compute the $F$-pure threshold.
+When $f$ is a diagonal polynomial, a binomial, or a form in two variables, algorithms of Hern\'andez \cite{HernandezFInvariantsOfDiagonalHyp, HernandezFPureThresholdOfBinomial} or Hern\'andez and Teixeira \cite{HernandezTeixeiraFThresholdFunctions} are executed to compute the $F$-pure threshold.
 %Algorithms for computing $F$-pure thresholds of binomials also appear in \cite{ShibutaTakagiLCThresholds}, though they are only valid in certain special characteristics.
 
-\medskip
+\smallskip
 {\small
@@
 }
-\medskip
+\smallskip
 
-The algorithm for computing the $F$-pure threshold of a binary form $f$ requires factoring $f$ into linear forms, and that may be difficult or impossible when that factorization occurs in a Galois field of excessively large order.
+\noindent The algorithm for computing the $F$-pure threshold of a binary form $f$ requires factoring $f$ into linear forms, and that may be difficult or impossible when that factorization occurs in a Galois field of excessively large order.
 This is a situation when the user will want to set the option \texttt{UseSpecialAlgorithms} to \texttt{false}.
@@
 }
-\medskip
+\smallskip
 
@@
 % If \texttt{isSimpleNormalCrossing(f)} outputs true, then the $F$-pure threshold is easily computed, since is just the minimum of the values $1/a_i$, for $1 \leq i \leq n$.
-Note that the function \texttt{factor} is called whenever \texttt{isSimpleNormalCrossing} is used, which can sometimes make the verification slow.
+Note that the function \texttt{factor} is called whenever \texttt{isSimpleNormalCrossing} is used, and that can sometimes make the verification slow.
 The user can avoid this by setting \texttt{UseSpecialAlgorithms} to \texttt{false}.
@@
 
-In the remainder of this section, we explain how the function  \texttt{fpt} proceeds when no special algorithm is available, or when \texttt{UseSpecialAlgorithms} is set to \texttt{false}, and describe the roles of the options \texttt{DepthOfSearch} and \texttt{Attempts}, whose values are both nonnegative integers.
-
-In this case, the \texttt{fpt} function either computes, and outputs, the exact value of the $F$-pure threshold of $f$, or otherwise recursively computes a finite sequence of lower and upper bounds for this value, and outputs the last of these, which will be the tightest among all computed.
-The value of the option \texttt{DepthOfSearch} determines the precision of the initial set of bounds, and the option \texttt{Attempts}, in conjunction with some various subroutines, determines whether, and how, to produce new, tighter bounds from the previous ones.
+We now explain how the function  \texttt{fpt} proceeds when no special algorithm is available, or when \texttt{UseSpecialAlgorithms} is set to \texttt{false}.
+In this case, \texttt{fpt} computes a sequence of lower and upper bounds for the $F$-pure threshold of $f$, and either finds its exact value in this process, or outputs the last of these sets of bounds, which will be the tightest among all computed.
+The value of the option \texttt{DepthOfSearch} determines the precision of the initial set of bounds, and the option \texttt{Attempts} determines, roughly, how many new, tighter sets of bounds are to be computed.
 
@@
 The \texttt{fpt} function first computes $\nu=\nu_f(p^e)$, which agrees with the output of \texttt{nu(e,f)}.
-It is well known that the $F$-pure threshold of $f$ is greater than $\nu/p^e$ and at most $(\nu+1)/p^e$, and applying  \cite[Proposition 4.2]{HernandezFPurityOfHypersurfaces} to this lower bound tells us that the $F$-pure threshold of $f$ must be at least $\nu/(p^e-1)$.
+It is well known that the $F$-pure threshold of $f$ is greater than $\nu/p^e$ and at most $(\nu+1)/p^e$, and applying  \cite[Proposition 4.2]{HernandezFPurityOfHypersurfaces} to the lower bound tells us that the $F$-pure threshold of $f$ must be at least $\nu/(p^e-1)$.
 In summary, we know that the $F$-pure threshold of $f$ must lie in the closed interval
@@
 
-i12 : fpt(f, Attempts => 1, DepthOfSearch => 3) -- the right-hand
-      endpoint (nu+1)/p^e is the F-pure threshold
+i12 : fpt(f, Attempts => 1, DepthOfSearch => 3) -- the right-hand endpoint
+      (ν+1)/p^e is the F-pure threshold
 
@@
 i15 : fpt(f, Attempts => 2, DepthOfSearch => 3) -- the left-hand endpoint
-      nu/(p^e-1) is the F-pure threshold
+      ν/(p^e-1) is the F-pure threshold
 
@@
 \begin{MyVerbatim}
-i12 : f = x^3*y^11*(x + y)^8*(x^2 + y^3)^8;
+i16 : f = x^3*y^11*(x + y)^8*(x^2 + y^3)^8;
 
-i13 : fpt(f, DepthOfSearch => 3, Attempts => 4)
+i17 : fpt(f, DepthOfSearch => 3, Attempts => 4)
 
         1   4
-o13 = {--, --}
+o17 = {--, --}
        20  75
 
-o13 : List
+o17 : List
 
-i14 : fpt(f, DepthOfSearch => 3, Attempts => 6)
+i18 : fpt(f, DepthOfSearch => 3, Attempts => 6)
 
         13   4
-o14 = {---, --}
+o18 = {---, --}
        250  75
 
-o14 : List
+o18 : List
 
-i15 : fpt(f, DepthOfSearch => 3, Attempts => 8)
+i19 : fpt(f, DepthOfSearch => 3, Attempts => 8)
 
        1
-o15 = --
+o19 = --
       19
 
-o15 : QQ
+o19 : QQ
 \end{MyVerbatim}
 }
-\medskip
+\smallskip
 
@@
 
-        3   1
-o21 = {--, --}
-       40  13
+        19   1
+o21 = {---, --}
+       250  13
 
@@
 
-        24   1
+        45   1
 o22 = {---, --}
-       313  13
+       589  13
 
@@
 }
-\medskip
-
-% f = x^7*y^5*(x + y)^5*(x^2 + y^3)^4;
-% fpt(f, DepthOfSearch => 3, Attempts => 5)
-% fpt(f, DepthOfSearch => 3, Attempts => 5, Bounds => oo)
+\smallskip
 
@@
 If successful, the new lower bound may coincide with the upper bound, in which case we can conclude that it is the desired $F$-pure threshold.
-If this is not the case, an $F$-regularity check is done at the new lower bound, to verify if it is the $F$-pure threshold.
+If this is not the case, a check is performed to verify if the new lower bound is the $F$-pure threshold.
 
-\medskip
+\smallskip
 {\small
@@
 \begin{MyVerbatim}
-i2 : f = 2*x^10*y^8+x^4*y^7-2*x^3*y^8;
+i23 : f = 2*x^10*y^8 + x^4*y^7 - 2*x^3*y^8;
 
-i3 : numeric fpt(f, DepthOfSearch => 3)
+i24 : numeric fpt(f, DepthOfSearch => 3)
 
-o3 = {.14, .144}
+o24 = {.14, .144}
 
-o3 : List
+o24 : List
 
-i4 : numeric fpt(f, DepthOfSearch => 3, FinalAttempt => true)
+i25 : numeric fpt(f, DepthOfSearch => 3, FinalAttempt => true)
       -- FinalAttempt improves the estimate slightly
 
-o4 = {.142067, .144}
+o25 = {.142067, .144}
 
-o4 : List
+o25 : List
 \end{MyVerbatim}
 }
-\medskip
+\smallskip
 
 The computations performed when \texttt{FinalAttempt} is set to \texttt{true} are often slow, and often fail to improve the estimate, and for this reason, this option should be used sparingly.
-It is often more effective to increase the values of \texttt{Attempts} or \texttt{DepthOfSearch}, instead.
+It is typically more effective to increase the values of \texttt{Attempts} or \texttt{DepthOfSearch}, instead.
 
-\medskip
+\smallskip
 {\small
@@
 \begin{MyVerbatim}
-i35 : time numeric fpt(f, DepthOfSearch => 3, FinalAttempt => true)
-     -- used 0.684759 seconds
+i26 : time numeric fpt(f, DepthOfSearch => 3, FinalAttempt => true)
+     -- used 0.72874 seconds
 
-o35 = {.142067, .144}
+o26 = {.142067, .144}
 
-o35 : List
+o26 : List
 
-i36 : time fpt(f, DepthOfSearch => 3, Attempts => 7) 
-     -- used 0.405148 seconds
+i27 : time fpt(f, DepthOfSearch => 3, Attempts => 7) 
+     -- used 0.452872 seconds
 
       1
-o36 = -
+o27 = -
       7
 
-o36 : QQ
+o27 : QQ
 
-i37 : time fpt(f, DepthOfSearch => 4) 
-     -- used 0.365025 seconds
+i28 : time fpt(f, DepthOfSearch => 4) 
+     -- used 0.338834 seconds
 
       1
-o37 = -
+o28 = -
       7
 
-o37 : QQ
+o28 : QQ
 \end{MyVerbatim}
 }
-\medskip
+\smallskip
 
@@
 \begin{MyVerbatim}
-i39 : fpt(f, DepthOfSearch => 3, FinalAttempt => true, Verbose => true)
+i29 : fpt(f, DepthOfSearch => 3, FinalAttempt => true, Verbose => true)
 
@@
         8009   18
-o39 = {-----, ---}
+o29 = {-----, ---}
        56375  125
 
-o39 : List
+o29 : List
 \end{MyVerbatim}
 }
-\medskip
+\smallskip
 
@@
 \begin{MyVerbatim}
-i31 : R = ZZ/7[x,y];
+i30 : R = ZZ/7[x,y];
 
-i32 : f = x*(y - 1)^2 - y*(x - 1)^3;
+i31 : f = x*(y - 1)^2 - y*(x - 1)^3;
+
+i32 : fpt(f)
+
+o32 = 1
 
@@
 o33 : QQ
-
-i34 : fpt(f)
-
-o34 = 1
 \end{MyVerbatim}
 }
-\medskip
+\smallskip
 
-\noindent In this case, most options enabled by \texttt{UseSpecialAlgorithms => true}
-are ignored except for the check for simple normal crossings.  \texttt{FinalCheck => true}
+\noindent In this case, most features enabled by \texttt{UseSpecialAlgorithms => true}
+are ignored, except for the check for simple normal crossings;  \texttt{FinalCheck => true}
 is also ignored.
@@
 \subsection{The function \texttt{isSimpleNormalCrossings}} \label{subsec.SNC}
-As mentioned earlier, the function \texttt{isSimpleNormalCrossings} verifies whether $f$ is a product of factors in simple normal crossing.
+As mentioned earlier, the function \texttt{isSimpleNormalCrossings} verifies whether a ring element $f$ is a product of factors in simple normal crossing.
 Suppose that $f$ has factorization $f_1^{a_i} f_2^{a_2} \cdots f_n^{a_n}$.  Recall that its factors $f_i$ are said to be in
 \emph{simple normal crossing} at a point if, locally, they form part of a regular system of parameters.
-The function \texttt{isSimpleNormalCrossings} determines whether $f$ has simple normal crossings by computing the Jacobian matrix of each subset of $\{ f_i \}_{i=1}^n$ (evaluated at the origin), and checking that these matrices have the expected rank, and that these subsets generate ideals of the appropriate height.
+The function \texttt{isSimpleNormalCrossings} determines whether $f$ has simple normal crossings at the origin by computing the Jacobian matrix of each subset of $\{ f_1, \ldots, f_n \}$ (evaluated at the origin), and checking that these matrices have the expected rank, and that these subsets generate ideals of the appropriate height.
 
-\medskip
+\smallskip
 {\small
@@
 \begin{MyVerbatim}
-i36 : R = ZZ/7[x, y, z];
+i34 : R = ZZ/7[x,y,z];
 
-i37 : isSimpleNormalCrossing(x^2 - y^2)
+i35 : isSimpleNormalCrossing(x^2 - y^2)
 
-o37 = true
+o35 = true
 
-i38 : isSimpleNormalCrossing(x^2 - y*z)
+i36 : isSimpleNormalCrossing(x^2 - y*z)
 
-o38 = false
+o36 = false
 \end{MyVerbatim}
 }
-\medskip
+\smallskip
 
 The function \texttt{isSimpleNormalCrossing} is exposed to the user, so can be used independent of any $F$-pure threshold calculation.
-If the user sets its option \texttt{AtOrigin} to \texttt{true} (its default value is \texttt{false}), then the function checks whether the $f_i$ are in simple normal crossing \emph{everywhere}, which can be much slower since Jacobian ideals are computed.
-Consider the following example illustrating this functionality.
+If the user sets its option \texttt{AtOrigin} to \texttt{false} (its default value is \texttt{true}), then the function checks whether the $f_i$ are in simple normal crossing \emph{everywhere}, which can be much slower, since Jacobian ideals are computed.
 
-\medskip
+\smallskip
 {\small
@@
 \begin{MyVerbatim}
-i39 : R = QQ[x, y, z];
+i37 : R = QQ[x,y,z];
 
-i40 : f = (y - (x - 1)^2)*y^2;
+i38 : f = (y - (x - 1)^2)*y^2; --SNC at the origin, but not globally
 
-i41 : isSimpleNormalCrossing(f)
+i39 : isSimpleNormalCrossing(f)
 
-o41 = true
+o39 = true
 
-i42 : isSimpleNormalCrossing(f, AtOrigin => false)
+i40 : isSimpleNormalCrossing(f, AtOrigin => false)
 
-o42 = false
+o40 = false
 \end{MyVerbatim}
 }
-\medskip
+\smallskip
 
@@
 
-One natural direction of development would be to better incorporate the test ideals $\tau(I^t)$ when computing $F$-thresholds in the case where the ideal $I$ is nonprincipal.
+One natural direction of development would be to  incorporate the test ideals $\tau(I^t)$ when computing $F$-thresholds in the case where the ideal $I$ is nonprincipal.
 The theoretical foundation for computing such test ideals has already largely been worked out in \cite{SchwedeTuckerTestIdealsOfNonPrincipal}, but such an update to the \emph{FrobeniusThresholds} package would require the  \emph{TestIdeals} package to be updated first.
 
-At the moment, the specialized algorithms called by the \texttt{fpt} function for computing the $F$-pure threshold of a homogeneous polynomial in two variables limits us to working with the standard grading on the ambient polynomial ring.
+At the moment, the specialized algorithm called by the \texttt{fpt} function for computing the $F$-pure threshold of a homogeneous polynomial in two variables limits us to working with the standard grading on the ambient polynomial ring.
 Clearly, it is desirable to be able to work with nonstandard gradings as well, and results of \cite{HernandezTeixeiraFThresholdFunctions} suggest an algorithm for doing so.
@@
 
-Finally, it would be desirable to develop and implement additional algorithms for computing $F$-pure threshold and $F$-jumping numbers for additional classes of polynomials.
+Finally, it would be desirable to develop and implement additional algorithms for computing $F$-pure thresholds and $F$-jumping numbers for additional classes of polynomials.
 The first, third, and fourth authors, along with Josep \'Alvarez Montaner, Jack Jeffries, and Luis N\'u\~nez-Betancourt,  are currently working on developing such algorithms.

### 2019-06-20 Fsing/FrobeniusThresholdsPaper/FrobeniusThresholds.tex
Minor changes to paper and doc

@@
 \DeclareMathOperator{\fpt}{fpt}
+
+\renewcommand{\geq}{\geqslant}
+\renewcommand{\leq}{\leqslant}
+\renewcommand{\ge}{\geqslant}
+\renewcommand{\le}{\leqslant}
 
@@
 
-i14 : time nu(2, m, m^2, Search => Linear) -- but linear seach gets luckier
+i14 : time nu(2, m, m^2, Search => Linear) -- but linear search gets luckier
      -- used 0.597035 seconds
@@
 If \texttt{UseSpecialAlgorithms} is set to \texttt{true} and $f$ does not fall into any of the aforementioned cases, then the function \texttt{fpt} next calls \texttt{isSimpleNormalCrossing(f)} (see Section~\ref{subsec.SNC}) to check whether the polynomial $f$ is (locally, at the origin) a product of factors that are in simple normal crossing, in which case the $F$-pure threshold is simply the reciprocal of the largest multiplicity occurring in that factorization.
-% If \texttt{isSimpleNormalCrossing(f)} outputs true, then the $F$-pure threshold is easily computed, since is just the minimum of the values $1/a_i$, for $1 \leq i \leq n$.
 Note that the function \texttt{factor} is called whenever \texttt{isSimpleNormalCrossing} is used, and that can sometimes make the verification slow.
@@
 The \texttt{fpt} function first computes $\nu=\nu_f(p^e)$, which agrees with the output of \texttt{nu(e,f)}.
-It is well known that the $F$-pure threshold of $f$ is greater than $\nu/p^e$ and at most $(\nu+1)/p^e$, and applying  \cite[Proposition 4.2]{HernandezFPurityOfHypersurfaces} to the lower bound tells us that the $F$-pure threshold of $f$ must be at least $\nu/(p^e-1)$.
+It is well known that the $F$-pure threshold of $f$ is greater than $\nu/p^e$ and at most $(\nu+1)/p^e$, and applying  \cite[Proposition~4.2]{HernandezFPurityOfHypersurfaces} to the lower bound tells us that the $F$-pure threshold of $f$ must be at least $\nu/(p^e-1)$.
 In summary, we know that the $F$-pure threshold of $f$ must lie in the closed interval
@@
 \noindent In this case, most features enabled by \texttt{UseSpecialAlgorithms => true}
-are ignored, except for the check for simple normal crossings;  \texttt{FinalCheck => true}
+are ignored, except for the check for simple normal crossings;  \texttt{FinalAttempt => true}
 is also ignored.

### 2019-06-21 Fsing/FrobeniusThresholdsPaper/FrobeniusThresholds.tex
Minor changes to documentation

@@
 \subsection{The function \texttt{isSimpleNormalCrossings}} \label{subsec.SNC}
-As mentioned earlier, the function \texttt{isSimpleNormalCrossings} verifies whether a ring element $f$ is a product of factors in simple normal crossing.
+As mentioned earlier, the function \texttt{isSimpleNormalCrossings} verifies whether a polynomial $f$ is a product of factors in simple normal crossing.
 Suppose that $f$ has factorization $f_1^{a_i} f_2^{a_2} \cdots f_n^{a_n}$.  Recall that its factors $f_i$ are said to be in

### 2019-11-22 Fsing/FrobeniusThresholdsPaper/FrobeniusThresholds.tex
Updated links to our packages to be permalinks

@@
 
-This paper describes the \emph{Macaulay2} package \emph{FrobeniusThresholds} \cite{M2, FThresholdsPackage}, which provides tools for computing or estimating certain fundamental invariants in positive characteristic commutative algebra, namely \emph{$F$-pure thresholds}, \emph{$F$-thresholds}, and \emph{$F$-jumping exponents}.
+This paper describes the \emph{Macaulay2} package \emph{FrobeniusThresholds}\footnote{This package was previously named \emph{FThresholds}} \cite{M2, FThresholdsPackage}, which provides tools for computing or estimating certain fundamental invariants in positive characteristic commutative algebra, namely \emph{$F$-pure thresholds}, \emph{$F$-thresholds}, and \emph{$F$-jumping exponents}.
 Recall that a ring of prime characteristic $p>0$ is \emph{$F$-pure} if the Frobenius map|that is, the ring endomorphism sending an element to its $p$-th power|is a pure morphism;  under natural geometric hypotheses, this is equivalent to the condition that the Frobenius morphism splits as a map of rings.
@@
 For example, it is closely related to the \emph{Bernstein--Sato polynomial} of $f$ \cite{MustataTakagiWatanabeFThresholdsAndBernsteinSato}.
-Thus, it is natural to ask whether one can recover the sequence $\big( \nu_f^{\idealm}(p^e) \big)_{e=0}^{\infty}$ from the limit $\ft^{\idealm}(f)$.
-Fortunately, the answer to this question is yes \cite{MustataTakagiWatanabeFThresholdsAndBernsteinSato, HernandezFPurityOfHypersurfaces}; for each $e$ we have
+Remarkably, 
+one can recover the sequence $\big( \nu_f^{\idealm}(p^e) \big)_{e=0}^{\infty}$ from the limit $\ft^{\idealm}(f)$ \cite{MustataTakagiWatanabeFThresholdsAndBernsteinSato, HernandezFPurityOfHypersurfaces}: For each $e$, we have
 \begin{equation*}
@@
 \subsection*{Acknowledgements.}  The authors enthusiastically thank everyone who helped complete the \emph{FrobeniusThresholds} package: the package coauthors Juliette Bruce and Daniel Smolkin, and contributors  Erin Bela, Zhibek Kadyrsizova, Moty Katzman, Sara Malec, and Marcus Robinson.
+We also thank the authors of the \emph{TestIdeals} package, which, beyond the authors of the present paper and those listed above, are Alberto Boix, Drew Ellingson, Matthew Mastroeni, and Maral Mostafazadehfard.
 
@@
 
-We first consider the \texttt{nu} function, a fundamental component of the package \emph{FrobeniusThresholds}.
+We first describe the \texttt{nu} function, a fundamental component of the package \emph{FrobeniusThresholds}.
 We adopt the setup established in the introduction: we work in a polynomial ring $R$ over a finite field of characteristic $p>0$,  $\idealm$ denotes the ideal generated by the variables, and $e$ is a natural number.

### 2019-11-22 Fsing/FrobeniusThresholdsPaper/FrobeniusThresholds.tex
Updated references

@@
 At the moment, the specialized algorithm called by the \texttt{fpt} function for computing the $F$-pure threshold of a homogeneous polynomial in two variables limits us to working with the standard grading on the ambient polynomial ring.
-Clearly, it is desirable to be able to work with nonstandard gradings as well, and results of \cite{HernandezTeixeiraFThresholdFunctions} suggest an algorithm for doing so.
+It is desirable to be able to work with nonstandard gradings as well, and results of \cite{HernandezTeixeiraFThresholdFunctions} suggest an algorithm for doing so.
 Thus, the package could be improved by finalizing and implementing such an algorithm.

### 2019-11-25 Fsing/FrobeniusThresholdsPaper/FrobeniusThresholds.tex
Updated paper as per referee's comments

@@
 
+For example, \emph{Hilbert-Kunz multiplicity} is realized in this way. 
+Given an ideal $I$ of a ring $R$ of characteristic $p>0$, $I^{[p^e]}$ denotes the $p^e$-th Frobenius power of $I$, that is, the ideal generated by the $p^e$-th powers of the elements of $I$.
+If $R$ has dimension $d$ and $\lambda\left(R/I^{[p^e]}\right)$ denotes the length of $R/I^{[p^e]}$, the limit of $\frac{\lambda\left(R/I^{[p^e]}\right)}{p^{ed}}$ is the Hilbert-Kunz multiplicity of $R$ with respect to $I$.
+
 Consider a nonzero polynomial $f$ and a natural number $e$.  If $f$ does not vanish at the origin, then set $\nu_f^{\idealm}(p^e) := \infty$.  Otherwise, $f \in \idealm$, and we instead define
-\[ \nu_f^{\idealm}(p^e) \coloneqq  \max \{ n \in \mathbb{N} : f^n \notin \idealm^{[p^e]} \}, \]
-where $\idealm^{[p^e]}$ denotes the $p^e$-th Frobenius power of $\idealm$, that is, the ideal generated by the $p^e$-th powers of the elements of $\idealm$.
+\[ \nu_f^{\idealm}(p^e) \coloneqq  \max \{ n \in \mathbb{N} : f^n \notin \idealm^{[p^e]} \}. \]
+%where $\idealm^{[p^e]}$ denotes the $p^e$-th Frobenius power of $\idealm$, that is, the ideal generated by the $p^e$-th powers of the elements of $\idealm$.
 %It is not hard to see that this number is the largest power of $f$ that is part of a free basis for the localization of the ambient polynomial ring at the origin, over its subring of $p^e$-th powers.

### 2019-11-25 Fsing/FrobeniusThresholdsPaper/FrobeniusThresholds.tex
Updated paper as per referee's comments

@@
 For example, \emph{Hilbert-Kunz multiplicity} is realized in this way. 
-Given an ideal $I$ of a ring $R$ of characteristic $p>0$, $I^{[p^e]}$ denotes the $p^e$-th Frobenius power of $I$, that is, the ideal generated by the $p^e$-th powers of the elements of $I$.
-If $R$ has dimension $d$ and $\lambda\left(R/I^{[p^e]}\right)$ denotes the length of $R/I^{[p^e]}$, the limit of $\frac{\lambda\left(R/I^{[p^e]}\right)}{p^{ed}}$ is the Hilbert-Kunz multiplicity of $R$ with respect to $I$.
+Suppose that $I$ is an ideal of a ring $R$ of characteristic $p>0$.
+Given an integer $e \geq 1$, 
+$I^{[p^e]}$ denotes the $p^e$-th Frobenius power of $I$, that is, the ideal generated by the $p^e$-th powers of the elements of $I$. 
+If $R$ has dimension $d$ and $\lambda\left(R/I^{[p^e]}\right)$ denotes the length of $R/I^{[p^e]}$, 
+then the limit of $\lambda\left(R/I^{[p^e]}\right)/p^{ed}$ as $e$ grows is the Hilbert-Kunz multiplicity of $R$ with respect to $I$.
 

### 2019-11-27 Fsing/FrobeniusThresholdsPaper/FrobeniusThresholds.tex
Updated paper as per referee's comments
Reorganize 'Options for nu' section

@@
 Normalize this integer by dividing by some power of $p^e$, and then take the limit as the integer $e$ tends to infinity.
-The resulting limit, if it exists, should then encode some interesting information about the initial data.
+The resulting limit, if it exists, should encode interesting information about the initial data.
 
@@
 
-\subsection{Options for \texttt{nu}}
-
-We now describe the options available for the function \texttt{nu}.
-As pointed out in the introduction, if $f \in \mathfrak{m}$, the values $\nu^{\mathfrak{m}}_f(p^e)$ can be recovered from the $F$-pure threshold of $f$.
-This is used to speed up computations for certain polynomials whose $F$-pure thresholds can be computed quickly via specialized algorithms or formulas, namely diagonal polynomials, binomials, forms in two variables, and products of factors in simple normal crossing (see Section~\ref{sec.FPT}).
-This feature can be disabled by setting the option \texttt{UseSpecialAlgorithms} (default value \texttt{true}) to \texttt{false}.\footnote{In Section~\ref{ss: UseSpecialAlgorithms} we discuss a couple of situations in which this may be desirable.}
-
-\smallskip
-{\small
-\setstretch{.67}
-\begin{MyVerbatim}
-i7 : R = ZZ/17[x,y,z];
-
-i8 : f = x^3 + y^4 + z^5; -- a diagonal polynomial
-
-i9 : time nu(10, f)
-     -- used 0.0161622 seconds
-
-o9 = 1541642394460
-
-i10 : time nu(10, f, UseSpecialAlgorithms => false)
-     -- used 2.06877 seconds
-
-o10 = 1541642394460
-\end{MyVerbatim}
-}
-\smallskip
-
 In general, the function \texttt{nu} works by searching through a list of integers $n$, and checking containments of the $n$-th power of $I$ in the specified Frobenius power of $J$.
@@
 This implies that when searching for the maximal exponent defining \texttt{nu(e,I,J)} for positive $e$, it is safe to start at $p$ times the output of \texttt{nu(e-1,I,J)}, and one need not search too far past this number.
-This also suggests that the most efficient way to compute \texttt{nu(e,I,J)} is to compute, successively, \texttt{nu(s,I,J)}, for each integer $s = 0,\ldots,e$, and this is indeed how the computation is done in most cases.
+% This also suggests that the most efficient way to compute \texttt{nu(e,I,J)} is to compute, successively, \texttt{nu(s,I,J)}, for each integer $s = 0,\ldots,e$, and this is indeed how the computation is done in most cases.
+
+\subsection{Options for \texttt{nu}}
 
@@
 \smallskip
+
+%We now describe the options available for the function \texttt{nu}.
 
@@
 o23 = 26
+\end{MyVerbatim}
+}
+\smallskip
+
+As pointed out in the introduction, if $f \in \mathfrak{m}$, the values $\nu^{\mathfrak{m}}_f(p^e)$ can be recovered from the $F$-pure threshold of $f$.
+This is used to speed up computations for certain polynomials whose $F$-pure thresholds can be computed quickly via specialized algorithms or formulas, namely diagonal polynomials, binomials, forms in two variables, and products of factors in simple normal crossing (see Section~\ref{sec.FPT}).
+This feature can be disabled by setting the option \texttt{UseSpecialAlgorithms} (default value \texttt{true}) to \texttt{false}.\footnote{In Section~\ref{ss: UseSpecialAlgorithms} we discuss a couple of situations in which this may be desirable.}
+
+\smallskip
+{\small
+\setstretch{.67}
+\begin{MyVerbatim}
+i7 : R = ZZ/17[x,y,z];
+
+i8 : f = x^3 + y^4 + z^5; -- a diagonal polynomial
+
+i9 : time nu(10, f)
+     -- used 0.0161622 seconds
+
+o9 = 1541642394460
+
+i10 : time nu(10, f, UseSpecialAlgorithms => false)
+     -- used 2.06877 seconds
+
+o10 = 1541642394460
 \end{MyVerbatim}

### 2019-12-04 Fsing/FrobeniusThresholdsPaper/FrobeniusThresholds.tex
Added explanation about why F-threshold exists

@@
 \[ \nu_f^{\idealm}(p^e) \coloneqq  \max \{ n \in \mathbb{N} : f^n \notin \idealm^{[p^e]} \}. \]
+If $f^n \notin \idealm^{[p^e]}$ for some $n$, then by the flatness of Frobenius \cite{KunzCharacterizationsOfRegularLocalRings}, $f^{pn} \notin \left( \idealm^{[p^e]} \right)^{[p]} = \idealm^{[p^{e+1}]}$.
+Hence the sequence $\left\{ \frac{ \nu_f^{\idealm}(p^e)}{p^e} \right\}_{e=1}^\infty$ is non-decreasing, and since $f \in \idealm$, $f^{p^e} \in \idealm^{[p^e]}$, the sequence is bounded above by $1$.
 %where $\idealm^{[p^e]}$ denotes the $p^e$-th Frobenius power of $\idealm$, that is, the ideal generated by the $p^e$-th powers of the elements of $\idealm$.
@@
 \[ \ft^{\idealm}(f) \coloneqq  \lim_{e \to \infty} \frac{ \nu_f^{\idealm}(p^e)}{p^e}. \]
-
-This limit exists, and is a rational number when $f\in \idealm$, though the latter is far from obvious  \cite{BlickleMustataSmithDiscretenessAndRationalityOfFThresholds}.
+This limit exists by the above discussion, and is a rational number when $f\in \idealm$, though the latter is far from obvious  \cite{BlickleMustataSmithDiscretenessAndRationalityOfFThresholds}.
 Inspired by its connections with the $F$-purity of pairs,  this limit is called the \emph{$F$-pure threshold} of $f$ at the origin.
@@
 the \emph{$F$-threshold of $I$ with respect to $J$}. 
-The value $\ft^{\idealm}(I)$ is called the \emph{$F$-pure threshold of $I$} at the origin, and if $I = \langle f \rangle$ is principal,  $\ft^{J}(f) \coloneqq  \ft^J(I)$ is called the \emph{$F$-threshold of $f$ with respect to $J$}.
+This limit again exists, and the value $\ft^{\idealm}(I)$ is called the \emph{$F$-pure threshold of $I$} at the origin, and if $I = \langle f \rangle$ is principal,  $\ft^{J}(f) \coloneqq  \ft^J(I)$ is called the \emph{$F$-threshold of $f$ with respect to $J$}.
 Like $F$-pure thresholds, $F$-thresholds are rational (when finite), and can be characterized in terms of test ideals.

### 2019-12-06 Fsing/FrobeniusThresholdsPaper/FrobeniusThresholds.tex
Updated paper as per referee's comments

@@
 \smallskip
+
+\noindent \textcolor{red}{Alternative to the next two paragraphs:}
+
+\textcolor{blue}{Within the \emph{TestIdeals} package, the functions \texttt{testIdeal} and \texttt{FPureModule} are used to compute the test ideals of $f$ at different parameters.
+By comparing test ideals of $f$ at different parameters, we can decide  whether $t$ is the $F$-pure threshold of $f$. 
+Since not only the $F$-pure thresholds, but also the higher $F$-jumping numbers, are determined by containment conditions on test ideals, the functionality is extended to determine whether a given number is an $F$-jumping number.}
 
@@
 It is desirable to be able to work with nonstandard gradings as well, and results of \cite{HernandezTeixeiraFThresholdFunctions} suggest an algorithm for doing so.
-Thus, the package could be improved by finalizing and implementing such an algorithm.
+For instance, the polynomial $f = x^6+x^2 y^2 + y^3$ is homogeneous under the grading $\deg x = 1, \deg y = 2$, and it is shown that the $F$-threshold of $f$ with respect to the ideal $\langle x, y^2 \rangle$ can be computed as the $F$-pure threshold of $x^3 + x^2 y + y^2$, which is homogeneous under the standard grading.
+The package could be improved by finalizing and implementing such an algorithm in greater generality.
 

### 2019-12-11 Fsing/FrobeniusThresholdsPaper/FrobeniusThresholds.tex
Small changes to paper

@@
 
-For example, \emph{Hilbert-Kunz multiplicity} is realized in this way. 
+For example, the \emph{Hilbert--Kunz multiplicity} is realized in this way. 
 Suppose that $I$ is an ideal of a ring $R$ of characteristic $p>0$.
@@
 If $R$ has dimension $d$ and $\lambda\left(R/I^{[p^e]}\right)$ denotes the length of $R/I^{[p^e]}$, 
-then the limit of $\lambda\left(R/I^{[p^e]}\right)/p^{ed}$ as $e$ grows is the Hilbert-Kunz multiplicity of $R$ with respect to $I$.
+then the limit of $\lambda\left(R/I^{[p^e]}\right)/p^{ed}$ as $e$ tends to infinity is the Hilbert--Kunz multiplicity of $R$ with respect to $I$.
 
-Consider a nonzero polynomial $f$ and a natural number $e$.  If $f$ does not vanish at the origin, then set $\nu_f^{\idealm}(p^e) := \infty$.  Otherwise, $f \in \idealm$, and we instead define
+Consider a nonzero polynomial $f$ and a natural number $e$.  If $f$ does not vanish at the origin, then set $\nu_f^{\idealm}(p^e) \coloneqq \infty$.  Otherwise, $f \in \idealm$, and we instead define
 \[ \nu_f^{\idealm}(p^e) \coloneqq  \max \{ n \in \mathbb{N} : f^n \notin \idealm^{[p^e]} \}. \]
 If $f^n \notin \idealm^{[p^e]}$ for some $n$, then by the flatness of Frobenius \cite{KunzCharacterizationsOfRegularLocalRings}, $f^{pn} \notin \left( \idealm^{[p^e]} \right)^{[p]} = \idealm^{[p^{e+1}]}$.
-Hence the sequence $\left\{ \frac{ \nu_f^{\idealm}(p^e)}{p^e} \right\}_{e=1}^\infty$ is non-decreasing, and since $f \in \idealm$, $f^{p^e} \in \idealm^{[p^e]}$, the sequence is bounded above by $1$.
+Hence the sequence $\Big( \frac{ \nu_f^{\idealm}(p^e)}{p^e} \Big)_{e=0}^\infty$ is non-decreasing, and since $f^{p^e} \in \idealm^{[p^e]}$, the sequence is bounded above by $1$.  
 %where $\idealm^{[p^e]}$ denotes the $p^e$-th Frobenius power of $\idealm$, that is, the ideal generated by the $p^e$-th powers of the elements of $\idealm$.
@@
 \[ \ft^{\idealm}(f) \coloneqq  \lim_{e \to \infty} \frac{ \nu_f^{\idealm}(p^e)}{p^e}. \]
-This limit exists by the above discussion, and is a rational number when $f\in \idealm$, though the latter is far from obvious  \cite{BlickleMustataSmithDiscretenessAndRationalityOfFThresholds}.
+This limit exists by the above discussion, and is a rational number when $f\in \idealm$, though the latter is far from obvious  \cite[Theorem~3.1]{BlickleMustataSmithDiscretenessAndRationalityOfFThresholds}.
 Inspired by its connections with the $F$-purity of pairs,  this limit is called the \emph{$F$-pure threshold} of $f$ at the origin.
@@
 \begin{MyVerbatim}
-i11 : R = ZZ/5[x,y,z];
+i7 : R = ZZ/5[x,y,z];
 
-i12 : m = ideal(x, y, z);
+i8 : m = ideal(x, y, z);
 
-o12 : Ideal of R
+o8 : Ideal of R
 
-i13 : time nu(2, m, m^2) -- uses binary search (default)
+i9 : time nu(2, m, m^2) -- uses binary search (default)
      -- used 1.82479 seconds
 
-o13 = 97
+o9 = 97
 
-i14 : time nu(2, m, m^2, Search => Linear) -- but linear search gets luckier
+i10 : time nu(2, m, m^2, Search => Linear) -- but linear search gets luckier
      -- used 0.597035 seconds
 
-o14 = 97
+o10 = 97
 \end{MyVerbatim}
@@
 \begin{MyVerbatim}
-i15 : nu(5, x^2*y^4 + y^2*z^7 + z^2*x^8, ReturnList => true)
+i11 : nu(5, x^2*y^4 + y^2*z^7 + z^2*x^8, ReturnList => true)
 
-o15 = {0, 1, 8, 44, 224, 1124}
+o11 = {0, 1, 8, 44, 224, 1124}
 
-o15 : List
+o11 : List
 \end{MyVerbatim}
@@
 \begin{MyVerbatim}
-i16 : R = ZZ/11[x,y,z];
+i12 : R = ZZ/11[x,y,z];
 
-i17 : f = x^3 + y^3 + z^3 + x*y*z;
+i13 : f = x^3 + y^3 + z^3 + x*y*z;
 
-i18 : time nu(3, f) -- ContainmentTest is set to FrobeniusRoot, by default
+i14 : time nu(3, f) -- ContainmentTest is set to FrobeniusRoot, by default
      -- used 0.153691 seconds
 
-o18 = 1209
+o14 = 1209
 
-i19 : time nu(3, f, ContainmentTest => StandardPower)
+i15 : time nu(3, f, ContainmentTest => StandardPower)
      -- used 10.1343 seconds
 
-o19 = 1209
+o15 = 1209
 \end{MyVerbatim}
@@
 \begin{MyVerbatim}
-i20 : R = ZZ/3[x,y];
+i16 : R = ZZ/3[x,y];
 
-i21 : m = ideal(x, y);
+i17 : m = ideal(x, y);
 
-o21 : Ideal of R
+o17 : Ideal of R
 
-i22 : nu(4, m^5)
+i18 : nu(4, m^5)
 
-o22 = 32
+o18 = 32
 
-i23 : nu(4, m^5, ContainmentTest => FrobeniusPower)
+i19 : nu(4, m^5, ContainmentTest => FrobeniusPower)
 
-o23 = 26
+o19 = 26
 \end{MyVerbatim}
@@
 \begin{MyVerbatim}
-i7 : R = ZZ/17[x,y,z];
+i20 : R = ZZ/17[x,y,z];
 
-i8 : f = x^3 + y^4 + z^5; -- a diagonal polynomial
+i21 : f = x^3 + y^4 + z^5; -- a diagonal polynomial
 
-i9 : time nu(10, f)
+i22 : time nu(10, f)
      -- used 0.0161622 seconds
 
-o9 = 1541642394460
+o22 = 1541642394460
 
-i10 : time nu(10, f, UseSpecialAlgorithms => false)
+i23 : time nu(10, f, UseSpecialAlgorithms => false)
      -- used 2.06877 seconds
 
-o10 = 1541642394460
+o23 = 1541642394460
 \end{MyVerbatim}

### 2019-12-14 Fsing/FrobeniusThresholdsPaper/FrobeniusThresholds.tex
Changes in Future Directions of FT paper

@@
 
-One natural direction of development would be to  incorporate the test ideals $\tau(I^t)$ when computing $F$-thresholds in the case where the ideal $I$ is nonprincipal.
-The theoretical foundation for computing such test ideals has already largely been worked out in \cite{SchwedeTuckerTestIdealsOfNonPrincipal}, but such an update to the \emph{FrobeniusThresholds} package would require the  \emph{TestIdeals} package to be updated first.
+As a natural and simple way to extend the functionality of the \emph{FrobeniusThresholds} package, we wish to implement a method analogous to \texttt{fpt} to compute $F$-thresholds of polynomials with respect to arbitrary ideals.
+Although most of our current specialized algorithms do no extend to such generality, our ``guess-and-check'' methods do, and will likely give us an effective tool in computing or estimating $F$-thresholds.
 
-At the moment, the specialized algorithm called by the \texttt{fpt} function for computing the $F$-pure threshold of a homogeneous polynomial in two variables limits us to working with the standard grading on the ambient polynomial ring.
-It is desirable to be able to work with nonstandard gradings as well, and results of \cite{HernandezTeixeiraFThresholdFunctions} suggest an algorithm for doing so.
-For instance, the polynomial $f = x^6+x^2 y^2 + y^3$ is homogeneous under the grading $\deg x = 1, \deg y = 2$, and it is shown that the $F$-threshold of $f$ with respect to the ideal $\langle x, y^2 \rangle$ can be computed as the $F$-pure threshold of $x^3 + x^2 y + y^2$, which is homogeneous under the standard grading.
-The package could be improved by finalizing and implementing such an algorithm in greater generality.
+The lack of specialized algorithms for the computation of $F$-thresholds, noted above, has one exception: the algorithm for computing the $F$-pure threshold of a homogeneous polynomial in two variables.
+Results of \cite{HernandezTeixeiraFThresholdFunctions} show that this algorithm can be easily modified to compute $F$-thresholds of such polynomials with respect to ideals generated by two relatively prime homogeneous polynomials.
+Once this is implemented, we will be able to compute $F$-thresholds of polynomials in two variables homogeneous under non-standard grading, as those agree with $F$-thresholds of standard-homogeneous polynomials (with respect to different ideals).
+For instance, the $F$-pure threshold of the polynomial $x^6+x^2 y^2 + y^3$, homogeneous under the grading $\deg x = 1, \deg y = 2$, can be computed as the $F$-threshold of the standard-homogeneous polynomial $x^6 + x^2 y^4 + y^6$ with respect to the ideal $\langle x, y^2\rangle$.
+%The package could be improved by finalizing and implementing such an algorithm in greater generality.
 
-Finally, it would be desirable to develop and implement additional algorithms for computing $F$-pure thresholds and $F$-jumping numbers for additional classes of polynomials.
+It would be desirable to develop and implement additional algorithms for computing $F$-pure thresholds and $F$-jumping numbers for additional classes of polynomials.
 The first, third, and fourth authors, along with Josep \'Alvarez Montaner, Jack Jeffries, and Luis N\'u\~nez-Betancourt,  are currently working on developing such algorithms.
 The theoretical foundation of these algorithms lies in polyhedral geometry and integer programming, making them natural candidates for  implementation in \emph{Macaulay2}.
+
+Finally, one natural direction of development would be to  incorporate the test ideals $\tau(I^t)$ when computing $F$-thresholds in the case where the ideal $I$ is nonprincipal.
+The theoretical foundation for computing such test ideals has already largely been worked out in \cite{SchwedeTuckerTestIdealsOfNonPrincipal}, but such an update to the \emph{FrobeniusThresholds} package would require the  \emph{TestIdeals} package to be updated first.
 

### 2019-12-19 Fsing/FrobeniusThresholdsPaper/FrobeniusThresholds.tex
Added alternate paragraph about compareFPT

@@
 Since not only the $F$-pure thresholds, but also the higher $F$-jumping numbers, are determined by containment conditions on test ideals, the functionality is extended to determine whether a given number is an $F$-jumping number.}
+
+\noindent \textcolor{red}{Another possibility:}
+
+\textcolor{blue}{
+   The general method applied calls upon functionality from the \emph{TestIdeals} package.
+   The test ideals $\tau(f^t)$ of $f$ vary discretely with the parameter $t$; the function \texttt{FPureModule} in \emph{TestIdeals} is used  to compute the ``last'' test ideal of $f$ with parameter in the interval $[0,t)$.
+   Comparing this with the test ideal $\tau(f^t)$, computed by the function \texttt{testIdeal}, we can determine whether $t$ is an $F$-jumping number of $f$, or more specifically, the $F$-pure threshold of $f$.
+}
 

### 2019-12-29 Fsing/FrobeniusThresholdsPaper/FrobeniusThresholds.tex
Updated Section 3

@@
 
-\textcolor{blue}{Within the \emph{TestIdeals} package, the functions \texttt{testIdeal} and \texttt{FPureModule} are used to compute the test ideals of $f$ at different parameters.
-By comparing test ideals of $f$ at different parameters, we can decide  whether $t$ is the $F$-pure threshold of $f$. 
-Since not only the $F$-pure thresholds, but also the higher $F$-jumping numbers, are determined by containment conditions on test ideals, the functionality is extended to determine whether a given number is an $F$-jumping number.}
-
-\noindent \textcolor{red}{Another possibility:}
+% \textcolor{blue}{Within the \emph{TestIdeals} package, the functions \texttt{testIdeal} and \texttt{FPureModule} are used to compute the test ideals of $f$ at different parameters.
+% By comparing test ideals of $f$ at different parameters, we can decide  whether $t$ is the $F$-pure threshold of $f$. 
+% Since not only the $F$-pure thresholds, but also the higher $F$-jumping numbers, are determined by containment conditions on test ideals, the functionality is extended to determine whether a given number is an $F$-jumping number.}
+% 
+% \noindent \textcolor{red}{Another possibility:}
 

### 2019-12-30 Fsing/FrobeniusThresholdsPaper/FrobeniusThresholds.tex
Updated compareFPT section

--- 2019-12-19 Fsing/FrobeniusThresholdsPaper/FrobeniusThresholds.tex
@@
 }
+
 \smallskip
 
-\noindent \textcolor{red}{Alternative to the next two paragraphs:}
-
-\textcolor{blue}{Within the \emph{TestIdeals} package, the functions \texttt{testIdeal} and \texttt{FPureModule} are used to compute the test ideals of $f$ at different parameters.
-By comparing test ideals of $f$ at different parameters, we can decide  whether $t$ is the $F$-pure threshold of $f$. 
-Since not only the $F$-pure thresholds, but also the higher $F$-jumping numbers, are determined by containment conditions on test ideals, the functionality is extended to determine whether a given number is an $F$-jumping number.}
-
-\noindent \textcolor{red}{Another possibility:}
-
-\textcolor{blue}{
 The general method applied calls upon functionality from the \emph{TestIdeals} package.
@@
    Comparing this with the test ideal $\tau(f^t)$, computed by the function \texttt{testIdeal}, we can determine whether $t$ is an $F$-jumping number of $f$, or more specifically, the $F$-pure threshold of $f$.
-}
 
-The general method applied calls upon functionality from the \emph{TestIdeals} package.
-The functions \texttt{testIdeal} and \texttt{FPureModule} therein are used to compute the test ideals $\tau(f^t)$ and $\tau(f^{t-\varepsilon})$, for $0<\varepsilon\ll 1$.
-By comparing these test ideals, we can decide whether $t$ is the $F$-pure threshold of $f$.
-For instance, when $R$ is a polynomial ring, $t$ is the $F$-pure threshold of $f$ at the origin if and only if $\tau(f^t)$ is contained in the homogeneous maximal ideal, but $\tau(f^{t-\varepsilon})$ is not.
-
-Since not only the $F$-pure thresholds, but also the higher $F$-jumping numbers, are determined by containment conditions on test ideals, the functionality is extended to determine whether a given number is an $F$-jumping number.
+% The general method applied calls upon functionality from the \emph{TestIdeals} package.
+% The functions \texttt{testIdeal} and \texttt{FPureModule} therein are used to compute the test ideals $\tau(f^t)$ and $\tau(f^{t-\varepsilon})$, for $0<\varepsilon\ll 1$.
+% By comparing these test ideals, we can decide whether $t$ is the $F$-pure threshold of $f$.
+% For instance, when $R$ is a polynomial ring, $t$ is the $F$-pure threshold of $f$ at the origin if and only if $\tau(f^t)$ is contained in the homogeneous maximal ideal, but $\tau(f^{t-\varepsilon})$ is not.
+% 
+% Since not only the $F$-pure thresholds, but also the higher $F$-jumping numbers, are determined by containment conditions on test ideals, the functionality is extended to determine whether a given number is an $F$-jumping number.
 

### 2020-06-09 Fsing/FrobeniusThresholdsPaper/response_to_report_C_on_v2.txt
Added new referee reports

190624-Witt-v2 (FrobeniusThresholds)

The package consists of 3600 lines of code and documentation, so it is
substantial.  It installs and the tests work without error.  The package is in
pretty good shape.

=============================================================================
comments on the code

Please remove the redundant top level directory submission-files/ from the zip
file.

The package TestIdeals has already been published, and there is no need to
include it in the zip file.

Consider choosing a better name for the function "nu", which is simply the
English spelling of a random Greek letter, and thus is not descriptive.
Something with words in it, such as "containmentPower", or even "index".

Consider renaming "fpt" to "pureThreshold" and "isFPT" to "isPureThreshold".
(The "F" for "Frobenius" can be assumed.)

Consider removing redundant parentheses, as in these lines:

		if (I1 == ideal sub(0, S1)) then (

		while ((i < #genList) and (x == sub(0, S1))) do(

		ideal(x) : (ideal(x) : I1)

		annihilator(coker ddual)

	    	(Hom(Hom(M1, S1^1), S1^1))

		if (o.IsGraded==true) then (

If o.IsGraded is always a Boolean value, then instead of

		if (o.IsGraded==true) then (

write

		if o.IsGraded then (

Similarly, instead of

		if (isWellDefined(h) == false) then

you can write

		if not isWellDefined h then

Fix all such comparisons with "true" and "false".

The value of an "if" expression is "null" if the predicate is false, so this
can be omitted:

    else (
        null
    )

Change "if" to "whether" in

       Verifying if special algorithms apply...

The newline characters in verbose messages such as this one

        if o.Verbose then print "\nVerifying if special algorithms apply...";

resulting in double-spaced output, wasting space on the screen and on the pages
of the article.

=============================================================================
comments on the documentation

In

	 "Takes on lists consisting of two numbers"

I don't know what "takes on lists" means.  Maybe say "accepts a list"?

Change

  	"whether to only consider the behavior at the origin"

to

  	"whether to consider only the behavior at the origin"

In

	"toggles verbose output"

you don't mean what you say, since "toggle" replaces false by true and true by
false.  You mean "whether the output is to be verbose"

In

	Consider a Veronese subring (which is étale in codimension 1)

the use of "étale" is incorrect -- it should be applied to ring homomorphism,
not to a ring.

=============================================================================
comments on the article

This

	 the condition that the Frobenius morphism splits as a map of rings

is ambiguous.  Do you mean "is a split surjection" or "is a split injection"?

It would be better if comments in the displayed example code, such as "uses
binary search (default)", were in the surrounding text, because then complete
sentences could be used, and they would be read by the reader in the normal
sequence.  For this purpose, displays could be split, to allow comments in the
text between the two parts.

The displayed example output seems to be a diffferent color, which is
disconcerting.

The displayed example output would look better if it were indented.

The use of "in" in

    	      f is a product of factors in simple normal crossing

sounds peculiar, as does speaking of f instead of its zero set.  Perhaps say
something like

		f defines a simple normal crossing divisor

You use "isSimpleNormalCrossings" in the text, but "isSimpleNormalCrossing" in
the code.

It's adverbs that come after verbs, so change

		can be used independent of

to

		can be used independently of

=============================================================================

### 2020-06-10 Fsing/FrobeniusThresholdsPaper/response_to_report_C_on_v2.txt
Made more changes suggested by referee
More changes

@@
 
-Consider removing redundant parentheses, as in these lines:
+*****************************************************************************
 
-		if (I1 == ideal sub(0, S1)) then (
+Consider removing redundant parentheses...
 
-		while ((i < #genList) and (x == sub(0, S1))) do(
-
-		ideal(x) : (ideal(x) : I1)
-
-		annihilator(coker ddual)
-
-	    	(Hom(Hom(M1, S1^1), S1^1))
-
-		if (o.IsGraded==true) then (
+-----------------------------------------------------------------------------
+In progress...
+*****************************************************************************
 
@@
 
+-----------------------------------------------------------------------------
+Done.
+*****************************************************************************
+
 The value of an "if" expression is "null" if the predicate is false, so this
@@
 
+-----------------------------------------------------------------------------
+We'd rather keep the "else null", to make clear the intention to return null.
+*****************************************************************************
+
 Change "if" to "whether" in
@@
        Verifying if special algorithms apply...
+
+-----------------------------------------------------------------------------
+Done.
+*****************************************************************************
 
@@
 of the article.
+
+-----------------------------------------------------------------------------
+Those were removed.
+*****************************************************************************
 
@@
 not to a ring.
+
+-----------------------------------------------------------------------------
+All of the above were fixed.
+*****************************************************************************
 

### 2020-06-10 Fsing/FrobeniusThresholdsPaper/FrobeniusThresholds.tex
Deleted redundant parentheses

@@
 \usepackage{fancyvrb}
-\DefineVerbatimEnvironment%
-{MyVerbatim}{Verbatim}
-{formatcom=\color{Violet}}
+% \DefineVerbatimEnvironment%
+% {MyVerbatim}{Verbatim}
+% {formatcom=\color{Violet}}
 
@@
 \setstretch{.67}
-\begin{MyVerbatim}
+\begin{Verbatim}
 i1 : R = ZZ/11[x,y];
@@
 o6 = 120
-\end{MyVerbatim}
+\end{Verbatim}
 }
@@
 \setstretch{.67}
-\begin{MyVerbatim}
+\begin{Verbatim}
 i7 : R = ZZ/5[x,y,z];
@@
 o10 = 97
-\end{MyVerbatim}
+\end{Verbatim}
 }
@@
 \setstretch{.67}
-\begin{MyVerbatim}
+\begin{Verbatim}
 i11 : nu(5, x^2*y^4 + y^2*z^7 + z^2*x^8, ReturnList => true)
@@
 o11 : List
-\end{MyVerbatim}
+\end{Verbatim}
 }
@@
 \setstretch{.67}
-\begin{MyVerbatim}
+\begin{Verbatim}
 i12 : R = ZZ/11[x,y,z];
@@
 o15 = 1209
-\end{MyVerbatim}
+\end{Verbatim}
 }
@@
 \setstretch{.67}
-\begin{MyVerbatim}
+\begin{Verbatim}
 i16 : R = ZZ/3[x,y];
@@
 o19 = 26
-\end{MyVerbatim}
+\end{Verbatim}
 }
@@
 \setstretch{.67}
-\begin{MyVerbatim}
+\begin{Verbatim}
 i20 : R = ZZ/17[x,y,z];
@@
 o23 = 1541642394460
-\end{MyVerbatim}
+\end{Verbatim}
 }
@@
 \setstretch{.67}
-\begin{MyVerbatim}
+\begin{Verbatim}
 i24 : R = ZZ/7[x,y];
@@
 o27 = 285
-\end{MyVerbatim}
+\end{Verbatim}
 }
@@
 \setstretch{.67}
-\begin{MyVerbatim}
+\begin{Verbatim}
 i1 : R = ZZ/11[x,y,z]/(x^2 - y*(z - 1));
@@
 o4 = false
-\end{MyVerbatim}
+\end{Verbatim}
 }
@@
 \setstretch{.67}
-\begin{MyVerbatim}
+\begin{Verbatim}
 i5 : R = ZZ/13[x,y];
@@
 o8 = false
-\end{MyVerbatim}
+\end{Verbatim}
 }
@@
 \setstretch{.67}
-\begin{MyVerbatim}
+\begin{Verbatim}
 i1 : R = ZZ/5[x,y,z];
@@
 o3 : List
-\end{MyVerbatim}
+\end{Verbatim}
 }
@@
 \setstretch{.67}
-\begin{MyVerbatim}
+\begin{Verbatim}
 i4 : fpt(x^17 + y^20 + z^24) -- a diagonal polynomial
@@
 o7 : QQ
-\end{MyVerbatim}
+\end{Verbatim}
 }
@@
 \setstretch{.67}
-\begin{MyVerbatim}
+\begin{Verbatim}
 i8 : fpt({x, y, x + y, x + 3*y}, {2, 6, 9, 10}) == oo
@@
 o8 = true
-\end{MyVerbatim}
+\end{Verbatim}
 }
@@
 \setstretch{.67}
-\begin{MyVerbatim}
+\begin{Verbatim}
 i9 : f = x^2*(x + y)^3*(x + 3*y^2)^5;
@@
 o12 : QQ
-\end{MyVerbatim}
+\end{Verbatim}
 }
@@
 \setstretch{.67}
-\begin{MyVerbatim}
+\begin{Verbatim}
 i13 : f = x^6*y^4 + x^4*y^9 + (x^2 + y^3)^3;
@@
 o15 : QQ
-\end{MyVerbatim}
+\end{Verbatim}
 }
@@
 \setstretch{.67}
-\begin{MyVerbatim}
+\begin{Verbatim}
 i16 : f = x^3*y^11*(x + y)^8*(x^2 + y^3)^8;
@@
 o19 : QQ
-\end{MyVerbatim}
+\end{Verbatim}
 }
@@
 \setstretch{.67}
-\begin{MyVerbatim}
+\begin{Verbatim}
 i20 : f = x^7*y^5*(x + y)^5*(x^2 + y^3)^4;
@@
 o22 : List
-\end{MyVerbatim}
+\end{Verbatim}
 }
@@
 \setstretch{.67}
-\begin{MyVerbatim}
+\begin{Verbatim}
 i23 : f = 2*x^10*y^8 + x^4*y^7 - 2*x^3*y^8;
@@
 o25 : List
-\end{MyVerbatim}
+\end{Verbatim}
 }
@@
 \setstretch{.67}
-\begin{MyVerbatim}
+\begin{Verbatim}
 i26 : time numeric fpt(f, DepthOfSearch => 3, FinalAttempt => true)
@@
 o28 : QQ
-\end{MyVerbatim}
+\end{Verbatim}
 }
@@
 \setstretch{.67}
-\begin{MyVerbatim}
+\begin{Verbatim}
 i29 : fpt(f, DepthOfSearch => 3, FinalAttempt => true, Verbose => true)
@@
 o29 : List
-\end{MyVerbatim}
+\end{Verbatim}
 }
@@
 \setstretch{.67}
-\begin{MyVerbatim}
+\begin{Verbatim}
 i30 : R = ZZ/7[x,y];
@@
 o33 : QQ
-\end{MyVerbatim}
+\end{Verbatim}
 }
@@
 
-\subsection{The function \texttt{isSimpleNormalCrossings}} \label{subsec.SNC}
-As mentioned earlier, the function \texttt{isSimpleNormalCrossings} verifies whether a polynomial $f$ is a product of factors in simple normal crossing.
+\subsection{The function \texttt{isSimpleNormalCrossing}} \label{subsec.SNC}
+As mentioned earlier, the function \texttt{isSimpleNormalCrossing} verifies whether a polynomial $f$ defines a simple normal crossing divisor.
 Suppose that $f$ has factorization $f_1^{a_i} f_2^{a_2} \cdots f_n^{a_n}$.  Recall that its factors $f_i$ are said to be in
 \emph{simple normal crossing} at a point if, locally, they form part of a regular system of parameters.
-The function \texttt{isSimpleNormalCrossings} determines whether $f$ has simple normal crossings at the origin by computing the Jacobian matrix of each subset of $\{ f_1, \ldots, f_n \}$ (evaluated at the origin), and checking that these matrices have the expected rank, and that these subsets generate ideals of the appropriate height.
+The function \texttt{isSimpleNormalCrossing} determines whether $f$ has simple normal crossings at the origin by computing the Jacobian matrix of each subset of $\{ f_1, \ldots, f_n \}$ (evaluated at the origin), and checking that these matrices have the expected rank, and that these subsets generate ideals of the appropriate height.
 
@@
 \setstretch{.67}
-\begin{MyVerbatim}
+\begin{Verbatim}
 i34 : R = ZZ/7[x,y,z];
@@
 o36 = false
-\end{MyVerbatim}
+\end{Verbatim}
 }
@@
 
-The function \texttt{isSimpleNormalCrossing} is exposed to the user, so can be used independent of any $F$-pure threshold calculation.
+The function \texttt{isSimpleNormalCrossing} is exposed to the user, so can be used independently of any $F$-pure threshold calculation.
 If the user sets its option \texttt{AtOrigin} to \texttt{false} (its default value is \texttt{true}), then the function checks whether the $f_i$ are in simple normal crossing \emph{everywhere}, which can be much slower, since Jacobian ideals are computed.
@@
 \setstretch{.67}
-\begin{MyVerbatim}
+\begin{Verbatim}
 i37 : R = QQ[x,y,z];
@@
 o40 = false
-\end{MyVerbatim}
+\end{Verbatim}
 }

### 2020-06-15 Fsing/FrobeniusThresholdsPaper/response_to_report_C_on_v2.txt
Deleted redundant parentheses
Finished deleting redundant parentheses
Made changes to the paper suggested by referee

@@
 -----------------------------------------------------------------------------
-In progress...
+We believe we have now removed the vast majority of redundant parentheses.
+-----------------------------------------------------------------------------
+
 *****************************************************************************
@@
 Done.
+-----------------------------------------------------------------------------
+
 *****************************************************************************
@@
 We'd rather keep the "else null", to make clear the intention to return null.
+-----------------------------------------------------------------------------
+
 *****************************************************************************
@@
 Those were removed.
-*****************************************************************************
+-----------------------------------------------------------------------------
 
@@
 All of the above were fixed.
-*****************************************************************************
+-----------------------------------------------------------------------------
 
@@
 
+-----------------------------------------------------------------------------
+We removed the ambiguity, saying it is a split injection. 
+-----------------------------------------------------------------------------
+
+*****************************************************************************
+
 It would be better if comments in the displayed example code, such as "uses
@@
 
+-----------------------------------------------------------------------------
+Those comments were removed and incorporated in surrounding text. 
+-----------------------------------------------------------------------------
+
+*****************************************************************************
+
 The displayed example output seems to be a diffferent color, which is
@@
 
+-----------------------------------------------------------------------------
+The displayed examples are now shown in black.
+-----------------------------------------------------------------------------
+
+*****************************************************************************
+
 The displayed example output would look better if it were indented.
+
+-----------------------------------------------------------------------------
+They are now indented.
+-----------------------------------------------------------------------------
+
+*****************************************************************************
 
@@
 
+-----------------------------------------------------------------------------
+All of the above were fixed.
+-----------------------------------------------------------------------------
+
 =============================================================================

### 2020-06-15 Fsing/FrobeniusThresholdsPaper/FrobeniusThresholds.tex
Made changes to the paper suggested by referee

--- 2019-12-30 Fsing/FrobeniusThresholdsPaper/FrobeniusThresholds.tex
@@
 {MyVerbatim}{Verbatim}
-{formatcom=\color{Violet}}
+{xleftmargin=5mm}
+%{formatcom=\color{Violet}}
 
@@
 This paper describes the \emph{Macaulay2} package \emph{FrobeniusThresholds}\footnote{This package was previously named \emph{FThresholds}} \cite{M2, FThresholdsPackage}, which provides tools for computing or estimating certain fundamental invariants in positive characteristic commutative algebra, namely \emph{$F$-pure thresholds}, \emph{$F$-thresholds}, and \emph{$F$-jumping exponents}.
-Recall that a ring of prime characteristic $p>0$ is \emph{$F$-pure} if the Frobenius map|that is, the ring endomorphism sending an element to its $p$-th power|is a pure morphism;  under natural geometric hypotheses, this is equivalent to the condition that the Frobenius morphism splits as a map of rings.
+Recall that a ring of prime characteristic $p>0$ is \emph{$F$-pure} if the Frobenius map|that is, the ring endomorphism sending an element to its $p$-th power|is a pure morphism;  under natural geometric hypotheses, this is equivalent to the condition that the Frobenius morphism is a split injection of rings.
 The concept of $F$-purity has proven to be important in commutative algebra, and has a rich history.
@@
 \texttt{Binary} (the default value) and \texttt{Linear}.
+In the example below, the default search method, \texttt{Binary}, is used.
 
@@
 
-i9 : time nu(2, m, m^2) -- uses binary search (default)
+i9 : time nu(2, m, m^2)
      -- used 1.82479 seconds
@@
 o9 = 97
+\end{MyVerbatim}
+}
+%\medskip
+\smallskip
 
-i10 : time nu(2, m, m^2, Search => Linear) -- but linear search gets luckier
+\noindent
+However, a linear search is faster in this case.
+
+\smallskip
+{\small
+\setstretch{.67}
+\begin{MyVerbatim}
+i10 : time nu(2, m, m^2, Search => Linear)
      -- used 0.597035 seconds
@@
 }
-%\medskip
 \smallskip
@@
 
-% \medskip
+In the example below, \texttt{ContainmentTest} is set to its default value for polynomials, namely \texttt{FrobeniusRoot}.
+
 \smallskip
@@
 
-i14 : time nu(3, f) -- ContainmentTest is set to FrobeniusRoot, by default
+i14 : time nu(3, f) 
      -- used 0.153691 seconds
@@
 o14 = 1209
+\end{MyVerbatim}
+}
+\smallskip
 
+\noindent
+If \texttt{ContainmentTest} is set to \texttt{StandardPower}, instead, the computation is significantly slower.
+
+\smallskip
+{\small
+\setstretch{.67}
+\begin{MyVerbatim}
 i15 : time nu(3, f, ContainmentTest => StandardPower)
@@
 }
-%\medskip
+\smallskip
 
@@
 As pointed out in the introduction, if $f \in \mathfrak{m}$, the values $\nu^{\mathfrak{m}}_f(p^e)$ can be recovered from the $F$-pure threshold of $f$.
-This is used to speed up computations for certain polynomials whose $F$-pure thresholds can be computed quickly via specialized algorithms or formulas, namely diagonal polynomials, binomials, forms in two variables, and products of factors in simple normal crossing (see Section~\ref{sec.FPT}).
+This is used to speed up computations for certain polynomials whose $F$-pure thresholds can be computed quickly via specialized algorithms or formulas, namely diagonal polynomials, binomials, forms in two variables, and polynomials that define simple normal crossing divisors (see Section~\ref{sec.FPT}).
 This feature can be disabled by setting the option \texttt{UseSpecialAlgorithms} (default value \texttt{true}) to \texttt{false}.\footnote{In Section~\ref{ss: UseSpecialAlgorithms} we discuss a couple of situations in which this may be desirable.}
+
+The following example shows, for a diagonal polynomial, how much faster the computation can be when special algorithms are enabled.
 
@@
 
-i21 : f = x^3 + y^4 + z^5; -- a diagonal polynomial
+i21 : f = x^3 + y^4 + z^5;
 
@@
 
-The \texttt{fpt} function has an option called \texttt{UseSpecialAlgorithms}, which, when set to \texttt{true} (its default value), tells \texttt{fpt} to first check whether $f$ is a diagonal polynomial, a binomial, a form in two variables, or a product of factors in simple normal crossing, in that order.
+The \texttt{fpt} function has an option called \texttt{UseSpecialAlgorithms}, which, when set to \texttt{true} (its default value), tells \texttt{fpt} to first check whether $f$ is a diagonal polynomial, a binomial, a form in two variables, or a polynomial that defines a simple normal crossing divisor, in that order.
 When $f$ is a diagonal polynomial, a binomial, or a form in two variables, algorithms of Hern\'andez \cite{HernandezFInvariantsOfDiagonalHyp, HernandezFPureThresholdOfBinomial} or Hern\'andez and Teixeira \cite{HernandezTeixeiraFThresholdFunctions} are executed to compute the $F$-pure threshold.
-%Algorithms for computing $F$-pure thresholds of binomials also appear in \cite{ShibutaTakagiLCThresholds}, though they are only valid in certain special characteristics.
+
+In the following example, we compute the $F$-pure threshold of a diagonal polynomial.
 
@@
 \begin{MyVerbatim}
-i4 : fpt(x^17 + y^20 + z^24) -- a diagonal polynomial
+i4 : fpt(x^17 + y^20 + z^24)
 
@@
 o4 : QQ
+\end{MyVerbatim}
+}
+\smallskip
 
-i5 : fpt(x^2*y^6*z^10 + x^10*y^5*z^3) -- a binomial
+\noindent
+Next, we compute the $F$-pure threshold of a binomial.
+
+\smallskip
+{\small
+\setstretch{.67}
+\begin{MyVerbatim}
+i5 : fpt(x^2*y^6*z^10 + x^10*y^5*z^3)
 
@@
 o5 : QQ
+\end{MyVerbatim}
+}
+\smallskip
 
+\noindent
+Finally, we compute the $F$-pure threshold of a form in two variables.
+
+\smallskip
+{\small
+\setstretch{.67}
+\begin{MyVerbatim}
 i6 : R = ZZ/5[x,y];
 
-i7 : fpt(x^2*y^6*(x + y)^9*(x + 3*y)^10) -- a form in two variables
+i7 : fpt(x^2*y^6*(x + y)^9*(x + 3*y)^10)
 
@@
 
-\noindent The algorithm for computing the $F$-pure threshold of a binary form $f$ requires factoring $f$ into linear forms, and that may be difficult or impossible when that factorization occurs in a Galois field of excessively large order.
+The algorithm for computing the $F$-pure threshold of a binary form $f$ requires factoring $f$ into linear forms, and that may be difficult or impossible when that factorization occurs in a Galois field of excessively large order.
 This is a situation when the user will want to set the option \texttt{UseSpecialAlgorithms} to \texttt{false}.
@@
 
-If \texttt{UseSpecialAlgorithms} is set to \texttt{true} and $f$ does not fall into any of the aforementioned cases, then the function \texttt{fpt} next calls \texttt{isSimpleNormalCrossing(f)} (see Section~\ref{subsec.SNC}) to check whether the polynomial $f$ is (locally, at the origin) a product of factors that are in simple normal crossing, in which case the $F$-pure threshold is simply the reciprocal of the largest multiplicity occurring in that factorization.
+If \texttt{UseSpecialAlgorithms} is set to \texttt{true} and $f$ does not fall into any of the aforementioned cases, then the function \texttt{fpt} next calls \texttt{isSimpleNormalCrossing(f)} (see Section~\ref{subsec.SNC}) to check whether the polynomial $f$ defines (locally, at the origin) a simple normal crossing divisor, in which case the $F$-pure threshold is simply the reciprocal of the largest multiplicity occurring in that factorization.
 Note that the function \texttt{factor} is called whenever \texttt{isSimpleNormalCrossing} is used, and that can sometimes make the verification slow.
@@
 If  \texttt{Attempts} is set to at least \texttt{1}, then a first check is run to verify whether the right-hand endpoint $(\nu+1)/p^e$ of the above interval \eqref{estimating-interval: e} is the $F$-pure threshold.
-We illustrate this below.
+
+To illustrate these options, first we obtain a rather crude estimate for the $F$-threshold of a polynomial.
 
@@
 
-i10 : fpt(f, Attempts => 0) -- a bad estimate
+i10 : fpt(f, Attempts => 0)
 
@@
 o10 : List
+\end{MyVerbatim}
+}
+\smallskip
 
-i11 : fpt(f, Attempts => 0, DepthOfSearch => 3) -- a better estimate
+\noindent
+Increasing the depth of search, we obtain a better estimate.
+
+\smallskip
+{\small
+\setstretch{.67}
+\begin{MyVerbatim}
+i11 : fpt(f, Attempts => 0, DepthOfSearch => 3)
 
@@
 o11 : List
+\end{MyVerbatim}
+}
+\smallskip
 
-i12 : fpt(f, Attempts => 1, DepthOfSearch => 3) -- the right-hand endpoint
-      (ν+1)/p^e is the F-pure threshold
+\noindent
+Finally, increasing the number of attempts we find that the right-hand endpoint of the above interval is the desired $F$-pure threshold.
+
+\smallskip
+{\small
+\setstretch{.67}
+\begin{MyVerbatim}
+i12 : fpt(f, Attempts => 1, DepthOfSearch => 3)
 
@@
 o14 : List
+\end{MyVerbatim}
+}
+\smallskip
 
-i15 : fpt(f, Attempts => 2, DepthOfSearch => 3) -- the left-hand endpoint
-      ν/(p^e-1) is the F-pure threshold
+\noindent
+With \texttt{Attempts} set to \texttt{2}, we find that the left-hand endpoint of the above interval is the desired $F$-pure threshold.
+
+\smallskip
+{\small
+\setstretch{.67}
+\begin{MyVerbatim}
+i15 : fpt(f, Attempts => 2, DepthOfSearch => 3)
 
@@
 o24 : List
+\end{MyVerbatim}
+}
+\smallskip
 
+\noindent
+With \texttt{FinalAttempt} set to \texttt{true}, we can slightly improve this estimate.
+
+\smallskip
+{\small
+\setstretch{.67}
+\begin{MyVerbatim}
 i25 : numeric fpt(f, DepthOfSearch => 3, FinalAttempt => true)
-      -- FinalAttempt improves the estimate slightly
 
@@
 i29 : fpt(f, DepthOfSearch => 3, FinalAttempt => true, Verbose => true)
-
 Starting fpt ...
-
 fpt is not 1 ...
-
-Verifying if special algorithms apply...
-
+Verifying whether special algorithms apply...
 Special fpt algorithms were not used ...
-
 ν has been computed: ν = nu(3,f) = 17 ...
-
 fpt lies in the interval [ν/(p^e-1),(ν+1)/p^e] = [17/124,18/125] ...
-
 Starting guessFPT ...
-
 The right-hand endpoint is not the fpt ...
-
 The left-hand endpoint is not the fpt ...
-
 guessFPT narrowed the interval down to (7/50,18/125) ...
-
 Beginning F-signature computation ...
-
 First F-signature computed: s(f,(ν-1)/p^e) = 793/15625 ...
-
 Second F-signature computed: s(f,ν/p^e) = 342/15625 ...
-
 Computed F-signature secant line intercept: 8009/56375 ...
-
 F-signature intercept is an improved lower bound;
 Using F-regularity to check if it is the fpt ...
-
 The new lower bound is not the fpt ...
-
 fpt failed to find the exact answer; try increasing the value of
     DepthOfSearch or Attempts.
-
 fpt lies in the interval (8009/56375,18/125).
@@
 
-\subsection{The function \texttt{isSimpleNormalCrossings}} \label{subsec.SNC}
-As mentioned earlier, the function \texttt{isSimpleNormalCrossings} verifies whether a polynomial $f$ is a product of factors in simple normal crossing.
-Suppose that $f$ has factorization $f_1^{a_i} f_2^{a_2} \cdots f_n^{a_n}$.  Recall that its factors $f_i$ are said to be in
-\emph{simple normal crossing} at a point if, locally, they form part of a regular system of parameters.
-The function \texttt{isSimpleNormalCrossings} determines whether $f$ has simple normal crossings at the origin by computing the Jacobian matrix of each subset of $\{ f_1, \ldots, f_n \}$ (evaluated at the origin), and checking that these matrices have the expected rank, and that these subsets generate ideals of the appropriate height.
+\subsection{The function \texttt{isSimpleNormalCrossing}} \label{subsec.SNC}
+As mentioned earlier, the function \texttt{isSimpleNormalCrossing} verifies whether a polynomial $f$ defines a simple normal crossing divisor.
+Suppose that $f$ has factorization $f_1^{a_i} f_2^{a_2} \cdots f_n^{a_n}$.
+Recall that $f$ defines a simple normal crossing divisor at a point if, locally, its factors form part of a regular system of parameters.
+The function \texttt{isSimpleNormalCrossing} determines whether $f$ defines a simple normal crossing divisor at the origin by computing the Jacobian matrix of each subset of $\{ f_1, \ldots, f_n \}$ (evaluated at the origin), and checking that these matrices have the expected rank, and that these subsets generate ideals of the appropriate height.
 
@@
 
-The function \texttt{isSimpleNormalCrossing} is exposed to the user, so can be used independent of any $F$-pure threshold calculation.
-If the user sets its option \texttt{AtOrigin} to \texttt{false} (its default value is \texttt{true}), then the function checks whether the $f_i$ are in simple normal crossing \emph{everywhere}, which can be much slower, since Jacobian ideals are computed.
+The function \texttt{isSimpleNormalCrossing} is exposed to the user, so can be used independently of any $F$-pure threshold calculation.
+If the user sets its option \texttt{AtOrigin} to \texttt{false} (its default value is \texttt{true}), then the function checks whether $f$ defines a simple normal crossing divisor \emph{everywhere}, which can be much slower, since Jacobian ideals are computed.
 
@@
 
-i38 : f = (y - (x - 1)^2)*y^2; --SNC at the origin, but not globally
+i38 : f = (y - (x - 1)^2)*y^2;
 

### 2020-06-15 Fsing/FrobeniusThresholdsPaper/response_to_report_C_on_v2.txt
Updated responses to referees

@@
-190624-Witt-v2 (FrobeniusThresholds)
+We thank the referee for carefully checking the package, paper, and
+documentation, and for the helpful suggestions and corrections.
 
-The package consists of 3600 lines of code and documentation, so it is
-substantial.  It installs and the tests work without error.  The package is in
-pretty good shape.
+Below we address in detail each of the refereee's comments.
 

### 2020-06-16 Fsing/FrobeniusThresholdsPaper/response_to_report_C_on_v2.txt
Replaced nu with frobeniusNu

@@
 
+-----------------------------------------------------------------------------
+Done.
+-----------------------------------------------------------------------------
+
+*****************************************************************************
+
 Consider choosing a better name for the function "nu", which is simply the
@@
 
+-----------------------------------------------------------------------------
+We replaced "nu" with "frobeniusNu", which, although still not descriptive,
+at least establishes a context. Having "Nu" as part of the name allows the
+user to relate this to the terminology/notation used in the literature.
+-----------------------------------------------------------------------------
+
+*****************************************************************************
+
 Consider renaming "fpt" to "pureThreshold" and "isFPT" to "isPureThreshold".
 (The "F" for "Frobenius" can be assumed.)
+
+-----------------------------------------------------------------------------
+We chose to leave it unchanged, as "fpt" is a very standard abbreviation.
+-----------------------------------------------------------------------------
 

### 2020-06-16 Fsing/FrobeniusThresholdsPaper/FrobeniusThresholds.tex
Replaced nu with frobeniusNu

@@
 
-\section{The {\tt nu} function}
+\section{The {\tt frobeniusNu} function}
 \label{sec.Nu}
 
-We first describe the \texttt{nu} function, a fundamental component of the package \emph{FrobeniusThresholds}.
+We first describe the \texttt{frobeniusNu} function, a fundamental component of the package \emph{FrobeniusThresholds}.
 We adopt the setup established in the introduction: we work in a polynomial ring $R$ over a finite field of characteristic $p>0$,  $\idealm$ denotes the ideal generated by the variables, and $e$ is a natural number.
-If $I$ and $J$ are ideals of $R$, the command \texttt{nu(e,I,J)} outputs the extended integer $\nu_I^J(p^e)$ defined in the introduction; if $f$ is an element of $R$, \texttt{nu(e,f,J)} outputs $\nu_f^J(p^e) \coloneqq \nu_{\langle f \rangle}^J(p^e)$.
-When the third argument is omitted from the function \texttt{nu}, it is assumed to be the maximal ideal $\idealm$.
+If $I$ and $J$ are ideals of $R$, the command \texttt{frobeniusNu(e,I,J)} outputs the extended integer $\nu_I^J(p^e)$ defined in the introduction; if $f$ is an element of $R$, \texttt{frobeniusNu(e,f,J)} outputs $\nu_f^J(p^e) \coloneqq \nu_{\langle f \rangle}^J(p^e)$.
+When the third argument is omitted from the function \texttt{frobeniusNu}, it is assumed to be the maximal ideal $\idealm$.
 
-\smallskip
+\bigskip
 {\small
@@
 
-i4 : nu(2, I, J)
+i4 : frobeniusNu(2, I, J)
 
@@
 
-i6 : nu(2, f, J)
+i6 : frobeniusNu(2, f, J)
 
@@
 }
+\bigskip
 
-In general, the function \texttt{nu} works by searching through a list of integers $n$, and checking containments of the $n$-th power of $I$ in the specified Frobenius power of $J$.
+In general, the function \texttt{frobeniusNu} works by searching through a list of integers $n$, and checking containments of the $n$-th power of $I$ in the specified Frobenius power of $J$.
 It is well known that, for any positive integer $e$,
@@
 For instance, the error term $L$ is at most $p-1$ when $I$ is principal and $J$ is arbitrary.
-This implies that when searching for the maximal exponent defining \texttt{nu(e,I,J)} for positive $e$, it is safe to start at $p$ times the output of \texttt{nu(e-1,I,J)}, and one need not search too far past this number.
-% This also suggests that the most efficient way to compute \texttt{nu(e,I,J)} is to compute, successively, \texttt{nu(s,I,J)}, for each integer $s = 0,\ldots,e$, and this is indeed how the computation is done in most cases.
+This implies that when searching for the maximal exponent defining \texttt{frobeniusNu(e,I,J)} for positive $e$, it is safe to start at $p$ times the output of \texttt{frobeniusNu(e-1,I,J)}, and one need not search too far past this number.
+% This also suggests that the most efficient way to compute \texttt{frobeniusNu(e,I,J)} is to compute, successively, \texttt{frobeniusNu(s,I,J)}, for each integer $s = 0,\ldots,e$, and this is indeed how the computation is done in most cases.
 
-\subsection{Options for \texttt{nu}}
+\subsection{Options for \texttt{frobeniusNu}}
 
@@
 
-\smallskip
+\bigskip
 {\small
@@
 
-i9 : time nu(2, m, m^2)
+i9 : time frobeniusNu(2, m, m^2)
      -- used 1.82479 seconds
@@
 }
-%\medskip
-\smallskip
+\medskip
 
@@
 
-\smallskip
+\medskip
 {\small
@@
 \begin{MyVerbatim}
-i10 : time nu(2, m, m^2, Search => Linear)
+i10 : time frobeniusNu(2, m, m^2, Search => Linear)
      -- used 0.597035 seconds
@@
 }
-\smallskip
+\medskip
 
-%We now describe the options available for the function \texttt{nu}.
+%We now describe the options available for the function \texttt{frobeniusNu}.
 
-If the option \texttt{ReturnList} is changed from its default value of \texttt{false} to \texttt{true}, \texttt{nu} outputs a list of the values $\nu_I^J(p^s)$, for $s=0,\ldots,e$, at no additional computational cost.
+If the option \texttt{ReturnList} is changed from its default value of \texttt{false} to \texttt{true}, \texttt{frobeniusNu} outputs a list of the values $\nu_I^J(p^s)$, for $s=0,\ldots,e$, at no additional computational cost.
 
 % \medskip
-\smallskip
+\medskip
 {\small
@@
 \begin{MyVerbatim}
-i11 : nu(5, x^2*y^4 + y^2*z^7 + z^2*x^8, ReturnList => true)
+i11 : frobeniusNu(5, x^2*y^4 + y^2*z^7 + z^2*x^8, ReturnList => true)
 
@@
 where $(I^n)^{[1/p^e]}$ denotes the $p^e$-th \emph{Frobenius root} of $I^n$, as defined in \cite{BlickleMustataSmithDiscretenessAndRationalityOfFThresholds}.
-The option \texttt{ContainmentTest} for \texttt{nu} allows the user to choose which of the two types of containment statements appearing above to use toward the calculation of $\nu_I^J(p^e)$.
+The option \texttt{ContainmentTest} for \texttt{frobeniusNu} allows the user to choose which of the two types of containment statements appearing above to use toward the calculation of $\nu_I^J(p^e)$.
 
-If \texttt{ContainmentTest} is set to \texttt{StandardPower}, then \texttt{nu(e,I,J)} is computed by testing the left-hand containment above, and when it is set to \texttt{FrobeniusRoot}, the right-hand containment is checked.
-For efficiency reasons, the default value for \texttt{ContainmentTest} is set to  \texttt{FrobeniusRoot} if the second argument passed to \texttt{nu} is a polynomial, and is set to \texttt{StandardPower} if the second argument is an ideal.
+If \texttt{ContainmentTest} is set to \texttt{StandardPower}, then \texttt{frobeniusNu(e,I,J)} is computed by testing the left-hand containment above, and when it is set to \texttt{FrobeniusRoot}, the right-hand containment is checked.
+For efficiency reasons, the default value for \texttt{ContainmentTest} is set to  \texttt{FrobeniusRoot} if the second argument passed to \texttt{frobeniusNu} is a polynomial, and is set to \texttt{StandardPower} if the second argument is an ideal.
 
@@
 
-i14 : time nu(3, f) 
+i14 : time frobeniusNu(3, f) 
      -- used 0.153691 seconds
@@
 }
-\smallskip
+\medskip
 
@@
 \begin{MyVerbatim}
-i15 : time nu(3, f, ContainmentTest => StandardPower)
+i15 : time frobeniusNu(3, f, ContainmentTest => StandardPower)
      -- used 10.1343 seconds
@@
 }
-\smallskip
+\medskip
 
-The option \texttt{ContainmentTest} has a third possible value, \texttt{FrobeniusPower}, which allows \texttt{nu} to compute a different but analogous invariant.
+The option \texttt{ContainmentTest} has a third possible value, \texttt{FrobeniusPower}, which allows \texttt{frobeniusNu} to compute a different but analogous invariant.
 The first, third, and fourth authors introduced the notion of a (generalized) Frobenius power $I^{[n]}$ of an ideal $I$, when $n$ is an arbitrary nonnegative integer \cite{hernandez+etal.frobenius_powers}.
-When \texttt{ContainmentTest} is set to \texttt{FrobeniusPower}, rather than  computing $\nu_I^J(p^e)$, the function \texttt{nu} computes the maximal integer $n$ for which $I^{[n]}$ is not contained in $J^{[p^e]}$.
+When \texttt{ContainmentTest} is set to \texttt{FrobeniusPower}, rather than  computing $\nu_I^J(p^e)$, the function \texttt{frobeniusNu} computes the maximal integer $n$ for which $I^{[n]}$ is not contained in $J^{[p^e]}$.
 This number is denoted $\mu_I^J(p^e)$ in \emph{loc.~cit.}, and equals $\nu_I^J(p^e)$ when $I$ is a principal ideal.
@@
 
-i18 : nu(4, m^5)
+i18 : frobeniusNu(4, m^5)
 
@@
 
-i19 : nu(4, m^5, ContainmentTest => FrobeniusPower)
+i19 : frobeniusNu(4, m^5, ContainmentTest => FrobeniusPower)
 
@@
 
-i22 : time nu(10, f)
+i22 : time frobeniusNu(10, f)
      -- used 0.0161622 seconds
@@
 
-i23 : time nu(10, f, UseSpecialAlgorithms => false)
+i23 : time frobeniusNu(10, f, UseSpecialAlgorithms => false)
      -- used 2.06877 seconds
@@
 }
-\smallskip
+\medskip
 
-The last option we describe for \texttt{nu} is \texttt{AtOrigin}.
+The last option we describe for \texttt{frobeniusNu} is \texttt{AtOrigin}.
 Recall that $\nu_I^\idealm(p^e)$ can be interpreted as the maximum integer $n$ for which $(I^n)^{[1/p^e]}$ is not contained in $\idealm$. 
-When the option \texttt{AtOrigin} is set to \texttt{false} (from its default value \texttt{true}), the function \texttt{nu} determines, instead, the maximum integer $n$ for which $(I^n)^{[1/p^e]}$ is the unit ideal, which can also be characterized as the minimal integer $\nu_I^\mathfrak{n}(p^e)$ as $\mathfrak{n}$ varies among all maximal ideals of the ring.
+When the option \texttt{AtOrigin} is set to \texttt{false} (from its default value \texttt{true}), the function \texttt{frobeniusNu} determines, instead, the maximum integer $n$ for which $(I^n)^{[1/p^e]}$ is the unit ideal, which can also be characterized as the minimal integer $\nu_I^\mathfrak{n}(p^e)$ as $\mathfrak{n}$ varies among all maximal ideals of the ring.
 
-\smallskip
+\medskip
 {\small
@@
 
-i26 : nu(3, f)
+i26 : frobeniusNu(3, f)
 
@@
 
-i27 : nu(3, f, AtOrigin => false)
+i27 : frobeniusNu(3, f, AtOrigin => false)
 
@@
 }
-
-\smallskip
+\medskip
 
@@
 
-In the following example, we compute the $F$-pure threshold of a diagonal polynomial.
+In the example below, we compute the $F$-pure threshold of a diagonal polynomial.
 
-\smallskip
+\medskip
 {\small
@@
 More specifically, let $e$ denote the value of the option \texttt{DepthOfSearch}, which conservatively defaults to \texttt{1}.
-The \texttt{fpt} function first computes $\nu=\nu_f(p^e)$, which agrees with the output of \texttt{nu(e,f)}.
+The \texttt{fpt} function first computes $\nu=\nu_f(p^e)$, which agrees with the output of \texttt{frobeniusNu(e,f)}.
 It is well known that the $F$-pure threshold of $f$ is greater than $\nu/p^e$ and at most $(\nu+1)/p^e$, and applying  \cite[Proposition~4.2]{HernandezFPurityOfHypersurfaces} to the lower bound tells us that the $F$-pure threshold of $f$ must be at least $\nu/(p^e-1)$.
@@
 Special fpt algorithms were not used ...
-ν has been computed: ν = nu(3,f) = 17 ...
+ν has been computed: ν = frobeniusNu(3,f) = 17 ...
 fpt lies in the interval [ν/(p^e-1),(ν+1)/p^e] = [17/124,18/125] ...
@@
 }
-\smallskip
 
